### 2018-02-16 main.tex
add the macros file

%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2018}

\begin{document}

\twocolumn[
\icmltitle{Differentially Private Bayesian Inference}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2018
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
\end{abstract}

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\mathsf{BayesInfer}(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\mathsf{BayesInfer}(x)$.

For now, we already have a prior distribution $prior$, an observed data set $x$.

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_emgs}

\subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\mathsf{BayesInfer}(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\mathsf{Hlg}$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\mathsf{Hlg}(\mathsf{BayesInfer}(x), r); r \in R.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{multline*}
\Delta_{g}u = 
\mathsf{Hlg}(\mathsf{BayesInfer}(x'), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\mathsf{Hlg}$ is monotonic, i.e. our utility function is monotonic.

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\mathsf{BayesInfer}$ with privacy mechanism as $\mathsf{PrivInfer}$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right) \\
& \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

Then, $\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
\subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

where local sensitivity is calculated by:

\begin{multline*}
\Delta_{l}u(x) = 
\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

\subsubsection{Security Analysis}
We will then prove that exponential mechanism with local sensitivity is non-differentialy private.
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& = exp\left(
\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} - 
\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
\right)  \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
\right) \\
& = \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}.
\end{split}
\end{equation*}

Without loss of generality, we consider the case that $\Delta_{l}u(y) < \Delta_{l}u(x)$, $r = arg(\max\limits_{r' \in R}\{u(x,r')\}) = arg(\min\limits_{r' \in R}\{u(y,r')\})$ and $\Delta_{l}u(y) = u(x,r) - u(y,r)$. We have:
\begin{equation*}
\begin{split}
& \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}\\
& > \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(x,r) + u(y,r'))}{2 \Delta_{l}u(x)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(y,r) + u(x,r'))}{2 \Delta_{l}u(y)})}\\
& > \frac
{|R|\ exp(\frac{\epsilon (u(x,r) + u(y,r))}{2 \Delta_{l}u(x)})}
{|R|\ exp(\frac{\epsilon (u(y,r) + u(x,r))}{2 \Delta_{l}u(y)})}\\
& = exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)})).
\end{split}
\end{equation*}

From Eq. \ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \mathsf{BayesInfer}(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$. Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
\begin{equation*}
\begin{split}
- \Delta_{l}u(x) & < \Delta_{l}u(y) \\
\Delta_{l}u(x) - \Delta_{l}u(y) & < 2 \Delta_{l}u(x) \\
- \Delta_{l}u(y) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
u(y,r) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} & > 2.
\end{split}
\end{equation*}

% \begin{equation*}
% \begin{split}
% \frac{\Delta_{l}u(x)}{\Delta_{l}u(y)} & > 0\\
% & > \frac{\Delta_{l}u(x)}{2u(y,r)}\\
% & = \frac{\Delta_{l}u(x) + 0}{2u(y,r)} \\
% & = \frac{\Delta_{l}u(x) + 2 u(x,r)}{2u(y,r)}
% \end{split}
% \end{equation*}
holds.

Then we can have:
\begin{equation*}
\begin{split}
& exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)}))\\
& > exp(\frac{\epsilon}{2} * 2) \\
& = exp(\epsilon),
\end{split}
\end{equation*}
i.e.
\begin{equation*}
\begin{split}
\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]}
& > exp(\epsilon).
\end{split}
\end{equation*}

Since there are cases where exponential mechanism with local sensitivity's privacy loss is greater than $e^{\epsilon}$. we can say it is non-differentially private.
% \begin{equation*}
% \begin{split}
% & \epsilon = 0.1\\
% data size = 2\\
% the prior is Beta(2，2)\\
% data set x = [1,0,]\\
% data set y = [0,0]\\
% -0.313380201461\\
% -0.0\\
% -0.313380201461\\
% 3 3\\
% 0.313380201461\\
% 0.322043464396\\
% 0.355913071207\\
% 0.322043464396\\
% -0.0\\
% -0.313380201461\\
% -0.57735026919\\
% 2 4\\
% 0.375460728684\\
% 0.360050126956\\
% 0.331218326999\\
% 0.308731546045
% \end{split}
% \end{equation*}

% Without loss of generality, we consider the case that $\Delta_{l}u(y) > \Delta_{l}u(x)$ and $\Delta_{l}u(x) = u(x,r) - u(y,r)$. We have:
% \begin{equation*}
% \begin{split}
% exp\left(
% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
% \right)
% & > exp\left(
% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(x)}
% \right)\\
% & = exp\left(
% \frac{\epsilon u(x,r) - \epsilon u(y,r)}{2 \Delta_{l}u(x)}
% \right) \\
% & = exp(\frac{\epsilon}{2});
% \end{split}
% \end{equation*}

% \textcolor{red}{For the second part:
% , we have:
% \begin{equation*}
% \begin{split}
% \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(x)} 
% & < \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(y)}\\
% & \leq \frac{\epsilon}{2}
% \end{split}
% \end{equation*}
% I cannot replace $exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}(y)})$ in $\left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)$ with $ > exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}(x)})$.
% So, I cannot find the relationship between the whole part and $exp(\epsilon)$.}

% For the second part:
% \begin{equation*}
% \begin{split}
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)
% & < \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < exp(\frac{\epsilon}{2})
% \end{split}
% \end{equation*}

% For the second part(a tighter bound):
% \begin{equation*}
% \begin{split}
% & \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right) \\
% & = \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})}
% \right)\\
% & < exp(\frac{\epsilon}{2} - \frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \end{split}
% \end{equation*}

\subsection{Exponential Mechanism of Varying Sensitivity}
\label{subsec_emvs}
\subsubsection{Mechanism Setting up}

\subsubsection{Security Analysis}

\subsection{Exponential Mechanism of Smooth Sensitivity}
\label{subsec_emss}
\subsubsection{Mechanism Setting up}

\subsubsection{Security Analysis}

\section{Privacy Fix}

\subsection{Propositions}
Assume we have a prior distribution $beta(1,1)$, an observed data set $x \in \{0,1\}^n$, $n>0$. We use the $x+1$ and $x-1$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if\ BayesInfer}(x) = beta(a_1 + 1,b_1 + 1)\\
&\mathsf{then}\mathsf{\ BayesInfer}(x + 1) = beta((a_1 + 1) +1, (b_1 - 1)+1)\\
&\quad \quad \mathsf{\ BayesInfer}(x - 1) = beta((a_1 - 1) +1, (b_1 + 1)+1),\\
\end{split}
\end{equation*}
\end{small}

$x_0$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if}\ n\ is\ even\\
&\mathsf{then}\ \mathsf{BayesInfer}(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
&\mathsf{else}\ \mathsf{BayesInfer}(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
\end{split}
\end{equation*}
\end{small}

$\mathsf{beta}(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.

Then, we have the following three statements, and proofs of the statements.
\renewcommand{\labelenumi}{\Roman{enumi}}
\begin{enumerate}
\item $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$;

or $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) > \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\forall x \leq x_0$.

\item $\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x + 1)),\forall x \geq x_0$;

$\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x - 1)),\forall x \leq x_0$.

\item $\forall x \neq x_0: \Delta_{l}u(x) > \Delta_{l}u(x_0)$.
\end{enumerate}

\subsection{proof}

\subsubsection{Statement I}
We use the MI (Mathematical Induction) method to prove the first statement.

\begin{proof}
Since the Hellinger distance is symmetric, if we prove the $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.

1. if $x = x_0$, $\mathsf{Hlg} (\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x_0 + 1), \mathsf{BayesInfer}(x_0 + 2))$ holds:

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\mathsf{Hlg}(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \mathsf{Hlg}(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\mathsf{beta}(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\mathsf{beta}(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

Since $n > 0$, it always holds.

2. if $x = x_0 + m$ holds, then also $x = x_0 + m + 1$ holds:

i.e $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
is what we know:

\begin{small}
\begin{equation*}
\begin{split}
& \sqrt{
1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}\\
& < \sqrt{
1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
& \frac{\mathsf{beta}(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}\\
& > \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

Now, we need to proof $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.

From $x = x_0 + m$ and property of $\mathsf{beta}(\alpha, \beta)$ function, we know:
\vspace*{9.5cm}

\begin{footnotesize}
\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \mathsf{Hlg}(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \mathsf{Hlg}(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}

i.e. $ x = x_0 + m + 1$ also holds when $x = x_0 + m$ is valid.
\end{proof}

\subsubsection{Statement II}
\begin{proof}

\begin{equation*}
\begin{split}
\because \quad 		& \Delta_l u(x) = |\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)\\
					& \leq \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y'));\\
\therefore \quad 	& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
					&< \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 - 1))\\
					& \quad \quad \quad = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)). \\
\end{split}
\end{equation*}

From above, we can conclude the Statement II.

\end{proof}

\subsubsection{Statement III}
\begin{proof}
From Statement I and Statement II, we can conclude that:
\begin{equation*}
\begin{split}
\mathsf{when} \quad	& x > x_0 \\
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1) \\
					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
\mathsf{when} \quad	& x < x_0 \\
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1) \\
					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 - 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
\end{split}
\end{equation*}

i.e $\forall \ x \neq x_0, \Delta_l u(x) > \Delta_l u(x_0)$.

\end{proof}

\section{Experimental Evaluations}
We got some results from these mechanisms.

\bibliographystyle{icml2018}
\bibliography{example_paper}

\end{document}

### 2018-02-16 main.tex
update macros file

@@
 \label{sec_setup}
-The Bayesian inference process is denoted as $\mathsf{BayesInfer}(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
-For conciseness, when prior is given, we use $\mathsf{BayesInfer}(x)$.
+The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
+For conciseness, when prior is given, we use $\bysinfer(x)$.
 
@@
 \begin{equation*}
-R = \{\mathsf{BayesInfer}(y)\ |\ y \in \mathcal{X}^n\}.
+R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
 \end{equation*}
 
-Hellinger distance $\mathsf{Hlg}$ is used here to score these candidates. The utility function:
+Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
 \begin{equation}
 \label{equ_utility}
-u(x,r) = -\mathsf{Hlg}(\mathsf{BayesInfer}(x), r); r \in R.
+u(x,r) = -\hlg(\bysinfer(x), r); r \in R.
 \end{equation}
@@
 \Delta_{g}u = 
-\mathsf{Hlg}(\mathsf{BayesInfer}(x'), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
+\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|\\
 \max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
@@
 % We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
-Since $\mathsf{Hlg}$ is monotonic, i.e.
+Since $\hlg$ is monotonic, i.e.
 our utility function is monotonic.
@@
 It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\mathsf{BayesInfer}$ with privacy mechanism as $\mathsf{PrivInfer}$.
+We denote the $\bysinfer$ with privacy mechanism as $\mathsf{PrivInfer}$.
 For adjacent data set $||x,y||_1 = 1$:
@@
 \Delta_{l}u(x) = 
-\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
+\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\\
 \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
@@
 From Eq.
-\ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \mathsf{BayesInfer}(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$.
+\ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \bysinfer(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$.
 Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
@@
 &\mathsf{if}\ n\ is\ even\\
-&\mathsf{then}\ \mathsf{BayesInfer}(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
-&\mathsf{else}\ \mathsf{BayesInfer}(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
+&\mathsf{then}\ \bysinfer(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
+&\mathsf{else}\ \bysinfer(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
 &\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
@@
 \begin{enumerate}
-\item $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$;
+\item $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$;
 
-or $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) > \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\forall x \leq x_0$.
+or $\hlg (\bysinfer(x), \bysinfer(x + 1)) > \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\forall x \leq x_0$.
 
-\item $\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x + 1)),\forall x \geq x_0$;
+\item $\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x + 1)),\forall x \geq x_0$;
 
-$\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x - 1)),\forall x \leq x_0$.
+$\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x - 1)),\forall x \leq x_0$.
 
@@
 \begin{proof}
-Since the Hellinger distance is symmetric, if we prove the $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.
+Since the Hellinger distance is symmetric, if we prove the $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.
 
-1. if $x = x_0$, $\mathsf{Hlg} (\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x_0 + 1), \mathsf{BayesInfer}(x_0 + 2))$ holds:
+1. if $x = x_0$, $\hlg (\bysinfer(x_0), \bysinfer(x_0 + 1)) < \hlg (\bysinfer(x_0 + 1), \bysinfer(x_0 + 2))$ holds:
 
@@
 \begin{split}
-\mathsf{Hlg}(
+\hlg(
 beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
 beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
-& <  \mathsf{Hlg}(
+& <  \hlg(
 beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
@@
 
-i.e $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
-< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
+i.e $\hlg(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
+< \hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
 is what we know:
@@
 
-Now, we need to proof $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
-< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.
+Now, we need to proof $\hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
+< \hlg(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.
 
@@
 \\
-& \mathsf{Hlg}(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
-< & \mathsf{Hlg}(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
+& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
+< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
 \end{split}
@@
 \begin{split}
-\because \quad 		& \Delta_l u(x) = |\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|,\\
+\because \quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
 					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
-\because \quad 		& \mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)\\
-					& \leq \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y'));\\
-\therefore \quad 	& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y')),\\
+\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
+					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
+\therefore \quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
 					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
-\therefore \quad 	& \Delta_l u(x) = \max \{\mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)),\\
-					& \quad \quad \quad \quad \quad \quad \quad \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\};\\
+\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
+					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
 					& According\ to\ Statement\ I:\\
@@
 \mathsf{then} \quad	
-					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
-					&< \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
+					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
 \mathsf{then} \quad	
-					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
+					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
 \mathsf{if}	 \quad	& x < x_0 \\
 \mathsf{then} \quad	
-					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
-					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)); \\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
+					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
 \mathsf{then} \quad	
-					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1));\\
+					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
 \mathsf{else} \quad	
-					& \Delta_l u(x_0) = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 - 1))\\
-					& \quad \quad \quad = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)). \\
+					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
+					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
 \end{split}
@@
 \mathsf{when} \quad	& x > x_0 \\
-					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1) \\
-					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1); \\
+					& \hlg(\bysinfer(x), \bysinfer(x + 1) \\
+					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
 					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
 \mathsf{when} \quad	& x < x_0 \\
-					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1) \\
-					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 - 1); \\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1) \\
+					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
 					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\

### 2018-02-16 main.tex
update macros

@@
 
-$\mathsf{beta}(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.
+$\betafun(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.
 
@@
 beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
-\sqrt{1 - \frac{\mathsf{beta}(
+\sqrt{1 - \frac{\betafun(
 \frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
@@
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
+\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
+\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
 }
@@
 }
-& < \sqrt{1 - \frac{\mathsf{beta}(
+& < \sqrt{1 - \frac{\betafun(
 \frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
@@
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
-\mathsf{beta}(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
+\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
+\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
 }
@@
 }\\
-\sqrt{1 - \frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
+\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
+\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
+\betafun(\frac{n}{2} + 2, \frac{n}{2})
 }
@@
 }
-& < \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
+& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
-\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
+\betafun(\frac{n}{2} + 2, \frac{n}{2})
+\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
 }
@@
 }\\
-\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
+\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
+\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
+\betafun(\frac{n}{2} + 2, \frac{n}{2})
 }
 }
-& > \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
+& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
-\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
+\betafun(\frac{n}{2} + 2, \frac{n}{2})
+\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
 }
 }\\
-\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n - 1}{2}) 
+\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
 \frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
+\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
 \frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
@@
 & > \frac{
-\mathsf{beta}(\frac{n + 3}{2}, \frac{n - 1}{2}) 
+\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
 \frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
+\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
 \frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
@@
 & \sqrt{
-1 - \frac{\mathsf{beta}(
+1 - \frac{\betafun(
 \frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
@@
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
 }
@@
 & < \sqrt{
-1 - \frac{\mathsf{beta}(
+1 - \frac{\betafun(
 \frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
@@
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }
@@
 \\
-& \frac{\mathsf{beta}(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
+& \frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
 }
 }\\
-& > \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
+& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }
@@
 
-From $x = x_0 + m$ and property of $\mathsf{beta}(\alpha, \beta)$ function, we know:
+From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:
 \vspace*{9.5cm}
@@
 \begin{split}
-& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
+& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
 \frac{n - 2m - 1}{n + 2m + 3}}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 \frac{n - 2m}{n + 2m + 2}
@@
 }\\
-> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
+> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
 \frac{n - 2m - 3}{n + 2m + 5}}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 \frac{n - 2m - 2}{n + 2m + 6}
@@
 \begin{split}
-& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
+& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }
 }\\
-> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
+> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }
@@
 \\
-& \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
+& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }
 }}\\
-< & \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
+< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
 {\sqrt{
-\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
+\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
+\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
 }

### 2018-03-12 main.tex
dilation property proof
update dilation property proof

@@
 
+\section{Dilation Property of Laplace Noise}
+\label{sec_Dila}
+\begin{proof}
+We take 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$.
+The dilation property is:
+\begin{equation*}
+Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
+\end{equation*}
+In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/2}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.
+
+\begin{itemize}
+	\item \textbf{case 1: $\lambda > 0$}
+
+	\begin{equation*}
+	\begin{split}
+	\because\ 		& 	h(e^{\lambda} z) =  \frac{1}{2} e^{-|e^{\lambda} z|} < \frac{1}{2} e^{-|z|} = h(z)\\
+	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
+						= \frac
+						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
+						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
+						= \frac
+						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
+						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
+					&	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
+						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}
+						\leq e^{\lambda}\\
+	\therefore\		&	ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)})
+						\leq \lambda \\
+	\because\		&	\\
+	\end{split}
+	\end{equation*}
+
+	\item \textbf{case 2: $\lambda < 0$}
+	\begin{equation*}
+	\begin{split}
+	\because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
+	\therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
+	\end{split}
+	\end{equation*}
+
+\end{itemize}
+
+\end{proof}
+
 \bibliographystyle{icml2018}

### 2018-03-16 main.tex
update dilation proof

@@
 \end{equation*}
-In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/2}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.
+In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.
 
@@
 						\leq \lambda \\
-	\because\		&	\\
+	\because\		&	\lambda \leq \beta = \frac{\epsilon}{2 ln(3 / \delta)}, \delta < 1 \\
+	\therefore\		&	\lambda \leq \frac{\epsilon}{2} \\
+	\therefore\		&	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} \leq \frac{\epsilon}{2} \\
 	\end{split}
@@
 
+	We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:
+
+	\begin{equation*}
+	|z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
+	\end{equation*}
+
+	We start from the thing we want to proof:
+
+	\begin{equation*}
+	Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} \in e^{\lambda} S] + \frac{\delta}{2}
+	\end{equation*}
+
+	\begin{equation*}
+	Pr[z \in S] \leq Pr[z \in S  G]
+	\end{equation*}
+
 \end{itemize}

### 2018-03-26 main.tex
dilation update
update proof of laplace dilation property.

@@
 \usepackage{amsthm}
+\usepackage{mathtools}
 \usepackage{mdframed}
@@
 	\item \textbf{case 2: $\lambda < 0$}
+	% \begin{equation*}
+	% \begin{split}
+	% \because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
+	% \therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
+	% \end{split}
+	% \end{equation*}
+
+	% We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:
+
+	% \begin{equation*}
+	% |z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
+	% \end{equation*}
+
+	% Also, from the Laplace distribution property we have:
+
+	% \begin{equation*}
+	% Pr[G] \geq 1 - \delta ;
+	% \end{equation*}
+
+	% \begin{equation*}
+	% Pr[\overline{G}] \leq \delta .
+	% \end{equation*}
+
+	% We start from the thing we want to proof:
+
+	% \begin{equation*}
+	% Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2};
+	% \end{equation*}
+
+	% \begin{equation*}
+	% \begin{split}
+	% \underset{z \thicksim Lap(1)}{Pr}[z \in S] \leq & Pr[z \in S \cap G] + Pr[z \in \overline{G}]\\
+	% \leq 	& Pr[z \in S \cap G] + \delta\\
+	% \leq 	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S \cap G] + \delta \\
+	% \leq	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
+	% \leq	& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
+	% =		& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(1)}{Pr}[z \in e^{\lambda} S] + \delta\\
+	% \end{split}
+	% \end{equation*}
+	From integral property, we firstly have:
+
+	\begin{equation*}
+	\frac{Pr[z\in e^{\lambda} S]}{Pr[z\in S]} 
+	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} 
+	= \frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} 
+	= e^{\lambda}e^{|z|(1 - e^{\lambda})}
+	\end{equation*}
+
 	\begin{equation*}
 	\begin{split}
-	\because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
-	\therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
+	\because\	& 1 - e^{\lambda} \leq |\lambda| \\
+	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
+	\leq \lambda + |z||\lambda|\\
+	\because\	& \lambda < 0\\
+	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
+	\leq |z||\lambda|\\
 	\end{split}
@@
 
-	We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:
+	By setting $h'(z) = e^{\lambda} h(e^{\lambda} z)$, we can get:
 
 	\begin{equation*}
-	|z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
+	\begin{split}
+	&\ln(\frac{h'(z)}{h(z)}) \leq |z||\lambda|\\
+	\Rightarrow & h'(z)\leq  e^{|z||\lambda|}h(z)
+	\end{split}
 	\end{equation*}
 
-	We start from the thing we want to proof:
+	By exchanging the notation of $h'$ and $h$, we have:
 
 	\begin{equation*}
-	Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} \in e^{\lambda} S] + \frac{\delta}{2}
+	h(z) \leq e^{|z||\lambda|}h'(z)
 	\end{equation*}
 
+	i.e.
+
 	\begin{equation*}
-	Pr[z \in S] \leq Pr[z \in S  G]
+	\underset{z \thicksim h}{Pr}[z \in S] 
+	\leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S]
+	= e^{|z||\lambda|}\underset{z \thicksim h}{Pr}[z \in e^{\lambda} S]
+	\end{equation*}
+
+	We consider an event $G = \{z |\ |z|\leq log(\frac{2}{\delta}) \}$. Under this event, we have:
+
+	\begin{equation*}
+	\begin{split}
+	|z||\lambda| 	& \leq log(\frac{2}{\delta})|\lambda|\\
+					& \leq log(\frac{2}{\delta}) \beta\\
+					&\leq log(\frac{2}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \\
+					&\leq \frac{\epsilon}{2}.
+	\end{split}
+	\end{equation*}
+
+	Then:
+
+	\begin{equation*}
+	\begin{split}
+	\underset{z \thicksim h}{Pr}[z \in S \cap G] 
+	& \leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S\cap G]\\
+	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G]\\
+	\end{split}
+	\end{equation*}
+
+	We also have:
+
+	\begin{equation*}
+	Pr[\overline{G}] = Pr[|z| > log(\frac{2}{\delta})] = exp(-log(\frac{2}{\delta})) = \frac{\delta}{2}
+	\end{equation*}
+
+	Then, we can get
+
+	\begin{equation*}
+	\begin{split}
+	\underset{z \thicksim h}{Pr}[z \in S] 
+	& \leq \underset{z \thicksim h}{Pr}[z \in S\cap G] + \underset{z \thicksim h}{Pr}[z \in \overline{G}]\\
+	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G] + \frac{\delta}{2}\\ 
+	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S] + \frac{\delta}{2}\\ 
+	& = e^{\frac{\epsilon}{2}} \underset{z \thicksim h}{Pr}[z \in e^{\lambda} S] + \frac{\delta}{2}\\ 
+	\end{split}
 	\end{equation*}

### 2018-03-29 main.tex
update laplace dilation
update  expomech proof
update exponential mech

@@
 % Attempt to make hyperref and algorithmic work together better:
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
 % \newenvironment{proofof}[1]{\par
@@
 
-\section{Dilation Property of Laplace Noise}
+\section{Smooth sensitivity}
+\label{sec_smoo}
+
+\subsection{Dilation Property of Laplace Noise}
 \label{sec_Dila}
-\begin{proof}
-We take 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$.
-The dilation property is:
+\begin{lem}
+For 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$.
+We have some prior knowledge that $|\lambda| \leq \beta$, the $h$ has dilation property:
 \begin{equation*}
@@
 \end{equation*}
-In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.
+\end{lem}
+
+\begin{proof}
 
@@
 
+	i.e. the dilation property.
+
 \end{itemize}
@@
 \end{proof}
+
+\subsection{Sliding Property of Exponential Mechanism}
+\begin{lem}
+for any exponential mechanism $\mathcal{M}_E(x, u, \mathcal{R})$ $Pr[]$
+\end{lem}
+\begin{proof}
+\end{proof}
+
+\subsection{Dilation Property of Exponential Mechanism}
 

### 2018-03-29 main.tex
fix problem in laplace dilation property

@@
 \begin{lem}
-For 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$.
-We have some prior knowledge that $|\lambda| \leq \beta$, the $h$ has dilation property:
+For 1-dimensional Laplace distribution: $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$ and $|\lambda| \leq \beta$, the dilation property holds for any $z$ sampled from $h$:
 \begin{equation*}
@@
 \begin{itemize}
+
+	From the integral substitution property, we have:
+
+	\begin{equation*}
+	\begin{split}
+	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
+						= &\frac
+						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
+						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
+						= \frac
+						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
+						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
+						= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
+						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
+	\end{split}
+	\end{equation*}
+
+	Then, we proof the property in cases of $\lambda > 0$ and $\lambda < 0$:
+
 	\item \textbf{case 1: $\lambda > 0$}
@@
 	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
-						= \frac
-						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
-						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
-						= \frac
-						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
-						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
-					&	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
+					% 	= \frac
+					% 	{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
+					% 	{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
+					% 	= \frac
+					% 	{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
+					% 	{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
+					% &	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
 						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}

### 2018-03-29 main.tex
format update

@@
-%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+\input{macros}
 
-\documentclass{article}
-% \usepackage[utf8]{inputenc}
-% \usepackage[english]{babel}
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{mathtools,amssymb}
-\usepackage{microtype}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{mathtools}
-\usepackage{mdframed}
-\usepackage{subfigure}
-\usepackage{booktabs} % for professional tables
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
-\usepackage{hyperref}
-% \renewcommand\qedsymbol{$\blacksquare$}
-% \theoremstyle{plain}
-%   \newtheorem{thm}{Theorem}
-% \theoremstyle{definition}
-%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
-% Attempt to make hyperref and algorithmic work together better:
-% \newenvironment{proofof}[1]{\par
-%   \pushQED{\qed}%
-%   \normalfont \topsep6\p@\@plus6\p@\relax
-%   \trivlist
-%   \item[\hskip\labelsep
-%         \bfseries
-%     Proof of #1\@addpunct{.}]\ignorespaces
-% }{%
-%   \popQED\endtrivlist\@endpefalse
-% }
-% Use the following line for the initial blind version submitted for review:
-\usepackage{icml2018}
-\input{macros}
-% If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2018}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Submission and Formatting Instructions for ICML 2018}
+\title{\textbf{Notes of DP - Bayesian Inference}\\}
+\author{Jiawen \textsc{Liu}}
 
 \begin{document}
-
-\twocolumn[
-\icmltitle{Differentially Private Bayesian Inference}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2018
-% package.
-
-% List of affiliations: The first argument should be a (short)
-% identifier you will use later to specify author affiliations
-% Academic affiliations should list Department, University, City, Region, Country
-% Industry affiliations should list Company, City, Region, Country
-
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
-
-\begin{icmlauthorlist}
-\icmlauthor{Aeiau Zzzz}{equal,to}
-\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-\icmlauthor{Cieua Vvvvv}{goo}
-\icmlauthor{Iaesut Saoeu}{ed}
-\icmlauthor{Fiuea Rrrr}{to}
-\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
-\icmlauthor{Aaoeu Iasoh}{goo}
-\icmlauthor{Buiui Eueu}{ed}
-\icmlauthor{Aeuia Zzzz}{ed}
-\icmlauthor{Bieea C.~Yyyy}{to,goo}
-\icmlauthor{Teoau Xxxx}{ed}
-\icmlauthor{Eee Pppp}{ed}
-\end{icmlauthorlist}
-
-\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
-
-\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
-
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine Learning, ICML}
-
-\vskip 0.3in
-]
-
-% this must go after the closing bracket ] following \twocolumn[ ...
-
-% This command actually creates the footnote in the first column
-% listing the affiliations and the copyright notice.
-% The command takes one argument, which is text to display at the start of the footnote.
-% The \icmlEqualContribution command is standard text for equal contribution.
-% Remove it (just {}) if you do not need this facility.
-
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
-
-\begin{abstract}
-\end{abstract}
-
 \section{Setting up}
@@
 where global sensitivity is calculated by:
-\begin{multline*}
+\begin{equation*}
 \Delta_{g}u = 
-\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|\\
-\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
-\end{multline*}
+\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}
+|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
+\end{equation*}
 
@@
 It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\bysinfer$ with privacy mechanism as $\mathsf{PrivInfer}$.
+We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
 For adjacent data set $||x,y||_1 = 1$:
@@
 \begin{split}
-& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
+\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
 & =\frac
@@
 {2 \Delta_{g}u}
-\right) \\
-& \cdot
+\right)
+\cdot
 \left(\frac
@@
 
-Then, $\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
+Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
 
@@
 \begin{split}
-& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
+\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} 
 & = exp\left(
@@
 \begin{split}
-\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]}
+\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
 & > exp(\epsilon).
@@
 \begin{equation*}
-\boxed{
 \begin{split}
@@
 \end{split}
-}
 \end{equation*}
@@
 From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:
-\vspace*{9.5cm}
 
@@
 \begin{split}
-\because \quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
+\because \footnote{the symbol of $\because$ here means because}
+\quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
 					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
@@
 					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
-\therefore \quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
+\therefore \footnote{the symbol of $\therefore$ here means therefore}
+\quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
 					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
@@
 		{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
-						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
-						= \frac
+		{\int_{S}{} \frac{1}{2}e^{-|z|} dz} \\
+		= &\frac
 		{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
 		{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
-						= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
-						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
+		= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} \\
+		= & \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
 	\end{split}
@@
 
-	Then, we proof the property in cases of $\lambda > 0$ and $\lambda < 0$:
+	Then, we proof the dilation property in cases of $\lambda > 0$ and $\lambda < 0$ separately:
 
@@
 \begin{lem}
-for any exponential mechanism $\mathcal{M}_E(x, u, \mathcal{R})$ $Pr[]$
+for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the sliding property holds:
+
+\begin{equation*}
+\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}] \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2}
+\end{equation*}
+
 \end{lem}
+
 \begin{proof}
@@
 
-\bibliographystyle{icml2018}
-\bibliography{example_paper}
+% \bibliographystyle{icml2018}
+% \bibliography{example_paper}
 

### 2018-03-29 main.tex
update sliding property of expomech

@@
 
-\begin{multline*}
+\begin{equation*}
 \Delta_{l}u(x) = 
-\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\\
 \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
-\end{multline*}
+\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
+\end{equation*}
 
@@
 \begin{split}
-& \frac
+\frac
 {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
@@
 {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
-+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}\\
++ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
 & > \frac
@@
 % \twocolumn{
+\begin{small}
 \begin{equation*}
@@
 \end{equation*}
+\end{small}
 
@@
 
-\begin{footnotesize}
+\begin{small}
 \begin{equation*}
@@
 \end{equation*}
-\end{footnotesize}
+\end{small}
 
@@
 \end{proof}
-
-\section{Experimental Evaluations}
-We got some results from these mechanisms.
 
@@
 \begin{equation*}
-\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}] \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2}
+\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+\leq
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
 \end{equation*}
+where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
+\begin{equation*}
+S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
+\end{equation*}
+where $\beta = \beta(\epsilon, \delta)$.
 
@@
 \begin{proof}
+We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
+\begin{equation*}
+\begin{split}
+LHS 
+  = \underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL_x}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL_x}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+\end{split}
+\end{equation*}
+
+By bounding the $\Delta \geq -S(x)$, we can get:
+
+\begin{equation*}
+\begin{split}
+\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
+& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{\epsilon}{2}}\\
+&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+\end{split}
+\end{equation*}
+
 \end{proof}
@@
 \subsection{Dilation Property of Exponential Mechanism}
+
+\section{Experimental Evaluations}
+We got some results from these mechanisms.
 

### 2018-04-02 main.tex
update title
update dilation expomech
update format
update

@@
 \title{\textbf{Notes of DP - Bayesian Inference}\\}
-\author{Jiawen \textsc{Liu}}
+% \author{Jiawen \textsc{Liu}}
+\date{\vspace{-10ex}}
 
 \begin{document}
+\maketitle
+
 \section{Setting up}
@@
 \begin{split}
-& \sqrt{
+\sqrt{
 1 - \frac{\betafun(
@@
 }
-}\\
+}
 & < \sqrt{
@@
 \\
-& \frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
+\frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
 {\sqrt{
@@
 }
-}\\
+}
 & > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
@@
 \begin{split}
-& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
+ \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
 \frac{n - 2m - 1}{n + 2m + 3}}
@@
 }
-}\\
+}
 > & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
@@
 \begin{split}
-& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
+\frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
 {\sqrt{
@@
 }
-}\\
+}
 > & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
@@
 \\
-& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
+\sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
 {\sqrt{
@@
 }
-}}\\
+}}
 < & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
@@
 \\
-& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
+\hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))
 < & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
@@
 \because \footnote{the symbol of $\because$ here means because}
-\quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
-					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
-\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
-					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
+\quad 		& \Delta_l u(x) = \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}} |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
+\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r) \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
 \therefore \footnote{the symbol of $\therefore$ here means therefore}
-\quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
-					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
-\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
-					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
+\quad 	& \Delta_l u(x) = \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}} \hlg(\bysinfer(x), \bysinfer(y')),\\
+\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)), \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
 					& According\ to\ Statement\ I:\\
@@
 \mathsf{then} \quad	
-					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
-					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1)) < \hlg(\bysinfer(x), \bysinfer(x + 1));\\
 \mathsf{then} \quad	
@@
 \mathsf{then} \quad	
-					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
-					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1))  > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
 \mathsf{then} \quad	
@@
 \mathsf{else} \quad	
-					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
-					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
+					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1)) = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
 \end{split}
@@
 \mathsf{when} \quad	& x > x_0 \\
-					& \hlg(\bysinfer(x), \bysinfer(x + 1) \\
-					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
+					& \hlg(\bysinfer(x), \bysinfer(x + 1) > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
 					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
 \mathsf{when} \quad	& x < x_0 \\
-					& \hlg(\bysinfer(x), \bysinfer(x - 1) \\
-					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
+					& \hlg(\bysinfer(x), \bysinfer(x - 1)  > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
 					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
@@
 \subsection{Dilation Property of Exponential Mechanism}
+\begin{lem}
+for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the dilation property holds:
+
+\begin{equation*}
+\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+\leq
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
+\end{equation*}
+where the sensitivity in mechanism is still smooth sensitivity as above.
+\end{lem}
+
+\begin{proof}
+
+\begin{equation*}
+\begin{split}
+\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
+& \leq \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
+exp(\frac{\epsilon \hat{s}}{2 S(x)})
+& \leq exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
+\frac{\epsilon \hat{s}}{2 S(x)}
+& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
+\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
+(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
+\end{split}
+\end{equation*}
+
+To proof this, we discuss some cases:
+\begin{itemize}
+	\item $\lambda > 0$
+	\begin{itemize}
+		\item $u(x,r) > 0$
+		\item $u(x,r) < 0$
+	\end{itemize}
+	\item $\lambda < 0$
+	\begin{itemize}
+		\item $u(x,r) > 0$
+		\item $u(x,r) < 0$
+	\end{itemize}
+\end{itemize}
+
+\end{proof}
 

### 2018-04-03 main.tex
update

@@
 To proof this, we discuss some cases:
+
+Since the sensitivity is always greater than 0, but the utility function and $\lambda$ can be positive or negative. That's what we need to discuss.
+
 \begin{itemize}
@@
 		\item $u(x,r) > 0$
+
+		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
+
 		\item $u(x,r) < 0$
+
+		This need to be discuss further.
+
 	\end{itemize}
@@
 		\item $u(x,r) > 0$
+
+		This need to be discuss further.
+
 		\item $u(x,r) < 0$
+
+		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
+
 	\end{itemize}
 \end{itemize}
+
+So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
 
@@
 
-% \bibliographystyle{icml2018}
-% \bibliography{example_paper}
-
 \end{document}

### 2018-04-03 main.tex
dilation property for expomech

@@
 
-		This need to be discuss further.
+		% This need to be discuss further.
+		We can have:
+		\begin{equation*}
+		\lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
+		\end{equation*}
 
@@
 
-		This need to be discuss further.
+		% This need to be discuss further.
+		We can have:
+		\begin{equation*}
+		\lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
+		\end{equation*}
+		Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
 
@@
 
-So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
+In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.
+
+% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
+
+% We take the absolute value of utility function, then there is only one case we need to discuss: $(1 - e^{\lambda}) |\hat{s}| \leq S(x)$, $\lambda < 0$.
 

### 2018-04-09 main.tex
update dilation proof

@@
 \begin{equation*}
-\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+\underset{z \thicksim \expomech}{Pr}[u(z) = \hat{s}]
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
 \end{equation*}
@@
 	\begin{itemize}
-		\item $u(x,r) > 0$
+		\item $u(r) > 0$
 
@@
 
-		\item $u(x,r) < 0$
+		\item $u(r) < 0$
 
 		% This need to be discuss further.
-		We can have:
-		\begin{equation*}
-		\lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
-		\end{equation*}
+		% We can have:
+		% \begin{equation*}
+		% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
+		% \end{equation*}
 
@@
 	\begin{itemize}
-		\item $u(x,r) > 0$
+		\item $u(r) > 0$
 
 		% This need to be discuss further.
-		We can have:
-		\begin{equation*}
-		\lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
-		\end{equation*}
-		Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
+		% We can have:
+		% \begin{equation*}
+		% \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
+		% \end{equation*}
+		% Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
 
-		\item $u(x,r) < 0$
+		\item $u(r) \leq 0$
 
@@
 
-In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.
+% In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.
+
+In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, we only need to consider the case $u(r) \leq 0$.
+
+Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the event $G = \{\lambda > 0, u(r) \leq 0\}$ is:
+\begin{equation*}
+u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+\end{equation*}
+By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with:
+\begin{equation*}
+\begin{split}
+Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
+\end{split}
+\end{equation*}
+In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
+\begin{equation*}
+\begin{split}
+Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
+& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
+\end{split}
+\end{equation*}
+
+When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
 

### 2018-04-09 main.tex
update dilation property

@@
 
-Since the sensitivity is always greater than 0, but the utility function and $\lambda$ can be positive or negative. That's what we need to discuss.
+The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two event that $G=\{\lambda < 0\}$, and $\overline{G} = \{\lambda > 0\}$:
 
 \begin{itemize}
-	\item $\lambda > 0$
-	\begin{itemize}
-		\item $u(r) > 0$
+
+	\item $\lambda < 0$
+	% \begin{itemize}
+		% \item $u(r) > 0$
+
+		% % This need to be discuss further.
+		% % We can have:
+		% % \begin{equation*}
+		% % \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
+		% % \end{equation*}
+		% % Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
+		% \item $u(r) \leq 0$
 
 		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
+	\item $\lambda > 0$
+	% \begin{itemize}
+	% 	% \item $u(r) > 0$
 
-		\item $u(r) < 0$
+	% 	% The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
 
-		% This need to be discuss further.
-		% We can have:
-		% \begin{equation*}
-		% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
-		% \end{equation*}
+	% 	% \item $u(r) < 0$
 
-	\end{itemize}
-	\item $\lambda < 0$
-	\begin{itemize}
-		\item $u(r) > 0$
+	% 	% This need to be discuss further.
+	% 	% We can have:
+	% 	% \begin{equation*}
+	% 	% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
+	% 	% \end{equation*}
 
-		% This need to be discuss further.
-		% We can have:
-		% \begin{equation*}
-		% \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
-		% \end{equation*}
-		% Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
-
-		\item $u(r) \leq 0$
-
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
-
-	\end{itemize}
+	% \end{itemize}
+	% \end{itemize}
 \end{itemize}
@@
 
-In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, we only need to consider the case $u(r) \leq 0$.
+In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.
 

### 2018-04-10 main.tex
fix bugs

@@
 \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
-& \leq \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
+&  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
 exp(\frac{\epsilon \hat{s}}{2 S(x)})
-& \leq exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
+& \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
 \frac{\epsilon \hat{s}}{2 S(x)}
@@
 
-To proof this, we discuss some cases:
+To proof this, we consider some cases:
 
-The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two event that $G=\{\lambda < 0\}$, and $\overline{G} = \{\lambda > 0\}$:
+The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:
 
@@
 
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
+		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
+		\begin{equation*}
+		\end{equation*}
 	\item $\lambda > 0$
@@
 	% 	% \item $u(r) < 0$
-
 	% 	% This need to be discuss further.
@@
 	% 	% \end{equation*}
-
 	% \end{itemize}
 	% \end{itemize}
-\end{itemize}
-
 % In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.
 
-In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.
+% In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.
 
-Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the event $G = \{\lambda > 0, u(r) \leq 0\}$ is:
+Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the case $\lambda > 0$ is:
 \begin{equation*}
@@
 \end{equation*}
-By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with:
+By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
 \begin{equation*}
@@
 \end{equation*}
+
 In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
@@
 
+\end{itemize}
 % So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

### 2018-04-10 main.tex
update

@@
 \begin{equation*}
-\underset{z \thicksim \expomech}{Pr}[u(z) = \hat{s}]
+\underset{r \thicksim \expomech}{Pr}[u(r) = z]
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
 \end{equation*}
@@
 
-\begin{equation*}
-\begin{split}
-\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
-&  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
-exp(\frac{\epsilon \hat{s}}{2 S(x)})
-& \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
-\frac{\epsilon \hat{s}}{2 S(x)}
-& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
-\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
-(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
-\end{split}
-\end{equation*}
-
-To proof this, we consider some cases:
+% \begin{equation*}
+% \begin{split}
+% \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
+% &  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
+% exp(\frac{\epsilon \hat{s}}{2 S(x)})
+% & \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
+% \frac{\epsilon \hat{s}}{2 S(x)}
+% & \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
+% \hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
+% (1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
+% \end{split}
+% \end{equation*}
 
 The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:
+
+We set the $h(z) = Pr[u(\expomech) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
+
+We first consider $\lambda < 0$.
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(z)}{h(e^{\lambda}z)} = \frac{exp(\frac{\epsilon z}{2 S(x)})}{exp(\frac{\epsilon (z \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
+
+Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\expomech) (1 - e^{\lambda})}{S(x)})$.
+Consider the event $G = \{ \expomech : u(\expomech) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
+Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
+The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$.
+Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.
+The $\beta$ is set as
 

### 2018-04-10 main.tex
update

@@
 \begin{lem}
-for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the dilation property holds:
+for any exponential mechanism $\expomech$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
 
@@
 Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.
-The $\beta$ is set as
 
+% \sout{
 \begin{itemize}
@@
 \end{itemize}
+% }
 % So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

### 2018-04-13 main.tex
update

@@
 
-\section{Setting up}
+\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
+\label{sec_bayesInfer}
+
+\section{Algorithm Setting up}
 \label{sec_setup}
@@
 
-\subsubsection{Mechanism Set up}
+% \subsubsection{Mechanism Set up}
 In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
@@
 
+The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+
 % We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
@@
 
-\subsubsection{Security Analysis}
-It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
+% \subsubsection{Security Analysis}
+% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
 We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
 For adjacent data set $||x,y||_1 = 1$:
-\begin{equation*}
-\begin{split}
-\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-& =\frac
-{\frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
-{\frac
-{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
-& = \left(\frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-\right)
-\cdot
-\left(\frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-\right)\\
-& = exp\left(\frac
-{\epsilon (u(x,r) - u(y,r))}
-{2 \Delta_{g}u}
-\right)
-\cdot
-\left(\frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-\right)\\
-& \leq
-exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
-\left(\frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-\right)\\
-& = exp(\epsilon).
-\end{split}
-\end{equation*}
+% \begin{equation*}
+% \begin{split}
+% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
+% & =\frac
+% {\frac
+% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
+% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
+% {\frac
+% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
+% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
+% & = \left(\frac
+% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
+% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
+% \right)
+% \cdot
+% \left(\frac
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
+% \right)\\
+% & = exp\left(\frac
+% {\epsilon (u(x,r) - u(y,r))}
+% {2 \Delta_{g}u}
+% \right)
+% \cdot
+% \left(\frac
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
+% \right)\\
+% & \leq
+% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
+% \left(\frac
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
+% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
+% \right)\\
+% & = exp(\epsilon).
+% \end{split}
+% \end{equation*}
 
-Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
+% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
 
@@
 \label{subsec_emls}
-\subsubsection{Mechanism Set up}
+% \subsubsection{Mechanism Set up}
 Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity.
@@
 
-\subsubsection{Security Analysis}
-We will then prove that exponential mechanism with local sensitivity is non-differentialy private.
-\begin{equation*}
-\begin{split}
-\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} 
-& = exp\left(
-\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} - 
-\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
-\right)  \cdot
-\left(\frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-\right) \\
-& = \frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
-+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
-+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}.
-\end{split}
-\end{equation*}
+The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.
 
-Without loss of generality, we consider the case that $\Delta_{l}u(y) < \Delta_{l}u(x)$, $r = arg(\max\limits_{r' \in R}\{u(x,r')\}) = arg(\min\limits_{r' \in R}\{u(y,r')\})$ and $\Delta_{l}u(y) = u(x,r) - u(y,r)$.
-We have:
-\begin{equation*}
-\begin{split}
-\frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
-+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
-+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-& > \frac
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(x,r) + u(y,r'))}{2 \Delta_{l}u(x)})}
-{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(y,r) + u(x,r'))}{2 \Delta_{l}u(y)})}\\
-& > \frac
-{|R|\ exp(\frac{\epsilon (u(x,r) + u(y,r))}{2 \Delta_{l}u(x)})}
-{|R|\ exp(\frac{\epsilon (u(y,r) + u(x,r))}{2 \Delta_{l}u(y)})}\\
-& = exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)})).
-\end{split}
-\end{equation*}
+\subsection{Exponential Mechanism with Smooth Sensitivity}
+\label{sec_smoo}
 
-From Eq.
-\ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \bysinfer(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$.
-Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
-\begin{equation*}
-\begin{split}
-- \Delta_{l}u(x) & < \Delta_{l}u(y) \\
-\Delta_{l}u(x) - \Delta_{l}u(y) & < 2 \Delta_{l}u(x) \\
-- \Delta_{l}u(y) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
-& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
-u(y,r) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
-& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
-\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} & > 2.
-\end{split}
-\end{equation*}
-
-% \begin{equation*}
-% \begin{split}
-% \frac{\Delta_{l}u(x)}{\Delta_{l}u(y)} & > 0\\
-% & > \frac{\Delta_{l}u(x)}{2u(y,r)}\\
-% & = \frac{\Delta_{l}u(x) + 0}{2u(y,r)} \\
-% & = \frac{\Delta_{l}u(x) + 2 u(x,r)}{2u(y,r)}
-% \end{split}
-% \end{equation*}
-holds.
-
-Then we can have:
-\begin{equation*}
-\begin{split}
-& exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)}))\\
-& > exp(\frac{\epsilon}{2} * 2) \\
-& = exp(\epsilon),
-\end{split}
-\end{equation*}
-i.e.
-\begin{equation*}
-\begin{split}
-\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-& > exp(\epsilon).
-\end{split}
-\end{equation*}
-
-Since there are cases where exponential mechanism with local sensitivity's privacy loss is greater than $e^{\epsilon}$. we can say it is non-differentially private.
-% \begin{equation*}
-% \begin{split}
-% & \epsilon = 0.1\\
-% data size = 2\\
-% the prior is Beta(2，2)\\
-% data set x = [1,0,]\\
-% data set y = [0,0]\\
-% -0.313380201461\\
-% -0.0\\
-% -0.313380201461\\
-% 3 3\\
-% 0.313380201461\\
-% 0.322043464396\\
-% 0.355913071207\\
-% 0.322043464396\\
-% -0.0\\
-% -0.313380201461\\
-% -0.57735026919\\
-% 2 4\\
-% 0.375460728684\\
-% 0.360050126956\\
-% 0.331218326999\\
-% 0.308731546045
-% \end{split}
-% \end{equation*}
-
-% Without loss of generality, we consider the case that $\Delta_{l}u(y) > \Delta_{l}u(x)$ and $\Delta_{l}u(x) = u(x,r) - u(y,r)$. We have:
-% \begin{equation*}
-% \begin{split}
-% exp\left(
-% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
-% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
-% \right)
-% & > exp\left(
-% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
-% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(x)}
-% \right)\\
-% & = exp\left(
-% \frac{\epsilon u(x,r) - \epsilon u(y,r)}{2 \Delta_{l}u(x)}
-% \right) \\
-% & = exp(\frac{\epsilon}{2});
-% \end{split}
-% \end{equation*}
-
-% \textcolor{red}{For the second part:
-% , we have:
-% \begin{equation*}
-% \begin{split}
-% \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(x)} 
-% & < \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(y)}\\
-% & \leq \frac{\epsilon}{2}
-% \end{split}
-% \end{equation*}
-% I cannot replace $exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}(y)})$ in $\left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)$ with $ > exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}(x)})$.
-% So, I cannot find the relationship between the whole part and $exp(\epsilon)$.}
-
-% For the second part:
-% \begin{equation*}
-% \begin{split}
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)
-% & < \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)\\
-% & < \left(\frac
-% {exp(\frac{\epsilon}{2})
-% \cdot
-% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)\\
-% & < exp(\frac{\epsilon}{2})
-% \end{split}
-% \end{equation*}
-
-% For the second part(a tighter bound):
-% \begin{equation*}
-% \begin{split}
-% & \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right) \\
-% & = \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
-% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
-% \cdot
-% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)\\
-% & < \left(\frac
-% {exp(\frac{\epsilon}{2})
-% \cdot
-% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
-% \cdot
-% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
-% \right)\\
-% & < \left(\frac
-% {exp(\frac{\epsilon}{2})}
-% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})}
-% \right)\\
-% & < exp(\frac{\epsilon}{2} - \frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
-% \end{split}
-% \end{equation*}
-
-\subsection{Exponential Mechanism of Varying Sensitivity}
-\label{subsec_emvs}
-\subsubsection{Mechanism Setting up}
-
-\subsubsection{Security Analysis}
-
-\subsection{Exponential Mechanism of Smooth Sensitivity}
-\label{subsec_emss}
-\subsubsection{Mechanism Setting up}
-
-\subsubsection{Security Analysis}
-
-\section{Privacy Fix}
-
-\subsection{Propositions}
-Assume we have a prior distribution $beta(1,1)$, an observed data set $x \in \{0,1\}^n$, $n>0$. We use the $x+1$ and $x-1$ to denote:
-\begin{small}
-\begin{equation*}
-\begin{split}
-&\mathsf{if\ BayesInfer}(x) = beta(a_1 + 1,b_1 + 1)\\
-&\mathsf{then}\mathsf{\ BayesInfer}(x + 1) = beta((a_1 + 1) +1, (b_1 - 1)+1)\\
-&\quad \quad \mathsf{\ BayesInfer}(x - 1) = beta((a_1 - 1) +1, (b_1 + 1)+1),\\
-\end{split}
-\end{equation*}
-\end{small}
-
-$x_0$ to denote:
-\begin{small}
-\begin{equation*}
-\begin{split}
-&\mathsf{if}\ n\ is\ even\\
-&\mathsf{then}\ \bysinfer(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
-&\mathsf{else}\ \bysinfer(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
-&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
-\end{split}
-\end{equation*}
-\end{small}
-
-$\betafun(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.
-
-Then, we have the following three statements, and proofs of the statements.
-\renewcommand{\labelenumi}{\Roman{enumi}}
-\begin{enumerate}
-\item $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$;
-
-or $\hlg (\bysinfer(x), \bysinfer(x + 1)) > \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\forall x \leq x_0$.
-
-\item $\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x + 1)),\forall x \geq x_0$;
-
-$\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x - 1)),\forall x \leq x_0$.
-
-\item $\forall x \neq x_0: \Delta_{l}u(x) > \Delta_{l}u(x_0)$.
-\end{enumerate}
-
-\subsection{proof}
-
-\subsubsection{Statement I}
-We use the MI (Mathematical Induction) method to prove the first statement.
-
-\begin{proof}
-Since the Hellinger distance is symmetric, if we prove the $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.
-
-1. if $x = x_0$, $\hlg (\bysinfer(x_0), \bysinfer(x_0 + 1)) < \hlg (\bysinfer(x_0 + 1), \bysinfer(x_0 + 2))$ holds:
-
-% \twocolumn{
-\begin{small}
-\begin{equation*}
-\begin{split}
-\hlg(
-beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
-beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
-& <  \hlg(
-beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
-beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
-\sqrt{1 - \frac{\betafun(
-\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
-\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
-}
-}
-}
-& < \sqrt{1 - \frac{\betafun(
-\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
-\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
-{\sqrt{
-\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
-\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
-}
-}
-}\\
-\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\betafun(\frac{n}{2} + 2, \frac{n}{2})
-}
-}
-}
-& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2, \frac{n}{2})
-\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
-}
-}
-}\\
-\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
-\betafun(\frac{n}{2} + 2, \frac{n}{2})
-}
-}
-& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2, \frac{n}{2})
-\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
-}
-}\\
-\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
-\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
-{\sqrt{
-\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
-\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
-\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
-& > \frac{
-\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
-\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
-{\sqrt{
-\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
-\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
-\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
-\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
-& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
-(n - 1) ^ 2 (n + 2)(n + 4)
-& > (n + 3) ^ 2 n (n - 2)\\
-n & > -1.
-\end{split}
-\end{equation*}
-\end{small}
-
-Since $n > 0$, it always holds.
-
-2. if $x = x_0 + m$ holds, then also $x = x_0 + m + 1$ holds:
-
-i.e $\hlg(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
-< \hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
-is what we know:
-
-\begin{small}
-\begin{equation*}
-\begin{split}
-\sqrt{
-1 - \frac{\betafun(
-\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
-\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-}
-}
-}
-& < \sqrt{
-1 - \frac{\betafun(
-\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
-\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}
-}\\
-\\
-\frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-}
-}
-& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}
-\end{split}
-\end{equation*}
-\end{small}
-
-Now, we need to proof $\hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
-< \hlg(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.
-
-From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:
-
-\begin{small}
-\begin{equation*}
-\begin{split}
- \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
-\frac{n - 2m - 1}{n + 2m + 3}}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-\frac{n - 2m}{n + 2m + 2}
-}
-}
-> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
-\frac{n - 2m - 3}{n + 2m + 5}}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-\frac{n - 2m - 2}{n + 2m + 6}
-}
-}\\
-\end{split}
-\end{equation*}
+\subsubsection{Algorithm Setting Up}
+The candidate set and utility function are still the same as before, differ only in the sensitivity.
+It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:
 
 \begin{equation*}
-\begin{split}
-\frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}
-> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}\\
-\\
-\sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}}
-< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
-{\sqrt{
-\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
-\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
-}
-}}\\
-\\
-\hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))
-< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
-\end{split}
+P[r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
+{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
 \end{equation*}
-\end{small}
+where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
+\begin{equation*}
+S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
+\end{equation*}
+where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
 
-i.e. $ x = x_0 + m + 1$ also holds when $x = x_0 + m$ is valid.
-\end{proof}
-
-\subsubsection{Statement II}
-\begin{proof}
-
-\begin{equation*}
-\begin{split}
-\because \footnote{the symbol of $\because$ here means because}
-\quad 		& \Delta_l u(x) = \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}} |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
-\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r) \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
-\therefore \footnote{the symbol of $\therefore$ here means therefore}
-\quad 	& \Delta_l u(x) = \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}} \hlg(\bysinfer(x), \bysinfer(y')),\\
-\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)), \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
-					& According\ to\ Statement\ I:\\
-\mathsf{if}	  \quad	& x > x_0 \\
-\mathsf{then} \quad	
-					& \hlg(\bysinfer(x), \bysinfer(x - 1)) < \hlg(\bysinfer(x), \bysinfer(x + 1));\\
-\mathsf{then} \quad	
-					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
-\mathsf{if}	 \quad	& x < x_0 \\
-\mathsf{then} \quad	
-					& \hlg(\bysinfer(x), \bysinfer(x - 1))  > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
-\mathsf{then} \quad	
-					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
-\mathsf{else} \quad	
-					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1)) = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
-\end{split}
-\end{equation*}
-
-From above, we can conclude the Statement II.
-
-\end{proof}
-
-\subsubsection{Statement III}
-\begin{proof}
-From Statement I and Statement II, we can conclude that:
-\begin{equation*}
-\begin{split}
-\mathsf{when} \quad	& x > x_0 \\
-					& \hlg(\bysinfer(x), \bysinfer(x + 1) > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
-					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
-\mathsf{when} \quad	& x < x_0 \\
-					& \hlg(\bysinfer(x), \bysinfer(x - 1)  > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
-					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
-\end{split}
-\end{equation*}
-
-i.e $\forall \ x \neq x_0, \Delta_l u(x) > \Delta_l u(x_0)$.
-
-\end{proof}
-
-\section{Smooth sensitivity}
-\label{sec_smoo}
-
-\subsection{Dilation Property of Laplace Noise}
-\label{sec_Dila}
-\begin{lem}
-For 1-dimensional Laplace distribution: $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$ and $|\lambda| \leq \beta$, the dilation property holds for any $z$ sampled from $h$:
-\begin{equation*}
-Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
-\end{equation*}
-\end{lem}
-
-\begin{proof}
-
-\begin{itemize}
-
-	From the integral substitution property, we have:
-
-	\begin{equation*}
-	\begin{split}
-	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
-		= &\frac
-		{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
-		{\int_{S}{} \frac{1}{2}e^{-|z|} dz} \\
-		= &\frac
-		{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
-		{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
-		= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} \\
-		= & \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
-	\end{split}
-	\end{equation*}
-
-	Then, we proof the dilation property in cases of $\lambda > 0$ and $\lambda < 0$ separately:
-
-	\item \textbf{case 1: $\lambda > 0$}
-
-	\begin{equation*}
-	\begin{split}
-	\because\ 		& 	h(e^{\lambda} z) =  \frac{1}{2} e^{-|e^{\lambda} z|} < \frac{1}{2} e^{-|z|} = h(z)\\
-	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
-					% 	= \frac
-					% 	{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
-					% 	{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
-					% 	= \frac
-					% 	{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
-					% 	{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
-					% &	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
-						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}
-						\leq e^{\lambda}\\
-	\therefore\		&	ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)})
-						\leq \lambda \\
-	\because\		&	\lambda \leq \beta = \frac{\epsilon}{2 ln(3 / \delta)}, \delta < 1 \\
-	\therefore\		&	\lambda \leq \frac{\epsilon}{2} \\
-	\therefore\		&	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} \leq \frac{\epsilon}{2} \\
-	\end{split}
-	\end{equation*}
-
-	\item \textbf{case 2: $\lambda < 0$}
-	% \begin{equation*}
-	% \begin{split}
-	% \because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
-	% \therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
-	% \end{split}
-	% \end{equation*}
-
-	% We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:
-
-	% \begin{equation*}
-	% |z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
-	% \end{equation*}
-
-	% Also, from the Laplace distribution property we have:
-
-	% \begin{equation*}
-	% Pr[G] \geq 1 - \delta ;
-	% \end{equation*}
-
-	% \begin{equation*}
-	% Pr[\overline{G}] \leq \delta .
-	% \end{equation*}
-
-	% We start from the thing we want to proof:
-
-	% \begin{equation*}
-	% Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2};
-	% \end{equation*}
-
-	% \begin{equation*}
-	% \begin{split}
-	% \underset{z \thicksim Lap(1)}{Pr}[z \in S] \leq & Pr[z \in S \cap G] + Pr[z \in \overline{G}]\\
-	% \leq 	& Pr[z \in S \cap G] + \delta\\
-	% \leq 	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S \cap G] + \delta \\
-	% \leq	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
-	% \leq	& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
-	% =		& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(1)}{Pr}[z \in e^{\lambda} S] + \delta\\
-	% \end{split}
-	% \end{equation*}
-	From integral property, we firstly have:
-
-	\begin{equation*}
-	\frac{Pr[z\in e^{\lambda} S]}{Pr[z\in S]} 
-	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} 
-	= \frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} 
-	= e^{\lambda}e^{|z|(1 - e^{\lambda})}
-	\end{equation*}
-
-	\begin{equation*}
-	\begin{split}
-	\because\	& 1 - e^{\lambda} \leq |\lambda| \\
-	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
-	\leq \lambda + |z||\lambda|\\
-	\because\	& \lambda < 0\\
-	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
-	\leq |z||\lambda|\\
-	\end{split}
-	\end{equation*}
-
-	By setting $h'(z) = e^{\lambda} h(e^{\lambda} z)$, we can get:
-
-	\begin{equation*}
-	\begin{split}
-	&\ln(\frac{h'(z)}{h(z)}) \leq |z||\lambda|\\
-	\Rightarrow & h'(z)\leq  e^{|z||\lambda|}h(z)
-	\end{split}
-	\end{equation*}
-
-	By exchanging the notation of $h'$ and $h$, we have:
-
-	\begin{equation*}
-	h(z) \leq e^{|z||\lambda|}h'(z)
-	\end{equation*}
-
-	i.e.
-
-	\begin{equation*}
-	\underset{z \thicksim h}{Pr}[z \in S] 
-	\leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S]
-	= e^{|z||\lambda|}\underset{z \thicksim h}{Pr}[z \in e^{\lambda} S]
-	\end{equation*}
-
-	We consider an event $G = \{z |\ |z|\leq log(\frac{2}{\delta}) \}$. Under this event, we have:
-
-	\begin{equation*}
-	\begin{split}
-	|z||\lambda| 	& \leq log(\frac{2}{\delta})|\lambda|\\
-					& \leq log(\frac{2}{\delta}) \beta\\
-					&\leq log(\frac{2}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \\
-					&\leq \frac{\epsilon}{2}.
-	\end{split}
-	\end{equation*}
-
-	Then:
-
-	\begin{equation*}
-	\begin{split}
-	\underset{z \thicksim h}{Pr}[z \in S \cap G] 
-	& \leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S\cap G]\\
-	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G]\\
-	\end{split}
-	\end{equation*}
-
-	We also have:
-
-	\begin{equation*}
-	Pr[\overline{G}] = Pr[|z| > log(\frac{2}{\delta})] = exp(-log(\frac{2}{\delta})) = \frac{\delta}{2}
-	\end{equation*}
-
-	Then, we can get
-
-	\begin{equation*}
-	\begin{split}
-	\underset{z \thicksim h}{Pr}[z \in S] 
-	& \leq \underset{z \thicksim h}{Pr}[z \in S\cap G] + \underset{z \thicksim h}{Pr}[z \in \overline{G}]\\
-	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G] + \frac{\delta}{2}\\ 
-	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S] + \frac{\delta}{2}\\ 
-	& = e^{\frac{\epsilon}{2}} \underset{z \thicksim h}{Pr}[z \in e^{\lambda} S] + \frac{\delta}{2}\\ 
-	\end{split}
-	\end{equation*}
-
-	i.e. the dilation property.
-
-\end{itemize}
-
-\end{proof}
-
-\subsection{Sliding Property of Exponential Mechanism}
+\subsubsection{Sliding Property of Exponential Mechanism}
 \begin{lem}
@@
 \end{equation*}
-where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
-\begin{equation*}
-S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
-\end{equation*}
-where $\beta = \beta(\epsilon, \delta)$.
 
@@
 
-\subsection{Dilation Property of Exponential Mechanism}
+\subsubsection{Dilation Property of Exponential Mechanism}
 \begin{lem}
@@
 
-% \begin{equation*}
-% \begin{split}
-% \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
-% &  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
-% exp(\frac{\epsilon \hat{s}}{2 S(x)})
-% & \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
-% \frac{\epsilon \hat{s}}{2 S(x)}
-% & \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
-% \hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
-% (1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
-% \end{split}
-% \end{equation*}
-
 The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:
@@
 The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.
+Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.\\
 
-% \sout{
+\textbf{Detail proof:}
 \begin{itemize}
@@
 	\item $\lambda < 0$
-	% \begin{itemize}
-		% \item $u(r) > 0$
-
-		% % This need to be discuss further.
-		% % We can have:
-		% % \begin{equation*}
-		% % \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
-		% % \end{equation*}
-		% % Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
-		% \item $u(r) \leq 0$
 
@@
 	\item $\lambda > 0$
-	% \begin{itemize}
-	% 	% \item $u(r) > 0$
-
-	% 	% The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
-
-	% 	% \item $u(r) < 0$
-	% 	% This need to be discuss further.
-	% 	% We can have:
-	% 	% \begin{equation*}
-	% 	% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
-	% 	% \end{equation*}
-	% \end{itemize}
-	% \end{itemize}
-% In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.
-
-% In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.
 
@@
 \end{itemize}
-% }
-% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
-
-% We take the absolute value of utility function, then there is only one case we need to discuss: $(1 - e^{\lambda}) |\hat{s}| \leq S(x)$, $\lambda < 0$.
 
@@
 \section{Experimental Evaluations}
-We got some results from these mechanisms.
+\subsection{Computation Efficiency}
+The formula to compute the local sensitivity is presented in Sec. \ref{subsec_emls}.
+
+\printbibliography
 

### 2018-04-13 main.tex
uodate efficiency

@@
 \label{sec_bayesInfer}
+The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
+For conciseness, when prior is given, we use $\bysinfer(x)$.
 
@@
 \label{sec_setup}
-The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
-For conciseness, when prior is given, we use $\bysinfer(x)$.
 
@@
 \subsection{Computation Efficiency}
-The formula to compute the local sensitivity is presented in Sec. \ref{subsec_emls}.
+The formula for computing the local sensitivity is presented in Sec.
+\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
+i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
+We also have some experiments for validating our proposal as in Fig.
+\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
+It is shown that maximum value taken when  $r = \bysinfer(x)$.
+
+ \begin{figure}[h]
+    \centering
+    \includegraphics[width=1.0\textwidth]{efficiency}
+    \label{fig_efficiency}
+    \caption{An Experimental Result for Finding the Local Sensitivity efficiently}
+    \end{figure}
+\subsection{}
 

### 2018-04-13 LocalSensitivityStudy.py
sensitivity efficiency code

@@ -1,0 +1,307 @@
+import numpy
+import matplotlib.pyplot as plt
+from copy import deepcopy
+import random
+import math
+import scipy
+from scipy.stats import beta
+from fractions import Fraction
+import operator
+
+
+
+
+def multibeta_function(alphas):
+	numerator = 1.0
+	denominator = 0.0
+	for alpha in alphas:
+		numerator = numerator * math.gamma(alpha)
+		denominator = denominator + alpha
+	# print numerator / math.gamma(denominator)
+	return numerator / math.gamma(denominator)
+
+def optimized_multibeta_function(alphas):
+	denominator = -1.0
+	nominators = []
+	denominators = []
+	r = 1.0
+	for alpha in alphas:
+		denominator = denominator + alpha
+	for alpha in alphas:
+		temp = alpha - 1
+		while temp > 0.0:
+			nominators.append(temp)
+			temp -=1
+		if temp < 0.0:
+			nominators.append(math.gamma(1 + temp))
+	while denominator > 0.0:
+		denominators.append(denominator)
+		denominator -= 1
+	if denominator < 0.0:
+		denominators.append(math.gamma(1 + denominator))
+	# print nominators
+	# print denominators
+	d_pointer = len(denominators) - 1
+	n_pointer = len(nominators) - 1
+	while d_pointer >= 0 and n_pointer >= 0:
+		# print nominators[n_pointer],denominators[d_pointer]
+		r *= nominators[n_pointer] / denominators[d_pointer]
+		n_pointer -= 1
+		d_pointer -= 1
+	while d_pointer >= 0:
+		# print n_pointer,denominators[d_pointer]
+		r *= 1.0 / denominators[d_pointer]
+		d_pointer -= 1
+	while n_pointer >= 0:
+		# print nominators[n_pointer] ,d_pointer
+		r *= nominators[n_pointer] 
+		n_pointer -= 1
+	# 	while temp > 0.0:
+	# 		r *= (temp / denominator)
+	# 		temp -= 1
+	# 		denominator -= 1
+	# 		print r,temp,denominator
+	# 	if temp < 0.0:
+	# 		r *= (math.gamma(1 + temp) / denominator)
+	# 		denominator -= 1
+	# 		print r, temp, denominator
+	# while denominator > 0.0:
+	# 	r /= denominator
+	# 	denominator -= 1
+	# if denominator < 0.0:
+	# 	r /= math.gamma(1 + denominator)
[…]

### 2018-04-13 main.tex
sensitivity efficiency code
update algorithm setting

@@
 For conciseness, when prior is given, we use $\bysinfer(x)$.
+
+In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.
 
@@
 
-\subsubsection{Algorithm Setting Up}
+\subsubsection{Algorithm Setting up}
 The candidate set and utility function are still the same as before, differ only in the sensitivity.
@@
 \label{fig_efficiency}
-    \caption{An Experimental Result for Finding the Local Sensitivity efficiently}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
 \end{figure}
-\subsection{}
+
+\subsection{Accuracy Study of Algorithms}
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
+  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
+\caption{The experimental results of accuracy of four algorithms}
+\label{fig_data}
+\end{center}
+\end{figure*}
+
+We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison.
+As in Fig.
+\ref{fig_data}, the two figures shown the accuracy of four algorithms under same configuration.
+The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
 

### 2018-04-13 sensitivity/LocalSensitivityStudy.py

@@ -269,21 +269,21 @@ class BayesInferwithDirPrior(object):
 			count += 1
 		y = numpy.array(y)
 		x = numpy.arange(0, len(y), 1)
-		plt.figure(figsize=(150,35))
+		plt.figure(figsize=(80,35))
 		plt.rc('text', usetex=True)
 		plt.rc('font', family='serif')
 		# plt.tight_layout()
 		plt.scatter(x, y, s = 100, c = 'b', marker = 'o', alpha = 0.7, edgecolors='white', label = r"$\displaystyle\max_{\{D'\ adj\ D\}}|H(D,r)-D(D',r)|$")
-		plt.axvline(x=xmark, color='r', label = 'True Posterior:'+str(self._posterior._alphas))
+		plt.axvline(x=xmark, color='r', label = 'True Posterior:'+str(self._posterior._alphas),linewidth = 6.0)
 		plt.ylim(0.0,self._LS_max+0.01)
 		plt.xlim(0.0,len(y)*1.0)
 		plt.grid()
-		plt.legend(prop={'size': 90})
-		plt.xticks(x, labels, rotation='vertical',fontsize=6)
-		plt.xlabel(r"$Candidates\ r\in R\ (3\ Order\ Dirichlet\ Distribution\ with\ Data\ Size\ 100)$", fontsize=60)
+		plt.legend(prop={'size': 90}, loc="best")
+		plt.xticks(x, labels, rotation='vertical',fontsize=7)
+		plt.xlabel(r"$Candidates\ r\in R\ (3\ Order\ Dirichlet\ Distribution\ with\ Data\ Size\ 50)$", fontsize=70)
 		plt.ylabel(r"$\displaystyle\max_{\{D'\ adj\ D\}}|H(D,r)-D(D',r)|$", fontsize=90)
 		#plt.show()
-		plt.savefig("Local_SensitivitiesOrder3size100labels_latex.png")
+		plt.savefig("Local_Sensitivitiessize50labels_latex.png")
 
 
 
@@ -291,7 +291,7 @@ class BayesInferwithDirPrior(object):
 if __name__ == "__main__":
 	# Tests the functioning of the module
 
-	sample_size = 100
+	sample_size = 50
 	epsilon = 0.8
 	prior = Dir([7, 4, 5])
 	Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon)

### 2018-04-13 main.tex
update algorithm setting up

@@
 For conciseness, when prior is given, we use $\bysinfer(x)$.
+$n$ is the size of the observed data size.
 
 In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.
+Columns of the data set is corresponding to the number of parameters in Dirichlet distribution.
+The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$.
 
@@
 
-\subsection{Accuracy Study of Algorithms}
+\subsection{Accuracy Study with Hellinger Distance}
 \begin{figure*}

### 2018-04-13 main.tex
update

--- 2018-04-13 main.tex
@@
 For conciseness, when prior is given, we use $\bysinfer(x)$.
+$n$ is the size of the observed data size.
 
-In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.
+In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$.
+Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution.
+The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$ in observed data set.
+
+In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
+Then we have only one column take value from $\{0,1\}$.
+THe posterior is computed as $(\alpha + n_1, \beta + n_0))$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
 
@@
 \label{sec_setup}
-
 For now, we already have a prior distribution $prior$, an observed data set $x$.
@@
 \end{equation*}
-where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
+where the sensitivity in mechanism is smooth sensitivity $S(x)$\cite{nissim2007smooth}, calculated by:
 \begin{equation*}

### 2018-04-13 main.tex
update

@@
 Then we have only one column take value from $\{0,1\}$.
-THe posterior is computed as $(\alpha + n_1, \beta + n_0))$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
+THe posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
 
@@
 % \subsubsection{Mechanism Set up}
+
 In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.

### 2018-04-17 main.tex
uodate
update

@@
 In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
-Then we have only one column take value from $\{0,1\}$.
-THe posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
+We can have only one column take value from $\{0,1\}$.
+The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
 

### 2018-04-17 main.tex
update

@@
 \label{sec_bayesInfer}
-The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
+In the Bayesian inference, first there is a prior distribution $\pi(\alphas)$ to present our belief about parameter $\alphas$.
+Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\alphas | x)$.
+The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
+\begin{equation*}
+Pr(\alphas | x) = \frac{Pr(x | \alphas) \pi(\alphas)}{Pr(x)}
+\end{equation*}
+It is denoted as $\bysinfer(x,\pi(\alphas))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\alphas)$ as input, outputting a posterior distribution of the parameter $\alphas$.
 For conciseness, when prior is given, we use $\bysinfer(x)$.
@@
 
-In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$.
+In our inference algorithm, we take a Dirichlet distribution as prior belief for the , $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$.
 Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution.

### 2018-04-17 main.tex
update

@@
 
-In our inference algorithm, we take a Dirichlet distribution as prior belief for the , $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$.
+In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$.
+
 Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution.

### 2018-04-17 main.tex
update example

--- 2018-04-17 main.tex
@@
 
-\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
+\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
 \label{sec_bayesInfer}
-The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$.
+In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$.
+Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$.
+The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
+\begin{equation*}
+Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
+\end{equation*}
+It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$.
 For conciseness, when prior is given, we use $\bysinfer(x)$.
@@
 
-In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$.
-Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution.
-The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$ in observed data set.
+In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, where $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$.
+$m$ is the order of the Dirichlet distribution.
+
+We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice.
+We want to infer the probability of getting each side $\xis$.
+We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time.
+The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.
 
 In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
-We can have only one column take value from $\{0,1\}$.
-The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
+The $m$ side dice change into a irregular coin with side $1$ and side $2$.
+The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $1$ in the observed data set and $n_0$ is the appearance time of the other side.
 

### 2018-04-18 dp_bayesian_inference_model_with_dirichlet_prior.py
update plot

@@ -137,7 +137,8 @@ class BayesInferwithDirPrior(object):
 		self._SS_Expon = 0.0
 		self._SS_Laplace = 0.0
 		self._candidate_VS_scores = {}
-		self._keys = ["Laplace Mechanism | Achieving" + str(self._epsilon) + "-DP"]
+		#self._keys = ["Laplace Mechanism | Achieving" + str(self._epsilon) + "-DP"]
+		self._keys = ["LaplaceMech"]
 		self._accuracy = {self._keys[0]:[]}
 	
 	def _set_bias(self, bias):
@@ -194,6 +195,7 @@ class BayesInferwithDirPrior(object):
 		beta = math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
 		self._SS_Hamming = max(self._LS, max([self._LS_Candidates[r] * math.exp(- beta * Hamming_Distance(self._posterior, r)) for r in self._candidates]))
 		key3 = "Exponential Mechanism with " + str(beta) + " - Bound Smooth Sensitivity (" + str(self._SS_Hamming) + ")|(" + str(self._epsilon) + "," + str(self._delta) + ")-DP"
+		key3 = "ExpoMech of SS"
 		self._accuracy[key3] = []
 		self._keys.append(key3)
 		print str(time.clock() - start) + "seconds."
@@ -206,7 +208,8 @@ class BayesInferwithDirPrior(object):
 
 	def _set_LS(self):
 		self._LS = self._posterior._hellinger_sensitivity(self._posterior)#self._posterior
-		key = "Exponential Mechanism with Local Sensitivity - " + str(self._LS) + "| Non Privacy"
+		#key = "Exponential Mechanism with Local Sensitivity - " + str(self._LS) + "| Non Privacy"
+		key = "Expomech of LS"
 		self._accuracy[key] = []
 		self._keys.append(key)		
 
@@ -215,7 +218,8 @@ class BayesInferwithDirPrior(object):
 		temp[0] += 1
 		temp[1] -= 1
 		self._GS = self._prior - Dir(temp)
-		key = "Exponential Mechanism with Global Sensitivity - " + str(self._GS) + "| Achieving" + str(self._epsilon) + "-DP"
+		#key = "Exponential Mechanism with Global Sensitivity - " + str(self._GS) + "| Achieving" + str(self._epsilon) + "-DP"
[…]

### 2018-04-19 main.tex
update plot
update plots

@@
 
-\subsection{Accuracy Study with Hellinger Distance}
+\subsection{Accuracy Study Based on Hellinger Distance}
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
+%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
+%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
+%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
+% \caption{The experimental results of accuracy of four algorithms}
+% \label{fig_data}
+% \end{center}
+% \end{figure*}
+
 \begin{figure*}
@@
 \centering
-  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
-  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
-\caption{The experimental results of accuracy of four algorithms}
-\label{fig_data}
+  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
+  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
+\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
+\label{fig_beta_hellinger}
 \end{center}
@@
 As in Fig.
-\ref{fig_data}, the two figures shown the accuracy of four algorithms under same configuration.
+\ref{fig_beta_hellinger}, the two figures shown the accuracy of four algorithms under same configuration.
 The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
+
+Then, we extended the $\betad$ to the Bernoulli distribution, got the result in Fig. \ref{fig_dirichlet_hellinger}
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
+    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
+  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
+    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
+\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
+\label{fig_dirichlet_hellinger}
+\end{center}
+\end{figure*}
+
+\subsection{Accuracy Study Based on L1 Norm Distance}
+For comparison, we study the accuracy of these four mechanisms based on l1 norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.
+\ref{fig_dirichlet_hellinger_l1}.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
+  \subfigure[accuracy measurement based on l1 norm]{
+    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
+\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and l1 norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
+\label{fig_dirichlet_hellinger_l1}
+\end{center}
+\end{figure*}
 

### 2018-04-19 dp_bayesian_inference_model_with_dirichlet_prior.py

@@ -11,7 +11,8 @@ import time
 from matplotlib.patches import Polygon
 
 
-
+def L1_Nrom(A, B):
+	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
 
 def multibeta_function(alphas):
 	numerator = 1.0
@@ -70,7 +71,7 @@ def Optimized_Hellinger_Distance_Dir(Dir1, Dir2):
 		math.sqrt(optimized_multibeta_function(Dir1._alphas) * optimized_multibeta_function(Dir2._alphas)))
 
 def Hamming_Distance(Dir1, Dir2):
-	temp = [abs(a - b) for a,b in Dir1._alphas,Dir2._alphas]
+	temp = [abs(a - b) for a,b in zip(Dir1._alphas,Dir2._alphas)]
 	return sum(temp)
 
 class Dir(object):
@@ -140,6 +141,7 @@ class BayesInferwithDirPrior(object):
 		#self._keys = ["Laplace Mechanism | Achieving" + str(self._epsilon) + "-DP"]
 		self._keys = ["LaplaceMech"]
 		self._accuracy = {self._keys[0]:[]}
+		self._accuracy_l1 = {self._keys[0]:[]}
 	
 	def _set_bias(self, bias):
 		self._bias = bias
@@ -195,8 +197,10 @@ class BayesInferwithDirPrior(object):
 		beta = math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
 		self._SS_Hamming = max(self._LS, max([self._LS_Candidates[r] * math.exp(- beta * Hamming_Distance(self._posterior, r)) for r in self._candidates]))
 		key3 = "Exponential Mechanism with " + str(beta) + " - Bound Smooth Sensitivity (" + str(self._SS_Hamming) + ")|(" + str(self._epsilon) + "," + str(self._delta) + ")-DP"
+		print key3
 		key3 = "ExpoMech of SS"
 		self._accuracy[key3] = []
+		self._accuracy_l1[key3] = []
 		self._keys.append(key3)
 		print str(time.clock() - start) + "seconds."
 
@@ -208,9 +212,11 @@ class BayesInferwithDirPrior(object):
 
 	def _set_LS(self):
 		self._LS = self._posterior._hellinger_sensitivity(self._posterior)#self._posterior
-		#key = "Exponential Mechanism with Local Sensitivity - " + str(self._LS) + "| Non Privacy"
[…]

### 2018-04-20 main.tex
update

@@
 
-\subsection{Accuracy Study Based on L1 Norm Distance}
-For comparison, we study the accuracy of these four mechanisms based on l1 norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.
+\subsection{Accuracy Study Based on $L_1$ Norm Distance}
+For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.
 \ref{fig_dirichlet_hellinger_l1}.
@@
     \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
-  \subfigure[accuracy measurement based on l1 norm]{
+  \subfigure[accuracy measurement based on $l_1$ norm]{
     \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and l1 norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
+\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$ norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
 \label{fig_dirichlet_hellinger_l1}

### 2018-04-23 main.tex
update accuracy
UPDATE
update l_1 norm
update
update detail

@@
 
+\section{Accuracy Analysis}
+\subsection{Laplace Mechanism}
+Fixing a data set $x$, we already had the accuracy bound based on the $l_1$ norm as:
+\begin{equation*}
+Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] \leq \gamma,
+\end{equation*}
+where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
+\begin{equation*}
+\begin{split}
+Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[|x| ||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+& = \gamma
+\end{split} 
+\end{equation*}
+
+\subsection{Exponential Mechanism with Global Sensitivity}
+
+\subsection{Exponential Mechanism with Local Sensitivity}
+
+\subsection{Exponential Mechanism with Smooth Sensitivity}
+
 \section{Experimental Evaluations}

### 2018-04-23 main.tex
update

@@
 \begin{split}
-Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[|x| ||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
 & = \gamma
@@
 
-\subsection{Accuracy Study Based on $L_1$ Norm Distance}
+\subsection{Accuracy Study Based on $L_1$ Norm}
 For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.

### 2018-04-23 dp_bayesian_inference_model_with_dirichlet_prior.py

@@ -510,15 +510,15 @@ def draw_error_l1(errors, model, filename):
 if __name__ == "__main__":
 	# Tests the functioning of the module
 
-	sample_size = 150
+	sample_size = 100
 	epsilon = 0.8
-	delta = 0.8
-	prior = Dir([7, 4, 5])
+	delta = 0.005
+	prior = Dir([2,2,2])
 	Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
 
 	Bayesian_Model._experiments(200)
 
-	draw_error(Bayesian_Model._accuracy,Bayesian_Model, "order-3-size-150-runs-200-epsilon-08-hellinger-box.png")
+	draw_error(Bayesian_Model._accuracy,Bayesian_Model, "order-3-size-100-runs-200-epsilon-08-hellinger-delta0005-box.png")
 
-	draw_error_l1(Bayesian_Model._accuracy_l1,Bayesian_Model, "order-3-size-150-runs-200-epsilon-08-l1norm-box.png")
+	draw_error_l1(Bayesian_Model._accuracy_l1,Bayesian_Model, "order-3-size-100-runs-200-epsilon-08-l1norm-delta0005-box.png")
 

### 2018-04-26 main.tex
update proof

@@
 \begin{proof}
+We firstly proof that $Pr[\expomech = z] = \underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)]$.
+Then we can use the exponential probability in following proofs.
+From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$.
+We can derive, if $u(z,x) = u(z',x)$ then $Pr[\expomech = z] = Pr[\expomech = z']$.
+We assume the number of candidates $r \in \mathsf{R}$ that satisfy $u(z,x) = u(r,x)$ is $|z|$, we have  $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = |z| Pr[\expomech = z]$.
+In our case, $u(r,x)$ come from Hellinger distance is axial symmetry, where the true output is the symmetry axis.
+It can be infer that |z| = 2 for any candidates, apart from the true output, i.e., $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = 2 Pr[\expomech = z]$.
+This parameter can be eliminate in both sides in proving.
+
 We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
@@
 LHS 
-  = \underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+  = \underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
 & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\

### 2018-04-26 main.tex
fixed the biblio
working on the style

@@
 \subsubsection{Algorithm Setting up}
-The candidate set and utility function are still the same as before, differ only in the sensitivity.
-It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:
+We define a new mechanism $\hexpmech(x)$
+which is similar to the exponential mechanism where we use
+$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
+summing up to $n+2$, as scoring function we use the Hellinger distance
+from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
+calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
+only difference is in the sensitivity part, since now we use the
+smooth sensitivity.
 
+\begin{definition} The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
 \begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
-{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
+\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
+{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
+{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
 \end{equation*}
-where the sensitivity in mechanism is smooth sensitivity $S(x)$\cite{nissim2007smooth}, calculated by:
+where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
 \begin{equation*}
-S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
+S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(x),-)\cdot e^{-\beta d(x,y)})),
 \end{equation*}
-where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+where $d$ is the Hamming distance between two datasets, and $\beta =
+\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
+\end{definition}
 
-\subsubsection{Sliding Property of Exponential Mechanism}
-\begin{lem}
-for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the sliding property holds:
+In what follows, we will use a correspondence between the probability
+ $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
+ $r\in\betaset$ and the probability 
+ $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+ \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
+ $r\in\betaset$ we have:
+$$
+\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
+\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+ \hlg(\bysinfer(x),r)]\Big )
+$$
+To see this, it is enough to notice that ...
 
-\begin{equation*}
-\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
-\leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
-\end{equation*}
-
-\end{lem}
-
-\begin{proof}
-We firstly proof that $Pr[\expomech = z] = \underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)]$.
-Then we can use the exponential probability in following proofs.
  From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$.
@@
 This parameter can be eliminate in both sides in proving.
+
+In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+
+\subsubsection{Sliding Property of Exponential Mechanism}
+\begin{lem}
+Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
+calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
+\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
+\begin{equation*}
+\underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+\leq
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+\end{equation*}
+
+\end{lem}
+
+\begin{proof}
 
@@
 
-\printbibliography
+\bibliographystyle{plain}
+\bibliography{bayesian.bib}
 

### 2018-04-27 main.tex
update formatte

@@
 $$
-To see this, it is enough to notice that ...
-
- From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$.
-We can derive, if $u(z,x) = u(z',x)$ then $Pr[\expomech = z] = Pr[\expomech = z']$.
-We assume the number of candidates $r \in \mathsf{R}$ that satisfy $u(z,x) = u(r,x)$ is $|z|$, we have  $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = |z| Pr[\expomech = z]$.
-In our case, $u(r,x)$ come from Hellinger distance is axial symmetry, where the true output is the symmetry axis.
-It can be infer that |z| = 2 for any candidates, apart from the true output, i.e., $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = 2 Pr[\expomech = z]$.
-This parameter can be eliminate in both sides in proving.
+To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
+We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
+We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
+It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+This parameter can be eliminate in both sides in proof.
 
@@
 \begin{equation*}
-\underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
 \end{equation*}
@@
 
-We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
+We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
 \begin{equation*}
@@
 LHS 
-  = \underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
+  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
 & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
@@
 & \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{\epsilon}{2}}\\
-&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
 \end{split}
@@
 \begin{lem}
-for any exponential mechanism $\expomech$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
 
 \begin{equation*}
-\underset{r \thicksim \expomech}{Pr}[u(r) = z]
+\underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = z]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
 \end{equation*}
@@
 
-We set the $h(z) = Pr[u(\expomech) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
+We set the $h(z) = Pr[u(\hexpmech(x)) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
 
@@
 
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\expomech) (1 - e^{\lambda})}{S(x)})$.
-Consider the event $G = \{ \expomech : u(\expomech) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
+Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
+Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
 Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
@@
 
-Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the case $\lambda > 0$ is:
+Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
 \begin{equation*}
-u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
 \end{equation*}
@@
 \begin{split}
-Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
 & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
@@
 \begin{split}
-Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
 & = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
@@
 
-When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
+When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
 

### 2018-05-01 main.tex
fix mistakes

@@
 In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
-The $m$ side dice change into a irregular coin with side $1$ and side $2$.
-The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $1$ in the observed data set and $n_0$ is the appearance time of the other side.
+The $m$ side dice change into a irregular coin with side $A$ and side $B$.
+The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.
 
@@
 \label{sec_setup}
-For now, we already have a prior distribution $prior$, an observed data set $x$.
+For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.
 
@@
 
-In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
+In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
 \begin{equation*}
-R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
+\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
 \end{equation*}
@@
 \label{equ_utility}
-u(x,r) = -\hlg(\bysinfer(x), r); r \in R.
+u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
 \end{equation}
 
-Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
+Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
 \begin{equation*}
@@
 {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
 \end{equation*}
@@
 \Delta_{g}u = 
-\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}
+\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
 |\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
@@
 Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity.
-This outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
+This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
 \begin{equation*}
@@
 {exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
-{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
 \end{equation*}
@@
 \Delta_{l}u(x) = 
-\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
+\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
 \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
@@
 \begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = z]
+\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = z]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = e^{\lambda} z] + \frac{\delta}{2},
 \end{equation*}
@@
 
-The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:
+The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),r)$ is smaller than zero, i.e., $u(r,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
-We set the $h(z) = Pr[u(\hexpmech(x)) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
+We set the $h(z) = Pr[u(\hexpmech(x)) = z] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
 

### 2018-05-01 main.tex
update lemma2.6
update lemma 2.6

@@
 
-We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
+We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
 \begin{equation*}
@@
   = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL_x}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL_x}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
+& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
 \end{split}
@@
 \begin{split}
-\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{\epsilon}{2}}\\
+\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
+& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
 &  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
@@
 
-We set the $h(z) = Pr[u(\hexpmech(x)) = z] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
+We set the $h(z) = Pr[u(\hexpmech(x)) = z] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
 
@@
 \end{itemize}
+
+\end{proof}
+
+\subsubsection{Privacy Analysis}
+\begin{lem}
+\label{lem_hexpmech_privacy}
+$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
+\end{lem}
+
+\begin{proof}
+of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
+\end{equation*}
+Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+Then,
+
+\begin{equation*}
+\begin{split}
+2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
+& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
+& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
+& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
+& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] + \delta \Big)\\
+\end{split}
+\end{equation*}
 

### 2018-05-01 main.tex
update lemma 2.6

@@
 & = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
+& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in ]\\
 & \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
@@
 \end{equation*}
+
+The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
+The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
 

### 2018-05-14 main.tex
fix mistake

@@
 & = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in ]\\
+& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
 & \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] + \delta \Big)\\
+& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
 \end{split}

### 2018-06-16 main.tex
update notes

@@
 \subsection{Accuracy Study Based on Hellinger Distance}
+\label{subsec_accuracy_hellinger}
 % \begin{figure*}
@@
 
+\subsection{Accuracy Study in Theory}
+\label{subsec_accuracy_theory}
+We studied the accuracy of our exponential mechanism and Laplace mechanism in theory.
+By computing the discrete probability of outputting each candidate in two mechanisms separately.
+We count the probabilities wrt.
+the steps from correct answer.
+For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
+Under the Hellinger distance measurement, if two candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
+i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
+
+So in order to be more concise and comparable to the experiment results in Sec.
+\ref{subsec_accuracy_hellinger}, we sum up the probabilities values of candidates whose steps (i.e., the hellinger distance) from the correct answer are the same:
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}{NL_x}
+\end{equation*}
+
+Then we get groups of discrete probabilities wrt.
+the steps (i.e., Hellinegr distance) from the correct answer, and plot them.
+Under different settings, we got same results as in Fig.
+\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.
+The x-axis is the hellinger distance from correct answer, i.e.
+steps from correct answer.
+Since they have the same meaning, here we just use the hellinger distance to label the x-axis.
+The y-axis is the probability of output candidates with corresponding steps from correct answer.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{50_50.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $,}
+\label{fig_theory_50_50}
+\end{center}
+\end{figure*}
+
+As shown in Fig.
+\ref{fig_theory_50_50}, our exponential mechanism is better than Laplace, both in experiments and in theory.
+In Fig.
+\ref{fig_theory_50_50} (a), the experiment results shown that the average accuracy of our mechanism is better than Laplace mechanism.
+In Our exponential mechanism can output good answer with higher probability and output bad answer with lower probability.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20) $,}
+\label{fig_theory_20_20_20}
+\end{center}
+\end{figure*}
+
+In Fig.
+\ref{fig_theory_20_20_20}, we plotted these discrete probabilities under the case (x=(20,20,20)),  I think this plot shows the laplace mech performs better than ExpMech to some extent but not significant.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $,}
+\label{fig_theory_20_20_20_20}
+\end{center}
+\end{figure*}
+
+In Fig.
+\ref{fig_theory_20_20_20_20}, we plotted these discrete probabilities under the case ($x=(20,20,20,20)$).
+this plot can show clearly that the Laplace Mech are better than Exp Mech when the size is larger and order is higher.
+The Laplace can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
 \bibliographystyle{plain}

### 2018-06-16 dp_bayesian_inference_model_with_dirichlet_prior_accuracy_study.py

@@ -699,23 +699,23 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 
 if __name__ == "__main__":
 
-	sample_size = 80
+	sample_size = 98
 	epsilon = 0.8
 	delta = 0.00005
-	prior = Dir([1,1,1,1])
-	observation = [20,20,20,20]
-	# Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
+	prior = Dir([1,1])
+	observation = [49,49]
+	Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
 
-	accuracy_study_discrete(sample_size,epsilon,delta,prior,observation)
+	# accuracy_study_discrete(sample_size,epsilon,delta,prior,observation)
 	# accuracy_study_exponential_mechanism_SS(sample_size,epsilon,delta,prior,observation)
 	# accuracy_study_laplace(sample_size,epsilon,delta,prior,observation)
 	# Tests the functioning of the module
 
 	#print Dir([50,50]) - Dir([47,53])
-	# Bayesian_Model._set_observation(observation)
-	# Bayesian_Model._experiments(1000)
+	Bayesian_Model._set_observation(observation)
+	Bayesian_Model._experiments(10000)
 
-	# draw_error(Bayesian_Model._accuracy,Bayesian_Model, "order-3-size-60-runs-1000-epsilon-08-hellinger-delta000005-observation202020-box.png")
+	draw_error(Bayesian_Model._accuracy,Bayesian_Model, "order-2-size-98-runs-1000-epsilon-08-hellinger-delta000005-observation202020-box.png")
 
 	# draw_error_l1(Bayesian_Model._accuracy_l1,Bayesian_Model, "order-2-size-100-runs-1000-epsilon-08-l1norm-delta000005box.png")
 	

### 2018-06-17 main.tex
update notes

@@
 % \end{figure*}
+We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison.
+We repeat the experiments for 10000 times and plot their accuracy after every execution.
+Under different parameters setting, we got two groups of results as in Fig.
+\ref{fig_beta_hellinger} and Fig.
+\ref{fig_dirichlet_hellinger}.
+y-axis is accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
 
@@
 \end{figure*}
+When prior distribution is $\betad$, under data size $n = 500$ and $300$, we get two experiment results shown in Fig. \ref{fig_beta_hellinger}.
 
-We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison.
-As in Fig.
-\ref{fig_beta_hellinger}, the two figures shown the accuracy of four algorithms under same configuration.
-The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
-
-Then, we extended the $\betad$ to the Bernoulli distribution, got the result in Fig. \ref{fig_dirichlet_hellinger}
+Then, we extended the $\betad$ to the $\dirichlet$ distribution as well as increase the data size, got the result in Fig. \ref{fig_dirichlet_hellinger}.
 \begin{figure*}
@@
 \subsection{Accuracy Study Based on $L_1$ Norm}
+\label{subsec_accuracy_l1}
 For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.
@@
 
-\subsection{Accuracy Study in Theory}
-\label{subsec_accuracy_theory}
-We studied the accuracy of our exponential mechanism and Laplace mechanism in theory.
-By computing the discrete probability of outputting each candidate in two mechanisms separately.
-We count the probabilities wrt.
+From results above, we can obtain some preliminary conclusions: 1) Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
+Both of the two exponential mechanisms are do much better than it with global sensitivity.
+2) The accuracy of our exponential mechanism is better than laplace mechanism.
+But the advantages are not significant.
+So we need to have a further exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism.
+
+\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
+\label{subsec_accuracy_tradeoff}
+Based on accuracy study in Sec.
+\ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to study the relationship between Laplace mechanism and our exponential mechanism further.
+We will work on some concrete cases based on accuracy bound and probability formula and then have analysis both in theory and experiments.
+
+\subsubsection{Theory Analysis}
+
+\begin{itemize}
+	\item In our exponential mechanism, the probability of outputting each candidates are calculated as: which is inversely proportional to the size of candidate size.
+
+	\item
+\end{itemize}
+
+\subsubsection{Experiment Analysis}
+We studied the accuracy trade-off between our exponential mechanism and Laplace mechanism in experiments.
+By computing the two mechanisms' discrete probabilities of outputting each candidate separately.
+Here, we count the probabilities wrt.
 the steps from correct answer.
@@
 
-So in order to be more concise and comparable to the experiment results in Sec.
-\ref{subsec_accuracy_hellinger}, we sum up the probabilities values of candidates whose steps (i.e., the hellinger distance) from the correct answer are the same:
+So in order to be more concise and comparable to the experiment results from Sec.
+\ref{subsec_accuracy_hellinger}, we sum up the probability values of candidates whose steps (i.e., the hellinger distance) from the correct answer are the same:
 \begin{equation*}
@@
 
-Then we get groups of discrete probabilities wrt.
-the steps (i.e., Hellinegr distance) from the correct answer, and plot them.
+Then we got groups of discrete probabilities wrt.
+the steps (i.e., Hellinegr distance) from the correct answer, and plotted them.
 Under different settings, we got same results as in Fig.
 \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.
-The x-axis is the hellinger distance from correct answer, i.e.
+Subfigs (a) are from Sec.
+\ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
+x-axis is labeled by each mechanism and y-axis is the accuracy of each executing result measured by Hellinegr distance.
+We name group (a) as experiment results.
+Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
+the steps.
+x-axis is the hellinger distance from correct answer, i.e.
 steps from correct answer.
@@
 The y-axis is the probability of output candidates with corresponding steps from correct answer.
+We name this group (b) as theory computing results.
 
@@
 
-As shown in Fig.
-\ref{fig_theory_50_50}, our exponential mechanism is better than Laplace, both in experiments and in theory.
+When the data size is small and the order of the prior distribution is low, our exponential mechanism is better than Laplace, both in experiments and in theory.
+as shown in Fig.
+\ref{fig_theory_50_50}.
 In Fig.
 \ref{fig_theory_50_50} (a), the experiment results shown that the average accuracy of our mechanism is better than Laplace mechanism.
-In Our exponential mechanism can output good answer with higher probability and output bad answer with lower probability.
+In the mean time, the theory calculation results in Fig.
+\ref{fig_theory_50_50} (b) shows our exponential mechanism can output good answer with higher probability and output bad answer with lower probability as well.
 
@@
     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
-\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20) $,}
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20) $}
 \label{fig_theory_20_20_20}
@@
 In Fig.
-\ref{fig_theory_20_20_20}, we plotted these discrete probabilities under the case (x=(20,20,20)),  I think this plot shows the laplace mech performs better than ExpMech to some extent but not significant.
+\ref{fig_theory_20_20_20}, we plotted these discrete probabilities under the case (x=(20,20,20)).
+Fig.
+\ref{fig_theory_20_20_20} (a) shows that the  the This plot shows the laplace mech performs better than ExpMech to some extent but not significant.
 
@@
 \ref{fig_theory_20_20_20_20}, we plotted these discrete probabilities under the case ($x=(20,20,20,20)$).
-this plot can show clearly that the Laplace Mech are better than Exp Mech when the size is larger and order is higher.
+This plot can show clearly that the Laplace Mech are better than Exp Mech when the size is larger and order is higher.
 The Laplace can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $,}
+\label{fig_theory_1_1_1_77}
+\end{center}
+\end{figure*}
+
+We also consider an edge case, In Fig.
+\ref{fig_theory_1_1_1_77}, we plotted these discrete probabilities under the case ($x=(1,1,1,77)$).
+This plot can show clearly that the Laplace Mech are better than Exp Mech when the size is larger and order is higher.
+The Laplace can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
+
+From these cases, we can have conclusions like:
+
 \bibliographystyle{plain}

### 2018-06-17 dp_bayesian_inference_model_with_dirichlet_prior_accuracy_study.py

@@ -410,7 +410,7 @@ class BayesInferwithDirPrior(object):
 		#self._show_all()
 		for i in range(times):
 			self._laplace_noize()
-			self._accuracy[self._keys[0]].append(Hellinger_Distance_Dir(self._posterior, self._laplaced_posterior))
+			self._accuracy[self._keys[0]].append(self._posterior - self._laplaced_posterior)
 			# self._laplace_noize()
 			# self._accuracy_l1[self._keys[0]].append(L1_Nrom(self._posterior, self._laplaced_posterior))
 			self._exponentialize_GS()
@@ -674,9 +674,9 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 		probabilities_lap_by_steps.append(pro_i)
 		# print "Pr[H(BI(x), r) = " + str(-Bayesian_Model._candidate_scores[class_i[0]]) + " ] = " + str(pro_i) + " (r = " + str(candidates_for_print) +")"
 #
-	plt.plot(steps[200:], probabilities_exp_by_steps[200:], 'ro', label=('Exp Mech'))
+	plt.plot(steps, probabilities_exp_by_steps, 'ro', label=('Exp Mech'))
 	# plt.plot(T, approximate_bounds, 'g^', label=('Expmech_SS zApproximate Bound'))
-	plt.plot(steps[200:], probabilities_lap_by_steps[200:], 'bs', label=('Laplace Mech'))
+	plt.plot(steps, probabilities_lap_by_steps, 'bs', label=('Laplace Mech'))
 	plt.xlabel("c / (steps from correct answer, in form of Hellinger Distance)")
 	plt.ylabel("Pr[H(BI(x),r) = c]")
 	plt.title("datasize: "+ str(sample_size) + ", x: "+ str(observation) + ", BI(x): beta"+ str(Bayesian_Model._posterior._alphas) + ", epsilon: "+ str(epsilon))
@@ -699,23 +699,23 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 
 if __name__ == "__main__":
 
-	sample_size = 80
+	sample_size = 500
 	epsilon = 0.8
 	delta = 0.00005
-	prior = Dir([1,1,1,1])
-	observation = [1,1,1,77]
-	# Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
+	prior = Dir([1,1])
+	observation = [100,400]
[…]

### 2018-06-18 main.tex
update notes

--- 2018-05-14 main.tex
@@
 
-\subsection{Accuracy Study Based on Hellinger Distance}
+\subsection{Accuracy Study}
+In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.
+
+\subsubsection{Accuracy Study Based on Hellinger Distance}
+\label{subsec_accuracy_hellinger}
 % \begin{figure*}
@@
 % \end{figure*}
+We first analyzed the accuracy based on the Hellinger distance.
+By repeating the experiments for 10000 times and plot their accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
+\ref{fig_beta_hellinger} and Fig.
+\ref{fig_dirichlet_hellinger}.
+X-axis are labeled with different mechanisms.
+We take four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
+Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.
 
@@
 \end{figure*}
+When prior distribution is $\betad$, under data size $n = 500$ and $300$, we get two experiment results shown in Fig.
+\ref{fig_beta_hellinger}.
+It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
 
-We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison.
-As in Fig.
-\ref{fig_beta_hellinger}, the two figures shown the accuracy of four algorithms under same configuration.
-The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
-
-Then, we extended the $\betad$ to the Bernoulli distribution, got the result in Fig. \ref{fig_dirichlet_hellinger}
+To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increase the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 \begin{figure*}
@@
 
-\subsection{Accuracy Study Based on $L_1$ Norm}
-For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig.
+In both of the two cases, the performance of our mechanism and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
+\begin{enumerate}
+	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
+Both of the two exponential mechanisms are do much better than it with global sensitivity.
+	\item The accuracy of our exponential mechanism is better than laplace mechanism. But the advantages are not significant.
+\end{enumerate}
+
+So we need to have a further exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism.
+
+\subsubsection{Accuracy Study Based on $L_1$ Norm}
+\label{subsec_accuracy_l1}
+In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison.
+That is shown in Fig.
 \ref{fig_dirichlet_hellinger_l1}.
@@
 
+The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
+
+\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
+\label{subsec_accuracy_tradeoff}
+Based on accuracy study in Sec.
+\ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism.
+We will do analysis both in theory and experiments based on accuracy bound and probability formula, and then study on some concrete cases.
+
+\subsubsection{Theory Analysis}
+In this part, we will do some theory analysis on the two mechanism's discrete probabilities of outputting each candidate separately.
+In following analysis, we will count the probabilities wrt.
+the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec.
+\ref{subsec_accuracy_hellinger}.
+For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
+Under the Hellinger distance measurement, if two candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
+i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
+
+\begin{itemize}
+
+	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer are calculated as:
+
+	\begin{equation*}
+	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
+	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
+	\end{equation*}
+
+	Every candidate will occupy a portion of 1 as their output probability.
+Suppose candidates within three steps from the correct answer are good answers, the portion occupied by the good answer are decreasing when the size of candidate set increasing.
+That's to say, the probability of outputting good answer are decreasing when the data size and dimension of prior distribution are increasing.
+More specifically, the candidate set size is $\sim n^{m-1}$, which means the probability of outputting good answers are decreasing with speed $\sim n^{m-1}$.
+
+	\item However, in Laplace mechanism, the probability of producing noise has little business with the size of the candidate set.
+In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ identical and independently.
+So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of every noise $|Lap_i|$.
+In order to get the probability of one candidate, we need to have a set $S_{noise}$ obtained from $L_{noise}$ by removing the duplicate values, a list $L_{noise/0}$ by removing the value 0.
+Then, the probabilities of outputting one candidate in Laplace mechanism can be computed by:
+
+	\begin{equation*}
+	\begin{split}
+	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
+	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[(|Lap_1|, |Lap_2|, \cdots, |Lap_{m-1}|)] \\
+	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[|Lap_1| \leq Lap(\frac{2}{\epsilon}) < |Lap_1| + 1] \\
+	& \times Pr[|Lap_2| \leq Lap(\frac{2}{\epsilon}) < |Lap_2| + 1] \times \cdots \\
+	& \times Pr[|Lap_{m-1}| \leq Lap(\frac{2}{\epsilon}) < |Lap_{m-1}| + 1]
+	\end{split}
+	\end{equation*}
+
+	By summing up the probability value of candidates whose steps from correct answer are the same, we can finally get the probability wrt. steps from correct answer.
+
+	From analysis above, we can see the probability of output the good answer will not changed a lot as the size of the candidate set increasing.
+Specifically, we can easily have the two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
+As a results, the probability of outputting good answers are decreasing with speed upper bounded by $(m-1)!
+\times 2^{m-1}$, which is much more smaller than in exponential mechanism.
+Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.
+
+	\item Then, we do some concrete cases analysis.
+
+	\begin{itemize}
+		\item when the prior is $\betad(1,1)$, the observed data set is $(1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
+
+		\begin{center}
+		 \begin{tabular}{c | c | c} 
+		 \hline
+		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
+		 \hline\hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
+		 \hline
+		\end{tabular}
+		\end{center}
+
+		\item when the prior is $\dirichlet(1,1,1)$, the observed data set is $(20,20,20)$ (suppose a black box will produce $A$, $B$, $C$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$, $20$ times $B$ and $20$ times $C$), we can get the posterior distribution $\dirichlet(21,21,21)$
+
+		\begin{center}
+		 \begin{tabular}{c | c | c} 
+		 \hline
+		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
+		 \hline\hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
+		 \hline
+		 \multicolumn{3}{c}{$\cdots$}  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
+		 \hline
+		\end{tabular}
+		\end{center}
+
+		In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
+
+		\item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
+Some probabilities from the two mechanisms are listed as follows:
+		\begin{center}
+		 \begin{tabular}{c | c | c} 
+		 \hline
+		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
+		 \hline\hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
+		 \hline
+		 \multicolumn{3}{c}{$\cdots$}  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
+		 \hline
+		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
+		 \hline
+		\end{tabular}
+		\end{center}
+
+		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
+These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
+Moreover, in our mechanism the bod answer and good answer have very similar outputting probabilities.
+
+	\end{itemize}
+
+\end{itemize}
+
+\subsubsection{Experiment Analysis}
+In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
+By computing the two mechanisms' discrete probabilities wrt.
+steps from correct answer.
+Then we got groups of discrete probabilities wrt.
+the steps (i.e., Hellinegr distance) from the correct answer, and plotted them.
+Under different settings, we got same results as in Fig.
+\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.
+
+Subfigs (a) are from Sec.
+\ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
+x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
+Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
+the steps.
+x-axis is the hellinger distance from correct answer, i.e.
+steps from correct answer.
+Since they have the same meaning, here we just use the hellinger distance to label the x-axis.
+The y-axis is the probability of output candidates with corresponding steps (i.e.
+Hellinger distance) from correct answer.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{50_50.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+\label{fig_theory_50_50}
+\end{center}
+\end{figure*}
+
+When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
+\ref{fig_theory_50_50}.
+In Fig.
+\ref{fig_theory_50_50} (a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
+In the mean time, the theory calculation results in Fig.
+\ref{fig_theory_50_50} (b) also shows our exponential mechanism can output good answer with higher probability and output bad answer with lower probability as well.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
+\label{fig_theory_20_20_20}
+\end{center}
+\end{figure*}
+
+In Fig.
+\ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$).
+SubFig.
+\ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism.
+Meanwhile, the SubFig.
+\ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers.
+The advantage is not significant.
+So, we increase the data size and the dimension to have the next case.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+\label{fig_theory_20_20_20_20}
+\end{center}
+\end{figure*}
+
+Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
+\ref{fig_theory_20_20_20_20}.
+In this plot, SubFig.
+\ref{fig_theory_20_20_20_20}(a) shows that the Laplace Mech are better than Exp Mech very obviously.
+SubFig (b) shows the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
+The advantage in the SubFig.
+\ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig.
+\ref{fig_theory_20_20_20_20}(b).
+So, we change the variance of the observed data set to have the next case.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
+  \subfigure[discrete probabilities wrt. hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
+\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+\label{fig_theory_1_1_1_77}
+\end{center}
+\end{figure*}
+
+In Fig.
+\ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities.
+This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b).
+In SubFig.
+\ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms.
+Also, in SubFig.
+\ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
+Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.
+
+From the theory and experimental analysis above, we obtained some conclusions
+\begin{enumerate}
+	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
+
+	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
+
+	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
+\end{enumerate}
+
 \bibliographystyle{plain}

### 2018-06-18 dp_bayesian_inference_model_with_dirichlet_prior_accuracy_study.py

@@ -649,7 +649,7 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 			i += 1
 		candidates_classfied_by_steps.append(candidates_for_classify)
 		probabilities_exp_by_steps.append(Bayesian_Model._SS_probabilities[j]*(i - j))
-		# print "Pr[H(BI(x), r) = " + str(-sorted_scores[j][1]) + " ] = " + str(Bayesian_Model._SS_probabilities[j]*(i - j)) + " (r = " + str(candidates_for_print) +")"
+		print "Pr[H(BI(x), r) = " + str(-sorted_scores[j][1]) + " ] = " + str(Bayesian_Model._SS_probabilities[j]*(i - j)) + " (r = " + str(candidates_for_print) +")"
    
 	# y = numpy.arange(0,4,1)
 	laplace_probabilities = {}
@@ -672,7 +672,7 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 			pro_i += laplace_probabilities[c]
 			candidates_for_print.append(c._alphas)
 		probabilities_lap_by_steps.append(pro_i)
-		# print "Pr[H(BI(x), r) = " + str(-Bayesian_Model._candidate_scores[class_i[0]]) + " ] = " + str(pro_i) + " (r = " + str(candidates_for_print) +")"
+		print "Pr[H(BI(x), r) = " + str(-Bayesian_Model._candidate_scores[class_i[0]]) + " ] = " + str(pro_i) + " (r = " + str(candidates_for_print) +")"
 #
 	plt.plot(steps, probabilities_exp_by_steps, 'ro', label=('Exp Mech'))
 	# plt.plot(T, approximate_bounds, 'g^', label=('Expmech_SS zApproximate Bound'))
@@ -699,23 +699,23 @@ def accuracy_study_discrete(sample_size,epsilon,delta,prior,observation):
 
 if __name__ == "__main__":
 
-	sample_size = 500
+	sample_size = 53
 	epsilon = 0.8
 	delta = 0.00005
-	prior = Dir([1,1])
-	observation = [100,400]
-	Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
+	prior = Dir([1,1,1,1])
+	observation = [1,1,1,50]
+	# Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
 
-	# accuracy_study_discrete(sample_size,epsilon,delta,prior,observation)
[…]

### 2018-06-18 main.tex
update notes

@@
 
-	Every candidate will occupy a portion of 1 as their output probability.
+	Each candidate will occupy a portion of ``$1$'' as their outputting probability.
 Suppose candidates within three steps from the correct answer are good answers, the portion occupied by the good answer are decreasing when the size of candidate set increasing.
-That's to say, the probability of outputting good answer are decreasing when the data size and dimension of prior distribution are increasing.
+That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing.
 More specifically, the candidate set size is $\sim n^{m-1}$, which means the probability of outputting good answers are decreasing with speed $\sim n^{m-1}$.
@@
 Specifically, we can easily have the two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
-As a results, the probability of outputting good answers are decreasing with speed upper bounded by $(m-1)!
-\times 2^{m-1}$, which is much more smaller than in exponential mechanism.
+As a result, the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
+\times 2^{m-1}$.
+Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)!
+\times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism.
 Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.

### 2018-06-18 main.tex
fix mistakes

@@
 \subsubsection{Theory Analysis}
-In this part, we will do some theory analysis on the two mechanism's discrete probabilities of outputting each candidate separately.
+In this part, we will do some theory analysis on the two mechanisms' discrete probabilities of outputting each candidate separately.
 In following analysis, we will count the probabilities wrt.

### 2018-06-18 main.tex
fix mistakes

@@
 We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plot their accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
+By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
 \ref{fig_beta_hellinger} and Fig.
 \ref{fig_dirichlet_hellinger}.
-X-axis are labeled with different mechanisms.
-We take four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
+X-axis is labeled with different mechanisms.
+We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
 Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.
@@
 \end{figure*}
-When prior distribution is $\betad$, under data size $n = 500$ and $300$, we get two experiment results shown in Fig.
+When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
 \ref{fig_beta_hellinger}.
@@
 
-To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increase the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
+To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 \begin{figure*}
@@
 
-In both of the two cases, the performance of our mechanism and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
+In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
 \begin{enumerate}
@@
 Both of the two exponential mechanisms are do much better than it with global sensitivity.
-	\item The accuracy of our exponential mechanism is better than laplace mechanism. But the advantages are not significant.
+	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
 \end{enumerate}
@@
 \label{subsec_accuracy_l1}
-In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison.
-That is shown in Fig.
+In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
 \ref{fig_dirichlet_hellinger_l1}.
@@
 \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism.
-We will do analysis both in theory and experiments based on accuracy bound and probability formula, and then study on some concrete cases.
+We will do analysis both in theory and experiment based on accuracy bound and probability formula, and then study on some concrete cases.
 
 \subsubsection{Theory Analysis}
-In this part, we will do some theory analysis on the two mechanisms' discrete probabilities of outputting each candidate separately.
+In this part, we will do theory analysis on the two mechanisms' discrete probabilities of outputting each candidate separately.
 In following analysis, we will count the probabilities wrt.
@@
 For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
-Under the Hellinger distance measurement, if two candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
+Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
 i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
+This will make the results more clear and observable.
 
@@
 
-	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer are calculated as:
+	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:
 
@@
 	Each candidate will occupy a portion of ``$1$'' as their outputting probability.
-Suppose candidates within three steps from the correct answer are good answers, the portion occupied by the good answer are decreasing when the size of candidate set increasing.
+Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing.
 That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing.
-More specifically, the candidate set size is $\sim n^{m-1}$, which means the probability of outputting good answers are decreasing with speed $\sim n^{m-1}$.
+More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.
 
-	\item However, in Laplace mechanism, the probability of producing noise has little business with the size of the candidate set.
+	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
 In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ identical and independently.

### 2018-06-18 main.tex
update notes

@@
 	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
-In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ identical and independently.
+In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are identical and independently.
 So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of every noise $|Lap_i|$.
-In order to get the probability of one candidate, we need to have a set $S_{noise}$ obtained from $L_{noise}$ by removing the duplicate values, a list $L_{noise/0}$ by removing the value 0.
+In order to get the probability of one candidate, we also need to have a set of noise $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and a list $L_{noise/0}$ by removing the value 0 from $L_{noise}$.
 Then, the probabilities of outputting one candidate in Laplace mechanism can be computed by:
@@
 
-	By summing up the probability value of candidates whose steps from correct answer are the same, we can finally get the probability wrt. steps from correct answer.
+	By summing up the probability value of candidates whose steps from correct answer are the same, we can finally get the probability wrt. steps from correct answer in Laplace mechanism.
 
-	From analysis above, we can see the probability of output the good answer will not changed a lot as the size of the candidate set increasing.
-Specifically, we can easily have the two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
-As a result, the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
+	From analysis above, we can see the probabilities of output the good answers will not changed a lot as the size of the candidate set increasing.
+Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
+From the two upper bounds, we can have that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
 \times 2^{m-1}$.
@@
 	\begin{itemize}
-		\item when the prior is $\betad(1,1)$, the observed data set is $(1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
+		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
 
@@
 
-		\item when the prior is $\dirichlet(1,1,1)$, the observed data set is $(20,20,20)$ (suppose a black box will produce $A$, $B$, $C$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$, $20$ times $B$ and $20$ times $C$), we can get the posterior distribution $\dirichlet(21,21,21)$
+		Here, there are only 5 kind of steps from correct answer.
+Our mechanism in the second column is clearly better than Laplace mechanism in the third column.
+When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism.
+On the other hand, when candidates are far away from correct answer (for example, $3, 4$) steps), our mechanism can output them with lower probabilities.
+
+		\item when the prior is $\dirichlet(1,1,1)$, the observed data set $x = (20,20,20)$ (suppose a black box will produce $A$, $B$, $C$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$, $20$ times $B$ and $20$ times $C$), we can get the posterior distribution $\dirichlet(21,21,21)$
 

### 2018-06-19 main.tex
update notes
complete the accuracy analysis part

@@
 \subsection{Laplace Mechanism}
-Fixing a data set $x$, we already had the accuracy bound based on the $l_1$ norm as:
+Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism as:
 \begin{equation*}
-Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] \leq \gamma,
-\end{equation*}
-where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
-\begin{equation*}
-\begin{split}
-Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-& = \gamma
-\end{split} 
+Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
 \end{equation*}
 
+So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.
+
+When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
+Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output.
+Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.
+
+% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
+% \begin{equation*}
+% \begin{split}
+% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
+% & = \gamma
+% \end{split} 
+% \end{equation*}
+
 \subsection{Exponential Mechanism with Global Sensitivity}
-
-\subsection{Exponential Mechanism with Local Sensitivity}
+Also, from the \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
+\end{equation*}
+where $|R|$ is the size of the candidate set.
+Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we have a simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
 
 \subsection{Exponential Mechanism with Smooth Sensitivity}
+We explored three accuracy bound for our exponential mechanism.
+
+First is the tight bound with very accurate calculation.
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
+\end{equation*}
+
+In order to be more efficiently, we design the second accuracy bound which is slightly looser than the first one:
+
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
+\end{equation*}
+
+In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
+
+\begin{equation*}
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
+\end{equation*}
+where we replace the $NL_x$ with a value only related to the size of the data. We haven't figure out the formula of this $N(n)$.
+
+In the three accuracy bounds, we will use the first one mostly in following analysis.
 
@@
 	\begin{itemize}
+
 		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:

### 2018-06-19 main.tex
update titles

@@
 
-\subsection{Accuracy Study}
+\subsection{Experimental Evaluations on Accuracy}
 In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.
 
-\subsubsection{Accuracy Study Based on Hellinger Distance}
+\subsubsection{Based on Hellinger Distance}
 \label{subsec_accuracy_hellinger}
@@
 
-\subsubsection{Accuracy Study Based on $L_1$ Norm}
+\subsubsection{Based on $L_1$ Norm}
 \label{subsec_accuracy_l1}
@@
 
-\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
+\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
 \label{subsec_accuracy_tradeoff}

### 2018-06-19 main.tex
fix mistake in notes

@@
 \begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = z]
+\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = e^{\lambda} z] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
 \end{equation*}
@@
 
-The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),r)$ is smaller than zero, i.e., $u(r,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
-We set the $h(z) = Pr[u(\hexpmech(x)) = z] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
+We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
 
 We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(z)}{h(e^{\lambda}z)} = \frac{exp(\frac{\epsilon z}{2 S(x)})}{exp(\frac{\epsilon (z \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
 
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
+Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
 Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
 Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.\\
+The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$.
+Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\
 

### 2018-06-19 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py
adjust figure location

@@ -659,7 +659,7 @@ def epsilon_study(sample_size,epsilon,delta,prior,x1, x2):
 	for key, item in x1_probabilities.items():
 		for k,i in x2_probabilities.items():
 			if key._alphas == k._alphas:
-				print "Pr[ ( M(x1) = " + str(key._alphas) + ") / ( M(x1) = " + str(key._alphas) + ") ] = " + str(math.log(item / i))
+				print "Pr[ ( M(x1) = " + str(key._alphas) + ") / ( M(x2) = " + str(key._alphas) + ") ] = exp(" + str(math.log(item / i)) + ")"
 
 
 

### 2018-06-19 main.tex
adjust figure location
fix location

@@
 % \end{figure*}
-We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
-\ref{fig_beta_hellinger} and Fig.
-\ref{fig_dirichlet_hellinger}.
-X-axis is labeled with different mechanisms.
-We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
-Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.
 
@@
 \end{figure*}
-When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
-\ref{fig_beta_hellinger}.
-It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
 
-To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 \begin{figure*}
@@
 \end{figure*}
+
+We first analyzed the accuracy based on the Hellinger distance.
+By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
+\ref{fig_beta_hellinger} and Fig.
+\ref{fig_dirichlet_hellinger}.
+X-axis is labeled with different mechanisms.
+We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
+Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.
+
+When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
+\ref{fig_beta_hellinger}.
+It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
+
+To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 
@@
 the steps.
-x-axis is the hellinger distance from correct answer, i.e.
+x-axis is the Hellinger distance from correct answer, i.e.
 steps from correct answer.
-Since they have the same meaning, here we just use the hellinger distance to label the x-axis.
+Since they have the same meaning, here we just use the Hellinger distance to label the x-axis.
 The y-axis is the probability of output candidates with corresponding steps (i.e.

### 2018-06-19 main.tex
fix mistakes in notes

@@
 \subsection{Laplace Mechanism}
-Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism as:
+Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
 \begin{equation*}
@@
 \subsection{Exponential Mechanism with Global Sensitivity}
-Also, from the \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
+Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
 \begin{equation*}
@@
 where $|R|$ is the size of the candidate set.
-Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we have a simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
+Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
 
 \subsection{Exponential Mechanism with Smooth Sensitivity}
-We explored three accuracy bound for our exponential mechanism.
+We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
 
@@
 
-In order to be more efficiently, we design the second accuracy bound which is slightly looser than the first one:
+In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
 
@@
 \end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. We haven't figure out the formula of this $N(n)$.
+where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
 
-In the three accuracy bounds, we will use the first one mostly in following analysis.
+Within the three accuracy bounds, we will mainly use the first one in following analysis.
 
@@
 \subsection{Computation Efficiency}
-The formula for computing the local sensitivity is presented in Sec.
+The formula for computing the local sensitivity presented in Sec.
 \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
@@
 \subsection{Experimental Evaluations on Accuracy}
-In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.
+In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
 
@@
 We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig.
+By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
 \ref{fig_beta_hellinger} and Fig.
@@
 We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
-Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.
+Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.
 
@@
 
-To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
+To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 
@@
 Based on accuracy study in Sec.
-\ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism.
-We will do analysis both in theory and experiment based on accuracy bound and probability formula, and then study on some concrete cases.
+\ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism.
+We will do analysis both in theory and experiment and do some concrete case studies.
 
@@
 	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
-In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are identical and independently.
-So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of every noise $|Lap_i|$.
-In order to get the probability of one candidate, we also need to have a set of noise $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and a list $L_{noise/0}$ by removing the value 0 from $L_{noise}$.
-Then, the probabilities of outputting one candidate in Laplace mechanism can be computed by:
+In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d.
+So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of each noise $|Lap_i|$.
+In order to get the probability of a single candidate, we also need to have the set of noises $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and the list $L_{noise/0}$ by removing 0s from $L_{noise}$.
+Then, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
 
@@
 
-	From analysis above, we can see the probabilities of output the good answers will not changed a lot as the size of the candidate set increasing.
+	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing.
 Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
-From the two upper bounds, we can have that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
+From the two upper bounds, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
 \times 2^{m-1}$.
@@
 
-		Here, there are only 5 kind of steps from correct answer.
+		Here, there are only 5 kinds of steps from correct answer.
 Our mechanism in the second column is clearly better than Laplace mechanism in the third column.
 When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism.
-On the other hand, when candidates are far away from correct answer (for example, $3, 4$) steps), our mechanism can output them with lower probabilities.
+On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.
 
@@
 These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bod answer and good answer have very similar outputting probabilities.
+Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
 
@@
 By computing the two mechanisms' discrete probabilities wrt.
-steps from correct answer.
-Then we got groups of discrete probabilities wrt.
-the steps (i.e., Hellinegr distance) from the correct answer, and plotted them.
-Under different settings, we got same results as in Fig.
+steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig.
 \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.

### 2018-06-19 main.tex
fix bugs in notes

@@
 steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig.
-\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.
+\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.
 
-Subfigs (a) are from Sec.
+Subfigs (a) based on Sec.
 \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
-x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
+The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
 Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
 the steps.
-x-axis is the Hellinger distance from correct answer, i.e.
+The x-axis is the Hellinger distance from correct answer, i.e.
 steps from correct answer.
-Since they have the same meaning, here we just use the Hellinger distance to label the x-axis.
+Since they have the same meaning, we just use the Hellinger distance to label the x-axis here.
 The y-axis is the probability of output candidates with corresponding steps (i.e.
@@
 \ref{fig_theory_50_50}.
-In Fig.
-\ref{fig_theory_50_50} (a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
-In the mean time, the theory calculation results in Fig.
-\ref{fig_theory_50_50} (b) also shows our exponential mechanism can output good answer with higher probability and output bad answer with lower probability as well.
+In Subfig.
+\ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
+In the mean time, the theory calculation results in Subfig.
+\ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.
 
@@
 The advantage is not significant.
-So, we increase the data size and the dimension to have the next case.
+So, we increase the data size and the dimension in next case to have a further study.
 
@@
 \ref{fig_theory_20_20_20_20}.
-In this plot, SubFig.
-\ref{fig_theory_20_20_20_20}(a) shows that the Laplace Mech are better than Exp Mech very obviously.
-SubFig (b) shows the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
+Subfig.
+\ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously.
+Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
 The advantage in the SubFig.
@@
 \ref{fig_theory_20_20_20_20}(b).
-So, we change the variance of the observed data set to have the next case.
+So, we change the variance of the observed data set in the next case.
 
@@
 This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b).
-In SubFig.
+In Subfig.
 \ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms.
-Also, in SubFig.
+Also, in Subfig.
 \ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.

### 2018-07-07 main.tex
fix mistake in notes
update notes

@@
 \begin{equation*}
-S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(x),-)\cdot e^{-\beta d(x,y)})),
+S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
 \end{equation*}
@@
 
+\subsection{Accuracy Evaluation wrt. Different Variables}
+\label{subsubsec_vs_variables}
+
+In this section, we evaluate the accuracy wrt.
+four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables.
+We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable.
+In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables.
+The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.
+
+\subsubsection{Accuracy Evaluation wrt. Datasize}
+\label{subsubsec_vs_datasize}
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
+    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
+  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
+    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
+\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
+\label{fig_vs_datasize}
+\end{center}
+\end{figure*}
+
+In Fig.
+\ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing.
+In Fig.
+\ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12.
+Same as in Fig.
+\ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.
+
+\subsubsection{Accuracy Evaluation wrt. Dimensions}
+\label{subsubsec_vs_dimension}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
+\caption{Accuracy measurement based on Hellinger distance wrt.
+different dimensions and data size.
+Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+\label{fig_vs_dimension}
+\end{figure}
+
+In Fig.
+\ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions.
+The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism.
+Accuracy of two mechanisms both decrease when dimensions go larger.
+We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase.
+In other words, dimension has little influence on whether we will beat Laplace mechanism.
+
+\subsubsection{Accuracy Evaluation wrt. Data variance}
+\label{subsubsec_vs_variance}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
+\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+\label{fig_vs_variance}
+\end{figure}
+
+In Fig.
+\ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means).
+We study this variable under two-dimension $\betad$ distribution in order to be concise.
+It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse.
+We will beat Laplace mechanism when observed data are more uniformly.
+
+\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
+\label{subsubsec_vs_prior}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
+\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
+\label{fig_vs_prior}
+\end{figure}
+
+In Fig.
+\ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig.
+\ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed.
+
+\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
+\label{subsec_vs_prior_variance}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\label{fig_vs_prior_variance}
+\end{figure}
+
+\subsection{Experiment Evaluations on Privacy}
+\label{subsec_experiment_privacy}
+In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
+The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
+\ref{sec_smoo} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
+We calculate the concrete privacy value in following ways wrt.
+the data size, and obtain plots in Fig.
+\ref{fig_privacy}.
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[data size range from 90 to 180]{
+    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20.eps}}
+  \subfigure[data size range from 90 to 180]{
+    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20(2).eps}} 
+\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
+\label{fig_privacy}
+\end{center}
+\end{figure*}
+
+$\epsilon = $
+
 \bibliographystyle{plain}

### 2018-07-07 main.tex
update privacy on notes

@@
 \ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed.
+The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
 
@@
 \end{figure}
+
+Here, we change the prior distribution and data variance in the same time.
+As shown in Fig.
+\ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary.
+Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.
 
@@
 
-$\epsilon = $
+$\epsilon = 0.8$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
+That is to say, we achieved a higher privacy level than expected.
+In next step, we are going to improve the accuracy using this property.
 

### 2018-07-07 main.tex
note organization updates

@@
 
-\section{Experimental Evaluations}
-\subsection{Computation Efficiency}
-The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
-i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
-We also have some experiments for validating our proposal as in Fig.
-\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
-It is shown that maximum value taken when  $r = \bysinfer(x)$.
+\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
+\label{subsec_accuracy_tradeoff}
+Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.
 
- \begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{efficiency}
-\label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\end{figure}
-
-\subsection{Experimental Evaluations on Accuracy}
-In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
-
-\subsubsection{Based on Hellinger Distance}
-\label{subsec_accuracy_hellinger}
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
-%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
-% \caption{The experimental results of accuracy of four algorithms}
-% \label{fig_data}
-% \end{center}
-% \end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
-  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
-\label{fig_beta_hellinger}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
-  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
-\label{fig_dirichlet_hellinger}
-\end{center}
-\end{figure*}
-
-We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
-\ref{fig_beta_hellinger} and Fig.
-\ref{fig_dirichlet_hellinger}.
-X-axis is labeled with different mechanisms.
-We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
-Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.
-
-When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
-\ref{fig_beta_hellinger}.
-It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
-
-To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
-
-In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
-\begin{enumerate}
-	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
-Both of the two exponential mechanisms are do much better than it with global sensitivity.
-	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
-\end{enumerate}
-
-So we need to have a further exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism.
-
-\subsubsection{Based on $L_1$ Norm}
-\label{subsec_accuracy_l1}
-In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
-\ref{fig_dirichlet_hellinger_l1}.
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
-  \subfigure[accuracy measurement based on $l_1$ norm]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
-\label{fig_dirichlet_hellinger_l1}
-\end{center}
-\end{figure*}
-
-The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
-
-\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
-\label{subsec_accuracy_tradeoff}
-Based on accuracy study in Sec.
-\ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism.
-We will do analysis both in theory and experiment and do some concrete case studies.
-
-\subsubsection{Theory Analysis}
-In this part, we will do theory analysis on the two mechanisms' discrete probabilities of outputting each candidate separately.
+\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
+In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately.
 In following analysis, we will count the probabilities wrt.
@@
 In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d.
-So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of each noise $|Lap_i|$.
-In order to get the probability of a single candidate, we also need to have the set of noises $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and the list $L_{noise/0}$ by removing 0s from $L_{noise}$.
-Then, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
+So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
 
@@
 	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
-	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[(|Lap_1|, |Lap_2|, \cdots, |Lap_{m-1}|)] \\
-	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[|Lap_1| \leq Lap(\frac{2}{\epsilon}) < |Lap_1| + 1] \\
-	& \times Pr[|Lap_2| \leq Lap(\frac{2}{\epsilon}) < |Lap_2| + 1] \times \cdots \\
-	& \times Pr[|Lap_{m-1}| \leq Lap(\frac{2}{\epsilon}) < |Lap_{m-1}| + 1]
+	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
+	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
+	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
 	\end{split}
 	\end{equation*}
-
-	By summing up the probability value of candidates whose steps from correct answer are the same, we can finally get the probability wrt. steps from correct answer in Laplace mechanism.
+	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.
 
 	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing.
-Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$.
-From the two upper bounds, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)!
-\times 2^{m-1}$.
-Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)!
-\times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism.
-Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.
+Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.
 
@@
 
-		\item when the prior is $\dirichlet(1,1,1)$, the observed data set $x = (20,20,20)$ (suppose a black box will produce $A$, $B$, $C$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$, $20$ times $B$ and $20$ times $C$), we can get the posterior distribution $\dirichlet(21,21,21)$
+		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$
 
@@
 
-		In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
+		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
+These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
+Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
 
-		\item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
+		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
+
+		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
 Some probabilities from the two mechanisms are listed as follows:
-		\begin{center}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
-		 \hline
-		 \multicolumn{3}{c}{$\cdots$}  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
-		 \hline
-		\end{tabular}
-		\end{center}
+		% \begin{center}
+		%  \begin{tabular}{c | c | c} 
+		%  \hline
+		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
+		%  \hline\hline
+		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
+		%  \hline
+		%  \multicolumn{3}{c}{$\cdots$}  \\
+		%  \hline
+		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
+		%  \hline
+		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
+		%  \hline
+		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
+		%  \hline
+		% \end{tabular}
+		% \end{center}
 
-		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
+		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
 These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
@@
 
-\subsubsection{Experiment Analysis}
-In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]{efficiency}
+\label{fig_efficiency}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\end{figure}
+
+\subsubsection{Accuracy Analysis wrt. prior distribution}
+
+\subsubsection{Accuracy Analysis wrt. data variance}
+
+\section{Experimental Evaluations}
+\label{experiment}
+
+\subsection{Computation Efficiency}
+\label{subsec_effi}
+The formula for computing the local sensitivity presented in Sec.
+\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
+i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
+We also have some experiments for validating our proposal as in Fig.
+\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
+It is shown that maximum value taken when  $r = \bysinfer(x)$.
+
+\subsection{Experimental Evaluations on Accuracy}
+\label{subsec_experiment_accuracy}
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
+  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
+    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
+\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
+\label{fig_beta_hellinger}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
+    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
+  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
+    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
+\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
+\label{fig_dirichlet_hellinger}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\centering
+  \subfigure[accuracy measurement based on Hellinger distance]{
+    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
+  \subfigure[accuracy measurement based on $l_1$ norm]{
+    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
+\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
+\label{fig_dirichlet_hellinger_l1}
+\end{center}
+\end{figure*}
+
+In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
+%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
+%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
+%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
+% \caption{The experimental results of accuracy of four algorithms}
+% \label{fig_data}
+% \end{center}
+% \end{figure*}
+
+We first analyzed the accuracy based on the Hellinger distance.
+By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
+\ref{fig_beta_hellinger} and Fig.
+\ref{fig_dirichlet_hellinger}.
+X-axis is labeled with different mechanisms.
+We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
+Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.
+
+When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
+\ref{fig_beta_hellinger}.
+It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
+
+To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
+
+Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
+\ref{fig_dirichlet_hellinger_l1}.
+
+The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
+
+In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
+\begin{enumerate}
+	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
+Both of the two exponential mechanisms are do much better than it with global sensitivity.
+	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
+\end{enumerate}
+
+In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.
+
+% \subsubsection{Experiment Analysis}
+% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
 By computing the two mechanisms' discrete probabilities wrt.
@@
 
-Subfigs (a) based on Sec.
+% Subfigs (a) based on Sec.
 \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
@@
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
-  \subfigure[discrete probabilities wrt. hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{50_50.eps}} 
-\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-\label{fig_theory_50_50}
-\end{center}
-\end{figure*}
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[accuracy measurement based on Hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
+%   \subfigure[discrete probabilities wrt. hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
+% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+% \label{fig_theory_50_50}
+% \end{center}
+% \end{figure*}
 
-When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
+% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
 \ref{fig_theory_50_50}.
@@
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
-  \subfigure[discrete probabilities wrt. hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
-\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
-\label{fig_theory_20_20_20}
-\end{center}
-\end{figure*}
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[accuracy measurement based on Hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
+%   \subfigure[discrete probabilities wrt. hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
+% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
+% \label{fig_theory_20_20_20}
+% \end{center}
+% \end{figure*}
 
-In Fig.
+% In Fig.
 \ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$).
@@
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
-  \subfigure[discrete probabilities wrt. hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
-\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-\label{fig_theory_20_20_20_20}
-\end{center}
-\end{figure*}
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[accuracy measurement based on Hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
+%   \subfigure[discrete probabilities wrt. hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
+% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+% \label{fig_theory_20_20_20_20}
+% \end{center}
+% \end{figure*}
 
-Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
+% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
 \ref{fig_theory_20_20_20_20}.
@@
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
-  \subfigure[discrete probabilities wrt. hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
-\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-\label{fig_theory_1_1_1_77}
-\end{center}
-\end{figure*}
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[accuracy measurement based on Hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
+%   \subfigure[discrete probabilities wrt. hellinger distance]{
+%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
+% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
+% \label{fig_theory_1_1_1_77}
+% \end{center}
+% \end{figure*}
 
-In Fig.
+% In Fig.
 \ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities.
@@
 
-From the theory and experimental analysis above, we obtained some conclusions
-\begin{enumerate}
-	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
+% From the theory and experimental analysis above, we obtained some conclusions
+% \begin{enumerate}
+% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
 
-	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
+% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
 
-	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
-\end{enumerate}
+% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
+% \end{enumerate}
 
-\subsection{Accuracy Evaluation wrt. Different Variables}
+\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
 \label{subsubsec_vs_variables}

### 2018-07-07 main.tex
update theory analysis

@@
 
-\begin{definition} The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
+\begin{definition}
+\label{def_smoo}
+The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
 \begin{equation*}
@@
 \subsection{Laplace Mechanism}
+\label{subsec_accuracy_lap}
 Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
@@
 \subsection{Exponential Mechanism with Global Sensitivity}
+\label{subsec_accuracy_global}
 Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
@@
 \subsection{Exponential Mechanism with Smooth Sensitivity}
+\label{subsec_accuracy_smoo}
 We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
@@
 In following analysis, we will count the probabilities wrt.
-the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec.
-\ref{subsec_accuracy_hellinger}.
+the steps from correct answer, in order to be more concise.
 For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
@@
 
+\subsubsection{Accuracy Analysis wrt. prior distribution}
+In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig.
+\ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{sensitivity}
+\label{fig_sensitivity}
+\caption{Hellinger distance study}
+\end{figure}
+
+As in Fig.
+\ref{fig_sensitivity}, the local sensitivity of Hellinger distance will decrease when $\betad$ distribution's two parameters get closer (i.e.
+more uniform) and larger.
+In the same time, our smooth sensitivity will also decrease based on the Def.
+\ref{def_smoo}.
+From accuracy bound in Sec.
+\ref{subsec_accuracy_smoo}, the accuracy will be improved when sensitivity go larger.
+In consequence, when we increase the prior distribution, the smooth sensitivity in our exponential mechanism will decrease, which means our accuracy will be improved.
+However, the sensitivity of $l_1$ norm in Laplace mechanism is fixed regardless the prior distribution.
+We will study this trade-off in Sec.
+\ref{subsubsec_vs_prior}.
+
+\subsubsection{Accuracy Analysis wrt. data variance}
+
+Similar as above, when the data variance is small (i.e.
+the data are uniform), the parameters of posterior distribution will get more uniform (i.e.
+closer).
+Based on Fig.
+\ref{fig_sensitivity}, the Hellinger distance's sensitivity will get smaller when parameter get closer.
+As a result, the accuracy will be improved in the same time.
+We will study this trade-off in Sec.
+\ref{subsubsec_vs_variance}
+
 \begin{figure}[h]
@@
 
-\subsubsection{Accuracy Analysis wrt. prior distribution}
-
-\subsubsection{Accuracy Analysis wrt. data variance}
-
 \section{Experimental Evaluations}
-\label{experiment}
+\label{sec_experiment}
 
@@
 \subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
-\label{subsubsec_vs_variables}
+\label{subsec_vs_variables}
 
@@
 \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-\label{subsec_vs_prior_variance}
+\label{subsubsec_vs_prior_variance}
 

### 2018-07-08 main-workshop.tex
update submission version

--- 2018-07-07 main.tex
@@
 
-\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
+\section{Problem Statement}
+
+\section{Technical Problem Statement}
 \label{sec_bayesInfer}
+
+Our technical problem is based on the Bernoulli-Beta Bayesian inference.
 In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$.
@@
 
-\section{Algorithm Setting up}
-\label{sec_setup}
-For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.
+\section{Baseline Approach}
 
-\subsection{Exponential Mechanism with Global Sensitivity}
-\label{subsec_emgs}
-
-% \subsubsection{Mechanism Set up}
-
-In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
-\begin{equation*}
-\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
-\end{equation*}
-
-Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
-\begin{equation}
-\label{equ_utility}
-u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
-\end{equation}
-
-Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
-\begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
-\end{equation*}
-where global sensitivity is calculated by:
-\begin{equation*}
-\Delta_{g}u = 
-\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
-|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
-\end{equation*}
-
-The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
-Since $\hlg$ is monotonic, i.e.
-our utility function is monotonic.
-
-% \subsubsection{Security Analysis}
-% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
-For adjacent data set $||x,y||_1 = 1$:
-% \begin{equation*}
-% \begin{split}
-% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-% & =\frac
-% {\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
-% {\frac
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
-% & = \left(\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp\left(\frac
-% {\epsilon (u(x,r) - u(y,r))}
-% {2 \Delta_{g}u}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & \leq
-% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp(\epsilon).
-% \end{split}
-% \end{equation*}
-
-% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
-
-\subsection{Exponential Mechanism with Local Sensitivity}
-\label{subsec_emls}
-% \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
-\begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
-\end{equation*}
-
-where local sensitivity is calculated by:
-
-\begin{equation*}
-\Delta_{l}u(x) = 
-\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
-\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
-\end{equation*}
-
-The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.
-
-\subsection{Exponential Mechanism with Smooth Sensitivity}
+\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
 \label{sec_smoo}
@@
 
-\section{Accuracy Analysis}
-\subsection{Laplace Mechanism}
-Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
-\begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
-\end{equation*}
-
-So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.
-
-When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
-Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output.
-Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.
-
-% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
-% \begin{equation*}
-% \begin{split}
-% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = \gamma
-% \end{split} 
-% \end{equation*}
-
-\subsection{Exponential Mechanism with Global Sensitivity}
-Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
-\end{equation*}
-where $|R|$ is the size of the candidate set.
-Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
-
-\subsection{Exponential Mechanism with Smooth Sensitivity}
-We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
-
-First is the tight bound with very accurate calculation.
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
-\end{equation*}
-
-In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
-\end{equation*}
-
-In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
-\end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
-
-Within the three accuracy bounds, we will mainly use the first one in following analysis.
-
-\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
-\label{subsec_accuracy_tradeoff}
-Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.
-
-\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
-In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately.
-In following analysis, we will count the probabilities wrt.
-the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec.
-\ref{subsec_accuracy_hellinger}.
-For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
-Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
-i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
-This will make the results more clear and observable.
-
-\begin{itemize}
-
-	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:
-
-	\begin{equation*}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
-	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
-	\end{equation*}
-
-	Each candidate will occupy a portion of ``$1$'' as their outputting probability.
-Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing.
-That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing.
-More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.
-
-	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
-In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d.
-So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
-
-	\begin{equation*}
-	\begin{split}
-	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
-	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
-	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
-	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
-	\end{split}
-	\end{equation*}
-	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.
-
-	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing.
-Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.
-
-	\item Then, we do some concrete cases analysis.
-
-	\begin{itemize}
-
-		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
-
-		\begin{center}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
-		 \hline
-		\end{tabular}
-		\end{center}
-
-		Here, there are only 5 kinds of steps from correct answer.
-Our mechanism in the second column is clearly better than Laplace mechanism in the third column.
-When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism.
-On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.
-
-		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$
-
-		\begin{center}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
-		 \hline
-		 \multicolumn{3}{c}{$\cdots$}  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
-		 \hline
-		\end{tabular}
-		\end{center}
-
-		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
-
-		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
-Some probabilities from the two mechanisms are listed as follows:
-		% \begin{center}
-		%  \begin{tabular}{c | c | c} 
-		%  \hline
-		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		%  \hline\hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
-		%  \hline
-		%  \multicolumn{3}{c}{$\cdots$}  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
-		%  \hline
-		% \end{tabular}
-		% \end{center}
-
-		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-	\end{itemize}
-
-\end{itemize}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{efficiency}
-\label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\end{figure}
-
-\subsubsection{Accuracy Analysis wrt. prior distribution}
-
-\subsubsection{Accuracy Analysis wrt. data variance}
-
-\section{Experimental Evaluations}
-\label{experiment}
+\section{Preliminary Experimental Results}
+\label{sec_experiment}
 
@@
 
-In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
+In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close.
+
+\section{Conclusions}
+We can obtain some preliminary conclusions: 
 \begin{enumerate}
@@
 
-% \subsubsection{Experiment Analysis}
-% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
-By computing the two mechanisms' discrete probabilities wrt.
-steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig.
-\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.
-
-% Subfigs (a) based on Sec.
-\ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
-The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
-Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
-the steps.
-The x-axis is the Hellinger distance from correct answer, i.e.
-steps from correct answer.
-Since they have the same meaning, we just use the Hellinger distance to label the x-axis here.
-The y-axis is the probability of output candidates with corresponding steps (i.e.
-Hellinger distance) from correct answer.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_50_50}
-% \end{center}
-% \end{figure*}
-
-% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
-\ref{fig_theory_50_50}.
-In Subfig.
-\ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
-In the mean time, the theory calculation results in Subfig.
-\ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$).
-SubFig.
-\ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism.
-Meanwhile, the SubFig.
-\ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers.
-The advantage is not significant.
-So, we increase the data size and the dimension in next case to have a further study.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
-\ref{fig_theory_20_20_20_20}.
-Subfig.
-\ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously.
-Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
-The advantage in the SubFig.
-\ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig.
-\ref{fig_theory_20_20_20_20}(b).
-So, we change the variance of the observed data set in the next case.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_1_1_1_77}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities.
-This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b).
-In Subfig.
-\ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms.
-Also, in Subfig.
-\ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
-Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.
-
-% From the theory and experimental analysis above, we obtained some conclusions
-% \begin{enumerate}
-% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
-
-% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
-
-% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
-% \end{enumerate}
-
-\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
-\label{subsubsec_vs_variables}
-
-In this section, we evaluate the accuracy wrt.
-four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables.
-We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable.
-In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables.
-The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.
-
-\subsubsection{Accuracy Evaluation wrt. Datasize}
-\label{subsubsec_vs_datasize}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
-  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
-\label{fig_vs_datasize}
-\end{center}
-\end{figure*}
-
-In Fig.
-\ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing.
-In Fig.
-\ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12.
-Same as in Fig.
-\ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.
-
-\subsubsection{Accuracy Evaluation wrt. Dimensions}
-\label{subsubsec_vs_dimension}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
-\caption{Accuracy measurement based on Hellinger distance wrt.
-different dimensions and data size.
-Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
-\label{fig_vs_dimension}
-\end{figure}
-
-In Fig.
-\ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions.
-The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism.
-Accuracy of two mechanisms both decrease when dimensions go larger.
-We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase.
-In other words, dimension has little influence on whether we will beat Laplace mechanism.
-
-\subsubsection{Accuracy Evaluation wrt. Data variance}
-\label{subsubsec_vs_variance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
-\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
-\label{fig_vs_variance}
-\end{figure}
-
-In Fig.
-\ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means).
-We study this variable under two-dimension $\betad$ distribution in order to be concise.
-It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse.
-We will beat Laplace mechanism when observed data are more uniformly.
-
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
-\label{subsubsec_vs_prior}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
-\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
-\label{fig_vs_prior}
-\end{figure}
-
-In Fig.
-\ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig.
-\ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed.
-The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
-
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-\label{subsec_vs_prior_variance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\label{fig_vs_prior_variance}
-\end{figure}
-
-Here, we change the prior distribution and data variance in the same time.
-As shown in Fig.
-\ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary.
-Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.
-
-\subsection{Experiment Evaluations on Privacy}
-\label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_smoo} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
-the data size, and obtain plots in Fig.
-\ref{fig_privacy}.
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20.eps}}
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20(2).eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
-\label{fig_privacy}
-\end{center}
-\end{figure*}
-
-$\epsilon = 0.8$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
-That is to say, we achieved a higher privacy level than expected.
-In next step, we are going to improve the accuracy using this property.
-
 \bibliographystyle{plain}

### 2018-07-08 main.tex
fix bugs
rename file

--- 2018-07-07 main.tex
@@
 
-\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
+\section{Problem Statement}
+Our research is based on an observation that under different measurement, mechanisms usually have different accuracy behavior.
+When adding noise according to a certain measurement, mechanism' accuracy behavior will be better than when adding noise according to other measurements.
+Here we study the private Bayesian inference based on Hellinger distance measurement.
+Showing that our newly-designed mechanism adding noise according to Hellinger distance performs better than baseline mechanism adding noise according to $l_1$ norm.
+
+\section{Technical Problem Statement}
 \label{sec_bayesInfer}
+
+Our study based on the Bernoulli-Beta Bayesian inference.
 In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$.
@@
 
-\section{Algorithm Setting up}
-\label{sec_setup}
-For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.
+\section{Baseline Approach - Laplace Mechanism}
+\label{sec_lap}
+Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism.
+In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
+Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$.
+The private posterior then will be $\dirichlet(\alpha_1 + n_1 + , \alpha_2 + n_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
 
-\subsection{Exponential Mechanism with Global Sensitivity}
-\label{subsec_emgs}
-
-% \subsubsection{Mechanism Set up}
-
-In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
-\begin{equation*}
-\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
-\end{equation*}
-
-Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
-\begin{equation}
-\label{equ_utility}
-u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
-\end{equation}
-
-Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
-\begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
-\end{equation*}
-where global sensitivity is calculated by:
-\begin{equation*}
-\Delta_{g}u = 
-\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
-|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
-\end{equation*}
-
-The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
-Since $\hlg$ is monotonic, i.e.
-our utility function is monotonic.
-
-% \subsubsection{Security Analysis}
-% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
-For adjacent data set $||x,y||_1 = 1$:
-% \begin{equation*}
-% \begin{split}
-% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-% & =\frac
-% {\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
-% {\frac
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
-% & = \left(\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp\left(\frac
-% {\epsilon (u(x,r) - u(y,r))}
-% {2 \Delta_{g}u}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & \leq
-% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp(\epsilon).
-% \end{split}
-% \end{equation*}
-
-% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
-
-\subsection{Exponential Mechanism with Local Sensitivity}
-\label{subsec_emls}
-% \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
-\begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
-\end{equation*}
-
-where local sensitivity is calculated by:
-
-\begin{equation*}
-\Delta_{l}u(x) = 
-\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
-\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
-\end{equation*}
-
-The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.
-
-\subsection{Exponential Mechanism with Smooth Sensitivity}
+\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
 \label{sec_smoo}
 
-\subsubsection{Algorithm Setting up}
+\subsection{Algorithm Setting up}
 We define a new mechanism $\hexpmech(x)$
@@
 
-\subsubsection{Sliding Property of Exponential Mechanism}
+\subsection{Sliding Property of Exponential Mechanism}
 \begin{lem}
@@
 
-\subsubsection{Dilation Property of Exponential Mechanism}
+\subsection{Dilation Property of Exponential Mechanism}
 \begin{lem}
@@
 
-\textbf{Detail proof:}
-\begin{itemize}
+% \textbf{Detail proof:}
+% \begin{itemize}
 
-	\item $\lambda < 0$
+% 	\item $\lambda < 0$
 
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
-		\begin{equation*}
-		\end{equation*}
-	\item $\lambda > 0$
+% 		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
+% 		\begin{equation*}
+% 		\end{equation*}
+% 	\item $\lambda > 0$
 
-Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
-\begin{equation*}
-u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-\end{equation*}
-By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
-\begin{equation*}
-\begin{split}
-Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
-\end{split}
-\end{equation*}
+% Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
+% \begin{equation*}
+% u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+% \end{equation*}
+% By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
+% \begin{equation*}
+% \begin{split}
+% Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+% & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
+% \end{split}
+% \end{equation*}
 
-In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
-\begin{equation*}
-\begin{split}
-Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
-& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
-\end{split}
-\end{equation*}
+% In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
+% \begin{equation*}
+% \begin{split}
+% Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
+% & = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
+% & = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
+% \end{split}
+% \end{equation*}
 
-When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
+% When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
 
-\end{itemize}
+% \end{itemize}
 
@@
 
-\subsubsection{Privacy Analysis}
+\subsection{Privacy Analysis}
 \begin{lem}
@@
 
-\section{Accuracy Analysis}
-\subsection{Laplace Mechanism}
-Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
-\begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
-\end{equation*}
-
-So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.
-
-When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
-Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output.
-Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.
-
-% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
-% \begin{equation*}
-% \begin{split}
-% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = \gamma
-% \end{split} 
-% \end{equation*}
-
-\subsection{Exponential Mechanism with Global Sensitivity}
-Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
-\end{equation*}
-where $|R|$ is the size of the candidate set.
-Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
-
-\subsection{Exponential Mechanism with Smooth Sensitivity}
-We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
-
-First is the tight bound with very accurate calculation.
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
-\end{equation*}
-
-In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
-\end{equation*}
-
-In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
-\end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
-
-Within the three accuracy bounds, we will mainly use the first one in following analysis.
-
-\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
-\label{subsec_accuracy_tradeoff}
-Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.
-
-\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
-In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately.
-In following analysis, we will count the probabilities wrt.
-the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec.
-\ref{subsec_accuracy_hellinger}.
-For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
-Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
-i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
-This will make the results more clear and observable.
-
-\begin{itemize}
-
-	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:
-
-	\begin{equation*}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
-	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
-	\end{equation*}
-
-	Each candidate will occupy a portion of ``$1$'' as their outputting probability.
-Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing.
-That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing.
-More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.
-
-	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
-In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d.
-So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
-
-	\begin{equation*}
-	\begin{split}
-	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
-	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
-	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
-	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
-	\end{split}
-	\end{equation*}
-	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.
-
-	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing.
-Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.
-
-	\item Then, we do some concrete cases analysis.
-
-	\begin{itemize}
-
-		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
-
-		\begin{center}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
-		 \hline
-		\end{tabular}
-		\end{center}
-
-		Here, there are only 5 kinds of steps from correct answer.
-Our mechanism in the second column is clearly better than Laplace mechanism in the third column.
-When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism.
-On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.
-
-		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$
-
-		\begin{center}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
-		 \hline
-		 \multicolumn{3}{c}{$\cdots$}  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
-		 \hline
-		\end{tabular}
-		\end{center}
-
-		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
-
-		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
-Some probabilities from the two mechanisms are listed as follows:
-		% \begin{center}
-		%  \begin{tabular}{c | c | c} 
-		%  \hline
-		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		%  \hline\hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
-		%  \hline
-		%  \multicolumn{3}{c}{$\cdots$}  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
-		%  \hline
-		% \end{tabular}
-		% \end{center}
-
-		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-	\end{itemize}
-
-\end{itemize}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{efficiency}
-\label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\end{figure}
-
-\subsubsection{Accuracy Analysis wrt. prior distribution}
-
-\subsubsection{Accuracy Analysis wrt. data variance}
-
-\section{Experimental Evaluations}
-\label{experiment}
-
-\subsection{Computation Efficiency}
-\label{subsec_effi}
-The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
-i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
-We also have some experiments for validating our proposal as in Fig.
-\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
-It is shown that maximum value taken when  $r = \bysinfer(x)$.
-
-\subsection{Experimental Evaluations on Accuracy}
-\label{subsec_experiment_accuracy}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
-  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
-\label{fig_beta_hellinger}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
-  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
-\label{fig_dirichlet_hellinger}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
-  \subfigure[accuracy measurement based on $l_1$ norm]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
-\label{fig_dirichlet_hellinger_l1}
-\end{center}
-\end{figure*}
-
-In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
-%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
-% \caption{The experimental results of accuracy of four algorithms}
-% \label{fig_data}
-% \end{center}
-% \end{figure*}
-
-We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
-\ref{fig_beta_hellinger} and Fig.
-\ref{fig_dirichlet_hellinger}.
-X-axis is labeled with different mechanisms.
-We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
-Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.
-
-When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
-\ref{fig_beta_hellinger}.
-It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
-
-To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
-
-Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
-\ref{fig_dirichlet_hellinger_l1}.
-
-The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
-
-In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
-\begin{enumerate}
-	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
-Both of the two exponential mechanisms are do much better than it with global sensitivity.
-	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
-\end{enumerate}
-
-In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.
-
-% \subsubsection{Experiment Analysis}
-% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
-By computing the two mechanisms' discrete probabilities wrt.
-steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig.
-\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.
-
-% Subfigs (a) based on Sec.
-\ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
-The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
-Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
-the steps.
-The x-axis is the Hellinger distance from correct answer, i.e.
-steps from correct answer.
-Since they have the same meaning, we just use the Hellinger distance to label the x-axis here.
-The y-axis is the probability of output candidates with corresponding steps (i.e.
-Hellinger distance) from correct answer.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_50_50}
-% \end{center}
-% \end{figure*}
-
-% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
-\ref{fig_theory_50_50}.
-In Subfig.
-\ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
-In the mean time, the theory calculation results in Subfig.
-\ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$).
-SubFig.
-\ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism.
-Meanwhile, the SubFig.
-\ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers.
-The advantage is not significant.
-So, we increase the data size and the dimension in next case to have a further study.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
-\ref{fig_theory_20_20_20_20}.
-Subfig.
-\ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously.
-Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
-The advantage in the SubFig.
-\ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig.
-\ref{fig_theory_20_20_20_20}(b).
-So, we change the variance of the observed data set in the next case.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_1_1_1_77}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities.
-This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b).
-In Subfig.
-\ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms.
-Also, in Subfig.
-\ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
-Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.
-
-% From the theory and experimental analysis above, we obtained some conclusions
-% \begin{enumerate}
-% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
-
-% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
-
-% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
-% \end{enumerate}
+\section{Preliminary Experimental Results}
+\label{sec_experiment}
 
 \subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
-\label{subsubsec_vs_variables}
+\label{subsec_vs_variables}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
+\includegraphics[width=0.8\textwidth]{accuracy_vs_mean_1_1}
 \caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
@@
 \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-\label{subsec_vs_prior_variance}
+\label{subsubsec_vs_prior_variance}
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 
-\subsection{Experiment Evaluations on Privacy}
-\label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_smoo} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
-the data size, and obtain plots in Fig.
-\ref{fig_privacy}.
+\section{Conclusions}
+We can obtain some preliminary conclusions: 
+\begin{enumerate}
+	\item We can beat Laplace mechanism when data size is small.
+	\item We will beat Laplace mechanism when observed data are more uniformly.
+  \item When prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
+\end{enumerate}
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20.eps}}
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20(2).eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
-\label{fig_privacy}
-\end{center}
-\end{figure*}
-
-$\epsilon = 0.8$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
-That is to say, we achieved a higher privacy level than expected.
-In next step, we are going to improve the accuracy using this property.
+In consequence, we have a better accuracy in small data size, in larger prior and in uniformly data.
 

### 2018-07-08 main-sketch.tex
updates

--- 2018-07-08 main.tex
@@
 
+Then we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.
+When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance.
+We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
+
 \section{Baseline Approach - Laplace Mechanism}
@@
 Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$.
-The private posterior then will be $\dirichlet(\alpha_1 + n_1 + , \alpha_2 + n_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
+The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
+\includegraphics[width=0.8\textwidth]{accuracy_vs_dimension}
 \caption{Accuracy measurement based on Hellinger distance wrt.
@@
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
+\includegraphics[width=0.8\textwidth]{accuracy_vs_prior_5_5_5}
 \caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
@@
 \centering
-\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\includegraphics[width=0.8\textwidth]{Accuracy_VS_Prior_mean.eps}
+\caption{Accuracy measurement based on Hellinger distance wrt.
+different prior distribution and data variances.
+Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
 \label{fig_vs_prior_variance}

### 2018-07-08 main-sketch.tex
use ccs template

@@
+\documentclass[sigconf, anonymous]{acmart}
+
+\fancyhf{} % Remove fancy page headers 
+\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
+\fancyfoot[C]{\thepage}
+
+\setcopyright{none} % No copyright notice required for submissions
+\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
+\acmYear{2017}
+
+\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
+
+%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
 \input{macros}
 
-\title{\textbf{Notes of DP - Bayesian Inference}\\}
-% \author{Jiawen \textsc{Liu}}
-\date{\vspace{-10ex}}
+\begin{document}
+\title{Template for ACM CCS 2017} % TODO: replace with your title
 
-\begin{document}
+\begin{abstract}
+Your abstract should go here. You will also need to upload a plain-text abstract into the web submission form.
+\end{abstract}
+
+% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10002978.10003029.10011703</concept_id>
+<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
+% -- end of section to replace with generated code
+
+\keywords{template; formatting; pickling} % TODO: replace with your keywords
+
 \maketitle
+
+% \input{main-sketch} % TODO: replace with your brilliant paper!
+% \input{macros}
 
@@
 
-\subsection{Algorithm Setting up}
+% \subsection{Algorithm Setting up}
 We define a new mechanism $\hexpmech(x)$
@@
 
-\subsection{Sliding Property of Exponential Mechanism}
-\begin{lem}
-Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
-calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
-\begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-\leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
-\end{equation*}
+% \subsection{Sliding Property of Exponential Mechanism}
+% \begin{lem}
+% Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
+% calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
+% \delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
+% \begin{equation*}
+% \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
+% \leq
+% e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+% \end{equation*}
 
-\end{lem}
+% \end{lem}
 
-\begin{proof}
+% \begin{proof}
 
-We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
-\begin{equation*}
-\begin{split}
-LHS 
-  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
-\end{split}
-\end{equation*}
+% We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
+% \begin{equation*}
+% \begin{split}
+% LHS 
+%   = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
+% & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
+% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
+% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
+% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+% \end{split}
+% \end{equation*}
 
-By bounding the $\Delta \geq -S(x)$, we can get:
+% By bounding the $\Delta \geq -S(x)$, we can get:
 
-\begin{equation*}
-\begin{split}
-\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
-\end{split}
-\end{equation*}
+% \begin{equation*}
+% \begin{split}
+% \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
+% & \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
+% &  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+% \end{split}
+% \end{equation*}
 
-\end{proof}
+% \end{proof}
 
-\subsection{Dilation Property of Exponential Mechanism}
-\begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
+% \subsection{Dilation Property of Exponential Mechanism}
+% \begin{lem}
+% for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
 
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
-\leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
-\end{equation*}
-where the sensitivity in mechanism is still smooth sensitivity as above.
-\end{lem}
+% \begin{equation*}
+% \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+% \leq
+% e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
+% \end{equation*}
+% where the sensitivity in mechanism is still smooth sensitivity as above.
+% \end{lem}
 
-\begin{proof}
+% \begin{proof}
 
-The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+% The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
+% We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
 
-We first consider $\lambda < 0$.
+% We first consider $\lambda < 0$.
 In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
 
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
+% Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
 Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
@@
 
-\end{proof}
+% \end{proof}
 
-\subsection{Privacy Analysis}
-\begin{lem}
-\label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
-\end{lem}
+% \subsection{Privacy Analysis}
+% \begin{lem}
+% \label{lem_hexpmech_privacy}
+% $\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
+% \end{lem}
 
-\begin{proof}
-of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
-\end{equation*}
-Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+% \begin{proof}
+% of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
+% \begin{equation*}
+% \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
+% \end{equation*}
+% Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
 Then,
 
-\begin{equation*}
-\begin{split}
-2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
-& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
-& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
-\end{split}
-\end{equation*}
+% \begin{equation*}
+% \begin{split}
+% 2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
+% & = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
+% & \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
+% & \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
+% & = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
+% \end{split}
+% \end{equation*}
 
-The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
+% The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
 The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
 
-\end{proof}
+% \end{proof}
 
@@
 
-\begin{figure*}
+\begin{figure}[ht]
 \begin{center}
@@
   \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
+    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1.eps}}
   \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
+    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
 \caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{accuracy_vs_dimension}
+\includegraphics[width=0.5\textwidth]{accuracy_vs_dimension}
 \caption{Accuracy measurement based on Hellinger distance wrt.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{accuracy_vs_mean_1_1}
+\includegraphics[width=0.5\textwidth]{accuracy_vs_mean_1_1}
 \caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{accuracy_vs_prior_5_5_5}
+\includegraphics[width=0.5\textwidth]{accuracy_vs_prior_5_5_5}
 \caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{Accuracy_VS_Prior_mean.eps}
+\includegraphics[width=0.5\textwidth]{Accuracy_VS_Prior_mean.eps}
 \caption{Accuracy measurement based on Hellinger distance wrt.
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{bayesian.bib}

### 2018-07-08 main-sketch.tex
fix plots 1

@@
 \begin{document}
-\title{Template for ACM CCS 2017} % TODO: replace with your title
+\title{Sketch of DP - Bayesian Inference} % TODO: replace with your title
 
@@
 
-\keywords{template; formatting; pickling} % TODO: replace with your keywords
+\keywords{differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
 
@@
   \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1.eps}}
+    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
   \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
+    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
+\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$}
 \label{fig_vs_datasize}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{accuracy_vs_dimension}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension}
 \caption{Accuracy measurement based on Hellinger distance wrt.
 different dimensions and data size.
-Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
 \label{fig_vs_dimension}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{accuracy_vs_mean_1_1}
-\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1}
+\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
 \label{fig_vs_variance}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{accuracy_vs_prior_5_5_5}
-\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
+\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data set is: $[5,5,5]$}
 \label{fig_vs_prior}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Accuracy_VS_Prior_mean.eps}
+\includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
 \caption{Accuracy measurement based on Hellinger distance wrt.
 different prior distribution and data variances.
-Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
+Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
 \label{fig_vs_prior_variance}

### 2018-07-08 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py

@@ -873,14 +873,15 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,mean):
 		xlabel.append(str(observation) + "/ExpMech")
 		xlabel.append(str(observation) + "/Laplace")
 
-	plt.figure(figsize=(15,12))
+	plt.figure(figsize=(12,10))
 	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', vert=2, whis=1.5,patch_artist=True)
-	plt.xlabel("different datasize")
-	plt.ylabel('Accuracy / Hellinegr Distance')
+	plt.xlabel("different datasize",fontsize=15)
+	plt.ylabel('Accuracy / Hellinegr Distance',fontsize=15)
 	#ax.set_xlim(0.5, len(errors) + 0.5)
 
-	plt.xticks(range(1, len(data)+1),xlabel,rotation=70)
-	plt.title('Accuracy / prior: ' + str(prior._alphas) + ", delta: " + str(delta) + ", epsilon:" + str(epsilon) +  ', mean:' + str(mean))
+	plt.xticks(range(1, len(data)+1),xlabel,rotation=70,fontsize=12)
+	plt.title("Accuracy VS. Data Size",fontsize=20)
+	print('Accuracy / prior: ' + str(prior._alphas) + ", delta: " + str(delta) + ", epsilon:" + str(epsilon) +  ', mean:' + str(mean))
 	for i in range(1, len(bplot["boxes"])/2 + 1):
 		box = bplot["boxes"][2 * (i - 1)]
 		box.set(color='navy', linewidth=1.5)
@@ -907,12 +908,13 @@ def accuracy_VS_prior(sample_size,epsilon,delta,priors,observation,mean):
 
 	plt.figure(figsize=(18,10))
 	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', vert=2, whis=1.5,patch_artist=True)
-	plt.xlabel("different prior distributions")
-	plt.ylabel('Accuracy / Hellinegr Distance')
+	plt.xlabel("different prior distributions",fontsize=15)
+	plt.ylabel('Accuracy / Hellinegr Distance',fontsize=15)
 	#ax.set_xlim(0.5, len(errors) + 0.5)
 
-	plt.xticks(range(1, len(data)+1),xlabel,rotation=70)
[…]

### 2018-07-08 main-sketch.tex
update abstract

@@
 \begin{abstract}
-Your abstract should go here. You will also need to upload a plain-text abstract into the web submission form.
+Differential privacy mechanisms now are widely used in different algorithms.
+Accuracy of these mechanisms is usually measured by $l_1$ norm regardless what mechanisms are based on.
+We observed that when mechanism protect privacy according to a certain measurement, mechanism' accuracy behavior will be better than when protect according to other measurements.
+This observation prompt us to design a new mechanism under Hellinger distance measurement based on basic exponential named exponential mechanism with smooth sensitivity.
+In this algorithm we add noise to data according to the Hellinger distance.
+We proved in experiments that we can have a better accuracy than Laplace mechanism which adding noise based on $l_1$ norm under Hellinger measurement.
 \end{abstract}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
 \caption{Accuracy measurement based on Hellinger distance wrt.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
 \caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
@@
 
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-\label{subsubsec_vs_prior_variance}
+% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
+% \label{subsubsec_vs_prior_variance}
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
-\caption{Accuracy measurement based on Hellinger distance wrt.
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
+% \caption{Accuracy measurement based on Hellinger distance wrt.
 different prior distribution and data variances.
 Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
-\label{fig_vs_prior_variance}
-\end{figure}
+% \label{fig_vs_prior_variance}
+% \end{figure}
 
-Here, we change the prior distribution and data variance in the same time.
+% Here, we change the prior distribution and data variance in the same time.
 As shown in Fig.

### 2018-07-08 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py

@@ -1037,17 +1037,17 @@ def accuracy_VS_prior_mean(sample_size,epsilon,delta,priors,observations):
 
 if __name__ == "__main__":
 
-	sample_size = 8
+	sample_size = 12
 	epsilon = 0.8
-	delta = 0.00001
-	prior = Dir([1,1])
+	delta = 0.00000001
+	prior = Dir([1,1,1])
 	x1 = [1,19]
 	x2 = [2,18]
 	observation = [5,5,5]
 	epsilons = numpy.arange(0.1, 2, 0.1)
 	sample_sizes = [i for i in range(1,5)]#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
-	observations =[[10,10,10],[1,1,28]]
-	priors = [Dir([4*i,4*i,4*i]) for i in range(5,15)]
+	observations =[[4,4,4],[0,0,12]]
+	priors = [Dir([4*i,4*i,4*i]) for i in range(5,20)]
 	mean = [int(1.0/len(prior._alphas) * 100)/100.0 for i in range(len(prior._alphas))]
 	# accuracy_VS_dimension(sample_sizes, epsilon, delta)
 	accuracy_VS_prior_mean(sample_size,epsilon,delta,priors,observations)

### 2018-07-14 main-sketch.tex
section 2 updates

@@
 
-Our study based on the Bernoulli-Beta Bayesian inference.
-In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$.
-Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$.
-The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
+We are studying the Bayesian inference in Beta-Bernoulli systems.
+So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems.
+Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$.
+By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
 \begin{equation*}
-Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
+Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
 \end{equation*}
-It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$.
+denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$.
 For conciseness, when prior is given, we use $\bysinfer(x)$.
@@
 
-In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, where $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$.
-$m$ is the order of the Dirichlet distribution.
+In Beta-Bernoulli systems, we take a Beta distribution as prior belief for our parameters and latent variables, $\betad(\alpha, \beta)$, where $\pi(\xi) = \betad(\xi | \alpha, \beta) = \frac{\xi^{\alpha} (1 - \xi)^{\beta}}{B(\alphas)}$, and the Bernoulli distribution as the likelihood for $Pr(\textbf{x} | \xi) = \xi^{\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}}(1 - \xi)^{n -\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}} $.
+%We are throwing an irregular coin with side $A$ and side $B$.
+The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.
 
-We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice.
+This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$).
+$\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i}\xi_i^{\sum\limits_{\mathrm{x_i} = x_i} \mathrm{x_i}}$.
+
+% We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice.
 We want to infer the probability of getting each side $\xis$.
@@
 
-In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
+% In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
 The $m$ side dice change into a irregular coin with side $A$ and side $B$.
@@
 
-Then we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.
+The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.
+we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.
 When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance.

### 2018-07-14 main-sketch.tex
update section 2

@@
 We are studying the Bayesian inference in Beta-Bernoulli systems.
-So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems.
+So this part we will technically describe our problem under Beta-Bernoulli systems of Bayesian inference.
 Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$.
@@
 
-The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.
+The posterior belief about parameters $\xis$ is inferred from the group of sensitive data.
+Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data.
+So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.
 we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.

### 2018-07-14 main-sketch.tex
update section2

@@
 So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.
-we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.
-When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance.
-We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
+Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper.
+When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance.
+However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}.
+That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
 

### 2018-07-14 main-sketch.tex
update section2

@@
 This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$).
-$\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i}\xi_i^{\sum\limits_{\mathrm{x_i} = x_i} \mathrm{x_i}}$.
+$\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i \in \xis}\xi_i^{\sum\limits_{\{\mathrm{x}_i|\mathrm{x}_i = x_i\}} \mathrm{x_i}}$.
 
@@
 The posterior belief about parameters $\xis$ is inferred from the group of sensitive data.
-Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data.
+Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data.
 So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.
@@
 % \subsection{Algorithm Setting up}
-We define a new mechanism $\hexpmech(x)$
-which is similar to the exponential mechanism where we use
-$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
-summing up to $n+2$, as scoring function we use the Hellinger distance
-from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
-calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
-only difference is in the sensitivity part, since now we use the
-smooth sensitivity.
+We define a new mechanism $\hexpmech(x)$ which is similar to the exponential mechanism where we use $\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters summing up to $n+2$, as scoring function we use the Hellinger distance from $\bysinfer(x)$, i.e.
+$\hlg(\bysinfer(x),-)$, and we calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}.
+The only difference is in the sensitivity part, since now we use the smooth sensitivity.
 

### 2018-07-14 main-sketch.tex
update bib

@@
 Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data.
-So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.
-Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper.
+So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it\cite{foulds2016theory}.
+Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over just parameters or values when we are protecting a distribution, for instance, Hellinger distance in our paper.
 When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance.

### 2018-07-14 main-sketch.tex
abstract

--- 2018-07-14 main-sketch.tex
@@
 \begin{abstract}
-Differential privacy mechanisms now are widely used in different algorithms.
-Accuracy of these mechanisms is usually measured by $l_1$ norm regardless what mechanisms are based on.
-We observed that when mechanism protect privacy according to a certain measurement, mechanism' accuracy behavior will be better than when protect according to other measurements.
-This observation prompt us to design a new mechanism under Hellinger distance measurement based on basic exponential named exponential mechanism with smooth sensitivity.
-In this algorithm we add noise to data according to the Hellinger distance.
-We proved in experiments that we can have a better accuracy than Laplace mechanism which adding noise based on $l_1$ norm under Hellinger measurement.
+
+  Bayesian inference is a statistical method which allows to derive
+  a \emph{posterior} distribution over a parameter, 
+  starting from a \emph{prior} distribution and observed data.
+  Many works have focused on making this
+  process differentially private adding noise on the parameters
+  representing the distributions\todo{cite?}.
+  % Also,  the sensitivity 
+  % was computed w.r.t. a numeric norm over the space of the numeric parameters
+  % characterizing the output distribution.
+  Also, the accuracy was measured
+  using metrics on the space of the numeric parameters representing the
+  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.
+
+  We designed a new mechanism for differentially private Bayesian inference
+  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
+  on probability distributions; we also measured the accuracy of the process
+  by using a metric over probability measures.
+  We compared the accuracy of this approach with the one based on $\ell_1$-norms.
+  Experimental results show that in some situations the former outperforms the latter.
+
 \end{abstract}
@@
 We are studying the Bayesian inference in Beta-Bernoulli systems.
-So this part we will technically describe our problem under Beta-Bernoulli systems of Bayesian inference.
+So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems.
 Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$.
@@
 
-The posterior belief about parameters $\xis$ is inferred from the group of sensitive data.
-Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data.
-So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.
-Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper.
-When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance.
-However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}.
-That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
+The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.
+we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$.
+When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance.
+We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
 

### 2018-07-14 main-sketch.tex
updates bib

@@
   process differentially private adding noise on the parameters
-  representing the distributions\todo{cite?}.
+  representing the distributions\cite{zhang2016differential}.
   % Also,  the sensitivity 
@@
   using metrics on the space of the numeric parameters representing the
-  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.
+  posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory}.
 

### 2018-07-14 main-sketch.tex
update bib
abstract second pass

--- 2018-07-14 main-sketch.tex
@@
 \begin{abstract}
+  Bayesian inference is a statistical method which allows to derive a
+\emph{posterior} distribution over a parameter, starting from a
+\emph{prior} distribution and observed data.  Many works have focused
+on making this process differentially private adding noise on the
+parameters representing the distributions\todo{cite?}.  Also, the
+accuracy was measured using metrics on  the numeric
+parameters representing the posterior distribution, e.g. $\ell_1$-norm
+\todo{cite?}.
 
-  Bayesian inference is a statistical method which allows to derive
-  a \emph{posterior} distribution over a parameter, 
-  starting from a \emph{prior} distribution and observed data.
-  Many works have focused on making this
-  process differentially private adding noise on the parameters
-  representing the distributions\todo{cite?}.
-  % Also,  the sensitivity 
-  % was computed w.r.t. a numeric norm over the space of the numeric parameters
-  % characterizing the output distribution.
-  Also, the accuracy was measured
-  using metrics on the space of the numeric parameters representing the
-  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.
-
-  We designed a new mechanism for differentially private Bayesian inference
-  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
-  on probability distributions; we also measured the accuracy of the process
-  by using a metric over probability measures.
-  We compared the accuracy of this approach with the one based on $\ell_1$-norms.
-  Experimental results show that in some situations the former outperforms the latter.
+In this work we present a new mechanism for differentially private Bayesian
+inference where the noise is added w.r.t  a smooth
+sensitivity computed with a metric on probability distributions.
+We also measure the accuracy of the process by using a metric over
+probability measures.  We compared the accuracy of this approach with
+the one based on the $\ell_1$-norm.  We present experimental results
+showing that the former outperforms the latter.
 
@@
 When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance.
-However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}.
+However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential} \cite{xiao2012bayesian}.
 That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.

### 2018-07-14 main-sketch.tex
prefer this word

@@
 In this work we present a new mechanism for differentially private Bayesian
-inference where the noise is added w.r.t  a smooth
+inference where the noise is calibrated w.r.t  a smooth
 sensitivity computed with a metric on probability distributions.

### 2018-07-14 main-sketch.tex
update abstracts

--- 2018-07-14 main-sketch.tex
@@
 \begin{abstract}
-
-  Bayesian inference is a statistical method which allows to derive
-  a \emph{posterior} distribution over a parameter, 
-  starting from a \emph{prior} distribution and observed data.
-  Many works have focused on making this
-  process differentially private adding noise on the parameters
-  representing the distributions\cite{zhang2016differential}.
+Bayesian inference is a statistical method which allows to derive a \emph{posterior} distribution over a parameter, starting from a \emph{prior} distribution and observed data.
+Even the posterior sampling is differentially private itself under some conditions \cite{wang2015privacy,dimitrakakis2014robust}, it can still leak sensitive information of observed data when we release the posterior distribution directly rather than just a sample from it.
+Many works have focused on making this process differentially private by adding noise on the parameters representing the distributions.
   % Also,  the sensitivity 
@@
   % characterizing the output distribution.
-  Also, the accuracy was measured
-  using metrics on the space of the numeric parameters representing the
-  posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory}.
+Also, the accuracy was measured using metrics on the space of the numeric parameters representing the posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory, zhang2016differential}.
 
-  We designed a new mechanism for differentially private Bayesian inference
-  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
-  on probability distributions; we also measured the accuracy of the process
-  by using a metric over probability measures.
+We designed a new mechanism for differentially private Bayesian inference where the noise is proportional to a smooth sensitivity computed w.r.t a metric on probability distributions; we also measured the accuracy of the process by using a metric over probability measures.
+We protect the whole Bayesian inference process with the posterior distribution.
 We compared the accuracy of this approach with the one based on $\ell_1$-norms.

### 2018-07-15 main-sketch.tex
abstract 3rd pass

--- 2018-07-14 main-sketch.tex
@@
 \emph{posterior} distribution over a parameter, starting from a
-\emph{prior} distribution and observed data.  Many works have focused
-on making this process differentially private adding noise on the
-parameters representing the distributions\todo{cite?}.  Also, the
-accuracy was measured using metrics on  the numeric
-parameters representing the posterior distribution, e.g. $\ell_1$-norm
-\todo{cite?}.
+\emph{prior} distribution and observed data.  In a setting where the
+data must be protected, different approaches have been taken to make
+this process differentially
+private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy}, for instance,
+proved that, under specific conditions, sampling from the posterior distribution
+is already differentially private.
+Other works, e.g. \cite{zhang2016differential,foulds2016theory}, 
+designed differentially private mechanisms that output a representation of the
+full posterior distribution. Also,  accuracy of the mechanisms was measured
+using metrics on the space of the numeric parameters of the posterior distribution,
+e.g. $\ell_1$-norm .
 
-In this work we present a new mechanism for differentially private Bayesian
-inference where the noise is added w.r.t  a smooth
-sensitivity computed with a metric on probability distributions.
-We also measure the accuracy of the process by using a metric over
-probability measures.  We compared the accuracy of this approach with
-the one based on the $\ell_1$-norm.  We present experimental results
-showing that the former outperforms the latter.
+In this work we present a new differentially private algorithm to compute the posterior.
+The noise is calibrated w.r.t. a smooth sensitivity computed with
+a metric on probability distributions; we measured the accuracy
+of the process by using a metric over probability measures.
+We compared the accuracy of this approach with the one
+based on $\ell_1$-norm. Experimental results show that
+when the data size is small or when the parameters of the prior
+distribution are large, the former outperforms the latter.
 

### 2018-07-15 main-sketch.tex
rewrite section2

@@
 \begin{abstract}
-Bayesian inference is a statistical method which allows to derive a
-\emph{posterior} distribution over a parameter, starting from a
-\emph{prior} distribution and observed data.  In a setting where the
-data must be protected, different approaches have been taken to make
-this process differentially
-private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy}, for instance,
-proved that, under specific conditions, sampling from the posterior distribution
-is already differentially private.
-Other works, e.g. \cite{zhang2016differential,foulds2016theory}, 
-designed differentially private mechanisms that output a representation of the
-full posterior distribution. Also,  accuracy of the mechanisms was measured
-using metrics on the space of the numeric parameters of the posterior distribution,
-e.g. $\ell_1$-norm .
+Bayesian inference is a statistical method which allows to derive a \emph{posterior} distribution over a parameter, starting from a \emph{prior} distribution and observed data.
+In a setting where the data must be protected, different approaches have been taken to make this process differentially private.
+\citet{dimitrakakis2014robust}, and \citet{wang2015privacy}, for instance, proved that, under specific conditions, sampling from the posterior distribution is already differentially private.
+Other works, e.g.
+\cite{zhang2016differential,foulds2016theory}, designed differentially private mechanisms that output a representation of the full posterior distribution.
+Also,  accuracy of the mechanisms was measured using metrics on the space of the numeric parameters of the posterior distribution, e.g.
+$\ell_1$-norm .
 
 In this work we present a new differentially private algorithm to compute the posterior.
-The noise is calibrated w.r.t. a smooth sensitivity computed with
-a metric on probability distributions; we measured the accuracy
-of the process by using a metric over probability measures.
-We compared the accuracy of this approach with the one
-based on $\ell_1$-norm. Experimental results show that
-when the data size is small or when the parameters of the prior
-distribution are large, the former outperforms the latter.
+The noise is calibrated w.r.t.
+a smooth sensitivity computed with a metric on probability distributions; we measured the accuracy of the process by using a metric over probability measures.
+We compared the accuracy of this approach with the one based on $\ell_1$-norm.
+Experimental results show that when the data size is small or when the parameters of the prior distribution are large, the former outperforms the latter.
 
@@
 \section{Problem Statement}
-Our research is based on an observation that under different measurement, mechanisms usually have different accuracy behavior.
-When adding noise according to a certain measurement, mechanism' accuracy behavior will be better than when adding noise according to other measurements.
-Here we study the private Bayesian inference based on Hellinger distance measurement.
-Showing that our newly-designed mechanism adding noise according to Hellinger distance performs better than baseline mechanism adding noise according to $l_1$ norm.
+The posterior belief from Bayesian inference is usually represented by a probabilistic distribution like $\betad(\alpha, \beta)$.
+When we try to make this distribution public, sensitive information of the data based on which the posterior drew from can be compromised.
+So, it is important to protect this posterior distribution.
+When our protection objective is a distribution rather than a numeric value or vector, it would be better to measure the accuracy by distance over distributions, for instance, Hellinger distance, than by numeric metrics like $\ell_1$-norm.
+Our research is based on the observation that under metrics over distribution, mechanisms usually have different behavior from under metrics over numeric values.
+If we measure accuracy based on distribution metrics, then mechanisms adding noise according to distribution measurements can out-performs mechanisms' adding noise according to numeric measurements.
 

### 2018-07-16 main-sketch.tex
introduction to bayesian things

--- 2018-07-15 main-sketch.tex
@@
 data must be protected, different approaches have been taken to make
-this process differentially
-private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy}, for instance,
-proved that, under specific conditions, sampling from the posterior distribution
-is already differentially private.
-Other works, e.g. \cite{zhang2016differential,foulds2016theory}, 
-designed differentially private mechanisms that output a representation of the
-full posterior distribution. Also,  accuracy of the mechanisms was measured
-using metrics on the space of the numeric parameters of the posterior distribution,
-e.g. $\ell_1$-norm .
+this process differentially private. \citet{dimitrakakis2014robust},
+and \citet{wang2015privacy}, for instance, proved that, under specific
+conditions, sampling from the posterior distribution is already
+differentially private. Other works,
+e.g. \cite{zhang2016differential,foulds2016theory}, designed
+differentially private mechanisms that output a representation of the
+full posterior distribution. Also, accuracy of the mechanisms was
+measured using metrics on the space of the numeric parameters of the
+posterior distribution, e.g. $\ell_1$-norm .
 
-In this work we present a new differentially private algorithm to compute the posterior.
-The noise is calibrated w.r.t. a smooth sensitivity computed with
-a metric on probability distributions; we measured the accuracy
-of the process by using a metric over probability measures.
-We compared the accuracy of this approach with the one
-based on $\ell_1$-norm. Experimental results show that
-when the data size is small or when the parameters of the prior
+In this work we present a new differentially private algorithm to
+compute the posterior in a Beta-Binomial system and in Dirichlet-Multinomial system.
+The noise is calibrated w.r.t. a smooth
+sensitivity computed with a metric on probability distributions; we
+measured the accuracy of the process by using a metric over
+probability measures. We compared the accuracy of this approach with
+the one based on $\ell_1$-norm. Experimental results show that when
+the data size is small or when the parameters of the prior
 distribution are large, the former outperforms the latter.
@@
 
+\section{Bayesian Inference Background}
+Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
+and given an observation $\dataobs$,
+the posterior distribution on $\theta$ given $\dataobs$ is computed as:
+\[
+  \Pr(\theta | \dataobs) = \frac{Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}
+\]
+where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
+\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.
+For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
+Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
+the initial belief on $\theta$. That is, when no data has been observed. In practice though,
+prior distributions and likelihood functions are usually chosen so that the posterior
+belongs to the same \emph{family} of distributions. In this case we say that the prior
+is conjugate of the likelihood function. Using conjugate priors simplify calculcations and allows
+for inference to be performed in a recursive fashion over the data.
+In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
+Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias})--
+of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
+the the vector of parameters of a categorical distributed random variable.
+In the former case the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
+$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+\[
+  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
+\]
+where $\betaf(\cdot,\cdot)$ is the beta function.
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ 0/1 values, that is $\dataobs=\ll x_1,\dots x_n \gg, x_i\in\{0,1\}$, and the likelihood function is:
+\[
+  \Pr(\dataobs | \theta)\equiv \theta^{a}(1-\theta)^{n-a}
+\]
+where $a=\displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
+From this it can easily be derived that the posterior distribution is:
+\[
+  \Pr(\theta|\dataobs)=\betad(\alpha+a,\beta+n-a)
+\]
+In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbf{N}$,
+and $\valpha\in(\mathbf{R^{+}})^{k}$, with p.d.f:
+\[
+  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
+\]
+where $\mbetaf(\cdot)$ is the generealised beta function.
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
+The likelihood function will be:
+\[
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
+\todo{to check}\]
+where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use
+Iverson bracket notation. The posterior distribution over $\vtheta$ turns out to be
+\[
+  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)
+\]
 \section{Problem Statement}
-Our research is based on an observation that under different measurement, mechanisms usually have different accuracy behavior.
-When adding noise according to a certain measurement, mechanism' accuracy behavior will be better than when adding noise according to other measurements.
-Here we study the private Bayesian inference based on Hellinger distance measurement.
-Showing that our newly-designed mechanism adding noise according to Hellinger distance performs better than baseline mechanism adding noise according to $l_1$ norm.
-
+% When we try
+% to make this distribution public, sensitive information of the data
+% based on which the posterior drew from can be compromised. So, it is
+% important to protect this posterior distribution. When our protection
+% objective is a distribution rather than a numeric value or vector, it
+% would be better to measure the accuracy by distance over
+% distributions, for instance, Hellinger distance, than by numeric
+% metrics like $\ell_1$-norm.
+This work will show that the same mechanism can
+perform differently when its accuracy is computed w.r.t to a metric
+over probability measures (e.g total variation distance, or Hellinger distance)
+from when the metric (e.g. $\ell_1$-norm) is over the parameters.  
 \section{Technical Problem Statement}
 \label{sec_bayesInfer}
-
-We are studying the Bayesian inference in Beta-Bernoulli systems.
-So this part we will technically describe our problem under Beta-Bernoulli systems of Bayesian inference.
-Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$.
-By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
-\begin{equation*}
-Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
-\end{equation*}
-denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$.
-For conciseness, when prior is given, we use $\bysinfer(x)$.
-$n$ is the size of the observed data size.
-
-In Beta-Bernoulli systems, we take a Beta distribution as prior belief for our parameters and latent variables, $\betad(\alpha, \beta)$, where $\pi(\xi) = \betad(\xi | \alpha, \beta) = \frac{\xi^{\alpha} (1 - \xi)^{\beta}}{B(\alphas)}$, and the Bernoulli distribution as the likelihood for $Pr(\textbf{x} | \xi) = \xi^{\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}}(1 - \xi)^{n -\sum\limits_{\mathrm{x_i} \in \textbf{x}}\mathrm{x_i}} $.
-%We are throwing an irregular coin with side $A$ and side $B$.
-The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.
-
-This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$).
-$\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i \in \xis}\xi_i^{\sum\limits_{\{\mathrm{x}_i|\mathrm{x}_i = x_i\}} \mathrm{x_i}}$.
-
-% We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice.
-We want to infer the probability of getting each side $\xis$.
-We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time.
-The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.
-
-% In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
-The $m$ side dice change into a irregular coin with side $A$ and side $B$.
-The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.
-
-The posterior belief about parameters $\xis$ is inferred from the group of sensitive data.
-Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data.
-So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it\cite{foulds2016theory}.
-Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over just parameters or values when we are protecting a distribution, for instance, Hellinger distance in our paper.
-When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance.
-However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential} \cite{xiao2012bayesian}.
-That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
+The posterior belief about parameters $\xis$ is inferred from the
+group of sensitive data. Because it is usually published in form of a
+distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
+can relieve a lot of information about sensitive data. So, the
+sensitive information we want to protect here is the posterior belief,
+i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
+it\cite{foulds2016theory}. Then it will be better if we can use a
+distance over two distributions to measure the accuracy than a
+distance over just parameters or values when we are protecting a
+distribution, for instance, Hellinger distance in our paper. When we
+measure the accuracy between true posterior and protected posterior
+using Hellinger distance, it would be better we can have a protection
+mechanism based on Hellinger distance. However, current mechanisms are
+mainly based on $l_1$ norm by Laplace mechanism
+\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
+design our exponential mechanism over Hellinger distance to protect
+the whole posterior distribution.
 

### 2018-07-16 main-sketch.tex
typo
fix typos

@@
 \[
-  \Pr(\theta | \dataobs) = \frac{Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}
+  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
 \]
 where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
-\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.
+$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.
 For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
@@
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias})--
+Specifically, we will consider the situation where $\theta$ represents the parameter --(informally called \emph{bias})--
 of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
@@
   \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
-\todo{to check}\]
+\]
 where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use
@@
 \[
-  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)
+  \Pr(\vtheta|\dataobs)=\dirichlet(\vtheta+\mathbf{z})
 \]

### 2018-07-16 main-sketch.tex
update baseline approach

@@
 \label{sec_lap}
-Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism.
-In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
-Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$.
-The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
+Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
+They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors.
+Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
+Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
+%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
+The private posterior then will be $\dirichlet(\alpha_1 + z_1 + Lap_1, \alpha_2 + z_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
 

### 2018-07-16 main-sketch.tex
fix expression in section 1

@@
 \[
-  \Pr(\dataobs | \theta)\equiv \theta^{a}(1-\theta)^{n-a}
+  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
 \]
-where $a=\displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
+where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
 From this it can easily be derived that the posterior distribution is:
 \[
-  \Pr(\theta|\dataobs)=\betad(\alpha+a,\beta+n-a)
+  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
 \]
@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
 \]
-where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use
+where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use
 Iverson bracket notation. The posterior distribution over $\vtheta$ turns out to be
 \[
-  \Pr(\vtheta|\dataobs)=\dirichlet(\vtheta+\mathbf{z})
+  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)
 \]
@@
 %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
-The private posterior then will be $\dirichlet(\alpha_1 + z_1 + Lap_1, \alpha_2 + z_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
+The private posterior then will be $\dirichlet(\alpha_1 + \Delta \alpha_1 + Lap_1, \alpha_2 + \Delta \alpha_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
 

### 2018-07-16 main-sketch.tex
revise baseline approach

@@
 %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
-The private posterior then will be $\dirichlet(\alpha_1 + \Delta \alpha_1 + Lap_1, \alpha_2 + \Delta \alpha_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
+The private posterior then will be $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
 

### 2018-07-16 main-sketch.tex
revise baseline approach

@@
 Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
-They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors.
-Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
+They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors.
+Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
 Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
 %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
-The private posterior then will be $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
+The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
 

### 2018-07-16 main-sketch.tex
work on section 2

--- 2018-07-16 main-sketch.tex
@@
 \[
-  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}
 \]
 where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
-$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.
+\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.
 For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
@@
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-Specifically, we will consider the situation where $\theta$ represents the parameter --(informally called \emph{bias})--
+Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias}--
 of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
@@
 \[
-  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
+  \Pr(\dataobs | \theta)\equiv \theta^{a}(1-\theta)^{n-a}
 \]
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
+where $a=\displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
 From this it can easily be derived that the posterior distribution is:
 \[
-  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
+  \Pr(\theta|\dataobs)=\betad(\alpha+a,\beta+n-a)
 \]
-In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbf{N}$,
+In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbb{N}$,
 and $\valpha\in(\mathbf{R^{+}})^{k}$, with p.d.f:
@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
-\]
-where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
+\todo{to check}\]
+where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use
 Iverson bracket notation. The posterior distribution over $\vtheta$ turns out to be
 \[
-  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)
+  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)
 \]
-\section{Problem Statement}
-% When we try
-% to make this distribution public, sensitive information of the data
-% based on which the posterior drew from can be compromised. So, it is
-% important to protect this posterior distribution. When our protection
-% objective is a distribution rather than a numeric value or vector, it
-% would be better to measure the accuracy by distance over
-% distributions, for instance, Hellinger distance, than by numeric
-% metrics like $\ell_1$-norm.
-This work will show that the same mechanism can
-perform differently when its accuracy is computed w.r.t to a metric
-over probability measures (e.g total variation distance, or Hellinger distance)
-from when the metric (e.g. $\ell_1$-norm) is over the parameters.  
+\section{The Problem and Baseline approach}
+We are interested in designing a mechanism for privately releasing
+\emph{fully} the posterior distributions derived in section \ref{},
+and not a sample from them.  It's worth noticing that the posterior
+distributions are fully characterized by their parameters, and the
+family (beta, Dirichlet) they belong to.  Hence, in case of the
+Beta-Binomial model we are interested in releasing a private version
+of the pair of parameters $(\alpha',\beta')=(\alpha+a,\beta+n-a)$, and
+in the case of the Dirichlet-Multinomial model we are interested in a
+private version of $\vtheta'=(\vtheta+)$.  \cite{} and \cite{} have
+already attacked this problem and their solution consisted in adding
+independent Laplacian noise to the parameters of the posteriors. That
+is, in the case of the Beta-Binomial system the value released would
+be: $(\tilde\alpha,\tilde\beta)$ where $\tilde\alpha\sim Lap(\alpha+a, \frac{2}{\epsilon})$, and
+$\tilde\beta\sim Lap(\beta+n-a, \frac{2}{\epsilon})$.  Where $Lap(\mu,\nu)$
+denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
+This mechanism is $\epsilon$-differentially private, and the noise is
+calibrated w.r.t to a sensitivity of 2 which is derived by using
+$\ell_1$ norm over the pair of parameters. Indeed, considering two
+adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent iff
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$.} data observations
+$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
+distributions, characterized by the pairs
+$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
+$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
+This argument extends similarly to the Dirichelet-Multinomial system.
+
+\noindent Also, in previous works, the accuracy has been measured again with respect to
+$\ell_1$ norm. That is, an upper bound has been given to
+\[
+  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
+\]
+where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
+In this work we will use a metric based on a different norm to compute the sensitivity
+and provide guarantees on the accuracy. In particular we will consider a metric
+over probability measures and not over the parameters that represent them.
+Specifically, we will use the Hellinger distance, which for two beta distributions
+$\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2)$ is defined as
+\[
+  \hellinger()\equiv\todo{to type down}
+\]
+The same change of metric will be applied to the experimental accuracy guarantees.
 \section{Technical Problem Statement}
@@
 \label{sec_lap}
-Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
-They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors.
-Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
-Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
-%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
-The private posterior then will be $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
+Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism.
+In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
+Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$.
+The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
 

### 2018-07-16 main-sketch.tex
conflicts solved

@@
 \[
-  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}
+  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
 \]
 where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
-\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.
+$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.
 For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
-\todo{to check}\]
-where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
+\]
+where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use
 Iverson bracket notation. The posterior distribution over $\vtheta$ turns out to be
 \[
-  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)
+  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)
 \]
@@
 \noindent Also, in previous works, the accuracy has been measured again with respect to
-$\ell_1$ norm. That is, an upper bound has been given to
+$\ell_1$ norm. That is, an lower bound has been given to
 \[
@@
 \label{sec_lap}
-Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism.
-In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
-Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$.
-The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
+Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
+They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors.
+Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
+Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
+%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
+The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
 

### 2018-07-16 main-sketch.tex
typo

@@
 \]
+where $+$ denotes the 
 \section{The Problem and Baseline approach}
@@
 
-\section{Baseline Approach - Laplace Mechanism}
-\label{sec_lap}
-Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
+% \section{Baseline Approach - Laplace Mechanism}
+% \label{sec_lap}
+% Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy.
 They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors.
@@
 Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
-%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
-The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
+% %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
+% The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
 

### 2018-07-16 main-sketch.tex
typos and function revise

@@
 \section{Bayesian Inference Background}
+\label{sec_background}
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
 \]
@@
 \[
-  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)
+  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha).
 \]
-where $+$ denotes the 
+%where $+$ denotes the
+
 \section{The Problem and Baseline approach}
 We are interested in designing a mechanism for privately releasing
-\emph{fully} the posterior distributions derived in section \ref{},
+\emph{fully} the posterior distributions derived in section \ref{sec_background},
 and not a sample from them.  It's worth noticing that the posterior
@@
 Beta-Binomial model we are interested in releasing a private version
-of the pair of parameters $(\alpha',\beta')=(\alpha+a,\beta+n-a)$, and
+of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
 in the case of the Dirichlet-Multinomial model we are interested in a
-private version of $\vtheta'=(\vtheta+)$.  \cite{} and \cite{} have
+private version of $\valpha'=(\valpha + \Delta \valpha)$.  \cite{} and \cite{} have
 already attacked this problem and their solution consisted in adding
@@
 is, in the case of the Beta-Binomial system the value released would
-be: $(\tilde\alpha,\tilde\beta)$ where $\tilde\alpha\sim Lap(\alpha+a, \frac{2}{\epsilon})$, and
-$\tilde\beta\sim Lap(\beta+n-a, \frac{2}{\epsilon})$.  Where $Lap(\mu,\nu)$
+be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$ with truncating method come from algorithm designed by \citet{zhang2016differential}
+.  Where $Lap(\mu,\nu)$
 denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
@@
 \[
-  \hellinger()\equiv\todo{to type down}
+  \hellinger()\equiv\sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}.
 \]

### 2018-07-16 main-sketch.tex
fix typo

@@
 \]
-In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbb{N}$,
+In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
 and $\valpha\in(\mathbf{R^{+}})^{k}$, with p.d.f:

### 2018-07-17 main-sketch.tex
remvoed a sentence not useful

@@
 \]
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.
+where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
 From this it can easily be derived that the posterior distribution is:
@@
 is, in the case of the Beta-Binomial system the value released would
-be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$ with truncating method come from algorithm designed by \citet{zhang2016differential}
-.  Where $Lap(\mu,\nu)$
+be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
+%with truncating method come from algorithm designed by \citet{zhang2016differential}
+Where $Lap(\mu,\nu)$
 denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
@@
 \noindent Also, in previous works, the accuracy has been measured again with respect to
-$\ell_1$ norm. That is, an lower bound has been given to
+$\ell_1$ norm. That is, a lower bound has been given to
 \[
@@
 Specifically, we will use the Hellinger distance, which for two beta distributions
-$\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2)$ is defined as
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
 \[
-  \hellinger()\equiv\sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}.
+  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
+  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
 \]

### 2018-07-17 main-sketch.tex
red marks

@@
 in the case of the Dirichlet-Multinomial model we are interested in a
-private version of $\valpha'=(\valpha + \Delta \valpha)$.  \cite{} and \cite{} have
+private version of $\valpha'=(\valpha + \Delta \valpha)$. \todo{ \cite{?} and \cite{?}} have
 already attacked this problem and their solution consisted in adding
@@
 The same change of metric will be applied to the experimental accuracy guarantees.
-\section{Technical Problem Statement}
-\label{sec_bayesInfer}
-The posterior belief about parameters $\xis$ is inferred from the
-group of sensitive data. Because it is usually published in form of a
-distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
-can relieve a lot of information about sensitive data. So, the
-sensitive information we want to protect here is the posterior belief,
-i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
-it\cite{foulds2016theory}. Then it will be better if we can use a
-distance over two distributions to measure the accuracy than a
-distance over just parameters or values when we are protecting a
-distribution, for instance, Hellinger distance in our paper. When we
-measure the accuracy between true posterior and protected posterior
-using Hellinger distance, it would be better we can have a protection
-mechanism based on Hellinger distance. However, current mechanisms are
-mainly based on $l_1$ norm by Laplace mechanism
-\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
-design our exponential mechanism over Hellinger distance to protect
-the whole posterior distribution.
+% \section{Technical Problem Statement}
+% \label{sec_bayesInfer}
+% The posterior belief about parameters $\xis$ is inferred from the
+% group of sensitive data. Because it is usually published in form of a
+% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
+% can relieve a lot of information about sensitive data. So, the
+% sensitive information we want to protect here is the posterior belief,
+% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
+% it\cite{foulds2016theory}. Then it will be better if we can use a
+% distance over two distributions to measure the accuracy than a
+% distance over just parameters or values when we are protecting a
+% distribution, for instance, Hellinger distance in our paper. When we
+% measure the accuracy between true posterior and protected posterior
+% using Hellinger distance, it would be better we can have a protection
+% mechanism based on Hellinger distance. However, current mechanisms are
+% mainly based on $l_1$ norm by Laplace mechanism
+% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
+% design our exponential mechanism over Hellinger distance to protect
+% the whole posterior distribution.
 

### 2018-07-17 main-sketch.tex
that was not the definition of hellinger just what it reduces to in case of betas...

@@
 over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance, which for two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$, which for two beta distributions
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is equal to
 \[

### 2018-07-17 main-sketch.tex
typo

--- 2018-07-17 main-sketch.tex
@@
 over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance, which for two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$, which for two beta distributions
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is equal to
 \[
@@
 \label{sec_smoo}
-
+Given a prior distribution $\betad(\alpha, \beta)$, depending on the dataset $\dataobs$, the posterior distribution will be one in the following set:
+$$
 % \subsection{Algorithm Setting up}

### 2018-07-17 main-sketch.tex
section 3 pass

@@
 They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors.
-Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
+% Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d.
 Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way.
@@
 \label{sec_smoo}
-Given a prior distribution $\betad(\alpha, \beta)$, depending on the dataset $\dataobs$, the posterior distribution will be one in the following set:
-$$
-% \subsection{Algorithm Setting up}
-We define a new mechanism $\hexpmech(x)$ which is similar to the exponential mechanism where we use $\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters summing up to $n+2$, as scoring function we use the Hellinger distance from $\bysinfer(x)$, i.e.
-$\hlg(\bysinfer(x),-)$, and we calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}.
-The only difference is in the sensitivity part, since now we use the smooth sensitivity.
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$,
+we define the follwing set:
 
-\begin{definition}
-\label{def_smoo}
-The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
+\[
+  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
+\]
+where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
+Notice that $\betaset$ has $n+2$ elements, and the Bayesian Inference
+process will produce an element from $\betaset$ that we denote by
+$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
+prior,  which from now on we consider fixed and we denote it by $\bprior$.
+
+We can now define the mechanism $\hexpmech$ which,
+given in input a sequence of observations $\dataobs$, and $\epsilon>0, \delta>0$,
+produces an element $r$ in $\betaset$ with probability:
+
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
-{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
-{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_\beta(\dataobs)})}
+{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_{\beta}(\dataobs)})}
 \end{equation*}
-where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
-\begin{equation*}
-S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
-\end{equation*}
-where $d$ is the Hamming distance between two datasets, and $\beta =
-\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
-\end{definition}
+The previous mechanism is very similar to the exponential mechanism as defined in \cite{expmech},  with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
+The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
+-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$, which is :
+\[
+   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\cdot \hellinger(\bysinfer(\dataobs'),-)\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
+ \]
 
+where $d$ is the Hamming distance between two datasets, $\Delta_{l}=????$, and $\gamma =
+\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$, to be determined later.
+\subsection{Analysis of the mechanism}
 In what follows, we will use a correspondence between the probability

### 2018-07-17 main-sketch.tex
section 3 pass
second pass on section 3

@@
 differentially private. Other works,
-e.g. \cite{zhang2016differential,foulds2016theory}, designed
+e.g. \cite{zhang2016differential}, \cite{foulds2016theory}, designed
 differentially private mechanisms that output a representation of the
@@
 \]
-%where $+$ denotes the
+where $+$ denotes the component wise  sum of vectors of reals.
 
@@
 in the case of the Dirichlet-Multinomial model we are interested in a
-private version of $\valpha'=(\valpha + \Delta \valpha)$. \todo{ \cite{?} and \cite{?}} have
+private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
 already attacked this problem and their solution consisted in adding
@@
 is, in the case of the Beta-Binomial system the value released would
-be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
+be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
 %with truncating method come from algorithm designed by \citet{zhang2016differential}
-Where $Lap(\mu,\nu)$
+where $Lap(\mu,\nu)$
 denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
@@
 $\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent iff
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$.} data observations
+adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$ } data observations
 $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_\beta(\dataobs)})}
-{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_{\beta}(\dataobs)})}
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_\beta(\dataobs)})}
+{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_{\beta}(\dataobs)})}
 \end{equation*}
@@
 \[
-   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\cdot \hellinger(\bysinfer(\dataobs'),-)\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
+   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),-)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
  \]
 
-where $d$ is the Hamming distance between two datasets, $\Delta_{l}=????$, and $\gamma =
-\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$, to be determined later.
+ where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
+ of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
+ denotes the local sensitivity at $\dataobs'$ (w.r.t $\ell_1$ norm)
+ of the function
+ \[\hellinger \circ \langle (\bysinfer(\dataobs', \cdot), \bysinfer(\cdot, \cdot)\rangle\]
+ that is:
+ \begin{equation*}
+ \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
+\end{equation*}
+Notice that we maximize also over $r$\todo{need to explain why}.
 \subsection{Analysis of the mechanism}

### 2018-07-17 main-sketch.tex
typo
fix little

@@
 \end{equation*}
-The previous mechanism is very similar to the exponential mechanism as defined in \cite{expmech},  with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
+this mechanism is based on the basic exponential mechanism, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
 The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
@@
 \[
-   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),-)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
+   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
  \]
@@
  of the function
- \[\hellinger \circ \langle (\bysinfer(\dataobs', \cdot), \bysinfer(\cdot, \cdot)\rangle\]
+ \[
+ \hellinger \circ \langle (\bysinfer(\dataobs'), \cdot), (\bysinfer(\cdot),\cdot)\rangle,
+ \]
  that is:
  \begin{equation*}
- \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
+ \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
 \end{equation*}
-Notice that we maximize also over $r$\todo{need to explain why}.
+
 \subsection{Analysis of the mechanism}

### 2018-07-17 main-sketch.tex
added one citation removed one thing

@@
 \end{equation*}
-this mechanism is based on the basic exponential mechanism, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
+this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
 The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
@@
  of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
- denotes the local sensitivity at $\dataobs'$ (w.r.t $\ell_1$ norm)
- of the function
- \[
- \hellinger \circ \langle (\bysinfer(\dataobs'), \cdot), (\bysinfer(\cdot),\cdot)\rangle,
- \]
- that is:
+ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--
+ of the scoring function used in our mechanism, that is:
  \begin{equation*}
- \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
+ \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
 \end{equation*}

### 2018-07-17 main-sketch.tex
rewrite 3.1

@@
 where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
-Notice that $\betaset$ has $n+2$ elements, and the Bayesian Inference
+Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference
 process will produce an element from $\betaset$ that we denote by
@@
  of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
- denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--
- of the scoring function used in our mechanism, that is:
+ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
  \begin{equation*}
@@
 \subsection{Analysis of the mechanism}
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
- $r\in\betaset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\betaset$ we have:
-$$
-\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]\Big )
-$$
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
+% In what follows, we will use a correspondence between the probability
+%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
+%  $r\in\betaset$ and the probability 
+%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
+%  $r\in\betaset$ we have:
+% $$
+% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
+% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+%  \hlg(\bysinfer(x),r)]\Big )
+% $$
+% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
 We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
@@
 
-In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+% In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+
+\begin{theorem}
+The mechanism $\hexpmech$ is $(\epsilon,\delta)-$differential privacy by setting $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, deduced from the proof of privacy.
+\end{theorem}
+
+This mechanism also extends to Dirichlet distribution $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+\[
+\hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
+\]
+and replacing the $\betaset$ with set of Dirichlet distribution candidates of the same dimension under the same settings.
+Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements when extends to Dirichlet distribution.
 

### 2018-07-17 main-sketch.tex
typos

--- 2018-07-17 main-sketch.tex
@@
 measured using metrics on the space of the numeric parameters of the
-posterior distribution, e.g. $\ell_1$-norm .
+posterior distribution, e.g. $\ell_1$-norm.
 
@@
 probability measures. We compared the accuracy of this approach with
-the one based on $\ell_1$-norm. Experimental results show that when
+the ones based on $\ell_1$-norm. Experimental results show that when
 the data size is small or when the parameters of the prior
@@
 where $\betaf(\cdot,\cdot)$ is the beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ 0/1 values, that is $\dataobs=\ll x_1,\dots x_n \gg, x_i\in\{0,1\}$, and the likelihood function is:
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs=\langle x_1,\dots x_n \rangle, x_i\in\{0,1\}$, and the likelihood function is:
 \[
@@
 \]
-where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use
-Iverson bracket notation. The posterior distribution over $\vtheta$ turns out to be
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where in $\iverson{\cdot}$ we use
+Iverson bracket notation. Denoting by $\Delta\valpha$ the vector $\langle  \Delta\alpha_1,\dots \Delta\alpha_k \rangle$ the posterior distribution over $\vtheta$ turns out to be
 \[
@@
 \noindent Also, in previous works, the accuracy has been measured again with respect to
-$\ell_1$ norm. That is, a lower bound has been given to
+$\ell_1$ norm. That is, an upper bound has been given to
 \[
@@
 over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$, which for two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is equal to
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$. Given two beta distributions
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
 \[
-  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
+  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
   \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
@@
 We can now define the mechanism $\hexpmech$ which,
-given in input a sequence of observations $\dataobs$, and $\epsilon>0, \delta>0$,
+given in input a sequence of observations $\dataobs$, $\epsilon>0$ and $\delta>0$,
 produces an element $r$ in $\betaset$ with probability:
@@
 this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
-The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
--- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$, which is :
+The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S_{\beta}(\dataobs)$
+-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
 \[

### 2018-07-17 main-sketch.tex
section 3 finished

@@
 $\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$ } data observations
+adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
 $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_\beta(\dataobs)})}
-{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_{\beta}(\dataobs)})}
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
+{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
 \end{equation*}
 this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
-The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S_{\beta}(\dataobs)$
+The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S(\dataobs)$
 -- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
-\[
-   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
- \]
-
+\begin{equation}
+  \label{eq:smooth}
+   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
+\end{equation}
  where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
@@
 
-\subsection{Analysis of the mechanism}
+This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+\[
+  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
+\]
+and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(x)$ in (\ref{eq:smooth}) will be
+computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
+Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We will denote by
+$\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
 % In what follows, we will use a correspondence between the probability
@@
 % In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$. 
+The following result guarantees that the mechanisms are indeed differentially private.
 
-\begin{theorem}
-The mechanism $\hexpmech$ is $(\epsilon,\delta)-$differential privacy by setting $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, deduced from the proof of privacy.
+\begin{theorem}[Privacy] 
+  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, then both
+  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
 \end{theorem}
-
-This mechanism also extends to Dirichlet distribution $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
-\[
-\hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
-\]
-and replacing the $\betaset$ with set of Dirichlet distribution candidates of the same dimension under the same settings.
-Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements when extends to Dirichlet distribution.
 

### 2018-07-17 main-sketch.tex
section 3 finished

@@
 \]
-and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(x)$ in (\ref{eq:smooth}) will be
+and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(\dataobs)$ in (\ref{eq:smooth}) will be
 computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.

### 2018-07-17 main-sketch.tex
future work

@@
 
-\section{Conclusions}
+\section{Conclusions and Future Works}
 We can obtain some preliminary conclusions: 
@@
 
-In consequence, we have a better accuracy in small data size, in larger prior and in uniformly data.
+In conclusion, this mechanism has better accuracy in small data size, larger prior and uniformly data. But this is not enough for application. We will continue our work in following three directions:
+\begin{enumerate}
+  \item For now, we just have a intuitive impression on the accuracy behavior of our mechanism, not a precise formula or bound on it.
+When we will beat the baseline mechanism and when not?
+How much influence will elements in experiment section have on the accuracy?
+Are there any other important factors we missed?
+These are three problems w.r.t.
+the accuracy we are going to explore next.
+  \item The $(\epsilon, \delta)-$dp is a privacy bound of our exponential mechanism $\hexpmech$ and $\hexpmechd$, but not a tight bound.
+The real privacy in experiments can be smaller than it.
+This means we can improve our accuracy in a way that increase the privacy bound but still achieve $(\epsilon, \delta)-$dp.
+  \item Our main idea is that mechanism based on metric over distribution but not numeric.
+The metric we are using is Hellinger distance here.
+It is worth to explore other distribution distance metric like KL-divergence and so on.
+\end{enumerate}
 

### 2018-07-17 main-sketch.tex
section 4 pass

--- 2018-07-17 main-sketch.tex
@@
 \section{The Problem and Baseline approach}
+\label{sec:base}
 We are interested in designing a mechanism for privately releasing
@@
 This mechanism is $\epsilon$-differentially private, and the noise is
-calibrated w.r.t to a sensitivity of 2 which is derived by using
+calibrated w.r.t. to a sensitivity of 2 which is derived by using
 $\ell_1$ norm over the pair of parameters. Indeed, considering two
@@
 this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
-The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S(\dataobs)$
+The difference is that in this mechanism we don't calibrate the noise w.r.t. to the global sensitivity of the scoring function but w.r.t. to the smooth sensitivity $S(\dataobs)$
 -- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
@@
  of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
- denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
+ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t. $\ell_1$ norm--of the scoring function used in our mechanism, that is:
  \begin{equation*}
@@
 \begin{theorem}[Privacy] 
-  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, then both
+  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, both
   $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
@@
 \label{sec_experiment}
+In this section, we evaluate the accuracy of the mechanisms defined in
+Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
+data variance, prior distribution, and some combinations thereof.
+Every plot is an average over 1000 runs.
 
-\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
-\label{subsec_vs_variables}
-
-In this section, we evaluate the accuracy wrt.
-four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables.
-We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable.
-In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables.
-The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.
-
-\subsubsection{Accuracy Evaluation wrt. Datasize}
+\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
+Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
+independent variables --or a combination thereof.
+The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
+is also drawn to give a rough guide to the significance of difference of medians;
+The whiskers extend from the box to show the range of the data. 
+A blue box in the plots represents the exponential mechanism behaviour,
+while the yellow box next to it represents the performance of a variation of the
+basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
+The variation considered performs a post processing on the released parameters so that they
+are consistent. For instance in the case \todo{more info about the truncation}.
+\subsubsection{Evaluation w.r.t. Datasize}
 \label{subsubsec_vs_datasize}
@@
 
-In Fig.
-\ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing.
-In Fig.
-\ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12.
-Same as in Fig.
-\ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.
+In Fig. \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
+This means that in the Beta-Binomial setting the datasets will be
+half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
+equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
+data size increases, the accuracy of $\hexpemech$ and $\expmechd$
+decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is
+smaller than 12, $\hexpmech$ outperforms the Laplace mechanism but fails to do so
+for bigger datasets. The same happens in as in Fig. \ref{fig_vs_datasize}(b),
+we can beat Laplace mechanism when data size is smaller than 15 and
+fail otherwise.
 

### 2018-07-17 main-sketch.tex
typo
second pass section 4

@@
 \[
-  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
+  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
 \]
@@
 data variance, prior distribution, and some combinations thereof.
-Every plot is an average over 1000 runs.
+Every plot is an average over 1000 runs. In all the experiments we set
+$\epsilon = 0.8$, and $\delta = 0.00000001$.
 
@@
 are consistent. For instance in the case \todo{more info about the truncation}.
-\subsubsection{Evaluation w.r.t. Datasize}
+\paragraph{Increasing data size with balanced datasets}
 \label{subsubsec_vs_datasize}
@@
     \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$}
+\caption{Balanced datasets}
 \label{fig_vs_datasize}
@@
 
-In Fig. \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
+In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
 This means that in the Beta-Binomial setting the datasets will be
 half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
-equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
-data size increases, the accuracy of $\hexpemech$ and $\expmechd$
-decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is
-smaller than 12, $\hexpmech$ outperforms the Laplace mechanism but fails to do so
-for bigger datasets. The same happens in as in Fig. \ref{fig_vs_datasize}(b),
-we can beat Laplace mechanism when data size is smaller than 15 and
-fail otherwise.
+equally split in all the $k=3$ bins. Figure \ref{fig_vs_datasize} shows that  when the
+data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
+decreases. In Figure \ref{fig_vs_datasize}(a), when the data size is
+smaller than 12, $\hexpmech$ can outperform the Laplace mechanism but it fails to do so
+for bigger datasets. The same happens in as in Figure \ref{fig_vs_datasize}(b):
+the Laplace mechanism starts performing better for datasets bigger than 15.
 
-\subsubsection{Accuracy Evaluation wrt. Dimensions}
+\paragraph{Increasing dimensions and data size with balanced dataset}
 \label{subsubsec_vs_dimension}
-
+In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
+different sizes and different dimensions. The plot shows that increasing the number of dimensions have
+a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
+mechanism. Fixing the number of dimensions and increasing the data size shows that
+the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
+In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
+mechanism.
 \begin{figure}[ht]
@@
 \includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
-\caption{Accuracy measurement based on Hellinger distance wrt.
-different dimensions and data size.
-Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
+\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
 \label{fig_vs_dimension}
@@
 
-In Fig.
-\ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions.
-The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism.
-Accuracy of two mechanisms both decrease when dimensions go larger.
-We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase.
-In other words, dimension has little influence on whether we will beat Laplace mechanism.
-
-\subsubsection{Accuracy Evaluation wrt. Data variance}
+\paragraph{Fixed data size and unbalaced datasets}
 \label{subsubsec_vs_variance}
+In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
+of balance of the datasets. We  study this variable only under
+two-dimensions $\betad$ distribution in order to be more concise. The plot shows
+that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
 
@@
 \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
-\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
+\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
 \label{fig_vs_variance}
@@
 
-In Fig.
-\ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means).
-We study this variable under two-dimension $\betad$ distribution in order to be concise.
-It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse.
-We will beat Laplace mechanism when observed data are more uniformly.
-
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
+\paragraph{Fixed dataset varying balanced priors}
 \label{subsubsec_vs_prior}
-
+In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
+We also considered balanced priors with increasing values in their dimensions.
+The plot shows that in the beginning the Laplace mechanism performs better but
+it is outperformed after a while.
 \begin{figure}[ht]
@@
 \includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
-\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data set is: $[5,5,5]$}
+\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
 \label{fig_vs_prior}
 \end{figure}
-
-In Fig.
-\ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig.
-\ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed.
-The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
 
@@
 % Here, we change the prior distribution and data variance in the same time.
-As shown in Fig.
-\ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary.
+As shown in Figure  \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary.
 Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

### 2018-07-17 main-sketch.tex
update intro

--- 2018-07-17 main-sketch.tex
@@
 % \input{macros}
+\section{Introduction}
+\label{sec_intro}
+When we publish a posterior belief inferred from a sensitive data set in form of a
+distribution, itself can relieve a lot of information about data set.
+So, we need to noise the posterior belief in order to protect the data set before release it.
+To be precise, distances over two distributions are used to measure the accuracy rather than distances over just parameters or values when we are noising distributions, for instance, Hellinger distance in our paper.
+Then we have this intuition that when measuring the accuracy between true posterior belief and noised one
+using metrics over distribution (Hellinegr distance), a mechanism based on the same distance can outperforms it based on other distance, $\ell_1$-norm for example.
+However, current mechanisms are mainly based on $l_1$ norm \cite{zhang2016differential,xiao2012bayesian} regardless of the accuracy metric.
+That's why we design our exponential mechanism based on a metric over distribution -- for specific, Hellinger distance.
 
@@
 equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
-data size increases, the accuracy of $\hexpemech$ and $\expmechd$
+data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
 decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is

### 2018-07-18 main-sketch.tex
revise section5

@@
   \item We can beat Laplace mechanism when data size is small.
-  \item We will beat Laplace mechanism when observed data are more uniformly.
+  \item We will beat Laplace mechanism when observed data are more balanced.
   \item When prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
@@
 
-In conclusion, this mechanism has better accuracy in small data size, larger prior and uniformly data. But this is not enough for application. We will continue our work in following three directions:
+In conclusion, our mechanism has better accuracy in small data size, larger prior and balanced data. But this is not enough for application. We will continue our work in following three aspects:
 \begin{enumerate}
   \item For now, we just have a intuitive impression on the accuracy behavior of our mechanism, not a precise formula or bound on it.
-When we will beat the baseline mechanism and when not?
-How much influence will elements in experiment section have on the accuracy?
+When will we beat the baseline mechanism and when will not?
+How much influence will elements in Sec.
+\ref{sec_experiment} have on the accuracy?
 Are there any other important factors we missed?
@@
 This means we can improve our accuracy in a way that increase the privacy bound but still achieve $(\epsilon, \delta)-$dp.
-  \item Our main idea is that mechanism based on metric over distribution but not numeric.
+  \item Our main idea is to have a mechanism based on metric over distribution but not numeric.
 The metric we are using is Hellinger distance here.
-It is worth to explore other distribution distance metric like KL-divergence and so on.
+It is worth to explore other distribution distance metric, for example, KL-divergence.
 \end{enumerate}

### 2018-07-18 main-sketch.tex
intro

@@
 % \input{macros}
-\section{Introduction}
+\section{An informal motivation}
 \label{sec_intro}
-When we publish a posterior belief inferred from a sensitive data set in form of a
-distribution, itself can relieve a lot of information about data set.
-So, we need to noise the posterior belief in order to protect the data set before release it.
-To be precise, distances over two distributions are used to measure the accuracy rather than distances over just parameters or values when we are noising distributions, for instance, Hellinger distance in our paper.
-Then we have this intuition that when measuring the accuracy between true posterior belief and noised one
-using metrics over distribution (Hellinegr distance), a mechanism based on the same distance can outperforms it based on other distance, $\ell_1$-norm for example.
-However, current mechanisms are mainly based on $l_1$ norm \cite{zhang2016differential,xiao2012bayesian} regardless of the accuracy metric.
-That's why we design our exponential mechanism based on a metric over distribution -- for specific, Hellinger distance.
+Publishing the posterior distribution inferred from a sensitive dataset can
+leak information about individuals on the dataset.
+So, we need to noise the posterior belief in order to
+protect the data set before releasing it. The question of how much noise to add
+is usually answered with an $\epsilon$, and a sensitivity value.
+Sensitivity can be computed in many different ways based on which metric space
+is imposed on the output set of the mechanism, and yet in literature (\cite{zhang2016differential,xiao2012bayesian} )
+only metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
+Another approach, which we will explore here, is to impose a metric over probability measures.
+An orthogonal question is that of how to measure the accuracy. Again,
+that can be answered in different ways based on the metric imposed on the output space, and yet again
+only in few works \todo{cite: I Think in one paper Dimitrakakis uses KL divergence to measure accuracy }
+distances over probability measures have been used for these purposes.
+
+The main motivation for this work is to check whether
+an approach based on probability measures can outperform
+in term of accuracy approaches based on metric over
+the numeric parameters of the distributions.
+
+That's why we design a variation of the exponential mechanism basing its scoring function
+on the Hellinger distance, and we also base on the same metric
+the experiments used to measure the accuracy.
 

### 2018-07-18 main-sketch.tex
intro

@@
 
-The main motivation for this work is to check whether
+The question that this work aims at answering is whether
 an approach based on probability measures can outperform
@@
 
-That's why we design a variation of the exponential mechanism basing its scoring function
-on the Hellinger distance, and we also base on the same metric
-the experiments used to measure the accuracy.
-
+We will see that in some cases this can happen.
 \section{Bayesian Inference Background}
@@
 over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$. Given two beta distributions
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
+The choice of Hellinger distance was dictated by two facts, first of all it simplifies
+calculations in the case of the probabilistic models considered here
+and second of all it also provides straightforwardly bounds for
+the total variation distance, which represents also the maximum advantage
+an unbounded adversary can have in distingishing two distributions. 
+Given two beta distributions
 $\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
@@
   \item We can beat Laplace mechanism when data size is small.
-  \item We will beat Laplace mechanism when observed data are more balanced.
-  \item When prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
+  \item We will beat Laplace mechanism when observed data are more
+balanced.
+  \item When prior distribution grow larger, we perform better and
+better and beat Laplace mechanism finally.
 \end{enumerate}
 
-In conclusion, our mechanism has better accuracy in small data size, larger prior and balanced data. But this is not enough for application. We will continue our work in following three aspects:
+In conclusion, our mechanism has better accuracy in small data size,
+larger prior and balanced data. But this is not enough for
+application. We will continue our work in following three aspects:
 \begin{enumerate}
-  \item For now, we just have a intuitive impression on the accuracy behavior of our mechanism, not a precise formula or bound on it.
-When will we beat the baseline mechanism and when will not?
-How much influence will elements in Sec.
-\ref{sec_experiment} have on the accuracy?
-Are there any other important factors we missed?
-These are three problems w.r.t.
-the accuracy we are going to explore next.
-  \item The $(\epsilon, \delta)-$dp is a privacy bound of our exponential mechanism $\hexpmech$ and $\hexpmechd$, but not a tight bound.
-The real privacy in experiments can be smaller than it.
-This means we can improve our accuracy in a way that increase the privacy bound but still achieve $(\epsilon, \delta)-$dp.
-  \item Our main idea is to have a mechanism based on metric over distribution but not numeric.
-The metric we are using is Hellinger distance here.
-It is worth to explore other distribution distance metric, for example, KL-divergence.
+  \item For now, we just have a intuitive impression on the accuracy
+behavior of our mechanism, not a precise formula or bound on it.  When
+will we beat the baseline mechanism and when will not? How much
+influence will elements in Sec. \ref{sec_experiment} have on the
+accuracy? Are there any other important factors we missed? These are
+three problems w.r.t. the accuracy we are going to explore next.
+  \item The $(\epsilon, \delta)-$dp is a privacy bound of our
+exponential mechanism $\hexpmech$ and $\hexpmechd$, but not a tight
+bound. The real privacy in experiments can be smaller than it. This
+means we can improve our accuracy in a way that increase the privacy
+bound but still achieve $(\epsilon, \delta)-$dp.
+  \item Our main idea is to have a mechanism based on metric over
+distribution but not numeric. The metric we are using is Hellinger
+distance here. It is worth to explore other distribution distance
+metric, for example, KL-divergence.
 \end{enumerate}

### 2018-07-18 main-sketch.tex
pass on concnlusions and futre work

@@
 \begin{theorem}[Privacy] 
+\label{thm:privacy}
   For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, both
@@
 \section{Conclusions and Future Works}
-We can obtain some preliminary conclusions:
+From what we have seen in the previous sections 
+we can obtain some preliminary conclusions. That is,
+the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases: 
 \begin{enumerate}
-  \item We can beat Laplace mechanism when data size is small.
-  \item We will beat Laplace mechanism when observed data are more
-balanced.
-  \item When prior distribution grow larger, we perform better and
-better and beat Laplace mechanism finally.
+  \item When the data size is small
+  \item When the observed data is balanced
+  \item When priors parameters increase (eventually).
 \end{enumerate}
 
-In conclusion, our mechanism has better accuracy in small data size,
-larger prior and balanced data. But this is not enough for
-application. We will continue our work in following three aspects:
+These results although very motivating, are still not enough for real world applications.
+Hence, we will continue our work in the follwoing directions:
 \begin{enumerate}
-  \item For now, we just have a intuitive impression on the accuracy
-behavior of our mechanism, not a precise formula or bound on it.  When
-will we beat the baseline mechanism and when will not? How much
-influence will elements in Sec. \ref{sec_experiment} have on the
+  \item For now, we just have a intuitive idea on the accuracy
+    behavior of our mechanisms, and not a precise formula or bound on it.
+    When do our mechanisms perform better than the baseline mechanism and when they don't?
+    How much influence will elements in Section \ref{sec_experiment} have on the
     accuracy? Are there any other important factors we missed? These are
-three problems w.r.t. the accuracy we are going to explore next.
-  \item The $(\epsilon, \delta)-$dp is a privacy bound of our
-exponential mechanism $\hexpmech$ and $\hexpmechd$, but not a tight
-bound. The real privacy in experiments can be smaller than it. This
-means we can improve our accuracy in a way that increase the privacy
-bound but still achieve $(\epsilon, \delta)-$dp.
-  \item Our main idea is to have a mechanism based on metric over
-distribution but not numeric. The metric we are using is Hellinger
-distance here. It is worth to explore other distribution distance
-metric, for example, KL-divergence.
+    all questions w.r.t. the accuracy that we are going to explore next, and in a more
+    principled and formal way.
+\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
+  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
+  Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
+  This means that we could improve accuracy, by adding less noise --
+  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
+\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
+  it is worth exploring other distances over distributions. An interesting class
+  of probability metrics is the family of  $f$-divergences \cite{??}.
 \end{enumerate}

### 2018-07-18 main-sketch.tex
pass on concnlusions and futre work

@@
 \fancyhf{} % Remove fancy page headers 
-\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
+% \fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
 \fancyfoot[C]{\thepage}
@@
 \setcopyright{none} % No copyright notice required for submissions
-\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
-\acmYear{2017}
+% \acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
+% \acmYear{2017}
 
@@
 \begin{document}
-\title{Sketch of DP - Bayesian Inference} % TODO: replace with your title
-
+\title{Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
+\subtitle{Extended Abstract}
 \begin{abstract}
@@
 % TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002978.10003029.10011703</concept_id>
-<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
+% \begin{CCSXML}
+% <ccs2012>
+% <concept>
+% <concept_id>10002978.10003029.10011703</concept_id>
+% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
+% <concept_significance>500</concept_significance>
+% </concept>
+% </ccs2012>
+% \end{CCSXML}
 
-\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-% -- end of section to replace with generated code
+% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
+% % -- end of section to replace with generated code
 
-\keywords{differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
+\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
 
@@
 that can be answered in different ways based on the metric imposed on the output space, and yet again
-only in few works \todo{cite: I Think in one paper Dimitrakakis uses KL divergence to measure accuracy }
+only in few works in literature (e.g. \cite{zhang2016differential})
 distances over probability measures have been used for these purposes.
@@
 the numeric parameters of the distributions. 
-
 We will see that in some cases this can happen.
@@
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
-and given an observation $\dataobs$,
-the posterior distribution on $\theta$ given $\dataobs$ is computed as:
+and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
 \[
@@
   it is worth exploring other distances over distributions. An interesting class
-  of probability metrics is the family of  $f$-divergences \cite{??}.
+  of probability metrics is the family of  $f$-divergences \todo{\cite{??}}.
 \end{enumerate}

### 2018-07-18 main-sketch.tex
final pass
fninish the todo in red

@@
 The variation considered performs a post processing on the released parameters so that they
-are consistent. For instance in the case \todo{more info about the truncation}.
+are consistent. For instance in the case when noise is greater than $n$ we will truncate to $n$ to rule out invalid values.
 \paragraph{Increasing data size with balanced datasets}
@@
   it is worth exploring other distances over distributions. An interesting class
-  of probability metrics is the family of  $f$-divergences \todo{\cite{??}}.
+  of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
 \end{enumerate}

### 2018-07-24 main-fullversion.tex
rename file
fix mistakes
update full version

--- 2018-07-07 main.tex
@@
+\documentclass[sigconf, anonymous]{acmart}
+
+\fancyhf{} % Remove fancy page headers 
+% \fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
+\fancyfoot[C]{\thepage}
+
+\setcopyright{none} % No copyright notice required for submissions
+% \acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
+% \acmYear{2017}
+
+\settopmatter{printacmref=false, printccs=true, printfolios=true}
 \input{macros}
@@
 
-		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:
+		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are shown in Tab.
+\ref{tab_8}
 
 		\begin{center}
+		\begin{table*}
 		 \begin{tabular}{c | c | c} 
@@
 		\end{tabular}
+		\caption{Probability with Prior $\betad(1,1)$ and data size $8$}
+		\label{tab_8}
+		\end{table*}
 		\end{center}
@@
 
-		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$
+		\item keep the prior unchanged, $\betad(1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for $40$ times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$ shown in Tab.
+\ref{tab_40}
 
 		\begin{center}
+		\begin{table*}
 		 \begin{tabular}{c | c | c} 
@@
 		\end{tabular}
+		\caption{Probability with Prior $\betad(1,1)$ and data size $40$}
+		\label{tab_40}
+		\end{table*}
 		\end{center}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=0.5\textwidth]{sensitivity}
+\includegraphics[width=0.48\textwidth]{sensitivity}
 \label{fig_sensitivity}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\textwidth]{efficiency}
+\includegraphics[width=0.48\textwidth]{efficiency}
 \label{fig_efficiency}
@@
   \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
+    \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
+    \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
 \caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
@@
   \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
+    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
   \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
+    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
 \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
@@
   \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
+    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
   \subfigure[accuracy measurement based on $l_1$ norm]{
-    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
+    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
 \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
@@
   \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
+    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
   \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
+    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
+\caption{Balanced datasets}
 \label{fig_vs_datasize}
 \end{center}
-\end{figure*}
+\end{figure}
 
-In Fig.
-\ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing.
-In Fig.
-\ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12.
-Same as in Fig.
-\ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.
+In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
+This means that in the Beta-Binomial setting the datasets will be
+half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
+equally split in all the $k=3$ bins. Figure \ref{fig_vs_datasize} shows that  when the
+data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
+decreases. In Figure \ref{fig_vs_datasize}(a), when the data size is
+smaller than 12, $\hexpmech$ can outperform the Laplace mechanism but it fails to do so
+for bigger datasets. The same happens in as in Figure \ref{fig_vs_datasize}(b):
+the Laplace mechanism starts performing better for datasets bigger than 15.
 
@@
 
-\begin{figure}[h]
+In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
+different sizes and different dimensions. The plot shows that increasing the number of dimensions have
+a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
+mechanism. Fixing the number of dimensions and increasing the data size shows that
+the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
+In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
+mechanism.
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
-\caption{Accuracy measurement based on Hellinger distance wrt.
-different dimensions and data size.
-Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
+\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
 \label{fig_vs_dimension}
 \end{figure}
-
-In Fig.
-\ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions.
-The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism.
-Accuracy of two mechanisms both decrease when dimensions go larger.
-We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase.
-In other words, dimension has little influence on whether we will beat Laplace mechanism.
 
@@
 
-\begin{figure}[h]
+In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
+of balance of the datasets. We  study this variable only under
+two-dimensions $\betad$ distribution in order to be more concise. The plot shows
+that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
+
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
-\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
+\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
 \label{fig_vs_variance}
@@
 
-In Fig.
-\ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means).
-We study this variable under two-dimension $\betad$ distribution in order to be concise.
-It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse.
-We will beat Laplace mechanism when observed data are more uniformly.
-
 \subsubsection{Accuracy Evaluation wrt. Prior Distribution}
 \label{subsubsec_vs_prior}
-
-\begin{figure}[h]
+In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
+We also considered balanced priors with increasing values in their dimensions.
+The plot shows that in the beginning the Laplace mechanism performs better but
+it is outperformed after a while.
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
-\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
+\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
+\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
 \label{fig_vs_prior}
@@
 
-In Fig.
-\ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig.
-\ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed.
-The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.
+% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
+% \label{subsubsec_vs_prior_variance}
 
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-\label{subsubsec_vs_prior_variance}
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean.eps}
+% \caption{Accuracy measurement based on Hellinger distance wrt.
+different prior distribution and data variances.
+Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
+% \label{fig_vs_prior_variance}
+% \end{figure}
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\label{fig_vs_prior_variance}
-\end{figure}
-
-Here, we change the prior distribution and data variance in the same time.
+% Here, we change the prior distribution and data variance in the same time.
 As shown in Fig.
@@
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20.eps}}
+    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20.eps}}
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20(2).eps}} 
+    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20(2).eps}} 
 \caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}

### 2018-07-26 main-sketch.tex
bettered english
fix abstract

@@
-\documentclass[sigconf, anonymous]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 \begin{document}
-\title{Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
+\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}%Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
 \subtitle{Extended Abstract}
 \begin{abstract}
-Bayesian inference is a statistical method which allows to derive a
+Bayesian inference is a statistical method which allows one to derive a
 \emph{posterior} distribution over a parameter, starting from a
-\emph{prior} distribution and observed data.  In a setting where the
-data must be protected, different approaches have been taken to make
+\emph{prior} distribution and observed data.  Settings where sensitive individual information is , different approaches have been taken to make
 this process differentially private. \citet{dimitrakakis2014robust},
@@
 differentially private. Other works,
-e.g. \cite{zhang2016differential}, \cite{foulds2016theory}, designed
+e.g., \cite{zhang2016differential}, \cite{foulds2016theory}, designed
 differentially private mechanisms that output a representation of the
-full posterior distribution. Also, accuracy of the mechanisms was
+full posterior distribution. Also, accuracy of these mechanisms was
 measured using metrics on the space of the numeric parameters of the
-posterior distribution, e.g. $\ell_1$-norm.
+posterior distribution, e.g., the $\ell_1$-norm.
 
 In this work we present a new differentially private algorithm to
-compute the posterior in a Beta-Binomial system and in Dirichlet-Multinomial system.
-The noise is calibrated w.r.t. a smooth
-sensitivity computed with a metric on probability distributions; we
-measured the accuracy of the process by using a metric over
-probability measures. We compared the accuracy of this approach with
-the ones based on $\ell_1$-norm. Experimental results show that when
-the data size is small or when the parameters of the prior
-distribution are large, the former outperforms the latter.
+compute the posterior in a Beta-Binomial system and in a Dirichlet-Multinomial system.
+We apply the exponential mechanism to the smooth sensitivity of a metric on probability distributions; we measured the accuracy of the process by using the same metric.
+We compared the accuracy of this approach with the ones based on $\ell_1$-norm.
+Experimental results show that when the data size is small or when the parameters of the prior distribution are large, the former outperforms the latter.
 
@@
 The variation considered performs a post processing on the released parameters so that they
-are consistent. For instance in the case when noise is greater than $n$ we will truncate to $n$ to rule out invalid values.
+are consistent. For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
 \paragraph{Increasing data size with balanced datasets}

### 2018-07-26 main-sketch.tex
fix sentences marked by Bun

@@
 \subtitle{Extended Abstract}
+
+\author{Gian Pietro Farina}
+\affiliation{%
+  \institution{University at Buffalo, SUNY}
+}
+\email{gianpiet@buffalo.edu}
+
+\author{Jiawen Liu}
+\affiliation{%
+  \institution{University at Buffalo, SUNY}
+}
+\email{jliu223@buffalo.edu}
+
+\author{Marco Gaboardi}
+\affiliation{%
+  \institution{University at Buffalo, SUNY}
+}
+\email{gaboardi@buffalo.edu}
+
+\author{Mark Bun}
+\affiliation{%
+  \institution{Princeton University}
+}
+\email{mbun@cs.princeton.edu}
+
 \begin{abstract}
@@
 leak information about individuals on the dataset.
-So, we need to noise the posterior belief in order to
-protect the data set before releasing it. The question of how much noise to add
-is usually answered with an $\epsilon$, and a sensitivity value.
+Differential privacy enables release of an approximate posterios distribution through the introduction of random noise.
+The amount of the noise that must be introduced depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to small changes in the data set.%So, we need to noise the posterior belief in order to protect the data set before releasing it.
+The question of how much noise to add is usually answered with an $\epsilon$, and a sensitivity value.
 Sensitivity can be computed in many different ways based on which metric space
-is imposed on the output set of the mechanism, and yet in literature (\cite{zhang2016differential,xiao2012bayesian} )
-only metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
-Another approach, which we will explore here, is to impose a metric over probability measures.
-An orthogonal question is that of how to measure the accuracy. Again,
-that can be answered in different ways based on the metric imposed on the output space, and yet again
+is imposed on the output set of the mechanism.
+In the literature on private Bayesian inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with respect to the vector of numbers parameterizing the output distribution using e.g.
+The $\ell_1$ norm.
+%metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
+%Another approach, which we will explore here, is to impose a metric over probability measures.
+A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
+A re-loved question is that of how to measure accuracy. Again,
+this can be answered in different ways based on the metric imposed on the output space, and yet again
 only in few works in literature (e.g. \cite{zhang2016differential})
-distances over probability measures have been used for these purposes.
+distances between probability measures have been used for these purposes.
 
 The question that this work aims at answering is whether
-an approach based on probability measures can outperform
-in term of accuracy approaches based on metric over
+an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
 the numeric parameters of the distributions. 
 We will see that in some cases this can happen.
+
 \section{Bayesian Inference Background}
@@
 \]
-where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
-$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.
+where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of observing $\dataobs$ under a value of $\theta$.
+Since we consider $\dataobs$ to be fixed, the likelihood is a function of $\theta$.
 For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
 Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
-the initial belief on $\theta$. That is, when no data has been observed. In practice though,
+the initial belief on $\theta$, that is, when no data has been observed. In practice though,
 prior distributions and likelihood functions are usually chosen so that the posterior
 belongs to the same \emph{family} of distributions. In this case we say that the prior
-is conjugate of the likelihood function. Using conjugate priors simplify calculcations and allows
-for inference to be performed in a recursive fashion over the data.
+is conjugate to the likelihood function. Use of a conjugate prior simplifies calculcations and allows for inference to be performed in a recursive fashion over the data.
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
@@
 of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
-the the vector of parameters of a categorical distributed random variable.
-In the former case the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
+the vector of parameters of a conjugate distributed random variable.
+In the former case, the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
 $\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
@@
 where $\betaf(\cdot,\cdot)$ is the beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs=\langle x_1,\dots x_n \rangle, x_i\in\{0,1\}$, and the likelihood function is:
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
 \[
@@
 In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
-and $\valpha\in(\mathbf{R^{+}})^{k}$, with p.d.f:
+and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
 \[
@@
 \]
-where $\mbetaf(\cdot)$ is the generealised beta function.
+where $\mbetaf(\cdot)$ is the generalized beta function.
 The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
@@
 \]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where in $\iverson{\cdot}$ we use
-Iverson bracket notation. Denoting by $\Delta\valpha$ the vector $\langle  \Delta\alpha_1,\dots \Delta\alpha_k \rangle$ the posterior distribution over $\vtheta$ turns out to be
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$represents Iverson bracket notation.
+Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
 \[
@@
 \label{sec:base}
-We are interested in designing a mechanism for privately releasing
-\emph{fully} the posterior distributions derived in section \ref{sec_background},
-and not a sample from them.  It's worth noticing that the posterior
-distributions are fully characterized by their parameters, and the
-family (beta, Dirichlet) they belong to.  Hence, in case of the
-Beta-Binomial model we are interested in releasing a private version
-of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-Multinomial model we are interested in a
-private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
-already attacked this problem and their solution consisted in adding
-independent Laplacian noise to the parameters of the posteriors. That
-is, in the case of the Beta-Binomial system the value released would
-be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
-%with truncating method come from algorithm designed by \citet{zhang2016differential}
-where $Lap(\mu,\nu)$
-denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
+We are interested in designing a mechanism for privately releasing the full posterior distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
+It's worth noticing that the posterior distributions are fully characterized by their parameters, and the family (beta, Dirichlet) they belong to.
+Hence, in case of the Beta-Binomial model we are interested in releasing a private version of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
+in the case of the Dirichlet-Multinomial model we are interested in a private version of $\valpha'=(\valpha + \Delta \valpha)$.
+\citet{zhang2016differential} and \citet{xiao2012bayesian} have already attacked this problem by adding independent Laplacian noise to the parameters of the posteriors.
+That is, in the case of the Beta-Binomial system, the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha + \tilde{\Delta \alpha},\beta + n - \tilde{\Delta \alpha})$ where $\tilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
 This mechanism is $\epsilon$-differentially private, and the noise is
@@
 
-\noindent Also, in previous works, the accuracy has been measured again with respect to
-$\ell_1$ norm. That is, an upper bound has been given to
+\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
 \[
@@
 Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
-The choice of Hellinger distance was dictated by two facts, first of all it simplifies
+Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
 calculations in the case of the probabilistic models considered here
-and second of all it also provides straightforwardly bounds for
-the total variation distance, which represents also the maximum advantage
+and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
 an unbounded adversary can have in distingishing two distributions. 
@@
 \label{sec_smoo}
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$,
-we define the follwing set:
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
 
@@
 \]
+
 where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
-Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference
-process will produce an element from $\betaset$ that we denote by
-$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
-prior,  which from now on we consider fixed and we denote it by $\bprior$.
+Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference process will produce an element from $\betaset$ that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the prior,  which from now on we consider fixed and we denote it by $\bprior$.
 
-We can now define the mechanism $\hexpmech$ which,
-given in input a sequence of observations $\dataobs$, $\epsilon>0$ and $\delta>0$,
-produces an element $r$ in $\betaset$ with probability:
+We can now define the mechanism $\hexpmech$ which, given in input a sequence of observations $\dataobs$ and parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
 
 \begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
-{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
+{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
-this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
-The difference is that in this mechanism we don't calibrate the noise w.r.t. to the global sensitivity of the scoring function but w.r.t. to the smooth sensitivity $S(\dataobs)$
--- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
+
+This mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as the range and $\hellinger(\cdot,\cdot)$ as the scoring function.
+The difference is that in this mechanism we don't calibrate the noise w.r.t.
+to the global sensitivity of the scoring function but w.r.t.
+to the smooth sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$.
+The smooth sensitivity is computed as follows:
 \begin{equation}
   \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
+   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\},
 \end{equation}
- where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
- of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
- denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t. $\ell_1$ norm--of the scoring function used in our mechanism, that is:
+where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$, the scoring function used in our mechanism.
+That is:
 \begin{equation*}
- \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
+\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
 \end{equation*}
@@
 \]
-and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(\dataobs)$ in (\ref{eq:smooth}) will be
-computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
-Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We will denote by
-$\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
+and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates.
+Also, the smooth sensitivity $S(\dataobs)$ in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
+Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case.
+We will denote by $\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
 % In what follows, we will use a correspondence between the probability
@@
 Every plot is an average over 1000 runs. In all the experiments we set
-$\epsilon = 0.8$, and $\delta = 0.00000001$.
+$\epsilon = 0.8$, and $\delta = 10^{-8}$.
 
 \noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
-Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
-independent variables --or a combination thereof.
-The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
-is also drawn to give a rough guide to the significance of difference of medians;
-The whiskers extend from the box to show the range of the data. 
-A blue box in the plots represents the exponential mechanism behaviour,
-while the yellow box next to it represents the performance of a variation of the
-basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
-The variation considered performs a post processing on the released parameters so that they
-are consistent. For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
+Accuracy is measured using Hellinger distance.
+The x-axis, instead shows  one of the previously mentioned independent variables --or a combination thereof.
+The boxes extend from the lower to the upper quartile values of the data, with a line at the median.
+A notch on the box around the median is also drawn to give a rough guide to the significance of difference of medians; The whiskers extend from the box to show the range of the data.
+A blue box in the plots represents our newly designed exponential mechanism behavior, while the yellow box next to it represents the performance of a variation of the basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
+The variation considered performs a post processing on the released parameters so that they are consistent.
+For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
+
 \paragraph{Increasing data size with balanced datasets}
@@
 In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
-This means that in the Beta-Binomial setting the datasets will be
-half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
-equally split in all the $k=3$ bins. Figure \ref{fig_vs_datasize} shows that  when the
+This means that in the Beta-Binomial setting the datasets will be half 1s and half 0s, while int the Dirichelet-Multinomial the data will be equally split in all the $k=3$ bins.
+Figure \ref{fig_vs_datasize} shows that  when the
 data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
@@
 \label{subsubsec_vs_dimension}
-In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
-different sizes and different dimensions. The plot shows that increasing the number of dimensions have
-a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
-mechanism. Fixing the number of dimensions and increasing the data size shows that
-the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
-In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
-mechanism.
+In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of different sizes and different dimensions.
+The plot shows that increasing the number of dimensions has a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace mechanism.
+Fixing the number of dimensions and increasing the data size shows that the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$.
+In other words, dimensions have little influence on whether our mechanisms will beat the Laplace mechanism.
+
 \begin{figure}[ht]
@@
 \label{subsubsec_vs_variance}
-In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
-of balance of the datasets. We  study this variable only under
-two-dimensions $\betad$ distribution in order to be more concise. The plot shows
-that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
+In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels of balance of the datasets.
+We  study this variable only under the two-dimensional $\betad$ distribution in order to be more concise.
+The plot shows that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
 
@@
 \section{Conclusions and Future Works}
-From what we have seen in the previous sections 
-we can obtain some preliminary conclusions. That is,
-the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases: 
+From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases: 
 \begin{enumerate}
@@
 
-These results although very motivating, are still not enough for real world applications.
-Hence, we will continue our work in the follwoing directions:
+These results although very motivating, are still not enough for real world applications. Hence, we will continue our work in the follwoing directions:
 \begin{enumerate}
-  \item For now, we just have a intuitive idea on the accuracy
-    behavior of our mechanisms, and not a precise formula or bound on it.
+  \item  For now, we just have a intuitive idea on the accuracy behavior of our mechanisms, and not a precise formula or bound on it.
 When do our mechanisms perform better than the baseline mechanism and when they don't?
-    How much influence will elements in Section \ref{sec_experiment} have on the
-    accuracy? Are there any other important factors we missed? These are
-    all questions w.r.t. the accuracy that we are going to explore next, and in a more
-    principled and formal way.
-\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
+How much influence will elements in Section \ref{sec_experiment} have on the accuracy?
+Are there any other important factors we missed?
+These are all questions w.r.t.
+the accuracy that we are going to explore next, and in a more principled and formal way.
+\item  Theorem \ref{thm:privacy} provides an upper bound on the  privacy loss for
   $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
 Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
-  This means that we could improve accuracy, by adding less noise --
-  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
-\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
-  it is worth exploring other distances over distributions. An interesting class
-  of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
+This means that we could improve accuracy, by adding less noise -- that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
+\item The choice of the Hellinger distance might seem quite ad-hoc.
+Hence, it is worth exploring other distances over distributions.
+An interesting class of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
 \end{enumerate}

### 2018-07-26 main-sketch.tex
update bugs
update author orders
fixed the fixes--still some work to do on the green comments (technical things...)

@@
 \input{macros}
+\usepackage{accents}
 
 \begin{document}
-\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}%Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
+\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
 \subtitle{Extended Abstract}
+
+\author{Jiawen Liu}
+\affiliation{%
+  \institution{University at Buffalo, SUNY}
+}
+\email{jliu223@buffalo.edu}
 
@@
 
-\author{Jiawen Liu}
-\affiliation{%
-  \institution{University at Buffalo, SUNY}
-}
-\email{jliu223@buffalo.edu}
-
 \author{Marco Gaboardi}
@@
 
-\author{Mark Bun}
-\affiliation{%
-  \institution{Princeton University}
-}
-\email{mbun@cs.princeton.edu}
-
-\begin{abstract}
-Bayesian inference is a statistical method which allows one to derive a
-\emph{posterior} distribution over a parameter, starting from a
-\emph{prior} distribution and observed data.  Settings where sensitive individual information is , different approaches have been taken to make
-this process differentially private. \citet{dimitrakakis2014robust},
-and \citet{wang2015privacy}, for instance, proved that, under specific
-conditions, sampling from the posterior distribution is already
-differentially private. Other works,
-e.g., \cite{zhang2016differential}, \cite{foulds2016theory}, designed
-differentially private mechanisms that output a representation of the
-full posterior distribution. Also, accuracy of these mechanisms was
-measured using metrics on the space of the numeric parameters of the
-posterior distribution, e.g., the $\ell_1$-norm.
+\begin{abstract} Bayesian inference is a statistical method which
+allows one to derive a \emph{posterior} distribution over a parameter,
+starting from a \emph{prior} distribution and observed data. Settings
+where sensitive individual information is involved, different
+approaches have been taken to make this process differentially
+private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy},
+for instance, proved that, under specific conditions, sampling from
+the posterior distribution is already differentially private. Other
+works, e.g., \cite{zhang2016differential}, \cite{foulds2016theory},
+designed differentially private mechanisms that output a
+representation of the full posterior distribution. Also, accuracy of
+these mechanisms was measured using metrics on the space of the
+numeric parameters of the posterior distribution, e.g., the
+$\ell_1$-norm.
 
 In this work we present a new differentially private algorithm to
-compute the posterior in a Beta-Binomial system and in a Dirichlet-Multinomial system.
-We apply the exponential mechanism to the smooth sensitivity of a metric on probability distributions; we measured the accuracy of the process by using the same metric.
-We compared the accuracy of this approach with the ones based on $\ell_1$-norm.
-Experimental results show that when the data size is small or when the parameters of the prior distribution are large, the former outperforms the latter.
+compute the posterior in a Beta-Binomial system and in a
+Dirichlet-Multinomial system. We apply the exponential mechanism to
+the smooth sensitivity of a metric on probability distributions; we
+measured the accuracy of the process by using the same metric. We
+compared the accuracy of this approach with the ones based on
+$\ell_1$-norm. Experimental results show that when the data size is
+small or when the parameters of the prior distribution are large, the
+former outperforms the latter.
 
@@
 
-% \input{main-sketch} % TODO: replace with your brilliant paper!
-% \input{macros}
 \section{An informal motivation}
@@
 leak information about individuals on the dataset.
-Differential privacy enables release of an approximate posterios distribution through the introduction of random noise.
-The amount of the noise that must be introduced depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to small changes in the data set.%So, we need to noise the posterior belief in order to protect the data set before releasing it.
-The question of how much noise to add is usually answered with an $\epsilon$, and a sensitivity value.
+Hence, in order to protect the dataset, random noise is added to the posterior belief before releasing it.
+The amount of the noise that must be introduced
+depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
+small changes in the data set. 
 Sensitivity can be computed in many different ways based on which metric space
-is imposed on the output set of the mechanism.
-In the literature on private Bayesian inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with respect to the vector of numbers parameterizing the output distribution using e.g.
-The $\ell_1$ norm.
-%metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
-%Another approach, which we will explore here, is to impose a metric over probability measures.
+is imposed on the output set of the mechanism. In the literature on private Bayesian
+inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
+respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
 A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
@@
 \]
-where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of observing $\dataobs$ under a value of $\theta$.
-Since we consider $\dataobs$ to be fixed, the likelihood is a function of $\theta$.
+where the expression $\Pr(\dataobs | \theta)$ denotes the
+\emph{likelihood} of observing $\dataobs$ under a value of
+$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
+a function of $\theta$.
 For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
@@
 belongs to the same \emph{family} of distributions. In this case we say that the prior
-is conjugate to the likelihood function. Use of a conjugate prior simplifies calculcations and allows for inference to be performed in a recursive fashion over the data.
+is conjugate to the likelihood function. Use of a conjugate prior
+simplifies calculations and allows for inference to be performed in a
+recursive fashion over the data.
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias}--
-of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
-the vector of parameters of a conjugate distributed random variable.
-In the former case, the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
+Specifically, we will consider the situation where $\theta$ represents
+the parameter --informally called \emph{bias}-- of a Bernoulli
+distributed random variable, and its immediate generalization where
+the parameter $\vtheta$ represents the vector of parameters of a
+categorically distributed random variable.  In the former case, the
+prior distribution over $\theta\in [0,1]$ is going to be a beta
+distribution, $\betad(\alpha, \beta)$, with parameters
 $\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+
 \[
@@
 \]
-In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
+In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
+is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
 and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
@@
 where $\mbetaf(\cdot)$ is the generalized beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
+coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
 The likelihood function will be:
@@
 \]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$represents Iverson bracket notation.
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
 Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
@@
 \]
-where $+$ denotes the component wise sum of vectors of reals.
+where $+$ denotes the componentwise sum of vectors of reals.
 
@@
 \label{sec:base}
-We are interested in designing a mechanism for privately releasing the full posterior distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
-It's worth noticing that the posterior distributions are fully characterized by their parameters, and the family (beta, Dirichlet) they belong to.
-Hence, in case of the Beta-Binomial model we are interested in releasing a private version of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-Multinomial model we are interested in a private version of $\valpha'=(\valpha + \Delta \valpha)$.
-\citet{zhang2016differential} and \citet{xiao2012bayesian} have already attacked this problem by adding independent Laplacian noise to the parameters of the posteriors.
-That is, in the case of the Beta-Binomial system, the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha + \tilde{\Delta \alpha},\beta + n - \tilde{\Delta \alpha})$ where $\tilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+We are interested in designing a mechanism for privately releasing the full posterior
+distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
+It's worth noticing that the posterior distributions are fully characterized
+by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
+Beta-Binomial model we are interested in releasing a private version of the pair of
+parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
+in the case of the Dirichlet-Multinomial model we are interested in a private version of
+$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
+have already attacked this problem by adding independent Laplacian noise to the
+parameters of the posteriors. That is, in the case of the Beta-Binomial system,
+the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
+where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
+and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
 This mechanism is $\epsilon$-differentially private, and the noise is
@@
 
-where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
-Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference process will produce an element from $\betaset$ that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the prior,  which from now on we consider fixed and we denote it by $\bprior$.
+where $\Delta\alpha$ is as defined in Section
+\ref{sec_background}. Notice that $\betaset$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\betaset$
+that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
+parametrize the result by the prior, which from now on we consider
+fixed and we denote it by $\bprior$.
 
-We can now define the mechanism $\hexpmech$ which, given in input a sequence of observations $\dataobs$ and parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
+We can now define the mechanism $\hexpmech$ which, given in input a
+sequence of observations $\dataobs$ and parameters $\epsilon>0$ and
+$\delta>0$, produces an element $r$ in $\betaset$ with probability:
 
@@
 
-This mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as the range and $\hellinger(\cdot,\cdot)$ as the scoring function.
-The difference is that in this mechanism we don't calibrate the noise w.r.t.
-to the global sensitivity of the scoring function but w.r.t.
-to the smooth sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$.
-The smooth sensitivity is computed as follows:
+This mechanism is based on the basic exponential mechanism
+\cite{talwar}, with $\betaset$ as the range and
+$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
+that in this mechanism we don't calibrate the noise w.r.t. to the
+global sensitivity of the scoring function but w.r.t. to the smooth
+sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of
+$\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is
+computed as follows:
 \begin{equation}
@@
 \end{equation}
-where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$, the scoring function used in our mechanism.
-That is:
+where $d$ is the Hamming distance between two datasets, $\gamma =
+\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
+be determined later, and where $\Delta_{l}\bigg
+(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
+sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
+of the scoring function used in our mechanism. That is:
 \begin{equation*}
@@
 \]
-and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates.
-Also, the smooth sensitivity $S(\dataobs)$ in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
-Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case.
-We will denote by $\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
+and by replacing the $\betaset$ with set of posterior Dirichlet
+distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
+over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
+that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+will denote by $\hexpmechd$ the mechanism for the
+Dirichlet-Multinomial system.
 % In what follows, we will use a correspondence between the probability
@@
 
-\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
-Accuracy is measured using Hellinger distance.
-The x-axis, instead shows  one of the previously mentioned independent variables --or a combination thereof.
-The boxes extend from the lower to the upper quartile values of the data, with a line at the median.
-A notch on the box around the median is also drawn to give a rough guide to the significance of difference of medians; The whiskers extend from the box to show the range of the data.
-A blue box in the plots represents our newly designed exponential mechanism behavior, while the yellow box next to it represents the performance of a variation of the basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
-The variation considered performs a post processing on the released parameters so that they are consistent.
-For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
+\noindent In the following whiskers-plots, the y-axis shows the
+accuracy (or equivalently, the error) of the mechanisms.  Accuracy is
+measured using Hellinger distance. The x-axis, instead shows one of
+the previously mentioned independent variables --or a combination
+thereof. The boxes extend from the lower to the upper quartile values
+of the data, with a line at the median. A notch on the box around the
+median is also drawn to give a rough guide to the significance of
+difference of medians; The whiskers extend from the box to show the
+range of the data. A blue box in the plots represents our newly
+designed exponential mechanism's behavior-- where the sensitivity is calibrated
+w.r.t Hellinger distance-- while the yellow box next to
+it represents the performance of a variation of the basic Laplace
+mechanism presented in Section (\ref{sec:base}) with the same
+settings: that is $\epsilon, \delta$, data, prior. The variation
+considered performs a postprocessing on the released parameters so
+that they are consistent. For instance when the sum of the noised
+parameters is greater than $n$ we will truncate them so that they sum
+up to $n$.
 
@@
 
-In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
-This means that in the Beta-Binomial setting the datasets will be half 1s and half 0s, while int the Dirichelet-Multinomial the data will be equally split in all the $k=3$ bins.
-Figure \ref{fig_vs_datasize} shows that  when the
-data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
-decreases. In Figure \ref{fig_vs_datasize}(a), when the data size is
-smaller than 12, $\hexpmech$ can outperform the Laplace mechanism but it fails to do so
-for bigger datasets. The same happens in as in Figure \ref{fig_vs_datasize}(b):
-the Laplace mechanism starts performing better for datasets bigger than 15.
+In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets
+of observations. This means that in the Beta-Binomial setting the
+datasets will be half 1s and half 0s, while int the
+Dirichelet-Multinomial the data will be equally split in all the $k=3$
+bins. Figure \ref{fig_vs_datasize} shows that when the data size
+increases, the accuracy of $\hexpmech$ and $\hexpmechd$ decreases. In
+Figure \ref{fig_vs_datasize}(a), when the data size is smaller than
+12, $\hexpmech$ can outperform the Laplace mechanism but it fails to
+do so for bigger datasets. The same happens in as in Figure
+\ref{fig_vs_datasize}(b): the Laplace mechanism starts performing
+better for datasets bigger than 15.
 
@@
 \label{subsubsec_vs_dimension}
-In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of different sizes and different dimensions.
-The plot shows that increasing the number of dimensions has a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace mechanism.
-Fixing the number of dimensions and increasing the data size shows that the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$.
-In other words, dimensions have little influence on whether our mechanisms will beat the Laplace mechanism.
+In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
+of different sizes and different dimensions. The plot shows that
+increasing the number of dimensions has a similar pejorative effect on
+$\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
+of dimensions and increasing the data size shows that the Laplace
+mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
+other words, dimensions have little influence on whether our
+mechanisms will beat the Laplace mechanism.
 
@@
 \label{subsubsec_vs_variance}
-In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels of balance of the datasets.
-We  study this variable only under the two-dimensional $\betad$ distribution in order to be more concise.
-The plot shows that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
+In Figure \ref{fig_vs_variance}, in the x-axis we considered different
+levels of balance of the datasets. We study this variable only under
+the two-dimensional $\betad$ distribution in order to be more
+concise. The plot shows that $\hexpmech$ accuracy is better than the
+one of Laplace when the dataset is balanced.
 
@@
 \begin{enumerate}
-  \item  For now, we just have a intuitive idea on the accuracy behavior of our mechanisms, and not a precise formula or bound on it.
-When do our mechanisms perform better than the baseline mechanism and when they don't?
-How much influence will elements in Section \ref{sec_experiment} have on the accuracy?
-Are there any other important factors we missed?
-These are all questions w.r.t.
-the accuracy that we are going to explore next, and in a more principled and formal way.
-\item  Theorem \ref{thm:privacy} provides an upper bound on the  privacy loss for
-  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
-Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
-This means that we could improve accuracy, by adding less noise -- that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
-\item The choice of the Hellinger distance might seem quite ad-hoc.
-Hence, it is worth exploring other distances over distributions.
-An interesting class of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
+  \item  For now, we just have a intuitive idea on the accuracy
+behavior of our mechanisms, and not a precise formula or bound on
+it. When do our mechanisms perform better than the baseline mechanism
+and when they don't? How much influence will elements in Section
+\ref{sec_experiment} have on the accuracy? Are there any other
+important factors we missed? These are all questions w.r.t. the
+accuracy that we are going to explore next, and in a more principled
+and formal way.
+\item  Theorem \ref{thm:privacy} provides an upper bound on the
+privacy loss for $\hexpmech$ and $\hexpmechd$ but not necessarily a
+tight one. Indeed, experiments have shown that the actual privacy loss
+in the experiments can be smaller than $\epsilon$. This means that we
+could improve accuracy, by adding less noise -- that is noise
+proportional to a higher value of $\epsilon$-- but still achieve
+$(\epsilon, \delta)$-dp.
+\item The choice of the Hellinger distance might seem quite
+ad-hoc. Hence, it is worth exploring other distances over
+distributions. An interesting class of probability metrics is the
+family of $f$-divergences \cite{CIT-004}.
 \end{enumerate}

### 2018-07-27 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py
update author orders

@@ -1051,7 +1051,7 @@ if __name__ == "__main__":
 	x2 = [2,18]
 	observation = [5,5,5]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = [i*200 for i in range(70,100)]#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = [i*100 for i in range(30,80)]#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.1,0.9]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [Dir([4*i,4*i,4*i]) for i in range(5,20)]

### 2018-07-27 main-sketch.tex
fixed the fixes--still some work to do on the green comments (technical things...)
alph order of co-authors
update authors
update author orders
update figures
paragraph

@@
 
-\author{Jiawen Liu}
+\author{Mark Bun}
 \affiliation{%
-  \institution{University at Buffalo, SUNY}
+  \institution{Princeton University}
 }
-\email{jliu223@buffalo.edu}
+\email{mbun@cs.princeton.edu}
 
@@
 \email{gaboardi@buffalo.edu}
+
+\author{Jiawen Liu}
+\affiliation{%
+  \institution{University at Buffalo, SUNY}
+}
+\email{jliu223@buffalo.edu}
 
@@
 \centering
-  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
-  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Balanced datasets}
+  \subfigure[Data set sizing from $300$ to $800$ ]{
+    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
+    \label{subsubsec_vs_datasize1a}
+  }
+  \subfigure[Data set sizing from $14000$ to $20000$]{
+    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
+  \label{subsubsec_vs_datasize1b}} 
+\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}
@@
 
-In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets
-of observations. This means that in the Beta-Binomial setting the
-datasets will be half 1s and half 0s, while int the
-Dirichelet-Multinomial the data will be equally split in all the $k=3$
-bins. Figure \ref{fig_vs_datasize} shows that when the data size
-increases, the accuracy of $\hexpmech$ and $\hexpmechd$ decreases. In
-Figure \ref{fig_vs_datasize}(a), when the data size is smaller than
-12, $\hexpmech$ can outperform the Laplace mechanism but it fails to
-do so for bigger datasets. The same happens in as in Figure
-\ref{fig_vs_datasize}(b): the Laplace mechanism starts performing
-better for datasets bigger than 15.
-
+In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{balanced} datasets
+of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
+and \ref{subsubsec_vs_datasize1b}) the datasets will be half 1s and half 0s, while int the
+Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_dir1a} and \ref{fig_vs_datasize_dir1b})
+the data will be equally split in all the $k=3$ bins.
+The results show that when the data size
+increases, the average errors of
+$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
+i.e with size less 650 in the case of Beta-Binomial systems,
+the Laplace mechanisms outperforms the exponential mechanisms,
+but for bigger datasets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
+we considered datasets of the order of 15 thousands elements,
+the exponential mechanisms outperforms the Laplacian mechanism.
 \paragraph{Increasing dimensions and data size with balanced dataset}

### 2018-07-27 main-sketch.tex
paragraph

@@
   \label{subsubsec_vs_datasize1b}} 
-\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\caption{With prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}
@@
 
-In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{balanced} datasets
+\begin{figure}[ht]
+\begin{center}
+\centering
+  \subfigure[Data set sizing from $300$ to $800$ ]{
+
+    \label{subsubsec_vs_datasize1adir}
+  }
+  \subfigure[Data set sizing from $14000$ to $20000$]{
+
+  \label{subsubsec_vs_datasize1bdir}} 
+\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_dir}
+\end{center}
+\end{figure}
+
+In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
 of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
-and \ref{subsubsec_vs_datasize1b}) the datasets will be half 1s and half 0s, while int the
-Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_dir1a} and \ref{fig_vs_datasize_dir1b})
-the data will be equally split in all the $k=3$ bins.
+and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
+the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
 The results show that when the data size
@@
 the exponential mechanisms outperforms the Laplacian mechanism.
+Similar experimental results were obtainted for the Dirichelet-Multinomial system.
 \paragraph{Increasing dimensions and data size with balanced dataset}

### 2018-07-27 main-sketch.tex
update figure

@@
   \label{subsubsec_vs_datasize1b}} 
-\caption{With prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}
@@
 the Laplace mechanisms outperforms the exponential mechanisms,
-but for bigger datasets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
-we considered datasets of the order of 15 thousands elements,
-the exponential mechanisms outperforms the Laplacian mechanism.
-Similar experimental results were obtainted for the Dirichelet-Multinomial system.
+but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
+we considered data sets of the order of 15 thousands elements,
+the exponential mechanisms outperforms the Laplace mechanism.
+Similar experimental results were obtained for the Dirichlet-Multinomial system.
+
 \paragraph{Increasing dimensions and data size with balanced dataset}
@@
 \begin{enumerate}
-  \item When the data size is small
-  \item When the observed data is balanced
-  \item When priors parameters increase (eventually).
+  \item When the data size is small, data is balanced and priors parameters increase
+  \item When the data size is large
 \end{enumerate}

### 2018-07-27 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py

@@ -884,7 +884,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	for observation in observations:
 		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
 		Bayesian_Model._set_observation(observation)
-		Bayesian_Model._experiments(10000)
+		Bayesian_Model._experiments(2000)
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[3]])
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[0]])
 		mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
@@ -1046,13 +1046,13 @@ if __name__ == "__main__":
 	datasize = 3000
 	epsilon = 0.8
 	delta = 0.00000001
-	prior = Dir([1,1])
+	prior = Dir([1,1,1])
 	x1 = [1,19]
 	x2 = [2,18]
 	observation = [5,5,5]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = [i*100 for i in range(30,80)]#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
-	percentage = [0.1,0.9]
+	datasizes = [i*100 for i in range(10,21a)]#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	percentage = [0.2,0.3,0.5]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [Dir([4*i,4*i,4*i]) for i in range(5,20)]
 	# print opt_hellinger2([20000,20000],[19999, 19999])

### 2018-07-28 main-sketch.tex
update figures

@@
   \subfigure[Data set sizing from $300$ to $800$ ]{
-
+    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
     \label{subsubsec_vs_datasize1adir}
@@
   \subfigure[Data set sizing from $14000$ to $20000$]{
-
+     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichelt.eps}   
   \label{subsubsec_vs_datasize1bdir}} 
-\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize_dir}

### 2018-07-28 main-sketch.tex
fix mistake
typo
removed some figures

@@
 
-\noindent In the following whiskers-plots, the y-axis shows the
-accuracy (or equivalently, the error) of the mechanisms.  Accuracy is
-measured using Hellinger distance. The x-axis, instead shows one of
+\noindent In the following some of the plots show
+mean error as a function of the datasize while others
+are whiskers-plots where the y-axis shows the average
+accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows one of
 the previously mentioned independent variables --or a combination
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
 \begin{center}
 \centering
-  \subfigure[Data set sizing from $300$ to $800$ ]{
+  \subfigure[Data set size from $300$ to $800$ ]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
@@
   }
-  \subfigure[Data set sizing from $14000$ to $20000$]{
+  \subfigure[Data set size from $14000$ to $20000$]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
@@
 \centering
-  \subfigure[Data set sizing from $300$ to $800$ ]{
+  \subfigure[Data set size from $300$ to $800$ ]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
@@
   }
-  \subfigure[Data set sizing from $14000$ to $20000$]{
-     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichelt.eps}   
+  \subfigure[Data set size from $14000$ to $20000$]{
+     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
   \label{subsubsec_vs_datasize1bdir}} 
@@
 
-\paragraph{Increasing dimensions and data size with balanced dataset}
-\label{subsubsec_vs_dimension}
-In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
-of different sizes and different dimensions. The plot shows that
-increasing the number of dimensions has a similar pejorative effect on
-$\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
-of dimensions and increasing the data size shows that the Laplace
-mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
-other words, dimensions have little influence on whether our
-mechanisms will beat the Laplace mechanism.
+% \paragraph{Increasing dimensions and data size with balanced dataset}
+% \label{subsubsec_vs_dimension}
+% In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
+% of different sizes and different dimensions. The plot shows that
+% increasing the number of dimensions has a similar pejorative effect on
+% $\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
+% of dimensions and increasing the data size shows that the Laplace
+% mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
+% other words, dimensions have little influence on whether our
+% mechanisms will beat the Laplace mechanism.
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
-\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
-\label{fig_vs_dimension}
-\end{figure}
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
+% \caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
+% \label{fig_vs_dimension}
+% \end{figure}
 
-\paragraph{Fixed data size and unbalaced datasets}
-\label{subsubsec_vs_variance}
-In Figure \ref{fig_vs_variance}, in the x-axis we considered different
-levels of balance of the datasets. We study this variable only under
-the two-dimensional $\betad$ distribution in order to be more
-concise. The plot shows that $\hexpmech$ accuracy is better than the
-one of Laplace when the dataset is balanced.
+% \paragraph{Fixed data size and unbalaced datasets}
+% \label{subsubsec_vs_variance}
+% In Figure \ref{fig_vs_variance}, in the x-axis we considered different
+% levels of balance of the datasets. We study this variable only under
+% the two-dimensional $\betad$ distribution in order to be more
+% concise. The plot shows that $\hexpmech$ accuracy is better than the
+% one of Laplace when the dataset is balanced.
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
-\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
-\label{fig_vs_variance}
-\end{figure}
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
+% \caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
+% \label{fig_vs_variance}
+% \end{figure}
 
@@
 it is outperformed after a while.
-\begin{figure}[ht]
+\begin{figure}[H]
 \centering
 \includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
-\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
+\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
 \label{fig_vs_prior}

### 2018-07-28 main-sketch.tex
removed some figures

@@
 \noindent In the following some of the plots show
-mean error as a function of the datasize while others
-are whiskers-plots where the y-axis shows the average
-accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows one of
-the previously mentioned independent variables --or a combination
-thereof. The boxes extend from the lower to the upper quartile values
+mean error as a function of the datasize while one
+is a whiskers-plot where the y-axis shows the average
+accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
+different balanced priors used. The boxes extend from the lower to the upper quartile values
 of the data, with a line at the median. A notch on the box around the

### 2018-07-28 main-sketch.tex
removed some figures

@@
 the exponential mechanisms outperforms the Laplace mechanism.
-Similar experimental results were obtained for the Dirichlet-Multinomial system.
+Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
+but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
+too high run time of the algorithm.
 

### 2018-07-28 main-sketch.tex
pass over the abstract

@@
 \begin{abstract} Bayesian inference is a statistical method which
-allows one to derive a \emph{posterior} distribution over a parameter,
-starting from a \emph{prior} distribution and observed data. Settings
-where sensitive individual information is involved, different
-approaches have been taken to make this process differentially
-private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy},
-for instance, proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private. Other
-works, e.g., \cite{zhang2016differential}, \cite{foulds2016theory},
+allows one to derive a \emph{posterior} distribution,
+starting from a \emph{prior} distribution and observed data. Several
+approaches have been explored in order to make this process differentially
+private. For example, \citet{dimitrakakis2014robust}, and
+\citet{wang2015privacy} proved that, under specific conditions, sampling from
+the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
 designed differentially private mechanisms that output a
-representation of the full posterior distribution. Also, accuracy of
-these mechanisms was measured using metrics on the space of the
-numeric parameters of the posterior distribution, e.g., the
-$\ell_1$-norm.
+representation of the full posterior distribution.
 
-In this work we present a new differentially private algorithm to
-compute the posterior in a Beta-Binomial system and in a
-Dirichlet-Multinomial system. We apply the exponential mechanism to
-the smooth sensitivity of a metric on probability distributions; we
-measured the accuracy of the process by using the same metric. We
-compared the accuracy of this approach with the ones based on
-$\ell_1$-norm. Experimental results show that when the data size is
-small or when the parameters of the prior distribution are large, the
-former outperforms the latter.
+When the output of a differentially private mechanism is a probability
+distribution, accuracy is naturally measured by means of
+\emph{probabilistic distances} measuring how far this distribution is
+from the original one. Some classical examples are total variation distance,
+Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
 
+In this work, we design a mechanism for
+bayesian inference exploring the idea of calibrating noise using the
+same probabilistic distance we want to measure accuracy with. 
+We focus on two discrete models, the Beta-Binomial and the
+Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
+Our mechanism can be understood as a version of  the exponential mechanism
+where the noise is calibrated to the smooth sensitivity of the
+utility function, rather than to its global sensitivity. In our
+setting, the utility function is the probability distance we want to
+use to measure accuracy. To show the usefulness of this mechanism we
+show an experimental analysis comparing it with an approach based on
+the Laplace mechanism.
 \end{abstract}
@@
 Publishing the posterior distribution inferred from a sensitive dataset can
-leak information about individuals on the dataset.
-Hence, in order to protect the dataset, random noise is added to the posterior belief before releasing it.
-The amount of the noise that must be introduced
+leak information about the individuals in the dataset.
+In order to guarantee differential privacy and to protect the
+individuals' data we can add noise to the posterior before releasing it.
+The amount of the noise that we need to  introduced
 depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
@@
 Sensitivity can be computed in many different ways based on which metric space
-is imposed on the output set of the mechanism. In the literature on private Bayesian
+we consider on the output set of the mechanism. In the literature on private Bayesian
 inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with

### 2018-08-01 LocalSensitivityStudy.py
rename and update github

@@ -1,307 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-
-
-
-
-def multibeta_function(alphas):
-	numerator = 1.0
-	denominator = 0.0
-	for alpha in alphas:
-		numerator = numerator * math.gamma(alpha)
-		denominator = denominator + alpha
-	# print numerator / math.gamma(denominator)
-	return numerator / math.gamma(denominator)
-
-def optimized_multibeta_function(alphas):
-	denominator = -1.0
-	nominators = []
-	denominators = []
-	r = 1.0
-	for alpha in alphas:
-		denominator = denominator + alpha
-	for alpha in alphas:
-		temp = alpha - 1
-		while temp > 0.0:
-			nominators.append(temp)
-			temp -=1
-		if temp < 0.0:
-			nominators.append(math.gamma(1 + temp))
-	while denominator > 0.0:
-		denominators.append(denominator)
-		denominator -= 1
-	if denominator < 0.0:
-		denominators.append(math.gamma(1 + denominator))
-	# print nominators
-	# print denominators
-	d_pointer = len(denominators) - 1
-	n_pointer = len(nominators) - 1
-	while d_pointer >= 0 and n_pointer >= 0:
-		# print nominators[n_pointer],denominators[d_pointer]
-		r *= nominators[n_pointer] / denominators[d_pointer]
-		n_pointer -= 1
-		d_pointer -= 1
-	while d_pointer >= 0:
-		# print n_pointer,denominators[d_pointer]
-		r *= 1.0 / denominators[d_pointer]
-		d_pointer -= 1
-	while n_pointer >= 0:
-		# print nominators[n_pointer] ,d_pointer
-		r *= nominators[n_pointer] 
-		n_pointer -= 1
-	# 	while temp > 0.0:
-	# 		r *= (temp / denominator)
-	# 		temp -= 1
-	# 		denominator -= 1
-	# 		print r,temp,denominator
-	# 	if temp < 0.0:
-	# 		r *= (math.gamma(1 + temp) / denominator)
-	# 		denominator -= 1
-	# 		print r, temp, denominator
-	# while denominator > 0.0:
-	# 	r /= denominator
-	# 	denominator -= 1
-	# if denominator < 0.0:
-	# 	r /= math.gamma(1 + denominator)
[…]

### 2018-08-01 bayesian_inference_model_with_Exponential_mechanism/bayesian_inference_model_with_Exponential_mechanism.py

@@ -1,174 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-
-def beta_function(alpha, beta):
-	return 1.0 * math.gamma(alpha) * math.gamma(beta)/math.gamma(alpha + beta)
-
-def Hellinger_Distance(beta1, beta2):
-	return math.sqrt(1 - beta_function((beta1[0] + beta2[0])/2.0, (beta1[1] + beta2[1])/2.0) \
-		/ math.sqrt(beta_function(beta1[0], beta1[1]) * beta_function(beta2[0], beta2[1])))
-
-class GenObservedDataset(object):
-
-	def __init__(self, alpha, beta, sample_size, epsilon):
-
-		self._alpha = alpha
-		self._beta = beta
-		self._sample_size = sample_size
-		self._epsilon = epsilon
-		self._theta = numpy.random.beta(self._alpha, self._beta)
-		self._observation = numpy.random.binomial(1, self._theta, self._sample_size)
-		self._ones = numpy.count_nonzero(self._observation == 1)
-		self._zeros = numpy.count_nonzero(self._observation == 0)
-		self._laplaced_ones = numpy.count_nonzero(self._observation == 1) + numpy.random.laplace(0, 1.0/self._epsilon)
-		self._laplaced_zeros = numpy.count_nonzero(self._observation == 0) + numpy.random.laplace(0, 1.0/self._epsilon)
-		self._randomized_ones = self._ones
-		self._randomized_zeros = self._zeros
-		self._randomized_observation = deepcopy(self._observation)
-		self._exponential_ones = self._ones
-		self._exponential_zeros = self._zeros
-
-	def _set_randomized_ones(self):
-		self._randomized_ones = numpy.count_nonzero(self._randomized_observation == 1)
-
-	def _set_randomized_zeros(self):
-		self._randomized_zeros = numpy.count_nonzero(self._randomized_observation == 0)
-
-	def _randomize_observation(self):
-		for i in range(self._sample_size):
-			if random.randint(0,1) == 1:
-				self._randomized_observation[i] = random.randint(0,1)
-			else:
-				self._randomized_observation[i] = self._observation[i]
-		self._set_randomized_ones()
-		self._set_randomized_zeros()
-
-	def _set_exponential(self):
[…]

### 2018-08-01 bayesian_inference_model_with_Laplace_mechanism/bayesian_inference_model_with_Laplace_mechanism.py

@@ -1,121 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-
-class GenObservedDataset(object):
-
-	"""Generate a Random DataSet with binary class labels.
-
-	All data points are randomly chosen from a normal distribution centered at the origin and having std deviation 1
-	Data is generated as a 2-D matrix of values (rows) with a fixed number of attributes (columns).
-	The last attribute of every value (row) is corresponds to the class label : 1 or -1.
-	The generated Data is split into three sub-sets : train, test and valid.
-
-	Attributes:
-		train: The training data set feature vectors
-		valid: The validation data set feature vectors
-		test: The testing data set feature vectors
-		train_labels: The training data set feature labels
-		valid_labels: The validation data set feature labels
-		test_labels: The test data set feature labels
-
-	"""
-
-	def __init__(self, alpha, beta, sample_size, epsilon):
-		"""Specify the data set parameters
-		Args:
-		Raises:
-			ValueError : if split_ratio is invalid.
-		"""
-		self._alpha = alpha
-		self._beta = beta
-		self._sample_size = sample_size
-		self._theta = numpy.random.beta(self._alpha, self._beta)
-		self._observation = numpy.random.binomial(1, self._theta, self._sample_size)
-		self._ones = numpy.count_nonzero(self._observation == 1)
-		self._zeros = numpy.count_nonzero(self._observation == 0)
-		self._noised_ones = numpy.count_nonzero(self._observation == 1) + numpy.random.laplace(0, 1.0/epsilon)
-		self._noised_zeros = numpy.count_nonzero(self._observation == 0) + numpy.random.laplace(0, 1.0/epsilon)
-
-	def _get_theta(self):
-		return self._theta
-		"""Equalizes the number of 1 and -1 labels"""
-
-	def _get_observation(self):
-		return self._observation
-
-	def _get_ones(self):
-		return self._ones
-
-	def _get_zeros(self):
-		return self._zeros
-
-	def _get_Laplace_ones(self):
-		return self._noised_ones
-
-	def _get_Laplace_zeros(self):
-		return self._noised_zeros
-
-	def _show_theta(self):
-		print "The theta generated from the prior distribution is: " + str(self._theta)
-
-	def _show_noised(self):
[…]

### 2018-08-01 bayesian_inference_model_with_RR_mechanism/bayesian_inference_model_with_RR_mechanism.py

@@ -1,143 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-
-class GenObservedDataset(object):
-
-	"""Generate a Random DataSet with binary class labels.
-
-	All data points are randomly chosen from a normal distribution centered at the origin and having std deviation 1
-	Data is generated as a 2-D matrix of values (rows) with a fixed number of attributes (columns).
-	The last attribute of every value (row) is corresponds to the class label : 1 or -1.
-	The generated Data is split into three sub-sets : train, test and valid.
-
-	Attributes:
-		train: The training data set feature vectors
-		valid: The validation data set feature vectors
-		test: The testing data set feature vectors
-		train_labels: The training data set feature labels
-		valid_labels: The validation data set feature labels
-		test_labels: The test data set feature labels
-
-	"""
-
-	def __init__(self, alpha, beta, sample_size, epsilon):
-		"""Specify the data set parameters
-		Args:
-		Raises:
-			ValueError : if split_ratio is invalid.
-		"""
-		self._alpha = alpha
-		self._beta = beta
-		self._sample_size = sample_size
-		self._theta = numpy.random.beta(self._alpha, self._beta)
-		self._observation = numpy.random.binomial(1, self._theta, self._sample_size)
-		self._ones = numpy.count_nonzero(self._observation == 1)
-		self._zeros = numpy.count_nonzero(self._observation == 0)
-		self._laplaced_ones = numpy.count_nonzero(self._observation == 1) + numpy.random.laplace(0, 1.0/epsilon)
-		self._laplaced_zeros = numpy.count_nonzero(self._observation == 0) + numpy.random.laplace(0, 1.0/epsilon)
-		self._randomized_ones = 0
-		self._randomized_zeros = 1
-		self._randomized_observation = deepcopy(self._observation)
-		self._randomize_observation()
-
-	def _get_theta(self):
-		return self._theta
-		"""Equalizes the number of 1 and -1 labels"""
-
-	def _get_observation(self):
-		return self._observation
-
-	def _get_ones(self):
-		return self._ones
-
-	def _get_zeros(self):
-		return self._zeros
-
-	def _get_laplace_ones(self):
-		return self._laplaced_ones
-
[…]

### 2018-08-01 bayesian_inference_model_with_beta_bernoli/bayesian_inference_model_with_beta_bernoli.py

@@ -1,73 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-
-class GenObservedDataset(object):
-
-
-
-	def __init__(self, alpha, beta, sample_size):
-
-		self._alpha = alpha
-		self._beta = beta
-		self._sample_size = sample_size
-		self._theta = numpy.random.beta(self._alpha, self._beta)
-		self._observation = numpy.random.binomial(1, self._theta, self._sample_size)
-
-	def _get_theta(self):
-		return self._theta
-		"""Equalizes the number of 1 and -1 labels"""
-
-	def _get_observation(self):
-		return self._observation
-
-	def _get_ones(self):
-		return numpy.count_nonzero(self._observation == 1)
-
-	def _get_zeros(self):
-		return numpy.count_nonzero(self._observation == 0)
-
-
-
-def observing(given_database, alpha, beta, sample_size, times = 1):
-	posterior_thetas = []
-	prior_thetas = []
-	count = 0
-	while count < times:
-		observation = GenObservedDataset(alpha, beta, sample_size)
-		prior_thetas.append(observation._get_theta())
-		if (given_database._get_observation() == observation._get_observation()).all():
-			posterior_thetas.append(observation._get_theta())
-			count = count + 1
-	return prior_thetas, posterior_thetas
-
-def draw_distribution(datas, titles):
-	plt.subplots(nrows=len(datas), ncols=1, figsize=(8,len(datas)*3))
-	for i in range(len(datas)):
-		datas[i] = [round(item,2) for item in datas[i]]#[round(item * 10 * 2.0)/2.0/10 for item in datas[i]]
-		X = list(set(datas[i]))
-		X.sort()
-		Y = []
-		for x in X:
-			Y.append(datas[i].count(x))
-		plt.subplot(len(datas),1,i+1)
-		plt.bar(range(len(Y)), Y, facecolor='g', tick_label = X)
-		plt.title(titles[i])
-	plt.show()
-
-	return
-
-if __name__ == "__main__":
-	# Tests the functioning of the module
-	alpha = 4
-	beta = 5
-	sample_size = 5
-	given_database = GenObservedDataset(alpha, beta, sample_size)
-	prior_thetas, posterior_thetas = observing(given_database, alpha, beta, sample_size, 1000)
-	print given_database._get_observation()
-
-	draw_distribution([prior_thetas, posterior_thetas, list(numpy.random.beta(alpha \
[…]

### 2018-08-01 dp-bayeinfer.py

@@ -1,0 +1,1100 @@
+import numpy
+import matplotlib.pyplot as plt
+from copy import deepcopy
+import random
+import math
+import scipy
+from scipy.stats import beta
+from fractions import Fraction
+import operator
+import time
+from matplotlib.patches import Polygon
+import statistics
+from decimal import *
+from scipy.special import gammaln
+
+def gen_betaln (alphas):
+        numerator=0.0
+        for alpha in alphas:
+	        numerator = numerator + gammaln(alpha)
+                
+        return(numerator/math.log(float(sum(alphas))))
+
+
+def opt_hellinger2(alphas, betas):
+        z=gen_betaln(numpy.divide(numpy.sum([alphas, betas], axis=0), 2.0))-0.5*(gen_betaln(alphas) + gen_betaln(betas))
+        return (math.sqrt(1-math.exp(z)))
+
+
+
+def L1_Nrom(A, B):
+	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
+
+def multibeta_function(alphas):
+	numerator = 1.0
+	denominator = 0.0
+	for alpha in alphas:
+		numerator = numerator * math.gamma(alpha)
+		denominator = denominator + alpha
+	# print numerator / math.gamma(denominator)
+	return numerator / math.gamma(denominator)
+
+def optimized_multibeta_function(alphas):
+	denominator = -1.0
+	nominators = []
+	denominators = []
+	r = 1.0
+	for alpha in alphas:
+		denominator = denominator + alpha
+	for alpha in alphas:
+		# print alpha
+		temp = alpha - 1
+		while temp > 0.0:
+			nominators.append(temp)
+			temp -=1.0
+		
+		if temp < 0.0 and temp > -1.0:
+			#print temp
+			nominators.append(math.gamma(1 + temp))
+	while denominator > 0.0:
+		denominators.append(denominator)
+		denominator -= 1.0
+	if denominator < 0.0 and denominator > -1.0:
+		denominators.append(math.gamma(1.0 + denominator))
+
+	denominators.sort()
+	nominators.sort()
+	# print nominators
+	# print denominators
+	d_pointer = len(denominators) - 1
+	n_pointer = len(nominators) - 1
+	while d_pointer >= 0 and n_pointer >= 0:
[…]

### 2018-08-01 dp_bayesian_inference_model_with_beta_prior.py

@@ -1,544 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import time
-
-def beta_function(alpha, beta):
-	f = Fraction(1,1)
-	t = (min(alpha, beta))
-	k = (max(alpha, beta))
-	if t % 1 == 0.0 and k % 1 == 0.0:
-		for i in range(1, int(t)):
-			f = f * Fraction(i, (i + int(k)))
-		f = f * Fraction(1, int(k))
-		f = (1.0 * f.numerator) / (f.denominator)
-	# else:
-	# 	f = math.gamma(alpha) * math.gamma(beta) / math.gamma(alpha + beta)
-	elif t % 1 == 0.0 and k % 1 != 0.0:
-		k = Fraction(int(k * 2), 2)
-		f = 1 / k
-		t = Fraction((int(t) - 1) * 2, 2)
-		while t >= 1:
-			f = f * t / (k + t)
-			t = t - 1
-		f = (1.0 * f.numerator) / (f.denominator)
-	elif k % 1 == 0.0 and t % 1 != 0.0:
-		t = Fraction(int(t * 2), 2)
-		f = 1 / t
-		k = Fraction(int(k - 1)*2, 2)
-		while k >= 1:
-			f = f * k / (k + t) 
-			k = k - 1
-		f = (1.0 * f.numerator) / (f.denominator)
-	else:
-		k = Fraction(int(k * 2), 2)
-		#print k
-		t = Fraction(int(t * 2), 2)
-		#print t
-		k = k - 1
-		s = k + t
-		while k > 0:
-			#print f,k,s
-			f = f * k / s
-			k = k - 1
-			s = s - 1
-		t = t - 1
-		while t > 0:
-			#print f,t,s
-			f = f * t / s
-			t = t - 1
-			s = s - 1
-		f =  math.sqrt(math.pi) * math.sqrt(math.pi) * (1.0 * f.numerator) / (f.denominator)
-	return f
-
-def beta_function_naive(alpha, beta):
- 	return 1.0 * math.gamma(alpha) * math.gamma(beta)/math.gamma(alpha + beta)
-
-def Varying_Sensitivity(sensitivities, r, hellingers, t):
-	score = 0.0
-	for i in range(len(sensitivities)):
[…]

### 2018-08-01 dp_bayesian_inference_model_with_dirichlet_prior.py

@@ -1,585 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-import time
-from matplotlib.patches import Polygon
-
-
-def L1_Nrom(A, B):
-	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
-
-def multibeta_function(alphas):
-	numerator = 1.0
-	denominator = 0.0
-	for alpha in alphas:
-		numerator = numerator * math.gamma(alpha)
-		denominator = denominator + alpha
-	# print numerator / math.gamma(denominator)
-	return numerator / math.gamma(denominator)
-
-def optimized_multibeta_function(alphas):
-	denominator = -1.0
-	nominators = []
-	denominators = []
-	r = 1.0
-	for alpha in alphas:
-		denominator = denominator + alpha
-	for alpha in alphas:
-		temp = alpha - 1
-		while temp > 0.0:
-			nominators.append(temp)
-			temp -=1.0
-		if temp < 0.0:
-			nominators.append(math.gamma(1 + temp))
-	while denominator > 0.0:
-		denominators.append(denominator)
-		denominator -= 1.0
-	if denominator < 0.0:
-		denominators.append(math.gamma(1.0 + denominator))
-
-	denominators.sort()
-	nominators.sort()
-	# print nominators
-	# print denominators
-	d_pointer = len(denominators) - 1
-	n_pointer = len(nominators) - 1
-	while d_pointer >= 0 and n_pointer >= 0:
-		# print nominators[n_pointer],denominators[d_pointer]
-		r *= nominators[n_pointer] / denominators[d_pointer]
-		n_pointer -= 1
-		d_pointer -= 1
-	while d_pointer >= 0:
-		# print n_pointer,denominators[d_pointer]
-		r *= 1.0 / denominators[d_pointer]
-		d_pointer -= 1
-	while n_pointer >= 0:
-		# print nominators[n_pointer] ,d_pointer
-		r *= nominators[n_pointer] 
-		n_pointer -= 1
-	return r
-
-def Hellinger_Distance_Dir(Dir1, Dir2):
-	return math.sqrt(1 - multibeta_function((numpy.array(Dir1._alphas) + numpy.array(Dir2._alphas)) / 2.0)/ \
[…]

### 2018-08-01 dp_bayesian_inference_model_with_dirichlet_prior_accuracy_study.py

@@ -1,735 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-import time
-from matplotlib.patches import Polygon
-from scipy.special import gammaln
-
-def gen_betaln (alphas):
-        numerator=0.0
-        for alpha in alphas:
-	        numerator = numerator + gammaln(alpha)
-                
-        return(numerator/math.log(float(sum(alphas))))
-
-
-def opt_hellinger2(alphas, betas):
-        z=gen_betaln(numpy.divide(numpy.sum([alphas, betas], axis=0), 2.0))-0.5*(gen_betaln(alphas) + gen_betaln(betas))
-        return (math.sqrt(1-math.exp(z)))
-
-
-def L1_Nrom(A, B):
-	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
-
-def multibeta_function(alphas):
-	numerator = 1.0
-	denominator = 0.0
-	for alpha in alphas:
-		numerator = numerator * math.gamma(alpha)
-		denominator = denominator + alpha
-	# print numerator / math.gamma(denominator)
-	return numerator / math.gamma(denominator)
-
-def optimized_multibeta_function(alphas):
-	denominator = -1.0
-	nominators = []
-	denominators = []
-	r = 1.0
-	for alpha in alphas:
-		denominator = denominator + alpha
-	for alpha in alphas:
-		temp = alpha - 1
-		while temp > 0.0:
-			nominators.append(temp)
-			temp -=1.0
-		if temp < 0.0:
-			nominators.append(math.gamma(1 + temp))
-	while denominator > 0.0:
-		denominators.append(denominator)
-		denominator -= 1.0
-	if denominator < 0.0:
-		denominators.append(math.gamma(1.0 + denominator))
-
-	denominators.sort()
-	nominators.sort()
-	# print nominators
-	# print denominators
-	d_pointer = len(denominators) - 1
-	n_pointer = len(nominators) - 1
-	while d_pointer >= 0 and n_pointer >= 0:
-		# print nominators[n_pointer],denominators[d_pointer]
-		r *= nominators[n_pointer] / denominators[d_pointer]
-		n_pointer -= 1
-		d_pointer -= 1
[…]

### 2018-08-01 dp_bayesian_inference_model_with_dirichlet_prior_epsilon_study.py

@@ -1,1100 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-import time
-from matplotlib.patches import Polygon
-import statistics
-from decimal import *
-from scipy.special import gammaln
-
-def gen_betaln (alphas):
-        numerator=0.0
-        for alpha in alphas:
-	        numerator = numerator + gammaln(alpha)
-                
-        return(numerator/math.log(float(sum(alphas))))
-
-
-def opt_hellinger2(alphas, betas):
-        z=gen_betaln(numpy.divide(numpy.sum([alphas, betas], axis=0), 2.0))-0.5*(gen_betaln(alphas) + gen_betaln(betas))
-        return (math.sqrt(1-math.exp(z)))
-
-
-
-def L1_Nrom(A, B):
-	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
-
-def multibeta_function(alphas):
-	numerator = 1.0
-	denominator = 0.0
-	for alpha in alphas:
-		numerator = numerator * math.gamma(alpha)
-		denominator = denominator + alpha
-	# print numerator / math.gamma(denominator)
-	return numerator / math.gamma(denominator)
-
-def optimized_multibeta_function(alphas):
-	denominator = -1.0
-	nominators = []
-	denominators = []
-	r = 1.0
-	for alpha in alphas:
-		denominator = denominator + alpha
-	for alpha in alphas:
-		# print alpha
-		temp = alpha - 1
-		while temp > 0.0:
-			nominators.append(temp)
-			temp -=1.0
-		
-		if temp < 0.0 and temp > -1.0:
-			#print temp
-			nominators.append(math.gamma(1 + temp))
-	while denominator > 0.0:
-		denominators.append(denominator)
-		denominator -= 1.0
-	if denominator < 0.0 and denominator > -1.0:
-		denominators.append(math.gamma(1.0 + denominator))
-
-	denominators.sort()
-	nominators.sort()
-	# print nominators
-	# print denominators
-	d_pointer = len(denominators) - 1
-	n_pointer = len(nominators) - 1
-	while d_pointer >= 0 and n_pointer >= 0:
[…]

### 2018-08-03 main-sketch.tex
rename and update github
fixed formula

@@
   \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\},
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
 \end{equation}
-where $d$ is the Hamming distance between two datasets, $\gamma =
+where $d$ is the $\frac{1}{2}\cdot \ell_1$ distance between two datasets,
+$C$ takes a datasets and maps it to its histogram,
+$\gamma =
 \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
@@
 \centering
-  \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
-    \label{subsubsec_vs_datasize1adir}
-  }
+  % \subfigure[Data set size from $300$ to $800$ ]{
+  %   \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
+  %   \label{subsubsec_vs_datasize1adir}
+  % }
   \subfigure[Data set size from $14000$ to $20000$]{
      \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
-  \label{subsubsec_vs_datasize1bdir}} 
+  \label{subsubsec_vs_datasize1bdir}
+  } 
 \caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}

### 2018-08-03 main-sketch.tex
fixed formula

@@
 \end{equation}
-where $d$ is the $\frac{1}{2}\cdot \ell_1$ distance between two datasets,
+where $d$ is the $\frac{1}{2}\cdot \ell_1$ distance between two histograms,
 $C$ takes a datasets and maps it to its histogram,

### 2018-08-16 codes/dpbayesinfer.py
re-organize

@@ -118,7 +118,6 @@ class BayesInferwithDirPrior(object):
 		for r in self._candidates:
 			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._SS))
 			self._SS_probabilities.append(temp)
-
 			nomalizer += temp
 
 		for i in range(len(self._SS_probabilities)):
@@ -228,20 +227,19 @@ class BayesInferwithDirPrior(object):
 		noised_alphas = []
 		rest = self._sample_size
 		for i in range(self._prior._size - 1):
-			alpha = self._posterior._alphas[i]
-			temp = math.floor(numpy.random.laplace(0, 2.0/self._epsilon))
-			if temp < - self._observation_counts[i]:
+			t = self._observation_counts[i] + math.floor(numpy.random.laplace(0, 2.0/self._epsilon))
+			if t < 0:
 				noised_alphas.append(0)
 				rest -= 0
-			elif (self._observation_counts[i] + temp) > rest:
+			elif t > rest:
 				noised_alphas.append(rest)
 				rest -= rest
 				for j in range(i+1,self._prior._size - 1):
 					noised_alphas.append(0)
 				break
 			else:
-				noised_alphas.append((self._observation_counts[i] + temp))
-				rest -= (self._observation_counts[i] + temp)
+				noised_alphas.append(t)
+				rest -= t
 		noised_alphas.append(rest)
 		self._laplaced_posterior = dirichlet(noised_alphas) + self._prior
 
@@ -250,13 +248,17 @@ class BayesInferwithDirPrior(object):
 
 		self._laplaced_posterior = dirichlet([alpha + math.floor(numpy.random.laplace(0, 1.0/self._epsilon)) for alpha in self._posterior._alphas])
 
+	def _laplace_fourier(self):
+		
+		
+		return
 
 	def _laplace_noize_navie(self):
 		t = numpy.random.laplace(0, 1.0/self._epsilon)
 		self._laplaced_posterior = dirichlet([self._posterior._alphas[0] + t, self._posterior._alphas[0] - t])
 
 	def _laplace_noize_zhang(self):
-		noised = [i + numpy.random.laplace(0, 2.0/self._epsilon) for i in self._posterior._alphas]
+		noised = [i + numpy.random.laplace(0, 2.0/self._epsilon) for i in self._observation_counts]
 		noised = [self._sample_size if i > self._sample_size else i for i in noised]
[…]

### 2018-08-16 codes/main.py

@@ -532,7 +532,7 @@ if __name__ == "__main__":
 	x1 = [1,499]
 	x2 = [0,500]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((200,500),10)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = gen_datasizes((10000,20000),10000)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.3,0.3,0.4]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([4*i,4*i,4*i]) for i in range(5,20)]

### 2018-08-16 dpbayesinfer.py

@@ -1,403 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-import time
-from matplotlib.patches import Polygon
-import statistics
-from decimal import *
-from dirichlet import dirichlet
-from scipy.special import gammaln
-
-
-def Hamming_Distance(c1, c2):
-	temp = [abs(a - b) for a,b in zip(c1,c2)]
-	return sum(temp)/2
-
-
-class BayesInferwithDirPrior(object):
-	def __init__(self, prior, sample_size, epsilon, delta):
-		self._prior = prior
-		self._sample_size = sample_size
-		self._epsilon = epsilon
-		self._delta = delta
-		self._bias = numpy.random.dirichlet(self._prior._alphas)
-		self._observation = numpy.random.multinomial(1, self._bias, self._sample_size)
-		self._observation_counts = numpy.sum(self._observation, 0)
-		self._posterior = dirichlet(self._observation_counts) + self._prior
-		self._laplaced_posterior = self._posterior
-		self._laplaced_zhang_posterior = self._posterior
-		self._exponential_posterior = self._posterior
-		self._SS_posterior = self._posterior
-		self._candidate_scores = {}
-		self._candidates = []
-		self._LS_probabilities = []
-		self._GS_probabilities = []
-		self._SS_probabilities = []
-		self._GS = 0.0
-		self._LS_Candidates = {}
-		self._VS = {}
-		self._SS = {}
-		self._LS = 0.0
-		self._SS = 0.0
-		# self._SS_Expon = 0.0
-		# self._SS_Laplace = 0.0
-		self._candidate_VS_scores = {}
-		#self._keys = ["Laplace Mechanism | Achieving" + str(self._epsilon) + "-DP"]
-		self._keys = ["LaplaceMech"]
-		self._accuracy = {self._keys[0]:[]}
-		self._accuracy_l1 = {self._keys[0]:[]}
-		self._accuracy_mean = {}
-	
-	def _set_bias(self, bias):
-		self._bias = bias
-		self._update_observation()
-
-	def _set_observation(self,observation):
-		self._observation_counts = observation
-		self._posterior = dirichlet(observation) + self._prior
-
[…]

### 2018-08-16 sensitivity-codes/TV_Sensitivity.py

@@ -1,72 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator, FormatStrFormatter
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from mpl_toolkits.mplot3d import Axes3D
-
-def beta_function(alpha, beta):
-	return 1.0 * math.gamma(alpha) * math.gamma(beta)/math.gamma(alpha + beta)
-
-def Hellinger_Distance(beta1, beta2):
-	return math.sqrt(1 - beta_function((beta1[0] + beta2[0])/2.0, (beta1[1] + beta2[1])/2.0) \
-		/ math.sqrt(beta_function(beta1[0], beta1[1]) * beta_function(beta2[0], beta2[1])))
-
-class Beta_Distribution(object):
-	def __init__(self, alpha, beta):
-		self._alpha = alpha
-		self._beta = beta
-
-	def __sub__(self, other):
-		return math.sqrt(1 - beta_function((self._alpha + other._alpha)/2.0, (self._beta + other._beta)/2.0) \
-			/ math.sqrt(beta_function(self._alpha, self._beta) * beta_function(other._alpha, other._beta)))
-
-	def show(self):
-		print "Beta(" + str(self._alpha) + ", " + str(self._beta) + ")"
-
-
-
-
-def generate_sensitivities():
-	sensitivities = []
-	for i in range(1, 81):
-		sensitivities.append([])
-		for j in range(1, 81):
-			sensitivities[i - 1].append(Beta_Distribution(i + 1, j) - Beta_Distribution(i, j + 1))
-			# print sensitivities[i - 1][j - 1]
-	return sensitivities
-
-
-if __name__ == "__main__":
-
-	sensitivities = generate_sensitivities()
-
-	fig = plt.figure()
-	ax = fig.gca(projection='3d')
-	# x = numpy.arange(1, 81, 1)
-	# y = numpy.arange(1, 81, 1)
-	# x, y = numpy.meshgrid(x,y)
-	x = []
-	y = []
-	z = []
-	for i in range(1, 81):
-		x = x + [i] * 80
-		y = y + range(1, 81)
-		z = z + sensitivities[i - 1]
-
[…]

### 2018-08-16 sensitivity-codes/dirichlet.py

@@ -1,154 +1,0 @@
-import numpy
-import matplotlib.pyplot as plt
-from copy import deepcopy
-import random
-import math
-import scipy
-from scipy.stats import beta
-from fractions import Fraction
-import operator
-import time
-from matplotlib.patches import Polygon
-import statistics
-from decimal import *
-from scipy.special import gammaln
-
-
-def gen_betaln (alphas):
-	numerator=0.0
-	for alpha in alphas:
-		numerator = numerator + gammaln(alpha)
-	return(numerator/math.log(float(sum(alphas))))
-
-
-def opt_hellinger(dirichlet1, dirichlet2):
-	alphas = deepcopy(dirichlet1._alphas)
-	betas = deepcopy(dirichlet2._alphas)
-	z=gen_betaln(numpy.divide(numpy.sum([alphas, betas], axis=0), 2.0))-0.5*(gen_betaln(alphas) + gen_betaln(betas))
-	return (math.sqrt(1-math.exp(z)))
-
-
-
-def L1_Nrom(A, B):
-	return numpy.sum(abs(numpy.array(A._alphas) - numpy.array(B._alphas)))
-
-# def multibeta_function(alphas):
-# 	numerator = 1.0
-# 	denominator = 0.0
-# 	for alpha in alphas:
-# 		numerator = numerator * math.gamma(alpha)
-# 		denominator = denominator + alpha
-# 	# print numerator / math.gamma(denominator)
-# 	return numerator / math.gamma(denominator)
-
-# def optimized_multibeta_function(alphas):
-# 	denominator = -1.0
-# 	nominators = []
-# 	denominators = []
-# 	r = 1.0
-# 	for alpha in alphas:
-# 		denominator = denominator + alpha
-# 	for alpha in alphas:
-# 		# print alpha
-# 		temp = alpha - 1
-# 		while temp > 0.0:
-# 			nominators.append(temp)
-# 			temp -=1.0
-		
-# 		if temp < 0.0 and temp > -1.0:
-# 			#print temp
-# 			nominators.append(math.gamma(1 + temp))
-# 	while denominator > 0.0:
-# 		denominators.append(denominator)
-# 		denominator -= 1.0
-# 	if denominator < 0.0 and denominator > -1.0:
-# 		denominators.append(math.gamma(1.0 + denominator))
-
-# 	denominators.sort()
-# 	nominators.sort()
-# 	# print nominators
[…]

### 2018-08-30 paper/main.tex
rename

--- 2018-07-24 main-fullversion.tex
@@
 
-\subsection{Experimental Evaluations on Accuracy}
-\label{subsec_experiment_accuracy}
+% \subsection{Experimental Evaluations on Accuracy}
+% \label{subsec_experiment_accuracy}
 
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
-  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-    \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
-\label{fig_beta_hellinger}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
-  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
-    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
-\label{fig_dirichlet_hellinger}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[accuracy measurement based on Hellinger distance]{
-    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
-  \subfigure[accuracy measurement based on $l_1$ norm]{
-    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
-\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
-\label{fig_dirichlet_hellinger_l1}
-\end{center}
-\end{figure*}
-
-In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
 % \begin{figure*}
@@
 % \centering
+%   \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
+%     \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
 %   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
-%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
-%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
-% \caption{The experimental results of accuracy of four algorithms}
-% \label{fig_data}
+%     \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
+% \caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
+% \label{fig_beta_hellinger}
 % \end{center}
@@
 
-We first analyzed the accuracy based on the Hellinger distance.
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
+%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
+%   \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
+%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
+% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
+% \label{fig_dirichlet_hellinger}
+% \end{center}
+% \end{figure*}
+
+% \begin{figure*}
+% \begin{center}
+% \centering
+%   \subfigure[accuracy measurement based on Hellinger distance]{
+%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
+%   \subfigure[accuracy measurement based on $l_1$ norm]{
+%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
+% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
+% \label{fig_dirichlet_hellinger_l1}
+% \end{center}
+% \end{figure*}
+
+% In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
+% % \begin{figure*}
+% % \begin{center}
+% % \centering
+% %   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
+% %     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
+% %   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
+% %     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
+% % \caption{The experimental results of accuracy of four algorithms}
+% % \label{fig_data}
+% % \end{center}
+% % \end{figure*}
+
+% We first analyzed the accuracy based on the Hellinger distance.
 By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
@@
 
-When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
+% When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
 \ref{fig_beta_hellinger}.
@@
 
-To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
+% To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
 
-Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
+% Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
 \ref{fig_dirichlet_hellinger_l1}.
 
-The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
+% The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
 
-In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
-\begin{enumerate}
-	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
+% In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
+% \begin{enumerate}
+% 	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
 Both of the two exponential mechanisms are do much better than it with global sensitivity.
-	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
-\end{enumerate}
+% 	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
+% \end{enumerate}
 
-In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.
+% In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
 \begin{center}
 \centering
-  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
-    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
-  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
-    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
-\caption{Balanced datasets}
+  \subfigure[Data set size from $300$ to $800$ ]{
+    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
+    \label{subsubsec_vs_datasize1a}
+  }
+  \subfigure[Data set size from $14000$ to $20000$]{
+    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
+  \label{subsubsec_vs_datasize1b}} 
+\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}
@@
 
-In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
-This means that in the Beta-Binomial setting the datasets will be
-half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
-equally split in all the $k=3$ bins. Figure \ref{fig_vs_datasize} shows that  when the
-data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
-decreases. In Figure \ref{fig_vs_datasize}(a), when the data size is
-smaller than 12, $\hexpmech$ can outperform the Laplace mechanism but it fails to do so
-for bigger datasets. The same happens in as in Figure \ref{fig_vs_datasize}(b):
-the Laplace mechanism starts performing better for datasets bigger than 15.
-
-\subsubsection{Accuracy Evaluation wrt. Dimensions}
-\label{subsubsec_vs_dimension}
-
-In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
-different sizes and different dimensions. The plot shows that increasing the number of dimensions have
-a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
-mechanism. Fixing the number of dimensions and increasing the data size shows that
-the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
-In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
-mechanism.
 \begin{figure}[ht]
+\begin{center}
 \centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
-\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
-\label{fig_vs_dimension}
+  % \subfigure[Data set size from $300$ to $800$ ]{
+  %   \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
+  %   \label{subsubsec_vs_datasize1adir}
+  % }
+  \subfigure[Data set size from $14000$ to $20000$]{
+     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
+  \label{subsubsec_vs_datasize1bdir}
+  } 
+\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_dir}
+\end{center}
 \end{figure}
 
-\subsubsection{Accuracy Evaluation wrt. Data variance}
-\label{subsubsec_vs_variance}
+In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
+of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
+and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
+the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
+The results show that when the data size
+increases, the average errors of
+$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
+i.e with size less 650 in the case of Beta-Binomial systems,
+the Laplace mechanisms outperforms the exponential mechanisms,
+but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
+we considered data sets of the order of 15 thousands elements,
+the exponential mechanisms outperforms the Laplace mechanism.
+Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
+but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
+too high run time of the algorithm.
 
-In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
-of balance of the datasets. We  study this variable only under
-two-dimensions $\betad$ distribution in order to be more concise. The plot shows
-that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
+% \subsubsection{Accuracy Evaluation wrt. Data variance}
+% \label{subsubsec_vs_variance}
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
-\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
-\label{fig_vs_variance}
-\end{figure}
+% In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
+% of balance of the datasets. We  study this variable only under
+% two-dimensions $\betad$ distribution in order to be more concise. The plot shows
+% that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
+
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
+% \caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
+% \label{fig_vs_variance}
+% \end{figure}
 

### 2018-09-26 paper/main.tex
update main
update main.tex

@@
 
-\settopmatter{printacmref=false, printccs=true, printfolios=true}
+\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
+
+%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
 \input{macros}
-
-\title{\textbf{Notes of DP - Bayesian Inference}\\}
-% \author{Jiawen \textsc{Liu}}
-\date{\vspace{-10ex}}
+\usepackage{accents}
 
 \begin{document}
+\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
+
+\begin{abstract} Bayesian inference is a statistical method which
+allows one to derive a \emph{posterior} distribution,
+starting from a \emph{prior} distribution and observed data. Several
+approaches have been explored in order to make this process differentially
+private. For example, \citet{dimitrakakis2014robust}, and
+\citet{wang2015privacy} proved that, under specific conditions, sampling from
+the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
+designed differentially private mechanisms that output a
+representation of the full posterior distribution.
+
+When the output of a differentially private mechanism is a probability
+distribution, accuracy is naturally measured by means of
+\emph{probabilistic distances} measuring how far this distribution is
+from the original one. Some classical examples are total variation distance,
+Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
+
+In this work, we design a mechanism for
+bayesian inference exploring the idea of calibrating noise using the
+same probabilistic distance we want to measure accuracy with. 
+We focus on two discrete models, the Beta-Binomial and the
+Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
+Our mechanism can be understood as a version of  the exponential mechanism
+where the noise is calibrated to the smooth sensitivity of the
+utility function, rather than to its global sensitivity. In our
+setting, the utility function is the probability distance we want to
+use to measure accuracy. To show the usefulness of this mechanism we
+show an experimental analysis comparing it with an approach based on
+the Laplace mechanism.
+\end{abstract}
+
+% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
+% \begin{CCSXML}
+% <ccs2012>
+% <concept>
+% <concept_id>10002978.10003029.10011703</concept_id>
+% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
+% <concept_significance>500</concept_significance>
+% </concept>
+% </ccs2012>
+% \end{CCSXML}
+
+% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
+% % -- end of section to replace with generated code
+
+\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
+
 \maketitle
 
-\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
-\label{sec_bayesInfer}
-In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$.
-Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$.
-The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
-\begin{equation*}
-Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
-\end{equation*}
-It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$.
-For conciseness, when prior is given, we use $\bysinfer(x)$.
-$n$ is the size of the observed data size.
+\section{An informal motivation}
+\label{sec_intro}
+Publishing the posterior distribution inferred from a sensitive dataset can
+leak information about the individuals in the dataset.
+In order to guarantee differential privacy and to protect the
+individuals' data we can add noise to the posterior before releasing it.
+The amount of the noise that we need to  introduced
+depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
+small changes in the data set. 
+Sensitivity can be computed in many different ways based on which metric space
+we consider on the output set of the mechanism. In the literature on private Bayesian
+inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
+respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
+A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
+A re-loved question is that of how to measure accuracy. Again,
+this can be answered in different ways based on the metric imposed on the output space, and yet again
+only in few works in literature (e.g. \cite{zhang2016differential})
+distances between probability measures have been used for these purposes.
 
-In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, where $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$.
-$m$ is the order of the Dirichlet distribution.
+The question that this work aims at answering is whether
+an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
+the numeric parameters of the distributions. 
+We will see that in some cases this can happen.
 
-We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice.
-We want to infer the probability of getting each side $\xis$.
-We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time.
-The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.
+\section{Bayesian Inference Background}
+\label{sec_background}
+Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
+and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
+\[
+  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+\]
+where the expression $\Pr(\dataobs | \theta)$ denotes the
+\emph{likelihood} of observing $\dataobs$ under a value of
+$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
+a function of $\theta$.
+For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
+Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
+the initial belief on $\theta$, that is, when no data has been observed. In practice though,
+prior distributions and likelihood functions are usually chosen so that the posterior
+belongs to the same \emph{family} of distributions. In this case we say that the prior
+is conjugate to the likelihood function. Use of a conjugate prior
+simplifies calculations and allows for inference to be performed in a
+recursive fashion over the data.
+In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
+Specifically, we will consider the situation where $\theta$ represents
+the parameter --informally called \emph{bias}-- of a Bernoulli
+distributed random variable, and its immediate generalization where
+the parameter $\vtheta$ represents the vector of parameters of a
+categorically distributed random variable.  In the former case, the
+prior distribution over $\theta\in [0,1]$ is going to be a beta
+distribution, $\betad(\alpha, \beta)$, with parameters
+$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
 
-In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$.
-The $m$ side dice change into a irregular coin with side $A$ and side $B$.
-The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.
+\[
+  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
+\]
+where $\betaf(\cdot,\cdot)$ is the beta function.
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
+\[
+  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
+\]
+where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
+From this it can easily be derived that the posterior distribution is:
+\[
+  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
+\]
+In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
+is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
+and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
+\[
+  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
+\]
+where $\mbetaf(\cdot)$ is the generalized beta function.
+The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
+coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
+The likelihood function will be:
+\[
+  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
+\]
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
+Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
+\[
+  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
+\]
+where $+$ denotes the componentwise sum of vectors of reals.
+
+\section{The Problem Statement}
+\label{sec:base}
+We are interested in designing a mechanism for privately releasing the full posterior
+distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
+It's worth noticing that the posterior distributions are fully characterized
+by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
+Beta-Binomial model we are interested in releasing a private version of the pair of
+parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
+in the case of the Dirichlet-Multinomial model we are interested in a private version of
+$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
+have already attacked this problem by adding independent Laplacian noise to the
+parameters of the posteriors. That is, in the case of the Beta-Binomial system,
+the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
+where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
+and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+This mechanism is $\epsilon$-differentially private, and the noise is
+calibrated w.r.t. to a sensitivity of 2 which is derived by using
+$\ell_1$ norm over the pair of parameters. Indeed, considering two
+adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
+$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
+distributions, characterized by the pairs
+$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
+$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
+This argument extends similarly to the Dirichelet-Multinomial system.
+
+\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
+\[
+  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
+\]
+where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
+In this work we will use a metric based on a different norm to compute the sensitivity
+and provide guarantees on the accuracy. In particular we will consider a metric
+over probability measures and not over the parameters that represent them.
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
+Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
+calculations in the case of the probabilistic models considered here
+and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
+an unbounded adversary can have in distingishing two distributions. 
+Given two beta distributions
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
+\[
+  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
+  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+\]
+The same change of metric will be applied to the experimental accuracy guarantees.
 
@@
 For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.
+
+\subsection{Baseline Approach - Laplace Mechanism}
+\label{subsec_lap}
 
@@
 \textbf{Detail proof:}
+
+	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
 \begin{itemize}
-
 	\item $\lambda < 0$
@@
 		\begin{equation*}
+		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
 		\end{equation*}
+		is always true when $\lambda < 0$
 	\item $\lambda > 0$
@@
 
-\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
+\subsection{Accuracy Analysis Comparing with Laplace mechanism}
 \label{subsec_accuracy_tradeoff}
@@
 \end{itemize}
-
 \subsubsection{Accuracy Analysis wrt. prior distribution}
-In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig.
-\ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.
 
@@
 \includegraphics[width=0.48\textwidth]{sensitivity}
+\caption{Hellinger distance study}
 \label{fig_sensitivity}
-\caption{Hellinger distance study}
 \end{figure}
+In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig.
+\ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.
 
@@
 
-% \subsection{Experimental Evaluations on Accuracy}
-% \label{subsec_experiment_accuracy}
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
-%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
-% \caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
-% \label{fig_beta_hellinger}
-% \end{center}
-% \end{figure*}
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
-%   \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
-% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
-% \label{fig_dirichlet_hellinger}
-% \end{center}
-% \end{figure*}
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
-%   \subfigure[accuracy measurement based on $l_1$ norm]{
-%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
-% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
-% \label{fig_dirichlet_hellinger_l1}
-% \end{center}
-% \end{figure*}
-
-% In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
-% % \begin{figure*}
-% % \begin{center}
-% % \centering
-% %   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
-% %     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
-% %   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
-% %     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
-% % \caption{The experimental results of accuracy of four algorithms}
-% % \label{fig_data}
-% % \end{center}
-% % \end{figure*}
-
-% We first analyzed the accuracy based on the Hellinger distance.
-By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig.
-\ref{fig_beta_hellinger} and Fig.
-\ref{fig_dirichlet_hellinger}.
-X-axis is labeled with different mechanisms.
-We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''.
-Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.
-
-% When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig.
-\ref{fig_beta_hellinger}.
-It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.
-
-% To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
-
-% Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig.
-\ref{fig_dirichlet_hellinger_l1}.
-
-% The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.
-
-% In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
-% \begin{enumerate}
-% 	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity.
-Both of the two exponential mechanisms are do much better than it with global sensitivity.
-% 	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
-% \end{enumerate}
-
-% In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.
-
-% \subsubsection{Experiment Analysis}
-% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism.
-By computing the two mechanisms' discrete probabilities wrt.
-steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig.
-\ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.
-
-% Subfigs (a) based on Sec.
-\ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times.
-The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance.
-Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt.
-the steps.
-The x-axis is the Hellinger distance from correct answer, i.e.
-steps from correct answer.
-Since they have the same meaning, we just use the Hellinger distance to label the x-axis here.
-The y-axis is the probability of output candidates with corresponding steps (i.e.
-Hellinger distance) from correct answer.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_50_50}
-% \end{center}
-% \end{figure*}
-
-% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig.
-\ref{fig_theory_50_50}.
-In Subfig.
-\ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism.
-In the mean time, the theory calculation results in Subfig.
-\ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$).
-SubFig.
-\ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism.
-Meanwhile, the SubFig.
-\ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers.
-The advantage is not significant.
-So, we increase the data size and the dimension in next case to have a further study.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_20_20_20_20}
-% \end{center}
-% \end{figure*}
-
-% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig.
-\ref{fig_theory_20_20_20_20}.
-Subfig.
-\ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously.
-Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism.
-The advantage in the SubFig.
-\ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig.
-\ref{fig_theory_20_20_20_20}(b).
-So, we change the variance of the observed data set in the next case.
-
-% \begin{figure*}
-% \begin{center}
-% \centering
-%   \subfigure[accuracy measurement based on Hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
-%   \subfigure[discrete probabilities wrt. hellinger distance]{
-%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
-% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
-% \label{fig_theory_1_1_1_77}
-% \end{center}
-% \end{figure*}
-
-% In Fig.
-\ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities.
-This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b).
-In Subfig.
-\ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms.
-Also, in Subfig.
-\ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
-Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.
-
-% From the theory and experimental analysis above, we obtained some conclusions
-% \begin{enumerate}
-% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.
-
-% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.
-
-% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
-% \end{enumerate}
-
 \subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
 \label{subsec_vs_variables}
+In this section, we evaluate the accuracy of the mechanisms defined in
+Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
+data variance, prior distribution, and some combinations thereof.
+Every plot is an average over 1000 runs. In all the experiments we set
+$\epsilon = 0.8$, and $\delta = 10^{-8}$.
 
-In this section, we evaluate the accuracy wrt.
-four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables.
-We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable.
-In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables.
-The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.
+\noindent In the following some of the plots show
+mean error as a function of the datasize while one
+is a whiskers-plot where the y-axis shows the average
+accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
+different balanced priors used. The boxes extend from the lower to the upper quartile values
+of the data, with a line at the median. A notch on the box around the
+median is also drawn to give a rough guide to the significance of
+difference of medians; The whiskers extend from the box to show the
+range of the data. A blue box in the plots represents our newly
+designed exponential mechanism's behavior-- where the sensitivity is calibrated
+w.r.t Hellinger distance-- while the yellow box next to
+it represents the performance of a variation of the basic Laplace
+mechanism presented in Section (\ref{sec:base}) with the same
+settings: that is $\epsilon, \delta$, data, prior. The variation
+considered performs a postprocessing on the released parameters so
+that they are consistent. For instance when the sum of the noised
+parameters is greater than $n$ we will truncate them so that they sum
+up to $n$.
 
-\subsubsection{Accuracy Evaluation wrt. Datasize}
+\paragraph{Increasing data size with balanced datasets}
 \label{subsubsec_vs_datasize}
@@
 
-% \subsubsection{Accuracy Evaluation wrt. Data variance}
-% \label{subsubsec_vs_variance}
-
-% In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
-% of balance of the datasets. We  study this variable only under
-% two-dimensions $\betad$ distribution in order to be more concise. The plot shows
-% that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.
-
-% \begin{figure}[ht]
-% \centering
-% \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
-% \caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
-% \label{fig_vs_variance}
-% \end{figure}
-
-\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
+\paragraph{Fixed dataset varying balanced priors}
 \label{subsubsec_vs_prior}
@@
 it is outperformed after a while.
-\begin{figure}[ht]
+\begin{figure}[H]
 \centering
 \includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
-\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
+\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
 \label{fig_vs_prior}
 \end{figure}
-
-% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
-% \label{subsubsec_vs_prior_variance}
-
-% \begin{figure}[ht]
-% \centering
-% \includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean.eps}
-% \caption{Accuracy measurement based on Hellinger distance wrt.
-different prior distribution and data variances.
-Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
-% \label{fig_vs_prior_variance}
-% \end{figure}
-
-% Here, we change the prior distribution and data variance in the same time.
-As shown in Fig.
-\ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary.
-Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.
 

### 2018-09-26 codes/main.py

@@ -352,7 +352,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	for observation in observations:
 		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
 		Bayesian_Model._set_observation(observation)
-		Bayesian_Model._experiments(1000)
+		Bayesian_Model._experiments(5000)
 		mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
 		mean_error[1].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[0]])
 		mean_error[2].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[4]])
@@ -532,7 +532,7 @@ if __name__ == "__main__":
 	x1 = [1,499]
 	x2 = [0,500]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((200,500),20)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = gen_datasizes((100,500),20)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.3,0.3,0.3]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([4*i,4*i,4*i]) for i in range(5,20)]

### 2018-09-26 paper/main.tex
update main tex

@@
 \label{sec_setup}
-For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
 
-\subsection{Baseline Approach - Laplace Mechanism}
+\[
+  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
+\]
+
+where $\Delta\alpha$ is as defined in Section
+\ref{sec_background}. Notice that $\betaset$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\betaset$
+that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
+parametrize the result by the prior, which from now on we consider
+fixed and we denote it by $\bprior$.
+
+\subsection{Baseline Approach}
+
+\subsubsection{Laplace Mechanism}
 \label{subsec_lap}
 
-\subsection{Exponential Mechanism with Global Sensitivity}
+\subsubsection{Exponential Mechanism}
 \label{subsec_emgs}
@@
 
-In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
+Exponential mechanism $\expmech{}{x}$ samples a element from the candidate set $\betaset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
 \begin{equation*}
-\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
+\underset{z \thicksim \expmech{}{x}}{Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 GS(x)})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
+\end{equation*}
+where $u(x,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS(x)$ is the global sensitivity calculated by:
+\begin{equation*}
+GS = 
+\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
+|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
 \end{equation*}
 
-Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
-\begin{equation}
-\label{equ_utility}
-u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
-\end{equation}
-
-Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
-\begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
-\end{equation*}
-where global sensitivity is calculated by:
-\begin{equation*}
-\Delta_{g}u = 
-\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
-|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
-\end{equation*}
-
-The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
 
@@
 
-\subsection{Exponential Mechanism with Local Sensitivity}
+\subsubsection{Exponential Mechanism with Local Sensitivity}
 \label{subsec_emls}
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
+Exponential mechanism with local sensitivity $\expmech{local}{x}$ share the same candidate set and utility function as it with global sensitivity.
+This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
 \begin{equation*}
-P[r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
+\underset{z \thicksim \expmech{local}{x}}{\Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
 \end{equation*}
@@
 \begin{equation*}
-\Delta_{l}u(x) = 
-\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
-\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
 \end{equation*}
 
-The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.
+The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
 
-\subsection{Exponential Mechanism with Smooth Sensitivity}
+\subsection{Our Approach - Exponential Mechanism with Smooth Sensitivity}
 \label{sec_smoo}
 
-\subsubsection{Algorithm Setting up}
-We define a new mechanism $\hexpmech(x)$
-which is similar to the exponential mechanism where we use
-$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
-summing up to $n+2$, as scoring function we use the Hellinger distance
-from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
-calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
-only difference is in the sensitivity part, since now we use the
-smooth sensitivity.
+\subsubsection{Setting up}
 
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
-{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
-{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
+{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
-where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
-\begin{equation*}
-S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
-\end{equation*}
+where $S_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
+
+\begin{equation}
+  \label{eq:smooth}
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
+\end{equation}
 where $d$ is the Hamming distance between two datasets, and $\beta =
@@
 
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
- $r\in\betaset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\betaset$ we have:
-$$
-\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]\Big )
-$$
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
-We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
-It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-This parameter can be eliminate in both sides in proof.
+This mechanism is based on the basic exponential mechanism
+\cite{talwar}, with $\betaset$ as the range and
+$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
+that in this mechanism we don't calibrate the noise w.r.t. to the
+global sensitivity of the scoring function but w.r.t. to the smooth
+sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of
+$\hellinger(\bysinfer(\dataobs), \cdot)$.
 
-In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
+be determined later, and where $LS(\dataobs')$ denotes the local
+sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
+of the scoring function used in our mechanism.
+
+This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+\[
+  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+\]
+and by replacing the $\betaset$ with set of posterior Dirichlet
+distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
+over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
+that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+will denote by $\hexpmechd$ the mechanism for the
+Dirichlet-Multinomial system.
+
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
 
@@
 \begin{proof}
+
+In what follows, we will use a correspondence between the probability
+ $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
+ $r\in\betaset$ and the probability 
+ $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+ \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
+ $r\in\betaset$ we have:
+
+$$
+\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
+\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
+ \hlg(\bysinfer(x),r)]\Big )
+$$
+
+To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
+We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
+We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
+It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+This parameter can be eliminate in both sides in proof.
 

### 2018-09-26 codes/main.py

@@ -352,7 +352,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	for observation in observations:
 		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
 		Bayesian_Model._set_observation(observation)
-		Bayesian_Model._experiments(5000)
+		Bayesian_Model._experiments(500)
 		mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
 		mean_error[1].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[0]])
 		mean_error[2].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[4]])
@@ -366,7 +366,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 
 	plot_mean_error(range(0,len(observations)),mean_error,datasizes, 
 		 "Different Data sizes",
-		['Our ExpMech',"LapMech (sensitivity = 2)", "LapMech (sensitivity = 3)"],
+		['Our ExpMech',"LapMech (sensitivity = 2)", "LapMech (sensitivity = 4)"],
 		"Mean Error VS. Data Size")
 	# plot_error_box(data,"Different Datasizes",xstick,"Accuracy VS. Data Size")
 	return
@@ -527,13 +527,13 @@ if __name__ == "__main__":
 	datasize = 500
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1,1])
+	prior = dirichlet([1,1,1,1])
 	observation = [20,20]
 	x1 = [1,499]
 	x2 = [0,500]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((100,500),20)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
-	percentage = [0.3,0.3,0.3]
+	datasizes = gen_datasizes((100,300),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	percentage = [0.25,0.25,0.25,0.25]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([4*i,4*i,4*i]) for i in range(5,20)]
 	# accuracy_VS_dimension(sample_sizes, epsilon, delta)

### 2018-09-27 codes/main.py
update notes

@@ -535,7 +535,7 @@ if __name__ == "__main__":
 	x1 = [1,499]
 	x2 = [0,500]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((100,300),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = gen_datasizes((100,600),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.25,0.25,0.25,0.25]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([4*i,4*i,4*i]) for i in range(5,20)]

### 2018-10-06 poster/main.tex
update poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dreuw & Deselaer's Poster
% LaTeX Template
% Version 1.0 (11/04/13)
%
% Created by:
% Philippe Dreuw and Thomas Deselaers
% http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}

%\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color
\input{macros}

\usepackage[orientation=landscape,size=custom,width=101.6,height=76.2,scale=1.4]{beamerposter}
%\usepackage[orientation=portrait,size=a0,scale=1.4]{beamerposter} % Use the beamerposter package for laying out the poster with a portrait orientation and an a0 paper size
\usepackage{proof}
%\usetheme{Icy}
\usetheme{I6pd2} % Use the I6pd2 theme supplied with this template

\usepackage[english]{babel} % English language/hyphenation

\usepackage{amsmath,amsthm,amssymb,latexsym} % For including math equations, theorems, symbols, etc

%\usepackage{times}\usefonttheme{professionalfonts}  % Uncomment to use Times as the main font
%\usefonttheme[onlymath]{serif} % Uncomment to use a Serif font within math environments

\boldmath % Use bold for everything within the math environment

\usepackage{booktabs} % Top and bottom rules for tables

\graphicspath{{figures/}} % Location of the graphics files

\usecaptiontemplate{\small\structure{\insertcaptionname~\insertcaptionnumber: }\insertcaption} % A fix for figure numbering

\usepackage{stmaryrd}

%MACROS
\newcommand{\interp}[2]{\llbracket {#2} \rrbracket_{#1}}
\newcommand{\stmod}[1]{\mathfrak{M}[{#1}]}

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions} % Poster title

\author{Mark Bun$^\dag$,
%Imdea Software\\[-3mm]
%\texttt{gjbarthe@gmail.com} \\
%\And 
Gian Pietro Farina$^{*}$,
%University of Dundee\\[-3mm] 
%\texttt{g.p.farina@dundee.ac.uk} \\
%\And
Marco Gaboardi$^{*}$,
%University of Dundee\\[-3mm] 
%\texttt{m.gaboardi@dundee.ac.uk} \\
%\And
Jiawen Liu$^{*}$
%Imdea Software
%\texttt{pierre-yves@strub.nu} \\
}

\institute{$^\dag$Princeton University, $^{*}$University at Buffalo, SUNY} % Institution(s)

%----------------------------------------------------------------------------------------
%	FOOTER TEXT
%----------------------------------------------------------------------------------------

\newcommand{\leftfoot}{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions} % Left footer text

\newcommand{\rightfoot}{mbun@cs.princeton.edu, gaboardi@buffalo.edu} % Right footer text

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of two major columns, each of which can be subdivided further with another \begin{columns} block - the [t] argument aligns each column's content to the top

\begin{column}{.02\textwidth}\end{column} % Empty spacer column

\begin{column}{.465\textwidth} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{block}{Objectives}
\noindent Design a tool for differentially private probabilistic
programming featuring:
\begin{enumerate}
\item programming constructs to describe bayesian models and perform probabilistic inference,
\item programming constructs useful to ensure differential privacy,
\item type-checking as a method to ensure that the actual programs are
  differentially private.
\end{enumerate}

\end{block}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:

\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
\end{block}

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Differentially private Bayesian inference}
% We are interested in the 
% situation where: we have some  private data $\vec{x}$, some public data
% $\vec{y}$, a set of parameter $\theta$, and a public prior $p(\theta)$
% on $\theta$. We want to compute the public posterior distribution $p(\theta\
% |\ \vec{x}, \vec{y})$ in a differentially private way. This
% corresponds to make sure that
% for given values $\epsilon$ and $\delta$, and for every $\vec{x}$ and $\vec{x'}$ 
% differing in one element we have
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.

\end{block}

%----------------------------------------------------------------------------------------
% OUR APPROACH
%----------------------------------------------------------------------------------------

\begin{block}{Our Approach - Exponential Mechanism with Smooth Sensitivity}

define the mechanism $\hexpmech$ which, given in input a
sequence of observations $\dataobs$ and parameters $\epsilon>0$ and
$\delta>0$, produces an element $r$ in $\betaset$ with probability:

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}

The smooth sensitivity is
computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

\end{block}

\end{column} % End of the first column

\begin{column}{.03\textwidth}\end{column} % Empty spacer column

\begin{column}{.465\textwidth} % The second column

\begin{block}{Some Experimental Results}
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.39\textwidth]{poster_1.eps}
    \label{fig_1}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.352\textwidth]{poster_2.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.372\textwidth]{poster_3.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.32\textwidth]{poster_4.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\end{block}

%----------------------------------------------------------------------------------------
% CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion and Future Work}

\begin{itemize}
  \item Our the probabiliy measure approach outperforms the $\ell_1$-norm approach when the Laplace noise cannot recognize the data to be protected is histogram and data size grow large.

  \item 
  \begin{enumerate}
    \item  The accuracy that we are going to explore next, and in a more principled and formal way.

    \item  Experiments have shown that the actual privacy loss
  in the experiments can be smaller than $\epsilon$. This means that we
  could improve accuracy, by adding less noise but still achieve
  $(\epsilon, \delta)$-dp.

    \item The choice of the Hellinger distance might seem quite ad-hoc. Hence, it is worth exploring other distances over distributions. An interesting class of probability metrics is the family of $f$-divergences \cite{CIT-004}.

    \item Other application of our scheme are going to be explored.
  \end{enumerate}
\end{itemize}
%\vspace{8mm}
%\vspace{8mm}
%where we require $t$ and $u$ to have distinct sets of free variables.
\end{block}

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

%------------------------------------------------

% \begin{block}{Results: Figure}

% \begin{figure}
% \includegraphics[width=0.8\linewidth]{placeholder.jpg}
% \caption{Figure caption}
% \end{figure}

% \end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\begin{block}{References}

%\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{bayesian}}

\end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

% \begin{block}{Acknowledgments}

% \begin{itemize}
% \item Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
% \end{itemize}

% \end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color

% \begin{block}{Contact Information}

% \begin{itemize}
% \item \textbf{Marco Gaboardi}
% \item Web: \href{http://staff.computing.dundee.ac.uk/marcogaboardi/}{http://staff.computing.dundee.ac.uk/marcogaboardi/}
% \item Email: \href{mailto:m.gaboardi@dundee.ac.uk}{m.gaboardi@dundee.ac.uk}
% %\item Phone: +1 617-384-9606
% \end{itemize}

% \end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the second column

\begin{column}{.015\textwidth}\end{column} % Empty spacer column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2018-10-08 poster/main.tex
update poster

@@
 \begin{block}{Objectives}
-\noindent Design a tool for differentially private probabilistic
-programming featuring:
+\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
 \begin{enumerate}
-\item programming constructs to describe bayesian models and perform probabilistic inference,
-\item programming constructs useful to ensure differential privacy,
-\item type-checking as a method to ensure that the actual programs are
-  differentially private.
+\item A differentially private bayesian mechanism,
+\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
+\item Applying smooth sensitivity in mechanism to achieve better accuracy.
 \end{enumerate}
@@
 \centering
-  \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.39\textwidth]{poster_1.eps}
+  \subfigure[\footnotesize{2-dimensional, data size $\in [100,500]$}]{
+    \includegraphics[width=0.328\textwidth]{poster_1.eps}
     \label{fig_1}
   }
-  \subfigure[Data set size from $14000$ to $20000$]{
-    \includegraphics[width=0.352\textwidth]{poster_2.eps}
+  \subfigure[\footnotesize{3-dimensional, data size $\in [100,500]$} ]{
+    \includegraphics[width=0.297\textwidth]{poster_2.eps}
   \label{subsubsec_vs_datasize1b}} 
-\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+  \subfigure[\footnotesize{4-dimensional, data size $\in [100,600]$}]{
+    \includegraphics[width=0.29\textwidth]{poster_3.eps}
+    \label{subsubsec_vs_datasize1a}
+  }
+  \caption{Increasing data size with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}
@@
 \centering
-  \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.372\textwidth]{poster_3.eps}
-    \label{subsubsec_vs_datasize1a}
-  }
-  \subfigure[Data set size from $14000$ to $20000$]{
-    \includegraphics[width=0.32\textwidth]{poster_4.eps}
+  \subfigure[2-dimensional]{
+    \includegraphics[width=0.31\textwidth]{poster_4.eps}
   \label{subsubsec_vs_datasize1b}}
-\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+  \subfigure[3-dimensional]{
+    \includegraphics[width=0.31\textwidth]{poster_5.eps}
+  \label{subsubsec_vs_datasize1b}} 
+  \subfigure[4-dimensional]{
+    \includegraphics[width=0.31\textwidth]{poster_6.eps}
+  \label{subsubsec_vs_datasize1b}} 
+\caption{The concrete outputting probabilities under different dimensions with data set of size $600$ ,unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
 \label{fig_vs_datasize}

### 2018-10-08 poster/main.tex
update plots

@@
 \usetheme{I6pd2} % Use the I6pd2 theme supplied with this template
+
+\setbeamercolor{background canvas}{bg=white!20}
 
@@
 
-\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
-
+\addtobeamertemplate{block end}{}{\vspace*{1ex}} % White space under blocks
 \begin{frame}[t] % The whole poster is enclosed in one beamer frame
@@
 
-\begin{column}{.02\textwidth}\end{column} % Empty spacer column
+\begin{column}{.015\textwidth}\end{column} % Empty spacer column
 
-\begin{column}{.465\textwidth} % The first column
+\begin{column}{.485\textwidth} % The first column
 
@@
 \begin{block}{Objectives}
+\begin{columns} % Subdivide the first main column
+\begin{column}{.6\textwidth}
 \noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
@@
 \end{enumerate}
+\end{column}
+\begin{column}{.4\textwidth}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.5\textwidth]{poster_0.eps}
+\caption{Hellinger Sensitivity}
+\label{fig_sensitivity}
+\end{figure}
+% \vspace{.1cm}
+\end{column}
+\end{columns}
+
+% \noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
+% \begin{enumerate}
+% \item A differentially private bayesian mechanism,
+% \item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
+% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
+% \end{enumerate}
 
@@
 % \begin{column}{.54\textwidth} % The first subdivided column within the first main column
-beta
-distribution, $\betad(\alpha, \beta)$, with parameters
-$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyper parameters $\alpha,\beta\in\mathbb{R}^{+}$;
 
-\[
-  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
-\]
-where $\betaf(\cdot,\cdot)$ is the beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
-\[
-  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
-\]
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
-From this it can easily be derived that the posterior distribution is:
-\[
-  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
-\]
+Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$
+
+Bernoulli likelihood function:
+  $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$
+where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
+
+Posterior distribution derived: 
+$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$
+
 \end{block}
+% and with p.d.f:
 
+% \[
+%   \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
+% \]
+% where $\betaf(\cdot,\cdot)$ is the beta function.
 %----------------------------------------------------------------------------------------
@@
 \begin{block}{Differentially private Bayesian inference}
-% We are interested in the 
-% situation where: we have some  private data $\vec{x}$, some public data
-% $\vec{y}$, a set of parameter $\theta$, and a public prior $p(\theta)$
-% on $\theta$. We want to compute the public posterior distribution $p(\theta\
-% |\ \vec{x}, \vec{y})$ in a differentially private way. This
-% corresponds to make sure that
-% for given values $\epsilon$ and $\delta$, and for every $\vec{x}$ and $\vec{x'}$ 
-% differing in one element we have
-Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
-and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
+
+In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
 
@@
 
-\begin{block}{Our Approach - Exponential Mechanism with Smooth Sensitivity}
+\begin{block}{Smoothed Hellinger Distance based Exponential Mechanism}
 
-define the mechanism $\hexpmech$ which, given in input a
-sequence of observations $\dataobs$ and parameters $\epsilon>0$ and
-$\delta>0$, produces an element $r$ in $\betaset$ with probability:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
-\end{equation*}
+Our approach defines the mechanism $\hexpmech$: given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
+$\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
+{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.$
 
@@
 computed as follows:
-\begin{equation}
+\begin{equation*}
   \label{eq:smooth}
    S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
-\end{equation}
+\end{equation*}
 where $d$ is the Hamming distance between two datasets,
@@
 
-\begin{column}{.03\textwidth}\end{column} % Empty spacer column
+\begin{column}{.01\textwidth}\end{column} % Empty spacer column
 
-\begin{column}{.465\textwidth} % The second column
+\begin{column}{.485\textwidth} % The second column
 
@@
 
-\begin{block}{Conclusion and Future Work}
+\begin{block}{Conclusion}
 
@@
   \item 
-  \begin{enumerate}
-    \item  The accuracy that we are going to explore next, and in a more principled and formal way.
+  % \begin{enumerate}
+  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
 
-    \item  Experiments have shown that the actual privacy loss
-  in the experiments can be smaller than $\epsilon$. This means that we
-  could improve accuracy, by adding less noise but still achieve
-  $(\epsilon, \delta)$-dp.
+  %   \item  Experiments have shown that the actual privacy loss
+  % in the experiments can be smaller than $\epsilon$. This means that we
+  % could improve accuracy, by adding less noise but still achieve
+  % $(\epsilon, \delta)$-dp.
 
-    \item The choice of the Hellinger distance might seem quite ad-hoc.
+  %   \item The choice of the Hellinger distance might seem quite ad-hoc.
 Hence, it is worth exploring other distances over distributions.
@@
 
-    \item Other application of our scheme are going to be explored.
-  \end{enumerate}
+  %   \item Other application of our scheme are going to be explored.
+  % \end{enumerate}
 \end{itemize}
@@
 
-\begin{column}{.015\textwidth}\end{column} % Empty spacer column
+\begin{column}{.01\textwidth}\end{column} % Empty spacer column
 

### 2018-10-08 poster/main.tex
update poster

@@
 
-Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$
+Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;
 
-Bernoulli likelihood function:
-  $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
+Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
 
 Posterior distribution derived: 
-$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$
+$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
 
@@
 
-Our approach defines the mechanism $\hexpmech$: given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
-$\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.$
+Our approach defines the mechanism $\hexpmech$:
 
-The smooth sensitivity is
-computed as follows:
-\begin{equation*}
-  \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
-\end{equation*}
-where $d$ is the Hamming distance between two datasets,
+Producing an element $r$ in $\betaset$ with:
+$
+\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
+\frac 
+{exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
+{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
+$,
+(given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$).
+
+$\betaset$ is the candidates set defined as $ \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
+
+The scoring function is instantiated by Hellinegr distance between two beta distributions, and $S(\dataobs)$ is the smooth sensitivity computed as:
+$
+S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\}
+$,
+where $d$: Hamming distance between two datasets,
+
+$LS(\dataobs')$ denotes the local sensitivity at $\bysinfer(\dataobs')$:
+$
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+$ and 
 $\gamma =
-\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
-be determined later, and where $\Delta_{l}\bigg
-(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
-sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
-of the scoring function used in our mechanism. That is:
-\begin{equation*}
-\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
-\end{equation*}
+\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
 

### 2018-10-08 poster/main.tex
update poster

@@
 
-$\betaset$ is the candidates set defined as $ \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
+\begin{itemize}
+  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
 
-The scoring function is instantiated by Hellinegr distance between two beta distributions, and $S(\dataobs)$ is the smooth sensitivity computed as:
+  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance.
+
+  \item[-] $S(\dataobs)$, the smooth sensitivity:
   $
@@
   $,
-where $d$: Hamming distance between two datasets,
+  where
+  \begin{itemize}
+   \item $d$: Hamming distance between two datasets,
 
-$LS(\dataobs')$ denotes the local sensitivity at $\bysinfer(\dataobs')$:
+   \item $LS(\dataobs')$, local sensitivity at $\dataobs'$:
    $
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
-$ and 
-$\gamma =
+   LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+   $,
+
+   \item $\gamma =
    \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
+ \end{itemize}
+\end{itemize}
 
@@
 \begin{block}{Some Experimental Results}
+Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
+
+Fig.
+\ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
+In baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2-dimensional and $2$ in higher dimensional by equivalent to histogram case, which gives us the red points in plots.
+Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
+
 \begin{figure}[H]
@@
     \includegraphics[width=0.328\textwidth]{poster_1.eps}
-    \label{fig_1}
+    \label{subfig_sampling_2d}
   }
@@
     \includegraphics[width=0.297\textwidth]{poster_2.eps}
-  \label{subsubsec_vs_datasize1b}} 
+  \label{subfig_sampling_3d}
+  } 
   \subfigure[\footnotesize{4-dimensional, data size $\in [100,600]$}]{
     \includegraphics[width=0.29\textwidth]{poster_3.eps}
-    \label{subsubsec_vs_datasize1a}
+    \label{subfig_sampling_4d}
   }
-  \caption{Increasing data size with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize}
+  \caption{Increasing data size}
+\label{fig_sampling}
 \end{center}
@@
 
+Fig. \ref{fig_concrete_prob} give us the concrete probability of outputting candidates with certain distance.
 \begin{figure}[H]
@@
     \includegraphics[width=0.31\textwidth]{poster_4.eps}
-  \label{subsubsec_vs_datasize1b}}
+  \label{fig_concrete_prob_2d}
+  }
   \subfigure[3-dimensional]{
     \includegraphics[width=0.31\textwidth]{poster_5.eps}
-  \label{subsubsec_vs_datasize1b}} 
+  \label{fig_concrete_prob_3d}
+  } 
   \subfigure[4-dimensional]{
     \includegraphics[width=0.31\textwidth]{poster_6.eps}
-  \label{subsubsec_vs_datasize1b}} 
-\caption{The concrete outputting probabilities under different dimensions with data set of size $600$ ,unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize}
+  \label{fig_concrete_prob_4d}
+  } 
+\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
+\label{fig_concrete_prob}
 \end{center}

### 2018-10-08 poster/main.tex
update poster

@@
 \frac 
-{exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
+{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
 {\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
@@
 
-\begin{block}{Some Experimental Results}
-Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
+\begin{block}{Preliminary Experimental Results}
+% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
 
@@
 \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
-In baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2-dimensional and $2$ in higher dimensional by equivalent to histogram case, which gives us the red points in plots.
+In baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2-dimensional and $2$ in higher dimensional by their equivalence to histogram, giving us the red points in plots.
 Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
+Points in blue are our smoothed Hellinger distance based exponential mechanism.
 
@@
 
-Fig. \ref{fig_concrete_prob} give us the concrete probability of outputting candidates with certain distance.
+Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensional respectively.
 \begin{figure}[H]
@@
 \end{figure}
-
+\scriptsize{Two groups of experiments both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
 \end{block}
@@
 \begin{itemize}
-  \item Our the probabiliy measure approach outperforms the $\ell_1$-norm approach when the Laplace noise cannot recognize the data to be protected is histogram and data size grow large.
-
-  \item 
+  \item The smoothed Hellinger distance based exponential mechanism outperforms the $\ell_1$-norm approach when data size growing under the case that Laplace noise doesn't have knowledge of the implicit histogram equivalence.
   % \begin{enumerate}

### 2018-10-08 poster/main.tex
update poster

@@
 \begin{columns} % Subdivide the first main column
-\begin{column}{.6\textwidth}
-\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
+\begin{column}{.65\textwidth}
+\noindent Design a differentially private Bayesian inference mechanism by scaling to a metric between distribution.
 \begin{enumerate}
-\item A differentially private bayesian mechanism,
-\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
+\item A differentially private Bayesian mechanism,
+\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
 \item Applying smooth sensitivity in mechanism to achieve better accuracy.
+This is motivated by the Fig.
+\ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
 \end{enumerate}
 \end{column}
-\begin{column}{.4\textwidth}
+\begin{column}{.3\textwidth}
 \begin{figure}[ht]
@@
 % \begin{column}{.54\textwidth} % The first subdivided column within the first main column
-Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyper parameters $\alpha,\beta\in\mathbb{R}^{+}$;
+Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$;
+\begin{itemize}
+  \item[-] Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;
 
-Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;
+  \item[-] Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
 
-Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
-
-Posterior distribution derived: 
-$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
-
+  \item[-] Posterior distribution derived: $\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
+\end{itemize}
 \end{block}
@@
 
-In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
+In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
 
@@
 $,
-(given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$).
+given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.
 
 \begin{itemize}
-  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
+  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$;
 
-  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance.
+  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance;
 
@@
   $,
-  where
+  where:
   \begin{itemize}

### 2018-10-08 poster/main.tex
update poster Objectives

@@
 \begin{columns} % Subdivide the first main column
-\begin{column}{.65\textwidth}
-\noindent Design a differentially private Bayesian inference mechanism by scaling to a metric between distribution.
+\begin{column}{.62\textwidth}
 \begin{enumerate}
-\item A differentially private Bayesian mechanism,
+\item Designing a differentially private Bayesian inference mechanism.
 \item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
-\item Applying smooth sensitivity in mechanism to achieve better accuracy.
-This is motivated by the Fig.
-\ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
+\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
 \end{enumerate}
 \end{column}
-\begin{column}{.3\textwidth}
+\begin{column}{.35\textwidth}
 \begin{figure}[ht]
 \centering
-\includegraphics[width=0.5\textwidth]{poster_0.eps}
+\includegraphics[width=0.85\textwidth]{poster_0.eps}
 \caption{Hellinger Sensitivity}
@@
 
-\begin{block}{Differentially private Bayesian inference}
+\begin{block}{Differentially Private Bayesian inference}
 Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
@@
 
-\begin{block}{Smoothed Hellinger Distance based Exponential Mechanism}
+\begin{block}{Smoothed Hellinger Distance Based Exponential Mechanism}
 

### 2018-10-08 codes/Hellinger_Sensitivity.py
update plots in poster Objectives.

@@ -46,7 +46,7 @@ if __name__ == "__main__":
 	sensitivities = generate_sensitivities()
 
 	fig = plt.figure()
-	ax = fig.gca(projection='3d')
+	ax = plt.axes(projection='3d')
 	# x = numpy.arange(1, 81, 1)
 	# y = numpy.arange(1, 81, 1)
 	# x, y = numpy.meshgrid(x,y)
@@ -58,12 +58,13 @@ if __name__ == "__main__":
 		y = y + range(1, 81)
 		z = z + sensitivities[i - 1]
 
-	#surf = ax.plot_surface(x, y, numpy.array(sensitivities), cmap=cm.coolwarm, linewidth=0, antialiased=False)
-	#fig.colorbar(surf, shrink=0.5, aspect=5)
+	# surf = ax.plot_surface(x, y, z, cmap=cm.coolwarm, linewidth=0, antialiased=False)
+	# fig.colorbar(surf, shrink=0.5, aspect=5)
 	ax.scatter(x, y, z)
-	ax.set_xlabel('Alpha')
-	ax.set_ylabel('Beta')
-	ax.set_zlabel('Hellinger(beta(a+1, b), Beta(a, b+1))')
+	ax.set_xlabel(r'$\alpha$')
+	ax.set_ylabel(r'$\beta$')
+	ax.set_zlabel(r'$\mathcal{H}(\mathsf{beta}(\alpha+1, b), \mathsf{beta}(\alpha, \beta+1))$')
+	ax.set_title("Local sensitivity")
 	plt.show()
 
 

### 2018-10-09 poster/main.tex
update plots in poster Objectives.
update plots in poster
some work

@@
 \begin{columns} % Subdivide the first main column
-\begin{column}{.62\textwidth}
+\begin{column}{.69\textwidth}
 \begin{enumerate}
 \item Designing a differentially private Bayesian inference mechanism.
-\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
-\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
+\item Measuring accuracy with a metric over distributions (Hellinger distance).
+\item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
+\item Applying smooth sensitivity in mechanism to achieve better accuracy.
+        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
 \end{enumerate}
 \end{column}
-\begin{column}{.35\textwidth}
+\begin{column}{.28\textwidth}
 \begin{figure}[ht]
@@
 \includegraphics[width=0.85\textwidth]{poster_0.eps}
-\caption{Hellinger Sensitivity}
+say something about beta...
+\caption{\footnotesize{Local sensitivity of Hellinger}}
 \label{fig_sensitivity}
@@
 
-\begin{block}{Bayesian Inference Background}
+\begin{block}{Bayesian inference: Beta-Binomial model}
 % The first subdivided column within the first main column
@@
 % \begin{column}{.54\textwidth} % The first subdivided column within the first main column
-Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$;
+%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
 \begin{itemize}
-  \item[-] Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;
+  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.
 
-  \item[-] Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
+  \item[-] Likelihood function: $\mathbb{L}_{\dataobs | \theta}= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
 
-  \item[-] Posterior distribution derived: $\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
+  \item[-] Posterior distribution over theta: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
 \end{itemize}
@@
 In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
-
+Explain parameters of baseline approach...
 \end{block}
@@
 
-Our approach defines the mechanism $\hexpmech$:
-
-Producing an element $r$ in $\betaset$ with:
+Our approach defines the mechanism $\hexpmech$, which outputs  an element $r$ in $\betaset$ with probaiblity:
 $
@@
 {\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
-$,
+$
+
 given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.
@@
 \begin{itemize}
-  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$;
+  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
 
-  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance;
+  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function based on the Hellinger distance.
 
@@
 
-   \item $\gamma =
-   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
+   \item $\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
  \end{itemize}
@@
 
-Fig.
-\ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
-In baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2-dimensional and $2$ in higher dimensional by their equivalence to histogram, giving us the red points in plots.
-Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
-Points in blue are our smoothed Hellinger distance based exponential mechanism.
+  Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
+  In the baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
+  (Should explain better).
+  giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
+  Points in blue are given by the $M_B...$.
 
@@
 
-Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensional respectively.
+Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensions respectively.
 \begin{figure}[H]
@@
 \begin{itemize}
-  \item The smoothed Hellinger distance based exponential mechanism outperforms the $\ell_1$-norm approach when data size growing under the case that Laplace noise doesn't have knowledge of the implicit histogram equivalence.
+\item The smoothed Hellinger distance based exponential mechanism outperforms the asymptotically the baseline 
+  approach  when the latter uses a sensitivity proportional to dimensionality.
+  (when can this happen?)
   % \begin{enumerate}

### 2018-10-09 poster/main.tex
update blocks.

@@
 \begin{block}{Objectives}
-\begin{columns} % Subdivide the first main column
-\begin{column}{.69\textwidth}
+% \begin{columns} % Subdivide the first main column
+% \begin{column}{.69\textwidth}
 \begin{enumerate}
@@
 \item Measuring accuracy with a metric over distributions (Hellinger distance).
-\item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
-\item Applying smooth sensitivity in mechanism to achieve better accuracy.
-        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
+% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
+% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
+%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
 \end{enumerate}
-\end{column}
-\begin{column}{.28\textwidth}
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.85\textwidth]{poster_0.eps}
-say something about beta...
-\caption{\footnotesize{Local sensitivity of Hellinger}}
-\label{fig_sensitivity}
-\end{figure}
+% \end{column}
+% \begin{column}{.28\textwidth}
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.85\textwidth]{poster_0.eps}
+% say something about beta...
+% \caption{\footnotesize{Local sensitivity of Hellinger}}
+% \label{fig_sensitivity}
+% \end{figure}
 % \vspace{.1cm}
-\end{column}
-\end{columns}
+% \end{column}
+% \end{columns}
 
@@
 
-\begin{block}{Differentially Private Bayesian inference}
+\begin{block}{Differentially Private Bayesian Inference and Motivation}
 Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
+\begin{columns} % Subdivide the first main column
+\begin{column}{.69\textwidth}
+\begin{enumerate}
 
-In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
+  \item In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
   Explain parameters of baseline approach...
+  \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
+  \item Applying smooth sensitivity in mechanism to achieve better accuracy.
+        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
+\end{enumerate}
+\end{column}
+\begin{column}{.28\textwidth}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.85\textwidth]{poster_0.eps}
+\caption{\footnotesize{Local sensitivity of Hellinger}}
+\label{fig_sensitivity}
+\end{figure}
+% \vspace{.1cm}
+\end{column}
+\end{columns}
+
 \end{block}

### 2018-10-09 poster/main.tex
update plots

@@
 \begin{block}{Differentially Private Bayesian Inference and Motivation}
-Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
 \begin{columns} % Subdivide the first main column
 \begin{column}{.69\textwidth}
+In a baseline approach, we release a private version of posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$ by sampling noise from $Lap(\mu,\nu)$ with mean $\mu$ and scale $\nu$, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
+This gives us motivation of following two contributions:
 \begin{enumerate}
-
-  \item In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
-  Explain parameters of baseline approach...
-  \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
-  \item Applying smooth sensitivity in mechanism to achieve better accuracy.
-        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
+  \item Calibrating the noise w.r.t sensitivity of the accuracy metric (Hellinger distance), v.s. the $\ell_1$ norm in baseline approach.
+  \item Applying smooth sensitivity in mechanism v.s. global sensitivity.
+        (Global sensitivity of Hellinger distance over $\betad$ distribution takes value at point $(0,0)$ as in Fig.
+\ref{fig_sensitivity}.
+But we can improve because it's very smooth and low in central part).
 \end{enumerate}
@@
 \centering
-\includegraphics[width=0.85\textwidth]{poster_0.eps}
+\includegraphics[width=0.9\textwidth]{poster_0.eps}
 \caption{\footnotesize{Local sensitivity of Hellinger}}
@@
 
-Our approach defines the mechanism $\hexpmech$, which outputs  an element $r$ in $\betaset$ with probaiblity:
-$
+We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probaiblity:
+\[
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
 \frac 
-{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
-{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
-$
+{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
+{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
+\]
 
-given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.
+given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, where:
 
@@
   $
-  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\}
+  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
   $,
@@
   \begin{itemize}
-   \item $d$: Hamming distance between two datasets,
+   \item $d$: Hamming distance between two data sets,
 
@@
   giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
-  Points in blue are given by the $M_B...$.
+  Points in blue are given by the $\hexpmech$.
 
@@
 \centering
-  \subfigure[\footnotesize{2-dimensional, data size $\in [100,500]$}]{
+  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
     \includegraphics[width=0.328\textwidth]{poster_1.eps}
@@
   }
-  \subfigure[\footnotesize{3-dimensional, data size $\in [100,500]$} ]{
+  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
     \includegraphics[width=0.297\textwidth]{poster_2.eps}
@@
   } 
-  \subfigure[\footnotesize{4-dimensional, data size $\in [100,600]$}]{
+  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
     \includegraphics[width=0.29\textwidth]{poster_3.eps}
@@
 \centering
-  \subfigure[2-dimensional]{
+  \subfigure[2 dimensions]{
     \includegraphics[width=0.31\textwidth]{poster_4.eps}
@@
   }
-  \subfigure[3-dimensional]{
+  \subfigure[3 dimensions]{
     \includegraphics[width=0.31\textwidth]{poster_5.eps}
@@
   } 
-  \subfigure[4-dimensional]{
+  \subfigure[4 dimensions]{
     \includegraphics[width=0.31\textwidth]{poster_6.eps}

### 2018-10-09 poster/main.tex
update poster

@@
 \begin{enumerate}
-\item Designing a differentially private Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance).
+\item Designing a differentially private ($\mathsf{dp}$) Bayesian inference mechanism.
+\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)).
 % \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
@@
 \begin{block}{Differentially Private Bayesian Inference and Motivation}
+Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
 \begin{columns} % Subdivide the first main column
 \begin{column}{.69\textwidth}
-In a baseline approach, we release a private version of posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$ by sampling noise from $Lap(\mu,\nu)$ with mean $\mu$ and scale $\nu$, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
-This gives us motivation of following two contributions:
 \begin{enumerate}
-  \item Calibrating the noise w.r.t sensitivity of the accuracy metric (Hellinger distance), v.s. the $\ell_1$ norm in baseline approach.
-  \item Applying smooth sensitivity in mechanism v.s. global sensitivity.
-        (Global sensitivity of Hellinger distance over $\betad$ distribution takes value at point $(0,0)$ as in Fig.
+  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
+But noise here is scaled to sensitivity $1$ over $\ell_1$ norm.
+Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s.
+the $\ell_1$ norm in baseline approach).
+  \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig.
 \ref{fig_sensitivity}.
-But we can improve because it's very smooth and low in central part).
+But it's very smooth when move away from edge.
+Motivated by this, we apply smooth sensitivity in mechanism (v.s.
+global sensitivity) to improve accuracy.
 \end{enumerate}
@@
 \includegraphics[width=0.9\textwidth]{poster_0.eps}
-\caption{\footnotesize{Local sensitivity of Hellinger}}
+\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
 \label{fig_sensitivity}
@@
   Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
-  In the baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
+  In the baseline approach, it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
   (Should explain better).

### 2018-10-09 poster/main.tex
update plots in poster

@@
 
-\begin{block}{Bayesian inference: Beta-Binomial model}
+\begin{block}{Bayesian inference ($\bysinfer$): Beta-Binomial model}
 % The first subdivided column within the first main column
@@
 
-\begin{block}{Differentially Private Bayesian Inference and Motivation}
+\begin{block}{Differentially Private Bayesian Inference and Motivations}
 Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
@@
 
-  \item[-] $S(\dataobs)$, the smooth sensitivity:
+  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
   $
@@
   Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
-  In the baseline approach, it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
-  (Should explain better).
-  giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
+  In the baseline approach (LapMech), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
+  (Posteriors of adjacent data sets differ only in two dimensions),
+  giving us the red points in plots. Without knowing equivalence, LapMech adds noise scaled to sensitivity proportional to dimensionality, giving us green points.
   Points in blue are given by the $\hexpmech$.
@@
   \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
-    \includegraphics[width=0.328\textwidth]{poster_1.eps}
+    \includegraphics[width=0.333\textwidth]{poster_1.eps}
     \label{subfig_sampling_2d}
@@
   \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
-    \includegraphics[width=0.297\textwidth]{poster_2.eps}
+    \includegraphics[width=0.302\textwidth]{poster_2.eps}
   \label{subfig_sampling_3d}
@@
   \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
-    \includegraphics[width=0.29\textwidth]{poster_3.eps}
+    \includegraphics[width=0.295\textwidth]{poster_3.eps}
     \label{subfig_sampling_4d}
   }
-  \caption{Increasing data size}
+  \caption{Average accuracy by increasing data set size}
 \label{fig_sampling}
@@
 \end{figure}
-\scriptsize{Two groups of experiments both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
+\footnotesize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
 \end{block}
@@
 \begin{itemize}
-\item The smoothed Hellinger distance based exponential mechanism outperforms the asymptotically the baseline 
+  \item The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
   approach  when the latter uses a sensitivity proportional to dimensionality.
-  (when can this happen?)
+  \item From experimental results, the outperformance happens when the data size is greater than $400$ .
   % \begin{enumerate}

### 2018-10-10 poster/main.tex
update files

@@
 
-  Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
-  In the baseline approach (LapMech), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
-  (Posteriors of adjacent data sets differ only in two dimensions),
+  Fig.
+\ref{fig_sampling} and Fig.
+\ref{subfig_prior} gives the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior distribution configuration.
+  In the baseline approach (LapMech {\small with noises being postprocessed to the closest integer}), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
+  (posteriors of adjacent data sets differ only in two dimensions),
   giving us the red points in plots. Without knowing equivalence, LapMech adds noise scaled to sensitivity proportional to dimensionality, giving us green points.
@@
 
-Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensions respectively.
+Fig.
+\ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2 and 3 respectively.
 \begin{figure}[H]
@@
 \centering
+   \subfigure[2 dimensions with data size $100$]{
+    \includegraphics[width=0.317\textwidth]{poster_6.eps}
+  \label{subfig_prior}
+  }
   \subfigure[2 dimensions]{
     \includegraphics[width=0.31\textwidth]{poster_4.eps}
-  \label{fig_concrete_prob_2d}
+  \label{subfig_concrete_prob_2d}
   }
@@
     \includegraphics[width=0.31\textwidth]{poster_5.eps}
-  \label{fig_concrete_prob_3d}
-  } 
-  \subfigure[4 dimensions]{
-    \includegraphics[width=0.31\textwidth]{poster_6.eps}
-  \label{fig_concrete_prob_4d}
+  \label{subfig_concrete_prob_3d}
   } 
@@
 \end{figure}
-\footnotesize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
+\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
 \end{block}

### 2018-10-10 codes/main.py

@@ -396,7 +396,7 @@ def plot_error_box(data, xlabel, xstick, title, legends, colors):
 	#ax.set_xlim(0.5, len(errors) + 0.5)
 
 
-	plt.xticks([i*l + (l+1)/2.0 for i in range(len(xstick))],xstick,rotation=70,fontsize=12)
+	plt.xticks([i*l + (l+1)/2.0 for i in range(len(xstick))],xstick,rotation=40,fontsize=12)
 	plt.title(title,fontsize=20)
 
 	for i in range(1, len(bplot["boxes"])/l + 1):
@@ -459,7 +459,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	# 	['Our ExpMech',"LapMech (sensitivity = 2)", "LapMech (sensitivity = 4)"],
 	# 	"Mean Error VS. Data Size")
 	plot_error_box(data,"Different Datasizes",datasizes,"Accuracy VS. Data Size",
-		['Our ExpMech',"LapMech (sensitivity = 2)", "LapMech (sensitivity = 3)"],
+		[r'$\mathcal{M}^{B}_{\mathcal{H}}$',"LapMech (sensitivity = 2)", "LapMech (sensitivity = 3)"],
 		['lightblue', 'navy', 'red'])
 	return
 
@@ -470,26 +470,35 @@ def accuracy_VS_prior(sample_size,epsilon,delta,priors,observation):
 	data = []
 	xstick = []
 	xstick_mean = []
-	mean_error = [[],[]]
+	mean_error = [[],[],[]]
 	for prior in priors:
 		Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
 		Bayesian_Model._set_observation(observation)
-		Bayesian_Model._experiments(500)
+		Bayesian_Model._experiments(3000)
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[3]])
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[0]])
+		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[4]])
 		mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
 		mean_error[1].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[0]])
-		xstick_mean.append(str(prior._alphas))
[…]

### 2018-10-10 poster/main.tex
update poster

@@
 Fig.
-\ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2 and 3 respectively.
+\ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities.
+On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
 \begin{figure}[H]
@@
   } 
-\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
+\caption{4-quantile and discrete probability plots}
 \label{fig_concrete_prob}
@@
 \begin{itemize}
-  \item The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
+  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
   approach  when the latter uses a sensitivity proportional to dimensionality.
-  \item From experimental results, the outperformance happens when the data size is greater than $400$ .
+  \item[-] From experimental results, the outperformance happens when the data size is greater than $400$ .
   % \begin{enumerate}

### 2018-10-10 codes/main.py

@@ -474,7 +474,7 @@ def accuracy_VS_prior(sample_size,epsilon,delta,priors,observation):
 	for prior in priors:
 		Bayesian_Model = BayesInferwithDirPrior(prior, sample_size, epsilon, delta)
 		Bayesian_Model._set_observation(observation)
-		Bayesian_Model._experiments(3000)
+		Bayesian_Model._experiments(1000)
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[3]])
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[0]])
 		data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[4]])

### 2018-10-10 poster/main.tex
update poster

@@
 \begin{enumerate}
-\item Designing a differentially private ($\mathsf{dp}$) Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)).
+\item Designing a differentially private Bayesian inference mechanism.
+\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)) $\todo{K-divergence}$.
 % \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
@@
 
-\begin{block}{Bayesian inference ($\bysinfer$): Beta-Binomial model}
+\begin{block}{Bayesian inference ($\bysinfer$): Example: Beta-Binomial model}
 % The first subdivided column within the first main column
@@
 \begin{enumerate}
-  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
-But noise here is scaled to sensitivity $1$ over $\ell_1$ norm.
+  \item  \todo{Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
+But noise here is proportional to $\ell_1$ norm.
 Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s.
-the $\ell_1$ norm in baseline approach).
+the $\ell_1$ norm in baseline approach).} \todo{grows linear with the dimension.} \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
   \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig.
 \ref{fig_sensitivity}.
-But it's very smooth when move away from edge.
+But it's very low when move away from edge.
 Motivated by this, we apply smooth sensitivity in mechanism (v.s.
 global sensitivity) to improve accuracy.
+  {sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
 \end{enumerate}
@@
    \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.317\textwidth]{poster_6.eps}
+    \includegraphics[width=0.317\textwidth]{poster_4.eps}
   \label{subfig_prior}
@@
   \subfigure[2 dimensions]{
-    \includegraphics[width=0.31\textwidth]{poster_4.eps}
+    \includegraphics[width=0.31\textwidth]{poster_5.eps}
   \label{subfig_concrete_prob_2d}
@@
   \subfigure[3 dimensions]{
-    \includegraphics[width=0.31\textwidth]{poster_5.eps}
+    \includegraphics[width=0.31\textwidth]{poster_6.eps}
   \label{subfig_concrete_prob_3d}

### 2018-10-10 codes/SmoothSenOpt.py

@@ -75,10 +75,10 @@ def plot_ss(ss,xstick,title,yaxis):
 
 	plt.plot(range(len(ss)),ss,'r^')
 
-	plt.xticks(range(len(ss)),xstick,rotation=70,fontsize=12)
+	# plt.xticks(range(len(ss)),xstick,rotation=70,fontsize=7)
 	plt.title(title,fontsize=20)
-	plt.xlabel(r"$x'$",fontsize=25)	
-	plt.ylabel(yaxis,fontsize=20)
+	plt.xlabel(r"$\alpha$",fontsize=25)	
+	plt.ylabel(yaxis,fontsize=15)
 	plt.grid()
 	plt.legend()
 	plt.show()
@@ -113,24 +113,24 @@ def ss_ls_component_study(prior, sample_size, epsilon, delta, percentage):
 	Bayesian_Model._set_candidate_scores()
 	Bayesian_Model._set_LS_Candidates()
 
-	xstick = [str((c._minus(Bayesian_Model._prior))._alphas) for c in Bayesian_Model._candidates]
+	xstick = [str(c._alphas) for c in Bayesian_Model._candidates]
 	beta = math.log(1 - epsilon / (2.0 * math.log(delta / (2.0 * (sample_size)))))
 	y=[Bayesian_Model._LS_Candidates[r] for r in Bayesian_Model._candidates]
 
 
-	plot_ss(y,xstick,'Local Sensitivity Component of Smooth Sensitivity w.r.t. x :' + str([sample_size*i for i in percentage]) + r'; $\epsilon:$' + str(epsilon) + r'; $\delta:$' + str(delta), r"$\Delta_l(H(BI(x'),-))}$")
+	plot_ss(y[1:-1],xstick,"", r"$\mathcal{H}(\mathsf{beta}(\alpha + 1, 100 - \alpha), \mathsf{beta}(\alpha, 101 - \alpha))$")
 
 	return
 
 
 if __name__ == "__main__":
-	percentage = [0.3,0.3,0.4]
-	datasize = 10
-	prior = dirichlet([1,1,1])
+	percentage = [0.5,0.5]
+	datasize = 100
+	prior = dirichlet([1,1])
 
-	ss_exponentiate_component_study(prior, datasize, 0.1, 0.00000001, percentage)
+	# ss_exponentiate_component_study(prior, datasize, 0.1, 0.00000001, percentage)
 
[…]

### 2018-10-10 codes/main.py

@@ -168,7 +168,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 
 	plt.plot(steps[-100:], probabilities_lap_2_by_steps[-100:], 'g', label=('LapMech (sensitivity = 2)'))
 
-	plt.xlabel("c / (steps from correct answer, in form of Hellinger Distance)")
+	plt.xlabel("c / Hellinger distance from true posterior")
 	plt.ylabel("Pr[H(BI(x),r) = c]")
 	plt.title("Discrete Probabilities")
 	plt.legend()
@@ -583,7 +583,7 @@ def gen_priors(r, step, d):
 
 if __name__ == "__main__":
 
-	datasize = 100
+	datasize = 600
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
@@ -594,7 +594,7 @@ if __name__ == "__main__":
 	datasizes = gen_datasizes((600,600),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.5,0.5]
 	datasets = gen_datasets(percentage, datasizes)
-	priors = [dirichlet([1,1])] + gen_priors([5,20], 5, 2) + gen_priors([40,100], 20, 2) + gen_priors([150,300], 50, 2)
+	priors = [dirichlet([1,1])] + gen_priors([5,20], 5, 2) + gen_priors([40,100], 20, 2) + gen_priors([150,300], 50, 2) + gen_priors([400,400], 50, 2)
 	# accuracy_VS_prior_mean(sample_size,epsilon,delta,priors,observations)
 	accuracy_VS_prior(datasize,epsilon,delta,priors,observation)
 	# accuracy_VS_mean(sample_size,epsilon,delta,prior)

### 2018-10-11 poster/main.tex
update plots isze

@@
 \begin{enumerate}
-  \item  \todo{Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
-But noise here is proportional to $\ell_1$ norm.
-Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s.
-the $\ell_1$ norm in baseline approach).} \todo{grows linear with the dimension.} \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
-  \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig.
+  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
+But noise here is proportional to $\ell_1$ norm, which grows linear with the dimension..
+Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$).
+%(v.s.
+the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
+  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig.
 \ref{fig_sensitivity}.
@@
 global sensitivity) to improve accuracy.
-  {sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
+  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
 \end{enumerate}
@@
    \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.317\textwidth]{poster_4.eps}
+    \includegraphics[width=0.304\textwidth]{poster_4.eps}
   \label{subfig_prior}

### 2018-10-11 codes/main.py

@@ -583,7 +583,7 @@ def gen_priors(r, step, d):
 
 if __name__ == "__main__":
 
-	datasize = 600
+	datasize = 100
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])

### 2018-10-11 poster/main.tex
update poster

@@
 \item Designing a differentially private Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)) $\todo{K-divergence}$.
+\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)), $f$-divergence, etc.
 % \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
@@
 \begin{enumerate}
-  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$.
-But noise here is proportional to $\ell_1$ norm, which grows linear with the dimension..
+  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm.
+But we measure results by a different metric and sensitivity grows linear with the dimension.
 Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$).
@@
 But it's very low when move away from edge.
-Motivated by this, we apply smooth sensitivity in mechanism (v.s.
-global sensitivity) to improve accuracy.
+Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
   %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
@@
 % Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
-
+Experiments are on three mechanisms and plotted as follows:
+\begin{itemize}
+  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
+  \item[-] Red: LapMech adding noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
+  (posteriors of adjacent data differ only in two dimensions).
+  \item[-] Blue: $\hexpmech$.
+\end{itemize}
   Fig.
 \ref{fig_sampling} and Fig.
-\ref{subfig_prior} gives the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior distribution configuration.
-  In the baseline approach (LapMech {\small with noises being postprocessed to the closest integer}), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
-  (posteriors of adjacent data sets differ only in two dimensions),
-  giving us the red points in plots. Without knowing equivalence, LapMech adds noise scaled to sensitivity proportional to dimensionality, giving us green points.
-  Points in blue are given by the $\hexpmech$.
+\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.
 
@@
    \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.304\textwidth]{poster_4.eps}
+    \includegraphics[width=0.31\textwidth]{poster_4.eps}
   \label{subfig_prior}
@@
   \subfigure[2 dimensions]{
-    \includegraphics[width=0.31\textwidth]{poster_5.eps}
+    \includegraphics[width=0.311\textwidth]{poster_5.eps}
   \label{subfig_concrete_prob_2d}
@@
   \subfigure[3 dimensions]{
-    \includegraphics[width=0.31\textwidth]{poster_6.eps}
+    \includegraphics[width=0.311\textwidth]{poster_6.eps}
   \label{subfig_concrete_prob_3d}

### 2018-10-11 codes/main.py

@@ -498,7 +498,7 @@ def accuracy_VS_prior(sample_size,epsilon,delta,priors,observation):
 	plot_error_box(data,r"Different Priors on $\theta$",[r"$\mathsf{beta}$" + str(i._alphas) for i in priors],
 		"Accuracy VS. Prior Distribution",
 		[r'$\mathcal{M}^{B}_{\mathcal{H}}$',"LapMech (sensitivity = 1)", "LapMech (sensitivity = 2)"],
-		['lightblue', 'navy', 'red'])
+		['navy', 'red', 'green'])
 	return
 
 def accuracy_VS_mean(sample_size,epsilon,delta,prior):

### 2018-10-11 poster/main.tex
update plots color

@@
 \item Designing a differentially private Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)), $f$-divergence, etc.
+\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
 % \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
@@
   \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm.
-But we measure results by a different metric and sensitivity grows linear with the dimension.
+But this sensitivity grows linear with the dimension, also we measure results by a different metric.
 Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$).
@@
 the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
-  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig.
+  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieves at edges as in Fig.
 \ref{fig_sensitivity}.
@@
   \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
-  \item[-] Red: LapMech adding noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
-  (posteriors of adjacent data differ only in two dimensions).
+  \item[-] Red: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
+  (posteriors of adjacent data sets differ only in two dimensions).
   \item[-] Blue: $\hexpmech$.
@@
   }
-  \subfigure[2 dimensions]{
+  \subfigure[2 dimensions with data size $600$]{
     \includegraphics[width=0.311\textwidth]{poster_5.eps}
@@
   }
-  \subfigure[3 dimensions]{
+  \subfigure[3 dimensions with data size $600$]{
     \includegraphics[width=0.311\textwidth]{poster_6.eps}
@@
   approach when the latter uses a sensitivity proportional to dimensionality.
-  \item[-] From experimental results, the outperformance happens when the data size is greater than $400$ .
+  \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.
   % \begin{enumerate}

### 2018-10-11 codes/main.py

@@ -147,24 +147,24 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	f_lap_1.close()
 	f_lap_2.close()	
 
-	plt.figure()
-	plt.plot(steps[-100:], probabilities_exp_by_steps[-100:], 'ro', label=(r'$\mathcal{M}^{B}_{\mathcal{H}}$'))
-	# plt.plot(T, approximate_bounds, 'g^', label=('Expmech_SS zApproximate Bound'))
-	plt.plot(steps[-100:], probabilities_lap_1_by_steps[-100:], 'b^', label=('LapMech (sensitivity = 1)'))
+	# plt.figure()
+	# plt.plot(steps[-100:], probabilities_exp_by_steps[-100:], 'ro', label=(r'$\mathcal{M}^{B}_{\mathcal{H}}$'))
+	# # plt.plot(T, approximate_bounds, 'g^', label=('Expmech_SS zApproximate Bound'))
+	# plt.plot(steps[-100:], probabilities_lap_1_by_steps[-100:], 'b^', label=('LapMech (sensitivity = 1)'))
 
-	plt.plot(steps[-100:], probabilities_lap_2_by_steps[-100:], 'gv', label=('LapMech (sensitivity = 2)'))
+	# plt.plot(steps[-100:], probabilities_lap_2_by_steps[-100:], 'gv', label=('LapMech (sensitivity = 2)'))
 
-	plt.xlabel("c / (steps from correct answer, in form of Hellinger Distance)")
-	plt.ylabel("Pr[H(BI(x),r) = c]")
-	plt.title("Discrete Probabilities")
-	plt.legend()
-	plt.grid()
-	plt.savefig("data_"+ str(observation) + "_prior_"+ str(Bayesian_Model._prior._alphas) + "_epsilon_"+ str(epsilon) + "_scatter.png")
+	# plt.xlabel("c / (steps from correct answer, in form of Hellinger Distance)")
+	# plt.ylabel("Pr[H(BI(x),r) = c]")
+	# plt.title("Discrete Probabilities")
+	# plt.legend()
+	# plt.grid()
+	# plt.savefig("data_"+ str(observation) + "_prior_"+ str(Bayesian_Model._prior._alphas) + "_epsilon_"+ str(epsilon) + "_scatter.png")
 	# plt.show()
 	plt.figure()
[…]

### 2018-10-11 poster/main.tex
update posters

@@
 
-\begin{block}{Bayesian inference ($\bysinfer$): Example: Beta-Binomial model}
+\begin{block}{Bayesian inference ($\bysinfer$) (A Beta-Binomial model example):}
 % The first subdivided column within the first main column
@@
 \[
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
+% \underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
+\mathbb{P}_{r \thicksim \hexpmech} =
 \frac 
@@
 \begin{itemize}
-  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
-  \item[-] Red: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
+  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
+  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
   (posteriors of adjacent data sets differ only in two dimensions).
-  \item[-] Blue: $\hexpmech$.
+  \item[-] \textbf{Blue}: $\hexpmech$.
 \end{itemize}
@@
    \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.31\textwidth]{poster_4.eps}
+    \includegraphics[width=0.313\textwidth]{poster_4.eps}
   \label{subfig_prior}
@@
   \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.311\textwidth]{poster_5.eps}
+    \includegraphics[width=0.31\textwidth]{poster_5.eps}
   \label{subfig_concrete_prob_2d}
@@
   \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.311\textwidth]{poster_6.eps}
+    \includegraphics[width=0.31\textwidth]{poster_6.eps}
   \label{subfig_concrete_prob_3d}

### 2018-10-11 codes/main.py

@@ -388,7 +388,7 @@ def hellinger_vs_l1norm(base_distribution):
 def plot_error_box(data, xlabel, xstick, title, legends, colors):
 	l = len(legends)
 	plt.figure(figsize=(0.5*len(data),9))
-	medianprops = dict(linestyle='--', linewidth=3.0, color='green')
+	medianprops = dict(linestyle='--', linewidth=3.0, color='lightblue')
 	# meanlineprops = dict(linestyle='--', linewidth=2.5, color='purple')
 	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', vert=2, whis=1.5, patch_artist=True, medianprops=medianprops)#, meanprops=meanlineprops, meanline=True,showmeans=True)
 	plt.xlabel(xlabel,fontsize=15)
@@ -583,11 +583,11 @@ def gen_priors(r, step, d):
 
 if __name__ == "__main__":
 
-	datasize = 600
+	datasize = 100
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
-	dataset = [300,300]
+	dataset = [50,50]
 	x1 = [1,499]
 	x2 = [0,500]
 	epsilons = numpy.arange(0.1, 2, 0.1)
@@ -596,7 +596,7 @@ if __name__ == "__main__":
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([1,1])] + gen_priors([5,20], 5, 2) + gen_priors([40,100], 20, 2) + gen_priors([150,300], 50, 2) + gen_priors([400,400], 50, 2)
 	# accuracy_VS_prior_mean(sample_size,epsilon,delta,priors,observations)
-	# accuracy_VS_prior(datasize,epsilon,delta,priors,observation)
+	accuracy_VS_prior(datasize,epsilon,delta,priors,dataset)
 	# accuracy_VS_mean(sample_size,epsilon,delta,prior)
 	# accuracy_VS_datasize(epsilon,delta,prior,datasets,datasizes)
 	# hellinger_vs_l1norm(Dir(observation))

### 2018-10-11 poster/main.tex
update the poster

@@
 \setbeamercolor{background canvas}{bg=white!20}
-
+% \setbeamercolor{block title}{fg=white,bg=blue!70}
+% \setbeamercolor{block body}{fg=black,bg=blue!10}
 \usepackage[english]{babel} % English language/hyphenation
@@
 
-\newcommand{\rightfoot}{mbun@cs.princeton.edu, gaboardi@buffalo.edu} % Right footer text
+\newcommand{\rightfoot}{mbun@cs.princeton.edu, \{gianpiet,gaboardi,jliu223\}@buffalo.edu} % Right footer text
 
@@
 
-\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color
+\setbeamercolor{block title}{fg=black,bg=white!70} % Change the block title color
 

### 2018-10-11 TPDP2018/poster/main.tex
update poster from Mark bun's feedback

--- 2018-10-11 poster/main.tex
@@
 \begin{enumerate}
-\item Designing a differentially private Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
+\item Design a differentially private Bayesian inference mechanism.
+\item Improve accuracy by calibrating noise to a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
+% Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
 % \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
@@
 \begin{itemize}
-  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.
+  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots, x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.
 
@@
 
-  \item[-] Posterior distribution over theta: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
+  \item[-] Posterior distribution over $\theta$: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
 \end{itemize}
@@
 the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
-  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieves at edges as in Fig.
+  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions is attained at edges as in Fig.
 \ref{fig_sensitivity}.
-But it's very low when move away from edge.
+But local sensitivity is very smooth and much smaller when move away from edge.
 Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
@@
 
-given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, where:
+given as input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, where:
 
 \begin{itemize}
-  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
+  \item[-] $\betaset$ is the set of candidates, defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
 
@@
 
-   \item $\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
+   \item $\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure $(\epsilon,\delta)$-differential privacy.
  \end{itemize}
@@
 \ref{fig_sampling} and Fig.
-\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.
+\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10,000$ times under each data size or prior configuration.
 

### 2018-10-11 codes/accuracy_by_sampling.py

@@ -28,12 +28,12 @@ def plot_error_box(data, xlabel, xstick, title, legends, colors):
 	# meanlineprops = dict(linestyle='--', linewidth=2.5, color='purple')
 	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', vert=2, whis=1.5, patch_artist=True, medianprops=medianprops)#, meanprops=meanlineprops, meanline=True,showmeans=True)
 	plt.xlabel(xlabel,fontsize=15)
-	plt.ylabel('Hellinegr Distance',fontsize=15)
+	plt.ylabel('Hellinger Distance',fontsize=15)
 	#ax.set_xlim(0.5, len(errors) + 0.5)
 
 
 	plt.xticks([i*l + (l+1)/2.0 for i in range(len(xstick))],xstick,rotation=40,fontsize=12)
-	plt.title(title,fontsize=20)
+	plt.title(title,fontsize=15)
 
 	for i in range(1, len(bplot["boxes"])/l + 1):
 		for j in range(l):
@@ -217,11 +217,11 @@ if __name__ == "__main__":
 #SETTING UP THE PARAMETERS
 #############################################################################
 
-	datasize = 150
+	datasize = 100
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1,1])
-	dataset = [50,50,50]
+	prior = dirichlet([1,1])
+	dataset = [50,50]
 #############################################################################
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS
 #############################################################################
@@ -242,7 +242,7 @@ if __name__ == "__main__":
 #DOING PLOTS OF ACCURACY V.S. THE PRIOR
 #############################################################################
 
-	# accuracy_VS_prior(datasize,epsilon,delta,priors,dataset)
+	accuracy_VS_prior(datasize,epsilon,delta,priors,dataset)
 
 #############################################################################
 #DOING PLOTS OF ACCURACY V.S. THE PRIOR AND MEAN

### 2018-10-11 TPDP2018/poster/main.tex
update poster

@@
 \begin{itemize}
-  \item[-] $\betaset$ is the set of candidates, defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
+  \item[-] $\betaset$: the set of candidates defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
 
@@
 
-  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
+  \item[-] $S(\dataobs)$ is the smooth sensitivity\cite{nissim2007smooth}:
   $
@@
   \begin{itemize}
-   \item $d$: Hamming distance between two data sets,
+   \item $d$ denotes the Hamming distance between two data sets,
 
-   \item $LS(\dataobs')$, local sensitivity at $\dataobs'$:
+   \item $LS(\dataobs')$ is local sensitivity at $\dataobs'$:
    $
@@
 \ref{fig_sampling} and Fig.
-\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10,000$ times under each data size or prior configuration.
+\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling $10000$ times under each data size or prior configuration.
 

### 2018-10-11 codes/discrete_probability.py

@@ -16,6 +16,10 @@ from dirichlet import dirichlet
 from dpbayesinfer import BayesInferwithDirPrior
 
 
+#############################################################################
+#CALCULATING THE DISCRETE PROBABILITIES
+#############################################################################
+
 def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 
 
@@ -31,7 +35,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 #############################################################################
 
 	for i in Bayesian_Model._candidates:
-		Bayesian_Model._candidate_scores[i] = round(Bayesian_Model._candidate_scores[i], 6)
+		Bayesian_Model._candidate_scores[i] = round(Bayesian_Model._candidate_scores[i], 7)
 
 #############################################################################
 #SORT the scores and put them into bins
@@ -91,8 +95,9 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 	#SENSITIVITY SETTING
 	#############################################################################
+	
 	def sensitivity_setting(dimension):
-		if dimension = 2:
+		if dimension == 2:
 			return (1.0,2.0)
 		else:
 			return (2.0,dimension*1.0)
@@ -121,6 +126,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 
 		laplace_probabilities_1[r] = t1 #/ (math.gamma(len(yset)) * (2 ** (len(list(filter(lambda a: a != 0, ylist))))))
 		laplace_probabilities_2[r] = t2 #/ (math.gamma(len(yset)) * (2 ** (len(list(filter(lambda a: a != 0, ylist))))))
+	
 	#############################################################################
 	#SUM UP the tail Laplace prob
 	#############################################################################
@@ -174,7 +180,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 
 	plt.xlabel("c / Hellinger distance from true posterior")
 	plt.ylabel("Pr[H(BI(x),r) = c]")
-	plt.title("Discrete Probabilities")
+	plt.title("Discrete Probabilities", fontsize=15)
 	plt.legend()
 	plt.grid()
 	plt.show()
@@ -236,11 +242,11 @@ if __name__ == "__main__":
 #############################################################################
 #SETTING UP THE PARAMETERS
 #############################################################################
[…]

### 2018-10-11 TPDP2018/poster/main.tex
some work

--- 2018-10-11 poster/main.tex
@@
 \author{Mark Bun$^\dag$,
-%Imdea Software\\[-3mm]
-%\texttt{gjbarthe@gmail.com} \\
-%\And 
 Gian Pietro Farina$^{*}$,
-%University of Dundee\\[-3mm] 
-%\texttt{g.p.farina@dundee.ac.uk} \\
-%\And
 Marco Gaboardi$^{*}$,
-%University of Dundee\\[-3mm] 
-%\texttt{m.gaboardi@dundee.ac.uk} \\
-%\And
 Jiawen Liu$^{*}$
-%Imdea Software
-%\texttt{pierre-yves@strub.nu} \\
 }
 
-\institute{$^\dag$Princeton University, $^{*}$University at Buffalo, SUNY} % Institution(s)
+\institute{$^{\dag}$Princeton University, $^{*}$University at Buffalo, SUNY} % Institution(s)
 
@@
 \begin{enumerate}
-\item Designing a differentially private Bayesian inference mechanism.
-\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
-% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
-% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
-%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
+\item Design a differentially private Bayesian inference mechanism.
+\item Improve accuracy by calibrating noise  to the sensitivity of a
+         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
 \end{enumerate}
-% \end{column}
-% \begin{column}{.28\textwidth}
-% \begin{figure}[ht]
-% \centering
-% \includegraphics[width=0.85\textwidth]{poster_0.eps}
-% say something about beta...
-% \caption{\footnotesize{Local sensitivity of Hellinger}}
-% \label{fig_sensitivity}
-% \end{figure}
-% \vspace{.1cm}
-% \end{column}
-% \end{columns}
-
-% \noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
-% \begin{enumerate}
-% \item A differentially private bayesian mechanism,
-% \item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
-% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
-% \end{enumerate}
-
 \end{block}
@@
 
-\begin{block}{Bayesian inference ($\bysinfer$) (A Beta-Binomial model example):}
+\begin{block}{Bayesian inference ($\bysinfer$), the Beta-Binomial model example:}
 % The first subdivided column within the first main column
@@
 \begin{itemize}
-  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.
+  \item  Prior on {\small $\theta: \mathbb{P}_{\theta}= \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data $\dataobs= (x_1,\dots, x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.}
 
-  \item[-] Likelihood function: $\mathbb{L}_{\dataobs | \theta}= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;
+  \item  Likelihood function: {\small $\mathbb{L}_{\theta|\dataobs }= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.}
 
-  \item[-] Posterior distribution over theta: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
+  \item Posterior on {\small $\theta$: $\bysinfer(x)\equiv\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\propto\mathbb{L}_{\theta|\dataobs }\cdot \mathbb{P}_{\theta}$.}
 \end{itemize}
@@
 
-\begin{block}{Differentially Private Bayesian Inference and Motivations}
-Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
+\begin{block}{Differentially private Bayesian inference and motivations}
 \begin{columns} % Subdivide the first main column
@@
 \begin{enumerate}
-  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm.
-But this sensitivity grows linear with the dimension, also we measure results by a different metric.
-Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$).
-%(v.s.
-the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
-  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieves at edges as in Fig.
-\ref{fig_sensitivity}.
-But it's very low when move away from edge.
-Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
-  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
+\item  Baseline approach: 
+  \begin{itemize}
+  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
+  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
+  \item \todo{$S\propto ||\cdot ||_{1}$}.
+  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
+  \end{itemize}
+  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}. 
+\item Another approach:
+  \begin{itemize}
+    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
+    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
+    \end{itemize}
+  \item A better approach:
+    \begin{itemize}
+      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
+    \end{itemize}
 \end{enumerate}
@@
 \includegraphics[width=0.9\textwidth]{poster_0.eps}
-\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
+\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
 \label{fig_sensitivity}
@@
 
-\begin{block}{Smoothed Hellinger Distance Based Exponential Mechanism}
+\begin{block}{Our approach: smoothed Hellinger distance based exponential mechanism}
 
-We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probaiblity:
+We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probability:
 \[
-% \underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
 \mathbb{P}_{r \thicksim \hexpmech} =
@@
 \]
-
-given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, where:
-
-\begin{itemize}
-  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.
-
-  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function based on the Hellinger distance.
-
-  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
-  $
-  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
-  $,
 where:
 \begin{itemize}
-   \item $d$: Hamming distance between two data sets,
+ \small{ \item  $\betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$. With prior distribution $\bprior=\betad(\alpha, \beta)$.}
+  \item \small{$-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function.}
 
-   \item $LS(\dataobs')$, local sensitivity at $\dataobs'$:
-   $
-   LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
-   $,
-
-   \item $\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
- \end{itemize}
+  \item \small{$S(\dataobs)\equiv \max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}$: smooth sensitivity\cite{nissim2007smooth}}, $d$ is the
+    Hamming distance.
+   \item \small{$LS(\dataobs')\equiv\max\limits_{y\in \datauni^n:\adj{y}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(y), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$ is the local sensitivity of $\dataobs',\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$}.
  \end{itemize}
@@
   \begin{block}{Preliminary Experimental Results}
-% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
     Experiments are on three mechanisms and plotted as follows:
 \begin{itemize}
-  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
-  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
+  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
+  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
   (posteriors of adjacent data sets differ only in two dimensions).
-  \item[-] \textbf{Blue}: $\hexpmech$.
+  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
 \end{itemize}
-  Fig.
-\ref{fig_sampling} and Fig.
-\ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.
-
+% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
+% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
+% by showing the quartiles of the experimental distribution of the Hellinger distance.
 \begin{figure}[H]
@@
 \centering
+  \subfigure[2 dimensions with data size $600$]{
+    \includegraphics[width=0.31\textwidth]{poster_5.eps}
+  \label{subfig_concrete_prob_2d}
+  }
+  \subfigure[3 dimensions with data size $600$]{
+    \includegraphics[width=0.31\textwidth]{poster_6.eps}
+  \label{subfig_concrete_prob_3d}
+  } 
+\subfigure[2 dimensions with data size $100$]{
+    \includegraphics[width=0.313\textwidth]{poster_4.eps}
+  \label{subfig_prior}
+  }
+
+% \caption{4-quantile and discrete probability plots}
+% \label{fig_concrete_prob}
+% \end{center}
+% \end{figure}
+% % Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
+%   Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior.
+% \begin{figure}[H]
+% \begin{center}
+% \centering
   \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
@@
   }
-  \caption{Average accuracy by increasing data set size}
+  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
+    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
 \label{fig_sampling}
 \end{center}
+
 \end{figure}
 
-Fig.
-\ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities.
-On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
-\begin{figure}[H]
-\begin{center}
-\centering
-   \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.313\textwidth]{poster_4.eps}
-  \label{subfig_prior}
-  }
-  \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.31\textwidth]{poster_5.eps}
-  \label{subfig_concrete_prob_2d}
-  }
-  \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.31\textwidth]{poster_6.eps}
-  \label{subfig_concrete_prob_3d}
-  } 
-\caption{4-quantile and discrete probability plots}
-\label{fig_concrete_prob}
-\end{center}
-\end{figure}
-\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
 \end{block}

### 2018-10-11 TPDP2018/poster/main.tex
update poster

@@
   \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
-  approach when the latter uses a sensitivity proportional to dimensionality.
+  approach but not the improved one.
   \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.

### 2018-10-11 codes/discrete_probability.py

@@ -247,11 +247,11 @@ if __name__ == "__main__":
 #############################################################################
 #SETTING UP THE PARAMETERS
 #############################################################################
-	datasize = 600
+	datasize = 1000
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1,1])
-	dataset = [200,200,200]
+	prior = dirichlet([1,1])
+	dataset = [500,500]
 
 #############################################################################
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS

### 2018-10-11 TPDP2018/poster/main.tex
update conclusion

@@
 \begin{itemize}
-  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
+  \item[-] The $\hexpmech$ outperforms asymptotically the baseline 
   approach but not the improved one.
-  \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.
+  \item[-] By increasing the prior, $\hexpmech$ can outperform LapMech under small data set size.
   % \begin{enumerate}

### 2018-10-11 TPDP2018/poster/main.tex
some more work on the poster

@@
 
-  \begin{block}{Preliminary Experimental Results}
-    Experiments are on three mechanisms and plotted as follows:
+  \begin{block}{Preliminary experimental results}
+    Experiments are about three mechanisms and plotted as follows:
 \begin{itemize}
   \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
-  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
-  (posteriors of adjacent data sets differ only in two dimensions).
+  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
+    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.
+
   \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
@@
 \begin{itemize}
-  \item[-] The $\hexpmech$ outperforms asymptotically the baseline 
-  approach but not the improved one.
-  \item[-] By increasing the prior, $\hexpmech$ can outperform LapMech under small data set size.
+  \item[-]  $\hexpmech$ outperforms the baseline approach but not the improved one.
+  \item[-] By increasing the prior, $\hexpmech$ can outperform both the baseline approach and the improved one.
   % \begin{enumerate}

### 2018-10-11 TPDP2018/poster/main.tex
fixing typos...

@@
 % \begin{column}{.69\textwidth}
-\begin{enumerate}
+\begin{itemize}
 \item Design a differentially private Bayesian inference mechanism.
@@
          metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
-\end{enumerate}
+\end{itemize}
 \end{block}
@@
 
-\begin{block}{Bayesian inference ($\bysinfer$), the Beta-Binomial model example:}
+\begin{block}{An example of Bayesian inference: the Beta-Binomial model}
 % The first subdivided column within the first main column
@@
 
-\begin{block}{Differentially private Bayesian inference and motivations}
+\begin{block}{Differentially private Bayesian inference}
 \begin{columns} % Subdivide the first main column
   \begin{column}{.69\textwidth}
-\begin{enumerate}
+    \vspace{-3cm}
+\begin{itemize}
 \item  Baseline approach: 
@@
   \end{itemize}
+  \end{itemize}
   {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
-\item Another approach:
-  \begin{itemize}
-    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
-    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
-    \end{itemize}
-  \item A better approach:
-    \begin{itemize}
-      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
-    \end{itemize}
-\end{enumerate}
 \end{column}
@@
 \end{columns}
+    \vspace{-1cm}
+\begin{itemize}
+\item Another approach:
+  \begin{itemize}
+    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
+    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
+    \end{itemize}
+  \item A better approach:
+    \begin{itemize}
+      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
+    \end{itemize}
+\end{itemize}
 
@@
 \]
-where:
 \begin{itemize}
@@
 \begin{itemize}
-  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
-  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
+  \item {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
+  \item {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
     Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.
 
-  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
+  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
+    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
 \end{itemize}
@@
 \begin{itemize}
-  \item[-]  $\hexpmech$ outperforms the baseline approach but not the improved one.
-  \item[-] By increasing the prior, $\hexpmech$ can outperform both the baseline approach and the improved one.
-  % \begin{enumerate}
+  \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
+  \item By increasing the prior parameters, $\hexpmech$ can outperform both the baseline approach and the improved one.
+  % \begin{itemize}
   %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
@@
   %   \item Other application of our scheme are going to be explored.
-  % \end{enumerate}
+  % \end{itemize}
 \end{itemize}

### 2018-10-13 TPDP2018/poster/main.tex
update poster and plots

@@
   \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
-  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
-  \item \todo{$S\propto ||\cdot ||_{1}$}.
+  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$
+  % \item \todo{$S\propto ||\cdot ||_{1}$}.
+  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$
   \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
@@
   \end{itemize}
-  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
+  {\color{red}{But $\Delta \bysinfer$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
 \end{column}
@@
   \item {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
-  \item {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
-    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.
+  \item {\textbf{\color{red}{Red}}}: Improved approach by using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
+    Indeed: we can see the output of the Bayesian inference as a histogram, so the $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.
 
@@
 \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.313\textwidth]{poster_4.eps}
+    \includegraphics[width=0.313\textwidth]{poster_6.eps}
   \label{subfig_prior}
@@
 
-% \caption{4-quantile and discrete probability plots}
-% \label{fig_concrete_prob}
-% \end{center}
-% \end{figure}
-% % Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
-%   Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior.
-% \begin{figure}[H]
-% \begin{center}
-% \centering
-  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
-    \includegraphics[width=0.333\textwidth]{poster_1.eps}
-    \label{subfig_sampling_2d}
+  % \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
+  %   \includegraphics[width=0.333\textwidth]{poster_1.eps}
+  %   \label{subfig_sampling_2d}
+  % }
+
+  \subfigure[2 dimensions with data size $100$]{
+    \includegraphics[width=0.313\textwidth]{poster_4.eps}
+  \label{subfig_prior}
   }
@@
   \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
-  \item By increasing the prior parameters, $\hexpmech$ can outperform both the baseline approach and the improved one.
+  \item By increasing the priors parameter, we can be comparable to the improved one.
   % \begin{itemize}

### 2018-10-13 codes/accuracy_by_sampling.py

@@ -26,7 +26,7 @@ def plot_error_box(data, xlabel, xstick, title, legends, colors):
 	plt.figure(figsize=(0.5*len(data),9))
 	medianprops = dict(linestyle='--', linewidth=3.0, color='lightblue')
 	# meanlineprops = dict(linestyle='--', linewidth=2.5, color='purple')
-	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', vert=2, whis=1.5, patch_artist=True, medianprops=medianprops)#, meanprops=meanlineprops, meanline=True,showmeans=True)
+	bplot = plt.boxplot(data, notch=1, widths=0.4, sym='+', showfliers=False, vert=2, whis=1.2, patch_artist=True, medianprops=medianprops)#, meanprops=meanlineprops, meanline=True,showmeans=True)
 	plt.xlabel(xlabel,fontsize=15)
 	plt.ylabel('Hellinger Distance',fontsize=15)
 	#ax.set_xlim(0.5, len(errors) + 0.5)
@@ -76,7 +76,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
 		Bayesian_Model._set_observation(observation)
 		print("start" + str(observation))
-		Bayesian_Model._experiments(3000)
+		Bayesian_Model._experiments(10000)
 		print("finished" + str(observation))
 		# mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
 		# mean_error[1].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[0]])
@@ -234,7 +234,7 @@ if __name__ == "__main__":
 	datasizes = gen_datasizes((600,600),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.5,0.5]
 	datasets = gen_datasets(percentage, datasizes)
-	priors = [dirichlet([1,1])] + gen_priors([5,20], 5, 2) + gen_priors([40,100], 20, 2) + gen_priors([150,300], 50, 2) + gen_priors([400,400], 50, 2)
+	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2) + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)
 	
[…]

### 2018-10-13 codes/discrete_probability.py

@@ -22,6 +22,7 @@ def LAPLACE_CDF(interval, scale):
 	else:
 		return (0.5 * math.exp( (interval[1]*1.0/scale))) - (0.5 * math.exp( (interval[0]/scale)))
 
+
 #############################################################################
 #CALCULATING THE DISCRETE PROBABILITIES
 #############################################################################
@@ -269,11 +270,14 @@ def discrete_probabilities_from_file(filenames,labels,savename):
 def gen_dataset(v, n):
 	return [int(n * i) for i in v]
 
+
 def gen_datasets(v, n_list):
 	return [gen_dataset(v,n) for n in n_list]
 
+
 def gen_datasizes(r, step):
 	return [i*step for i in range(r[0]/step,r[1]/step + 1)]
+
 
 def gen_priors(r, step, d):
 	return [dirichlet([step*i for j in range(d)]) for i in range(r[0]/step,r[1]/step + 1)]
@@ -284,11 +288,11 @@ if __name__ == "__main__":
 #############################################################################
 #SETTING UP THE PARAMETERS
 #############################################################################
-	datasize = 300
+	datasize = 100000
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1,1])
-	dataset = [100,100,100]
+	prior = dirichlet([1,1])
+	dataset = [50000,50000]
 
 #############################################################################
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS

### 2018-10-13 codes/dpbayesinfer.py

@@ -152,6 +152,7 @@ class BayesInferwithDirPrior(object):
 		# self._keys.append(key2)
 
 	def _set_SS_probabilities(self):
+		nomalizer = 0.0
 		for r in self._candidates:
 			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._SS))
 			self._SS_probabilities.append(temp)
@@ -364,13 +365,13 @@ class BayesInferwithDirPrior(object):
 		self._set_GS()
 		self._set_LS()
 		self._set_SS()
-		self._set_SS_probabilities
+		self._set_SS_probabilities()
 		self._keys.append('Laplace_s2')
 		self._accuracy['Laplace_s2'] = []
 		self._accuracy_mean['Laplace_s2'] = []
 		#self._show_all()
 		for i in range(times):
-			self._laplace_noize(sensitivity = 2.0)
+			self._laplace_noize(sensitivity = 1.0)
 			# print self._laplaced_posterior._alphas
 			self._accuracy[self._keys[0]].append(self._posterior - self._laplaced_posterior)
 			# self._laplace_noize()
@@ -389,7 +390,7 @@ class BayesInferwithDirPrior(object):
 			# self._accuracy[self._keys[4]].append(self._posterior - self._SS_posterior)
 			self._exponentialize_SS()
 			self._accuracy[self._keys[3]].append(self._posterior - self._exponential_posterior)
-			self._laplace_noize(sensitivity = 3.0)
+			self._laplace_noize(sensitivity = 2.0)
 			# print self._laplaced_posterior._alphas
 			self._accuracy[self._keys[4]].append(self._posterior - self._laplaced_posterior)
 			

### 2018-10-13 codes/discrete_probability.py
update codes

@@ -288,11 +288,11 @@ if __name__ == "__main__":
 #############################################################################
 #SETTING UP THE PARAMETERS
 #############################################################################
-	datasize = 100000
+	datasize = 600
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1])
-	dataset = [50000,50000]
+	prior = dirichlet([1,1,1,1])
+	dataset = [150,150,150,150]
 
 #############################################################################
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS

### 2018-10-13 TPDP2018/poster/main.tex
update codes
added hellinger def. and fixed typos

@@
 \usepackage[orientation=landscape,size=custom,width=101.6,height=76.2,scale=1.4]{beamerposter}
+\makeatletter
+\providecommand*{\diff}%
+{\@ifnextchar^{\DIfF}{\DIfF^{}}}
+\def\DIfF^#1{%
+\mathop{\mathrm{\mathstrut d}}%
+\nolimits^{#1}\gobblespace}
+\def\gobblespace{%
+\futurelet\diffarg\opspace}
+\def\opspace{%
+\let\DiffSpace\!%
+\ifx\diffarg(%
+\let\DiffSpace\relax
+\else
+\ifx\diffarg[%
+\let\DiffSpace\relax
+\else
+\ifx\diffarg\{%
+\let\DiffSpace\relax
+\fi\fi\fi\DiffSpace}
 %\usepackage[orientation=portrait,size=a0,scale=1.4]{beamerposter} % Use the beamerposter package for laying out the poster with a portrait orientation and an a0 paper size
@@
   \begin{column}{.69\textwidth}
-    \vspace{-3cm}
+    \vspace{-2.0cm}
 \begin{itemize}
@@
   \begin{itemize}
-  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
-  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$
+  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$.
+  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$.
   % \item \todo{$S\propto ||\cdot ||_{1}$}.
-  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$
-  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
+  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$.
+  \item Measure accuracy with a metric over distributions. E.g. $\hellinger(f,g)^2\equiv 1- \int(\sqrt{f(x){g(x)}}\diff x)$ ($f,g$ densities).
   \end{itemize}
   \end{itemize}
-  {\color{red}{But $\Delta \bysinfer$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
+  {\color{blue}{But $\Delta \bysinfer$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
 \end{column}
@@
   \begin{itemize}
-    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
+    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{blue}{but global sensitivity is still too big.}}
     \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
     \end{itemize}
-  \item A better approach:
+  \item A different approach:
     \begin{itemize}
@@
   \item {\textbf{\color{red}{Red}}}: Improved approach by using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
-    Indeed: we can see the output of the Bayesian inference as a histogram, so the $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.
+    Indeed: we can see the output of the Bayesian inference as a histogram, and $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.
 
@@
 \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.313\textwidth]{poster_6.eps}
+    \includegraphics[width=0.31\textwidth]{poster_6.eps}
   \label{subfig_prior}
@@
   \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.313\textwidth]{poster_4.eps}
+    \includegraphics[width=0.314\textwidth]{poster_4.eps}
   \label{subfig_prior}
@@
   \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
-    \includegraphics[width=0.302\textwidth]{poster_2.eps}
+    \includegraphics[width=0.31\textwidth]{poster_2.eps}
   \label{subfig_sampling_3d}
@@
   \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
-    \includegraphics[width=0.295\textwidth]{poster_3.eps}
+    \includegraphics[width=0.304\textwidth]{poster_3.eps}
     \label{subfig_sampling_4d}
@@
 \begin{itemize}
-  \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
-  \item By increasing the priors parameter, we can be comparable to the improved one.
+  \item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
+  \item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
   % \begin{itemize}

### 2018-10-13 TPDP2018/poster/main.tex
update the prior plots
size adjust

@@
   \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.31\textwidth]{poster_5.eps}
+    \includegraphics[width=0.312\textwidth]{poster_5.eps}
   \label{subfig_concrete_prob_2d}
@@
   \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.31\textwidth]{poster_6.eps}
+    \includegraphics[width=0.312\textwidth]{poster_6.eps}
   \label{subfig_concrete_prob_3d}
@@
 \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.31\textwidth]{poster_6.eps}
+    \includegraphics[width=0.308\textwidth]{poster_4.eps}
   \label{subfig_prior}
@@
 
-  % \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
-  %   \includegraphics[width=0.333\textwidth]{poster_1.eps}
-  %   \label{subfig_sampling_2d}
+  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
+    \includegraphics[width=0.333\textwidth]{poster_1.eps}
+    \label{subfig_sampling_2d}
+  }
+  % \subfigure[2 dimensions with data size $100$]{
+  %   \includegraphics[width=0.314\textwidth]{poster_4.eps}
+  % \label{subfig_prior}
   % }
-
-  \subfigure[2 dimensions with data size $100$]{
-    \includegraphics[width=0.314\textwidth]{poster_4.eps}
-  \label{subfig_prior}
-  }
   \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
-    \includegraphics[width=0.31\textwidth]{poster_2.eps}
+    \includegraphics[width=0.301\textwidth]{poster_2.eps}
   \label{subfig_sampling_3d}
@@
   \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
-    \includegraphics[width=0.304\textwidth]{poster_3.eps}
+    \includegraphics[width=0.294\textwidth]{poster_3.eps}
     \label{subfig_sampling_4d}
   }
-  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
-    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
+  \caption{{\footnotesize Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
+      balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }}
 \label{fig_sampling}

### 2018-10-18 notes/proof-practice/main.tex
update gaussian notes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University/School Laboratory Report
% LaTeX Template
% Version 3.1 (25/3/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Linux and Unix Users Group at Virginia Tech Wiki 
% (https://vtluug.org/wiki/Example_LaTeX_chem_lab_report)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=3.5cm}
\usepackage[version=3]{mhchem} % Package for chemical equation typesetting
\usepackage{siunitx} % Provides the \SI{}{} and \si{} command for typesetting SI units
\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements 
\usepackage{datetime}
\setlength\parindent{0pt} % Removes all indentation from paragraphs

\renewcommand{\labelenumi}{\alph{enumi}.} % Make numbering in the enumerate environment by letter rather than number (e.g. section 6)

%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{\textbf{Proof of DP - Bayesian Inference}\\
% \begin{large}
% \textbf{Probability Distributions and Bayesian Networks}% Title
% \end{large}
}
\author{Jiawen \textsc{Liu}} % Author name

% \date{\currenttime\ \today} % Date for the report

\begin{document}

\maketitle % Insert the title, author and date

% \begin{center}
% \begin{tabular}{l r}
% Date Performed: & January 1, 2012 \\ % Date the experiment was performed
% %Partners: & James Smith \\ % Partner names
% %& Mary Smith \\
% Instructor: & Professor Sargur N. Srihari % Instructor/supervisor
% \end{tabular}
% \end{center}

% If you wish to include an abstract, uncomment the lines below
% \begin{abstract}
% Abstract text
% \end{abstract}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
If we want the posterior distribution from the Bayesian inference is $\epsilon$ - differential privacy, this mechanism should satisfy:
\begin{equation*}
\frac{Pr[BayesInfer_{DP}(d_1) \in S]}{Pr[BayesInfer_{DP}(d_2) \in S]} \leq e^{\epsilon},
\end{equation*}
where $BayesInfer_{DP}$ is a differentially private Bayesian inference mechanism: $d \rightarrow posterior\ distribution$. $d_1$, $d_2$ is a pair of adjacent observed data sets. Since in our model, this inference is based on a bias $p$ with beta prior distribution: $p \sim Beta(\alpha_0, \beta_0)$ and an observed data set $d \sim B(n,p)$, which result in a posterior distribution on $p \sim Beta(\alpha_0 + k, \beta_0 + l)$ where $k$ and $l$ is the number of $1$ and $0$ in $d$. As a result, the requirement above can be rewrote as:
\begin{equation*}
\frac{Pr[Beta(\alpha_0 + k^*_1, \beta_0 + l^*_1) \in S]}{Pr[Beta(\alpha_0 + k^*_2, \beta_0 + l^*_2) \in S]} \leq e^{\epsilon},
\end{equation*}
where $k^*_1$ and $l^*_1$ is the number of $1$ and $0$ in $d_1$ after protection, the same with $k^*_2$ and $l^*_2$.  $S\subseteq B = \{Beta(a,b) | a,b \in N\}$. The equation above is equivalent to:
\begin{equation*}
\frac{Pr[\langle \alpha_0 + k^*_1, \beta_0 + l^*_1 \rangle = S]}{Pr[ \langle \alpha_0 + k^*_2, \beta_0 + l^*_2 \rangle = S]} \leq e^{\epsilon}.
\end{equation*}

Under Laplace mechanism, the sensitivity of $BayesInfer_{DP}: d \rightarrow k$, $d \rightarrow l$ are both $1$, we have $k^* = k + Lap(\frac{1}{\frac{\epsilon}{2}}) = k + Lap(\frac{2}{\epsilon})$, and $l^* = l + Lap(\frac{2}{\epsilon})$. When $\langle \alpha_0 + k^*, \beta_0 + l^* \rangle = S$, since $S = Beta(s_1,s_2) = \langle s_1, s_2 \rangle $, we have $ (s_1 - \alpha_0  - k) \sim Lap(\frac{2}{\epsilon}), (s_2 - \beta_0 - l) \sim Lap(\frac{2}{\epsilon})$. Then,
\begin{equation*}
\frac{Pr[\langle \alpha_0 + k^*_1, \beta_0 + l^*_1 \rangle = S]}{Pr[\langle \alpha_0 + k^*_2, \beta_0 + l^*_2 \rangle = S]} = \frac{exp(-\frac{(s_1 - \alpha_0  - k_1)}{\frac{2}{\epsilon}})) exp(-\frac{(s_2 - \beta_0  - l_1)}{\frac{2}{\epsilon}}))}{exp(-\frac{(s_1 - \alpha_0  - k_2)}{\frac{2}{\epsilon}})) exp(-\frac{(s_2 - \beta_0  - l_2)}{\frac{2}{\epsilon}}))} = exp(\epsilon)
\end{equation*}
i.e.
\begin{equation*}
\frac{Pr[BayesInfer_{DP}(d_1) \in S]}{Pr[BayesInfer_{DP}(d_2) \in S]} \leq e^{\epsilon},
\end{equation*}

%----------------------------------------------------------------------------------------
%	SECTION 6
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

% \bibliographystyle{apalike}

% \bibliography{dp-proof}

%----------------------------------------------------------------------------------------

\end{document}

### 2018-10-21 fullpaper/main.tex
update full paper

--- 2018-09-26 paper/main.tex
@@
 
-\subsection{Baseline Approach}
-
-\subsubsection{Laplace Mechanism}
-\label{subsec_lap}
+\subsection{Baseline Approaches}
 
 \subsubsection{Exponential Mechanism}
-\label{subsec_emgs}
-
-% \subsubsection{Mechanism Set up}
 
@@
 Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
-Since $\hlg$ is monotonic, i.e.
-our utility function is monotonic.
-
-% \subsubsection{Security Analysis}
-% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
-For adjacent data set $||x,y||_1 = 1$:
-% \begin{equation*}
-% \begin{split}
-% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-% & =\frac
-% {\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
-% {\frac
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
-% & = \left(\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp\left(\frac
-% {\epsilon (u(x,r) - u(y,r))}
-% {2 \Delta_{g}u}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & \leq
-% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp(\epsilon).
-% \end{split}
-% \end{equation*}
-
-% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
 
@@
 
-\subsection{Our Approach - Exponential Mechanism with Smooth Sensitivity}
+\subsubsection{Laplace Mechanism}
+\begin{itemize}
+  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$.
+  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$.
+  % \item \todo{$S\propto ||\cdot ||_{1}$}.
+  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$.
+  \end{itemize}
+
+\subsubsection{Improved Baseline Approach}
+
+y using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
+    Indeed: we can see the output of the Bayesian inference as a histogram, and $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.
+
+\subsection{Our approach: smoothed Hellinger distance based exponential mechanism}
 \label{sec_smoo}
@@
 
-\subsubsection{Sliding Property of Exponential Mechanism}
+\subsubsection{Sliding Property of $\hexpmech$}
 \begin{lem}
@@
 
-\subsubsection{Dilation Property of Exponential Mechanism}
+\subsubsection{Dilation Property of $\hexpmech$}
 \begin{lem}

### 2018-10-21 codes/sampling_on_gaussian_bayesinfer.py

@@ -117,7 +117,7 @@ if __name__ == "__main__":
 	known_variance = 1.0
 	data = gen_data(datasize, 0.1)
 	rounds = 1000
-	datas = gen_datas([199, 299, 399, 499, 599, 699],[0.1 for i in range(6)])#[9,19,29,39,49,99,199,299],[0.1 for i in range(8)])
+	datas = gen_datas([9, 99, 199, 299, 399, 499, 599, 699, 999],[0.1 for i in range(9)])#[9,19,29,39,49,99,199,299],[0.1 for i in range(8)])
 
 
 	sampling_experiments(prior, datas, known_variance, epsilon, delta, rounds)

### 2018-10-21 fullpaper/main.tex
update notes and full paper

@@
 
-\section{An informal motivation}
+\section{Introduction}
+\label{sec_intro}
+
+\section{Motivation}
 \label{sec_intro}
@@
 \[
-  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
+  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
 \]
@@
 where $\Delta\alpha$ is as defined in Section
-\ref{sec_background}. Notice that $\betaset$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\betaset$
+\ref{sec_background}. Notice that $\candidateset$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\candidateset$
 that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
@@
 
-Exponential mechanism $\expmech{}{x}$ samples a element from the candidate set $\betaset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{}{x}}{Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 GS(x)})}
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 GS})}
 {\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
@@
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}$ share the same candidate set and utility function as it with global sensitivity.
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with global sensitivity.
 This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{local}{x}}{\Pr}[z=r] = \frac
+\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
@@
 \label{def_smoo}
-The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
+The mechanism $\hexpmech(x)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
+{\displaystyle\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
@@
 This mechanism is based on the basic exponential mechanism
-\cite{talwar}, with $\betaset$ as the range and
+\cite{talwar}, with $\candidateset$ as the range and
 $\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
@@
 \]
-and by replacing the $\betaset$ with set of posterior Dirichlet
+and by replacing the $\candidateset$ with set of posterior Dirichlet
 distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
@@
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
 will denote by $\hexpmechd$ the mechanism for the
@@
 
-\subsubsection{Sliding Property of $\hexpmech$}
+\section{Privacy Analysis}
+The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.
+
+\subsection{Sliding Property of $\hexpmech$}
 \begin{lem}
-Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
-calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
+Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
 \delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
@@
  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
- $r\in\betaset$ and the probability 
+ $r\in\candidateset$ and the probability 
  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\betaset$ we have:
+ $r\in\candidateset$ we have:
 
@@
 
-\subsubsection{Dilation Property of $\hexpmech$}
+\subsection{Dilation Property of $\hexpmech$}
 \begin{lem}
@@
 		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
-\begin{equation*}
+		\begin{equation}
+		\label{eq_dilation_case2}
 		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-\end{equation*}
-By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
+		\end{equation}
+		Based on the accuracy property of exponential mechanism:
 		\begin{equation*}
 		\begin{split}
-Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
+		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})}\\
 		\end{split}
@@
 
-In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
+		we derived the accuracy bound for $\hexpmech$:
+
+		\begin{equation*}
+		\begin{split}
+		Pr[u(\hexpmech(x)) \leq c] 
+		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)})
+		\end{split}
+		\end{equation*}
+
+		In beta-binomial model, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
 		\begin{equation*}
@@
 
-\subsubsection{Privacy Analysis}
+\subsection{$(\epsilon, \delta)-$Differential Privacy}
 \begin{lem}
@@
 
-% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
-% \begin{equation*}
-% \begin{split}
-% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = \gamma
-% \end{split} 
-% \end{equation*}
+\subsection{Accuracy Bound for Exponential Mechanism}
+\label{subsec_accuracy_global}
+The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
+\begin{equation*}
+Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
+\end{equation*}
+where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal results.
 
-\subsection{Exponential Mechanism with Global Sensitivity}
-\label{subsec_accuracy_global}
-Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
-\end{equation*}
-where $|R|$ is the size of the candidate set.
-Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
-
-\subsection{Exponential Mechanism with Smooth Sensitivity}
+\subsection{Accuracy Bound for $\hexpmech$}
 \label{subsec_accuracy_smoo}
@@
 
-Within the three accuracy bounds, we will mainly use the first one in following analysis.
-
-\subsection{Accuracy Analysis Comparing with Laplace mechanism}
-\label{subsec_accuracy_tradeoff}
-Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.
-
-\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
-In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately.
-In following analysis, we will count the probabilities wrt.
-the steps from correct answer, in order to be more concise.
-For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$.
-Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer.
-i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.
-This will make the results more clear and observable.
-
-\begin{itemize}
-
-	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:
-
-	\begin{equation*}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
-	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
-	\end{equation*}
-
-	Each candidate will occupy a portion of ``$1$'' as their outputting probability.
-Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing.
-That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing.
-More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.
-
-	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set.
-In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d.
-So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:
+Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
 
@@
 \begin{split}
-	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
-	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
-	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
-	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
+Pr[u(\hexpmech(x)) \leq c] 
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
 \end{split}
 \end{equation*}
-	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.
 
-	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing.
-Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.
-
-	\item Then, we do some concrete cases analysis.
-
-	\begin{itemize}
-
-		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are shown in Tab.
-\ref{tab_8}
-
-		\begin{center}
-		\begin{table*}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
-		 \hline
-		\end{tabular}
-		\caption{Probability with Prior $\betad(1,1)$ and data size $8$}
-		\label{tab_8}
-		\end{table*}
-		\end{center}
-
-		Here, there are only 5 kinds of steps from correct answer.
-Our mechanism in the second column is clearly better than Laplace mechanism in the third column.
-When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism.
-On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.
-
-		\item keep the prior unchanged, $\betad(1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for $40$ times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$ shown in Tab.
-\ref{tab_40}
-
-		\begin{center}
-		\begin{table*}
-		 \begin{tabular}{c | c | c} 
-		 \hline
-		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		 \hline\hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
-		 \hline
-		 \multicolumn{3}{c}{$\cdots$}  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
-		 \hline
-		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
-		 \hline
-		\end{tabular}
-		\caption{Probability with Prior $\betad(1,1)$ and data size $40$}
-		\label{tab_40}
-		\end{table*}
-		\end{center}
-
-		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.
-
-		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$.
-Some probabilities from the two mechanisms are listed as follows:
-		% \begin{center}
-		%  \begin{tabular}{c | c | c} 
-		%  \hline
-		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
-		%  \hline\hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
-		%  \hline
-		%  \multicolumn{3}{c}{$\cdots$}  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
-		%  \hline
-		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
-		%  \hline
-		% \end{tabular}
-		% \end{center}
-
-		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly.
-These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism.
-Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.
-
-	\end{itemize}
-
-\end{itemize}
-\subsubsection{Accuracy Analysis wrt. prior distribution}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.48\textwidth]{sensitivity}
-\caption{Hellinger distance study}
-\label{fig_sensitivity}
-\end{figure}
-In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig.
-\ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.
-
-As in Fig.
-\ref{fig_sensitivity}, the local sensitivity of Hellinger distance will decrease when $\betad$ distribution's two parameters get closer (i.e.
-more uniform) and larger.
-In the same time, our smooth sensitivity will also decrease based on the Def.
-\ref{def_smoo}.
-From accuracy bound in Sec.
-\ref{subsec_accuracy_smoo}, the accuracy will be improved when sensitivity go larger.
-In consequence, when we increase the prior distribution, the smooth sensitivity in our exponential mechanism will decrease, which means our accuracy will be improved.
-However, the sensitivity of $l_1$ norm in Laplace mechanism is fixed regardless the prior distribution.
-We will study this trade-off in Sec.
-\ref{subsubsec_vs_prior}.
-
-\subsubsection{Accuracy Analysis wrt. data variance}
-
-Similar as above, when the data variance is small (i.e.
-the data are uniform), the parameters of posterior distribution will get more uniform (i.e.
-closer).
-Based on Fig.
-\ref{fig_sensitivity}, the Hellinger distance's sensitivity will get smaller when parameter get closer.
-As a result, the accuracy will be improved in the same time.
-We will study this trade-off in Sec.
-\ref{subsubsec_vs_variance}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.48\textwidth]{efficiency}
-\label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\end{figure}
+which has been used in the dilation property proof.
 
@@
 It is shown that maximum value taken when  $r = \bysinfer(x)$.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.48\textwidth]{efficiency}
+\label{fig_efficiency}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\end{figure}
 

### 2018-10-21 Arxiv/main.tex
rename folder
update arvix plots and texts

--- 2018-10-21 fullpaper/main.tex
@@
 \section{Motivation}
-\label{sec_intro}
+\label{sec_moti}
 Publishing the posterior distribution inferred from a sensitive dataset can
@@
 \end{equation*}
-where $S_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
+where $S_\beta(x)$ is the smooth sensitivity of $\hellinger(\bysinfer(x),-)$, calculated by:
 
@@
  $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
+ $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
+ \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
  $r\in\candidateset$ we have:
@@
 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]\Big )
+\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
+ \hellinger(\bysinfer(x),r)]\Big )
 $$
 
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
+To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
 We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
 We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
+Because Hellinger distance  $\hellinger(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
 It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
@@
 
-The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
@@
 \section{Accuracy Analysis}
-\subsection{Laplace Mechanism}
+
+\subsection{Accuracy Bound for Laplace Mechanism}
 \label{subsec_accuracy_lap}
-Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
+Accuracy bound for Laplace mechanism is provided by its probability density function:
 \begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
+Pr[|Y| \geq t] = e^{- \frac{t}{b}},
 \end{equation*}
+where $Y \sim Lap(b)$, $b = \frac{GS}{\epsilon}$
 
-So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.
-
-When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d.
-Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output.
-Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.
+After post-processing:  $Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{t - 1}{b}} - e^{- \frac{t}{b}})$.
 
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(x), z)}{S(x)}}}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
+\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
 \end{equation*}
@@
 The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
-i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
+\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hellinger(\bysinfer(x), r) - \hellinger(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hellinger(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
+i.e., the maximum value over $\max\limits_{r \in R}$ always achieves at $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(x), \bysinfer(x)) - \hellinger(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(y'), \bysinfer(x))|\}$.
 We also have some experiments for validating our proposal as in Fig.
@@
 
-\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
+\subsection{Theoretical Results}
+
+\begin{figure}[H]
+\begin{center}
+\centering
+  \subfigure[2 dimensions with data size $600$]{
+    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
+  \label{subfig_theory_2d}
+  }
+  \subfigure[3 dimensions with data size $600$]{
+    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
+  \label{subfig_theory_3d}
+  } 
+\end{center}
+\end{figure}
+
+\subsection{Experimental Results}
 \label{subsec_vs_variables}
+
 In this section, we evaluate the accuracy of the mechanisms defined in
@@
   \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
+    \includegraphics[width=0.45\textwidth]{sampling_2d.eps}
     \label{subsubsec_vs_datasize1a}
   }
-  \subfigure[Data set size from $14000$ to $20000$]{
-    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
-  \label{subsubsec_vs_datasize1b}} 
 \caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
@@
 \centering
-  % \subfigure[Data set size from $300$ to $800$ ]{
-  %   \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
-  %   \label{subsubsec_vs_datasize1adir}
-  % }
   \subfigure[Data set size from $14000$ to $20000$]{
-     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
+     \includegraphics[width=0.45\textwidth]{sampling_3d.eps}   
+  \label{subsubsec_vs_datasize1bdir}
+  } 
+\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_dir}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\centering
+  \subfigure[Data set size from $14000$ to $20000$]{
+     \includegraphics[width=0.45\textwidth]{sampling_4d.eps}   
   \label{subsubsec_vs_datasize1bdir}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
+\includegraphics[width=0.45\textwidth]{sampling_prior.eps}
 \caption{Observed data set is: $(5,5,5)$, varying balanced priors}
@@
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20.eps}}
+    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20.eps}}
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20(2).eps}} 
+    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20(2).eps}} 
 \caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}

### 2018-10-21 Arxiv/main.tex
update arvix paper

@@
 
-\section{Algorithm Setting up}
-\label{sec_setup}
+\section{Mechanisms Introduction}
+\label{sec_mechs}
 Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
@@
 \subsection{Baseline Approaches}
+\label{subsec_baselines}
 
 \subsubsection{Exponential Mechanism}
-
 Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
@@
 \subsection{Our approach: smoothed Hellinger distance based exponential mechanism}
-\label{sec_smoo}
+\label{subsec_hexpmech}
 
@@
 In this section, we evaluate the accuracy of the mechanisms defined in
-Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
+Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
 data variance, prior distribution, and some combinations thereof.
 Every plot is an average over 1000 runs. In all the experiments we set
-$\epsilon = 0.8$, and $\delta = 10^{-8}$.
+$\epsilon = 1.0$, and $\delta = 10^{-8}$.
 
@@
 it represents the performance of a variation of the basic Laplace
-mechanism presented in Section (\ref{sec:base}) with the same
+mechanism presented in Section (\ref{subsec_baselines}) with the same
 settings: that is $\epsilon, \delta$, data, prior. The variation
@@
 \centering
-  \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.45\textwidth]{sampling_2d.eps}
-    \label{subsubsec_vs_datasize1a}
-  }
-\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize}
+    \includegraphics[width=0.48\textwidth]{sampling_2d.eps}
+\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_2d}
 \end{center}
@@
 \centering
-  \subfigure[Data set size from $14000$ to $20000$]{
-     \includegraphics[width=0.45\textwidth]{sampling_3d.eps}   
-  \label{subsubsec_vs_datasize1bdir}
-  } 
-\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_dir}
+     \includegraphics[width=0.48\textwidth]{sampling_3d.eps}   
+\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_3d}
 \end{center}
@@
 \centering
-  \subfigure[Data set size from $14000$ to $20000$]{
-     \includegraphics[width=0.45\textwidth]{sampling_4d.eps}   
-  \label{subsubsec_vs_datasize1bdir}
-  } 
-\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_dir}
+     \includegraphics[width=0.48\textwidth]{sampling_4d.eps}    
+\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_4d}
 \end{center}
@@
 
-In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
-of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
-and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
-Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
-the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
-The results show that when the data size
-increases, the average errors of
-$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
-i.e with size less 650 in the case of Beta-Binomial systems,
-the Laplace mechanisms outperforms the exponential mechanisms,
-but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
+In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
+of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
+the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
+The results show that when the data size increases, the average errors of
+$\hexpmech$, Laplace mechanism and decrease. For small datasets,
+i.e with size less $300$ in the case of Beta-Binomial models,
+both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
+But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
 we considered data sets of the order of 15 thousands elements,
-the exponential mechanisms outperforms the Laplace mechanism.
-Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
-but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
-too high run time of the algorithm.
+the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved baseline Laplace mechanism.
+Similar experimental tendencies were obtained for the Dirichlet-Multinomial system (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
 
@@
 \label{subsubsec_vs_prior}
-In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
-We also considered balanced priors with increasing values in their dimensions.
+In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ .
+We studied the accuracy under different priors, where the priors considered  are also balanced.
 The plot shows that in the beginning the Laplace mechanism performs better but
@@
 \centering
-\includegraphics[width=0.45\textwidth]{sampling_prior.eps}
-\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
+\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
+\caption{Observed data set is: $(50,50)$, varying balanced priors}
 \label{fig_vs_prior}
@@
 
-\subsection{Experiment Evaluations on Privacy}
+\subsection{Experiment Evaluations on Privacy Loss}
 \label{subsec_experiment_privacy}
@@
 The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_smoo} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
+\ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
 We calculate the concrete privacy value in following ways wrt.
@@
     \includegraphics[width=0.21\textwidth]{global_epsilon_20_20(2).eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
+\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
 \label{fig_privacy}

### 2018-10-21 Arxiv/main.tex
update plots onprivacy loss

@@
 
-\subsection{Baseline Approaches}
+\subsection{Baseline Mechanisms}
 \label{subsec_baselines}
@@
 
-\subsubsection{Improved Baseline Approach}
+\subsubsection{Improved Baseline Mechanism}
 
@@
 
-\subsection{Our approach: smoothed Hellinger distance based exponential mechanism}
+\subsection{Our Mechanism: Smoothed Hellinger Distance Based Exponential Mechanism $\hexpmech$}
 \label{subsec_hexpmech}
@@
 we considered data sets of the order of 15 thousands elements,
-the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved baseline Laplace mechanism.
-Similar experimental tendencies were obtained for the Dirichlet-Multinomial system (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
+the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
+Similar experimental tendencies were obtained for the Dirichlet-Multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
 
@@
 We studied the accuracy under different priors, where the priors considered  are also balanced.
-The plot shows that in the beginning the Laplace mechanism performs better but
-it is outperformed after a while.
+Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
 \begin{figure}[H]
@@
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20.eps}}
+    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
   \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20(2).eps}} 
+    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
+  \subfigure[data size range from 90 to 180]{
+    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
+  \subfigure[data size range from 90 to 180]{
+    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
 \caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}

### 2018-10-21 Arxiv/main.tex
update arxiv paper

@@
 We focus on two discrete models, the Beta-Binomial and the
-Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
+Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
 Our mechanism can be understood as a version of  the exponential mechanism
@@
 use to measure accuracy. To show the usefulness of this mechanism we
-show an experimental analysis comparing it with an approach based on
+show an experimental analysis comparing it with mechanisms based on
 the Laplace mechanism.
 \end{abstract}
-
-% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-% \begin{CCSXML}
-% <ccs2012>
-% <concept>
-% <concept_id>10002978.10003029.10011703</concept_id>
-% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-% <concept_significance>500</concept_significance>
-% </concept>
-% </ccs2012>
-% \end{CCSXML}
-
-% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-% % -- end of section to replace with generated code
 
@@
 parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-Multinomial model we are interested in a private version of
+in the case of the Dirichlet-multinomial model we are interested in a private version of
 $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
@@
 the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
-and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
+and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
 This mechanism is $\epsilon$-differentially private, and the noise is
@@
 $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system.
+This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.
 
-\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
+Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
 \[
@@
 where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
-In this work we will use a metric based on a different norm to compute the sensitivity
-and provide guarantees on the accuracy. In particular we will consider a metric
-over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
-Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
-calculations in the case of the probabilistic models considered here
-and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
-an unbounded adversary can have in distingishing two distributions. 
+However, this accuracy metric is meaningless when the object released is a distribution rather than a numerical value, and distribution metrics such as $f$-divergence, Hellinger distance, etc.
+come into mind overtly when we are measuring distance between distributions.
+
+In this work we will use a metric based on a different norm (a distribution metric) to compute the sensitivity
+and provide guarantees on the accuracy. 
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
 Given two beta distributions
@@
 \]
-The same change of metric will be applied to the experimental accuracy guarantees.
 
-\section{Mechanisms Introduction}
+Our choice to use Hellinger distance is motivated by three facts:
+\begin{itemize}
+\item It simplifies calculations in the case of the probabilistic models considered here.
+\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
+an unbounded adversary can have in distingishing two distributions. 
+\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity.
+As shown in Fig.
+\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
+\caption{\footnotesize{Sensitivity of $\hellinger$}}
+\label{fig_sensitivity}
+\end{figure}
+\end{itemize}
+
+\section{Mechanism Proposition}
 \label{sec_mechs}
 Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
-
 \[
-  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
+  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
 \]
-
-where $\Delta\alpha$ is as defined in Section
-\ref{sec_background}. Notice that $\candidateset$ has $n + 1$ elements, and
+where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
+Notice that $\candidateset$ has $n + 1$ elements, and
 the Bayesian Inference process will produce an element from $\candidateset$
@@
 \label{subsec_baselines}
+Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
 
@@
 \end{equation*}
-where $u(x,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS(x)$ is the global sensitivity calculated by:
+where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
 \begin{equation*}
@@
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with global sensitivity.
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
 This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
@@
 
-where local sensitivity is calculated by:
+where $LS(x)$ is the local sensitivity calculated by:
 
@@
 
-\subsubsection{Laplace Mechanism}
-\begin{itemize}
-  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$.
-  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$.
-  % \item \todo{$S\propto ||\cdot ||_{1}$}.
-  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$.
-  \end{itemize}
+\subsubsection{Baseline Mechanism - Laplace Mechanism}
+ Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
 
-\subsubsection{Improved Baseline Mechanism}
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \] 
+ where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+ where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
+$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
 
-y using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
-    Indeed: we can see the output of the Bayesian inference as a histogram, and $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.
+ Then release it as the private posterior distribution.
 
-\subsection{Our Mechanism: Smoothed Hellinger Distance Based Exponential Mechanism $\hexpmech$}
+ The sensitivity used in this baseline mechanism is:
+ \[
+ \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
+ \]
+ which is proportional to the dimensionality.
+
+\subsubsection{Improved Laplace Mechanism}
+
+ Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
+Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+
+ Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \]
+ where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
+
+Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+
+\subsection{ $\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
 \label{subsec_hexpmech}
-
-\subsubsection{Setting up}
 
@@
 
-This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
 \[
@@
 will denote by $\hexpmechd$ the mechanism for the
-Dirichlet-Multinomial system.
+Dirichlet-multinomial system.
 
@@
 \end{equation*}
-where $Y \sim Lap(b)$, $b = \frac{GS}{\epsilon}$
+where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
 
-After post-processing:  $Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{t - 1}{b}} - e^{- \frac{t}{b}})$.
+After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
+\[
+Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
+\]
 
@@
 \end{equation*}
-where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal results.
+where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
 
@@
 the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
-Similar experimental tendencies were obtained for the Dirichlet-Multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
+Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}

### 2018-10-22 Arxiv/main.tex
update computation efficiency

@@
 
-\section{Privacy Analysis}
+\section{Privacy Proof}
 The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.
@@
 
-\subsection{Computation Efficiency}
+\subsection{Computation Efficiency Optimization}
 \label{subsec_effi}
 The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hellinger(\bysinfer(x), r) - \hellinger(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hellinger(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
-i.e., the maximum value over $\max\limits_{r \in R}$ always achieves at $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(x), \bysinfer(x)) - \hellinger(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(y'), \bysinfer(x))|\}$.
-We also have some experiments for validating our proposal as in Fig.
-\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
-It is shown that maximum value taken when  $r = \bysinfer(x)$.
+\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$
+can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
+by applying the distance triangle property.
+
+Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(x)$:
+\begin{equation*}
+\begin{split}
+LS(\dataobs) 
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+\end{split}
+\end{equation*}
+
+This equation is validated by experimental result shown in Fig.
+\ref{fig_efficiency}.
+We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
+It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
 
@@
 \includegraphics[width=0.48\textwidth]{efficiency}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
 \label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
 \end{figure}
@@
   }
+\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
+\label{fig_theory}
 \end{center}
 \end{figure}
+In Fig.
+\ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms.
+We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
+the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.
+
+In Fig.
+\ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line).
+This means $\hexpmech$ can produce good results with larger probability than baseline mechanism.
+However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$.
+It outperforms $\hexpmech$.
 
@@
 \centering
-    \includegraphics[width=0.48\textwidth]{sampling_2d.eps}
+    \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
 \caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
@@
 \centering
-     \includegraphics[width=0.48\textwidth]{sampling_3d.eps}   
+     \includegraphics[width=0.4\textwidth]{sampling_3d.eps}   
 \caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
@@
 \centering
-     \includegraphics[width=0.48\textwidth]{sampling_4d.eps}    
+     \includegraphics[width=0.4\textwidth]{sampling_4d.eps}    
 \caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
@@
 
-In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
-of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
-Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
-the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
-The results show that when the data size increases, the average errors of
+In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
+of observations. The results show that when the data size increases, the average errors of
 $\hexpmech$, Laplace mechanism and decrease. For small datasets,

### 2018-10-22 Arxiv/main.tex
update efficiency plots

@@
 \includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
-\caption{\footnotesize{Sensitivity of $\hellinger$}}
+\caption{{Sensitivity of $\hellinger$}}
 \label{fig_sensitivity}
@@
 
-This equation is validated by experimental result shown in Fig.
+This equation is validated by an experimental result shown in Fig.
 \ref{fig_efficiency}.
-We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
+We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
 It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
@@
 \centering
-  \subfigure[data size range from 90 to 180]{
+  \subfigure[data size range from 50 to 100]{
     \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
-  \subfigure[data size range from 90 to 180]{
+  \subfigure[data size range from 100 to 200]{
     \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
-  \subfigure[data size range from 90 to 180]{
+  \subfigure[data size range from 200 to 500]{
     \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
-  \subfigure[data size range from 90 to 180]{
+  \subfigure[data size range from 500 to 1000]{
     \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 

### 2018-10-22 codes/LocalSensitivityStudy.py

@@ -154,6 +154,10 @@ class BayesInferwithDirPrior(object):
 		self._observation = numpy.random.multinomial(1, self._bias, self._sample_size)
 		self._posterior = Dir(self._observation_counts) + self._prior
 
+	def _set_observation(self,data):
+		self._observation_counts = data
+		self._posterior = Dir(self._observation_counts) + self._prior
+
 	def _set_candidate_scores(self):
 		self._set_candidates([], numpy.sum(self._observation))
 		# for r in self._candidates:
@@ -270,20 +274,22 @@ class BayesInferwithDirPrior(object):
 		y = numpy.array(y)
 		x = numpy.arange(0, len(y), 1)
 		plt.figure(figsize=(80,35))
-		plt.rc('text', usetex=True)
-		plt.rc('font', family='serif')
-		# plt.tight_layout()
-		plt.scatter(x, y, s = 100, c = 'b', marker = 'o', alpha = 0.7, edgecolors='white', label = r"$\displaystyle\max_{\{D'\ adj\ D\}}|H(D,r)-D(D',r)|$")
+		# plt.rc('text', usetex=True)
+		# plt.rc('font', family='serif')
+		fig = plt.gcf()
+		fig.subplots_adjust(bottom=0.1, left=0.05, right= 0.95, top=0.95)
+		plt.tight_layout()
+		plt.scatter(x, y, s = 100, c = 'b', marker = 'o', alpha = 0.7, edgecolors='white', label = r"$\max_{x'\ adj\ x}|\mathcal{H}(x,r)-\mathcal{H}(x',r)|$")
 		plt.axvline(x=xmark, color='r', label = 'True Posterior:'+str(self._posterior._alphas),linewidth = 6.0)
 		plt.ylim(0.0,self._LS_max+0.01)
 		plt.xlim(0.0,len(y)*1.0)
 		plt.grid()
 		plt.legend(prop={'size': 90}, loc="best")
 		plt.xticks(x, labels, rotation='vertical',fontsize=7)
-		plt.xlabel(r"$Candidates\ r\in R\ (3\ Order\ Dirichlet\ Distribution\ with\ Data\ Size\ 50)$", fontsize=70)
-		plt.ylabel(r"$\displaystyle\max_{\{D'\ adj\ D\}}|H(D,r)-D(D',r)|$", fontsize=90)
+		plt.xlabel(r"$Candidates\ r \in R$", fontsize=70)
[…]

### 2018-10-22 codes/main.py

@@ -13,7 +13,7 @@ import statistics
 from decimal import *
 from scipy.special import gammaln
 from dirichlet import dirichlet
-from dpbayesinfer import BayesInferwithDirPrior
+from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 
 
 def draw_error(errors, model, filename):

### 2018-10-22 Arxiv/main.tex
Update Arxiv/main.tex
update reference

@@
 \label{sec_intro}
+Data analysis techniques are broadly used in. The data privacy is the persistent
 
-\section{Motivation}
-\label{sec_moti}
 Publishing the posterior distribution inferred from a sensitive dataset can
@@
 
-\section{Bayesian Inference Background}
-\label{sec_background}
+\noindent \textbf{Main contributions.}
+\begin{itemize}
+	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
+	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
+         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
+	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
+\end{itemize}
+
+\noindent \textbf{Related Work.}
+
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \citet{wang2015differentially}, the gradient decedent algorithm in deep learning \citet{abadi2016deep}, logical regression \citet{chaudhuri2009privacy}, principle component analysis \citet{chaudhuri2012near}, probabilitic inference \citet{williams2010probabilistic} and convergence in statistic estimation \citet{chaudhuri2012convergence}, etc.
+
+In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy.
+There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+\citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zhang2015differential} and \citet{wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private: \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential}  \citet{foulds2016theory}.
+3) The inference process is differentially private and the posterior distribution released should be private itself.
+The third topic where our work focus on is still very new.
+
+\section{Preliminaries}
+\label{sec_Pre}
+
+\noindent \textbf{Bayesian Inference.}
+
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
@@
 recursive fashion over the data.
+
+\noindent \textbf{Beta-binomial System.}
+
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-Specifically, we will consider the situation where $\theta$ represents
+specifically, a Beta-binomial mode. We will consider the situation the underlying data is binomial distribution ($\sim binomial(\theta)$), where $\theta$ represents
 the parameter --informally called \emph{bias}-- of a Bernoulli
-distributed random variable, and its immediate generalization where
-the parameter $\vtheta$ represents the vector of parameters of a
-categorically distributed random variable.  In the former case, the
+distributed random variable. The
 prior distribution over $\theta\in [0,1]$ is going to be a beta
@@
 $\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
-
 \[
@@
 \]
-In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
+
+\noindent \textbf{Dirichlet-multinomial Systems.}
+
+The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data where multinomially distributed.
+The \emph{bias} is represented by parameter $\vtheta$ represents the vector of parameters of a categorically distributed random variable.
+The prior distribution over $\vtheta\in [0,1]^{k}$
 is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
@@
 
-\section{The Problem Statement}
-\label{sec:base}
+\noindent \textbf{Differential Privacy.} 
+\begin{definition}
+$\epsilon-$differential privacy.
+
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+\begin{equation*}
+\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B],
+\end{equation*}
+where $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+\end{definition}
+
+\begin{definition}
+$(\epsilon,\delta)-$differential privacy.
+
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+\begin{equation*}
+\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
+\end{equation*}
+vwhere $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+\end{definition}
+
+\section{Technical Problem Statement and Motivations}
+\label{sec_moti}
 We are interested in designing a mechanism for privately releasing the full posterior
@@
 
-$\epsilon = 0.8$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
+$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
 That is to say, we achieved a higher privacy level than expected.

### 2018-10-22 Arxiv/main.tex
update introduction

@@
 \label{sec_intro}
-Data analysis techniques are broadly used in. The data privacy is the persistent
+Data analysis techniques are broadly used in various applications in different areas to improve their service, including disease-medicine service, financial service, location service, social network and so on.
+In order to provide a better service, large of data are collected from users for analysis.
+As a consequence, the data privacy came to be a critical issue in all data analysis algorithms.
+Sensitivity information in data can be revealed through the analysis results.
+The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.
 
+Plenty of work have been developed to solve this issue(), They guranteed the privacy in specific data analysis algorithms.
+
+Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
 Publishing the posterior distribution inferred from a sensitive dataset can
@@
 There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zhang2015differential} and \citet{wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private: \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential}  \citet{foulds2016theory}.
+\citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}.
 3) The inference process is differentially private and the posterior distribution released should be private itself.
@@
 
-The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data where multinomially distributed.
-The \emph{bias} is represented by parameter $\vtheta$ represents the vector of parameters of a categorically distributed random variable.
+The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data multinomially distributed.
+The \emph{bias} is represented by parameter $\vtheta$, the vector of parameters of a categorically distributed random variable.
 The prior distribution over $\vtheta\in [0,1]^{k}$

### 2018-10-23 Arxiv/main.tex
update proof

@@
 \label{sec_intro}
-Data analysis techniques are broadly used in various applications in different areas to improve their service, including disease-medicine service, financial service, location service, social network and so on.
+Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on.
 In order to provide a better service, large of data are collected from users for analysis.
-As a consequence, the data privacy came to be a critical issue in all data analysis algorithms.
+As a consequence, the data privacy came to be a critical issue.
 Sensitivity information in data can be revealed through the analysis results.
@@
 
-Plenty of work have been developed to solve this issue(), They guranteed the privacy in specific data analysis algorithms.
+Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms.
+They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy.
+But they are not giving better accuracy than the differential privacy mechanism itself.
+Here, we are proposing mechanism with better accuracy.
 
@@
 	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
-         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
+         metric over distributions (e.g.
+Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
+2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
 	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
@@
 \section{Preliminaries}
-\label{sec_Pre}
+\label{sec_background}
 
@@
 \end{equation*}
-where $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+where $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
 \end{definition}
@@
 \end{equation*}
-vwhere $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
 \end{definition}
@@
 
-Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
+However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
 \[
@@
 where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
-However, this accuracy metric is meaningless when the object released is a distribution rather than a numerical value, and distribution metrics such as $f$-divergence, Hellinger distance, etc.
+This accuracy metric is meaningless when the results released are distributions rather than numerical values.
+In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc.
 come into mind overtly when we are measuring distance between distributions.
+This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
+and provide guarantees on the accuracy.
 
-In this work we will use a metric based on a different norm (a distribution metric) to compute the sensitivity
-and provide guarantees on the accuracy. 
 Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
@@
 As shown in Fig.
-\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
+\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
 \begin{figure}[ht]
@@
 
-\subsection{ $\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
+\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
 \label{subsec_hexpmech}
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
 
-\section{Privacy Proof}
-The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.
+\section{Privacy Analysis}
 
-\subsection{Sliding Property of $\hexpmech$}
+\subsection{Privacy Analysis for Baseline Mechanisms}
+In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \citet{dwork2014algorithmic}.
+The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \citet{dwork2014algorithmic}.
+
+\subsection{Privacy Analysis for $\hexpmech$}
+
+The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\
+
+\noindent \textbf{Sliding Property of $\hexpmech$}
 \begin{lem}
@@
  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\candidateset$ we have:
+ \hellinger(\bysinfer(x),r)]$ for the utility score for $r$.
+In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
+More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.
 
+ From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
+ \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
  $$
-\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
+ =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
  \hellinger(\bysinfer(x),r)]\Big )
+ $$ or 
  $$
+ =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
+ $$
+ % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
+We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
+ We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e.
+$u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
 
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
-We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-Because Hellinger distance  $\hellinger(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
-It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-This parameter can be eliminate in both sides in proof.
+ The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.
+
+ In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$.
+The proofs are given by parts:
+
+ \begin{itemize}
+ 	\item for $r \in R_1$:
 
@@
 		\end{equation*}
+	\item for $r \in R_2$: Actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
+\end{itemize}
+
+The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.
 
@@
 
-\subsection{Dilation Property of $\hexpmech$}
+\noindent \textbf{Dilation Property of $\hexpmech$}
 \begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:
 
@@
 where the sensitivity in mechanism is still smooth sensitivity as above.
+
+More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
 \end{lem}
@@
 \begin{proof}
+We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.
 
@@
 
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
+We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.
 
@@
 \textbf{Detail proof:}
+	To show:
+	\begin{equation*}
+	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+	\leq
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
+	\end{equation*}
+	for $z \in R_1$.
 
-	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
+	Let $Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$ and $Pr[u(\hexpmech(x)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(x)})}{NL(x)}$ by definition.
+
+	After simplification, we need to show: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$.
+	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+
 \begin{itemize}
@@
 
-		In beta-binomial model, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
+		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
 		\begin{equation*}
@@
 
+		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
+
 \end{itemize}
@@
 
-\subsection{$(\epsilon, \delta)-$Differential Privacy}
+\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
 \begin{lem}
@@
 \begin{proof}
-of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
+
+For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
+\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z = r] + \delta. 
 \end{equation*}
-Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+
+Let partition $R_1, R_2 \subset \candidateset$ the same as above. Then we prove by part:
+\begin{itemize}
+	\item for $r \in R_1$:
+
+	Given that $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
 Then,
@@
 	\begin{split}
-2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
-& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
-& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
+	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
+	& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\\
+	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\\
+	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
 	\end{split}
 	\end{equation*}
-
-The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
+	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
 The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
 
+	\item for $r \in R_2$:
+
+	Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+Then,
+
+	\begin{equation*}
+	\begin{split}
+	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
+	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
+	\end{split}
+	\end{equation*}
+	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.
+
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
+The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+\end{itemize}
+
+Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.
+
+Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
 \end{proof}
@@
 
-\subsection{Accuracy Bound for Laplace Mechanism}
+\subsection{Accuracy Bound for Baseline Mechanisms}
+
+\subsubsection{Accuracy Bound for Exponential Mechanism}
+\label{subsec_accuracy_global}
+The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
+\begin{equation*}
+Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
+\end{equation*}
+where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
+
+\subsubsection{Accuracy Bound for Laplace Mechanism}
 \label{subsec_accuracy_lap}
@@
 
-\subsection{Accuracy Bound for Exponential Mechanism}
-\label{subsec_accuracy_global}
-The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
-\begin{equation*}
-Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
-\end{equation*}
-where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
+\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
+\label{subsec_accuracy_lap}
+Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
+\[
+Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
+\]
 
@@
     \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
-  \subfigure[data size range from 200 to 500]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
-  \subfigure[data size range from 500 to 1000]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
+  % \subfigure[data size range from 200 to 500]{
+  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
+  % \subfigure[data size range from 500 to 1000]{
+  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
 \caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
@@
 
+\section{Conclusion and Future Work}
+From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:
+
+\begin{enumerate}
+	\item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
+  	\item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
+\end{enumerate}
+
+These results although very motivating, are still not enough for real world applications. Hence, we will continue our work in the follwoing directions:
+\begin{enumerate}
+  \item  For now, we just have a intuitive idea on the accuracy
+behavior of our mechanisms, and not a precise formula or bound on
+it. When do our mechanisms perform better than the baseline mechanism
+and when they don't? How much influence will elements in Section
+\ref{sec_experiment} have on the accuracy? Are there any other
+important factors we missed? These are all questions w.r.t. the
+accuracy that we are going to explore next, and in a more principled
+and formal way.
+\item  Theorem \ref{lem_hexpmech_privacy} provides an upper bound on the
+privacy loss for $\hexpmech$ and $\hexpmechd$ but not necessarily a
+tight one. Indeed, experiments have shown that the actual privacy loss
+in the experiments can be smaller than $\epsilon$. This means that we
+could improve accuracy, by adding less noise -- that is noise
+proportional to a higher value of $\epsilon$-- but still achieve
+$(\epsilon, \delta)$-dp.
+\item The choice of the Hellinger distance might seem quite
+ad-hoc. Hence, it is worth exploring other distances over
+distributions. An interesting class of probability metrics is the
+family of $f$-divergences \cite{CIT-004}.
+\end{enumerate}
+
 \bibliographystyle{ACM-Reference-Format}

### 2018-10-23 notes/fullproof/main.tex
update proof

--- 2018-10-22 Arxiv/main.tex
@@
 \begin{document}
-\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
+\title{Full proof on the differential privacy property of $\hexpmech$}
 
-\begin{abstract} Bayesian inference is a statistical method which
-allows one to derive a \emph{posterior} distribution,
-starting from a \emph{prior} distribution and observed data. Several
-approaches have been explored in order to make this process differentially
-private. For example, \citet{dimitrakakis2014robust}, and
-\citet{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
-designed differentially private mechanisms that output a
-representation of the full posterior distribution.
-
-When the output of a differentially private mechanism is a probability
-distribution, accuracy is naturally measured by means of
-\emph{probabilistic distances} measuring how far this distribution is
-from the original one. Some classical examples are total variation distance,
-Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
-
-In this work, we design a mechanism for
-bayesian inference exploring the idea of calibrating noise using the
-same probabilistic distance we want to measure accuracy with. 
-We focus on two discrete models, the Beta-Binomial and the
-Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
-Our mechanism can be understood as a version of  the exponential mechanism
-where the noise is calibrated to the smooth sensitivity of the
-utility function, rather than to its global sensitivity. In our
-setting, the utility function is the probability distance we want to
-use to measure accuracy. To show the usefulness of this mechanism we
-show an experimental analysis comparing it with mechanisms based on
-the Laplace mechanism.
+\begin{abstract}
 \end{abstract}
@@
 
-\section{Introduction}
-\label{sec_intro}
-Data analysis techniques are broadly used in. The data privacy is the persistent
-
-Publishing the posterior distribution inferred from a sensitive dataset can
-leak information about the individuals in the dataset.
-In order to guarantee differential privacy and to protect the
-individuals' data we can add noise to the posterior before releasing it.
-The amount of the noise that we need to  introduced
-depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
-small changes in the data set. 
-Sensitivity can be computed in many different ways based on which metric space
-we consider on the output set of the mechanism. In the literature on private Bayesian
-inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
-respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
-A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
-A re-loved question is that of how to measure accuracy. Again,
-this can be answered in different ways based on the metric imposed on the output space, and yet again
-only in few works in literature (e.g. \cite{zhang2016differential})
-distances between probability measures have been used for these purposes.
-
-The question that this work aims at answering is whether
-an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
-the numeric parameters of the distributions. 
-We will see that in some cases this can happen.
-
-\noindent \textbf{Main contributions.}
-\begin{itemize}
-	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
-         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
-	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
-\end{itemize}
-
-\noindent \textbf{Related Work.}
-
-A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \citet{wang2015differentially}, the gradient decedent algorithm in deep learning \citet{abadi2016deep}, logical regression \citet{chaudhuri2009privacy}, principle component analysis \citet{chaudhuri2012near}, probabilitic inference \citet{williams2010probabilistic} and convergence in statistic estimation \citet{chaudhuri2012convergence}, etc.
-
-In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy.
-There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zhang2015differential} and \citet{wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private: \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential}  \citet{foulds2016theory}.
-3) The inference process is differentially private and the posterior distribution released should be private itself.
-The third topic where our work focus on is still very new.
-
 \section{Preliminaries}
-\label{sec_Pre}
+\label{sec_background}
 
@@
 \end{equation*}
-vwhere $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
 \end{definition}
-
-\section{Technical Problem Statement and Motivations}
-\label{sec_moti}
-We are interested in designing a mechanism for privately releasing the full posterior
-distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
-It's worth noticing that the posterior distributions are fully characterized
-by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
-Beta-Binomial model we are interested in releasing a private version of the pair of
-parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-multinomial model we are interested in a private version of
-$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
-have already attacked this problem by adding independent Laplacian noise to the
-parameters of the posteriors. That is, in the case of the Beta-Binomial system,
-the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
-and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
-This mechanism is $\epsilon$-differentially private, and the noise is
-calibrated w.r.t. to a sensitivity of 2 which is derived by using
-$\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
-$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
-distributions, characterized by the pairs
-$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
-$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.
-
-Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
-\[
-  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
-\]
-where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
-However, this accuracy metric is meaningless when the object released is a distribution rather than a numerical value, and distribution metrics such as $f$-divergence, Hellinger distance, etc.
-come into mind overtly when we are measuring distance between distributions.
-
-In this work we will use a metric based on a different norm (a distribution metric) to compute the sensitivity
-and provide guarantees on the accuracy. 
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
-Given two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
-\[
-  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
-  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
-\]
-
-Our choice to use Hellinger distance is motivated by three facts:
-\begin{itemize}
-\item It simplifies calculations in the case of the probabilistic models considered here.
-\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
-an unbounded adversary can have in distingishing two distributions. 
-\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity.
-As shown in Fig.
-\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
-\caption{{Sensitivity of $\hellinger$}}
-\label{fig_sensitivity}
-\end{figure}
-\end{itemize}
 
@@
 
-\subsection{Baseline Mechanisms}
-\label{subsec_baselines}
-Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
-
-\subsubsection{Exponential Mechanism}
-Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
-\end{equation*}
-where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
-\begin{equation*}
-GS = 
-\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
-|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
-\end{equation*}
-
-Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-\subsubsection{Exponential Mechanism with Local Sensitivity}
-\label{subsec_emls}
-% \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
-\end{equation*}
-
-where $LS(x)$ is the local sensitivity calculated by:
-
-\begin{equation*}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
-\end{equation*}
-
-The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
-
-\subsubsection{Baseline Mechanism - Laplace Mechanism}
- Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \] 
- where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
- where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
-$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
-
- Then release it as the private posterior distribution.
-
- The sensitivity used in this baseline mechanism is:
- \[
- \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
- \]
- which is proportional to the dimensionality.
-
-\subsubsection{Improved Laplace Mechanism}
-
- Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
-Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
-
- Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \]
- where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
-where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
-
-Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-\subsection{ $\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
+\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
 \label{subsec_hexpmech}
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
 
-\section{Privacy Proof}
-The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.
+\section{Privacy Analysis}
 
-\subsection{Sliding Property of $\hexpmech$}
+\subsection{Privacy Analysis for $\hexpmech$}
+
+The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\
+
+\noindent \textbf{Sliding Property of $\hexpmech$}
 \begin{lem}
@@
 
-\subsection{Dilation Property of $\hexpmech$}
+\noindent \textbf{Dilation Property of $\hexpmech$}
 \begin{lem}
@@
 
-\subsection{Accuracy Bound for Laplace Mechanism}
-\label{subsec_accuracy_lap}
-Accuracy bound for Laplace mechanism is provided by its probability density function:
-\begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t}{b}},
-\end{equation*}
-where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
-
-After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
-\[
-Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
-\]
-
-\subsection{Accuracy Bound for Exponential Mechanism}
-\label{subsec_accuracy_global}
-The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
-\begin{equation*}
-Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
-\end{equation*}
-where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
+\subsection{Accuracy Bound for Baseline Mechanisms}
 
@@
 
-\section{Experimental Evaluations}
-\label{sec_experiment}
-
-\subsection{Computation Efficiency Optimization}
-\label{subsec_effi}
-The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$
-can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
-by applying the distance triangle property.
-
-Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(x)$:
-\begin{equation*}
-\begin{split}
-LS(\dataobs) 
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
-\end{split}
-\end{equation*}
-
-This equation is validated by an experimental result shown in Fig.
-\ref{fig_efficiency}.
-We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
-It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.48\textwidth]{efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\label{fig_efficiency}
-\end{figure}
-
-\subsection{Theoretical Results}
-
-\begin{figure}[H]
-\begin{center}
-\centering
-  \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
-  \label{subfig_theory_2d}
-  }
-  \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
-  \label{subfig_theory_3d}
-  }
-\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
-\label{fig_theory}
-\end{center}
-\end{figure}
-In Fig.
-\ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms.
-We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
-Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
-the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.
-
-In Fig.
-\ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line).
-This means $\hexpmech$ can produce good results with larger probability than baseline mechanism.
-However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$.
-It outperforms $\hexpmech$.
-
-\subsection{Experimental Results}
-\label{subsec_vs_variables}
-
-In this section, we evaluate the accuracy of the mechanisms defined in
-Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
-data variance, prior distribution, and some combinations thereof.
-Every plot is an average over 1000 runs. In all the experiments we set
-$\epsilon = 1.0$, and $\delta = 10^{-8}$.
-
-\noindent In the following some of the plots show
-mean error as a function of the datasize while one
-is a whiskers-plot where the y-axis shows the average
-accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
-different balanced priors used. The boxes extend from the lower to the upper quartile values
-of the data, with a line at the median. A notch on the box around the
-median is also drawn to give a rough guide to the significance of
-difference of medians; The whiskers extend from the box to show the
-range of the data. A blue box in the plots represents our newly
-designed exponential mechanism's behavior-- where the sensitivity is calibrated
-w.r.t Hellinger distance-- while the yellow box next to
-it represents the performance of a variation of the basic Laplace
-mechanism presented in Section (\ref{subsec_baselines}) with the same
-settings: that is $\epsilon, \delta$, data, prior. The variation
-considered performs a postprocessing on the released parameters so
-that they are consistent. For instance when the sum of the noised
-parameters is greater than $n$ we will truncate them so that they sum
-up to $n$.
-
-\paragraph{Increasing data size with balanced datasets}
-\label{subsubsec_vs_datasize}
-
-\begin{figure}[H]
-\begin{center}
-\centering
-    \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
-\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_2d}
-\end{center}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{center}
-\centering
-     \includegraphics[width=0.4\textwidth]{sampling_3d.eps}   
-\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_3d}
-\end{center}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{center}
-\centering
-     \includegraphics[width=0.4\textwidth]{sampling_4d.eps}    
-\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_4d}
-\end{center}
-\end{figure}
-
-In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
-of observations. The results show that when the data size increases, the average errors of
-$\hexpmech$, Laplace mechanism and decrease. For small datasets,
-i.e with size less $300$ in the case of Beta-Binomial models,
-both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
-But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
-we considered data sets of the order of 15 thousands elements,
-the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
-Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
-
-\paragraph{Fixed dataset varying balanced priors}
-\label{subsubsec_vs_prior}
-In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ .
-We studied the accuracy under different priors, where the priors considered  are also balanced.
-Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
-\caption{Observed data set is: $(50,50)$, varying balanced priors}
-\label{fig_vs_prior}
-\end{figure}
-
-\subsection{Experiment Evaluations on Privacy Loss}
-\label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
-the data size, and obtain plots in Fig.
-\ref{fig_privacy}.
-
-\begin{figure}
-\begin{center}
-\centering
-  \subfigure[data size range from 50 to 100]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
-  \subfigure[data size range from 100 to 200]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
-  \subfigure[data size range from 200 to 500]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
-  \subfigure[data size range from 500 to 1000]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
-\label{fig_privacy}
-\end{center}
-\end{figure}
-
-$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
-That is to say, we achieved a higher privacy level than expected.
-In next step, we are going to improve the accuracy using this property.
-
 \bibliographystyle{ACM-Reference-Format}

### 2018-10-23 codes/discrete_probability_on_betabinomial.py

@@ -320,7 +320,7 @@ if __name__ == "__main__":
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
-	dataset = [30,30]
+	dataset = [2,58]
 
 #############################################################################
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS

### 2018-10-23 Arxiv/main.tex
update proof

@@
 
-In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy.
-There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
 \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}.
 2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}.
-3) The inference process is differentially private and the posterior distribution released should be private itself.
+3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
 The third topic where our work focus on is still very new.
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2}) -$differentially private.
+(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
@@
 		\end{equation*}
-	\item for $r \in R_2$: Actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
+	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
 \end{itemize}
@@
 
-\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
+\noindent \textbf{$(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})-$Differential Privacy of $\hexpmech$}
 \begin{lem}
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
+$\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})$-differential privacy.
 \end{lem}

### 2018-10-23 Arxiv/main.tex
update format

@@
-\documentclass[sigconf]{acmart}
+% \documentclass[sigconf]{acmart}
+\documentclass{article}
 
-\fancyhf{} % Remove fancy page headers 
-% \fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
-\fancyfoot[C]{\thepage}
-
-\setcopyright{none} % No copyright notice required for submissions
-% \acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
-% \acmYear{2017}
-
-\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
+% We want page numbers on submissions
 
@@
 approaches have been explored in order to make this process differentially
-private. For example, \citet{dimitrakakis2014robust}, and
-\citet{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
+private. For example, \cite{dimitrakakis2014robust}, and
+\cite{wang2015privacy} proved that, under specific conditions, sampling from
+the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
 designed differentially private mechanisms that output a
@@
 \end{abstract}
-
-\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
+ % TODO: replace with your keywords
 
@@
 
-A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \citet{wang2015differentially}, the gradient decedent algorithm in deep learning \citet{abadi2016deep}, logical regression \citet{chaudhuri2009privacy}, principle component analysis \citet{chaudhuri2012near}, probabilitic inference \citet{williams2010probabilistic} and convergence in statistic estimation \citet{chaudhuri2012convergence}, etc.
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
 
 In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}.
+\cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
@@
 in the case of the Dirichlet-multinomial model we are interested in a private version of
-$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
+$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
 have already attacked this problem by adding independent Laplacian noise to the
@@
 global sensitivity of the scoring function but w.r.t. to the smooth
-sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of
+sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
 $\hellinger(\bysinfer(\dataobs), \cdot)$.
@@
 \subsection{Privacy Analysis for Baseline Mechanisms}
-In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \citet{dwork2014algorithmic}.
-The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \citet{dwork2014algorithmic}.
+In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
+The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
 Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{plain}
 \bibliography{bayesian.bib}

### 2018-10-23 notes/fullproof/main.tex
uodate full proof

@@
 \begin{document}
-\title{Full proof on the differential privacy property of $\hexpmech$}
+\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
 
-\begin{abstract}
-\end{abstract}
-
-\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
+\author[*]{Jiawen Liu}
+\author[**]{Mark Bun}
+\author[*]{Gian Pietro Farina}
+\author[*]{Marco Gaboardi}
+\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
 
 \maketitle
-
 \section{Preliminaries}
@@
 
+\section{Technical Problem Statement and Motivations}
+\label{sec_moti}
+We are interested in designing a mechanism for privately releasing the full posterior
+distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
+It's worth noticing that the posterior distributions are fully characterized
+by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
+Beta-Binomial model we are interested in releasing a private version of the pair of
+parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
+in the case of the Dirichlet-multinomial model we are interested in a private version of
+$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
+have already attacked this problem by adding independent Laplacian noise to the
+parameters of the posteriors. That is, in the case of the Beta-Binomial system,
+the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
+where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
+and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+This mechanism is $\epsilon$-differentially private, and the noise is
+calibrated w.r.t. to a sensitivity of 2 which is derived by using
+$\ell_1$ norm over the pair of parameters. Indeed, considering two
+adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
+$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
+distributions, characterized by the pairs
+$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
+$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
+This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.
+
+However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
+\[
+  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
+\]
+where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
+This accuracy metric is meaningless when the results released are distributions rather than numerical values.
+In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc.
+come into mind overtly when we are measuring distance between distributions.
+This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
+and provide guarantees on the accuracy.
+
+Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
+Given two beta distributions
+$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
+\[
+  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
+  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+\]
+
+Our choice to use Hellinger distance is motivated by three facts:
+\begin{itemize}
+\item It simplifies calculations in the case of the probabilistic models considered here.
+\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
+an unbounded adversary can have in distingishing two distributions. 
+\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity.
+As shown in Fig.
+\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
+\caption{{Sensitivity of $\hellinger$}}
+\label{fig_sensitivity}
+\end{figure}
+\end{itemize}
+
 \section{Mechanism Proposition}
@@
 fixed and we denote it by $\bprior$.
+
+\subsection{Baseline Mechanisms}
+\label{subsec_baselines}
+Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
+
+\subsubsection{Exponential Mechanism}
+Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+\begin{equation*}
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
+\end{equation*}
+where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
+\begin{equation*}
+GS = 
+\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
+|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
+\end{equation*}
+
+Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+
+\subsubsection{Exponential Mechanism with Local Sensitivity}
+\label{subsec_emls}
+% \subsubsection{Mechanism Set up}
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
+This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
+\begin{equation*}
+\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
+\end{equation*}
+
+where $LS(x)$ is the local sensitivity calculated by:
+
+\begin{equation*}
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
+\end{equation*}
+
+The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
+
+\subsubsection{Baseline Mechanism - Laplace Mechanism}
+ Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \] 
+ where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+ where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
+$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
+
+ Then release it as the private posterior distribution.
+
+ The sensitivity used in this baseline mechanism is:
+ \[
+ \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
+ \]
+ which is proportional to the dimensionality.
+
+\subsubsection{Improved Laplace Mechanism}
+
+ Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
+Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+
+ Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \]
+ where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
+
+Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
 
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2}) -$differentially private.
+(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
 \section{Privacy Analysis}
+
+\subsection{Privacy Analysis for Baseline Mechanisms}
+In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
+The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
 
@@
 		\end{equation*}
+	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
+\end{itemize}
+
+The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.
 
@@
 \begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:
 
@@
 	\begin{split}
-2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
-& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
-& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
+	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
+	& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\\
+	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\\
+	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
 	\end{split}
 	\end{equation*}
-
-The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
+	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
 The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
 
-\end{proof}
+	\item for $r \in R_2$:
 
-\section{Accuracy Analysis}
-
-\subsection{Accuracy Bound for Baseline Mechanisms}
-
-\subsection{Accuracy Bound for $\hexpmech$}
-\label{subsec_accuracy_smoo}
-We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
-
-First is the tight bound with very accurate calculation.
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(x), z)}{S(x)}}}{NL_x}.
-\end{equation*}
-
-In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
-\end{equation*}
-
-In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
-\end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
-
-Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
+	Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+Then,
 
@@
 	\begin{split}
-Pr[u(\hexpmech(x)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
+	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
+	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
 	\end{split}
 	\end{equation*}
+	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.
 
-which has been used in the dilation property proof.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
+The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+\end{itemize}
 
-\bibliographystyle{ACM-Reference-Format}
+Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.
+
+Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
+\end{proof}
+
+\bibliographystyle{plain}
 \bibliography{bayesian.bib}

### 2018-10-23 Arxiv/main.tex
adding authors
uodate full proof
update delta

@@
 \title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
+
+\author[*]{Jiawen Liu}
+\author[**]{Mark Bun}
+\author[*]{Gian Pietro Farina}
+\author[*]{Marco Gaboardi}
+\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
 
@@
 	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
-         metric over distributions (e.g.
+
+	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
 Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
+
+  \item A full proof on applying exponential mechanism to the smooth sensitivity is $(\epsilon, \delta)-$differential privacy is given in paper.
+
 	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
@@
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
+{\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2}) -$differentially private.
-(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
@@
 Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
+\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
 \begin{equation*}
@@
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\delta' + \hat{s})] + \frac{\delta'}{2},
 \end{equation*}
@@
 		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(x)})}{NL(x)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)} + \frac{- \epsilon \delta'}{2 S(x)})}{NL(x)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \delta'}{2 S(x)})}.\\
 		\end{split}
@@
 
-		By bounding the $\Delta \geq -S(x)$, we can get:
+		By bounding the $\delta' \geq -S(x)$, we can get:
 
@@
 		\begin{split}
-		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \delta'}{2 S(x)}}
+		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
+		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
 		\end{split}
@@
 \begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
 
@@
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
 \end{equation*}
@@
 
-More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
+More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
 \end{lem}
@@
 Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\
+The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$.
+Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\
 
@@
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2}
 	\end{equation*}
@@
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
+		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
 
-		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
+		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
 
@@
 
-\noindent \textbf{$(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})-$Differential Privacy of $\hexpmech$}
+\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
 \begin{lem}
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \frac{e^{\frac{\epsilon}{2}} \delta}{2})$-differential privacy.
+$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
 \end{lem}
@@
 	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 
@@
 	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 \end{itemize}
 
-Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.
+Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 

### 2018-10-23 Arxiv/main.tex
update format

@@
 
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B],
+\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B].
 \end{equation*}
-where $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+
 \end{definition}
@@
 
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
 \begin{equation*}
@@
 $\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
-$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
+adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
 distributions, characterized by the pairs
@@
 Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
+This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
 \begin{equation*}
 \underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
+{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
 \end{equation*}
 
-where $LS(x)$ is the local sensitivity calculated by:
+where $LS(\dataobs)$ is the local sensitivity calculated by:
 
@@
 \label{def_smoo}
-The mechanism $\hexpmech(x)$ outputs a candidate $r \in \candidateset$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
@@
 \end{equation*}
-where $S_\beta(x)$ is the smooth sensitivity of $\hellinger(\bysinfer(x),-)$, calculated by:
+where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
 
@@
 \begin{lem}
-Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
+Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
 \delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
 \begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
+\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\delta' + \hat{s})] + \frac{\delta'}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
 \end{equation*}
@@
 In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
+ $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
  $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]$ for the utility score for $r$.
+ $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
+ \hellinger(\bysinfer(\dataobs),r)]$ for the utility score for $r$.
 In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
@@
  From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
- \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
+ \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ either 
  $$
- =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]\Big )
+ =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
+ \hellinger(\bysinfer(\dataobs),r)]\Big )
  $$ or 
  $$
- =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
+ =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]
  $$
- % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
- We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e.
-$u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+ % proportional too $\hellinger(\bysinfer(\dataobs),r)$, i.e., $u(x,z)$.
+We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r']$.
+ We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
+$u(z,\dataobs) = u(r,\dataobs)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 
@@
 
-		We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
+		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
 		\begin{equation*}
@@
 		LHS 
-		  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)} + \frac{- \epsilon \delta'}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \delta'}{2 S(x)})}.\\
+		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
+		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
 		\end{split}
@@
 
-		By bounding the $\delta' \geq -S(x)$, we can get:
+		By bounding the $\delta' \geq -S(\dataobs)$, we can get:
 
@@
 		\begin{split}
-		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \delta'}{2 S(x)}}
-		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
+		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
+		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
+		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
 		\end{split}
@@
 \begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
 
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
 \end{equation*}
@@
 
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.
+We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.
 
 We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.
 
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
-Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
+Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$.
+Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$.
 Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
@@
 	\begin{equation*}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2}
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2}
 	\end{equation*}
@@
 
-	Let $Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$ and $Pr[u(\hexpmech(x)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(x)})}{NL(x)}$ by definition.
+	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
 
-	After simplification, we need to show: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$.
-	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
+	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
@@
 		\begin{equation*}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
 		\end{equation*}
@@
 
-		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
+		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
 		\begin{equation}
 		\label{eq_dilation_case2}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
 		\end{equation}
@@
 		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})}\\
+		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})}\\
 		\end{split}
@@
 		\begin{split}
-		Pr[u(\hexpmech(x)) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)})
+		Pr[u(\hexpmech(\dataobs)) \leq c] 
+		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)})
 		\end{split}
@@
 		\begin{split}
-		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
+		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
+		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
 		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
@@
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
+		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
 
@@
 
-For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
+For all $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$, we need to show that:
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z = r] + \delta. 
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
 \end{equation*}
@@
 
-	Given that $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
@@
 	\begin{split}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
-	& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\\
-	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\\
-	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
+	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
+	& = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\\
+	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\\
+	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(\dataobs',z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
 	\end{split}
@@
 	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
+The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 
@@
 
-	Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
+	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(y,z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
@@
 	\begin{split}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
-	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
+	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
+	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
+	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
 	\end{split}
@@
 
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
+The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 \end{itemize}
@@
 Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
+		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(x), z)}{S(x)}}}{NL_x}.
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(\dataobs), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), z)}{S(\dataobs)}}}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{N(n)},
 \end{equation*}
@@
 \begin{split}
-Pr[u(\hexpmech(x)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
+Pr[u(\hexpmech(\dataobs)) \leq c] 
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
 \end{split}
@@
 
-Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(x)$:
+Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
 \begin{equation*}

### 2018-10-23 Arxiv/main.tex
update
update the figure size

@@
 
-\author[*]{Jiawen Liu}
-\author[**]{Mark Bun}
-\author[*]{Gian Pietro Farina}
-\author[*]{Marco Gaboardi}
-\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
-\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
+% \author[*]{Jiawen Liu}
+% \author[**]{Mark Bun}
+% \author[*]{Gian Pietro Farina}
+% \author[*]{Marco Gaboardi}
+% \affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+% \affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{efficiency}
+\includegraphics[width=0.8\textwidth]{efficiency}
 \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
@@
   \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
+    \includegraphics[width=0.4\textwidth]{theory_2d.eps}
   \label{subfig_theory_2d}
@@
   \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
+    \includegraphics[width=0.4\textwidth]{theory_3d.eps}
   \label{subfig_theory_3d}
@@
 \centering
-    \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
+    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
 \caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
@@
 \centering
-     \includegraphics[width=0.4\textwidth]{sampling_3d.eps}   
-\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+{
+        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
         \label{fig_vs_datasize_3d}
+}
+\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+{
+     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
+\label{fig_vs_datasize_4d}
+}
 \end{center}
@@
 
-\begin{figure}[ht]
-\begin{center}
-\centering
-     \includegraphics[width=0.4\textwidth]{sampling_4d.eps}    
-\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_4d}
-\end{center}
-\end{figure}
+% \begin{figure}[ht]
+% \begin{center}
+% \centering
+
+% \end{center}
+% \end{figure}
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
+\includegraphics[width=0.8\textwidth]{sampling_prior.eps}
 \caption{Observed data set is: $(50,50)$, varying balanced priors}
@@
   \subfigure[data size range from 50 to 100]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
+    \includegraphics[width=0.4\textwidth]{global_epsilon_size50to100.eps}}
   \subfigure[data size range from 100 to 200]{
-    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
+    \includegraphics[width=0.4\textwidth]{global_epsilon_size100to200.eps}} 
   % \subfigure[data size range from 200 to 500]{

### 2018-10-24 Arxiv/main.tex
update label

@@
 
-The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\
+The differential privacy property of $\hexpmech$ is proved based on following two lemmas: Lemma \ref{lem_sliding} and Lemma \ref{lem_dilation}.\\
 
@@
 \begin{lem}
+\label{lem_sliding}
 Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
@@
  $$
- =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]
+ =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)].
  $$
@@
 \begin{lem}
+\label{lem_dilation}
 for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
@@
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2}
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
 	\end{equation*}
@@
 		\label{eq_dilation_case2}
-		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
+		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
 		\end{equation}
+
 		Based on the accuracy property of exponential mechanism:
@@
 		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})}\\
+		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
 		\end{split}
 		\end{equation*}
-
 		we derived the accuracy bound for $\hexpmech$:
-
 		\begin{equation*}
@@
 		Pr[u(\hexpmech(\dataobs)) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)})
+		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
 		\end{split}
@@
 		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
-		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
+		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
 		\end{split}

### 2018-10-24 Arxiv/main.tex
update lemma and theorem

@@
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
+{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
@@
  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
- \hellinger(\bysinfer(\dataobs),r)]$ for the utility score for $r$.
+ \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.
 In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
-More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.
 
- From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
- \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ either 
+ \begin{lem}
+ \label{lem_hellinegr_equality}
+ for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
   $$
- =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
- \hellinger(\bysinfer(\dataobs),r)]\Big )
+  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2 \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
+  $$
+ \end{lem}
+
+ \begin{thm}
+ \label{thm_candidate_divide}
+ there are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
+ $$
+ = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
  $$ or 
  $$
- =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)].
+ =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
  $$
+ \end{thm}
  % proportional too $\hellinger(\bysinfer(\dataobs),r)$, i.e., $u(x,z)$.
 We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r']$.
+ \begin{proof} of Theorem \ref{thm_candidate_divide}.
+
  We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
 $u(z,\dataobs) = u(r,\dataobs)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
-It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+
+ From Lemma \ref{lem_hellinegr_equality}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 
  The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.
+ \end{proof}
 

### 2018-10-24 Arxiv/main.tex
reformatting
update theorem

@@
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-specifically, a Beta-binomial mode. We will consider the situation the underlying data is binomial distribution ($\sim binomial(\theta)$), where $\theta$ represents
+specifically, a Beta-binomial mode. We will consider the situation the underlying data is binomial distribution ($\thicksim binomial(\theta)$), where $\theta$ represents
 the parameter --informally called \emph{bias}-- of a Bernoulli
@@
 the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
+where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
 and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
@@
  \] 
- where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
+ where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
  \[
@@
  \]
- where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
+ where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
 $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
@@
  \]
- where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
+ where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
  \[
@@
  \]
-where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
+where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
 
@@
 
- \begin{lem}
- \label{lem_hellinegr_equality}
+ \begin{thm}
+ \label{thm_hellinegr_equality}
  for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
@@
   $$
- \end{lem}
+ \end{thm}
 
@@
 
- From Lemma \ref{lem_hellinegr_equality}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ From Theorem \ref{thm_hellinegr_equality}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 
@@
 \begin{proof}
-We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.
+Based on Theorem \ref{thm_hellinegr_equality} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
+It is enough to proof under just one partition.
+Without loss of generalization, we take $R_1$.
 
@@
 \end{equation*}
-where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
+where $Y \thicksim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
 

### 2018-10-24 Arxiv/main.tex
update dirichlet theorem

@@
 
-% \author[*]{Jiawen Liu}
-% \author[**]{Mark Bun}
-% \author[*]{Gian Pietro Farina}
-% \author[*]{Marco Gaboardi}
-% \affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
-% \affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
-
+\author[*]{Jiawen Liu}
+\author[**]{Mark Bun}
+\author[*]{Gian Pietro Farina}
+\author[*]{Marco Gaboardi}
+\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
+\date{}
+\maketitle
 \begin{abstract} Bayesian inference is a statistical method which
@@
  % TODO: replace with your keywords
-
-\maketitle
 
@@
  \begin{thm}
- \label{thm_hellinegr_equality}
+ \label{thm_hellinegr_equality_beta}
  for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
@@
 \begin{thm}
+ \label{thm_hellinegr_equality_dirichlet}
+ In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
+  $$
+  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2).
+  $$
+ \end{thm}
+
+ \begin{thm}
  \label{thm_candidate_divide}
- there are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
+ There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
  $$
@@
  \end{thm}
- % proportional too $\hellinger(\bysinfer(\dataobs),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r']$.
  \begin{proof} of Theorem \ref{thm_candidate_divide}.
 
- We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
-$u(z,\dataobs) = u(r,\dataobs)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
+$u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 
- From Theorem \ref{thm_hellinegr_equality}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ \end{proof}
 
- The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.
+\begin{thm}
+ \label{thm_candidate_divide_dirichlet}
+ In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
+ $$
+ \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
+ = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
+ $$ 
+ and $|z| = \min\{\frac{k!}{a_1! a_2! \cdots a_{k_a}!},\frac{k!}{b_1! b_2! \cdots b_{k_b}!}\}$, where $\sum{a_i} = \sum{b_i} = k$.
+ \end{thm}
+
+ \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
+ By 
  \end{proof}
@@
 \begin{proof}
-Based on Theorem \ref{thm_hellinegr_equality} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
+Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
 It is enough to proof under just one partition.

### 2018-10-24 Arxiv/main.tex
update theorems

@@
   $$
-  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2).
+  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
   $$
+  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
  \end{thm}
@@
  $$ 
- and $|z| = \min\{\frac{k!}{a_1! a_2! \cdots a_{k_a}!},\frac{k!}{b_1! b_2! \cdots b_{k_b}!}\}$, where $\sum{a_i} = \sum{b_i} = k$.
+ and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{a_i} = \sum{b_i} = k$.
  \end{thm}
@@
  \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
- By 
+
+ Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
+ $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
+ $|a_i|$ denotes the number of values in $\valpha$ having the value$a_i$ and $|b_i|$ the same in $\vbeta$.
+ Then, by combination and permutation, there are $\frac{k!
+k!}{|a_1|!
+|a_2|!
+\cdots |a_{k_a}|!
+\cdot |b_1|!
+|b_2|!
+\cdots |b_{k_b}|!}$ possible combination that satisfy the condition in Theorem \ref{thm_hellinegr_equality_dirichlet}.
  \end{proof}

### 2018-10-24 Arxiv/main.tex
update
fix typo

@@
  $$ 
- and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{a_i} = \sum{b_i} = k$.
+ and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{|a_i|} = \sum{|b_i|} = k$.
  \end{thm}
@@
  $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
- $|a_i|$ denotes the number of values in $\valpha$ having the value$a_i$ and $|b_i|$ the same in $\vbeta$.
- Then, by combination and permutation, there are $\frac{k!
+ $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
+ Then, by combination and permutation rules, there are $\frac{k!
 k!}{|a_1|!

### 2018-10-24 Arxiv/main.tex
update theorem

@@
  $$ 
- and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{|a_i|} = \sum{|b_i|} = k$.
+ and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
  \end{thm}
@@
  $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
- Then, by combination and permutation rules, there are $\frac{k!
+ Then, there are $\frac{k!
 k!}{|a_1|!
@@
 |b_2|!
-\cdots |b_{k_b}|!}$ possible combination that satisfy the condition in Theorem \ref{thm_hellinegr_equality_dirichlet}.
+\cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
  \end{proof}

### 2018-10-24 Arxiv/main.tex
update proofs

@@
  \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.
-In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
-
- \begin{thm}
- \label{thm_hellinegr_equality_beta}
- for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
-  $$
-  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2 \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
-  $$
- \end{thm}
-
-\begin{thm}
- \label{thm_hellinegr_equality_dirichlet}
- In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
-  $$
-  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
-  $$
-  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
- \end{thm}
-
- \begin{thm}
- \label{thm_candidate_divide}
- There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
- $$
- = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
- $$ or 
- $$
- =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
- $$
- \end{thm}
- \begin{proof} of Theorem \ref{thm_candidate_divide}.
 
@@
 
- From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
- \end{proof}
-
-\begin{thm}
- \label{thm_candidate_divide_dirichlet}
- In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
- $$
- \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
- = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
- $$ 
- and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
- \end{thm}
-
- \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
-
- Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
- $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
- $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
- Then, there are $\frac{k!
-k!}{|a_1|!
-|a_2|!
-\cdots |a_{k_a}|!
-\cdot |b_1|!
-|b_2|!
-\cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
- \end{proof}
-
- In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$.
+ % It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ % let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$.
 The proofs are given by parts:
-
- \begin{itemize}
- 	\item for $r \in R_1$:
 
@@
 		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
-		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
+		& = |r| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
 		\end{split}
@@
 		\begin{split}
-		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
-		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
+		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
+		& |r| \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
 		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
@@
 		\end{equation*}
-	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
-\end{itemize}
-
-The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.
 
@@
 \begin{proof}
-Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
-It is enough to proof under just one partition.
-Without loss of generalization, we take $R_1$.
 
@@
 
-	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
+	Let $Pr[u(\hexpmech(\dataobs)) = c] = |r|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = |r|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
 
@@
 
-		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
+		apply this bound to eq. \ref{eq_dilation_case2}:
 		\begin{equation*}
@@
 
-		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
+		Particularly in Beta-binomial system, $|\candidateset| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.
 
@@
 
-Let partition $R_1, R_2 \subset \candidateset$ the same as above. Then we prove by part:
-\begin{itemize}
-	\item for $r \in R_1$:
-
 	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
-
-	\begin{equation*}
-	\begin{split}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\\
-	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\\
-	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(\dataobs',z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
-	\end{split}
-	\end{equation*}
-	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
-The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
-
-	\item for $r \in R_2$:
 
@@
 	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
 	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
@@
 	\end{equation*}
-	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.
+	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.
 
@@
 The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
-\end{itemize}
 
-Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
-
-Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
+Since $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 \end{proof}

### 2018-10-24 notes/fullproof/main.tex
update proofs

@@
 \affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
-
+\date{}
 \maketitle
@@
 
-\subsection{Baseline Mechanisms}
-\label{subsec_baselines}
-Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
-
-\subsubsection{Exponential Mechanism}
-Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
-\end{equation*}
-where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
-\begin{equation*}
-GS = 
-\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
-|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
-\end{equation*}
-
-Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-\subsubsection{Exponential Mechanism with Local Sensitivity}
-\label{subsec_emls}
-% \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
-\end{equation*}
-
-where $LS(x)$ is the local sensitivity calculated by:
-
-\begin{equation*}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
-\end{equation*}
-
-The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
-
-\subsubsection{Baseline Mechanism - Laplace Mechanism}
- Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \] 
- where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
- where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
-$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
-
- Then release it as the private posterior distribution.
-
- The sensitivity used in this baseline mechanism is:
- \[
- \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
- \]
- which is proportional to the dimensionality.
-
-\subsubsection{Improved Laplace Mechanism}
-
- Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
-Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
-
- Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \]
- where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
-where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
-
-Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
 \subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
@@
 \label{def_smoo}
-The mechanism $\hexpmech(x)$ outputs a candidate $r \in \candidateset$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
+{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
 \end{equation*}
-where $S_\beta(x)$ is the smooth sensitivity of $\hellinger(\bysinfer(x),-)$, calculated by:
+where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
 
@@
 \begin{lem}
-Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
+\label{lem_sliding}
+Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
+\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
 \begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
+\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
 \end{equation*}
@@
 In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
+ $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
  $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]$ for the utility score for $r$.
+ $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
+ \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.
 In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
-More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.
 
- From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
- \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
+ \begin{thm}
+ \label{thm_hellinegr_equality_beta}
+ for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
   $$
- =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]\Big )
+  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2, \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
+  $$
+ \end{thm}
+
+\begin{thm}
+ \label{thm_hellinegr_equality_dirichlet}
+ In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
+  $$
+  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
+  $$
+  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
+ \end{thm}
+
+ \begin{thm}
+ \label{thm_candidate_divide}
+ There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
+ $$
+ = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
  $$ or 
  $$
- =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
+ =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
  $$
- % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
- We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e.
-$u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
+ \end{thm}
+ \begin{proof} of Theorem \ref{thm_candidate_divide}.
 
- The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.
+ Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
+$u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+
+ From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
+ \end{proof}
+
+\begin{thm}
+ \label{thm_candidate_divide_dirichlet}
+ In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
+ $$
+ \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
+ = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
+ $$ 
+ and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
+ \end{thm}
+
+ \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
+
+ Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
+ $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
+ $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
+ Then, there are $\frac{k!
+k!}{|a_1|!
+|a_2|!
+\cdots |a_{k_a}|!
+\cdot |b_1|!
+|b_2|!
+\cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
+ \end{proof}
 
@@
 		LHS 
-		  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
+		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
 		\end{split}
@@
 
-		By bounding the $\Delta \geq -S(x)$, we can get:
+		By bounding the $\delta' \geq -S(\dataobs)$, we can get:
 
@@
 		\begin{split}
-		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
+		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
+		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
 		\end{split}
@@
 \begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:
+\label{lem_dilation}
+for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
 
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
 \end{equation*}
@@
 \begin{proof}
-We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.
+Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
+It is enough to proof under just one partition.
+Without loss of generalization, we take $R_1$.
 
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.
+We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.
 
 We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.
 
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
-Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
+Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$.
+Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$.
 Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\
+The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$.
+Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\
 
@@
 	\begin{equation*}
-	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
+	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
 	\end{equation*}
@@
 
-		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
+		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
 		\begin{equation}
 		\label{eq_dilation_case2}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
+		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
 		\end{equation}
+
 		Based on the accuracy property of exponential mechanism:
@@
 		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})}\\
+		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
 		\end{split}
 		\end{equation*}
-
 		we derived the accuracy bound for $\hexpmech$:
-
 		\begin{equation*}
 		\begin{split}
-		Pr[u(\hexpmech(x)) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)})
+		Pr[u(\hexpmech(\dataobs)) \leq c] 
+		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
 		\end{split}
@@
 		\begin{split}
-		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
-		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
+		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
+		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
+		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
 		\end{split}
@@
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
+		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
 
-		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
+		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
 
@@
 	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
+The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 
@@
 
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
+	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
+The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
 \end{itemize}
 
-Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.
+Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 

### 2018-10-24 Arxiv/main.tex
fix typo

@@
 By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
-(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
@@
 		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
-		& |r| \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
+		&  \leq |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
 		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
@@
 	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
+	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
 	\end{split}
@@
 
-Since $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+ $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 \end{proof}

### 2018-10-25 Arxiv/main.tex
fix typo in arixv

@@
 the Bayesian Inference process will produce an element from $\candidateset$
-that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
+that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
 parametrize the result by the prior, which from now on we consider

### 2018-10-25 Arxiv/main.tex
small edit
fix typos

@@
 \begin{equation*}
-\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
+\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = \hat{s}]
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
+e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
 \end{equation*}
@@
 		LHS 
-		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
-		& = |r| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
+		  = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
+		& = |z| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
+		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
 		\end{split}
@@
 		\begin{split}
-		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
-		&  \leq |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
+		|z|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
+		&  \leq |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
+		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = (\delta' + \hat{s})] \leq RHS\\
 		\end{split}

### 2018-10-25 Arxiv/main.tex
fix typos

@@
 	\begin{equation*}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
+	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)]
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
+	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
 	\end{equation*}
-	for $z \in R_1$.
+  we need to show:
+  \begin{equation*}
+  Pr[u(\hexpmech(\dataobs), \dataobs) = u(r,\dataobs)]
+  \leq
+  e^{\frac{\epsilon}{2}} Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
+  \end{equation*}
 
-	Let $Pr[u(\hexpmech(\dataobs)) = c] = |r|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = |r|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
+	Let $u(r,\dataobs) = c$, $Pr[u(\hexpmech(\dataobs), \dataobs) = c] = |z|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} c] = |z|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
 
-	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
-	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+	After simplification, we need to show: $u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
+	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
 
@@
 		\begin{equation*}
-		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
+		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
 		\end{equation*}
@@
 
-		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
+		Because $\hat{s} = u(r, \dataobs)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs), \dataobs)$.
+Then, what we need to proof under the case $\lambda > 0$ is:
 		\begin{equation}
 		\label{eq_dilation_case2}
-		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
+		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
 		\end{equation}
@@
 		\begin{split}
-		Pr[u(\hexpmech(\dataobs)) \leq c] 
+		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
 		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
@@
 		\begin{split}
-		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
+		Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
 		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
@@
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
+		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
 
@@
 
-	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
+	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
 
-	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(y,z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
+	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = u(r, \dataobs)]$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
@@
 	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U]\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_2]\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(z,, \dataobs') = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
 	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,

### 2018-10-26 Arxiv/main.tex
rewrite sliding property

@@
 \[
-  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
+  \candidateset{\dataobs}\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
 \]
 where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
-Notice that $\candidateset$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\candidateset$
+Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
 that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
@@
 \subsubsection{Exponential Mechanism}
-Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+Exponential mechanism $\expmech{}{x}{u}{\candidateset{\dataobs}}$ samples a element from the candidate set $\candidateset{\dataobs} = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset{\dataobs}} }{Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 GS})}
@@
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset{\dataobs}}$ share the same candidate set and utility function as it with standard exponential mechanism.
 This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
+\underset{z \thicksim \expmech{local}{x}{u}{\candidateset{\dataobs}}}{\Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
@@
 \label{def_smoo}
-The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset{\dataobs}$ with probability
 \begin{equation*}
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
+{\nomalizer{\dataobs}}.
 \end{equation*}
@@
 This mechanism is based on the basic exponential mechanism
-\cite{talwar}, with $\candidateset$ as the range and
+\cite{talwar}, with $\candidateset{\dataobs}$ as the range and
 $\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
@@
 \]
-and by replacing the $\candidateset$ with set of posterior Dirichlet
+and by replacing the $\candidateset{\dataobs}$ with set of posterior Dirichlet
 distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
@@
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+that $\candidateset{\dataobs}$ has $\binom{n + 1}{m - 1}$ elements in this case. We
 will denote by $\hexpmechd$ the mechanism for the
@@
 
+In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_convert} and \ref{lem_cadinality}.
+
+\begin{lem}
+\label{lem_score_pro_convert}
+  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
+  $$
+  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
+  $$  
+\end{lem}
+\begin{proof} of lemma \ref{lem_score_pro_convert}.
+\begin{itemize}
+  \item $\implies$
+  \begin{equation*}
+  \begin{split}
+  \ux{r'} = \ux{r''} 
+  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
+  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
+  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r''] \\
+  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
+  \end{split}
+  \end{equation*}
+
+  \item $\impliedby$
+
+    \begin{equation*}
+  \begin{split}
+  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
+  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r'']\\
+  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
+  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
+  & \implies \ux{r'} = \ux{r''}.
+  \end{split}
+  \end{equation*}
+\end{itemize}
+
+\end{proof}
+
+\begin{definition}
+\label{def_cardinality}
+  $\cardinality{r}$
+
+  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t.
+$ R_r = \{ r' : \ux{r'} = \ux{r}, r' \in \candidateset{\dataobs}\} \subset \candidateset{\dataobs}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$,
+\end{definition}
+
+\begin{lem}
+\label{lem_cadinality}
+ Given $\hexpmech(\dataobs)$, then the following property holds:
+\begin{equation*}
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
+ \end{equation*}
+\end{lem}
+\begin{proof} of Lemma \ref{lem_cadinality}.\\
+To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
+$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
+By Definition \ref{def_cardinality}, $R_r$ is this set.\\
+$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
+By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
+Apply Lemma \ref{lem_score_pro_convert} in $R_r$, \\
+$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
+$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
+$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
+\end{proof}
+
 \noindent \textbf{Sliding Property of $\hexpmech$}
+
 \begin{lem}
 \label{lem_sliding}
-Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
+
+Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = \hat{s}]
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
+e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
 \end{equation*}
-
 \end{lem}
 
-\begin{proof}
+\begin{proof} of Lemma \ref{lem_sliding}:
 
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
- $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
- \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.
+Let $\ux{t} = \ux{r} + k$.
+In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
+\begin{itemize}
+  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
+  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+\end{itemize}
 
- Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
-$u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
-
- % It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
- % let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$.
-The proofs are given by parts:
-
-		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
+Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
+\begin{itemize}
+  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$ and $k \geq 0$.\\
+  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$.\\
+  By Lemma \ref{lem_score_pro_convert}, $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r} \hexpmechPr{\dataobs}{z = r}$.\\
+  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$.\\
+  $\implies$\\
     \begin{equation*}
@@
     LHS 
-		  = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
-		& = |z| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+    & = RHS.
     \end{split}
@@
 
-		By bounding the $\delta' \geq -S(\dataobs)$, we can get:
+  \item $u(\dataobs, r) \neq 0$, $\ux{r} + k \neq 0$ and $-\ux{r} < k < 0$
 
+  \item $\ux{r} = 0$.\\
+  By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
+  Destruct $k$:
+  \begin{itemize}
+    \item $k = 0$:\\
     \begin{equation*}
     \begin{split}
-		|z|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
-		&  \leq |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = (\delta' + \hat{s})] \leq RHS\\
+    LHS 
+    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
+    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
+    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+    & = RHS.
     \end{split}
     \end{equation*}
+    \item $k \neq 0$:\\
+    By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$.\\
+    $\implies$\\
+    \begin{equation*}
+    \begin{split}
+    LHS 
+    & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
+    & < 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
+    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+    & = RHS.
+    \end{split}
+    \end{equation*}
+
+  \end{itemize}
+  \item $\ux{r} \neq 0, \ux{r} + k = 0$
+    By $\ux{r} + k = 0$, $\cardinality{t} = 1$.\\
+    By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
+    $\implies$\\
+    \begin{equation*}
+    \begin{split}
+    LHS 
+    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
+    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 1 \cdot \hexpmechPr{\dataobs}{z = t}\\
+    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
+    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
+    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+    & = e^{\ln 2} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+    & = e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+    & = RHS.
+    \end{split}
+    \end{equation*}
+
+\end{itemize}
 
@@
 \label{lem_dilation}
-for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
+for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:
 
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
+\hexpmechPr{\dataobs}{u(z,\dataobs) = c}
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
+e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,\dataobs) = e^{\lambda} c} + \frac{\delta'}{2},
 \end{equation*}
@@
 	\begin{equation*}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)]
+	\hexpmechPr{\dataobs}{u(z,\dataobs) = u(r,\dataobs)}
 	\leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
+	e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,x) = e^{\lambda} u(r,\dataobs)} + \frac{\delta'}{2},
 	\end{equation*}
@@
 		\begin{split}
-		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+		Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
 		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
@@
 		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
+		& \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
 		\end{split}
@@
 
-		Particularly in Beta-binomial system, $|\candidateset| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.
+		Particularly in Beta-binomial system, $|\candidateset{\dataobs}| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.
 
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
+\hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
 \end{equation*}
 
-	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
+	Given that $\hexpmechPr{\dataobs}{z = r} = \hexpmechPr{\dataobs}{u(\dataobs,z) = u(\dataobs,r)}$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
 
-	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = u(r, \dataobs)]$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
+	Given that $2\Big( \hexpmechPr{\dataobs}{z = r}\Big) = \hexpmechPr{\dataobs}{u(z, \dataobs) = u(r, \dataobs)}$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
 Then,
@@
 	\begin{split}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U]\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_2]\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(z,, \dataobs') = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
+	\hexpmechPr{\dataobs}{z = r}
+	& = 	\frac{1}{|z|}\Big( \hexpmechPr{\dataobs}{ u(z, \dataobs) = U}\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \hexpmechPr{\dataobs}{u(z, \dataobs) = U_2}\Big)\\
+	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \hexpmechPr{\dataobs}{u(z, \dataobs) = U_3} + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
+	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(z, \dataobs') = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
 	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
@@
 \begin{equation*}
-Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
 		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(\dataobs), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), z)}{S(\dataobs)}}}{NL_x}.
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} = \sum\limits_{\{z | \hellinger(\bysinfer(\dataobs), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), z)}{S(\dataobs)}}}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{NL_x}.
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{NL_x}.
 \end{equation*}
@@
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ \hellinger(\bysinfer(\dataobs), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{N(n)},
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{N(n)},
 \end{equation*}
@@
 Pr[u(\hexpmech(\dataobs)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
+& \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}),
 \end{split}
@@
 \ref{fig_efficiency}.
-We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
+We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset{\dataobs}$.
 It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

### 2018-10-26 Arxiv/main.tex
revise sliding property

@@
 
-In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_convert} and \ref{lem_cadinality}.
+In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.
 
 \begin{lem}
-\label{lem_score_pro_convert}
+\label{lem_score_pro_eq}
   Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
@@
 \end{lem}
-\begin{proof} of lemma \ref{lem_score_pro_convert}.
+\begin{proof} of lemma \ref{lem_score_pro_eq}.
 \begin{itemize}
@@
 \begin{lem}
-\label{lem_cadinality}
+\label{lem_score_pro_convert}
  Given $\hexpmech(\dataobs)$, then the following property holds:
@@
 \end{lem}
-\begin{proof} of Lemma \ref{lem_cadinality}.\\
+\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
 To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
@@
 
+\todo{
+In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
+\begin{itemize}
+  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 1\}$.
+  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 2\}$.
+\end{itemize}
+}
+
 Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
 \begin{itemize}
-  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$ and $k \geq 0$.\\
-  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$.\\
-  By Lemma \ref{lem_score_pro_convert}, $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r} \hexpmechPr{\dataobs}{z = r}$.\\
-  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$.\\
+  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
+  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
+  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{r} = 2$}\\
+  Destruct k:
+  \begin{itemize}
+    \item  $k \geq 0$: $\implies$\\
+      \begin{equation*}
+      \begin{split}
+      LHS 
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+    \item $-\ux{r} < k < 0$: $\implies$\\
+
+      \begin{equation*}
+      \begin{split}
+      LHS 
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \end{itemize}
+
+  \item $\ux{r} = 0, \ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
+        By $\ux{r} = 0$, $\cardinality{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
+        By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
         $\implies$\\
@@
         LHS 
-    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+        & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ Definition\ \ref{def_smoo})\\
+        & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{r} = 1) \\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{t} = 2)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
         & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
@@
 
-  \item $u(\dataobs, r) \neq 0$, $\ux{r} + k \neq 0$ and $-\ux{r} < k < 0$
-
-  \item $\ux{r} = 0$.\\
-  By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
-  Destruct $k$:
-  \begin{itemize}
-    \item $k = 0$:\\
+  \item $\ux{r} \neq 0, \ux{r} + k = 0$ \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
+      By $\ux{r} + k = 0$, $\cardinality{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
+      By $\ux{r} \neq 0$, $\cardinality{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
+      $\implies$\\
+      \begin{equation*}
+      \begin{split}
+      LHS   
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{t} = 1)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \item $\ux{r} = 0, \ux{r} + k = 0$: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}\\
+
         \begin{equation*}
@@
         \end{equation*}
-    \item $k \neq 0$:\\
-    By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$.\\
-    $\implies$\\
-    \begin{equation*}
-    \begin{split}
-    LHS 
-    & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
-    & < 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
-    & = RHS.
-    \end{split}
-    \end{equation*}
 
 \end{itemize}
-  \item $\ux{r} \neq 0, \ux{r} + k = 0$
-    By $\ux{r} + k = 0$, $\cardinality{t} = 1$.\\
-    By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
-    $\implies$\\
-    \begin{equation*}
-    \begin{split}
-    LHS 
-    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 1 \cdot \hexpmechPr{\dataobs}{z = t}\\
-    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
-    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
-    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-    & = e^{\ln 2} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-    & = e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-    & = RHS.
-    \end{split}
-    \end{equation*}
-
-\end{itemize}
+Then, the proof is finished.
 

### 2018-10-26 Arxiv/main.tex
rewrite differential privacy proof case 1

--- 2018-10-26 Arxiv/main.tex
@@
 \begin{definition}
+\label{def_epsilon_dp}
 $\epsilon-$differential privacy.
@@
 \begin{definition}
+\label{def_epsilon_delta_dp}
 $(\epsilon,\delta)-$differential privacy.
@@
 \end{lem}
-\begin{proof} of lemma \ref{lem_score_pro_convert}.
+\begin{proof} of Lemma \ref{lem_score_pro_eq}.
 \begin{itemize}
@@
   \begin{split}
-  \ux{r'} = \ux{r''} 
+  & \ux{r'} = \ux{r''} \\
+  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
   & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
@@
   = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
-  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r''] \\
+  & Apply\ Definition\ \ref{def_smoo} :\\
   & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
@@
   & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
-  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r'']\\
+  & Apply\ Definition\ \ref{def_smoo} :\\
   & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
@@
   & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
+  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
   & \implies \ux{r'} = \ux{r''}.
@@
   Define $\cardinality{r}$ as the cardinality of $R_r$ s.t.
-$ R_r = \{ r' : \ux{r'} = \ux{r}, r' \in \candidateset{\dataobs}\} \subset \candidateset{\dataobs}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$,
+$ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t.
+\ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$,
 \end{definition}
@@
 By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
-Apply Lemma \ref{lem_score_pro_convert} in $R_r$, \\
+Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
 $\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
@@
 \leq
-e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
+e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
 \end{equation*}
@@
 
-Let $\ux{t} = \ux{r} + k$.
 In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
@@
 
+\todo{
+In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
+\begin{itemize}
+  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 1\}$.
+  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 2\}$.
+\end{itemize}
+}
+
 Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
 \begin{itemize}
-  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$ and $k \geq 0$.\\
-  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$.\\
-  By Lemma \ref{lem_score_pro_convert}, $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r} \hexpmechPr{\dataobs}{z = r}$.\\
-  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$.\\
+  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
+  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
+  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{r} = 2$}\\
+  Destruct k:
+  \begin{itemize}
+    \item  $k \geq 0$: $\implies$\\
+      \begin{equation*}
+      \begin{split}
+      LHS 
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+    \item $-\ux{r} < k < 0$: $\implies$\\
+
+      \begin{equation*}
+      \begin{split}
+      LHS 
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \end{itemize}
+
+  \item $\ux{r} = 0, \ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
+        By $\ux{r} = 0$, $\cardinality{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
+        By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
         $\implies$\\
@@
         LHS 
-    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
-    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ Definition\ \ref{def_smoo})\\
+        & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{r} = 1) \\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{t} = 2)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
+        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
         & = RHS.
@@
 
-  \item $u(\dataobs, r) \neq 0$, $\ux{r} + k \neq 0$ and $-\ux{r} < k < 0$
-
-  \item $\ux{r} = 0$.\\
-  By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
-  Destruct $k$:
-  \begin{itemize}
-    \item $k = 0$:\\
+  \item $\ux{r} \neq 0, \ux{r} + k = 0$ \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
+      By $\ux{r} + k = 0$, $\cardinality{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
+      By $\ux{r} \neq 0$, $\cardinality{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
+      $\implies$\\
+      \begin{equation*}
+      \begin{split}
+      LHS   
+      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{t} = 1)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \item $\ux{r} = 0, \ux{r} + k = 0$: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}\\
+
         \begin{equation*}
@@
         & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
-    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
         & = RHS.
@@
 \label{lem_dilation}
-for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:
-
-\begin{equation*}
-\hexpmechPr{\dataobs}{u(z,\dataobs) = c}
+Given $\hexpmech(\dataobs)$ in Beta-binomial system, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:
+
+\begin{equation*}
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
 \leq
-e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,\dataobs) = e^{\lambda} c} + \frac{\delta'}{2},
-\end{equation*}
-where the sensitivity in mechanism is still smooth sensitivity as above.
-
-More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
+e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
+\end{equation*}
 \end{lem}
 
-\begin{proof}
-
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
-
-We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.
-
+\begin{proof} of Lemma \ref{lem_dilation}.
+
+\todo{
+The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:\\
+We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.\\
 We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.
-
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.\\
 Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$.
@@
 The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\
-
-\textbf{Detail proof:}
+Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.
+}
+
+  In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
+  \begin{itemize}
+    \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \end{itemize}
+  Let $\ux{t} = e^{\lambda} \ux{r}$, then the proof is given by cases:
+
+  \begin{itemize}
+    \item $\ux{r} = 0$:
+
+        By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{t} = 1$.
+
+    \item $\ux{r} \neq 0$:\\
+        By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{t} = 2$.
+
         To show:
         \begin{equation*}
-	\hexpmechPr{\dataobs}{u(z,\dataobs) = u(r,\dataobs)}
+        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
         \leq
-	e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,x) = e^{\lambda} u(r,\dataobs)} + \frac{\delta'}{2},
-	\end{equation*}
-  we need to show:
-  \begin{equation*}
-  Pr[u(\hexpmech(\dataobs), \dataobs) = u(r,\dataobs)]
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
+        \end{equation*}
+
+        We need to show 
+        \begin{equation*}
+        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
         \leq
-  e^{\frac{\epsilon}{2}} Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
-  \end{equation*}
-
-	Let $u(r,\dataobs) = c$, $Pr[u(\hexpmech(\dataobs), \dataobs) = c] = |z|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} c] = |z|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
-
-	After simplification, we need to show: $u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
-	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
+        \begin{equation*}
+         \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
+        \leq
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = \ux{t}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By Lemma \ref{lem_score_pro_convert}, we need to show:
+        \begin{equation*}
+        \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}
+        \leq
+        e^{\frac{\epsilon}{2}} \cardinality{t} \cdot \hexpmechPr{\dataobs}{z = t}
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By $\cardinality{t} = \cardinality{r} = 2$, we need to show:
+        \begin{equation*}
+        \hexpmechPr{\dataobs}{z = r}
+        \leq
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By Definition \ref{def_smoo}, we need to show:
+        \begin{equation*}
+        \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
+        \leq
+        e^{\frac{\epsilon}{2}} \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By simplification, $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$, $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$ and $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
+        \begin{equation*}
+        \ux{r}(1 - e ^ {\lambda})
+        \leq 
+        S(\dataobs),
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        Then, prove it by two cases: $\lambda \leq 0$, and $\lambda > 0$:
 
       \begin{itemize}
-	\item $\lambda < 0$
-
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
-		\begin{equation*}
-		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
-		\end{equation*}
-		is always true when $\lambda < 0$
-	\item $\lambda > 0$
-
-		Because $\hat{s} = u(r, \dataobs)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs), \dataobs)$.
-Then, what we need to proof under the case $\lambda > 0$ is:
-		\begin{equation}
+        \item $\lambda < 0$:
+
+          \begin{equation*}
+          \ux{r}(1 - e ^ {\lambda}) \leq 0 \leq S(\dataobs)
+          \end{equation*}
+          is always true.
+
+        \item $\lambda > 0$:
+
+          To show:
+          \begin{equation*}
+          \ux{r}(1 - e ^ {\lambda})
+          \leq 
+          S(\dataobs),
+          \end{equation*}
+          holds with failure probability $\frac{\delta'}{2}$.
+
+          We need to show:
+          \begin{equation*}
           \label{eq_dilation_case2}
-		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
-		\end{equation}
+          \ux{r}
+          \leq 
+          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
+          \end{equation*}         
+          holds with failure probability $\frac{\delta'}{2}$.
 
@@
           \begin{equation*}
-		\begin{split}
-		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
-		& \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
-		\end{split}
+          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
           \end{equation*}
@@
           \begin{split}
-		Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
-		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
-		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
-		\end{split}
-		\end{equation*}
-
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
-
-		Particularly in Beta-binomial system, $|\candidateset{\dataobs}| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.
+          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
+          & = |\candidateset{\dataobs}|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
+          & = |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
+          \end{split}
+          \end{equation*}
+
+          By setting $|\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
+          \begin{equation*}
+          \begin{split}
+          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
+          \end{split}
+          \end{equation*}
+          holds, i.e.,
+          \begin{equation*}
+          \label{eq_dilation_case2}
+          \ux{r}
+          \leq 
+          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
+          \end{equation*}         
+          holds with failure probability $\frac{\delta'}{2}$ is proved.
+
+          Particularly, $|\candidateset{\dataobs}| = n + 1$ because in Beta-binomial system.
+
+      \end{itemize}
 
@@
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
+$\hexpmech$ is $(\epsilon, \delta)$-differential privacy in Beta-binomial system.
 \end{lem}
 
-\begin{proof}
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
+
+  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
 
@@
   \begin{equation*}
-\hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
-\end{equation*}
-
-	Given that $\hexpmechPr{\dataobs}{z = r} = \hexpmechPr{\dataobs}{u(\dataobs,z) = u(\dataobs,r)}$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
-Then,
-
-	Given that $2\Big( \hexpmechPr{\dataobs}{z = r}\Big) = \hexpmechPr{\dataobs}{u(z, \dataobs) = u(r, \dataobs)}$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
-Then,
+  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r} + \delta. 
+  \end{equation*}
+
+   In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$, when considering data set $\dataobs$:
+  \begin{itemize}
+    \item[*] $\cardinality{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[*] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \end{itemize}
+  when considering data set $\dataobs'$:
+  \begin{itemize}
+    \item[*] $\cardinality{r} = 1$, $\uxadj{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[*] $\cardinality{r} = 2$, $\uxadj{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \end{itemize}
+
+  Then the proof is given by cases:
+  \begin{itemize}
+    \item $\ux{r} \neq 0$, $\uxadj{r} \neq 0$:
+
+    By $\ux{r} \neq 0$, $\cardinality{r} = 2$ under data set $\dataobs$.
+
+      Apply \ Lemma\ \ref{lem_score_pro_convert}:  
+      \begin{equation*}
+      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
+      \end{equation*}
+
+      Apply \ Lemma\ \ref{lem_sliding}:
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
+      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply \ Lemma \ref{lem_dilation}:
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply Lemma \ref{lem_score_pro_convert}:
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{t} = 2$.\\
+      Apply  $\cardinality{r} = 2$ and  $\cardinality{t} = 2$:\\
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}} 2 \hexpmechPr{\dataobs}{z = t} \\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big)\\
+      \end{split}
+      \end{equation*}
+
+      Apply Definition \ref{def_smoo} and $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$:
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      2  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big)
+      \end{split}
+      \end{equation*}
+
+      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      2 \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big)\\
+       \end{split}
+      \end{equation*}
+
+      Apply Definition \ref{def_smoo} and $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      2  \hexpmechPr{\dataobs'}{z = r}
+      + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big)\\
+      & = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs'}{z = r} \\
+      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)\\
+      \end{split}
+      \end{equation*}
+
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}$, and
+      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)$.
+
+    \item $\ux{r} = 0$, $\uxadj{r} \neq 0$:
+    \item $\ux{r} \neq 0$, $\uxadj{r} = 0$:
+    \item $\ux{r} = 0$, $\uxadj{r} = 0$:
+  \end{itemize}
 

### 2018-10-26 Arxiv/main.tex
rewrite differential privacy other cases

@@
 \label{def_cardinality}
-  $\cardinality{r}$
-
-  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t.
+  $\cardinality{\dataobs}{r}$
+
+  Define $\cardinality{\dataobs}{r}$ as the cardinality of $R_r$ s.t.
 $ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t.
@@
 \begin{equation*}
-\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
  \end{equation*}
@@
 $\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
-$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
-$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
+$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
+$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
 \end{proof}
@@
 
-In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
+In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
 \begin{itemize}
-  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
-  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
 \end{itemize}
@@
 \todo{
-In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
+In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
 \begin{itemize}
-  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 1\}$.
-  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 2\}$.
+  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
+  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
 \end{itemize}
@@
 \begin{itemize}
-  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
-  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
-  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{r} = 2$}\\
+  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
+  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
+  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}\\
   Destruct k:
@@
       LHS 
-      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
       (Apply\ Definition\ \ref{def_smoo})\\
-      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
       (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
       & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
@@
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
@@
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \cardinality{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
@@
 
-  \item $\ux{r} = 0, \ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
-        By $\ux{r} = 0$, $\cardinality{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
-        By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
+  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
+        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
+        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
         $\implies$\\
@@
         LHS 
-        & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
         (Apply\ Definition\ \ref{def_smoo})\\
-        & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
         (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{r} = 1) \\
+        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
         & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
@@
         & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{t} = 2)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
         & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
@@
 
-  \item $\ux{r} \neq 0, \ux{r} + k = 0$ \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
-      By $\ux{r} + k = 0$, $\cardinality{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
-      By $\ux{r} \neq 0$, $\cardinality{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
-      $\implies$\\
+  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}
+
+      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}
+
+      $\implies$
       \begin{equation*}
@@
       LHS   
-      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
       (Apply\ Definition\ \ref{def_smoo})\\
-      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
       (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
       & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
@@
       & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{t} = 1)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
       & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
@@
 
-  \item $\ux{r} = 0, \ux{r} + k = 0$: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}\\
+  \item {\boldmath $\ux{r} = 0, \ux{r} + k = 0$}: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}
 
@@
 
-  In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
+  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
   \begin{itemize}
-    \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+    \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
   \end{itemize}
@@
   \begin{itemize}
-    \item $\ux{r} = 0$:
-
-        By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
-        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{t} = 1$.
-
-    \item $\ux{r} \neq 0$:\\
-        By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
-        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{t} = 2$.
+    \item {\boldmath$\ux{r} = 0$}:
+
+        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{\dataobs}{t} = 1$.
+
+    \item {\boldmath$\ux{r} \neq 0$}:\\
+        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
 
@@
         \begin{equation*}
-        \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}
+        \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}
         \leq
-        e^{\frac{\epsilon}{2}} \cardinality{t} \cdot \hexpmechPr{\dataobs}{z = t}
+        e^{\frac{\epsilon}{2}} \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}
         \end{equation*}
@@
 
-        By $\cardinality{t} = \cardinality{r} = 2$, we need to show:
+        By $\cardinality{\dataobs}{t} = \cardinality{\dataobs}{r} = 2$, we need to show:
         \begin{equation*}
@@
       \begin{itemize}
-        \item $\lambda < 0$:
+        \item {\boldmath$\lambda < 0$}:
 
@@
 
-        \item $\lambda > 0$:
+        \item {\boldmath$\lambda > 0$}:
 
@@
 
-\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
+\noindent \textbf{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
 \begin{lem}
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy in Beta-binomial system.
+$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
 \end{lem}
@@
 
-  For all $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$, we need to show that:
-  \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r} + \delta. 
-  \end{equation*}
-
-   In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$, when considering data set $\dataobs$:
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
+  \begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon'} \hexpmechPr{\dataobs'}{z = r} + \delta. 
+  \end{equation*}
+
+   In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$, when considering data set $\dataobs$:
   \begin{itemize}
-    \item[*] $\cardinality{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[*] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+    \item[*] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[*] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
   \end{itemize}
@@
   \begin{itemize}
-    \item[*] $\cardinality{r} = 1$, $\uxadj{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[*] $\cardinality{r} = 2$, $\uxadj{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R_r$ containing only the correct posterior.
+    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
   \end{itemize}
 
-  Then the proof is given by cases:
-  \begin{itemize}
-    \item $\ux{r} \neq 0$, $\uxadj{r} \neq 0$:
-
-    By $\ux{r} \neq 0$, $\cardinality{r} = 2$ under data set $\dataobs$.
-
-      Apply \ Lemma\ \ref{lem_score_pro_convert}:  
-      \begin{equation*}
-      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
-      \end{equation*}
-
-      Apply \ Lemma\ \ref{lem_sliding}:
-      \begin{equation*}
-      \begin{split}
-      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
-      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
-      \end{split}
-      \end{equation*}
-
-      Apply \ Lemma \ref{lem_dilation}:
-      \begin{equation*}
-      \begin{split}
-      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      Apply Lemma \ref{lem_score_pro_convert}:  
+      \begin{equation*}
+      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{\dataobs}{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
+      \end{equation*}
+
+      Apply Lemma \ref{lem_sliding}:
+      \begin{equation*}
+      \begin{split}
+      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply Lemma \ref{lem_dilation}:
+      \begin{equation*}
+      \begin{split}
+      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
       \big( e^{\frac{\epsilon}{2}}
@@
       \begin{split}
-      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
       \big( e^{\frac{\epsilon}{2}}
@@
       \begin{split}
-      & = \frac{1}{\cardinality{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
       \big( e^{\frac{\epsilon}{2}}
-      \cardinality{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
+      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
       & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
@@
 
-      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{t} = 2$.\\
-      Apply  $\cardinality{r} = 2$ and  $\cardinality{t} = 2$:\\
-      \begin{equation*}
-      \begin{split}
-      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}} 2 \hexpmechPr{\dataobs}{z = t} \\
+      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset{\dataobs}$:
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
+      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+       \end{split}
+      \end{equation*}
+
+      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
       & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big)\\
-      \end{split}
-      \end{equation*}
-
-      Apply Definition \ref{def_smoo} and $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$:
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      2  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big)
-      \end{split}
-      \end{equation*}
-
-      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      2 \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big)\\
-       \end{split}
-      \end{equation*}
-
-      Apply Definition \ref{def_smoo} and $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$:\\
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{2} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      2  \hexpmechPr{\dataobs'}{z = r}
-      + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big)\\
-      & = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
+      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
       \hexpmechPr{\dataobs'}{z = r} \\
-      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)\\
-      \end{split}
-      \end{equation*}
-
-      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}$, and
-      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      \end{split}
+      \end{equation*}
+
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}$, and
+      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
       \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)$.
 
-    \item $\ux{r} = 0$, $\uxadj{r} \neq 0$:
-    \item $\ux{r} \neq 0$, $\uxadj{r} = 0$:
-    \item $\ux{r} = 0$, $\uxadj{r} = 0$:
+ Then the proof is given by cases:
+  \begin{itemize}
+    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} \neq 0$}:
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
+
+      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      $$ and
+      $$
+      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}:
+
+      By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
+
+      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      $$ and
+      $$
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} = 0$}:
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
+
+      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln (\frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      $$ and
+      $$
+      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
+
+      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln (e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      $$ and
+      $$
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      $$
+
   \end{itemize}
 
-	\begin{equation*}
-	\begin{split}
-	\hexpmechPr{\dataobs}{z = r}
-	& = 	\frac{1}{|z|}\Big( \hexpmechPr{\dataobs}{ u(z, \dataobs) = U}\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \hexpmechPr{\dataobs}{u(z, \dataobs) = U_2}\Big)\\
-	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \hexpmechPr{\dataobs}{u(z, \dataobs) = U_3} + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(z, \dataobs') = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
-	\end{split}
-	\end{equation*}
-	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.
-
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
-The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
-
- $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
+      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
+      $
+      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
+      $, and
+      $
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      $
 \end{proof}

### 2018-10-26 Arxiv/main.tex
fix typos in proof

@@
 \label{lem_score_pro_eq}
-  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
+  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset{\dataobs}$, then following holds:
   $$
-  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
+  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
   $$  
@@
   \begin{split}
-  & \ux{r'} = \ux{r''} \\
-  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
-  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
-  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
+  & \ux{r_1} = \ux{r_2} \\
+  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
+  & \implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
+  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
   & Apply\ Definition\ \ref{def_smoo} :\\
-  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
+  & \implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
   \end{split}
@@
   \begin{split}
-  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
+  & \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} \\
   & Apply\ Definition\ \ref{def_smoo} :\\
-  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
-  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
-  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
-  & \implies \ux{r'} = \ux{r''}.
+  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
+  & \implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
+  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
+  & \implies \ux{r_1} = \ux{r_2}.
   \end{split}
@@
 \label{def_cardinality}
-  $\cardinality{\dataobs}{r}$
-
-  Define $\cardinality{\dataobs}{r}$ as the cardinality of $R_r$ s.t.
-$ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t.
-\ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$,
+  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.
+
+  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset{\dataobs}$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
+
+  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
 \end{definition}
@@
 To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
-$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
-By Definition \ref{def_cardinality}, $R_r$ is this set.\\
-$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
-By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
+$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
+By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
+$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
+By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
 Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
@@
 
-Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
+Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity.
+In Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
 \begin{equation*}
@@
 \label{lem_dilation}
-Given $\hexpmech(\dataobs)$ in Beta-binomial system, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:
-
+Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the following \emph{dilation property} holds:
 \begin{equation*}
@@
   \end{itemize}
-  Let $\ux{t} = e^{\lambda} \ux{r}$, then the proof is given by cases:
-
+  Let $\ux{t} = e^{\lambda} \ux{r}$.
+
+  \begin{assert}
+  \label{cardinality_eq}
+  For any $r\in \candidateset{\dataobs}$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
+  \end{assert}
+
+  \begin{proof} of Assertion \ref{cardinality_eq}.
+
+  The proof is given by cases:
   \begin{itemize}
@@
         By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
+  \end{itemize}
+
+  Then, in either case, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
+
+  \end{proof}
 
@@
 
-        By $\cardinality{\dataobs}{t} = \cardinality{\dataobs}{r} = 2$, we need to show:
+        By Assertion \ref{cardinality_eq}, we need to show:
         \begin{equation*}
@@
 
-        \item {\boldmath$\lambda > 0$}:
+        \item {\boldmath $\lambda > 0$}:
 
@@
           We need to show:
-          \begin{equation*}
+          \begin{equation}
           \label{eq_dilation_case2}
@@
           \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
-          \end{equation*}         
+          \end{equation}         
           holds with failure probability $\frac{\delta'}{2}$.
@@
 
-          apply this bound to eq. \ref{eq_dilation_case2}:
+          apply this bound to Equation. \ref{eq_dilation_case2}:
           \begin{equation*}
@@
           \begin{equation*}
-          \label{eq_dilation_case2}
           \ux{r}
@@
           Particularly, $|\candidateset{\dataobs}| = n + 1$ because in Beta-binomial system.
-
-      \end{itemize}
 
@@
       & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
-      \end{split}
-      \end{equation*}
-
-      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}$, and
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
+      \end{split}
+      \end{equation*}
+
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \ln \Big( \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big)$, and
       $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)$.
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.
 
@@
       $$
-      \epsilon' = \ln( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
       $$ and
@@
       \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
       $$
-      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      \epsilon' = \ln \Big( 2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
       $$ and
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
       $$
@@
       $$
-      \epsilon' = \ln (\frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      \epsilon' = \ln \Big( \frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
       $$ and
@@
       \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
     \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:
+
       By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
@@
 
-      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 1$:
 
@@
       $$
-      \epsilon' = \ln (e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
+      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
       $$ and
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
-      $
+      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
+      $\\
+
 \end{proof}

### 2018-10-26 Arxiv/main.tex
fix typos

@@
       (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
       & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
-      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
       & = RHS.
@@
         & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
         & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
         & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
-        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
         & = RHS.
@@
       & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
       & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
@@
       & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
       & = RHS.
@@
         & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
-        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
         & = RHS.

### 2018-10-26 Arxiv/main.tex
fix typos

@@
   \item $\implies$
-  \begin{equation*}
-  \begin{split}
-  & \ux{r_1} = \ux{r_2} \\
-  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
-  & \implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
-  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
-  & Apply\ Definition\ \ref{def_smoo} :\\
-  & \implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
-  \end{split}
-  \end{equation*}
+
+  $\ux{r_1} = \ux{r_2}$
+
+  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:\\
+  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
+  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.
+
+  Apply\ Definition\ \ref{def_smoo}:\\
+  $\implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}$.
 
@@
 
-    \begin{equation*}
-  \begin{split}
-  & \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} \\
-  & Apply\ Definition\ \ref{def_smoo} :\\
-  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
-  & \implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
-  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
-  & \implies \ux{r_1} = \ux{r_2}.
-  \end{split}
-  \end{equation*}
+  $\hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} $
+
+  Apply Definition \ref{def_smoo}:\\
+  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+    = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.\\
+  $\implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$.
+
+  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:
+  $\implies \ux{r_1} = \ux{r_2}$.
+
 \end{itemize}
@@
 $\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
-By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
-Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
-$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
-$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
+By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
+Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
+$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
+$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
 $\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
@@
 \begin{itemize}
-  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
-  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
 \end{itemize}
@@
   By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
-  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}\\
-  Destruct k:
+  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}
   \begin{itemize}
-    \item  $k \geq 0$: $\implies$\\
+    \item  $k \geq 0$: $\implies$
       \begin{equation*}
@@
 
-    \item $-\ux{r} < k < 0$: $\implies$\\
-
+    \item $-\ux{r} < k < 0$: $\implies$
       \begin{equation*}
@@
         By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
-        $\implies$\\
+        $\implies$
         \begin{equation*}
@@
 
-  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}
-
-      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}
-
-      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}
-
+  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
+      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
       $\implies$
@@
 \begin{itemize}
-    \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
 \end{itemize}
@@
 \begin{itemize}
-    \item[*] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[*] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
 \end{itemize}
@@
   \begin{itemize}
-    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R_r$ containing only the correct posterior.
-    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
+    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R^{\dataobs'}_r$ contains only the correct posterior.
+    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R^{\dataobs'}_r$ contains 2 elements by the symmetry property of $\hellinger$.
   \end{itemize}

### 2018-10-31 notes/privacy-proof/main.tex
update the privacy proof notes

--- 2018-10-23 notes/fullproof/main.tex
@@
 \begin{document}
-\title{Full proof on the differential privacy property of $\hexpmech$}
+\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
 
-\begin{abstract}
-\end{abstract}
-
-\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
-
+\author[*]{Jiawen Liu}
+\author[**]{Mark Bun}
+\author[*]{Gian Pietro Farina}
+\author[*]{Marco Gaboardi}
+\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
+\date{}
 \maketitle
@@
 \begin{definition}
+\label{def_epsilon_dp}
 $\epsilon-$differential privacy.
 
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B],
+\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B].
 \end{equation*}
-where $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+
 \end{definition}
@@
 \begin{definition}
+\label{def_epsilon_delta_dp}
 $(\epsilon,\delta)-$differential privacy.
 
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
+A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
 \begin{equation*}
@@
 \end{definition}
+
+\section{$\gamma$ -Smooth Sensitivity}
+\label{sec_mechs}
+$S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
+
+\begin{equation}
+  \label{eq:smooth}
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
+\end{equation}
+where $d$ is the Hamming distance between two data sets, and $\gamma = 1$.
 
@@
 \label{def_smoo}
-The mechanism $\hexpmech(x)$ outputs a candidate $r \in \candidateset$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\displaystyle\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
+{\nomalizer{\dataobs}}.
 \end{equation*}
-where $S_\beta(x)$ is the smooth sensitivity of $\hellinger(\bysinfer(x),-)$, calculated by:
+where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
 
@@
   \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
-where $d$ is the Hamming distance between two datasets, and $\beta =
-\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
+where $d$ is the Hamming distance between two datasets, and $\gamma = 0.5$.
 \end{definition}
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
+By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
@@
 
-\subsection{Privacy Analysis for $\hexpmech$}
+\begin{lem}
+\label{lem_hexpmech_privacy}
+$\hexpmech$ is $2\epsilon$-differential privacy in Beta-binomial system.
+\end{lem}
 
-The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
+  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
 
-\noindent \textbf{Sliding Property of $\hexpmech$}
-\begin{lem}
-Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
   \begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-\leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
+  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
   \end{equation*}
 
-\end{lem}
+  By definition \ref{def_smoo}:
 
-\begin{proof}
-
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
- $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\candidateset$ we have:
-
-$$
-\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
- \hellinger(\bysinfer(x),r)]\Big )
-$$
-
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
-We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-Because Hellinger distance  $\hellinger(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
-It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-This parameter can be eliminate in both sides in proof.
-
-We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
   \begin{equation*}
   \begin{split}
-LHS 
-  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
+  \hexpmechPr{\dataobs}{z = r} 
+  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\nomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\nomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
   \end{split}
@@
 
-By bounding the $\Delta \geq -S(x)$, we can get:
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon}{2} \big) \\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)\\
+  \end{split}
+  \end{equation*}
 
@@
   \begin{split}
-\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
   \end{split}
@@
 
-\end{proof}
-
-\noindent \textbf{Dilation Property of $\hexpmech$}
-\begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
 
   \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
-\leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
-\end{equation*}
-where the sensitivity in mechanism is still smooth sensitivity as above.
-\end{lem}
-
-\begin{proof}
-
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
-
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
-
-We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
-
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
-Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
-Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\
-
-\textbf{Detail proof:}
-
-	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
-\begin{itemize}
-	\item $\lambda < 0$
-
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
-		\begin{equation*}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-		\end{equation*}
-		is always true when $\lambda < 0$
-	\item $\lambda > 0$
-
-		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
-		\begin{equation}
-		\label{eq_dilation_case2}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-		\end{equation}
-		Based on the accuracy property of exponential mechanism:
-		\begin{equation*}
   \begin{split}
-		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})}\\
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
   \end{split}
@@
 
-		we derived the accuracy bound for $\hexpmech$:
+  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)}| \leq \gamma$:
 
@@
   \begin{split}
-		Pr[u(\hexpmech(x)) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)})
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2} \cdot \gamma
+  \big)\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  \end{split}
+  \end{equation*}
+  Doing the same transformation in the denominator:
+
+  \begin{equation*}
+  \begin{split}
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
   \end{split}
@@
 
-		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
+
   \begin{equation*}
   \begin{split}
-		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
-		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon\cdot(\ux{r'})}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
   \end{split}
@@
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
-
-		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
-
-\end{itemize}
-
-\end{proof}
-
-\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
-\begin{lem}
-\label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
-\end{lem}
-
-\begin{proof}
-of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
-\end{equation*}
-Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
-Then,
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
 
@@
   \begin{split}
-2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
-& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
-& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
   \end{split}
@@
 
-The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
-
-\end{proof}
-
-\section{Accuracy Analysis}
-
-\subsection{Accuracy Bound for Baseline Mechanisms}
-
-\subsection{Accuracy Bound for $\hexpmech$}
-\label{subsec_accuracy_smoo}
-We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
-
-First is the tight bound with very accurate calculation.
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hellinger(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(x), z)}{S(x)}}}{NL_x}.
-\end{equation*}
-
-In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
-\end{equation*}
-
-In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hellinger(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
-\end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
-
-Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
-
+  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma$ $\implies$
+  $\frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}-
+  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
       \begin{equation*}
   \begin{split}
-Pr[u(\hexpmech(x)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset{\dataobs}} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  }\\
+  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
   \end{split}
@@
 
-which has been used in the dilation property proof.
+  By setting the $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
+\end{proof}
 
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{plain}
 \bibliography{bayesian.bib}

### 2018-10-31 codes/dpbayesinfer_Betabinomial.py

@@ -134,9 +134,8 @@ class BayesInferwithDirPrior(object):
 		#CALCULATING THE SENSITIVITY
 		###################################################################################################################################
 		t0 = time.time()
-		self._set_local_sensitivities()
 		start = time.clock()
-		beta = 0.000001 # math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
+		beta = 0.001 # math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
 		self._SS = max(self._LS, max([self._LS_Candidates[r] * math.exp(- beta * Hamming_Distance(self._observation_counts, [r._alphas[i] - self._prior._alphas[i] for i in range(self._prior._size)])) for r in self._candidates]))
 		t1 = time.time()
 		print("smooth sensitivity"+str(t1 - t0)), self._SS
@@ -147,7 +146,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(self._SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._SS))
 			self._SS_probabilities.append(temp)
 			nomalizer += temp
 
@@ -174,7 +173,6 @@ class BayesInferwithDirPrior(object):
 		#CALCULATING THE SENSITIVITY
 		###################################################################################################################################
 		t0 = time.time()
-		self._set_local_sensitivities()
 		start = time.clock()
 		beta = 0.5
 		self._alpha_SS = max([(1.0 / (1.0/self._LS_Candidates[r] + beta * Hamming_Distance(self._observation_counts, [r._alphas[i] - self._prior._alphas[i] for i in range(self._prior._size)]))) for r in self._candidates])
@@ -187,7 +185,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(self._alpha_SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._alpha_SS))
 			self._alpha_SS_probabilities.append(temp)
 			nomalizer += temp
 
[…]

### 2018-10-31 codes/sampling_on_betabinomial_bayesinfer.py

@@ -241,8 +241,8 @@ if __name__ == "__main__":
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS
 #############################################################################
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((200,500),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
-	percentage = [0.5,0.5]
+	datasizes = gen_datasizes((30,300),30)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	percentage = [1.0/3,1.0/3,1/3.0]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2)# + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)
 	

### 2018-10-31 notes/privacy-proof/main.tex
update codes for experiments and fix typos in proof

@@
 
-\section{$\gamma$ -Smooth Sensitivity}
+\section{$\gamma$-Smooth Sensitivity}
 \label{sec_mechs}
-$S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
+
+\begin{definition}
+
+$S(\dataobs)$ is the $\gamma -$smooth sensitivity of data set $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:
 
 \begin{equation}
-  \label{eq:smooth}
+\label{eq_gamma_smooth}
+|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma.
+\end{equation}
+\end{definition}
+
+\begin{thm}
+\label{thm_gamma_smooth}
+$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
+\begin{equation}
+  \label{eq_smooth}
    S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
-where $d$ is the Hamming distance between two data sets, and $\gamma = 1$.
+where $d$ is the Hamming distance between two data sets.
+\end{thm}
 
-\section{Mechanism Proposition}
+\begin{proof}
+of Theorem. \ref{thm_gamma_smooth}.
+
+\end{proof}
+
+\section{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
 \label{sec_mechs}
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
+Given a prior distribution $\bprior = \betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
 \[
-  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
+  \candidateset\dataobs \equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
 \]
 where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
-Notice that $\candidateset$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\candidateset$
+Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
 that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
@@
 
-\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
-\label{subsec_hexpmech}
-
 \begin{definition}
 \label{def_smoo}
-The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset\dataobs$ with probability
 \begin{equation*}
@@
 \end{equation*}
-where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
-
-\begin{equation}
-  \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
-\end{equation}
-where $d$ is the Hamming distance between two datasets, and $\gamma = 0.5$.
+where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
 \end{definition}
-
-This mechanism is based on the basic exponential mechanism
-\cite{talwar}, with $\candidateset$ as the range and
-$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
-that in this mechanism we don't calibrate the noise w.r.t. to the
-global sensitivity of the scoring function but w.r.t. to the smooth
-sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
-$\hellinger(\bysinfer(\dataobs), \cdot)$.
-
-$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
-be determined later, and where $LS(\dataobs')$ denotes the local
-sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
-of the scoring function used in our mechanism.
-
-This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
-\[
-  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
-\]
-and by replacing the $\candidateset$ with set of posterior Dirichlet
-distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
-over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
-will denote by $\hexpmechd$ the mechanism for the
-Dirichlet-multinomial system.
-
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
-(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
 
@@
   \big)\\
-  \end{split}
-  \end{equation*}
-
-  \begin{equation*}
-  \begin{split}
   & = exp\big( \frac{\epsilon}{2} \big) \cdot 

### 2018-10-31 codes/dpbayesinfer_Betabinomial.py

@@ -135,7 +135,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		t0 = time.time()
 		start = time.clock()
-		beta = 0.001 # math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
+		beta = 1 # math.log(1 - self._epsilon / (2.0 * math.log(self._delta / (2.0 * (self._sample_size)))))
 		self._SS = max(self._LS, max([self._LS_Candidates[r] * math.exp(- beta * Hamming_Distance(self._observation_counts, [r._alphas[i] - self._prior._alphas[i] for i in range(self._prior._size)])) for r in self._candidates]))
 		t1 = time.time()
 		print("smooth sensitivity"+str(t1 - t0)), self._SS
@@ -174,7 +174,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		t0 = time.time()
 		start = time.clock()
-		beta = 0.5
+		beta = 1
 		self._alpha_SS = max([(1.0 / (1.0/self._LS_Candidates[r] + beta * Hamming_Distance(self._observation_counts, [r._alphas[i] - self._prior._alphas[i] for i in range(self._prior._size)]))) for r in self._candidates])
 		t1 = time.time()
 		print ("alpha smooth sensitivity"+str(t1 - t0)), self._alpha_SS

### 2018-10-31 codes/sampling_on_betabinomial_bayesinfer.py

@@ -241,8 +241,8 @@ if __name__ == "__main__":
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS
 #############################################################################
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((30,300),30)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
-	percentage = [1.0/3,1.0/3,1/3.0]
+	datasizes = gen_datasizes((100,500),50)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	percentage = [0.5,0.5]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2)# + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)
 	

### 2018-10-31 notes/gamma-sensitivity-proof/main.tex
rename file prove the gamma smooth sensitivity

--- 2018-10-31 notes/privacy-proof/main.tex
@@
 \begin{definition}
-
-$S(\dataobs)$ is the $\gamma -$smooth sensitivity of data set $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:
+Given data set $\dataobs$, $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:
 
@@
 \label{eq_gamma_smooth}
-|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma.
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
 \end{equation}
@@
   \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
@@
 of Theorem. \ref{thm_gamma_smooth}.
+For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
+
+By Definition \ref{eq_smooth}:
+\begin{equation*}
+\begin{split}
+S(\dataobs) 
+& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
+\frac{1}{S(\dataobs)} 
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
+\end{split}
+\end{equation*}
+
+Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
+
+\begin{equation*}
+\begin{split}
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
+& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
+& = \gamma + \frac{1}{S(\dataobs')}
+\end{split}
+\end{equation*}
 
@@
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $2\epsilon$-differential privacy in Beta-binomial system.
+$\hexpmech$ is $2\epsilon$-differential privacy.
 \end{lem}
@@
   \hexpmechPr{\dataobs}{z = r} 
-  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} \\
+  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
   & = \frac {exp\big(
@@
   \big)}
-  {\nomalizer{\dataobs}} \\
+  {\unomalizer{\dataobs}} \\
   & = \frac {exp\big(
@@
   \big)}
-  {\nomalizer{\dataobs}}
+  {\unomalizer{\dataobs}}
   \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\

### 2018-10-31 notes/2epsilon/main.tex
rename folder
Update notes/2epsilon/main.tex

--- 2018-10-31 notes/gamma-sensitivity-proof/main.tex
@@
 \label{thm_gamma_smooth}
-$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
+$S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
 \begin{equation}
@@
 of Theorem. \ref{thm_gamma_smooth}.
+
 For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
@@
 \end{split}
+\end{equation*}
+$\implies$
+\begin{equation*}
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
 \end{equation*}
@@
 \end{equation*}
-where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
+where $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
 \end{definition}
@@
 \begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
+
   By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

### 2018-10-31 Arxiv/main.tex
Update Arxiv/main.tex
update codes for experiments and fix typos in proof
update typos

@@
 \[
-  \candidateset{\dataobs}\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
+  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
 \]
 where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
-Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
+Notice that $\candidateset$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\candidateset$
 that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
@@
 \subsubsection{Exponential Mechanism}
-Exponential mechanism $\expmech{}{x}{u}{\candidateset{\dataobs}}$ samples a element from the candidate set $\candidateset{\dataobs} = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{}{x}{u}{\candidateset{\dataobs}} }{Pr}[z=r] = \frac
+Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+\begin{equation*}
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 GS})}
@@
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset{\dataobs}}$ share the same candidate set and utility function as it with standard exponential mechanism.
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
 This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{local}{x}{u}{\candidateset{\dataobs}}}{\Pr}[z=r] = \frac
+\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
@@
 \label{def_smoo}
-The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset{\dataobs}$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
@@
 \end{equation}
-where $d$ is the Hamming distance between two datasets, and $\beta =
-\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
+where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
 \end{definition}
@@
 This mechanism is based on the basic exponential mechanism
-\cite{talwar}, with $\candidateset{\dataobs}$ as the range and
+\cite{talwar}, with $\candidateset$ as the range and
 $\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
@@
 \]
-and by replacing the $\candidateset{\dataobs}$ with set of posterior Dirichlet
+and by replacing the $\candidateset$ with set of posterior Dirichlet
 distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
@@
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset{\dataobs}$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
 will denote by $\hexpmechd$ the mechanism for the
@@
 
-In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.
+In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.
 
@@
 \label{lem_score_pro_eq}
-  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset{\dataobs}$, then following holds:
+  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
   $$
@@
 
-  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:\\
+  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
   $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
@@
 
-  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:
+  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
   $\implies \ux{r_1} = \ux{r_2}$.
@@
 
-  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset{\dataobs}$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
+  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
 
@@
 To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
-$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
+$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset \land \ux{r'} = \ux{r}\}}.$\\
 By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
@@
 Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity.
-In Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
+In Beta-binomial system, for any $r\in \candidateset$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
 \begin{equation*}
@@
 \todo{
-In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
+In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset$:
 \begin{itemize}
-  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
-  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
+  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
+  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
 \end{itemize}
@@
 \label{lem_dilation}
-Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the following \emph{dilation property} holds:
+Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
 \begin{equation*}
@@
   \label{cardinality_eq}
-  For any $r\in \candidateset{\dataobs}$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
+  For any $r\in \candidateset$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
   \end{assert}
@@
           \begin{split}
-          Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
+          Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
           & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
@@
           \begin{equation*}
-          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
+          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
           \end{equation*}
@@
           Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
-          & = |\candidateset{\dataobs}|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
-          & = |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
-          \end{split}
-          \end{equation*}
-
-          By setting $|\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
+          & = |\candidateset|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
+          & = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
+          \end{split}
+          \end{equation*}
+
+          By setting $|\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
           \begin{equation*}
@@
 
-          Particularly, $|\candidateset{\dataobs}| = n + 1$ because in Beta-binomial system.
+          Particularly, $|\candidateset| = n + 1$ because in Beta-binomial system.
 
@@
       \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big).
@@
       \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big).
@@
       \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big).
@@
 
-      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset{\dataobs}$:
+      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$:
       \begin{equation*}
@@
       \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big).
@@
       \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big).
@@
       \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
-      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
       \big ) \Big)\\
@@
       & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
       \end{split}
@@
       $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.
 
@@
       \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
       $$
@@
       \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
       $$
@@
       \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
       $\\
@@
 \begin{equation*}
-Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
+Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
 		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
@@
 Pr[u(\hexpmech(\dataobs)) \leq c] 
-& \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}),
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
 \end{split}
@@
 \ref{fig_efficiency}.
-We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset{\dataobs}$.
+We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
 It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

### 2018-10-31 notes/2epsilon/main.tex
update typos

@@
 \begin{document}
-\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
+\title{Proof of 2$\epsilon-$Differential Privacy}
 
@@
 \begin{definition}
-Given data set $\dataobs$, $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:
+Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:
 
+For any $\adj{\dataobs}{\dataobs'}$:
 \begin{equation}
@@
 \end{equation}
+
+$S(\dataobs)$ is $\gamma -$smooth sensitivity.
+
 \end{definition}
@@
   \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
+   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
 \end{equation}
@@
 \[
-  \candidateset\dataobs \equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
+  \candidateset \equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
 \]
 where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
-Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
+Notice that $\candidateset$ has $n + 1$ elements, and
+the Bayesian Inference process will produce an element from $\candidateset$
 that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
 parametrize the result by the prior, which from now on we consider
-fixed and we denote it by $\bprior$.
+fixed and we denote it by $\bprior$. Given data size n, $\candidateset$ is fixed.
 
@@
 \label{def_smoo}
-The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset\dataobs$ with probability
+The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\nomalizer{\dataobs}}.
+  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
+{\unomalizer{\dataobs}}.
 \end{equation*}
-where $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
 \end{definition}
 
-\section{Privacy Analysis}
+\section{$\hexpmech$ Privacy Analysis}
 
@@
 
-  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
+  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
 
@@
 
-  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)}| \leq \gamma$:
+  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:
 
@@
   {
-  \sum_{r'\in \candidateset{\dataobs}} 
+  \sum_{r'\in \candidateset} 
   exp 
@@
 
-  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma$ $\implies$
+  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
   $\frac{- \epsilon}{2}
@@
 
-  By setting the $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
+  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
 \end{proof}

### 2018-11-01 Arxiv/main.tex
fix typos

@@
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B].
+\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
 \end{equation*}
@@
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
-\end{equation*}
-vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
+\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
+\end{equation*} 
 \end{definition}
@@
 
-\subsubsection{Baseline Mechanism - Laplace Mechanism}
+\subsubsection{Laplace Mechanism}
  Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
@@
 
-This mechanism is based on the basic exponential mechanism
+This mechanism is based on the standard exponential mechanism
 \cite{talwar}, with $\candidateset$ as the range and
@@
 sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
-$\hellinger(\bysinfer(\dataobs), \cdot)$.
-
-$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
-be determined later, and where $LS(\dataobs')$ denotes the local
-sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
-of the scoring function used in our mechanism.
+$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
+sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.
 
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 

### 2018-11-01 notes/2epsilon/main.tex
fix typos

@@
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
+\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta,
 \end{equation*}
@@
 \label{thm_gamma_smooth}
-$S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
+Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
 \begin{equation}
@@
 
-By Definition \ref{eq_smooth}:
+By Equation (\ref{eq_smooth}):
 \begin{equation*}
@@
   By definition \ref{def_smoo}:
-
   \begin{equation*}
@@
   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
-
   \begin{equation*}
@@
   Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
-
   \begin{equation*}
@@
   \end{equation*}
+
   Doing the same transformation in the denominator:
-
   \begin{equation*}
@@
   Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
-
   \begin{equation*}
@@
   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
-
   \begin{equation*}

### 2018-11-01 Arxiv/main.tex
rearrange
update contents table

@@
 \documentclass{article}
-
 % We want page numbers on submissions
@@
 \input{macros}
-\usepackage{accents}
 
@@
 \author[*]{Marco Gaboardi}
-\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
-\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
+\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
 \date{}
 \maketitle
+{\footnotesize \tableofcontents}
+
+\newpage
 \begin{abstract} Bayesian inference is a statistical method which
@@
 \end{equation*}
-
 which has been used in the dilation property proof.
@@
 
-\subsection{Computation Efficiency Optimization}
+\subsection{Efficiency Evaluation}
 \label{subsec_effi}
 The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$
+\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
 can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
@@
 
-\subsection{Theoretical Results}
+\subsection{Accuracy Evaluation}
+\subsubsection{Theoretical Results}
 
@@
 
-\subsection{Experimental Results}
+\subsubsection{Experimental Results}
 \label{subsec_vs_variables}
@@
 
-\subsection{Experiment Evaluations on Privacy Loss}
+\subsection{Privacy Evaluation}
 \label{subsec_experiment_privacy}

### 2018-11-01 Arxiv/main.tex
Update Arxiv/main.tex

@@
 \maketitle
-{\footnotesize \tableofcontents}
+{\small \tableofcontents}
 
@@
 
-\noindent \textbf{Sliding Property of $\hexpmech$}
+\subsubsection{Sliding Property of $\hexpmech$}
 
@@
 
-\noindent \textbf{Dilation Property of $\hexpmech$}
+\subsubsection{Dilation Property of $\hexpmech$}
 \begin{lem}
@@
 
-\noindent \textbf{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
+\subsubsection{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
 \begin{lem}
@@
 
+\end{proof}
+
+\subsubsection{$\gamma$-Smooth Sensitivity}
+\label{sec_mechs}
+
+\begin{definition}
+Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:
+
+For any $\adj{\dataobs}{\dataobs'}$:
+\begin{equation}
+\label{eq_gamma_smooth}
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
+\end{equation}
+
+$S(\dataobs)$ is $\gamma -$smooth sensitivity.
+
+\end{definition}
+
+\begin{thm}
+\label{thm_gamma_smooth}
+Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
+\begin{equation}
+  \label{eq_smooth}
+   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
+\end{equation}
+where $d$ is the Hamming distance between two data sets.
+\end{thm}
+
+\begin{proof}
+of Theorem. \ref{thm_gamma_smooth}.
+
+For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
+
+By Equation (\ref{eq_smooth}):
+\begin{equation*}
+\begin{split}
+S(\dataobs) 
+& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
+\frac{1}{S(\dataobs)} 
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
+\end{split}
+\end{equation*}
+
+Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
+
+\begin{equation*}
+\begin{split}
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
+& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
+& = \gamma + \frac{1}{S(\dataobs')}
+\end{split}
+\end{equation*}
+$\implies$
+\begin{equation*}
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
+\end{equation*}
+
+\end{proof}
+
+Under this smooth sensitivity, we define $\hexpmech$ as:
+\begin{definition}
+\label{def_smoo_2}
+$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+\begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
+{\unomalizer{\dataobs}}.
+\end{equation*}
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
+\end{definition}
+
+\subsubsection{$\hexpmech$ $2\epsilon$ Privacy Analysis}
+
+\begin{lem}
+\label{lem_hexpmech_privacy}
+$\hexpmech$ is $2\epsilon$-differential privacy.
+\end{lem}
+
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
+
+  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
+
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
+  \begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
+  \end{equation*}
+
+  By definition \ref{def_smoo_2}:
+  \begin{equation*}
+  \begin{split}
+  \hexpmechPr{\dataobs}{z = r} 
+  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon}{2} \big) \\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)\\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2} \cdot \gamma
+  \big)\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  \end{split}
+  \end{equation*}
+
+  Doing the same transformation in the denominator:
+  \begin{equation*}
+  \begin{split}
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon\cdot(\ux{r'})}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
+  $\frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}-
+  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  }\\
+  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
+  \end{split}
+  \end{equation*}
+
+  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
 \end{proof}

### 2018-11-01 Arxiv/main.tex
Update Arxiv/main.tex

@@
 \label{lem_dilation}
-Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
+Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $1 - \frac{\delta'}{2} = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})$, the following \emph{dilation property} holds:
 \begin{equation*}
@@
 
-          Particularly, $|\candidateset| = n + 1$ because in Beta-binomial system.
+          Particularly, $|\candidateset| = n + 1$ in Beta-binomial system.
 
@@
 
-\subsubsection{$\hexpmech$ $2\epsilon$ Privacy Analysis}
+\subsubsection{$\hexpmech$ $2\epsilon-$Differential Privacy Proof}
 

### 2018-11-02 Arxiv/main.tex
update notes and Arixv
remove the dilation property and sliding property proof and save them into notes of SlidingDilation

@@
 \begin{definition}
-\label{def_smoo}
-The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\begin{equation*}
-\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\nomalizer{\dataobs}}.
-\end{equation*}
-where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:
-
-\begin{equation}
-  \label{eq:smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
-\end{equation}
-where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
+\label{def_smoo_2}
+$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+\begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
+{\unomalizer{\dataobs}}.
+\end{equation*}
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
 \end{definition}
@@
 Dirichlet-multinomial system.
-
-% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
-
-\section{Privacy Analysis}
-
-\subsection{Privacy Analysis for Baseline Mechanisms}
-In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
-The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
-
-\subsection{Privacy Analysis for $\hexpmech$}
-
-The differential privacy property of $\hexpmech$ is proved based on following two lemmas: Lemma \ref{lem_sliding} and Lemma \ref{lem_dilation}.\\
-
-In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.
-
-\begin{lem}
-\label{lem_score_pro_eq}
-  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
-  $$
-  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
-  $$  
-\end{lem}
-\begin{proof} of Lemma \ref{lem_score_pro_eq}.
-\begin{itemize}
-  \item $\implies$
-
-  $\ux{r_1} = \ux{r_2}$
-
-  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
-  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
-  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.
-
-  Apply\ Definition\ \ref{def_smoo}:\\
-  $\implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}$.
-
-  \item $\impliedby$
-
-  $\hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} $
-
-  Apply Definition \ref{def_smoo}:\\
-  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-    = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.\\
-  $\implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$.
-
-  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
-  $\implies \ux{r_1} = \ux{r_2}$.
-
-\end{itemize}
-
-\end{proof}
-
-\begin{definition}
-\label{def_cardinality}
-  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.
-
-  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
-
-  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
-\end{definition}
-
-\begin{lem}
-\label{lem_score_pro_convert}
- Given $\hexpmech(\dataobs)$, then the following property holds:
-\begin{equation*}
-\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
- \end{equation*}
-\end{lem}
-\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
-To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
-$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset \land \ux{r'} = \ux{r}\}}.$\\
-By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
-$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
-By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
-Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
-$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
-$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
-$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
-\end{proof}
-
-\subsubsection{Sliding Property of $\hexpmech$}
-
-\begin{lem}
-\label{lem_sliding}
-
-Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity.
-In Beta-binomial system, for any $r\in \candidateset$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
-\begin{equation*}
-\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
-\leq
-e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
-\end{equation*}
-\end{lem}
-
-\begin{proof} of Lemma \ref{lem_sliding}:
-
-In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
-\begin{itemize}
-  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
-  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
-\end{itemize}
-
-\todo{
-In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset$:
-\begin{itemize}
-  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
-  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
-\end{itemize}
-}
-
-Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
-\begin{itemize}
-  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
-  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
-  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}
-  \begin{itemize}
-    \item  $k \geq 0$: $\implies$
-      \begin{equation*}
-      \begin{split}
-      LHS 
-      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-      (Apply\ Definition\ \ref{def_smoo})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}                                 (Apply\ Definition\ \ref{def_smoo})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}                               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}                         (Apply \ \ux{t} = \ux{r} + k)\\
-      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-      & = RHS.
-      \end{split}
-      \end{equation*}
-
-    \item $-\ux{r} < k < 0$: $\implies$
-      \begin{equation*}
-      \begin{split}
-      LHS 
-      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-      (Apply\ Definition\ \ref{def_smoo})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
-      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
-      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-      & = RHS.
-      \end{split}
-      \end{equation*}
-
-  \end{itemize}
-
-  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
-        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
-        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
-        $\implies$
-        \begin{equation*}
-        \begin{split}
-        LHS 
-        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-        (Apply\ Definition\ \ref{def_smoo})\\
-        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
-        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
-        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
-        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
-        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
-        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
-        & = RHS.
-        \end{split}
-        \end{equation*}
-
-  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
-      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
-      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
-      $\implies$
-      \begin{equation*}
-      \begin{split}
-      LHS   
-      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-      (Apply\ Definition\ \ref{def_smoo})\\
-      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
-      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
-      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
-      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
-      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
-      & = RHS.
-      \end{split}
-      \end{equation*}
-
-  \item {\boldmath $\ux{r} = 0, \ux{r} + k = 0$}: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}
-
-        \begin{equation*}
-        \begin{split}
-        LHS 
-        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
-        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
-        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
-        & = RHS.
-        \end{split}
-        \end{equation*}
-
-\end{itemize}
-Then, the proof is finished.
-
-\end{proof}
-
-\subsubsection{Dilation Property of $\hexpmech$}
-\begin{lem}
-\label{lem_dilation}
-Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $1 - \frac{\delta'}{2} = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})$, the following \emph{dilation property} holds:
-\begin{equation*}
-\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
-\leq
-e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
-\end{equation*}
-\end{lem}
-
-\begin{proof} of Lemma \ref{lem_dilation}.
-
-\todo{
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:\\
-We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.\\
-We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.\\
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$.
-Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$.
-Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.
-}
-
-  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
-\begin{itemize}
-  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
-  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
-\end{itemize}
- Let $\ux{t} = e^{\lambda} \ux{r}$.
-
-  \begin{assert}
-  \label{cardinality_eq}
-  For any $r\in \candidateset$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
-  \end{assert}
-
-  \begin{proof} of Assertion \ref{cardinality_eq}.
-
-  The proof is given by cases:
-  \begin{itemize}
-    \item {\boldmath$\ux{r} = 0$}:
-
-        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$.\\
-        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{\dataobs}{t} = 1$.
-
-    \item {\boldmath$\ux{r} \neq 0$}:\\
-        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
-        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
-  \end{itemize}
-
-  Then, in either case, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
-
-  \end{proof}
-
-        To show:
-        \begin{equation*}
-        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
-        \leq
-        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
-        \end{equation*}
-
-        We need to show 
-        \begin{equation*}
-        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
-        \leq
-        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}},
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        By $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
-        \begin{equation*}
-         \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
-        \leq
-        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = \ux{t}},
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        By Lemma \ref{lem_score_pro_convert}, we need to show:
-        \begin{equation*}
-        \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}
-        \leq
-        e^{\frac{\epsilon}{2}} \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        By Assertion \ref{cardinality_eq}, we need to show:
-        \begin{equation*}
-        \hexpmechPr{\dataobs}{z = r}
-        \leq
-        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        By Definition \ref{def_smoo}, we need to show:
-        \begin{equation*}
-        \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
-        \leq
-        e^{\frac{\epsilon}{2}} \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}},
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        By simplification, $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$, $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$ and $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
-        \begin{equation*}
-        \ux{r}(1 - e ^ {\lambda})
-        \leq 
-        S(\dataobs),
-        \end{equation*}
-        holds with failure probability $\frac{\delta'}{2}$.
-
-        Then, prove it by two cases: $\lambda \leq 0$, and $\lambda > 0$:
-
-      \begin{itemize}
-        \item {\boldmath$\lambda < 0$}:
-
-          \begin{equation*}
-          \ux{r}(1 - e ^ {\lambda}) \leq 0 \leq S(\dataobs)
-          \end{equation*}
-          is always true.
-
-        \item {\boldmath $\lambda > 0$}:
-
-          To show:
-          \begin{equation*}
-          \ux{r}(1 - e ^ {\lambda})
-          \leq 
-          S(\dataobs),
-          \end{equation*}
-          holds with failure probability $\frac{\delta'}{2}$.
-
-          We need to show:
-          \begin{equation}
-          \label{eq_dilation_case2}
-          \ux{r}
-          \leq 
-          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
-          \end{equation}         
-          holds with failure probability $\frac{\delta'}{2}$.
-
-          Based on the accuracy property of exponential mechanism:
-          \begin{equation*}
-          \begin{split}
-          Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-          & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
-          \end{split}
-          \end{equation*}
-          we derived the accuracy bound for $\hexpmech$:
-          \begin{equation*}
-          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
-          \end{equation*}
-
-          apply this bound to Equation. \ref{eq_dilation_case2}:
-          \begin{equation*}
-          \begin{split}
-          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
-          & = |\candidateset|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
-          & = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
-          \end{split}
-          \end{equation*}
-
-          By setting $|\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
-          \begin{equation*}
-          \begin{split}
-          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
-          \end{split}
-          \end{equation*}
-          holds, i.e.,
-          \begin{equation*}
-          \ux{r}
-          \leq 
-          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
-          \end{equation*}         
-          holds with failure probability $\frac{\delta'}{2}$ is proved.
-
-          Particularly, $|\candidateset| = n + 1$ in Beta-binomial system.
-
-      \end{itemize}
-
-\end{proof}
-
-\subsubsection{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
-\begin{lem}
-\label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
-\end{lem}
-
-\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
-
-  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
-
-  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
-  \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon'} \hexpmechPr{\dataobs'}{z = r} + \delta. 
-  \end{equation*}
-
-   In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$, when considering data set $\dataobs$:
-\begin{itemize}
-  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
-  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
-\end{itemize}
- when considering data set $\dataobs'$:
-  \begin{itemize}
-    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R^{\dataobs'}_r$ contains only the correct posterior.
-    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R^{\dataobs'}_r$ contains 2 elements by the symmetry property of $\hellinger$.
-  \end{itemize}
-
-      Apply Lemma \ref{lem_score_pro_convert}:  
-      \begin{equation*}
-      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{\dataobs}{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
-      \end{equation*}
-
-      Apply Lemma \ref{lem_sliding}:
-      \begin{equation*}
-      \begin{split}
-      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
-      \end{split}
-      \end{equation*}
-
-      Apply Lemma \ref{lem_dilation}:
-      \begin{equation*}
-      \begin{split}
-      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big).
-      \end{split}
-      \end{equation*}
-
-      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
-      \begin{equation*}
-      \begin{split}
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big).
-      \end{split}
-      \end{equation*}
-
-      Apply Lemma \ref{lem_score_pro_convert}:
-      \begin{equation*}
-      \begin{split}
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big).
-      \end{split}
-      \end{equation*}
-
-      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$:
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big).
-      \end{split}
-      \end{equation*}
-
-      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big).
-       \end{split}
-      \end{equation*}
-
-      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
-      \begin{equation*}
-      \begin{split}          
-      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
-      \big( e^{\frac{\epsilon}{2}}
-      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
-      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
-      \big ) \Big)\\
-      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
-      \hexpmechPr{\dataobs'}{z = r} \\
-      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
-      \end{split}
-      \end{equation*}
-
-      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \ln \Big( \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big)$, and
-      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.
-
- Then the proof is given by cases:
-  \begin{itemize}
-    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} \neq 0$}:
-
-      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
-
-      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
-
-      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
-
-      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
-      $$
-      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
-      $$ and
-      $$
-      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
-      $$
-
-    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}:
-
-      By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
-
-      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
-
-      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 2$:
-
-      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
-      $$
-      \epsilon' = \ln \Big( 2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
-      $$ and
-      $$
-      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
-      $$
-
-    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} = 0$}:
-
-      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
-
-      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
-
-      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
-
-      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
-      $$
-      \epsilon' = \ln \Big( \frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
-      $$ and
-      $$
-      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
-      $$
-
-    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:
-
-      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
-
-      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
-
-      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 1$:
-
-      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
-      $$
-      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
-      $$ and
-      $$
-      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
-      $$
-
-  \end{itemize}
-
-      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
-      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
-      $
-      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
-      $, and
-      $
-      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
-      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
-      $\\
-
-\end{proof}
 
@@
 Under this smooth sensitivity, we define $\hexpmech$ as:
-\begin{definition}
-\label{def_smoo_2}
-$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
-{\unomalizer{\dataobs}}.
-\end{equation*}
-where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
-\end{definition}
 

### 2018-11-02 notes/SlidingDilation/main.tex
update notes and Arixv
remove the dilation property and sliding property proof and save them into notes of SlidingDilation

% \documentclass[sigconf]{acmart}
\documentclass{article}

% We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}
\usepackage{accents}

\begin{document}
\title{Proof of 2$\epsilon-$Differential Privacy}

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle

\section{Preliminaries}
\label{sec_background}

\noindent \textbf{Bayesian Inference.}

Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
\[
  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression $\Pr(\dataobs | \theta)$ denotes the
\emph{likelihood} of observing $\dataobs$ under a value of
$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distributions. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior
simplifies calculations and allows for inference to be performed in a
recursive fashion over the data.

\noindent \textbf{Beta-binomial System.}

In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
specifically, a Beta-binomial mode. We will consider the situation the underlying data is binomial distribution ($\thicksim binomial(\theta)$), where $\theta$ represents
the parameter --informally called \emph{bias}-- of a Bernoulli
distributed random variable. The
prior distribution over $\theta\in [0,1]$ is going to be a beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]

\noindent \textbf{Dirichlet-multinomial Systems.}

The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data multinomially distributed. The \emph{bias} is represented by parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the componentwise sum of vectors of reals.

\noindent \textbf{Differential Privacy.} 
\begin{definition}
\label{def_epsilon_dp}
$\epsilon-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

\end{definition}

\begin{definition}
\label{def_epsilon_delta_dp}
$(\epsilon,\delta)-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

\section{$\gamma$-Smooth Sensitivity}
\label{sec_mechs}

\begin{definition}
Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:

For any $\adj{\dataobs}{\dataobs'}$:
\begin{equation}
\label{eq_gamma_smooth}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation}

$S(\dataobs)$ is $\gamma -$smooth sensitivity.

\end{definition}

\begin{thm}
\label{thm_gamma_smooth}
Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

\end{proof}

\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{subsec_hexpmech}

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
\end{definition}

This mechanism is based on the standard exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.

\section{Privacy Analysis}

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.

\subsection{Privacy Analysis for $\hexpmech$}

The differential privacy property of $\hexpmech$ is proved based on following two lemmas: Lemma \ref{lem_sliding} and Lemma \ref{lem_dilation}.\\

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
  $$
  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$

  $\ux{r_1} = \ux{r_2}$

  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.

  Apply\ Definition\ \ref{def_smoo}:\\
  $\implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}$.

  \item $\impliedby$

  $\hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} $

  Apply Definition \ref{def_smoo}:\\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
    = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.\\
  $\implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$.

  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
  $\implies \ux{r_1} = \ux{r_2}$.

\end{itemize}

\end{proof}

\begin{definition}
\label{def_cardinality}
  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.

  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.

  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

\subsubsection{Sliding Property of $\hexpmech$}

\begin{lem}
\label{lem_sliding}

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, for any $r\in \candidateset$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

\begin{proof} of Lemma \ref{lem_sliding}:

In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

\todo{
In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
\end{itemize}
}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}
  \begin{itemize}
    \item  $k \geq 0$: $\implies$
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}                                 (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}                               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}                         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

    \item $-\ux{r} < k < 0$: $\implies$
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

  \end{itemize}

  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
        $\implies$
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
      $\implies$
      \begin{equation*}
      \begin{split}
      LHS   
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

  \item {\boldmath $\ux{r} = 0, \ux{r} + k = 0$}: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}

        \begin{equation*}
        \begin{split}
        LHS 
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

\end{itemize}
Then, the proof is finished.

\end{proof}

\subsubsection{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $1 - \frac{\delta'}{2} = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

\begin{proof} of Lemma \ref{lem_dilation}.

\todo{
The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:\\
We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.\\
We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.\\
Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$. Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.
}

  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
\end{itemize}
 Let $\ux{t} = e^{\lambda} \ux{r}$.

  \begin{assert}
  \label{cardinality_eq}
  For any $r\in \candidateset$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
  \end{assert}

  \begin{proof} of Assertion \ref{cardinality_eq}.

  The proof is given by cases:
  \begin{itemize}
    \item {\boldmath$\ux{r} = 0$}:

        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$.\\
        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{\dataobs}{t} = 1$.

    \item {\boldmath$\ux{r} \neq 0$}:\\
        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
  \end{itemize}

  Then, in either case, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.

  \end{proof}

        To show:
        \begin{equation*}
        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
        \end{equation*}

        We need to show 
        \begin{equation*}
        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        By $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
        \begin{equation*}
         \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = \ux{t}},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        By Lemma \ref{lem_score_pro_convert}, we need to show:
        \begin{equation*}
        \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}
        \leq
        e^{\frac{\epsilon}{2}} \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        By Assertion \ref{cardinality_eq}, we need to show:
        \begin{equation*}
        \hexpmechPr{\dataobs}{z = r}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        By Definition \ref{def_smoo}, we need to show:
        \begin{equation*}
        \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
        \leq
        e^{\frac{\epsilon}{2}} \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        By simplification, $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$, $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$ and $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
        \begin{equation*}
        \ux{r}(1 - e ^ {\lambda})
        \leq 
        S(\dataobs),
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

        Then, prove it by two cases: $\lambda \leq 0$, and $\lambda > 0$:

      \begin{itemize}
        \item {\boldmath$\lambda < 0$}:

          \begin{equation*}
          \ux{r}(1 - e ^ {\lambda}) \leq 0 \leq S(\dataobs)
          \end{equation*}
          is always true.

        \item {\boldmath $\lambda > 0$}:

          To show:
          \begin{equation*}
          \ux{r}(1 - e ^ {\lambda})
          \leq 
          S(\dataobs),
          \end{equation*}
          holds with failure probability $\frac{\delta'}{2}$.

          We need to show:
          \begin{equation}
          \label{eq_dilation_case2}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation}         
          holds with failure probability $\frac{\delta'}{2}$.

          Based on the accuracy property of exponential mechanism:
          \begin{equation*}
          \begin{split}
          Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
          & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
          \end{split}
          \end{equation*}
          we derived the accuracy bound for $\hexpmech$:
          \begin{equation*}
          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
          \end{equation*}

          apply this bound to Equation. \ref{eq_dilation_case2}:
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
          & = |\candidateset|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
          & = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
          \end{split}
          \end{equation*}

          By setting $|\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
          \end{split}
          \end{equation*}
          holds, i.e.,
          \begin{equation*}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$ is proved.

          Particularly, $|\candidateset| = n + 1$ in Beta-binomial system.

      \end{itemize}

\end{proof}

\subsubsection{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
\end{lem}

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.

  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon'} \hexpmechPr{\dataobs'}{z = r} + \delta. 
  \end{equation*}

   In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$, when considering data set $\dataobs$:
\begin{itemize}
  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
\end{itemize}
 when considering data set $\dataobs'$:
  \begin{itemize}
    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R^{\dataobs'}_r$ contains only the correct posterior.
    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R^{\dataobs'}_r$ contains 2 elements by the symmetry property of $\hellinger$.
  \end{itemize}

      Apply Lemma \ref{lem_score_pro_convert}:  
      \begin{equation*}
      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{\dataobs}{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
      \end{equation*}

      Apply Lemma \ref{lem_sliding}:
      \begin{equation*}
      \begin{split}
      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
      \end{split}
      \end{equation*}

      Apply Lemma \ref{lem_dilation}:
      \begin{equation*}
      \begin{split}
      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Lemma \ref{lem_score_pro_convert}:
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$:
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
       \end{split}
      \end{equation*}

      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big)\\
      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs'}{z = r} \\
      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
      \end{split}
      \end{equation*}

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \ln \Big( \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big)$, and
      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.

 Then the proof is given by cases:
  \begin{itemize}
    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} \neq 0$}:

      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.

      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.

      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}:

      By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.

      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.

      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 2$:

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( 2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
      $$

    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} = 0$}:

      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.

      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.

      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( \frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:

      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.

      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.

      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 1$:

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

  \end{itemize}

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
      $
      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
      $, and
      $
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
      $\\

\end{proof}

\bibliographystyle{plain}
\bibliography{bayesian.bib}

\end{document}

### 2018-11-02 notes/fullproof/main.tex
update notes and Arixv
remove the dilation property and sliding property proof and save them into notes of SlidingDilation

@@
 \author[*]{Marco Gaboardi}
-\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
-\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
+\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
+\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
 \date{}
 \maketitle
+{\small \tableofcontents}
+
+\newpage
+\begin{abstract} Bayesian inference is a statistical method which
+allows one to derive a \emph{posterior} distribution,
+starting from a \emph{prior} distribution and observed data. Several
+approaches have been explored in order to make this process differentially
+private. For example, \cite{dimitrakakis2014robust}, and
+\cite{wang2015privacy} proved that, under specific conditions, sampling from
+the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
+designed differentially private mechanisms that output a
+representation of the full posterior distribution.
+
+When the output of a differentially private mechanism is a probability
+distribution, accuracy is naturally measured by means of
+\emph{probabilistic distances} measuring how far this distribution is
+from the original one. Some classical examples are total variation distance,
+Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
+
+In this work, we design a mechanism for
+bayesian inference exploring the idea of calibrating noise using the
+same probabilistic distance we want to measure accuracy with. 
+We focus on two discrete models, the Beta-Binomial and the
+Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
+Our mechanism can be understood as a version of  the exponential mechanism
+where the noise is calibrated to the smooth sensitivity of the
+utility function, rather than to its global sensitivity. In our
+setting, the utility function is the probability distance we want to
+use to measure accuracy. To show the usefulness of this mechanism we
+show an experimental analysis comparing it with mechanisms based on
+the Laplace mechanism.
+\end{abstract}
+ % TODO: replace with your keywords
+
+\section{Introduction}
+\label{sec_intro}
+Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on.
+In order to provide a better service, large of data are collected from users for analysis.
+As a consequence, the data privacy came to be a critical issue.
+Sensitivity information in data can be revealed through the analysis results.
+The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.
+
+Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms.
+They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy.
+But they are not giving better accuracy than the differential privacy mechanism itself.
+Here, we are proposing mechanism with better accuracy.
+
+Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
+Publishing the posterior distribution inferred from a sensitive dataset can
+leak information about the individuals in the dataset.
+In order to guarantee differential privacy and to protect the
+individuals' data we can add noise to the posterior before releasing it.
+The amount of the noise that we need to introduced
+depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
+small changes in the data set. 
+Sensitivity can be computed in many different ways based on which metric space
+we consider on the output set of the mechanism. In the literature on private Bayesian
+inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
+respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
+A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
+A re-loved question is that of how to measure accuracy. Again,
+this can be answered in different ways based on the metric imposed on the output space, and yet again
+only in few works in literature (e.g. \cite{zhang2016differential})
+distances between probability measures have been used for these purposes.
+
+The question that this work aims at answering is whether
+an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
+the numeric parameters of the distributions. 
+We will see that in some cases this can happen.
+
+\noindent \textbf{Main contributions.}
+\begin{itemize}
+  \item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
+
+  \item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
+Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
+2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
+
+  \item A full proof on applying exponential mechanism to the smooth sensitivity is $(\epsilon, \delta)-$differential privacy is given in paper.
+
+  \item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
+\end{itemize}
+
+\noindent \textbf{Related Work.}
+
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
+
+In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+\cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
+3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
+The third topic where our work focus on is still very new.
+
 \section{Preliminaries}
@@
 \begin{equation*}
-\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
+\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
 \end{equation*} 
-vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
 \end{definition}
@@
 the Bayesian Inference process will produce an element from $\candidateset$
-that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
+that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
 parametrize the result by the prior, which from now on we consider
 fixed and we denote it by $\bprior$.
+
+\subsection{Baseline Mechanisms}
+\label{subsec_baselines}
+Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
+
+\subsubsection{Exponential Mechanism}
+Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+\begin{equation*}
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
+\end{equation*}
+where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
+\begin{equation*}
+GS = 
+\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
+|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
+\end{equation*}
+
+Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+
+\subsubsection{Exponential Mechanism with Local Sensitivity}
+\label{subsec_emls}
+% \subsubsection{Mechanism Set up}
+Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
+This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
+\begin{equation*}
+\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
+{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
+\end{equation*}
+
+where $LS(\dataobs)$ is the local sensitivity calculated by:
+
+\begin{equation*}
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
+\end{equation*}
+
+The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
+
+\subsubsection{Laplace Mechanism}
+ Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \] 
+ where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+ where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
+$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
+
+ Then release it as the private posterior distribution.
+
+ The sensitivity used in this baseline mechanism is:
+ \[
+ \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
+ \]
+ which is proportional to the dimensionality.
+
+\subsubsection{Improved Laplace Mechanism}
+
+ Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
+Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+
+ Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \]
+ where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
+
+Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
 
@@
 \underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
-{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
+{\nomalizer{\dataobs}}.
 \end{equation*}
@@
 \end{equation}
-where $d$ is the Hamming distance between two datasets, and $\beta =
-\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
+where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
 \end{definition}
 
-This mechanism is based on the basic exponential mechanism
+This mechanism is based on the standard exponential mechanism
 \cite{talwar}, with $\candidateset$ as the range and
@@
 
-By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
-(or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)
+% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
 
@@
 
-\noindent \textbf{Sliding Property of $\hexpmech$}
+In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.
+
+\begin{lem}
+\label{lem_score_pro_eq}
+  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
+  $$
+  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
+  $$  
+\end{lem}
+\begin{proof} of Lemma \ref{lem_score_pro_eq}.
+\begin{itemize}
+  \item $\implies$
+
+  $\ux{r_1} = \ux{r_2}$
+
+  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
+  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
+  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.
+
+  Apply\ Definition\ \ref{def_smoo}:\\
+  $\implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}$.
+
+  \item $\impliedby$
+
+  $\hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} $
+
+  Apply Definition \ref{def_smoo}:\\
+  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+    = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.\\
+  $\implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$.
+
+  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
+  $\implies \ux{r_1} = \ux{r_2}$.
+
+\end{itemize}
+
+\end{proof}
+
+\begin{definition}
+\label{def_cardinality}
+  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.
+
+  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
+
+  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
+\end{definition}
+
+\begin{lem}
+\label{lem_score_pro_convert}
+ Given $\hexpmech(\dataobs)$, then the following property holds:
+\begin{equation*}
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
+ \end{equation*}
+\end{lem}
+\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
+To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
+$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset \land \ux{r'} = \ux{r}\}}.$\\
+By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
+$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
+By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
+Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
+$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
+$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
+$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
+\end{proof}
+
+\subsubsection{Sliding Property of $\hexpmech$}
+
 \begin{lem}
 \label{lem_sliding}
-Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
+
+Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity.
+In Beta-binomial system, for any $r\in \candidateset$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
 \begin{equation*}
-\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
 \leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
+e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
 \end{equation*}
-
 \end{lem}
 
-\begin{proof}
+\begin{proof} of Lemma \ref{lem_sliding}:
 
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
- $r\in\candidateset$ and the probability 
- $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
- \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.
-In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.
+In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
+\begin{itemize}
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
+\end{itemize}
 
- \begin{thm}
- \label{thm_hellinegr_equality_beta}
- for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
-  $$
-  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2, \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
-  $$
- \end{thm}
+\todo{
+In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset$:
+\begin{itemize}
+  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
+  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
+\end{itemize}
+}
 
-\begin{thm}
- \label{thm_hellinegr_equality_dirichlet}
- In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
-  $$
-  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
-  $$
-  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
- \end{thm}
-
- \begin{thm}
- \label{thm_candidate_divide}
- There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either
- $$
- = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
- $$ or 
- $$
- =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
- $$
- \end{thm}
- \begin{proof} of Theorem \ref{thm_candidate_divide}.
-
- Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e.
-$u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
-
- From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
- \end{proof}
-
-\begin{thm}
- \label{thm_candidate_divide_dirichlet}
- In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
- $$
- \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
- = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
- $$ 
- and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
- \end{thm}
-
- \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
-
- Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
- $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
- $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
- Then, there are $\frac{k!
-k!}{|a_1|!
-|a_2|!
-\cdots |a_{k_a}|!
-\cdot |b_1|!
-|b_2|!
-\cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
- \end{proof}
-
- In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$.
-The proofs are given by parts:
-
+Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
 \begin{itemize}
- 	\item for $r \in R_1$:
-
-		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
+  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
+  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
+  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}
+  \begin{itemize}
+    \item  $k \geq 0$: $\implies$
       \begin{equation*}
@@
       LHS 
-		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
-		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
-		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
+      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}                                 (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}                               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}                         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
       \end{split}
@@
 
-		By bounding the $\delta' \geq -S(\dataobs)$, we can get:
+    \item $-\ux{r} < k < 0$: $\implies$
+      \begin{equation*}
+      \begin{split}
+      LHS 
+      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
+      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \end{itemize}
+
+  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
+        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
+        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
+        $\implies$
+        \begin{equation*}
+        \begin{split}
+        LHS 
+        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ Definition\ \ref{def_smoo})\\
+        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
+        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & = RHS.
+        \end{split}
+        \end{equation*}
+
+  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
+      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
+      $\implies$
+      \begin{equation*}
+      \begin{split}
+      LHS   
+      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ Definition\ \ref{def_smoo})\\
+      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
+      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
+      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
+      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
+      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
+      & = RHS.
+      \end{split}
+      \end{equation*}
+
+  \item {\boldmath $\ux{r} = 0, \ux{r} + k = 0$}: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}
 
@@
         \begin{split}
-		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
-		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
-		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
+        LHS 
+        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
+        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
+        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
+        & = RHS.
         \end{split}
         \end{equation*}
-	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
+
 \end{itemize}
-
-The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.
+Then, the proof is finished.
 
@@
 
-\noindent \textbf{Dilation Property of $\hexpmech$}
+\subsubsection{Dilation Property of $\hexpmech$}
 \begin{lem}
 \label{lem_dilation}
-for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:
-
+Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $1 - \frac{\delta'}{2} = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})$, the following \emph{dilation property} holds:
 \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
+\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
 \leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
+e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
 \end{equation*}
-where the sensitivity in mechanism is still smooth sensitivity as above.
-
-More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
 \end{lem}
 
-\begin{proof}
-Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$.
-It is enough to proof under just one partition.
-Without loss of generalization, we take $R_1$.
+\begin{proof} of Lemma \ref{lem_dilation}.
 
-The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
-
-We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.
-
+\todo{
+The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:\\
+We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.\\
 We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.
-
+In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.\\
 Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$.
@@
 The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\
+Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.
+}
 
-\textbf{Detail proof:}
+  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
+\begin{itemize}
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
+\end{itemize}
+ Let $\ux{t} = e^{\lambda} \ux{r}$.
+
+  \begin{assert}
+  \label{cardinality_eq}
+  For any $r\in \candidateset$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
+  \end{assert}
+
+  \begin{proof} of Assertion \ref{cardinality_eq}.
+
+  The proof is given by cases:
+  \begin{itemize}
+    \item {\boldmath$\ux{r} = 0$}:
+
+        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} = 0$, $\cardinality{\dataobs}{t} = 1$.
+
+    \item {\boldmath$\ux{r} \neq 0$}:\\
+        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
+        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
+  \end{itemize}
+
+  Then, in either case, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
+
+  \end{proof}
+
         To show:
         \begin{equation*}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
+        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
         \leq
-	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
         \end{equation*}
-	for $z \in R_1$.
 
-	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.
+        We need to show 
+        \begin{equation*}
+        \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
+        \leq
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
 
-	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
-	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
+        By $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
+        \begin{equation*}
+         \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
+        \leq
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = \ux{t}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By Lemma \ref{lem_score_pro_convert}, we need to show:
+        \begin{equation*}
+        \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}
+        \leq
+        e^{\frac{\epsilon}{2}} \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By Assertion \ref{cardinality_eq}, we need to show:
+        \begin{equation*}
+        \hexpmechPr{\dataobs}{z = r}
+        \leq
+        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By Definition \ref{def_smoo}, we need to show:
+        \begin{equation*}
+        \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}
+        \leq
+        e^{\frac{\epsilon}{2}} \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}},
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        By simplification, $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$, $\ux{t} = \hellinger(\bysinfer(\dataobs),t)$ and $\ux{t} = e^{\lambda} \ux{r}$, we need to show:
+        \begin{equation*}
+        \ux{r}(1 - e ^ {\lambda})
+        \leq 
+        S(\dataobs),
+        \end{equation*}
+        holds with failure probability $\frac{\delta'}{2}$.
+
+        Then, prove it by two cases: $\lambda \leq 0$, and $\lambda > 0$:
 
       \begin{itemize}
-	\item $\lambda < 0$
+        \item {\boldmath$\lambda < 0$}:
 
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
           \begin{equation*}
-		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
+          \ux{r}(1 - e ^ {\lambda}) \leq 0 \leq S(\dataobs)
           \end{equation*}
-		is always true when $\lambda < 0$
-	\item $\lambda > 0$
+          is always true.
 
-		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
+        \item {\boldmath $\lambda > 0$}:
+
+          To show:
+          \begin{equation*}
+          \ux{r}(1 - e ^ {\lambda})
+          \leq 
+          S(\dataobs),
+          \end{equation*}
+          holds with failure probability $\frac{\delta'}{2}$.
+
+          We need to show:
           \begin{equation}
           \label{eq_dilation_case2}
-		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
+          \ux{r}
+          \leq 
+          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
           \end{equation}         
+          holds with failure probability $\frac{\delta'}{2}$.
 
@@
           \begin{equation*}
+          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
+          \end{equation*}
+
+          apply this bound to Equation. \ref{eq_dilation_case2}:
+          \begin{equation*}
           \begin{split}
-		Pr[u(\hexpmech(\dataobs)) \leq c] 
-		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
+          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
+          & = |\candidateset|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
+          & = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
           \end{split}
@@
 
-		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
+          By setting $|\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
           \begin{equation*}
           \begin{split}
-		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
-		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
-		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
+          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
           \end{split}
           \end{equation*}
+          holds, i.e.,
+          \begin{equation*}
+          \ux{r}
+          \leq 
+          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
+          \end{equation*}         
+          holds with failure probability $\frac{\delta'}{2}$ is proved.
 
-		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.
-
-		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.
+          Particularly, $|\candidateset| = n + 1$ in Beta-binomial system.
 
@@
 
-\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
+\subsubsection{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
 \begin{lem}
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
+$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
 \end{lem}
 
-\begin{proof}
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
 
-For all $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$, we need to show that:
+  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
+
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
   \begin{equation*}
-\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
+  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon'} \hexpmechPr{\dataobs'}{z = r} + \delta. 
   \end{equation*}
 
-Let partition $R_1, R_2 \subset \candidateset$ the same as above. Then we prove by part:
+   In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$, when considering data set $\dataobs$:
 \begin{itemize}
-	\item for $r \in R_1$:
+  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$.  $R^{\dataobs}_r$ contains only the correct posterior.
+  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R^{\dataobs}_r$ contains 2 elements by the symmetry property of $\hellinger$.
+\end{itemize}
+ when considering data set $\dataobs'$:
+  \begin{itemize}
+    \item[*] $\cardinality{\dataobs'}{r} = 1$, $\uxadj{r} = 0$,  $R^{\dataobs'}_r$ contains only the correct posterior.
+    \item[*] $\cardinality{\dataobs'}{r} = 2$, $\uxadj{r} \neq 0$. $R^{\dataobs'}_r$ contains 2 elements by the symmetry property of $\hellinger$.
+  \end{itemize}
 
-	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
-Then,
+      Apply Lemma \ref{lem_score_pro_convert}:  
+      \begin{equation*}
+      \hexpmechPr{\dataobs}{z = r} = \frac{1}{\cardinality{\dataobs}{r}} \hexpmechPr{\dataobs}{\ux{z} = \ux{r}}.
+      \end{equation*}
+
+      Apply Lemma \ref{lem_sliding}:
+      \begin{equation*}
+      \begin{split}
+      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + (\uxadj{r} - \ux{r})} \Big)\\
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = \uxadj{r} } \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply Lemma \ref{lem_dilation}:
+      \begin{equation*}
+      \begin{split}
+      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply Lemma \ref{lem_score_pro_convert}:
+      \begin{equation*}
+      \begin{split}
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$:
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+      \end{split}
+      \end{equation*}
+
+      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big).
+       \end{split}
+      \end{equation*}
+
+      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
+      \begin{equation*}
+      \begin{split}          
+      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
+      \big( e^{\frac{\epsilon}{2}}
+      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
+      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
+      \big ) \Big)\\
+      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
+      \hexpmechPr{\dataobs'}{z = r} \\
+      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
+      \end{split}
+      \end{equation*}
+
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \ln \Big( \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big)$, and
+      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.
+
+ Then the proof is given by cases:
+  \begin{itemize}
+    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} \neq 0$}:
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
+
+      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
+      $$ and
+      $$
+      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}:
+
+      By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} \neq 0 \implies \ux{t} \neq 0 \implies \cardinality{\dataobs}{t} = 2$.
+
+      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln \Big( 2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
+      $$ and
+      $$
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} \neq 0$, $\uxadj{r} = 0$}:
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
+
+      Apply  $\cardinality{\dataobs}{r} = 2$ and  $\cardinality{\dataobs}{t} = 2$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln \Big( \frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
+      $$ and
+      $$
+      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      $$
+
+    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:
+
+      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.
+
+      Apply $\uxadj{r} = 0 \implies \ux{t} = 0 \implies \cardinality{\dataobs}{t} = 1$.
+
+      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 1$:
+
+      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
+      $$
+      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
+      $$ and
+      $$
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
+      $$
+
+  \end{itemize}
+
+      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
+      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
+      $
+      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
+      $, and
+      $
+      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
+      \Big( 1 - |\candidateset|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
+      $\\
+
+\end{proof}
+
+\subsubsection{$\gamma$-Smooth Sensitivity}
+\label{sec_mechs}
+
+\begin{definition}
+Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:
+
+For any $\adj{\dataobs}{\dataobs'}$:
+\begin{equation}
+\label{eq_gamma_smooth}
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
+\end{equation}
+
+$S(\dataobs)$ is $\gamma -$smooth sensitivity.
+
+\end{definition}
+
+\begin{thm}
+\label{thm_gamma_smooth}
+Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
+\begin{equation}
+  \label{eq_smooth}
+   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
+\end{equation}
+where $d$ is the Hamming distance between two data sets.
+\end{thm}
+
+\begin{proof}
+of Theorem. \ref{thm_gamma_smooth}.
+
+For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
+
+By Equation (\ref{eq_smooth}):
+\begin{equation*}
+\begin{split}
+S(\dataobs) 
+& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
+\frac{1}{S(\dataobs)} 
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
+\end{split}
+\end{equation*}
+
+Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
 
@@
 \begin{split}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\\
-	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\\
-	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(\dataobs',z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
+& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
+& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
+& = \gamma + \frac{1}{S(\dataobs')}
 \end{split}
 \end{equation*}
-	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
-The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
+$\implies$
+\begin{equation*}
+\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
+\end{equation*}
 
-	\item for $r \in R_2$:
+\end{proof}
 
-	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(y,z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$.
-Then,
+Under this smooth sensitivity, we define $\hexpmech$ as:
+\begin{definition}
+\label{def_smoo_2}
+$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+\begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
+{\unomalizer{\dataobs}}.
+\end{equation*}
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
+\end{definition}
+
+\subsubsection{$\hexpmech$ $2\epsilon-$Differential Privacy Proof}
+
+\begin{lem}
+\label{lem_hexpmech_privacy}
+$\hexpmech$ is $2\epsilon$-differential privacy.
+\end{lem}
+
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
+
+  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
+
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
+  \begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
+  \end{equation*}
+
+  By definition \ref{def_smoo_2}:
+  \begin{equation*}
+  \begin{split}
+  \hexpmechPr{\dataobs}{z = r} 
+  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}} \\
+  & = \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot exp\big( \frac{\epsilon}{2} \big) \\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)\\
+  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  exp
+  \big(
+  \frac{\epsilon}{2} \cdot \gamma
+  \big)\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  \end{split}
+  \end{equation*}
+
+  Doing the same transformation in the denominator:
+  \begin{equation*}
+  \begin{split}
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon\cdot(\ux{r'})}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
+  $\frac{- \epsilon}{2}
+  (\frac{1}{S(\dataobs)}-
+  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
+  \big)
+  }\\
+  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \big)
+  }\\
+  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
+  \end{split}
+  \end{equation*}
+
+  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
+\end{proof}
+
+\section{Accuracy Analysis}
+
+\subsection{Accuracy Bound for Baseline Mechanisms}
+
+\subsubsection{Accuracy Bound for Exponential Mechanism}
+\label{subsec_accuracy_global}
+The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
+\begin{equation*}
+Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+     \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
+\end{equation*}
+where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
+
+\subsubsection{Accuracy Bound for Laplace Mechanism}
+\label{subsec_accuracy_lap}
+Accuracy bound for Laplace mechanism is provided by its probability density function:
+\begin{equation*}
+Pr[|Y| \geq t] = e^{- \frac{t}{b}},
+\end{equation*}
+where $Y \thicksim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
+
+After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
+\[
+Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
+\]
+
+\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
+\label{subsec_accuracy_lap}
+Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
+\[
+Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
+\]
+
+\subsection{Accuracy Bound for $\hexpmech$}
+\label{subsec_accuracy_smoo}
+We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
+
+First is the tight bound with very accurate calculation.
+\begin{equation*}
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} = \sum\limits_{\{z | \hellinger(\bysinfer(\dataobs), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), z)}{S(\dataobs)}}}{NL_x}.
+\end{equation*}
+
+In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
+
+\begin{equation*}
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{NL_x}.
+\end{equation*}
+
+In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
+
+\begin{equation*}
+\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{N(n)},
+\end{equation*}
+where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
+
+Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
 
@@
 \begin{split}
-	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
-	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
-	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
-	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
-	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
+Pr[u(\hexpmech(\dataobs)) \leq c] 
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
 \end{split}
 \end{equation*}
-	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.
+which has been used in the dilation property proof.
 
-	The first inequality holds by the sliding property, since the $U_1 \geq -S(\dataobs)$.
-The second inequality holds by the dilation property, since $\frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})}$.
-\end{itemize}
+\section{Experimental Evaluations}
+\label{sec_experiment}
 
-Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
+\subsection{Efficiency Evaluation}
+\label{subsec_effi}
+The formula for computing the local sensitivity presented in Sec.
+\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
+can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
+by applying the distance triangle property.
 
-Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
-\end{proof}
+Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
+\begin{equation*}
+\begin{split}
+LS(\dataobs) 
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+\end{split}
+\end{equation*}
+
+This equation is validated by an experimental result shown in Fig.
+\ref{fig_efficiency}.
+We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
+It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.8\textwidth]{efficiency}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\label{fig_efficiency}
+\end{figure}
+
+\subsection{Accuracy Evaluation}
+\subsubsection{Theoretical Results}
+
+\begin{figure}
+\begin{center}
+\centering
+  \subfigure[2 dimensions with data size $600$]{
+    \includegraphics[width=0.4\textwidth]{theory_2d.eps}
+  \label{subfig_theory_2d}
+  }
+  \subfigure[3 dimensions with data size $600$]{
+    \includegraphics[width=0.4\textwidth]{theory_3d.eps}
+  \label{subfig_theory_3d}
+  }
+\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
+\label{fig_theory}
+\end{center}
+\end{figure}
+In Fig.
+\ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms.
+We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
+the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.
+
+In Fig.
+\ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line).
+This means $\hexpmech$ can produce good results with larger probability than baseline mechanism.
+However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$.
+It outperforms $\hexpmech$.
+
+\subsubsection{Experimental Results}
+\label{subsec_vs_variables}
+
+In this section, we evaluate the accuracy of the mechanisms defined in
+Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
+data variance, prior distribution, and some combinations thereof.
+Every plot is an average over 1000 runs. In all the experiments we set
+$\epsilon = 1.0$, and $\delta = 10^{-8}$.
+
+\noindent In the following some of the plots show
+mean error as a function of the datasize while one
+is a whiskers-plot where the y-axis shows the average
+accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
+different balanced priors used. The boxes extend from the lower to the upper quartile values
+of the data, with a line at the median. A notch on the box around the
+median is also drawn to give a rough guide to the significance of
+difference of medians; The whiskers extend from the box to show the
+range of the data. A blue box in the plots represents our newly
+designed exponential mechanism's behavior-- where the sensitivity is calibrated
+w.r.t Hellinger distance-- while the yellow box next to
+it represents the performance of a variation of the basic Laplace
+mechanism presented in Section (\ref{subsec_baselines}) with the same
+settings: that is $\epsilon, \delta$, data, prior. The variation
+considered performs a postprocessing on the released parameters so
+that they are consistent. For instance when the sum of the noised
+parameters is greater than $n$ we will truncate them so that they sum
+up to $n$.
+
+\paragraph{Increasing data size with balanced datasets}
+\label{subsubsec_vs_datasize}
+
+\begin{figure}
+\begin{center}
+\centering
+    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
+\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\label{fig_vs_datasize_2d}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\centering
+\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+{
+        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
+        \label{fig_vs_datasize_3d}
+}
+\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+{
+     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
+\label{fig_vs_datasize_4d}
+}
+\end{center}
+\end{figure}
+
+% \begin{figure}[ht]
+% \begin{center}
+% \centering
+
+% \end{center}
+% \end{figure}
+
+In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
+of observations. The results show that when the data size increases, the average errors of
+$\hexpmech$, Laplace mechanism and decrease. For small datasets,
+i.e with size less $300$ in the case of Beta-Binomial models,
+both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
+But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
+we considered data sets of the order of 15 thousands elements,
+the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
+Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
+
+\paragraph{Fixed dataset varying balanced priors}
+\label{subsubsec_vs_prior}
+In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ .
+We studied the accuracy under different priors, where the priors considered  are also balanced.
+Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{sampling_prior.eps}
+\caption{Observed data set is: $(50,50)$, varying balanced priors}
+\label{fig_vs_prior}
+\end{figure}
+
+\subsection{Privacy Evaluation}
+\label{subsec_experiment_privacy}
+In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
+The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
+\ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
+We calculate the concrete privacy value in following ways wrt.
+the data size, and obtain plots in Fig.
+\ref{fig_privacy}.
+
+\begin{figure}
+\begin{center}
+\centering
+  \subfigure[data size range from 50 to 100]{
+    \includegraphics[width=0.4\textwidth]{global_epsilon_size50to100.eps}}
+  \subfigure[data size range from 100 to 200]{
+    \includegraphics[width=0.4\textwidth]{global_epsilon_size100to200.eps}} 
+  % \subfigure[data size range from 200 to 500]{
+  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
+  % \subfigure[data size range from 500 to 1000]{
+  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
+\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
+\label{fig_privacy}
+\end{center}
+\end{figure}
+
+$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
+That is to say, we achieved a higher privacy level than expected.
+In next step, we are going to improve the accuracy using this property.
+
+\section{Conclusion and Future Work}
+From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:
+
+\begin{enumerate}
+  \item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
+    \item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
+\end{enumerate}
+
+These results although very motivating, are still not enough for real world applications. Hence, we will continue our work in the follwoing directions:
+\begin{enumerate}
+  \item  For now, we just have a intuitive idea on the accuracy
+behavior of our mechanisms, and not a precise formula or bound on
+it. When do our mechanisms perform better than the baseline mechanism
+and when they don't? How much influence will elements in Section
+\ref{sec_experiment} have on the accuracy? Are there any other
+important factors we missed? These are all questions w.r.t. the
+accuracy that we are going to explore next, and in a more principled
+and formal way.
+\item  Theorem \ref{lem_hexpmech_privacy} provides an upper bound on the
+privacy loss for $\hexpmech$ and $\hexpmechd$ but not necessarily a
+tight one. Indeed, experiments have shown that the actual privacy loss
+in the experiments can be smaller than $\epsilon$. This means that we
+could improve accuracy, by adding less noise -- that is noise
+proportional to a higher value of $\epsilon$-- but still achieve
+$(\epsilon, \delta)$-dp.
+\item The choice of the Hellinger distance might seem quite
+ad-hoc. Hence, it is worth exploring other distances over
+distributions. An interesting class of probability metrics is the
+family of $f$-divergences \cite{CIT-004}.
+\end{enumerate}
 

### 2018-11-02 Arxiv/main.tex
update proof
revise the parameter 2 in formula into 4 and achieve \epsilon dp

@@
 
-\begin{definition}
-\label{def_smoo_2}
-$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
-{\unomalizer{\dataobs}}.
-\end{equation*}
-where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
-\end{definition}
-
-This mechanism is based on the standard exponential mechanism
-\cite{talwar}, with $\candidateset$ as the range and
-$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
-that in this mechanism we don't calibrate the noise w.r.t. to the
-global sensitivity of the scoring function but w.r.t. to the smooth
-sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
-$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
-sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.
-
-This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
-\[
-  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
-\]
-and by replacing the $\candidateset$ with set of posterior Dirichlet
-distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
-over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
-will denote by $\hexpmechd$ the mechanism for the
-Dirichlet-multinomial system.
-
 \subsubsection{$\gamma$-Smooth Sensitivity}
@@
 
-Under this smooth sensitivity, we define $\hexpmech$ as:
-
-\subsubsection{$\hexpmech$ $2\epsilon-$Differential Privacy Proof}
+\subsubsection{$\hexpmech$ Proposition}
+
+\begin{definition}
+\label{def_smoo_2}
+$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+\begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
+{\unomalizer{\dataobs}}.
+\end{equation*}
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
+\end{definition}
+
+This mechanism is based on the standard exponential mechanism
+\cite{talwar}, with $\candidateset$ as the range and
+$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
+that in this mechanism we don't calibrate the noise w.r.t. to the
+global sensitivity of the scoring function but w.r.t. to the smooth
+sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
+$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
+sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.
+
+This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+\[
+  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+\]
+and by replacing the $\candidateset$ with set of posterior Dirichlet
+distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
+over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
+will denote by $\hexpmechd$ the mechanism for the
+Dirichlet-multinomial system.
+
+\section{Privacy Analysis}
+
+\subsection{Privacy Analysis for Baseline Mechanisms}
+In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
+The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
+
+\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
 
@@
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $2\epsilon$-differential privacy.
+$\hexpmech$ is $\epsilon$-differential privacy.
 \end{lem}
@@
   \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
+  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
   \end{equation*}
@@
   \hexpmechPr{\dataobs}{z = r} 
-  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
   & = \frac {exp\big(
-  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
+  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
   \big)}
@@
   & = \frac {exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
   \big)}
   {\unomalizer{\dataobs}}
-  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
+  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
   \end{split}
@@
   & \leq \frac {exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
   \big)}
   {\unomalizer{\dataobs}}
-  \cdot exp\big( \frac{\epsilon}{2} \big) \\
-  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
+  \cdot exp\big( \frac{\epsilon}{4} \big) \\
+  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
   \big)
@@
   \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
-  \big)
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)\\
-  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
   \big)\\
@@
   \begin{split}
-  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
   \big)\\
@@
   \big(
-  \frac{\epsilon}{2} \cdot \gamma
+  \frac{\epsilon}{4} \cdot \gamma
   \big)\\
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \begin{split}
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
   \big)
   }\\
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
   \big)
@@
 
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon}{2}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{4}
   \big)
   }\\
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon}{2}
-  \big)
-  exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
-  \big)
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
+  \big)
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
   \big)
   }\\
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{- \epsilon\cdot(\ux{r'})}{2}
+  \frac{- \epsilon\cdot(\ux{r'})}{4}
   (\frac{1}{S(\dataobs)}
@@
 
-  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon}{2}
-  \big)
-  exp
-  \big(
-  \frac{- \epsilon}{2}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{4}
   (\frac{1}{S(\dataobs)}
@@
   Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
-  $\frac{- \epsilon}{2}
+  $\frac{- \epsilon}{4}
   (\frac{1}{S(\dataobs)}-
-  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
-  \begin{equation*}
-  \begin{split}
-  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
+  \begin{equation*}
+  \begin{split}
+  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon}{2}
-  \big)
-  exp
-  \big(
-  \frac{- \epsilon}{2} \cdot \gamma
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  exp
+  \big(
+  \frac{- \epsilon}{4} \cdot \gamma
   \big)
   }\\
-  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
-  \big)
-  exp 
-  \big(
-  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)
+  exp 
+  \big(
+  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
   \big)
   }\\
-  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
-  \frac {
-  exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
+  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
+  \frac {
+  exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
   \big)
@@
   \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4\cdot S(\dataobs')}
   \big)
   }\\
-  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
-  \end{split}
-  \end{equation*}
-
-  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
+  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
+  \end{split}
+  \end{equation*}
+
+  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.
 \end{proof}

### 2018-11-02 notes/SlidingDilation/main.tex
update dilation and sliding property proof

@@
 \begin{document}
-\title{Proof of 2$\epsilon-$Differential Privacy}
+\title{Proof of Sliding and Dilation Property}
 
@@
 \end{definition}
-
-\section{$\gamma$-Smooth Sensitivity}
-\label{sec_mechs}
-
-\begin{definition}
-Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:
-
-For any $\adj{\dataobs}{\dataobs'}$:
-\begin{equation}
-\label{eq_gamma_smooth}
-\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
-\end{equation}
-
-$S(\dataobs)$ is $\gamma -$smooth sensitivity.
-
-\end{definition}
-
-\begin{thm}
-\label{thm_gamma_smooth}
-Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
-\begin{equation}
-  \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
-\end{equation}
-where $d$ is the Hamming distance between two data sets.
-\end{thm}
-
-\begin{proof}
-of Theorem. \ref{thm_gamma_smooth}.
-
-For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
-
-By Equation (\ref{eq_smooth}):
-\begin{equation*}
-\begin{split}
-S(\dataobs) 
-& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
-\frac{1}{S(\dataobs)} 
-& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
-\end{split}
-\end{equation*}
-
-Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
-
-\begin{equation*}
-\begin{split}
-& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
-& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
-& = \gamma + \frac{1}{S(\dataobs')}
-\end{split}
-\end{equation*}
-$\implies$
-\begin{equation*}
-\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
-\end{equation*}
-
-\end{proof}
 

### 2018-11-02 Arxiv/main.tex
Update Arxiv/main.tex
fix sensitivity proof
Update Arxiv/main.tex
fix typos

@@
 \maketitle
-{\small \tableofcontents}
+{\footnotesize \tableofcontents}
 
@@
 S(\dataobs) 
-& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
+& = \max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \}\\
 \frac{1}{S(\dataobs)} 
-& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
+& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
 \end{split}
@@
 \begin{split}
-& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
-& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
+& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
+& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
+\}\\
+& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
+\}\\
 & = \gamma + \frac{1}{S(\dataobs')}
@@
 
-\subsubsection{$\hexpmech$ Proposition}
+\subsection{$\hexpmech$ Proposition}
 
@@
 distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
+in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
@@
 
-\subsection{Privacy Analysis for Baseline Mechanisms}
-In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
+% \subsection{Privacy Analysis for Baseline Mechanisms}
+% In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
 The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
 
-\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
+\subsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
 

### 2018-11-12 Arxiv/main.tex
Update Arxiv/main.tex
fix typos
update figures

@@
 \]
-where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
+where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
 Notice that $\candidateset$ has $n + 1$ elements, and
@@
 
-\subsection{$\hexpmech$ Proposition}
+\subsubsection{$\hexpmech$ Proposition}
 
@@
   Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.
+
 \end{proof}
@@
 \begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t}{b}},
-\end{equation*}
-where $Y \thicksim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.
+Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}},
+\end{equation*}
+where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.
 
@@
 \[
-Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
-\]
+Pr[\lfloor Y \rfloor = t] 
+= Pr[ t-1 \leq Y < t] 
+= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
+\]
+
+Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism.
+By applying the accuracy bound into Hellinger distance in our case:
+$$
+\begin{array}{rcl}
+& Pr[\hlg(\bysinfer(\dataobs), r_L ) = \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)] 
+=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+\end{array}
+$$
+where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor$.\\
+By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
+\begin{itemize}
+\item[\textbf{case 1:}] \textbf{t is even}\\
+
+\item[\textbf{case 2:}] \textbf{t is odd}
+\end{itemize}
 
@@
 \centering
-  \subfigure[data size range from 50 to 100]{
-    \includegraphics[width=0.4\textwidth]{global_epsilon_size50to100.eps}}
-  \subfigure[data size range from 100 to 200]{
-    \includegraphics[width=0.4\textwidth]{global_epsilon_size100to200.eps}} 
-  % \subfigure[data size range from 200 to 500]{
-  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
-  % \subfigure[data size range from 500 to 1000]{
-  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
+    \includegraphics[width=0.6\textwidth]{privacyloss.eps}
+\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$ and observed data are uniformly distributed}
 \label{fig_privacy}
@@
 
-$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
-That is to say, we achieved a higher privacy level than expected.
-In next step, we are going to improve the accuracy using this property.
+$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected.
 

### 2018-11-12 Arxiv/main.tex
update laplace accuracy
update laplace accuracy bound

@@
 \[
-Pr[\lfloor Y \rfloor = t] 
+Pr\big[\lfloor Y \rfloor = t\big] 
 = Pr[ t-1 \leq Y < t] 
@@
 \begin{array}{rcl}
-& Pr[\hlg(\bysinfer(\dataobs), r_L ) = \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)] 
+& Pr\big[\hlg(\bysinfer(\dataobs), r_L ) 
+= \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
 =  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
@@
 $$
-where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor$.\\
+where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
 By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
+
 \begin{itemize}
   \item[\textbf{case 1:}] \textbf{t is even}\\
-
-\item[\textbf{case 2:}] \textbf{t is odd}
+  \begin{align*}
+  & Pr\Bigg[\hlg(\bysinfer(\dataobs), r_L ) 
+  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+  \cdot
+  \prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
+  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+  \end{align*}
+
+  \item[\textbf{case 2:}] \textbf{t is odd}\\
+  let $t = 2 m + \frac{1}{2}$
+  \begin{align*}
+   Pr\Bigg[ \hlg(\bysinfer(\dataobs), r_L ) = & \\
+  \qquad &
+  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
+  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \cdot \\
+  \qquad &\cdot 
+  \prod_{k = 0}^{m-1}
+  \sqrt{(1 + \frac{1}{2(\alpha + k)})
+  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+  } \\
+  \qquad & \cdot 
+  \prod_{k = 1}^{m} 
+  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
+  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+  \end{align*}
+
 \end{itemize}

### 2018-11-12 Arxiv/main.tex
Update Arxiv/main.tex

@@
 \label{subsec_accuracy_lap}
-Accuracy bound for Laplace mechanism is provided by its probability density function:
-\begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}},
-\end{equation*}
-where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.
-
-After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
+Accuracy bound for Laplace mechanism is provided by its probability density function\cite{dwork2014algorithmic}:
+$$
+Pr[|Y| \geq t \cdot b] = e^{- t},
+$$
+where $Y \thicksim Lap(b)$, i.e.,
+\begin{equation*}
+Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
+\end{equation*}
+in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.
+
+After post-processing, Laplace noise is discretized. Then the probability mess function for discretized Laplace mechanism is obtained by:
 \[
@@
 Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism.
-By applying the accuracy bound into Hellinger distance in our case:
+By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
 $$
@@
   \item[\textbf{case 2:}] \textbf{t is odd}\\
-  let $t = 2 m + \frac{1}{2}$
+  let $t = 2 m + 1$
   \begin{align*}
@@
 Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
-\[
-Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
-\]
 

### 2018-11-12 Arxiv/main.tex
update accuracy bound for expmench

@@
 \begin{array}{rcl}
-& Pr\big[\hlg(\bysinfer(\dataobs), r_L ) 
-= \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
+& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
 =  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
@@
 where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
-By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
+By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
 
@@
   \begin{align*}
-  & Pr\Bigg[\hlg(\bysinfer(\dataobs), r_L ) 
+  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
   = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
@@
   \begin{align*}
-   Pr\Bigg[ \hlg(\bysinfer(\dataobs), r_L ) = & \\
+   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
   \qquad &
   1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \cdot \\
+  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
   \qquad &\cdot 
@@
 \label{subsec_accuracy_smoo}
-We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.
-
-First is the tight bound with very accurate calculation.
-\begin{equation*}
-\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} = \sum\limits_{\{z | \hellinger(\bysinfer(\dataobs), z) \geq c\}} \frac{e^{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), z)}{S(\dataobs)}}}{NL_x}.
-\end{equation*}
-
-In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:
-
-\begin{equation*}
-\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{NL_x}.
-\end{equation*}
-
-In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:
-
-\begin{equation*}
-\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(\dataobs)}})}{N(n)},
-\end{equation*}
-where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.
-
-Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
+We explored following accuracy bound for $\hexpmech$:
+  \begin{align*}
+  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} 
+  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \geq c\}} \frac{\exp{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)}}}{\unomalizer{\dataobs}}\\
+  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
+  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|\exp{(\frac{- \epsilon}{4 S(\dataobs)})}}\\
+  = & \exp{\big(\frac{ \epsilon (1 - c)}{4 S(\dataobs)}}\big)\\
+  \end{align*}
+
+Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we also derived a loose bound:
 
@@
 Pr[u(\hexpmech(\dataobs)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
-\end{split}
-\end{equation*}
-which has been used in the dilation property proof.
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
+\end{split}
+\end{equation*}
+
+Unfolding the Hellinger distance in the accuracy bound, we get:
 

### 2018-11-12 Arxiv/main.tex
update accuracy bound in Exponential mechanism

@@
 Pr\big[\lfloor Y \rfloor = t\big] 
-= Pr[ t-1 \leq Y < t] 
-= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
+= Pr[ t \leq Y < t + 1] 
+= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
 \]
@@
 = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
 \end{array}
@@
 where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
+Also, we have:
+\begin{align*}
+ Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
+  = \quad & Pr[ - t \leq Y < t + 1] \\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
+ \end{align*}
 By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
@@
   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
-  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+  \end{align*}
+
+  We also have:
+  \begin{align*}
+  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
+  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+  \cdot
+  \prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
   \end{align*}
@@
   \begin{align*}
-   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
+   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
   \qquad &
@@
   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
+  \geq \quad & Pr[ - t \leq Y < t + 1] \\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
   \end{align*}
@@
 We explored following accuracy bound for $\hexpmech$:
+
+\begin{itemize}
+  \item[\textbf{lower bound}]
   \begin{align*}
-  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} 
-  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \geq c\}} \frac{\exp{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)}}}{\unomalizer{\dataobs}}\\
-  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
-  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|\exp{(\frac{- \epsilon}{4 S(\dataobs)})}}\\
-  = & \exp{\big(\frac{ \epsilon (1 - c)}{4 S(\dataobs)}}\big)\\
+  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
+  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
+  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
+  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
   \end{align*}
+
+  Also, we have:
+  \begin{align*}
+  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
+  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
+  \end{align*}
+
+  in the Bate-binomial model.\\
+  Unfolding the Hellinegr distance in this accuracy bound:\\
+  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t) = $
+  \begin{align*}
+  & 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+  \cdot
+  \prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
+  \end{align*}
+  when t is even, and when t is odd, let $t = 2 m + 1$:
+  \begin{align*}
+  \qquad &
+  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
+  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
+  \qquad &\cdot 
+  \prod_{k = 0}^{m-1}
+  \sqrt{(1 + \frac{1}{2(\alpha + k)})
+  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+  } \\
+  \qquad & \cdot 
+  \prod_{k = 1}^{m} 
+  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
+  \end{align*}
+
+\end{itemize}
 
@@
 \end{equation*}
-
-Unfolding the Hellinger distance in the accuracy bound, we get:
 

### 2018-11-13 Arxiv/main.tex
Update Arxiv/main.tex

@@
   Unfolding the Hellinegr distance in this accuracy bound:\\
-  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t) = $
+  $c^2 = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)^2 = $
   \begin{align*}

### 2018-11-13 Arxiv/main.tex
update accuracy analysis

--- 2018-11-12 Arxiv/main.tex
@@
 \label{subsec_accuracy_global}
-The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
+The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
 \begin{equation*}
@@
 \label{subsec_accuracy_lap}
-Accuracy bound for Laplace mechanism is provided by its probability density function\cite{dwork2014algorithmic}:
+Accuracy bound for Laplace mechanism is given by its probability density function\cite{dwork2014algorithmic}:
 $$
@@
 
-Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism.
+Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
@@
 $$
-where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
-Also, we have:
+When $\alpha = \beta$, we also have:
 \begin{align*}
@@
   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
   \end{align*} 
+  when $\alpha = \beta$.
 
@@
   let $t = 2 m + 1$
+  \begin{align*}
+  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
+  \qquad &
+  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
+  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
+  \qquad &\cdot 
+  \prod_{k = 0}^{m-1}
+  \sqrt{(1 + \frac{1}{2(\alpha + k)})
+  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+  } \\
+  \qquad & \cdot 
+  \prod_{k = 1}^{m} 
+  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
+  \geq \quad & Pr[ - t \leq Y < t + 1] \\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
+  \end{align*}
+
+  we also have: 
   \begin{align*}
@@
   \geq \quad & Pr[ - t \leq Y < t + 1] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
+  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
   \end{align*}
+  when $\alpha = \beta$
 
@@
 \label{subsec_accuracy_smoo}
-We explored following accuracy bound for $\hexpmech$:
+
+\begin{definition}
+\label{def_cardinality}
+  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.
+
+  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
+
+  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
+\end{definition}
+% \begin{itemize}
+%   \item[\textbf{lower bound}]
+%   \begin{align*}
+%   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
+%   = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
+%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
+%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
+%   \end{align*}
+
+  We have following probability distribution for accuracy:
+  \begin{align}
+  \label{eq_acc}
+  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
+  = & \frac{\cardinality{\dataobs}{c} \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
+  \end{align}
+  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, and $\cardinality{\dataobs}{c} = 2$ when $t \neq 0$.\\
+  Unfolding the Hellinegr distance in this accuracy bound:
 
  \begin{itemize}
-  \item[\textbf{lower bound}]
+
+  \item[\textbf{case 1:}] \textbf{t is even}
+
   \begin{align*}
-  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
-  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
-  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
-  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
-  \end{align*}
-
-  Also, we have:
-  \begin{align*}
-  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
-  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
-  \end{align*}
-
-  in the Bate-binomial model.\\
-  Unfolding the Hellinegr distance in this accuracy bound:\\
-  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t) = $
-  \begin{align*}
-  & 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 =  1 - \prod_{k = 0}^{\frac{t}{2} - 1}
   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
@@
   \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
+  = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+  \cdot
+  \prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
   \end{align*}
-  when t is even, and when t is odd, let $t = 2 m + 1$:
+
+  \item[\textbf{case 2:}] \textbf{t is odd}
+
   \begin{align*}
-  \qquad &
+  c^2 = \qquad &
   1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
@@
   \end{align*}
+  Substitute the $c$ in Equation, (\ref{eq_acc})
 

### 2018-11-14 Arxiv/main.tex
update accuracy analysis

@@
 \label{subsec_accuracy_lap}
-Accuracy bound for Laplace mechanism is given by its probability density function\cite{dwork2014algorithmic}:
+Given\cite{dwork2014algorithmic}:
 $$
@@
 $$
-where $Y \thicksim Lap(b)$, i.e.,
+where $Y \thicksim Lap(b)$, we get:
 \begin{equation*}
@@
 
-After post-processing, Laplace noise is discretized. Then the probability mess function for discretized Laplace mechanism is obtained by:
+After post-processing, we get:
 \[
@@
 Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
-By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
+By applying Hellinger distance in our case, we get:
 $$
@@
  \end{align*}
-By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
-
+ By simplifying the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
 \begin{itemize}
@@
   \qquad &
-  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
+  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
 \qquad &\cdot 
@@
   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  \geq \quad & Pr[ - t \leq Y < t + 1] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
+  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
   \end{align*}
@@
 \label{subsec_accuracy_smoo}
-
-\begin{definition}
-\label{def_cardinality}
-  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.
-
-  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.
-
-  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
-\end{definition}
-% \begin{itemize}
-%   \item[\textbf{lower bound}]
-%   \begin{align*}
-%   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
-%   = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
-%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
-%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
-%   \end{align*}
-
-  We have following probability distribution for accuracy:
+  In Beta-binomial model,
+  we have following formula for accuracy:
   \begin{align}
@@
   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
-  = & \frac{\cardinality{\dataobs}{c} \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
+  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
   \end{align}
-  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, and $\cardinality{\dataobs}{c} = 2$ when $t \neq 0$.\\
+  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
   Unfolding the Hellinegr distance in this accuracy bound:
@@
   \begin{align*}
-  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 =  1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 = 
+  1 - \prod_{k = 0}^{\frac{t}{2} - 1}
   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
@@
   \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}
+  {\nomalizer{\dataobs}}
   \end{align*}

### 2018-11-14 Arxiv/main.tex
update accuracy analysis

@@
 
-\subsubsection{Accuracy Bound for Exponential Mechanism}
-\label{subsec_accuracy_global}
-The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
-\begin{equation*}
-Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
-		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
-\end{equation*}
-where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
+% \subsubsection{Accuracy Bound for Exponential Mechanism}
+% \label{subsec_accuracy_global}
+% The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
+% \begin{equation*}
+% Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+% 		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
+% \end{equation*}
+% where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.
 
@@
 \label{subsec_accuracy_lap}
-Given\cite{dwork2014algorithmic}:
+If $Y \thicksim Lap(b)$, we have\cite{dwork2014algorithmic}:
 $$
-Pr[|Y| \geq t \cdot b] = e^{- t},
+Pr[|Y| \geq t \cdot b] = e^{- t}.
 $$
-where $Y \thicksim Lap(b)$, we get:
+Based on this, we get:
 \begin{equation*}
@@
 
-After post-processing, we get:
+After post-processing (i.e., taking the floor value of $Y$), we get:
 \[
@@
   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
-  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
+  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
   \end{align}
   $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
-  Unfolding the Hellinegr distance in this accuracy bound:
+  Unfolding the Hellinegr distance in this accuracy formula:
 
@@
 \end{itemize}
-
-Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we also derived a loose bound:
-
-\begin{equation*}
-\begin{split}
-Pr[u(\hexpmech(\dataobs)) \leq c] 
-& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
-\end{split}
-\end{equation*}
 

### 2018-11-14 codes/dpbayesinfer_Betabinomial.py

@@ -185,7 +185,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(4 * self._alpha_SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._alpha_SS))
 			self._alpha_SS_probabilities.append(temp)
 			nomalizer += temp
 

### 2018-11-15 codes/discrete_probability_on_betabinomial.py
update accuracy plots.

@@ -228,10 +228,10 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 	
 	step,lap_1 = calculate_prob_lap(Candidate_bins_by_step, Bayesian_Model, 
-		sensitivity = 2.0, savename = "_lap_1.txt")
+		sensitivity = 1.0, savename = "_lap_1.txt")
 
 	step,lap_2 = calculate_prob_lap(Candidate_bins_by_step, Bayesian_Model, 
-		sensitivity = 10.0, savename = "_lap_2.txt")
+		sensitivity = 2.0, savename = "_lap_2.txt")
 
 
 	#############################################################################
@@ -247,8 +247,8 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 		r'$\mathcal{M}_{\mathcal{H}}$ with $\gamma -$Sensitivity',
 		r"NON PRIVATE $\mathcal{M}_{\mathcal{E}}$",
 		r"STANDARD $\mathcal{M}_{\mathcal{E}}$",
-		'IMPROVED LapMech (sensitivity = 2)', 
-		'LapMech (sensitivity = 10)']
+		'IMPROVED LapMech (sensitivity =1)', 
+		'LapMech (sensitivity = 2)']
 
 
 	#############################################################################
@@ -256,29 +256,29 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 
 	plt.figure()
-	# plt.plot(step, exp, 'o', label=(labels[0]))
+	plt.plot(step, exp, 'o', label=(labels[0]))
 
-	# plt.plot(step, exp_new, '*', label=(labels[1]))
+	plt.plot(step, exp_new, '*', label=(labels[1]))
 
-	# plt.plot(step, exp_LS, '-', label=(labels[2]))
+	plt.plot(step, exp_LS, '-', label=(labels[2]))
 
-	# plt.plot(step, exp_GS, '-', label=(labels[3]))
+	plt.plot(step, exp_GS, '-', label=(labels[3]))
 
-	# plt.plot(step, lap_1,'^', color = 'navy', label=(labels[4]))
+	plt.plot(step, lap_1,'-', color = 'navy', label=(labels[4]))
 
-	# plt.plot(step, lap_2, '.',color = 'lightblue', label=(labels[5]))
+	plt.plot(step, lap_2, '-',color = 'lightblue', label=(labels[5]))
 
[…]

### 2018-11-15 codes/dpbayesinfer_Betabinomial.py

@@ -146,7 +146,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(4 * self._SS))
 			self._SS_probabilities.append(temp)
 			nomalizer += temp
 
@@ -185,7 +185,7 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._alpha_SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(4 * self._alpha_SS))
 			self._alpha_SS_probabilities.append(temp)
 			nomalizer += temp
 

### 2018-11-15 Arxiv/main.tex
update accuracy plots.
update plots of accuracy

@@
 \subsubsection{Theoretical Results}
+In Fig.
+\ref{fig_theory} and \ref{fig_theory_epsilon}, we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms.
+We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
+Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
+the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.
+
+We consider 6 mechanisms in our comparison, including the Laplace mechanism, improved Laplace mechanism, standard exponential mechanism, non-private exponential mechanism (using local sensitivity) and two newly designed mechanisms (one with smooth sensitivity achieving $(\epsilon, \delta)-$dp and the other with $\gamma$ sensitivity achieving $\epsilon-$dp).
 
@@
   \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.4\textwidth]{theory_2d.eps}
+    \includegraphics[width=0.45\textwidth]{theory_2d.eps}
   \label{subfig_theory_2d}
@@
   \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.4\textwidth]{theory_3d.eps}
+    \includegraphics[width=0.45\textwidth]{theory_3d.eps}
   \label{subfig_theory_3d}
   }
-\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
+\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 1.0$}
 \label{fig_theory}
@@
 \end{figure}
-In Fig.
-\ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms.
-We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
-Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
-the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.
 
@@
 
+\begin{figure}
+\begin{center}
+\centering
+  \subfigure[2 dimensions of data size 1000]{
+    \includegraphics[width=0.45\textwidth]{epsilon5_2d_1000.eps}
+  \label{subfig_theory_2d}
+  }
+  \subfigure[2 dimensions of data size 10000]{
+    \includegraphics[width=0.45\textwidth]{epsilon5_2d_10000.eps}
+  \label{subfig_theory_3d}
+  }
+\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$}
+\label{fig_theory_epsilon}
+\end{center}
+\end{figure}
+Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig. \ref{fig_theory_epsilon}. In 2 dimensions, we can perform better than Laplace mechanisms.
+
 \subsubsection{Experimental Results}
@@
 Every plot is an average over 1000 runs. In all the experiments we set
-$\epsilon = 1.0$, and $\delta = 10^{-8}$.
+$\epsilon = 1.0$.
 
@@
     \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
-\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
+\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$}
 \label{fig_vs_datasize_2d}
@@
 \centering
-\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
 {
@@
 }
-\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
+\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
 {
@@
     \includegraphics[width=0.6\textwidth]{privacyloss.eps}
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$ and observed data are uniformly distributed}
+\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
 \label{fig_privacy}

### 2018-11-15 codes/discrete_probability_on_betabinomial.py

@@ -222,16 +222,28 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 	exp_GS = calculate_prob_exp(Candidate_bins_by_step, Bayesian_Model, mechanism_parameter = 2,
 		sensitivity = Bayesian_Model._GS, savename = "_exp_GS.txt")
+	
+	#############################################################################
+	#SETTING THE SENSITIVITY
+	#############################################################################
+	
+	if (len(prior._alphas) == 2):
+		sensitivity1 = 1.0
+		sensitivity2 = 2.0
+	else:
+		sensitivity1 = 2.0
+		sensitivity2 = len(prior._alphas)*1.0
+
 
 	#############################################################################
 	#CALCULATE the Laplace prob within the same bin
 	#############################################################################
 	
 	step,lap_1 = calculate_prob_lap(Candidate_bins_by_step, Bayesian_Model, 
-		sensitivity = 1.0, savename = "_lap_1.txt")
+		sensitivity = sensitivity1, savename = "_lap_1.txt")
 
 	step,lap_2 = calculate_prob_lap(Candidate_bins_by_step, Bayesian_Model, 
-		sensitivity = 2.0, savename = "_lap_2.txt")
+		sensitivity = sensitivity2, savename = "_lap_2.txt")
 
 
 	#############################################################################
@@ -247,8 +259,8 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 		r'$\mathcal{M}_{\mathcal{H}}$ with $\gamma -$Sensitivity',
 		r"NON PRIVATE $\mathcal{M}_{\mathcal{E}}$",
 		r"STANDARD $\mathcal{M}_{\mathcal{E}}$",
-		'IMPROVED LapMech (sensitivity =1)', 
-		'LapMech (sensitivity = 2)']
+		'IMPROVED LapMech (sensitivity ='+ str(sensitivity1) +')', 
+		'LapMech (sensitivity = '+ str(sensitivity1) +')']
 
 
 	#############################################################################
@@ -357,7 +369,7 @@ if __name__ == "__main__":
 	#SETTING UP THE PARAMETERS
 	#############################################################################
 	datasize = 600
-	epsilon = 1.0
+	epsilon = 5.0
 	delta = 0.00000001
 	prior = dirichlet([1,1,1])
 	dataset = [200,200,200]

### 2018-11-18 codes/Hellinger_Sensitivity_Dirichlet.py
update privacy proof

@@ -16,8 +16,8 @@ from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 
 def generate_sensitivities():
 	sensitivities = []
-	for i in range(1, 500):
-		j = 1000 - i
+	for i in range(1, 5000):
+		j = 10000 - i
 		sensitivities.append((dirichlet([i + 2, j]) - dirichlet([i + 1, j + 1]))/
 			(dirichlet([i + 1, j + 1]) - dirichlet([i, j + 2])))
 
@@ -30,8 +30,8 @@ if __name__ == "__main__":
 
 	fig = plt.figure()
 
-	plt.scatter(range(1, 500), sensitivities)
-	plt.xlabel(r'$\alpha, \beta = 1000 - \alpha$')
+	plt.scatter(range(1, 5000), sensitivities)
+	plt.xlabel(r'$\alpha, \beta = 10000 - \alpha$')
 	plt.ylabel(r'$\frac{\mathcal{H}(\mathsf{beta}(\alpha+2, \beta),\mathsf{beta}(\alpha + 1, \beta+1))}{\mathcal{H}(\mathsf{beta}(\alpha + 1, \beta + 1), \mathsf{beta}(\alpha, \beta + 2))}$')
 	plt.show()
 

### 2018-11-18 codes/Hellinger_Sensitivity.py
update privacy proof

@@ -16,8 +16,9 @@ from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 
 def generate_sensitivities():
 	sensitivities = []
-	for i in range(1, 5000):
-		j = 10000 - i
+	for i in range(1, 1000):
+		j = i
+		i = 2000 - j
 		sensitivities.append((dirichlet([i + 2, j]) - dirichlet([i + 1, j + 1]))/
 			(dirichlet([i + 1, j + 1]) - dirichlet([i, j + 2])))
 
@@ -30,8 +31,8 @@ if __name__ == "__main__":
 
 	fig = plt.figure()
 
-	plt.scatter(range(1, 5000), sensitivities)
-	plt.xlabel(r'$\alpha, \beta = 10000 - \alpha$')
+	plt.scatter(range(1, 1000), sensitivities)
+	plt.xlabel(r'$\beta, \alpha = 2000 - \beta$')
 	plt.ylabel(r'$\frac{\mathcal{H}(\mathsf{beta}(\alpha+2, \beta),\mathsf{beta}(\alpha + 1, \beta+1))}{\mathcal{H}(\mathsf{beta}(\alpha + 1, \beta + 1), \mathsf{beta}(\alpha, \beta + 2))}$')
 	plt.show()
 

### 2018-11-19 codes/dpbayesinfer_Betabinomial.py
update privacy analysis

@@ -183,13 +183,15 @@ class BayesInferwithDirPrior(object):
 		###################################################################################################################################
 		#CALCULATING THE SENSITIVITY
 		###################################################################################################################################
+		x = self._observation_counts
 		nomalizer = 0.0
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(4 * self._alpha_SS))
+			temp = math.exp(self._epsilon * self._candidate_scores[r]/(2 * self._alpha_SS))
 			self._alpha_SS_probabilities.append(temp)
 			nomalizer += temp
 
 		for i in range(len(self._alpha_SS_probabilities)):
+			r = self._candidates[i]
 			self._alpha_SS_probabilities[i] = self._alpha_SS_probabilities[i]/nomalizer
 		return nomalizer
 

### 2018-11-19 codes/privacyloss.py

@@ -37,7 +37,7 @@ def privacy_loss(sample_sizes,epsilon,delta,prior):
 			candidates[i]._minus(prior)
 
 		candidates = [dirichlet([0,n]), dirichlet([1,n-1]),dirichlet([2,n-2]), 
-		dirichlet([n,0]), dirichlet([n-1, 1]), dirichlet([n - 2, 2])]
+		dirichlet([3, n - 3])]
 		#########################################################################################################################
 		#MAX PRIVACY LOSS UNDER SIZE N
 		#########################################################################################################################			
@@ -79,44 +79,67 @@ def privacy_loss(sample_sizes,epsilon,delta,prior):
 
 
 def privacy_loss_x1_x2(sample_size,epsilon,delta,prior,x1, x2):
+
+	print "Adjacent data set:", x1, x2
+	#########################################################################################################################
+	#OBTAIN DECOMPOSED OUTPUTTING PROBABILITIES UNDER TWO ADJACENT DATA SET
+	#########################################################################################################################	
+	x1_nomalizer, x1_probabilities = decomposed_probability_values(sample_size,epsilon,delta,prior,x1)
+	x2_nomalizer, x2_probabilities = decomposed_probability_values(sample_size,epsilon,delta,prior,x2)
+
+	print "NL(x1) =", x1_nomalizer, "NL(x2) =", x2_nomalizer
+	print "NL(x2)/NL(x1) = exp(", math.log(x2_nomalizer / x1_nomalizer),")"
+
+	epsilons = {}
+	for key, item in x1_probabilities.items():
+		i = x2_probabilities[key]
+		epsilons[key] = math.log(item / i)
+		print "nominator(x1," + key + ") =", item, "; nominator(x2," + key + ") =", i
+		print "nominator(x1,r)/nominator(x2,r) = exp(", epsilons[key],")"
+
+	sorted_epsilons = sorted(epsilons.items(), key=operator.itemgetter(1))
+	
+	
+	# return max(sorted_epsilons[-1][1], abs(sorted_epsilons[0][1]))
 	#########################################################################################################################
[…]

### 2018-11-19 codes/privacyloss.py
update privacy proof

@@ -141,6 +141,24 @@ def decomposed_probability_values(sample_size,epsilon,delta,prior,observation):
 	
 	return nomalizer, probabilities_exp
 
+def nomalizer_study(datasizes, epsilon, delta, prior):
+	loss_in_nomalizer = []
+	for datasize in datasizes:
+		x1_nomalizer, probabilities = decomposed_probability_values(datasize,epsilon,delta,prior,[datasize-1,1])
+		x2_nomalizer, probabilities = decomposed_probability_values(datasize,epsilon,delta,prior,[datasize,0])
+		loss_in_nomalizer.append(math.log(x1_nomalizer/x2_nomalizer))
+
+	#########################################################################################################################
+	#PLOT THE PRIVACY LOSS UNDER DIFFERENT DATA SIZE
+	#########################################################################################################################			
+	plt.figure()
+	plt.title(("PRIVACY LOSS in Denominator"))
+	plt.plot(datasizes,loss_in_nomalizer, 'bo-', label=('Exp Mech with Local Sensitivity'))
+	plt.xlabel("Data Size")
+	plt.ylabel(r"privacy loss in Denominator ($log(\frac{NL(n-1,1)}{NL(n,0)})$)")
+	plt.grid()
+	plt.legend(loc='best')
+	plt.show()
 
 def probability_values(sample_size,epsilon,delta,prior,observation):
 	
@@ -170,7 +188,7 @@ def gen_datasets(v, n_list):
 
 
 def gen_datasizes(r, step):
-	return [i*step for i in range(r[0]/step,r[1]/step + 1)]
+	return [(r[0] + i*step) for i in range(0,(r[1] - r[0])/step + 1)]
 
 def gen_priors(r, step, d):
 	return [dirichlet([step*i for j in range(d)]) for i in range(r[0]/step,r[1]/step + 1)]
@@ -178,19 +196,18 @@ def gen_priors(r, step, d):
 
 if __name__ == "__main__":
 
-	datasize = 6
-	epsilon = 1.0
+	datasize = 20
+	epsilon = 2.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
 	dataset = [50,50]
 	epsilons = numpy.arange(0.1, 2, 0.1)
[…]

### 2018-11-23 codes/privacyloss.py
fix typo

@@ -70,7 +70,7 @@ def privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 	epsilons = {}
 	for key, item in x1_probabilities.items():
 		i = x2_probabilities[key]
-		epsilons[key] = math.log(item / i)
+		epsilons[key] = abs(math.log(item / i))
 
 	return sorted(epsilons.items(), key=operator.itemgetter(1))
 
@@ -80,8 +80,6 @@ def privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 #########################################################################################################################	
 def numerator_privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 
-	print "Adjacent data set:", x1, x2
-
 	x1_nomalizer, x1_probabilities = decomposed_probability_values(datasize,epsilon,delta,prior,x1)
 	x2_nomalizer, x2_probabilities = decomposed_probability_values(datasize,epsilon,delta,prior,x2)
 
@@ -89,6 +87,7 @@ def numerator_privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 	for key, item in x1_probabilities.items():
 		i = x2_probabilities[key]
 		epsilons[key] = abs(math.log(item / i))
+		# print "numerator", key, epsilons[key]
 
 	return sorted(epsilons.items(), key=operator.itemgetter(1))
 
@@ -104,7 +103,7 @@ def denumerator_privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 	print "NL(x1) =", x1_nomalizer, "NL(x2) =", x2_nomalizer
 	print "NL(x2)/NL(x1) = exp(", math.log(x2_nomalizer / x1_nomalizer),")"
 
-	return math.log(x2_nomalizer / x1_nomalizer)
+	return abs(math.log(x2_nomalizer / x1_nomalizer))
 
 
 
@@ -122,6 +121,9 @@ def plot_privacyloss(x, y, label):
 	plt.show()
 
 
+#########################################################################################################################
+# DECOMPOSED PRIVACY UNDER DIFFERENET DATA SIZE - DENUMERATOR
+#########################################################################################################################	
 def denumerator_study(datasizes, epsilon, delta, prior):
 	loss_in_nomalizer = []
 	for datasize in datasizes:
[…]

### 2018-12-03 Arxiv/main.tex
update privacy proof
Update main.tex

@@
   \hexpmechPr{\dataobs}{z = r} 
-  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
-  & = \frac {exp\big(
+  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+  & = \frac {\exp\big(
   \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
@@
   {\unomalizer{\dataobs}} \\
-  & = \frac {exp\big(
+  & = \frac {\exp\big(
   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
@@
   {\unomalizer{\dataobs}}
-  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
+  \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
   \end{split}
   \end{equation*}
-
   Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
@@
   {\unomalizer{\dataobs}}
-  \cdot exp\big( \frac{\epsilon}{4} \big) \\
-  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  exp
+  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
+  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   {\unomalizer{\dataobs}}
-  exp
+  \exp
   \big(
@@
   \big)
-  exp
+  \exp
   \big(
@@
   \big)\\
-  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  exp
+  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \begin{split}
-  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  exp
+  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \big)\\
-  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \begin{split}
-  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \sum_{r'\in \candidateset} 
-  exp 
+  \exp 
   \big(
@@
   }\\
-  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \big)
-  exp 
+  \exp 
   \big(
@@
   \begin{split}
-  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  exp
+  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
   \big(
@@
   \frac {
-  exp
+  \exp
   \big(
@@
   {
-  \sum_{r'\in \candidateset} 
-  exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4\cdot S(\dataobs')}
-  \big)
+  \unomalizer{\dataobs'}
   }\\
@@
 \]
+when $t \geq 0$, and\\
+\[
+Pr\big[\lfloor Y \rfloor = t\big] 
+= Pr[ t \leq Y < t + 1] 
+= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+\]
+when $t < 0$.\\
 
@@
 $$
-When $\alpha = \beta$, we also have:
-\begin{align*}
- Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-  = \quad & Pr[ - t \leq Y < t + 1] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
- \end{align*}
- By simplifying the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
+when $t \geq 0$, and\\
+$$
+\begin{array}{rcl}
+& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
+= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+\end{array}
+$$
+when $t < 0$.\\
+
+% When $\alpha = \beta$, we also have:
+% \begin{align*}
+%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
+%   = \quad & Pr[ - t \leq Y < t + 1] \\
+%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
+%  \end{align*}
+Unfolding the Hellinger distance formula($\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$), we get:
 \begin{itemize}
-  \item[\textbf{case 1:}] \textbf{t is even}\\
+  \item[\textbf{case}] \textbf{t is even}\\
   \begin{align*}
@@
 
-  We also have:
-  \begin{align*}
-  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
-  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot
-  \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
-  \end{align*} 
-  when $\alpha = \beta$.
-
-  \item[\textbf{case 2:}] \textbf{t is odd}\\
+%   We also have:
+%   \begin{align*}
+%   & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
+%   \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+%   \cdot
+%   \prod_{k = 1}^{\frac{t}{2}}
+%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
+%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
+%   \end{align*} 
+%   when $\alpha = \beta$.
+% in 2 dimensions, where $\epsilon = 1.0$. 
+% \begin{itemize}
+% 	\item \textbf{Case} of baseline Laplace mechanism, where $\Delta \bysinfer = 2$:\\
+
+% 	\item \textbf{Case} of improved Laplace mechanism, where $\Delta \bysinfer = 1$
+% \end{itemize}
+
+  \item[\textbf{case}] \textbf{t is odd}\\
   let $t = 2 m + 1$
@@
   \end{align*}
-
-  we also have: 
-  \begin{align*}
-   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
-  \qquad &
-  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
-  \qquad &\cdot 
-  \prod_{k = 0}^{m-1}
-  \sqrt{(1 + \frac{1}{2(\alpha + k)})
-  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  } \\
-  \qquad & \cdot 
-  \prod_{k = 1}^{m} 
-  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  \geq \quad & Pr[ - t \leq Y < t + 1] \\
-  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
-  \end{align*}
-  when $\alpha = \beta$
-
+  % we also have: 
+  % \begin{align*}
+  %  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
+  % \qquad &
+  % 1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
+  % \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
+  % \qquad &\cdot 
+  % \prod_{k = 0}^{m-1}
+  % \sqrt{(1 + \frac{1}{2(\alpha + k)})
+  % (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+  % } \\
+  % \qquad & \cdot 
+  % \prod_{k = 1}^{m} 
+  % \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
+  % \geq \quad & Pr[ - t \leq Y < t + 1] \\
+  % = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
+  % \end{align*}
+  % when $\alpha = \beta$
 \end{itemize}
+
+In both cases, $Pr[\hellinger(\bysinfer(\dataobs), r_L )^2 = 0]$ asymptotically equal to 1 when data size increases.
 
@@
   $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
-  Unfolding the Hellinegr distance in this accuracy formula:
-
- \begin{itemize}
-
-  \item[\textbf{case 1:}] \textbf{t is even}
-
-  \begin{align*}
-  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 = 
-  1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot
-  \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
-  = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot
-  \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}
-  {\nomalizer{\dataobs}}
-  \end{align*}
-
-  \item[\textbf{case 2:}] \textbf{t is odd}
-
-  \begin{align*}
-  c^2 = \qquad &
-  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
-  \qquad &\cdot 
-  \prod_{k = 0}^{m-1}
-  \sqrt{(1 + \frac{1}{2(\alpha + k)})
-  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  } \\
-  \qquad & \cdot 
-  \prod_{k = 1}^{m} 
-  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
-  \end{align*}
-  Substitute the $c$ in Equation, (\ref{eq_acc})
-
-\end{itemize}
+%   Unfolding the Hellinegr distance in this accuracy formula:
+%  \begin{itemize}
+
+%   \item[\textbf{case 1:}] \textbf{t is even}
+
+%   \begin{align*}
+%   &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 = 
+%   1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+%   \cdot
+%   \prod_{k = 1}^{\frac{t}{2}}
+%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
+%   = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+%   \cdot
+%   \prod_{k = 1}^{\frac{t}{2}}
+%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}
+%   {\nomalizer{\dataobs}}
+%   \end{align*}
+
+%   \item[\textbf{case 2:}] \textbf{t is odd}
+
+%   \begin{align*}
+%   c^2 = \qquad &
+%   1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
+%   \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
+%   \qquad &\cdot 
+%   \prod_{k = 0}^{m-1}
+%   \sqrt{(1 + \frac{1}{2(\alpha + k)})
+%   (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+%   } \\
+%   \qquad & \cdot 
+%   \prod_{k = 1}^{m} 
+%   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
+%   \end{align*}
+%   Substitute the $c$ in Equation, (\ref{eq_acc})
+
+% \end{itemize}
 

### 2018-12-04 Arxiv/main.tex
update a bit about accuracy comparison.

@@
 \label{subsec_baselines}
-Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.
+Baseline Mechanisms are introduced in prior to our mechanism, $\hexpmech$.
 
@@
 \subsubsection{Laplace Mechanism}
- Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:
+ Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech$. $\lapmech$ produces an output $r_L$:
 
@@
  \] 
- where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
+ where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
  \[
@@
 
- Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:
+ Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, then the improved Laplace mechanism $\ilapmech$ is producing an output $r_{IL}$:
 
@@
 = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+= \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
 \end{array}
@@
   \begin{align*}
-  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
+  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 =
   \qquad &
@@
   \end{align*}
-  % we also have: 
-  % \begin{align*}
-  %  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
-  % \qquad &
-  % 1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-  % \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
-  % \qquad &\cdot 
-  % \prod_{k = 0}^{m-1}
-  % \sqrt{(1 + \frac{1}{2(\alpha + k)})
-  % (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  % } \\
-  % \qquad & \cdot 
-  % \prod_{k = 1}^{m} 
-  % \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  % \geq \quad & Pr[ - t \leq Y < t + 1] \\
-  % = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
-  % \end{align*}
-  % when $\alpha = \beta$
+
 \end{itemize}
 
-In both cases, $Pr[\hellinger(\bysinfer(\dataobs), r_L )^2 = 0]$ asymptotically equal to 1 when data size increases.
+\begin{itemize}
+  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
+  \item[\textbf{t = 1}]
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$. 
+  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+  \cdot
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
+\end{itemize}
+In all cases above, probabilities are fixed whenever data size changes.
 
@@
   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
-  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
+  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
   \end{align}
   $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
+
+For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
+
+\begin{table*}[h!]
+\centering
+\begin{tabular}{ |c|c|c|c| } 
+\hline
+ c & 0 
+ & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
+  & $1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
+ \hline
+ $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
+ & 0.39346934028 & 0.39346934028 & 0.39346934028  \\
+ \hline
+ $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
+ \hline
+ $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ &  &  & \\
+ \hline
+\end{tabular}
+\caption{Accuracy Comparison in Theoretical}
+\label{tab_acc_theo}
+\end{table*}
+
 %   Unfolding the Hellinegr distance in this accuracy formula:

### 2018-12-04 Arxiv/main.tex
Update main.tex

@@
 \label{subsec_accuracy_lap}
-Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
+Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.
 
@@
 
-\begin{table*}[h!]
+\begin{table}[h!]
+\scriptsize
 \centering
@@
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
- & 0.39346934028 & 0.39346934028 & 0.39346934028  \\
+ & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
  \hline
  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
+ \hline
+ $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
  & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
- \hline
- $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- &  &  & \\
  \hline
@@
 \label{tab_acc_theo}
-\end{table*}
+\end{table}
+
+In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
+\begin{table}[h!]
+\scriptsize
+\centering
+\begin{tabular}{ |c|c|c|c| } 
+\hline
+ c & 0 
+ & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
+  & $1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
+ \hline
+ $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
+ & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
+ \hline
+ $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
+ \hline
+ $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ & $\frac{2}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
+ \hline
+\end{tabular}
+\caption{Accuracy Comparison in Theoretical}
+\label{tab_acc_theo}
+\end{table}
+
+The probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.
 

### 2018-12-05 Arxiv/main.tex
update accuracy analysis

@@
 \label{subsec_accuracy_lap}
-If $Y \thicksim Lap(b)$, we have\cite{dwork2014algorithmic}:
-$$
-Pr[|Y| \geq t \cdot b] = e^{- t}.
-$$
-Based on this, we get:
-\begin{equation*}
-Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
-\end{equation*}
-in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.
-
-After post-processing (i.e., taking the floor value of $Y$), we get:
+Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
+Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.\\
+
+Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
 \[
@@
 \]
-when $t < 0$.\\
+when $t < 0$.
 
@@
 
+Given $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:
+
 \begin{itemize}
@@
 \end{itemize}
-In all cases above, probabilities are fixed whenever data size changes.
+In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
 Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.
+
+Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
+
+\begin{itemize}
+  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
+  \item[\textbf{t = 1}]
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
+  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+  \cdot
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
+\end{itemize}
+In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
 
+\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
 For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
-
 \begin{table}[h!]
@@
  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
+ & $\frac{1}{\nomalizer{\dataobs}}$
+ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+ \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
+ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
  \hline
@@
  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & $\frac{2}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
+ & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
+  &$\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
  \hline
@@
 
-The probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.
+When $\epsilon$ and dimensions are fixed, the probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.
+
+By solving following equations:
+\begin{itemize}
+  \item
+\[
+\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
+\]
+we can get the range where we can do better than $\lapmech$ on outputting the correct answer and
+
+\[
+\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
+\]
+we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and
+
+  \item 
+  \item 
+  \item 
+  \item 
+\end{itemize}
 

### 2018-12-13 Arxiv/main.tex
Update main.tex

@@
  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+ & $\frac{1}{\nomalizer{\dataobs}}$ 
+ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
+ \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
-  &$\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
+ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 we can get the range where we can do better than $\lapmech$ on outputting the correct answer and
-
 \[
@@
   \item 
+\[
+\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+ \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+ = 0.11932560927\ or\ 0.11627207896
+\]
+we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
+
   \item 
-  \item 
-  \item 
+\[
+\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+     = 0.07237464051\ or\ 0.04277410743
+\]
+we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one.
+
+  \item Following equations can be in the same way.
 \end{itemize}

### 2018-12-13 Arxiv/main.tex
update main accuracy

@@
 \[
-\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
-\]
-we can get the range where we can do better than $\lapmech$ on outputting the correct answer and
-\[
-\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
-\]
-we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and
+\frac{1}{\nomalizer{\dataobs}} = 0.19673467014\ or\ 0.31606027941
+\]
+we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer.
 

### 2018-12-18 Arxiv/main.tex
update localsensitivity analysis

@@
 
-	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
+	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
 Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
@@
 
-  \item A full proof on applying exponential mechanism to the smooth sensitivity is $(\epsilon, \delta)-$differential privacy is given in paper.
-
-	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
+  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
+
+	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
 \end{itemize}

### 2018-12-18 codes/LocalSensitivityStudy.py

@@ -7,308 +7,86 @@ import scipy
 from scipy.stats import beta
 from fractions import Fraction
 import operator
+import time
+from matplotlib.patches import Polygon
+import statistics
+from decimal import *
+from scipy.special import gammaln
+from dirichlet import dirichlet
+from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 
 
 
+def ratio_of_adj_local_sensitivity(datasizes, prior, beta, delta):
+	ratios = []
+	for datasize in datasizes:
+		ratio_max = 0.0
+		max_position = 0
+		candidates = [[datasize-2,2],[datasize-1,1],[datasize, 0],[0,datasize], [1, datasize - 1], [2, datasize - 2]]
+		candidates = [list(i) for i in numpy.array(candidates) +1]
+		for C in candidates:
+		#########################################################################################################################
+		#GET THE ADJACENT DATA SET OF DATA SET C			
+			C_adj = get_adjacent_set(C)
+				#########################################################################################################################
+				#GET THE PRIVACY LOSS UNDER TWO ADJACENT DATA SET C	AND 		
+			ratio = (1.0 / dirichlet(C_adj)._hellinger_sensitivity() - 1.0 / dirichlet(C)._hellinger_sensitivity())
+			if ratio_max < ratio:
+				ratio_max = ratio
+				max_position = C
 
-def multibeta_function(alphas):
-	numerator = 1.0
-	denominator = 0.0
-	for alpha in alphas:
-		numerator = numerator * math.gamma(alpha)
-		denominator = denominator + alpha
-	# print numerator / math.gamma(denominator)
-	return numerator / math.gamma(denominator)
-
-def optimized_multibeta_function(alphas):
-	denominator = -1.0
-	nominators = []
-	denominators = []
-	r = 1.0
-	for alpha in alphas:
-		denominator = denominator + alpha
-	for alpha in alphas:
-		temp = alpha - 1
-		while temp > 0.0:
-			nominators.append(temp)
-			temp -=1
-		if temp < 0.0:
-			nominators.append(math.gamma(1 + temp))
-	while denominator > 0.0:
[…]

### 2018-12-20 Arxiv/main.tex
update mehcnaisms and structure, including problem statement and motivation, notation

@@
 
-In this work, we design a mechanism for
-bayesian inference exploring the idea of calibrating noise using the
-same probabilistic distance we want to measure accuracy with. 
+In this work, we explore the design space for differentially private bayesian inference, by considering different metrics and different algorithms we design a mechanism. 
 We focus on two discrete models, the Beta-Binomial and the
@@
 simplifies calculations and allows for inference to be performed in a
-recursive fashion over the data.
+recursive fashion over the data. Then, we have:
+\[
+  \bysinfer(\Pr(\dataobs | \theta), \Pr(\theta), \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+\]
 
@@
 where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
-From this it can easily be derived that the posterior distribution is:
-\[
-  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
+From this, the inference can be easily derived:
+\[
+   \bysinfer(binomial(\theta), \betad(\alpha, \beta), \dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
 \]
@@
 with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
-Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
-\[
-  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
+Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the inference over $\vtheta$ turns out to be
+\[
+   \bysinfer(multinomial(\theta), \dirichlet(\valpha), \dataobs)=\dirichlet(\valpha + \Delta \valpha)
 \]
@@
 \label{sec_moti}
-We are interested in designing a mechanism for privately releasing the full posterior
+We are interested in exploring mechanisms for privately releasing the full posterior
 distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
 It's worth noticing that the posterior distributions are fully characterized
-by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
+by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
 Beta-Binomial model we are interested in releasing a private version of the pair of
@@
 $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.
+This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.
 
@@
 come into mind overtly when we are measuring distance between distributions.
-This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
+This gives us motivation on exploring the design space of mechanisms by considering different norms (a distribution metric) to compute the sensitivity
 and provide guarantees on the accuracy.
@@
 Given two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
-\[
-  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
+$\betad(\alpha_1, \beta_1),$ and $\betad(\alpha_2, \beta_2)$ the following equality holds 
+\[
+  \hellinger(\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2))=
   \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
@@
   \item It simplifies calculations in the case of the probabilistic models considered here.
-\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
-an unbounded adversary can have in distingishing two distributions. 
+
+  \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an unbounded adversary can have in distingishing two distributions.
+
   \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity.
 As shown in Fig.
-\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
+\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
 \begin{figure}[ht]
@@
 \label{sec_mechs}
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
-\[
-  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
-\]
-where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
-Notice that $\candidateset$ has $n + 1$ elements, and
-the Bayesian Inference process will produce an element from $\candidateset$
-that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
-parametrize the result by the prior, which from now on we consider
-fixed and we denote it by $\bprior$.
-
-\subsection{Baseline Mechanisms}
-\label{subsec_baselines}
-Baseline Mechanisms are introduced in prior to our mechanism, $\hexpmech$.
-
-\subsubsection{Exponential Mechanism}
-Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+
+\subsection{Laplace Mechanism Family}
+
+\subsubsection{using $\ell_1$ norm metric}
+ Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech(\bysinfer, \dataobs)$, producing an output:
+
+ \[
+\lapmech(\bysinfer, \dataobs) = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \] 
+ where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
+ \[
+ \lapmech(\bysinfer, \dataobs) = \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+ where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
+$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
+
+ We use $ \lapmech(\dataobs) = \betad(\tilde{\alpha}, \tilde{\beta})$ or $\dirichlet(\tilde{\valpha})$ for short. Then release it as the private posterior distribution.
+
+ The sensitivity of the inference process w.r.t. $\ell_1$ norm in $\lapmech$ is:
+ \[
+ \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
+ \]
+ which is proportional to the dimensionality.
+
+\subsubsection{using improved $\ell_1$ norm metric}
+ Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
+Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+
+ Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, then the improved Laplace mechanism $\ilapmech(\bysinfer, \dataobs)$ is producing an output:
+
+ \[
+ \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+ \]
+ where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
+ \[
+ \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \]
+where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
+
+Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+
+\subsection{Exponential Mechanism Family}
+In this section, we explore the exponential mechanism family: $\expmech{}{\cdot}{\cdot}{\cdot}$ by considering Hellinger distance metrics and different sensitivities.
+
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:
+
+\[
+  \candidateset\equiv\{\bysinfer(binomial(\theta), \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
+\]
+For simplicity:
+\[
+  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
+\]
+over all $\dataobs \in \{0,1\}^n$, where $\Delta\alpha$ is as defined in Section \ref{sec_background}, and
+\[
+  \candidateset\equiv\{\dirichlet(\valpha')\mid \valpha'=\valpha + \Delta\valpha\},
+\]
+over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.
+
+We don't explicitly
+parametrize the result by the prior and likelihood, which from now on we consider
+fixed and we denote them by $\bprior$ and $binomial(\theta)$, $multinomial(\theta)$. We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed.
+
+\subsubsection{Standard Exponential Mechanism}
+Standard exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
 \begin{equation*}
@@
 \end{equation*}
-where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
+where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
+the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
 \begin{equation*}
@@
 
-\subsubsection{Exponential Mechanism with Local Sensitivity}
+\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
 \label{subsec_emls}
@@
 
-where $LS(\dataobs)$ is the local sensitivity calculated by:
+where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
 
@@
 
-\subsubsection{Laplace Mechanism}
- Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech$. $\lapmech$ produces an output $r_L$:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \] 
- where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
- where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
-$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
-
- Then release it as the private posterior distribution.
-
- The sensitivity used in this baseline mechanism is:
- \[
- \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
- \]
- which is proportional to the dimensionality.
-
-\subsubsection{Improved Laplace Mechanism}
-
- Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
-Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
-
- Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, then the improved Laplace mechanism $\ilapmech$ is producing an output $r_{IL}$:
-
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \]
- where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
-where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
-
-Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
-\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
+\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity}
 \label{subsec_hexpmech}
 
-\subsubsection{$\gamma$-Smooth Sensitivity}
-\label{sec_mechs}
-
 \begin{definition}
-Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:
-
+\label{def_gamma_smooth}
+Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
+\begin{equation}
+  \label{eq_smooth}
+   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
+\end{equation}
+where $d$ is the Hamming distance between two data sets.
+\end{definition}
+
+\begin{thm}
+\label{thm_gamma_smooth}
+Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:\\
 For any $\adj{\dataobs}{\dataobs'}$:
@@
 
-$S(\dataobs)$ is $\gamma -$smooth sensitivity.
-
-\end{definition}
-
-\begin{thm}
-\label{thm_gamma_smooth}
-Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
-\begin{equation}
-  \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
-\end{equation}
-where $d$ is the Hamming distance between two data sets.
 \end{thm}
@@
 
-\subsubsection{$\hexpmech$ Proposition}
-
 \begin{definition}
@@
 \end{equation*}
-where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
+where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Definition \ref{def_gamma_smooth} by setting $\gamma = 1$.
 \end{definition}
 
-This mechanism is based on the standard exponential mechanism
-\cite{talwar}, with $\candidateset$ as the range and
-$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
-that in this mechanism we don't calibrate the noise w.r.t. to the
-global sensitivity of the scoring function but w.r.t. to the smooth
-sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
-$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
-sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.
-
-This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
+Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
 \[
@@
 The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
-
-\subsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
+\subsection{Privacy of Laplace Mechanism Family}
+Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+
+\subsection{Privacy of Exponential Mechanism Family}
+\subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
+Standard exponential mechanism in $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+
+\subsubsection{$\expmech{local}{}{}{}$ non-Differential Privacy}
+Exponential mechanism with local sensitivity non-differential privacy.
+
+\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
 
@@
 The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
+\ref{sec_mechs}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
 can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
@@
 it represents the performance of a variation of the basic Laplace
-mechanism presented in Section (\ref{subsec_baselines}) with the same
+mechanism presented in Section (\ref{sec_mechs}) with the same
 settings: that is $\epsilon, \delta$, data, prior. The variation

### 2018-12-20 codes/privacyloss.py

@@ -126,8 +126,21 @@ def plot_privacyloss(x, y, label):
 #########################################################################################################################	
 def privacy_loss_in_denumerator(datasizes, epsilon, delta, prior):
 	loss_in_nomalizer = []
+	max_loss = 0.0
 	for datasize in datasizes:
-		loss_in_nomalizer.append(denumerator_privacy_loss_one_pair(datasize,epsilon,delta,prior,[datasize-1,1],[datasize,0]))
+		candidates = [[datasize-2,2],[datasize-1,1],[datasize, 0],[0,datasize], [1, datasize - 1], [2, datasize - 2]]
+
+		for C in candidates:
+		#########################################################################################################################
+		#GET THE ADJACENT DATA SET OF DATA SET C			
+			C_adj = get_adjacent_set(C)
+				#########################################################################################################################
+				#GET THE PRIVACY LOSS UNDER TWO ADJACENT DATA SET C	AND 		
+			loss = denumerator_privacy_loss_one_pair(datasize,epsilon,delta,prior,C,C_adj)
+			if abs(max_loss) < abs(loss):
+				max_loss = loss
+
+		loss_in_nomalizer.append(max_loss)
 
 	plot_privacyloss(datasizes, loss_in_nomalizer, "in denumerator")
 
@@ -237,9 +250,9 @@ if __name__ == "__main__":
 	prior = dirichlet([1,1])
 	dataset = [50,50]
 	epsilons = numpy.arange(0.1, 2, 0.1)
-	datasizes = gen_datasizes((2,20),2) + gen_datasizes((25,100),10) + gen_datasizes((100,500), 100) + gen_datasizes((1000,5000),1000)  + gen_datasizes((10000,50000),10000)
+	datasizes = gen_datasizes((100000,500000),100000)# gen_datasizes((10,20),2) + gen_datasizes((25,100),10) + gen_datasizes((100,500), 100) + gen_datasizes((1000,5000),1000)  + gen_datasizes((10000,50000),10000) + 
 	# datasizes =  gen_datasizes((15,50),10)
-	percentage = [0.5,0.5]
+	percentage = [0.1,0.9]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = [dirichlet([1,1])] + gen_priors([5,20], 5, 2) + gen_priors([40,100], 20, 2) + gen_priors([150,300], 50, 2) + gen_priors([400,400], 50, 2)
 	privacy_loss(datasizes,epsilon,delta,prior)

### 2018-12-27 ICML2019/main.tex
convert template into ICML 2019

--- 2018-12-20 Arxiv/main.tex
@@
 \input{macros}
+\icmltitlerunning{Exploring Design Space for Differentially Private Bayesian Inference}
 
 \begin{document}
-\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
-
-\author[*]{Jiawen Liu}
-\author[**]{Mark Bun}
-\author[*]{Gian Pietro Farina}
-\author[*]{Marco Gaboardi}
-\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
-\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
-\date{}
-\maketitle
-{\footnotesize \tableofcontents}
-
-\newpage
+
+\twocolumn[
+\icmltitle{Exploring Design Space for Differentially Private Bayesian Inference}
+
+% It is OKAY to include author information, even for blind
+% submissions: the style file will automatically remove it for you
+% unless you've provided the [accepted] option to the icml2019
+% package.
+
+% List of affiliations: The first argument should be a (short)
+% identifier you will use later to specify author affiliations
+% Academic affiliations should list Department, University, City, Region, Country
+% Industry affiliations should list Company, City, Region, Country
+
+% You can specify symbols, otherwise they are numbered in order.
+% Ideally, you should not use this facility. Affiliations will be numbered
+% in order of appearance and this is the preferred way.
+\icmlsetsymbol{equal}{*}
+
+\begin{icmlauthorlist}
+\icmlauthor{Jiawen Liu}{to}
+\icmlauthor{Mark Bun}{ed}
+\icmlauthor{Gian Pietro Farina}{to}
+\icmlauthor{Marco Gaboardi}{to}
+\end{icmlauthorlist}
+
+\icmlaffiliation{to}{Department of Computer Science and Engineering, University at Buffalo, SUNY, New York, United State}
+\icmlaffiliation{ed}{Princeton University, United State}
+
+% \icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
+% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+
+% You may provide any keywords that you
+% find helpful for describing your paper; these are used to populate
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{Machine Learning, ICML}
+
+\vskip 0.3in
+]
+
+\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
+
 \begin{abstract} Bayesian inference is a statistical method which
@@
 \centering
-\includegraphics[width=0.8\textwidth]{efficiency}
+\includegraphics[width=0.45\textwidth]{efficiency}
 \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
@@
   \subfigure[2 dimensions of data size 1000]{
-    \includegraphics[width=0.45\textwidth]{epsilon5_2d_1000.eps}
+    \includegraphics[width=0.42\textwidth]{epsilon5_2d_1000.eps}
   \label{subfig_theory_2d}
@@
   \subfigure[2 dimensions of data size 10000]{
-    \includegraphics[width=0.45\textwidth]{epsilon5_2d_10000.eps}
+    \includegraphics[width=0.42\textwidth]{epsilon5_2d_10000.eps}
   \label{subfig_theory_3d}
@@
 \centering
-    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
+    \includegraphics[width=0.45\textwidth]{sampling_2d.eps}
 \caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$}
@@
 {
-        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
+        \includegraphics[width=0.42\textwidth]{sampling_3d.eps} 
         \label{fig_vs_datasize_3d}
@@
 {
-     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
+     \includegraphics[width=0.42\textwidth]{sampling_4d.eps} 
 \label{fig_vs_datasize_4d}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{sampling_prior.eps}
+\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
 \caption{Observed data set is: $(50,50)$, varying balanced priors}
@@
 \centering
-    \includegraphics[width=0.6\textwidth]{privacyloss.eps}
+    \includegraphics[width=0.48\textwidth]{privacyloss.eps}
 \caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
@@
 
-\bibliographystyle{plain}
-\bibliography{bayesian.bib}
+\bibliography{bysinfer}
+\bibliographystyle{icml2019}
 

### 2018-12-27 ICML2019/main.tex
update algorithms and Accuracy

@@
 
-\noindent \textbf{Related Work.}
-
-A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
-
-In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
-3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
-The third topic where our work focus on is still very new.
-
 \section{Preliminaries}
@@
 
-\section{Technical Problem Statement and Motivations}
+\section{Problem Statement}
 \label{sec_moti}
@@
  where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
- \[
- \lapmech(\bysinfer, \dataobs) = \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
+ \begin{equation*}
+ \begin{split}
+ & \lapmech(\bysinfer, \dataobs) = \\
+ & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+ \end{split}
+ \end{equation*}
  where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
@@
 \begin{equation*}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
 \end{equation*}
@@
   {\unomalizer{\dataobs}}
-  \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
+  \\
+  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
   \end{split}
@@
   } 
-  {\unomalizer{\dataobs}}
-  \exp
+  {\unomalizer{\dataobs}}\\
+  & \cdot \exp
   \big(
@@
   }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
+  & \cdot 
   \frac {
@@
 
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
   \begin{equation*}
@@
   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{2}
+  \big)}\\
+  & \cdot\frac{1}{
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
   \big)
@@
   \big)
-  }\\
+  }
   \end{split}
@@
   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
+  \big)}\\
+  & \cdot \frac{1}{
   \exp 
@@
 Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.\\
+Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
 
@@
 \]
-when $t \geq 0$, and\\
+when $t \geq 0$, and
 \[
@@
 & Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
+& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
 \end{array}
@@
 & Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-= \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
+= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
+& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
 \end{array}
@@
 %  \end{align*}
-Unfolding the Hellinger distance formula($\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$), we get:
-\begin{itemize}
-  \item[\textbf{case}] \textbf{t is even}\\
+Unfolding the Hellinger distance formula, we get:\\
+  \noindent \textbf{case: t is even}\\
   \begin{align*}
-  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
-  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
@@
 
-  \item[\textbf{case}] \textbf{t is odd}\\
+  \noindent \textbf{case: t is odd}\\
   let $t = 2 m + 1$
   \begin{align*}
-  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 =
-  \qquad &
+  & Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
+  & =
   1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
@@
   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+  = & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
   \end{align*}
 
-\end{itemize}
-
-Given $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:
-
-\begin{itemize}
-  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
-  \item[\textbf{t = 1}]
+Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:
+
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
+
   $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.
-  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
   \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
-\end{itemize}
+
 In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
@@
 
-\begin{itemize}
-  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
-  \item[\textbf{t = 1}]
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
+
   $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$.
-  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
   \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
-\end{itemize}
+
 In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
@@
   we have following formula for accuracy:
-  \begin{align}
+  \begin{align*}
   \label{eq_acc}
-  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
+  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
   = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
-  \end{align}
-  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
+  \end{align*}
+
+  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
 
@@
 \[
-\frac{1}{\nomalizer{\dataobs}} = 0.19673467014\ or\ 0.31606027941
+\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
 \]
@@
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
- = 0.11932560927\ or\ 0.11627207896
+ = 0.119325609\ or\ 0.116272079
 \]
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
-
+\vspace{12cm}
   \item 
@@
     {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-     = 0.07237464051\ or\ 0.04277410743
+     = 0.072374641\ or\ 0.042774107
 \]
@@
 
-\section{Conclusion and Future Work}
+\section{Related Work}
+
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
+
+In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+\cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
+3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
+The third topic where our work focus on is still very new.
+
+\section{Conclusion}
 From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:
@@
 
-These results although very motivating, are still not enough for real world applications. Hence, we will continue our work in the follwoing directions:
-\begin{enumerate}
-  \item  For now, we just have a intuitive idea on the accuracy
-behavior of our mechanisms, and not a precise formula or bound on
-it. When do our mechanisms perform better than the baseline mechanism
-and when they don't? How much influence will elements in Section
-\ref{sec_experiment} have on the accuracy? Are there any other
-important factors we missed? These are all questions w.r.t. the
-accuracy that we are going to explore next, and in a more principled
-and formal way.
-\item  Theorem \ref{lem_hexpmech_privacy} provides an upper bound on the
-privacy loss for $\hexpmech$ and $\hexpmechd$ but not necessarily a
-tight one. Indeed, experiments have shown that the actual privacy loss
-in the experiments can be smaller than $\epsilon$. This means that we
-could improve accuracy, by adding less noise -- that is noise
-proportional to a higher value of $\epsilon$-- but still achieve
-$(\epsilon, \delta)$-dp.
-\item The choice of the Hellinger distance might seem quite
-ad-hoc. Hence, it is worth exploring other distances over
-distributions. An interesting class of probability metrics is the
-family of $f$-divergences \cite{CIT-004}.
-\end{enumerate}
-
 \bibliography{bysinfer}

### 2018-12-27 ICML2019/main.tex
update abstract and conclusion

@@
 Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
-Our mechanism can be understood as a version of  the exponential mechanism
-where the noise is calibrated to the smooth sensitivity of the
-utility function, rather than to its global sensitivity. In our
-setting, the utility function is the probability distance we want to
-use to measure accuracy. To show the usefulness of this mechanism we
-show an experimental analysis comparing it with mechanisms based on
-the Laplace mechanism.
+For different algorithms, we explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
+For different metrics, we apply them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
+use to measure accuracy. To show the usefulness of these mechanisms we
+show an experimental analysis comparing their performance.
 \end{abstract}
@@
 
-\section{Preliminaries}
+\section{Problem Setting}
+
+\subsection{Preliminaries}
 \label{sec_background}
@@
 
-\section{Problem Statement}
-\label{sec_moti}
+\subsection{Technical Problem Statement}
+\label{subsec_problem}
 We are interested in exploring mechanisms for privately releasing the full posterior
@@
  Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech(\bysinfer, \dataobs)$, producing an output:
-
- \[
-\lapmech(\bysinfer, \dataobs) = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \] 
+$$
+\begin{array}{rcl}
+& \lapmech(\bysinfer, \dataobs) \\
+& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+\end{array} 
+$$
  where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
- \begin{equation*}
- \begin{split}
+$$
+\begin{array}{rcl}
  & \lapmech(\bysinfer, \dataobs) = \\
- & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \end{split}
- \end{equation*}
+ & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
+ & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+\end{array} 
+$$
  where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
@@
 
- \[
- \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
- \]
+$$
+\begin{array}{rcl}
+& \ilapmech(\bysinfer, \dataobs) \\
+& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
+\end{array} 
+$$
  where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
- \[
- \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
- \]
+$$
+\begin{array}{rcl}
+ & \ilapmech(\bysinfer, \dataobs) = \\
+ & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
+ & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
+\end{array} 
+$$
 where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
@@
 The third topic where our work focus on is still very new.
+moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism.
+That's why we explore different metrics and different algorithms over the design space.
 
 \section{Conclusion}
-From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:
-
-\begin{enumerate}
-	\item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
-  	\item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
-\end{enumerate}
+From what we have seen in the previous sections we can obtain following conclusions.
+We explored the design space of the mechanisms for differentially privacy Bayesian inference, by considering different metrics and different algorithms.
+\begin{itemize}
+  \item The accuracy can change a lot when considering different metrics and using different sensitivity values.
+  \item Different algorithms have different performance w.r.t.
+different aspect.
+From the experimental results, Laplace mechanism family have a good efficiency and accuracy when using $\ell_1$ norm metric.
+But exponential mechanism family can be a good application when considering different metrics.
+\end{itemize}
 

### 2018-12-27 ICML2019/main.tex
fix bug

@@
 
-\subsubsection{Standard Exponential Mechanism}
+\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
 Standard exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:

### 2018-12-27 ICML2019/main.tex
fix bug

@@
 \label{def_epsilon_dp}
-$\epsilon-$differential privacy.
-
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
-\begin{equation*}
-\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
-\end{equation*}
-
-\end{definition}
-
-\begin{definition}
-\label{def_epsilon_delta_dp}
-$(\epsilon,\delta)-$differential privacy.
-
-A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
-\begin{equation*}
-\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
-\end{equation*} 
+
+A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ is $(\epsilon, \delta)-$differential privacy, if for all adjacent
+\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subset Range(\mathcal{M})$:
+\begin{equation*}
+\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] = e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
+\end{equation*}
+
 \end{definition}
@@
 \subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
-Standard exponential mechanism in $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
 

### 2018-12-28 ICML2019/main.tex
fix bug
update plots

@@
 
-\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
+\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}
 
@@
 \end{lem}
-
 \begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
@@
 
-We consider 6 mechanisms in our comparison, including the Laplace mechanism, improved Laplace mechanism, standard exponential mechanism, non-private exponential mechanism (using local sensitivity) and two newly designed mechanisms (one with smooth sensitivity achieving $(\epsilon, \delta)-$dp and the other with $\gamma$ sensitivity achieving $\epsilon-$dp).
+We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$), standard exponential mechanism ($\mathsf{expMech}$), non-private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
 

### 2018-12-28 codes/discrete_probability_on_betabinomial.py

@@ -199,15 +199,15 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#SUM UP the prob within the same bin
 	#############################################################################
 
-	exp = calculate_prob_exp(Candidate_bins_by_step, Bayesian_Model, mechanism_parameter = 4, 
-		sensitivity = Bayesian_Model._SS, savename = "_exp.txt")
+	# exp = calculate_prob_exp(Candidate_bins_by_step, Bayesian_Model, mechanism_parameter = 4, 
+	# 	sensitivity = Bayesian_Model._SS, savename = "_exp.txt")
 
 
 	#############################################################################
 	#SUM UP the prob within the same bin
 	#############################################################################
 
-	exp_new = calculate_prob_exp(Candidate_bins_by_step, Bayesian_Model, mechanism_parameter = 4,
+	exp_gamma = calculate_prob_exp(Candidate_bins_by_step, Bayesian_Model, mechanism_parameter = 4,
 		sensitivity = Bayesian_Model._alpha_SS, savename = "_exp_new.txt")
 
 
@@ -255,12 +255,11 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 
 	labels = [
-		r'$\mathcal{M}_{\mathcal{H}}$ with Smooth Sensitivity',
-		r'$\mathcal{M}_{\mathcal{H}}$ with $\gamma -$Sensitivity',
-		r"NON PRIVATE $\mathcal{M}_{\mathcal{E}}$",
-		r"STANDARD $\mathcal{M}_{\mathcal{E}}$",
-		'IMPROVED LapMech (sensitivity ='+ str(sensitivity1) +')', 
-		'LapMech (sensitivity = '+ str(sensitivity1) +')']
+		r'$\mathsf{expMech}^{smoo}$ ',
+		r"$\mathsf{expMech}^{local}$",
+		r"$\mathsf{expMech}$",
+		r'$\mathsf{ilapMech}$ (sensitivity = '+ str(sensitivity1) +')', 
+		r'$\mathsf{lapMech}$ (sensitivity = '+ str(sensitivity1) +')']
 
 
 	#############################################################################
[…]

### 2018-12-28 codes/discrete_probability_on_betabinomial.py
update experiments

@@ -259,7 +259,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 		r"$\mathsf{expMech}^{local}$",
 		r"$\mathsf{expMech}$",
 		r'$\mathsf{ilapMech}$ (sensitivity = '+ str(sensitivity1) +')', 
-		r'$\mathsf{lapMech}$ (sensitivity = '+ str(sensitivity1) +')']
+		r'$\mathsf{lapMech}$ (sensitivity = '+ str(sensitivity2) +')']
 
 
 	#############################################################################
@@ -367,7 +367,7 @@ if __name__ == "__main__":
 	#SETTING UP THE PARAMETERS
 	#############################################################################
 	datasize = 600
-	epsilon = 5.0
+	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1,1])
 	dataset = [200,200,200]

### 2018-12-28 codes/privacyloss.py

@@ -112,8 +112,8 @@ def denumerator_privacy_loss_one_pair(datasize,epsilon,delta,prior, x1, x2):
 #########################################################################################################################			
 def plot_privacyloss(x, y, label):
 	plt.figure()
-	plt.title(("PRIVACY LOSS " + label))
-	plt.plot(x,y, 'bo-', label=(r'Exp Mech with $\gamma$ Sensitivity ($\frac{\epsilon}{4}$)'))
+	plt.title(("PRIVACY LOSS" + label))
+	plt.plot(x,y, 'bo-', label=(r'$\mathsf{expMech}^{smoo}$'))
 	plt.xlabel("Data Size")
 	plt.ylabel(r"privacy loss " + label)
 	plt.grid()

### 2018-12-28 ICML2019/main.tex
update experiments

@@
 \subsection{Exponential Mechanism Family}
-In this section, we explore the exponential mechanism family: $\expmech{}{\cdot}{\cdot}{\cdot}$ by considering Hellinger distance metrics and different sensitivities.
+In this section, we explore the exponential mechanism family: $\expmech(\cdot,\cdot,\cdot)$ by considering Hellinger distance metrics and different sensitivities.
 
@@
 \subsubsection{Standard Exponential Mechanism with Hellinger Metric}
-Standard exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+Standard exponential mechanism $\expmech(x,u,\candidateset)$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
+\begin{equation*}
+\underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 GS})}
@@
 % \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism.
+Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$ share the same candidate set and utility function as it with standard exponential mechanism.
 This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
@@
 \subsection{Privacy of Exponential Mechanism Family}
-\subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
+\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
 Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
 
-\subsubsection{$\expmech{local}{}{}{}$ non-Differential Privacy}
+\subsubsection{$\lexpmech$ non-Differential Privacy}
 Exponential mechanism with local sensitivity non-differential privacy.
@@
 LS(\dataobs) 
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
   & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
@@
 \centering
-  \subfigure[2 dimensions with data size $600$]{
-    \includegraphics[width=0.45\textwidth]{theory_2d.eps}
+  \subfigure[2 dimensions, data size $600$]{
+    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
   \label{subfig_theory_2d}
   }
-  \subfigure[3 dimensions with data size $600$]{
-    \includegraphics[width=0.45\textwidth]{theory_3d.eps}
+  \subfigure[3 dimensions, data size $600$]{
+    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
   \label{subfig_theory_3d}
@@
 
-In Fig.
-\ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line).
-This means $\hexpmech$ can produce good results with larger probability than baseline mechanism.
-However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$.
-It outperforms $\hexpmech$.
+Candidates of smaller distance from true posterior are considered to be good results, which can result in good accuracy.
+From Fig.
+\ref{fig_theory}, it can be derived that all these mechanisms (except standard exponential mechanism $\expmech$ in green line) can output good results with larger probability.
+The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non-private.
+For these are $\epsilon -$differentially private, the improved laplace mechanism $\ilapmech$ with $\ell_1$ norm metric can produce good results with higher probability, i.e., perform better in terms of accuracy than others.
+As the dimension increases from 2 to 3, mechanisms' behavior remain the same.
 
@@
 \centering
-  \subfigure[2 dimensions of data size 1000]{
-    \includegraphics[width=0.42\textwidth]{epsilon5_2d_1000.eps}
+  \subfigure[data size 1000]{
+    \includegraphics[width=0.22\textwidth]{epsilon5_2d_1000.eps}
   \label{subfig_theory_2d}
   }
-  \subfigure[2 dimensions of data size 10000]{
-    \includegraphics[width=0.42\textwidth]{epsilon5_2d_10000.eps}
+  \subfigure[data size 10000]{
+    \includegraphics[width=0.22\textwidth]{epsilon5_2d_10000.eps}
   \label{subfig_theory_3d}
   }
-\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$}
+\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$, in 2 dimensions}
 \label{fig_theory_epsilon}
@@
 \end{figure}
-Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig. \ref{fig_theory_epsilon}. In 2 dimensions, we can perform better than Laplace mechanisms.
+
+Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig.
+\ref{fig_theory_epsilon} in 2 dimensions.
+The $\lexpmech$ is still the one with the best accuracy, but it is non-private.
+However, the $\lapmech$ and $\ilapmech$ having the similar performance, and $\hexpmech$ can produce the correct posterior with higher probability than the others.
+And the standard exponential mechanism $\expmech$ is still the worst one.
 
@@
 
-\begin{figure}
-\begin{center}
-\centering
-    \includegraphics[width=0.45\textwidth]{sampling_2d.eps}
-\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$}
-\label{fig_vs_datasize_2d}
-\end{center}
-\end{figure}
-
 \begin{figure}[ht]
@@
 \centering
+\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
+{ \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
+\label{fig_vs_datasize_2d}
+}
+
 \subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
 {
-        \includegraphics[width=0.42\textwidth]{sampling_3d.eps} 
+  \includegraphics[width=0.4\textwidth]{sampling_3d.eps} 
   \label{fig_vs_datasize_3d}
@@
 {
-     \includegraphics[width=0.42\textwidth]{sampling_4d.eps} 
+  \includegraphics[width=0.4\textwidth]{sampling_4d.eps} 
   \label{fig_vs_datasize_4d}
@@
 \end{figure}
-
-% \begin{figure}[ht]
-% \begin{center}
-% \centering
-
-% \end{center}
-% \end{figure}
 

### 2018-12-29 ICML2019/main.tex
update experiments

@@
 difference of medians; The whiskers extend from the box to show the
-range of the data. A blue box in the plots represents our newly
-designed exponential mechanism's behavior-- where the sensitivity is calibrated
-w.r.t Hellinger distance-- while the yellow box next to
+range of the data. A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
+w.r.t Hellinger distance-- while the green box next to
 it represents the performance of a variation of the basic Laplace
-mechanism presented in Section (\ref{sec_mechs}) with the same
-settings: that is $\epsilon, \delta$, data, prior. The variation
+mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
+settings: that is $\epsilon$, data, prior. The variation
 considered performs a postprocessing on the released parameters so

### 2018-12-29 ICML2019/main.tex
update experiments

@@
 \subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
-{ \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
+{ \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
 \label{fig_vs_datasize_2d}
@@
 {
-  \includegraphics[width=0.4\textwidth]{sampling_3d.eps} 
+  \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
   \label{fig_vs_datasize_3d}
@@
 {
-  \includegraphics[width=0.4\textwidth]{sampling_4d.eps} 
+  \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
   \label{fig_vs_datasize_4d}
@@
 of observations. The results show that when the data size increases, the average errors of
-$\hexpmech$, Laplace mechanism and decrease. For small datasets,
-i.e with size less $300$ in the case of Beta-Binomial models,
-both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
+$\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
+i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
 But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
 we considered data sets of the order of 15 thousands elements,
-the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
+the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
 Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
@@
 \centering
-\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
+\includegraphics[width=0.35\textwidth]{sampling_prior.eps}
 \caption{Observed data set is: $(50,50)$, varying balanced priors}
@@
 \centering
-    \includegraphics[width=0.48\textwidth]{privacyloss.eps}
+    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
 \caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}

### 2019-01-03 ICML2019/main.tex
pass on section 2

@@
 \begin{abstract} Bayesian inference is a statistical method which
-allows one to derive a \emph{posterior} distribution,
+allows to derive a \emph{posterior} distribution,
 starting from a \emph{prior} distribution and observed data. Several
 approaches have been explored in order to make this process differentially
-private. For example, \cite{dimitrakakis2014robust}, and
+private. For example \cite{dimitrakakis2014robust} and
 \cite{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
+the posterior distribution is already differentially private, while \cite{zhang2016differential} and \cite{foulds2016theory}
 designed differentially private mechanisms that output a
@@
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
-and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
-\[
-  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is defined as:
+\[
+  \Pr(\theta | \dataobs) \equiv \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
 \]
@@
 prior distributions and likelihood functions are usually chosen so that the posterior
-belongs to the same \emph{family} of distributions. In this case we say that the prior
+belongs to the same \emph{family} of distribution of the prior. In this case we say that the prior
 is conjugate to the likelihood function. Use of a conjugate prior
 simplifies calculations and allows for inference to be performed in a
-recursive fashion over the data. Then, we have:
-\[
-  \bysinfer(\Pr(\dataobs | \theta), \Pr(\theta), \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
-\]
+recursive fashion over the data.
+% Then, we have:
+% \[
+%   \bysinfer(\Pr(\dataobs | \theta), \Pr(\theta), \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+% \]
 
@@
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-specifically, a Beta-binomial mode. We will consider the situation the underlying data is binomial distribution ($\thicksim binomial(\theta)$), where $\theta$ represents
+We will consider the situation where the underlying data is drawn from a binomial distribution
+($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
 the parameter --informally called \emph{bias}-- of a Bernoulli
-distributed random variable. The
+distributed random variable and $n$ is the number of draws. The
 prior distribution over $\theta\in [0,1]$ is going to be a beta
@@
 where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
-From this, the inference can be easily derived:
-\[
-   \bysinfer(binomial(\theta), \betad(\alpha, \beta), \dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
-\]
+The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
+From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
+posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
+in section \ref{} when the private mechanisms will be described.
 
@@
 
-The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data multinomially distributed.
-The \emph{bias} is represented by parameter $\vtheta$, the vector of parameters of a categorically distributed random variable.
-The prior distribution over $\vtheta\in [0,1]^{k}$
-is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
+The beta-binomial model can be immediately generalized to the Dirichlet-multinomial model, with underlying data multinomially distributed.
+The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
+is given by a Dirichelet distribution, $\dirichlet{n}{\valpha}$, for $k\in\mathbb{N}$,
 and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
@@
 with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
-Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the inference over $\vtheta$ turns out to be
-\[
-   \bysinfer(multinomial(\theta), \dirichlet(\valpha), \dataobs)=\dirichlet(\valpha + \Delta \valpha)
+Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
+\[
+   \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)=\dirichlet{\valpha + \Delta \valpha} 
 \]
@@
 
-A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ is $(\epsilon, \delta)-$differential privacy, if for all adjacent
-\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subset Range(\mathcal{M})$:
-\begin{equation*}
-\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] = e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
+A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ and range $\range$, is $(\epsilon, \delta)$-differential privacy, if for all adjacent
+\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
+\begin{equation*}
+\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] \leq e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
 \end{equation*}
@@
 
-However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
+However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
 \[
@@
 where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
-This accuracy metric is meaningless when the results released are distributions rather than numerical values.
-In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc.
-come into mind overtly when we are measuring distance between distributions.
-This gives us motivation on exploring the design space of mechanisms by considering different norms (a distribution metric) to compute the sensitivity
-and provide guarantees on the accuracy.
-
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
-Given two beta distributions
-$\betad(\alpha_1, \beta_1),$ and $\betad(\alpha_2, \beta_2)$ the following equality holds 
-\[
-  \hellinger(\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2))=
+\todo{This
+accuracy metric is meaningless when the results released are
+distributions rather than numerical values. In contrast, distribution
+metrics such as $f$-divergence, Hellinger distance, etc. come into
+mind overtly when we are measuring distance between
+distributions. }
+{\color{blue}im not sure this is a good way to put it...}
+This gives us motivation on exploring the design space
+of mechanisms by considering different norms (a distribution metric)
+to compute the sensitivity and provide guarantees on the accuracy.
+
+We will use the Hellinger distance $\hellinger(\cdot,\cdot)$, 
+Given two probability distributions $\textup{P}$ and $\textup{Q}$,
+the Hellinger distance between them is defined as:
+\[
+\todo{def}
+\]
+When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above reduces to: 
+\[
   \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
@@
 
-  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity.
-As shown in Fig.
-\ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
+  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity},
+    taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
 \begin{figure}[ht]

### 2019-01-04 ICML2019/main.tex
update abstract

@@
 private. For example \cite{dimitrakakis2014robust} and
-\cite{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private, while \cite{zhang2016differential} and \cite{foulds2016theory}
+\cite{wang2015privacy} proved the differentially privacy ofsampling from
+the posterior distribution under specific conditions, \cite{zhang2016differential} and \cite{foulds2016theory}
 designed differentially private mechanisms that output a
 representation of the full posterior distribution. 
-
-When the output of a differentially private mechanism is a probability
-distribution, accuracy is naturally measured by means of
-\emph{probabilistic distances} measuring how far this distribution is
-from the original one. Some classical examples are total variation distance,
-Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
-
-In this work, we explore the design space for differentially private bayesian inference, by considering different metrics and different algorithms we design a mechanism. 
-We focus on two discrete models, the Beta-Binomial and the
+% When the output of a differentially private mechanism is a probability
+% distribution, accuracy is naturally measured by means of
+% \emph{probabilistic distances} measuring how far this distribution is
+% from the original one. Some classical examples are total variation distance,
+% Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
+Laplace mechanism is mostly used while exponential mechanisms have not yet been fully explored.
+Also, $\ell_1$ norm is mainly used to measure the accuracy while \emph{probabilistic distances} are more suitable when the output of a differentially private mechanism is a probability distribution.
+
+In this work, we explore the design space for differentially private bayesian inference mechanism, by considering different metrics and different algorithms. 
+We focused on two discrete models, the Beta-Binomial and the
 Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
-For different algorithms, we explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
-For different metrics, we apply them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
+We explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
+Also, we apply different metric them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
 use to measure accuracy. To show the usefulness of these mechanisms we

### 2019-01-04 ICML2019/main.tex
update abstract

@@
 private. For example \cite{dimitrakakis2014robust} and
-\cite{wang2015privacy} proved the differentially privacy ofsampling from
+\cite{wang2015privacy} proved the differential privacy of sampling from
 the posterior distribution under specific conditions, \cite{zhang2016differential} and \cite{foulds2016theory}
-designed differentially private mechanisms that output a
-representation of the full posterior distribution. 
+designed differentially private (DP) mechanisms for this inference process. 
 % When the output of a differentially private mechanism is a probability
@@
 Laplace mechanism is mostly used while exponential mechanisms have not yet been fully explored.
-Also, $\ell_1$ norm is mainly used to measure the accuracy while \emph{probabilistic distances} are more suitable when the output of a differentially private mechanism is a probability distribution.
-
-In this work, we explore the design space for differentially private bayesian inference mechanism, by considering different metrics and different algorithms. 
+Also, $\ell_1$ norm is mainly used to measure the accuracy while \emph{probabilistic distances} are more suitable when the output of a DP mechanism is a probability distribution.
+
+In this work, we explore the design space for DP bayesian inference, by considering different metrics and different algorithms. 
 We focused on two discrete models, the Beta-Binomial and the
-Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
-We explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
-Also, we apply different metric them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
+Dirichlet-multinomial models, and one distribution distance, Hellinger distance. 
+We design mechanisms based on the Laplace algorithm and exponential algorithm and adopt different metrics in them by calibrating noise to the sensitivity of metric that we want to
 use to measure accuracy. To show the usefulness of these mechanisms we
-show an experimental analysis comparing their performance.
+show experimental analysis on their performance.
 \end{abstract}

### 2019-01-04 ICML2019/main.tex
another pass

--- 2019-01-03 ICML2019/main.tex
@@
 
-\begin{abstract} Bayesian inference is a statistical method which
-allows to derive a \emph{posterior} distribution,
-starting from a \emph{prior} distribution and observed data. Several
-approaches have been explored in order to make this process differentially
-private. For example \cite{dimitrakakis2014robust} and
-\cite{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private, while \cite{zhang2016differential} and \cite{foulds2016theory}
-designed differentially private mechanisms that output a
-representation of the full posterior distribution.
-
-When the output of a differentially private mechanism is a probability
-distribution, accuracy is naturally measured by means of
-\emph{probabilistic distances} measuring how far this distribution is
-from the original one. Some classical examples are total variation distance,
-Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
-
-In this work, we explore the design space for differentially private bayesian inference, by considering different metrics and different algorithms we design a mechanism. 
-We focus on two discrete models, the Beta-Binomial and the
-Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
-For different algorithms, we explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
-For different metrics, we apply them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
-use to measure accuracy. To show the usefulness of these mechanisms we
-show an experimental analysis comparing their performance.
+\begin{abstract}
+% Several approaches have been explored in order to make Bayesian inference
+% differentially private.
+% For instance, \cite{dimitrakakis2014robust} and
+% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
+% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
+% designed differentially private (d.p.) mechanisms by adding laplacian noise
+% to the numeric parameters of the posterior distributions. 
+% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
+% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
+% of the released posterior distribution and the actual real ones of posterior distribution.
+We explore the design space for differentially private Bayesian
+inference.  We focused on two discrete models for parametric Bayesian
+inference i.e., the Beta-Binomial and the Dirichlet-multinomial
+models. We propose a variation of the exponential mechanism that uses
+a scoring function based on a metric over probailistic measures, i.e.,
+the Hellinger distance. We compare it with other approaches based on
+the perturbation of the parameters of the posterior distribution.  We
+measure the accuracy using the Hellinger distance over the posterior
+distribution released and the real one as opposed to measuring the
+$\ell_1$ or $\ell_{\infty}$ distance on the parameters.  We finally
+present an experimental analysis on the accuracy of these mechanisms.
 \end{abstract}
@@
 
-\section{Problem Setting}
-
-\subsection{Preliminaries}
+\section{Preliminaries}
 \label{sec_background}
-
-\noindent \textbf{Bayesian Inference.}
-
+\noindent \textbf{Bayesian inference.} 
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
@@
 % \]
-
-\noindent \textbf{Beta-binomial System.}
-
+% \noindent \textbf{Beta-binomial System.}
 In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
@@
 in section \ref{} when the private mechanisms will be described.
-
-\noindent \textbf{Dirichlet-multinomial Systems.}
+% \noindent \textbf{Dirichlet-multinomial Systems.}
 
@@
 \noindent \textbf{Differential Privacy.}
+\emph{Differential privacy} is a strong quantitative notion of statistical privacy proposed by \cite{}.
+Differential privacy of a mechanism implies that changing the input of a mechanism slightly only reflects
+in a controlled and bounded way on the output distribution. 
+Formally, the $\epsilon$ parameter
+controls how much two outputs starting from \emph{close} inputs can differ. When two inputs are close we call them \emph{adjacent}.
+By adjacency we usually mean a relation over input databases which includes all the pair of databases which differ by at most one row.
+The formal definition of $\epsilon$-differential privacy follows.
 \begin{definition}
@@
 
-A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ and range $\range$, is $(\epsilon, \delta)$-differential privacy, if for all adjacent
-\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
+A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ and codomain $\range$, is $\epsilon$-differential private, if for all adjacent
+\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, iff
 $\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
@@
 
-\subsection{Technical Problem Statement}
+\noindent \textbf{Technical Problem Statement.}
 \label{subsec_problem}
@@
 {\color{blue}im not sure this is a good way to put it...}
-This gives us motivation on exploring the design space
-of mechanisms by considering different norms (a distribution metric)
+This gives us motivation for exploring the design space
+of mechanisms by considering different norms. e.g. a norm over space of measures.
 to compute the sensitivity and provide guarantees on the accuracy.

### 2019-01-05 ICML2019/main.tex
update the section 3

@@
 The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
-is given by a Dirichelet distribution, $\dirichlet{n}{\valpha}$, for $k\in\mathbb{N}$,
+is given by a Dirichlet distribution, $\dirichlet{\valpha}$, for $k\in\mathbb{N}$,
 and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
@@
 \label{sec_mechs}
-
 \subsection{Laplace Mechanism Family}
 
-\subsubsection{using $\ell_1$ norm metric}
- Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech(\bysinfer, \dataobs)$, producing an output:
-$$
-\begin{array}{rcl}
-& \lapmech(\bysinfer, \dataobs) \\
-& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
-\end{array} 
-$$
- where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
-$$
-\begin{array}{rcl}
- & \lapmech(\bysinfer, \dataobs) = \\
- & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
- & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
-\end{array} 
-$$
- where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model.
-$\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.
-
- We use $ \lapmech(\dataobs) = \betad(\tilde{\alpha}, \tilde{\beta})$ or $\dirichlet(\tilde{\valpha})$ for short. Then release it as the private posterior distribution.
-
- The sensitivity of the inference process w.r.t. $\ell_1$ norm in $\lapmech$ is:
- \[
- \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
- \]
- which is proportional to the dimensionality.
-
-\subsubsection{using improved $\ell_1$ norm metric}
- Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism.
-Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
-
- Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, then the improved Laplace mechanism $\ilapmech(\bysinfer, \dataobs)$ is producing an output:
-
-$$
-\begin{array}{rcl}
-& \ilapmech(\bysinfer, \dataobs) \\
-& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
-\end{array} 
-$$
- where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
-$$
-\begin{array}{rcl}
- & \ilapmech(\bysinfer, \dataobs) = \\
- & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
- & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
-\end{array} 
-$$
-where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.
-
-Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
+\subsubsection{Using $\ell_1$ Norm Metric}
+  We firstly present the fully explored mechanism in Laplace family -- Laplace mechanism.
+This mechanism ($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$) simply adds Laplace noise with post-processing to the posterior distribution parameters, producing an output: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$ with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid, as shown in Mechanism \ref{mech:lapmech}.\\
+  Since we are adding noise directly to the parameter, the sensitivity should be calibrated to $\ell_1$ of two Beta distributions:
+  $
+   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
+  $,
+  i.e., proportional to the dimensionality.
+
+  \begin{algorithm}
+  \caption{$\lapmech$ in Beta-binomial model}
+  \label{mech:lapmech}
+  \begin{algorithmic}
+  \REQUIRE observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \STATE \quad {\bf let} $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
+  \STATE \quad {\bf let} $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \ENSURE $\betad(\tilde{\alpha}, \tilde{\beta})$
+  \end{algorithmic}
+  \end{algorithm}
+
+  In Dirichlet-multinomial model, $\lapmech$ produces output: $ \dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0},$
+  where $\eta_i \thicksim \lap{0}{\frac{k - 1}{\epsilon}}$.
+  We will use $ \lapmech(\dataobs) = \betad(\tilde{\alpha}, \tilde{\beta})$ or $\dirichlet{\tilde{\valpha}}$ for short.
+
+\subsubsection{Using $\ell_1$ Norm with Improved Sensitivity}
+ The $\lapmech$ presented above can be improved in our Bayesian inference model, by adding noise scaled to smaller sensitivity in this improved Laplace mechanism $\ilapmech$.\\
+ In terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+As a results, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.\\
+ By calibrating noise to this improved sensitivity, $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces output:
+ $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)
+$
+with $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model and
+$\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, 
+\alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}
+$
+with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Mechanism \ref{mech:ilapmech}.
+  \begin{algorithm}
+  \caption{$\ilapmech$ in Dirichlet-multinomial model}
+  \label{mech:ilapmech}
+  \begin{algorithmic}
+  \REQUIRE observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$.
+  \STATE \quad {\bf Initialize} $\tilde{\valpha} = (0,\dots )$, $k = |\mathcal{X}|$.
+  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \ENSURE $\dirichlet{\tilde{\valpha}}$
+  \end{algorithmic}
+  \end{algorithm}
 

### 2019-01-05 ICML2019/main.tex
update mechanisms

@@
 \subsection{Exponential Mechanism Family}
-In this section, we explore the exponential mechanism family: $\expmech(\cdot,\cdot,\cdot)$ by considering Hellinger distance metrics and different sensitivities.
-
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:
-
-\[
-  \candidateset\equiv\{\bysinfer(binomial(\theta), \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
+In this section, we explore the exponential mechanism family: $\expmech$ by considering Hellinger distance metrics and different sensitivities.\\
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:
+\[
+  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs')\mid \dataobs' \in \{0,1\}^n\}.
 \]
 For simplicity:
-\[
+$
   \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
-\]
+$
 over all $\dataobs \in \{0,1\}^n$, where $\Delta\alpha$ is as defined in Section \ref{sec_background}, and
-\[
-  \candidateset\equiv\{\dirichlet(\valpha')\mid \valpha'=\valpha + \Delta\valpha\},
-\]
-over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.
-
-We don't explicitly
-parametrize the result by the prior and likelihood, which from now on we consider
-fixed and we denote them by $\bprior$ and $binomial(\theta)$, $multinomial(\theta)$. We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed.
+$
+  \candidateset\equiv\{\dirichlet{\valpha'} \mid \valpha'=\valpha + \Delta\valpha\}
+$,
+over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.\\
+We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed, denoted by $\bprior$ and $\binomial{n}{\theta}$, $\multinomial{n}{\vtheta}$.
 
 \subsubsection{Standard Exponential Mechanism with Hellinger Metric}
-Standard exponential mechanism $\expmech(x,u,\candidateset)$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\begin{equation*}
+Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
+\[
 \underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
@@
 {\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
-\end{equation*}
+\]
 where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
@@
 
-Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.
-
 \subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
 \label{subsec_emls}
-% \subsubsection{Mechanism Set up}
-Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$ share the same candidate set and utility function as it with standard exponential mechanism.
-This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
-\begin{equation*}
-\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
+In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$.
+This is just an attempt since local sensitivity is non-private.
+$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
+\[
+\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
 {exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
 {\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
-\end{equation*}
-
+\]
 where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
-
 \begin{equation*}
@@
 \end{equation*}
-
-The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.
 
@@
 \label{subsec_hexpmech}
-
+In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and differential privacy simultaneously, by scaling the noise to a new sensitivity.
+We first define the new sensitivity we are going to use and then present the mechanism.
 \begin{definition}
@@
 \begin{proof}
-of Theorem. \ref{thm_gamma_smooth}.
-
-For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:
-
-By Equation (\ref{eq_smooth}):
-\begin{equation*}
-\begin{split}
-S(\dataobs) 
-& = \max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \}\\
+of Theorem. \ref{thm_gamma_smooth}.\\
+For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
+From Equation (\ref{eq_smooth}), we can get:
+\[
 \frac{1}{S(\dataobs)} 
-& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
-\end{split}
-\end{equation*}
+ = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
+\]
 
@@
 \end{equation*}
-$\implies$
-\begin{equation*}
-\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
-\end{equation*}
-
+Then we can get:
+$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
 \end{proof}
@@
 \end{definition}
-
-Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
-\[
-  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet{\valpha}$ by rewriting the Hellinger distance as:
+\[
+  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
 \]
@@
 
-% \subsection{Privacy Analysis for Baseline Mechanisms}
-% In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}.
-The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
 \subsection{Privacy of Laplace Mechanism Family}
@@
 \end{lem}
-\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
-
-  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
-
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
+  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
   For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
@@
   \end{equation*}
-
   By definition \ref{def_smoo_2}:
@@
   \big)
+  }\\
+  & \cdot 
+  \frac{1}
+  {
   \exp 
@@
 
-  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.
+  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
 

### 2019-01-05 ICML2019/main.tex
adjust the format

@@
 when $t < 0$.\\
-
-% When $\alpha = \beta$, we also have:
-% \begin{align*}
-%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
-%   = \quad & Pr[ - t \leq Y < t + 1] \\
-%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
-%  \end{align*}
 Unfolding the Hellinger distance formula, we get:\\
@@
   \end{align*}
-
-%   We also have:
-%   \begin{align*}
-%   & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
-%   \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-%   \cdot
-%   \prod_{k = 1}^{\frac{t}{2}}
-%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
-%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
-%   \end{align*} 
-%   when $\alpha = \beta$.
-% in 2 dimensions, where $\epsilon = 1.0$. 
-% \begin{itemize}
-% 	\item \textbf{Case} of baseline Laplace mechanism, where $\Delta \bysinfer = 2$:\\
-
-% 	\item \textbf{Case} of improved Laplace mechanism, where $\Delta \bysinfer = 1$
-% \end{itemize}
 
@@
 
-Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:
-
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
-
+  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
+  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
   $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.
-
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
   $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
@@
   \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
-
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
 In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
@@
 For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
-\begin{table}[h!]
+\begin{table*}[t]
 \scriptsize
@@
 \label{tab_acc_theo}
-\end{table}
+\end{table*}
 
 In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
-\begin{table}[h!]
+\begin{table*}[t]
 \scriptsize
@@
 \label{tab_acc_theo}
-\end{table}
+\end{table*}
 
@@
 By solving following equations:
-\begin{itemize}
-  \item
   \[
@@
   we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
-
-  \item 
   \[
@@
   we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
-\vspace{12cm}
-  \item 
   \[
@@
 \]
-we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one.
-
-  \item Following equations can be in the same way.
-\end{itemize}
-
-%   Unfolding the Hellinegr distance in this accuracy formula:
-%  \begin{itemize}
-
-%   \item[\textbf{case 1:}] \textbf{t is even}
-
-%   \begin{align*}
-%   &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 = 
-%   1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-%   \cdot
-%   \prod_{k = 1}^{\frac{t}{2}}
-%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
-%   = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-%   \cdot
-%   \prod_{k = 1}^{\frac{t}{2}}
-%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}
-%   {\nomalizer{\dataobs}}
-%   \end{align*}
-
-%   \item[\textbf{case 2:}] \textbf{t is odd}
-
-%   \begin{align*}
-%   c^2 = \qquad &
-%   1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
-%   \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
-%   \qquad &\cdot 
-%   \prod_{k = 0}^{m-1}
-%   \sqrt{(1 + \frac{1}{2(\alpha + k)})
-%   (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-%   } \\
-%   \qquad & \cdot 
-%   \prod_{k = 1}^{m} 
-%   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
-%   \end{align*}
-%   Substitute the $c$ in Equation, (\ref{eq_acc})
-
-% \end{itemize}
+we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
 

### 2019-01-05 ICML2019/main.tex
fix problem in section2

@@
 $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.
-
+This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.\\
 However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
@@
 where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
-\todo{This
-accuracy metric is meaningless when the results released are
-distributions rather than numerical values. In contrast, distribution
-metrics such as $f$-divergence, Hellinger distance, etc. come into
-mind overtly when we are measuring distance between
-distributions. }
-{\color{blue}im not sure this is a good way to put it...}
+\todo{However, distance between
+distributions are more naturally to be measured by distribution
+metrics such as $f$-divergence, Hellinger distance, etc., than the $\ell_1$ norm shown above.}
+{\color{blue} changed a bit, still not sure this is a good way to put it...}
 This gives us motivation for exploring the design space
 of mechanisms by considering different norms. e.g. a norm over space of measures.
-to compute the sensitivity and provide guarantees on the accuracy.
-
+to compute the sensitivity and provide guarantees on the accuracy.\\
 We will use the Hellinger distance $\hellinger(\cdot,\cdot)$, 
@@
 \[
-\todo{def}
+\hellinger^2(P,Q) = \frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
 \]
@@
 \[
-  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+ \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
 \]
@@
 \centering
-\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
-\caption{{Sensitivity of $\hellinger$}}
+\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
+\caption{{The local sensitivity of $\hellinger$}}
 \label{fig_sensitivity}
@@
   prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$.
-  \STATE \quad {\bf Initialize} $\tilde{\valpha} = (0,\dots )$, $k = |\mathcal{X}|$.
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
   \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:

### 2019-01-05 ICML2019/main.tex
update accuracy

@@
 For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
+In this table, the first column is the value of distance $c$ from the correct posterior distribution.
+The first row is three mechanisms: $\lapmech$, $\ilapmech$ and $\hexpmech$.
+For each mechanism, we calculate the probability of outputting corresponding candidates which is at distance $c$ from the correct posterior distribution and put into the table.
+We calculate the first three nearest candidates and the others trival.
 \begin{table*}[t]
@@
 \centering
-\begin{tabular}{ |c|c|c|c| } 
+\caption{Accuracy Comparison in Theoretical}
+\label{tab_acc_theo}
+\begin{tabular}{ |c|c|c|c|c| } 
 \hline
@@
     \cdot
-    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
  \hline
- $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
- & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
+ $\lapmech $
+ & 0.19673467014 & 0.11932560927 & 0.07237464051 & \dots \\
  \hline
- $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
+ $\ilapmech $
+ & 0.31606027941 & 0.11627207896 & 0.04277410743 & \dots \\
  \hline
- $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+ $\hexpmech $
  & $\frac{1}{\nomalizer{\dataobs}}$
@@
     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
-    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
+    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots\\
  \hline
 \end{tabular}
-\caption{Accuracy Comparison in Theoretical}
-\label{tab_acc_theo}
 \end{table*}
 
-In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
-\begin{table*}[t]
-\scriptsize
-\centering
-\begin{tabular}{ |c|c|c|c| } 
-\hline
- c & 0 
- & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
-  & $1 - 
-    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-    \cdot
-    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
- \hline
- $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
- & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
- \hline
- $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
- \hline
- $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
- & $\frac{1}{\nomalizer{\dataobs}}$ 
- & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
- \cdot
- \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
- & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
-    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-    \cdot
-    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
-    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
- \hline
-\end{tabular}
-\caption{Accuracy Comparison in Theoretical}
-\label{tab_acc_theo}
-\end{table*}
+% In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
+% \begin{table*}[t]
+% \scriptsize
+% \centering
+% \begin{tabular}{ |c|c|c|c|c| } 
+% \hline
+%  c & 0 
+%  & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
+%   & $1 - 
+%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%     \cdot
+%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
+%  \hline
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
+%  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
+%  \hline
+%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+%  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
+%  \hline
+%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+%  & $\frac{1}{\nomalizer{\dataobs}}$ 
+%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
+%  \cdot
+%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
+%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
+%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%     \cdot
+%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+%     {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots \\
+%  \hline
+% \end{tabular}
+% \caption{Accuracy Comparison in Theoretical}
+% \label{tab_acc_theo}
+% \end{table*}
 
@@
   \[
-\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
+\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}

### 2019-01-13 ICML2019/main.tex
fix plot
working on the abstract

@@
 \input{macros}
-\icmltitlerunning{Exploring Design Space for Differentially Private Bayesian Inference}
+\icmltitlerunning{Exploring the Design Space of Differentially Private
+  Bayesian Inference under Hellinger Metric}
 
@@
 \twocolumn[
-\icmltitle{Exploring Design Space for Differentially Private Bayesian Inference}
+\icmltitle{Exploring the Design Space of Differentially Private
+  Bayesian Inference under Hellinger Metric}
 
@@
 \icmlauthor{Jiawen Liu}{to}
+\icmlauthor{Gian Pietro Farina}{to}
 \icmlauthor{Mark Bun}{ed}
-\icmlauthor{Gian Pietro Farina}{to}
 \icmlauthor{Marco Gaboardi}{to}
@@
 % of the released posterior distribution and the actual real ones of posterior distribution.
-We explore the design space for differentially private Bayesian
-inference.  We focused on two discrete models for parametric Bayesian
-inference i.e., the Beta-Binomial and the Dirichlet-multinomial
+We explore the design space of differentially private Bayesian
+inference mechanism.  We focus on two discrete models for parametric Bayesian
+inference: the Beta-Binomial and the Dirichlet-multinomial
 models. We propose a variation of the exponential mechanism that uses

### 2019-01-13 ICML2019/main.tex
pass over the abstract

--- 2019-01-05 ICML2019/main.tex
@@
 \input{macros}
-\icmltitlerunning{Exploring Design Space for Differentially Private Bayesian Inference}
+\icmltitlerunning{Exploring the Design Space of Differentially Private
+  Bayesian Inference under Hellinger Distance}
 
@@
 \twocolumn[
-\icmltitle{Exploring Design Space for Differentially Private Bayesian Inference}
+\icmltitle{Exploring the Design Space of Differentially Private
+  Bayesian Inference under Hellinger Distance}
 
@@
 \icmlauthor{Jiawen Liu}{to}
+\icmlauthor{Gian Pietro Farina}{to}
+\icmlauthor{Tetsuya Sato}{to}
 \icmlauthor{Mark Bun}{ed}
-\icmlauthor{Gian Pietro Farina}{to}
 \icmlauthor{Marco Gaboardi}{to}
@@
 
-\icmlaffiliation{to}{Department of Computer Science and Engineering, University at Buffalo, SUNY, New York, United State}
-\icmlaffiliation{ed}{Princeton University, United State}
+\icmlaffiliation{to}{Department of Computer Science and Engineering, University at Buffalo, SUNY, New York, United States}
+\icmlaffiliation{ed}{Princeton University, United States}
 
@@
 % of the released posterior distribution and the actual real ones of posterior distribution.
-We explore the design space for differentially private Bayesian
-inference.  We focused on two discrete models for parametric Bayesian
-inference i.e., the Beta-Binomial and the Dirichlet-multinomial
-models. We propose a variation of the exponential mechanism that uses
-a scoring function based on a metric over probailistic measures, i.e.,
-the Hellinger distance. We compare it with other approaches based on
-the perturbation of the parameters of the posterior distribution.  We
-measure the accuracy using the Hellinger distance over the posterior
-distribution released and the real one as opposed to measuring the
-$\ell_1$ or $\ell_{\infty}$ distance on the parameters.  We finally
-present an experimental analysis on the accuracy of these mechanisms.
+We explore the design space of differentially private Bayesian
+inference mechanisms with accuracy measured in terms of Hellinger
+distance over posterior distributtions.  
+We focus on two discrete models for parametric Bayesian
+inference: the Beta-Binomial and the Dirichlet-Multinomial
+models. We study two mechanisms based on the 
+Laplace perturbation of the parameters of the posterior distribution under
+$\ell_1$ norm, and compare them with variations of the exponential
+mechanism calibrated to Hellinger distance. We
+measure the accuracy using the Hellinger distance between the posterior
+distribution released by the different mechanisms and the real one.
+We compare the accuracy theoretically and experimentally.
 \end{abstract}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{efficiency}
+\includegraphics[width=0.45\textwidth]{efficiency.eps}
 \caption{Experimental Results for Finding the Local Sensitivity Efficiently}

### 2019-01-13 ICML2019/main.tex
pass on sec 2

--- 2019-01-05 ICML2019/main.tex
@@
   \icmlauthor{Jiawen Liu}{to}
+  \icmlauthor{Gian Pietro Farina}{to}
   \icmlauthor{Mark Bun}{ed}
-\icmlauthor{Gian Pietro Farina}{to}
   \icmlauthor{Marco Gaboardi}{to}
@@
 % of the released posterior distribution and the actual real ones of posterior distribution.
-We explore the design space for differentially private Bayesian
-inference.  We focused on two discrete models for parametric Bayesian
-inference i.e., the Beta-Binomial and the Dirichlet-multinomial
+In this work we explore the design space for differentially private Bayesian
+inference.  We focus on two discrete models for parametric Bayesian
+inference i.e., the Beta-Binomial and the Dirichlet-Multinomial
 models. We propose a variation of the exponential mechanism that uses
-a scoring function based on a metric over probailistic measures, i.e.,
+a scoring function based on a metric over probabilistic measures, i.e.,
 the Hellinger distance. We compare it with other approaches based on
@@
 The question that this work aims at answering is whether
-an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
+an approach based on probability metrics can improve on
+the accuracy of approaches based on metrics over
 the numeric parameters of the distributions. 
@@
 \begin{itemize}
-	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
+	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
 
@@
 
-\section{Mechanism Proposition}
+\section{Private Mechanisms}
 \label{sec_mechs}
-\subsection{Laplace Mechanism Family}
-
-\subsubsection{Using $\ell_1$ Norm Metric}
-  We firstly present the fully explored mechanism in Laplace family -- Laplace mechanism.
-This mechanism ($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$) simply adds Laplace noise with post-processing to the posterior distribution parameters, producing an output: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$ with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid, as shown in Mechanism \ref{mech:lapmech}.\\
+\subsection{Calibrating noise w.r.t. $\ell_1$ norm}
+We start off by presenting a mechanism based on the Laplace primitive.
+The mechanism, denoted by {\color{red}{i think this macro has too many arguments}}($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$),
+simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
+post-processing phase by {\color{red}{flooring}} and  truncating the noisy parameters so that they belong to the right interval.
+In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
+with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
+$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
 Since we are adding noise directly to the parameter, the sensitivity should be calibrated to $\ell_1$ of two Beta distributions:
@@
 i.e., proportional to the dimensionality.
-
   \begin{algorithm}
@@
 
-  In Dirichlet-multinomial model, $\lapmech$ produces output: $ \dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0},$
+  In Dirichlet-Multinomial model, $\lapmech$ produces output:
+  $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0},$
   where $\eta_i \thicksim \lap{0}{\frac{k - 1}{\epsilon}}$.
@@
 \subsubsection{Using $\ell_1$ Norm with Improved Sensitivity}
- The $\lapmech$ presented above can be improved in our Bayesian inference model, by adding noise scaled to smaller sensitivity in this improved Laplace mechanism $\ilapmech$.\\
- In terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
+ The accuracy of the previous $\lapmech$ can be improved, by adding noise scaled to smaller sensitivity.
+ In terms of two adjacent data sets $\dataobs, \dataobs'$, the posterior distributions that they induce -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
 As a results, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.\\

### 2019-01-13 ICML2019/main.tex

@@
 \icmlauthor{Gian Pietro Farina}{to}
+\icmlauthor{Tetsuya Sato}{to}
 \icmlauthor{Mark Bun}{ed}
@@
 % of the released posterior distribution and the actual real ones of posterior distribution.
-In this work we explore the design space for differentially private Bayesian
-inference.  We focus on two discrete models for parametric Bayesian
-inference i.e., the Beta-Binomial and the Dirichlet-Multinomial
-models. We propose a variation of the exponential mechanism that uses
-a scoring function based on a metric over probabilistic measures, i.e.,
-the Hellinger distance. We compare it with other approaches based on
-the perturbation of the parameters of the posterior distribution.  We
-measure the accuracy using the Hellinger distance over the posterior
-distribution released and the real one as opposed to measuring the
-$\ell_1$ or $\ell_{\infty}$ distance on the parameters.  We finally
-present an experimental analysis on the accuracy of these mechanisms.
+We explore the design space of differentially private Bayesian
+inference mechanisms with accuracy measured in terms of Hellinger
+distance over posterior distributtions.  
+We focus on two discrete models for parametric Bayesian
+inference: the Beta-Binomial and the Dirichlet-Multinomial
+models. We study two mechanisms based on the 
+Laplace perturbation of the parameters of the posterior distribution under
+$\ell_1$ norm, and compare them with variations of the exponential
+mechanism calibrated to Hellinger distance. We
+measure the accuracy using the Hellinger distance between the posterior
+distribution released by the different mechanisms and the real one.
+We compare the accuracy theoretically and experimentally.
 \end{abstract}

### 2019-01-15 ICML2019/main.tex
pass on absrtract

@@
 inference mechanisms with accuracy measured in terms of Hellinger
-distance over posterior distributtions.  
+distance over posterior distributions.  
 We focus on two discrete models for parametric Bayesian
@@
 Laplace perturbation of the parameters of the posterior distribution under
-$\ell_1$ norm, and compare them with variations of the exponential
-mechanism calibrated to Hellinger distance. We
-measure the accuracy using the Hellinger distance between the posterior
+$\ell_1$ norm, and compare them with variations of the Exponential
+mechanism where the score function is based on the Hellinger distance.
+Accuracy is measured through the Hellinger distance between the posterior
 distribution released by the different mechanisms and the real one.

### 2019-01-16 ICML2019/main.tex
starting a pass on the abstract

@@
 Laplace perturbation of the parameters of the posterior distribution under
-$\ell_1$ norm, and compare them with variations of the Exponential
-mechanism where the score function is based on the Hellinger distance.
+$\ell_1$ norm, and compare them with a discrete mechanism calibrating 
+its score function to a smooth bound on the Hellinger distance.
 Accuracy is measured through the Hellinger distance between the posterior
@@
 \label{sec_intro}
-Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on.
-In order to provide a better service, large of data are collected from users for analysis.
-As a consequence, the data privacy came to be a critical issue.
-Sensitivity information in data can be revealed through the analysis results.
-The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.
-
-Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms.
-They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy.
-But they are not giving better accuracy than the differential privacy mechanism itself.
-Here, we are proposing mechanism with better accuracy.
+Data analysis techniques have brought significant improvements in a
+variety of applications including applications from the medical,
+financial, social, and transportation fields. In order to provide
+better services, these applications need large amounts of users data
+putting at risk the privacy of individual users contributing their data. 
+Differential privacy was proposed a decade ago to address these
+situations and it on its way to become a gold standard in data
+privacy.
+
+Bayesian inference is a standard statistical tool that is useful to
+estimate a posterior distribution when given a prior distribution and
+some observed data.
+
+In this work we consider the design space of  parametric Bayesian
+inference mechanisms guaranteeing differential privacy. Our work is
+motivated by recent developments in the area of probabilistic
+programming where several tools have been proposed to perfor
+parametric and non-parametric Bayesian inference in an efficient
+way. The in
+for our work is the recent development of
+
+In particular
+we focus on two classical models: the Beta-Binomial and the
+Dirichlet-Multinomial models. These are classical models
 

### 2019-01-17 ICML2019/main.tex
move the proof into appendix
pass until section 3.3 included

--- 2019-01-15 ICML2019/main.tex
@@
 
-\subsubsection{Using $\ell_1$ Norm with Improved Sensitivity}
- The accuracy of the previous $\lapmech$ can be improved, by adding noise scaled to smaller sensitivity.
- In terms of two adjacent data sets $\dataobs, \dataobs'$, the posterior distributions that they induce -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.
-As a results, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.\\
- By calibrating noise to this improved sensitivity, $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces output:
- $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)
-$
-with $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model and
-$\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, 
-\alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}
-$
-with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Mechanism \ref{mech:ilapmech}.
+\subsection{Improving the sensitivity}
+ The accuracy of $\lapmech$ can be reduced to a constant.
+ Indeed, two adjacent data sets $\dataobs, \dataobs'$  induce posterior distributions -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ --
+ whose parameters differ by at most 2 w.r.t $\ell_1$ norm. This because we can see the parameters of the distributions as an histogram.
+ Hence, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.
+ {\color{red} Notice that we are using the bounded notion of differential privacy \cite{????}.}
+ \todo{why 1 in 2 dimensions?}
+ We denote the mechanism which calibrates the noise to this smaller sensitivity as $\ilapmech$.
+ $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces:
+ $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0) $
+ where $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in the Beta-binomial model and
+ $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
+ with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}.
   \begin{algorithm}
@@
 
-\subsection{Exponential Mechanism Family}
-In this section, we explore the exponential mechanism family: $\expmech$ by considering Hellinger distance metrics and different sensitivities.\\
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:
+\subsection{A new mechanism}
+In this section, we explore a new mechanism which we denote by $\expmech$.
+The idea is that $\expmech$ will sample and output a distribution with higher probability when
+it is closer to the real posterior; importantly  \emph{closer} is measured using a metric over probability
+distributions as opposed to a metric over the parameters that represent it. In this work we will
+use the Hellinger distance, but this approach could be extended to other $f$-divergences. We will
+start by describing how the mechanism works in the case of the Beta-Binomial model noticing that
+the extension to the Dirichelet-Multinomial model is straightforward.
+Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
+we define the follwing set  where the mechanism will sample from:
 \[
@@
 \]
-For simplicity:
-$
-  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
-$
-over all $\dataobs \in \{0,1\}^n$, where $\Delta\alpha$ is as defined in Section \ref{sec_background}, and
-$
-  \candidateset\equiv\{\dirichlet{\valpha'} \mid \valpha'=\valpha + \Delta\valpha\}
-$,
-over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.\\
-We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed, denoted by $\bprior$ and $\binomial{n}{\theta}$, $\multinomial{n}{\vtheta}$.
+Notice that the above set reduces to:
+\[
+  \{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
+\]
+We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process on the observed data $\dataobs$
+when the other two parameters, that is prior and likelihood, are fixed.
 

### 2019-01-17 ICML2019/main.tex

@@
 \end{thm}
-
-\begin{proof}
-of Theorem. \ref{thm_gamma_smooth}.\\
-For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
-From Equation (\ref{eq_smooth}), we can get:
-\[
-\frac{1}{S(\dataobs)} 
- = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
-\]
-
-Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
-
-\begin{equation*}
-\begin{split}
-& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
-& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
-\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
-\}\\
-& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
-\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
-\}\\
-& = \gamma + \frac{1}{S(\dataobs')}
-\end{split}
-\end{equation*}
-Then we can get:
-$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
-\end{proof}
+Proof is in Appendix I.
 
@@
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $\epsilon$-differential privacy.
+$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
 \end{lem}
-\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
-  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
-  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
-  \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
-  \end{equation*}
-  By definition \ref{def_smoo_2}:
-  \begin{equation*}
-  \begin{split}
-  \hexpmechPr{\dataobs}{z = r} 
-  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
-  & = \frac {\exp\big(
-  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}} \\
-  & = \frac {\exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}}
-  \\
-  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
-  \end{split}
-  \end{equation*}
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \frac {exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}}
-  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
-  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)\\
-  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
-  \big)\\
-  \end{split}
-  \end{equation*}
-
-  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
-  \big)\\
-  \end{split}
-  \end{equation*}
-
-  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}
-  \exp
-  \big(
-  \frac{\epsilon}{4} \cdot \gamma
-  \big)\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  \end{split}
-  \end{equation*}
-
-  Doing the same transformation in the denominator:
-  \begin{equation*}
-  \begin{split}
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
-  & \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  \end{split}
-  \end{equation*}
-
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  & \cdot 
-  \frac{1}
-  {
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
-  \big)
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)}\\
-  & \cdot\frac{1}{
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon\cdot(\ux{r'})}{4}
-  (\frac{1}{S(\dataobs)}
--
-  \frac{1}{S(\dataobs')})
-  \big)
-  }
-  \end{split}
-  \end{equation*}
-
-  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)}\\
-  & \cdot \frac{1}{
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon}{4}
-  (\frac{1}{S(\dataobs)}
--
-  \frac{1}{S(\dataobs')})
-  \big)
-  }\\
-  \end{split}
-  \end{equation*}
-
-  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
-  $\frac{- \epsilon}{4}
-  (\frac{1}{S(\dataobs)}-
-  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon}{4} \cdot \gamma
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
-  \big)
-  }\\
-  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \unomalizer{\dataobs'}
-  }\\
-  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
-  \end{split}
-  \end{equation*}
-
-  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
-
-\end{proof}
+(Proof is in Appendix II)
 
@@
 
+\newpage
+\section*{Appendix I}
+\label{app_sensitivity}
+\begin{proof}
+of Theorem. \ref{thm_gamma_smooth}.\\
+For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
+From Equation (\ref{eq_smooth}), we can get:
+\[
+\frac{1}{S(\dataobs)} 
+ = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
+\]
+
+Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
+
+\begin{equation*}
+\begin{split}
+& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
+& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
+\}\\
+& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
+\}\\
+& = \gamma + \frac{1}{S(\dataobs')}
+\end{split}
+\end{equation*}
+Then we can get:
+$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
+\end{proof}
+
+\section*{Appendix II}
+\label{app_privacyproof}
+\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
+  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
+  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
+  \begin{equation*}
+  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
+  \end{equation*}
+  By definition \ref{def_smoo_2}:
+  \begin{equation*}
+  \begin{split}
+  \hexpmechPr{\dataobs}{z = r} 
+  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+  & = \frac {\exp\big(
+  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}} \\
+  & = \frac {\exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \\
+  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
+  \end{split}
+  \end{equation*}
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \frac {exp\big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+  \big)}
+  {\unomalizer{\dataobs}}
+  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
+  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  & \cdot \exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)\\
+  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  & \cdot \exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  & \cdot \exp
+  \big(
+  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+  \big)\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
+  \begin{equation*}
+  \begin{split}
+  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}
+  \exp
+  \big(
+  \frac{\epsilon}{4} \cdot \gamma
+  \big)\\
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {\unomalizer{\dataobs}}\\
+  \end{split}
+  \end{equation*}
+
+  Doing the same transformation in the denominator:
+  \begin{equation*}
+  \begin{split}
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
+  \big)
+  }\\
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
+  & \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  }\\
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+  \big)
+  }\\
+  & \cdot 
+  \frac{1}
+  {
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  \exp
+  \big(
+  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
+  \big)
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
+  \big)
+  }\\
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)}\\
+  & \cdot\frac{1}{
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  \exp
+  \big(
+  \frac{- \epsilon\cdot(\ux{r'})}{4}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }
+  \end{split}
+  \end{equation*}
+
+  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
+  \begin{equation*}
+  \begin{split}
+  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)}\\
+  & \cdot \frac{1}{
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  \exp
+  \big(
+  \frac{- \epsilon}{4}
+  (\frac{1}{S(\dataobs)}
+-
+  \frac{1}{S(\dataobs')})
+  \big)
+  }\\
+  \end{split}
+  \end{equation*}
+
+  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
+  $\frac{- \epsilon}{4}
+  (\frac{1}{S(\dataobs)}-
+  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
+  \begin{equation*}
+  \begin{split}
+  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)
+  \exp 
+  \big(
+  \frac{-\epsilon}{4}
+  \big)
+  \exp
+  \big(
+  \frac{- \epsilon}{4} \cdot \gamma
+  \big)
+  }\\
+  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \sum_{r'\in \candidateset} 
+  \exp 
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+  \big)
+  \exp 
+  \big(
+  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
+  \big)
+  }\\
+  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
+  \frac {
+  \exp
+  \big(
+  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+  \big)
+  } 
+  {
+  \unomalizer{\dataobs'}
+  }\\
+  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
+  \end{split}
+  \end{equation*}
+
+  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
+
+\end{proof}
 \end{document}

### 2019-01-17 ICML2019/main.tex
using \exp and \Pr

@@
 \[
-\underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
+\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
+{\exp(\frac{\epsilon u(x,r)}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
 \]
@@
 This is just an attempt since local sensitivity is non-private.
-$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
+$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
 \[
 \underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
-{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
+{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
 \]
@@
 \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
+  \hexpmechPr{\dataobs}{z = r} = \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
 {\unomalizer{\dataobs}}.
@@
 \label{subsec_accuracy_lap}
-Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
+Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
+Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
 
@@
 \[
-Pr\big[\lfloor Y \rfloor = t\big] 
-= Pr[ t \leq Y < t + 1] 
+\Pr\big[\lfloor Y \rfloor = t\big] 
+= \Pr[ t \leq Y < t + 1] 
 = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
@@
 \[
-Pr\big[\lfloor Y \rfloor = t\big] 
-= Pr[ t \leq Y < t + 1] 
+\Pr\big[\lfloor Y \rfloor = t\big] 
+= \Pr[ t \leq Y < t + 1] 
 = \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
@@
 \begin{array}{rcl}
-& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
 = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
@@
 \begin{array}{rcl}
-& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
 = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
@@
   \begin{align*}
-  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+  & \Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
   & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
@@
   \begin{align*}
-  & Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
+  & \Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
   & =
@@
   \begin{split}
-  & \leq \frac {exp\big(
+  & \leq \frac {\exp\big(
   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}

### 2019-01-17 ICML2019/main.tex
tweak.

@@
 Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
-\[
-\Pr\big[\lfloor Y \rfloor = t\big] 
-= \Pr[ t \leq Y < t + 1] 
-= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-\]
-when $t \geq 0$, and
-\[
-\Pr\big[\lfloor Y \rfloor = t\big] 
-= \Pr[ t \leq Y < t + 1] 
-= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-\]
-when $t < 0$.
+%\[
+%\Pr\big[\lfloor Y \rfloor = t\big] 
+%= \Pr[ t \leq Y < t + 1] 
+%= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+%\]
+%when $t \geq 0$, and
+%\[
+%\Pr\big[\lfloor Y \rfloor = t\big] 
+%= \Pr[ t \leq Y < t + 1] 
+%= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+%\]
+%when $t < 0$.
+\begin{align*}
+\Pr\big[\lfloor Y \rfloor = t\big]&= \Pr[ t \leq Y < t + 1]\\
+&= 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
 
@@
 By applying Hellinger distance in our case, we get:
-$$
-\begin{array}{rcl}
-& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
-& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
-\end{array}
-$$
-when $t \geq 0$, and\\
-$$
-\begin{array}{rcl}
-& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
-& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
-\end{array}
-$$
-when $t < 0$.\\
+%$$
+%\begin{array}{rcl}
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
+%& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+%\end{array}
+%$$
+%when $t \geq 0$, and\\
+%$$
+%\begin{array}{rcl}
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
+%& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
+%\end{array}
+%$$
+%when $t < 0$.\\
+\begin{align*}
+&
+\Pr\left[
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+\right]
+\\
+&\qquad = 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
+
 Unfolding the Hellinger distance formula, we get:\\
@@
 
-  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%  \cdot
+%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
+Instantiating $t$ with specific values ($1, 2, 3$ for example), we get the following accuracy equations on Laplace mechanism:
+\begin{align*}
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
+&= 0.19673467014,\\
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\ 
+&= 0.11932560927,\\
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
   \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} \\
+&= 0.07237464051.
+\end{align*}
 In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
@@
 
-Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
-
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
-
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$.
-
-  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+Given $t$ with the same specific values ($1, 2, 3$ as above), we get the following accuracy equations on improved Laplace mechanism:
+%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
+%
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
+%
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
+%
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%  \cdot
+%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
+\begin{align*}
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
+&= 0.31606027941,\\
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
+&= 0.11627207896,\\
+&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
   \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
-
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
+&= 0.04277410743.
+\end{align*}
 In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
@@
   we have following formula for accuracy:
+%  \begin{align*}
+%  \label{eq_acc}
+%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
+%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
+%  \end{align*}
+%
+%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
   \begin{align*}
-  \label{eq_acc}
-  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
-  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
+  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
+  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
+  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
-
-  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
 
@@
 The formula for computing the local sensitivity presented in Sec.
-\ref{sec_mechs}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
-can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
+\ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
+\[
+LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+\]
+can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
 by applying the distance triangle property.
@@
 Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
-\begin{equation*}
-\begin{split}
-LS(\dataobs) 
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
-  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
-\end{split}
-\end{equation*}
+%\begin{equation*}
+%\begin{split}
+%LS(\dataobs) 
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+%\end{split}
+\begin{align*}
+&LS(\dataobs)\\
+& = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{|\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+  &\qquad\qquad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))\}.
+\end{align*}
+
+%\end{equation*}
 

### 2019-01-18 ICML2019/main.tex
Tweak.
fix bugs

@@
 Unfolding the Hellinger distance formula, we get:\\
-  \noindent \textbf{case: t is even}\\
+  \noindent \textbf{case: t is even}
   \begin{align*}
-  & \Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  &\Pr\left[
+\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
+&= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot
-  \prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
-  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+  \cdot\prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
+\end{aligned}
+\right] \\
+  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
   \end{align*}
-
-  \noindent \textbf{case: t is odd}\\
+  \noindent \textbf{case: t is odd}
   let $t = 2 m + 1$
   \begin{align*}
-  & \Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
+  & \Pr\left[
+	\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
   & =
@@
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
-\qquad &\cdot 
+&\cdot 
   \prod_{k = 0}^{m-1}
@@
   (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  } \\
-  \qquad & \cdot 
+  }\\ &\cdot 
   \prod_{k = 1}^{m} 
-  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
-  = & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
+\right] \\
+   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
   \end{align*}
@@
 \begin{align*}
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
+&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
 &= 0.31606027941,\\
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
 &= 0.11627207896,\\
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 \]
-can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
+can be reduced to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
 by applying the distance triangle property.
@@
 \begin{align*}
-&LS(\dataobs)\\
-& = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{|\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
-  &\qquad\qquad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
-  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))\}.
+LS(\dataobs)
+& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+\left|~
+\begin{aligned}
+&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
+&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{aligned}
+\right|\\
+  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
 \end{align*}

### 2019-01-18 ICML2019/main.tex
move proof about accuracy into Appendix

@@
 \label{subsec_accuracy_lap}
-Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
-
-Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
-%\[
-%\Pr\big[\lfloor Y \rfloor = t\big] 
-%= \Pr[ t \leq Y < t + 1] 
-%= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-%\]
-%when $t \geq 0$, and
-%\[
-%\Pr\big[\lfloor Y \rfloor = t\big] 
-%= \Pr[ t \leq Y < t + 1] 
-%= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-%\]
-%when $t < 0$.
-\begin{align*}
-\Pr\big[\lfloor Y \rfloor = t\big]&= \Pr[ t \leq Y < t + 1]\\
-&= 
-\begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}) & t < 0
-\end{cases}
-\end{align*}
-
-Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
-By applying Hellinger distance in our case, we get:
-%$$
-%\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
-%& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
-%\end{array}
-%$$
-%when $t \geq 0$, and\\
-%$$
-%\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
-%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
-%& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
-%\end{array}
-%$$
-%when $t < 0$.\\
+\begin{lem}
+\label{lem_acc_lap}
+Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
 \begin{align*}
@@
 \end{align*}
-
-Unfolding the Hellinger distance formula, we get:\\
-  \noindent \textbf{case: t is even}
-  \begin{align*}
-  &\Pr\left[
-\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
-&= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot\prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
-\end{aligned}
-\right] \\
-  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
-  \end{align*}
-  \noindent \textbf{case: t is odd}
-  let $t = 2 m + 1$
-  \begin{align*}
-  & \Pr\left[
-	\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
-  & =
-  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
-&\cdot 
-  \prod_{k = 0}^{m-1}
-  \sqrt{(1 + \frac{1}{2(\alpha + k)})
-  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  }\\ &\cdot 
-  \prod_{k = 1}^{m} 
-  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
-\right] \\
-   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
-  \end{align*}
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+\end{lem}
+(Proof is in Appendix III)
 
@@
 \end{proof}
+
+\section*{Appendix III}
+\begin{proof} of Lemma \ref{lem_acc_lap}.
+
+Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
+Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
+
+Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
+%\[
+%\Pr\big[\lfloor Y \rfloor = t\big] 
+%= \Pr[ t \leq Y < t + 1] 
+%= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+%\]
+%when $t \geq 0$, and
+%\[
+%\Pr\big[\lfloor Y \rfloor = t\big] 
+%= \Pr[ t \leq Y < t + 1] 
+%= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+%\]
+%when $t < 0$.
+\begin{align*}
+\Pr\big[\lfloor Y \rfloor = t\big]&= \Pr[ t \leq Y < t + 1]\\
+&= 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
+
+Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+By applying Hellinger distance in our case, we get:
+%$$
+%\begin{array}{rcl}
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
+%& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+%\end{array}
+%$$
+%when $t \geq 0$, and\\
+%$$
+%\begin{array}{rcl}
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
+%& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
+%\end{array}
+%$$
+%when $t < 0$.\\
+\begin{align*}
+&
+\Pr\left[
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+\right]
+\\
+&\qquad = 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
+
+Unfolding the Hellinger distance formula, we get:\\
+  \noindent \textbf{case: t is even}
+  \begin{align*}
+  &\Pr\left[
+\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
+&= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+  \cdot\prod_{k = 1}^{\frac{t}{2}}
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
+\end{aligned}
+\right] \\
+  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
+  \end{align*}
+  \noindent \textbf{case: t is odd}
+  let $t = 2 m + 1$
+  \begin{align*}
+  & \Pr\left[
+  \begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
+  & =
+  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
+&\cdot 
+  \prod_{k = 0}^{m-1}
+  \sqrt{(1 + \frac{1}{2(\alpha + k)})
+  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+  }\\ &\cdot 
+  \prod_{k = 1}^{m} 
+  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
+\right] \\
+   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
+  \end{align*}
+
+\end{proof}
 \end{document}

### 2019-01-18 ICML2019/main.tex
fix bugs in accuracy

@@
 %  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
-Instantiating $t$ with specific values ($1, 2, 3$ for example), we get the following accuracy equations on Laplace mechanism:
+Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
 \begin{align*}
@@
 
-Given $t$ with the same specific values ($1, 2, 3$ as above), we get the following accuracy equations on improved Laplace mechanism:
+Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
 %Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
@@
 \label{subsec_accuracy_smoo}
+\begin{lem}
+\label{lem_acc_hexp}
   In Beta-binomial model,
-  we have following formula for accuracy:
+  we have following accuracy bound for this mechanism:
 %  \begin{align*}
@@
 %  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
+
   \begin{align*}
@@
   \end{align*}
+\end{lem}
 

### 2019-01-18 ICML2019/main.tex
clear up the formulas in accuracy section and fix macros file
Shrink

@@
 	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-
 	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
@@
 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
-
   \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
-
 	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
@@
 \]
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
+where $\Delta \alpha = \sum_{i=1}^{n}x_i$.
 The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
@@
 \[
-  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
+\Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
 \]
@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
-\]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
+\Pr(\dataobs|\vtheta)\equiv\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
+\]
+with $\Delta \alpha_i=\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
 Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
@@
 \]
-where $+$ denotes the componentwise sum of vectors of reals.
+where $+$ denotes the componentwise sum of vectors.
 
@@
 \footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, iff
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
+$\sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
 \begin{equation*}
@@
 \]
-
 Our choice to use Hellinger distance is motivated by three facts:
@@
   \item It simplifies calculations in the case of the probabilistic models considered here.
-
   \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an unbounded adversary can have in distingishing two distributions. 
-
   \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity},
@@
 where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
-\begin{equation*}
+\begin{equation}\label{eq:local_sensitivity_scoring}
 LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
-\end{equation*}
+\end{equation}
 
@@
 \label{thm_gamma_smooth}
-Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:\\
-For any $\adj{\dataobs}{\dataobs'}$:
-\begin{equation}
-\label{eq_gamma_smooth}
-\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
-\end{equation}
-
+Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
+whenever $\adj{\dataobs}{\dataobs'}$, 
+%\begin{equation}
+%\label{eq_gamma_smooth}
+$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
+%\end{equation}
 \end{thm}
-Proof is in Appendix I.
+(Proof is in Appendix I.)
 
@@
 \begin{align*}
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
-&= 0.19673467014,\\
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\ 
-&= 0.11932560927,\\
-&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+&\lapmechPr{\dataobs}{
+\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
+} = 0.19673467014,\\
+&\lapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+\end{aligned}
+  } = 0.11932560927,\\
+&\lapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
   \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} \\
-&= 0.07237464051.
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
+  \end{aligned}
+} = 0.07237464051.
 \end{align*}
@@
 \begin{align*}
-&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
-&= 0.31606027941,\\
-&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
-&= 0.11627207896,\\
-&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+&\ilapmechPr{\dataobs}{
+\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
+&\ilapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+  \end{aligned}
+} = 0.116272079,\\
+&\ilapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - 
   \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
   \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
-&= 0.04277410743.
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
+    \end{aligned}
+} = 0.04277411.
 \end{align*}
@@
 %  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
-
   \begin{align*}
@@
 \label{subsec_effi}
-The formula for computing the local sensitivity presented in Sec.
+%The formula for computing the local sensitivity presented in Sec.
 \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
-\[
-LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
-\]
-can be reduced to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
-by applying the distance triangle property.
-
+%\[
+%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+%\]
+By the triangle inequality of Hellinger distance, the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec.
+\ref{sec_mechs} can be simplified to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$.
 Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:

### 2019-01-18 ICML2019/main.tex
pass abstract, section 2 and section 3

--- 2019-01-18 ICML2019/main.tex
@@
 Laplace perturbation of the parameters of the posterior distribution under
-$\ell_1$ norm, and compare them with a discrete mechanism calibrating 
-its score function to a smooth bound on the Hellinger distance.
+$\ell_1$ norm, and compare them with a discrete mechanism
+calibrating noise to a smooth upper bound on the Hellinger distance.
 Accuracy is measured through the Hellinger distance between the posterior
@@
 
-The beta-binomial model can be immediately generalized to the Dirichlet-multinomial model, with underlying data multinomially distributed.
+The Beta-Binomial model can be immediately generalized to the Dirichlet-Multinomial model, with underlying data multinomially distributed.
 The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
@@
 \]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents the Iverson bracket notation.
 Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
@@
 \noindent \textbf{Differential Privacy.}
-\emph{Differential privacy} is a strong quantitative notion of statistical privacy proposed by \cite{}.
+\emph{Differential privacy} is a strong quantitative notion of statistical privacy proposed by \cite{dwork2006}.
 Differential privacy of a mechanism implies that changing the input of a mechanism slightly only reflects
@@
 
-\noindent \textbf{Technical Problem Statement.}
+\noindent \textbf{Problem setting.}
 \label{subsec_problem}
 We are interested in exploring mechanisms for privately releasing the full posterior
-distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
+distributions derived in Section \ref{sec_background}.
 It's worth noticing that the posterior distributions are fully characterized
-by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
-Beta-Binomial model we are interested in releasing a private version of the pair of
+by their parameters, and the family (Beta and Dirichlet distribution) they belong to. Hence, in case of the
+Beta-Binomial model we are interested in releasing a private version of the Beta distribution with 
 parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-multinomial model we are interested in a private version of
+in the case of the Dirichlet-Multinomial model we are interested in a private version of the Dirichlet distribution with parameter
 $\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
@@
 parameters of the posteriors. That is, in the case of the Beta-Binomial system,
-the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
+the values released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
 where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
@@
 $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.\\
+This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Section \ref{sec_mechs}.\\
 However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
@@
 \]
-where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
+where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
 \todo{However, distance between
@@
 of mechanisms by considering different norms. e.g. a norm over space of measures.
-to compute the sensitivity and provide guarantees on the accuracy.\\
-We will use the Hellinger distance $\hellinger(\cdot,\cdot)$, 
+to compute the sensitivity and provide guarantees on the accuracy.
+
+We will use the \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$.
 Given two probability distributions $\textup{P}$ and $\textup{Q}$,
-the Hellinger distance between them is defined as:
-\[
-\hellinger^2(P,Q) = \frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
-\]
-When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above reduces to: 
+the square of the Hellinger distance between them is defined as:
+\[
+\hellinger(P,Q)^2 =\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
+\]
+When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above can be reduced to: 
 \[
@@
 
-  \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an unbounded adversary can have in distingishing two distributions.
-
-  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity},
-    taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
+  \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an adversary can have in distingishing two distributions.
+
+  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. Indeed, as shown in Figure \ref{fig_sensitivity}, there can be a gap
+    between the global sensitivity and the local sensitivity.
 \begin{figure}[ht]

### 2019-01-18 ICML2019/main.tex

@@
 \[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
+\Pr(\dataobs|\vtheta)\equiv\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
 \]

### 2019-01-19 ICML2019/main.tex
Reducing formulas.

@@
 Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
+\todo{Is it correct
+$\lapmechPr{\dataobs}{\ldots}$? }
 \begin{align*}
@@
 Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
+\todo{What is the value of $\varepsilon$?}
+%\begin{align*}
+%&\lapmechPr{\dataobs}{
+%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
+%} = 0.19673467014,\\
+%&\lapmechPr{\dataobs}{
+%\begin{aligned}
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+%\end{aligned}
+%  } = 0.11932560927,\\
+%&\lapmechPr{\dataobs}{
+%\begin{aligned}
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& = 1 - 
+%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%  \cdot
+%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
+%  \end{aligned}
+%} = 0.07237464051.
+%\end{align*}
+%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 \begin{align*}
 &\lapmechPr{\dataobs}{
-\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
-} = 0.19673467014,\\
-&\lapmechPr{\dataobs}{
 \begin{aligned}
-& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
 \end{aligned}
-  } = 0.11932560927,\\
-&\lapmechPr{\dataobs}{
-\begin{aligned}
-& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-& = 1 - 
-  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-  \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
-  \end{aligned}
-} = 0.07237464051.
+}\\
+& \qquad = \begin{cases}
+0.19673467014 & t = 0\\
+0.11932560927 & t = 1\\
+0.07237464051 & t = 2
+\end{cases}.
 \end{align*}
-In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
 Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
+\todo{
+What is the value of $\varepsilon$?
+Do we have the formula
+\[
+\ilapmechPr{\dataobs}{\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+}?
+\]
+}
 %Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
@@
 %  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
+%\begin{align*}
+%&\ilapmechPr{\dataobs}{
+%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
+%&\ilapmechPr{\dataobs}{
+%\begin{aligned}
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+%  \end{aligned}
+%} = 0.116272079,\\
+%&\ilapmechPr{\dataobs}{
+%\begin{aligned}
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& = 1 - 
+%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%  \cdot
+%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
+%    \end{aligned}
+%} = 0.04277411.
+%\end{align*}
+%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 \begin{align*}
 &\ilapmechPr{\dataobs}{
-\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
-&\ilapmechPr{\dataobs}{
 \begin{aligned}
-& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
 \end{aligned}
-} = 0.116272079,\\
-&\ilapmechPr{\dataobs}{
-\begin{aligned}
-& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-& = 1 - 
-  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-  \cdot
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
-    \end{aligned}
-} = 0.04277411.
+}\\
+& \qquad = \begin{cases}
+0.31606027941 & t = 0\\
+0.11627207896 & t = 1\\
+0.04277410743 & t = 2
+\end{cases}.
 \end{align*}
-In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
   \begin{align*}
-  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
+  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
   &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
-  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
 By solving following equations:
-  \[
-  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
-  \]
-  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
-  \[
-  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-   = 0.119325609\ or\ 0.116272079
-  \]
-  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
-  \[
-\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
-    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-    \cdot
-    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
-    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-     = 0.072374641\ or\ 0.042774107
-\]
+%  \[
+  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
+\begin{align*}
+ &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
+ & = 0.19673467 \text{ or } 0.316060279
+\end{align*}
+%  \]
+%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
+%  \[
+%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+\begin{align*}
+  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
+  &= 0.119325609 \text{ or } 0.116272079
+\end{align*}
+%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
+%  \[
+%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
+%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+%    \cdot
+%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+\begin{align*}
+ &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
+ &=0.072374641 \text{ or }  0.042774107
+%\]
+\end{align*}
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
@@
 %\]
-By the triangle inequality of Hellinger distance, the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec.
-\ref{sec_mechs} can be simplified to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$.
-Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
+By the triangle inequality of Hellinger distance,
+the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
+\[
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+\]
+\todo{
+Do we need the experimental on this formula?
+It is proved mathematically by case analysis.
+For any $r \in \mathcal{R}$, we have
+\begin{align*}
+&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+& = 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
+\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
+\end{cases}\\
+& \leq 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+\end{cases}\\
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{align*}
+I think it would be a proposition.
+}
+%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
 %\begin{equation*}
@@
 %\end{split}
-\begin{align*}
-LS(\dataobs)
-& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-\left|~
-\begin{aligned}
-&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
-&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
-\end{aligned}
-\right|\\
-  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
-\end{align*}
+%\begin{align*}
+%LS(\dataobs)
+%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+%\left|~
+%\begin{aligned}
+%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
+%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+%\end{aligned}
+%\right|\\
+%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
+%\end{align*}
 

### 2019-01-19 ICML2019/main.tex
Tweak.

@@
 %\]
-By the triangle inequality of Hellinger distance,
-the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
+Thanks to the symmetry and triangle-inequality of the Hellinger
+distance, we can simplify the local sensitivity.
+\begin{lem}
 \[
@@
 \]
-\todo{
-Do we need the experimental on this formula?
-It is proved mathematically by case analysis.
-For any $r \in \mathcal{R}$, we have
+\end{lem}
+\begin{proof}
+For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
 \begin{align*}
@@
 \begin{cases}
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
-\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
 \end{cases}\\
@@
 \end{align*}
-I think it would be a proposition.
-}
+By taking the supremum, we conclude the statement of this lemma.
+\end{proof}
+
 %In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.

### 2019-01-19 ICML2019/main.tex
fix formulas

--- 2019-01-19 ICML2019/main.tex
@@
 GS = 
-\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
+\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
 |\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 %  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
-Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
-\todo{What is the value of $\varepsilon$?}
+Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
 %\begin{align*}
@@
 
-Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
-\todo{
-What is the value of $\varepsilon$?
-Do we have the formula
-\[
-\ilapmechPr{\dataobs}{\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
+
+\begin{align*}
+&
+\Pr\left[
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
 \end{aligned}
-}?
-\]
-}
+\right]
+\\
+&\qquad = 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
 %Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
@@
 }
-%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
-%\begin{equation*}
-%\begin{split}
-%LS(\dataobs) 
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
-%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
-%\end{split}
-%\begin{align*}
-%LS(\dataobs)
-%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-%\left|~
-%\begin{aligned}
-%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
-%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
-%\end{aligned}
-%\right|\\
-%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
-%\end{align*}
-
-%\end{equation*}
-
-This equation is validated by an experimental result shown in Fig.
+
+% This equation is validated by an experimental result shown in Fig.
 \ref{fig_efficiency}.
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{efficiency.eps}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\label{fig_efficiency}
-\end{figure}
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{efficiency.eps}
+% \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+% \label{fig_efficiency}
+% \end{figure}
 

### 2019-01-19 ICML2019/main.tex

@@
 \end{align*}
-I think it would be a proposition.
-}
+By taking the supremum, we conclude the statement of this lemma.
+\end{proof}
+
+%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
+%\begin{equation*}
+%\begin{split}
+%LS(\dataobs) 
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+%\end{split}
+%\begin{align*}
+%LS(\dataobs)
+%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+%\left|~
+%\begin{aligned}
+%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
+%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+%\end{aligned}
+%\right|\\
+%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
+%\end{align*}
 

### 2019-01-19 ICML2019/main.tex
Fix lemma
move proof into apendix
fix problems in formula
fix typo
fix notation

@@
 \label{sec_mechs}
-\subsection{Calibrating noise w.r.t. $\ell_1$ norm}
+\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
 We start off by presenting a mechanism based on the Laplace primitive.
@@
   \begin{algorithmic}
-  \REQUIRE observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
+  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
   prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
   \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
-  \STATE \quad {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
-  \STATE \quad {\bf let} $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
-  \STATE \quad {\bf let} $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
+  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
+  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
   % \RETURN $a_{k+1}$.
-  \ENSURE $\betad(\tilde{\alpha}, \tilde{\beta})$
+  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
   \end{algorithmic}
@@
 
-\subsection{Improving the sensitivity}
+\subsection{Improving the sensitivity ($\ilapmech$)}
  The accuracy of $\lapmech$ can be reduced to a constant.
@@
   \begin{algorithmic}
-  \REQUIRE observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
   prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
@@
   \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
-  \ENSURE $\dirichlet{\tilde{\valpha}}$
+  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
   \end{algorithmic}
@@
 \[
-  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs')\mid \dataobs' \in \{0,1\}^n\}.
+  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
 \]
@@
 
-\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
+\subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
 Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
@@
 
-\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
+\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity ($\lexpmech$)}
 \label{subsec_emls}
@@
 
-\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity}
+Thanks to the symmetry and triangle-inequality of the Hellinger
+distance, we can simplify the local sensitivity.
+\begin{lem}
+\[
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+\]
+\end{lem}
+
+(Proof is in Appendix IV.)
+
+\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity ($\hexpmech$)}
 \label{subsec_hexpmech}
@@
 Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
-\todo{Is it correct
-$\lapmechPr{\dataobs}{\ldots}$? }
 \begin{align*}
 &
-\Pr\left[
+\lapmechPr{\dataobs}{
 \begin{aligned}
@@
 \end{aligned}
-\right]
+}
 \\
@@
 &
-\Pr\left[
+\ilapmechPr{\dataobs}{
 \begin{aligned}
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{2}} - e^{- \frac{\epsilon (t + 1)}{2}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{2}} - e^{\frac{\epsilon (t)}{2}}) & t < 0
 \end{cases}
@@
 
-\subsection{Efficiency Evaluation}
-\label{subsec_effi}
-%The formula for computing the local sensitivity presented in Sec.
+% \subsection{Efficiency Evaluation}
+% \label{subsec_effi}
+% %The formula for computing the local sensitivity presented in Sec.
 \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
-%\[
-%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
-%\]
-Thanks to the symmetry and triangle-inequality of the Hellinger
-distance, we can simplify the local sensitivity.
-\begin{lem}
-\[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
-\]
-\end{lem}
-\begin{proof}
-For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
-\begin{align*}
-&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
-& = 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
-\end{cases}\\
-& \leq 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
-\end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
-\end{align*}
-By taking the supremum, we conclude the statement of this lemma.
-\end{proof}
+% %\[
+% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+% %\]
+% Thanks to the symmetry and triangle-inequality of the Hellinger
+% distance, we can simplify the local sensitivity.
+% \begin{lem}
+% \[
+% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+% \]
+% \end{lem}
+% \begin{proof}
+% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
+% \begin{align*}
+% &\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+% & = 
+% \begin{cases}
+% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+% \end{cases}\\
+% & \leq 
+% \begin{cases}
+% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+% \end{cases}\\
+% &= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+% \end{align*}
+% The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+% Hence, we conclude the statement of this lemma.
+% \end{proof}
 
@@
 \end{proof}
+
+\section*{Appendix IV}
+\begin{proof}
+For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
+\begin{align*}
+&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+& = 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+\end{cases}\\
+& \leq 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+\end{cases}\\
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{align*}
+The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+Hence, we conclude the statement of this lemma.
+\end{proof}
 \end{document}

### 2019-01-19 ICML2019/main.tex
pass

--- 2019-01-19 ICML2019/main.tex
@@
 Differential privacy was proposed a decade ago to address these
-situations and it on its way to become a gold standard in data
+situations and it is on its way to become the gold standard in data
 privacy.
@@
 Bayesian inference is a standard statistical tool that is useful to
-estimate a posterior distribution when given a prior distribution and
-some observed data.
+estimate a posterior distribution when a prior distribution is given
+and some data is observed.
 
@@
 motivated by recent developments in the area of probabilistic
-programming where several tools have been proposed to perfor
+programming where several tools have been proposed to perform
 parametric and non-parametric Bayesian inference in an efficient
-way. The in
-for our work is the recent development of
-
-In particular
-we focus on two classical models: the Beta-Binomial and the
-Dirichlet-Multinomial models. These are classical models
-
-Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
-Publishing the posterior distribution inferred from a sensitive dataset can
-leak information about the individuals in the dataset.
+way.
+
+We focus on two classical models: the Beta-Binomial and the
+Dirichlet-Multinomial models. In the Beta-Binomial model the goal
+is to estimate an unknown fraction of a population from a sequence
+of Bernoulli trials each of which is either 0 or 1 and from an initial
+prior belief, a Beta distribution, on that fraction; the trials are assumed to be independent
+given the value of the bias. In the Dirichlet-Multinomial model a Multinomial
+distribution is used to describe categorical data with more than
+two possible outcomes. Similarly, the aim is to learn the various
+unknown proportions of a population from a sequence of trials
+each of which having more than two possible outcomes. Again,
+a prior belief, a Dirichlet distribution, is used to describe the initial knowledge
+about those fractions. The posterior distributions on the proportions will be
+respectively a Beta distribution and a Dirichlet distribution.
+
+In our work  the posterior distribution is the analysis result we obtained from the data.
+While the prior distributions are considerd public information,  publishing the posterior distribution
+inferred from a sensitive dataset can leak information about the individuals in the dataset.
 In order to guarantee differential privacy and to protect the
 individuals' data we can add noise to the posterior before releasing it.
-The amount of the noise that we need to introduced
+The amount of the noise that we need to introduce
 depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
@@
 Sensitivity can be computed in many different ways based on which metric space
-we consider on the output set of the mechanism. In the literature on private Bayesian
-inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
-respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
-A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
-A re-loved question is that of how to measure accuracy. Again,
-this can be answered in different ways based on the metric imposed on the output space, and yet again
+we consider on the output space of the mechanism. In the literature on private Bayesian
+inference (e.g. \cite{zhang2016differential,xiao2012bayesian}), it is usually measured on
+the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
+A more natural approach which we explore here, is to measure sensitivity with respect to
+a metric on the space of inferred probability distributions.
+Another question is that of how to measure accuracy. Again,
+this can be answered in different ways based on the metric
+imposed on the output space, and yet again
 only in few works in literature (e.g. \cite{zhang2016differential})
@@
 \noindent \textbf{Main contributions.}
+What follows is a summary of the main contributions of this work.
 \begin{itemize}
@@
 GS = 
-\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
+\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
 |\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
@@
 Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
-\todo{Is it correct
-$\lapmechPr{\dataobs}{\ldots}$? }
 \begin{align*}
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 %  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
-Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
-%\begin{align*}
-%&\lapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
-%} = 0.19673467014,\\
-%&\lapmechPr{\dataobs}{
-%\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
-%\end{aligned}
-%  } = 0.11932560927,\\
-%&\lapmechPr{\dataobs}{
-%\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-%& = 1 - 
-%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-%  \cdot
-%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
-%  \end{aligned}
-%} = 0.07237464051.
-%\end{align*}
-%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
+Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
 \begin{align*}
 &\lapmechPr{\dataobs}{
+\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
+} = 0.19673467014,\\
+&\lapmechPr{\dataobs}{
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
 \end{aligned}
-}\\
-& \qquad = \begin{cases}
-0.19673467014 & t = 0\\
-0.11932560927 & t = 1\\
-0.07237464051 & t = 2
-\end{cases}.
+  } = 0.11932560927,\\
+&\lapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - 
+  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+  \cdot
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
+  \end{aligned}
+} = 0.07237464051.
 \end{align*}
+In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
 
-Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
-
-\begin{align*}
-&
-\Pr\left[
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-\right]
-\\
-&\qquad = 
-\begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
-\end{cases}
-\end{align*}
+Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
 %Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
@@
 %  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
-%\begin{align*}
-%&\ilapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
-%&\ilapmechPr{\dataobs}{
-%\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
-%  \end{aligned}
-%} = 0.116272079,\\
-%&\ilapmechPr{\dataobs}{
-%\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
-%& = 1 - 
-%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-%  \cdot
-%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
-%    \end{aligned}
-%} = 0.04277411.
-%\end{align*}
-%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 \begin{align*}
 &\ilapmechPr{\dataobs}{
+\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
+&\ilapmechPr{\dataobs}{
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
   \end{aligned}
-}\\
-& \qquad = \begin{cases}
-0.31606027941 & t = 0\\
-0.11627207896 & t = 1\\
-0.04277410743 & t = 2
-\end{cases}.
+} = 0.116272079,\\
+&\ilapmechPr{\dataobs}{
+\begin{aligned}
+& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+& = 1 - 
+  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+  \cdot
+  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
+    \end{aligned}
+} = 0.04277411.
 \end{align*}
+In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
 
@@
   \begin{align*}
-  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
+  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
   &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
-  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
 By solving following equations:
-%  \[
-  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
- & = 0.19673467 \text{ or } 0.316060279
-\end{align*}
-%  \]
-%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
-%  \[
-%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
-  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
-  &= 0.119325609 \text{ or } 0.116272079
-\end{align*}
-%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
-%  \[
-%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
-%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
-%    \cdot
-%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
-%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
- &=0.072374641 \text{ or }  0.042774107
-%\]
-\end{align*}
+  \[
+  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
+  \]
+  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
+  \[
+  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+   = 0.119325609\ or\ 0.116272079
+  \]
+  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
+  \[
+\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
+    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
+    \cdot
+    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
+    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+     = 0.072374641\ or\ 0.042774107
+\]
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
@@
 %\]
-By the triangle inequality of Hellinger distance,
-the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
-\[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
-\]
-\todo{
-Do we need the experimental on this formula?
-It is proved mathematically by case analysis.
-For any $r \in \mathcal{R}$, we have
+By the triangle inequality of Hellinger distance, the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec.
+\ref{sec_mechs} can be simplified to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$.
+Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
+%\begin{equation*}
+%\begin{split}
+%LS(\dataobs) 
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+%\end{split}
 \begin{align*}
-&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
-& = 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
-\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
-\end{cases}\\
-& \leq 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
-\end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+LS(\dataobs)
+& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+\left|~
+\begin{aligned}
+&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
+&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{aligned}
+\right|\\
+  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
 \end{align*}
-I think it would be a proposition.
-}
-
-% This equation is validated by an experimental result shown in Fig.
+
+%\end{equation*}
+
+This equation is validated by an experimental result shown in Fig.
 \ref{fig_efficiency}.
@@
 
-% \begin{figure}[ht]
-% \centering
-% \includegraphics[width=0.45\textwidth]{efficiency.eps}
-% \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-% \label{fig_efficiency}
-% \end{figure}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.45\textwidth]{efficiency.eps}
+\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
+\label{fig_efficiency}
+\end{figure}
 

### 2019-01-20 ICML2019/main.tex
Tweak

--- 2019-01-19 ICML2019/main.tex
@@
 where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
-\begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
-\end{equation}
+\begin{equation*}\label{eq:local_sensitivity_scoring}
+LS(\dataobs)= \max_{\substack{\dataobs' \in \datauni^n: \adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
+\end{equation*}
+%
+Thanks to the symmetry and triangle-inequality of the Hellinger
+distance, we can simplify the local sensitivity.
+\begin{lem}
+\[
+LS(\dataobs) = \max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+\]
+\end{lem}
+
+(Proof is in Appendix IV.)
 
@@
 \section{Accuracy Analysis}
-
+In this section, we fix $\alpha$ and $\beta$.
+For simplicity, for any integer $t$, we write
+$
+c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+$
 \subsection{Accuracy Bound for Baseline Mechanisms}
@@
 \Pr\left[
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+%\end{aligned}
+\hellinger(\bysinfer(\dataobs), z ) = c(t)
 \right]
@@
 &\lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+%\end{aligned}
+\hellinger(\bysinfer(\dataobs), z ) = c(t)
 }\\
@@
 Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
-
+%
 \begin{align*}
@@
 &\ilapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+%\end{aligned}
+\hellinger(\bysinfer(\dataobs), z ) = c(t)
 }\\
@@
   \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
-  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
-  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}%\\
+%  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
- & = 0.19673467 \text{ or } 0.316060279
-\end{align*}
+ & \qquad = 0.19673467 \text{ or } 0.316060279,\\
+%\end{align*}
 %  \]
@@
 %   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
+%\begin{align*}
   &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
-  &= 0.119325609 \text{ or } 0.116272079
-\end{align*}
+  & \qquad = 0.119325609 \text{ or } 0.116272079,\\
+%\end{align*}
 %  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
@@
 %    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
+%\begin{align*}
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
- &=0.072374641 \text{ or }  0.042774107
+ & \qquad = 0.072374641 \text{ or }  0.042774107
 %\]
@@
 \end{proof}
+
+\section{Appendix IV}
+\begin{proof}
+For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
+\begin{align*}
+&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+& = 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+\end{cases}\\
+& \leq 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+\end{cases}\\
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{align*}
+The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+Hence, we conclude the statement of this lemma.
+\end{proof}
 \end{document}

### 2019-01-20 ICML2019/main.tex
pass on section 3

@@
 	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g.
-Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
-2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
-  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
-	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
+    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
+	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions
+      (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale
+      the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
+  \item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing their performances in terms of accuracy and privacy.
 \end{itemize}
@@
 where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
-\todo{However, distance between
-distributions are more naturally to be measured by distribution
-metrics such as $f$-divergence, Hellinger distance, etc., than the $\ell_1$ norm shown above.}
-{\color{blue} changed a bit, still not sure this is a good way to put it...}
+However, distance between
+distributions are more naturally  measured by distribution
+metrics such as $f$-divergences, e.g. Hellinger distance, etc., than the $\ell_1$ norm shown above.
+{\color{blue} still not sure this is a good way to put it...}
 This gives us motivation for exploring the design space
@@
 \]
-When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above can be reduced to: 
+When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$, we can unfold the above and derive: 
 \[
@@
 \includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
-\caption{{The local sensitivity of $\hellinger$}}
+\caption{Local sensitivity of $\hellinger$. Data size is 100. $\alpha$ is the number of 1s.}
 \label{fig_sensitivity}
@@
 We start off by presenting a mechanism based on the Laplace primitive.
-The mechanism, denoted by {\color{red}{i think this macro has too many arguments}}($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$),
+The mechanism, denoted by $\lapmech$, takes in input the data $\dataobs$, a mechanism, $\bysinfer$, that is used to perform inference on some parameter,
+a prior and a likelihood function, and the $\epsilon$ parameter measuring the privacy level.
+Now, $\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$,
 simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
-post-processing phase by {\color{red}{flooring}} and  truncating the noisy parameters so that they belong to the right interval.
+post-processing phase by flooring and  truncating the noisy parameters so that they belong to the right interval.
 In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
@@
 $[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
-Since we are adding noise directly to the parameter, the sensitivity should be calibrated to $\ell_1$ of two Beta distributions:
-$
+Since we are adding noise directly to the parameters, the sensitivity should be calibrated w.r.t $\ell_1$-norm. That is,
+the sensitivity is defined as:
+\[
    \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
-$,
-i.e., proportional to the dimensionality.
+\]
+This value can be quickly seen as being upper bounded by  the dimensionality. (e.g. 2 for the Beta-Binomial model and  $k$ for
+the Dirichlet-Multinomial model).
   \begin{algorithm}
-  \caption{$\lapmech$ in Beta-binomial model}
+  \caption{$\lapmech$ for the Beta-Binomial model}
   \label{mech:lapmech}
@@
  $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
- with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}.
+ with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}. We will also from now on
+ write $\ilapmech(\dataobs)$ when the other parameters are obvious from the context.
   \begin{algorithm}
-  \caption{$\ilapmech$ in Dirichlet-multinomial model}
+  \caption{$\ilapmech$ in Dirichlet-Multinomial model}
   \label{mech:ilapmech}
@@
 
-\subsection{A new mechanism}
-In this section, we explore a new mechanism which we denote by $\expmech$.
+\subsection{A new family of mechanisms}
+In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
+of the exponential mechanism \cite{??} where the scoring function is based on a metric over
+probability distributoins.
 The idea is that $\expmech$ will sample and output a distribution with higher probability when
-it is closer to the real posterior; importantly  \emph{closer} is measured using a metric over probability
+it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
 distributions as opposed to a metric over the parameters that represent it. In this work we will
@@
 \]
+Where $\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)$ denotes the posterior beta distribution inferred starting from the parameters in input.
 Notice that the above set reduces to:
@@
 
-\subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
-Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\[
-\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
-{\exp(\frac{\epsilon u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
-\]
-where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
-the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
+\subsubsection{A first approach: the $\expmech$ mechanism}
+$\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
+\[
+%\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
+\frac
+  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})},
+\]
+where $u(x,r)$ is the Hellinger scoring function: $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
 \begin{equation*}
-GS = 
+GS \equiv 
 \max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
@@
 \end{equation*}
-
-\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity ($\lexpmech$)}
+Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{??} proves privacy $\epsilon$ differential privacy of $\expmech$.
+
+\subsubsection{A second approach based on local sensitivity: $\lexpmech$}
 \label{subsec_emls}
-In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$.
-This is just an attempt since local sensitivity is non-private.
-$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
-\[
-\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
+Figure \ref{??} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
+$GS$ is relatively big and hence the variance of the distribution $\expmech$ ends up also being too big. In order to solve this issue we
+will proceed in two steps. We will first define $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
+the noise. This is known to be a non private approach, but it will guide us towards new insights.
+We will then proceed to use a smooth bound the local sensitivity to
+calibrate the noise.
+
+$\lexpmech$ shares candidate set and utility function with $\expmech$,
+and outputs a result $r \in \mathcal{R}$ with probability:
+\[
+%\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
+{\Pr}[z=r] = \frac
   {\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
@@
 \]
-where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
+where $LS(\dataobs)$ is the local sensitivity of the scoring function, defined as:
 \begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
+LS(\dataobs)\equiv\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
 \end{equation}
-
-Thanks to the symmetry and triangle-inequality of the Hellinger
-distance, we can simplify the local sensitivity.
+The above can be proven to simplify to:
 \begin{lem}
@@
 \end{lem}
-
-(Proof is in Appendix IV.)
-
-\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity ($\hexpmech$)}
+The interested reader can check the proof in the Appendix \ref{??}.
+
+\subsubsection{A third approach based on smooth sensitivity: $\hexpmech$}
 \label{subsec_hexpmech}
-In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and differential privacy simultaneously, by scaling the noise to a new sensitivity.
-We first define the new sensitivity we are going to use and then present the mechanism.
+In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and $\epsilon$-differential privacy simultaneously,
+by scaling the noise to a smooth upper bound on the local sensitivity.
+We first define the smooth sensitivity on a input $\dataobs$. The following definition is specific to binary data, that is it will
+be useful to privately release a posterior Beta distribution. The extension to categorical data is straightforward.
 \begin{definition}
 \label{def_gamma_smooth}
-Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
+Given a data set $\dataobs$ of size $n$, we define the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer(\dataobs),\cdot)$ as:
 \begin{equation}
   \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
@@
   \label{thm_gamma_smooth}
-Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
-whenever $\adj{\dataobs}{\dataobs'}$, 
-%\begin{equation}
-%\label{eq_gamma_smooth}
-$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
-%\end{equation}
+  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
+  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
 \end{thm}
-(Proof is in Appendix I.)
-
-\begin{definition}
-\label{def_smoo_2}
-$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} = \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
+The interested reader will find the proof in Appendix \ref{??}.
+We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+\[\frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
 {\unomalizer{\dataobs}}.
-\end{equation*}
-where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Definition \ref{def_gamma_smooth} by setting $\gamma = 1$.
-\end{definition}
-Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet{\valpha}$ by rewriting the Hellinger distance as:
+\]
+where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
+
+As already mentioned $\expmech, \lexpmech, \sexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
+Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
 \[
@@
 \]
-and by replacing the $\candidateset$ with set of posterior Dirichlet
+and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
 distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
@@
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
-will denote by $\hexpmechd$ the mechanism for the
-Dirichlet-multinomial system.
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here?}}
 

### 2019-01-20 ICML2019/main.tex
first pass section 4

@@
 \end{definition}
+
+It is possible to achieve $\epsilon$-differential privacy through use and composition of
+a few basic components. Some of these components are now reviewed.
+
+\noindent \emph{Laplace mechanism.}
+The Laplace mechanism releases a random number drawn from the Laplace distribution with
+mean $\mu=q(d)$ and scale $\nu$. Where $q$ is a numeric query on a database $d$.
+If $\nu\geq \frac{\Delta_f}{\epsilon}$, with $\Delta_f=\displaystyle\max_{d,d':\adj{d}{d'}}{\lvert f(d_1)-f(d_2)\lvert}$
+then the mechanism is $\epsilon$-differentially private as proven in \cite{???}.
+
+\noindent \emph{Exponential mechanism.}
+
+\noindent \emph{Composition.}
+
+\noindent \emph{Postprocessing.}
 
@@
 %\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
-{\Pr}[z=r] = \frac
-  {\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
+\frac
+  {\exp(\frac{\epsilon \cdot u(x,r)}{2\cdot LS(\dataobs)})}
+{\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS(\dataobs)})},
 \]
@@
 We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\[\frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
-{\unomalizer{\dataobs}}.
+\[
+  \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
+  {\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{4\cdot S(\dataobs)})},
 \]
@@
 
-As already mentioned $\expmech, \lexpmech, \sexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
+As already mentioned $\expmech, \lexpmech, \hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
 Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
@@
 over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here?}}
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here? and was $\datauni$} defined?}
 
@@
 \subsection{Privacy of Laplace Mechanism Family}
-Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
+Mechanisms $\lapmech$ and $\ilapmech$ are trivially $\epsilon$-differentially private since the mechanisms
+add Laplacian noise proportional to the $\ell_1$-norm sensitivity to the arguments of the posterior distributions.
+\begin{lem}
+  $\lapmech$, $\ilapmech$ are $\epsilon$-differentially private.
+\end{lem}
 
@@
 
-\subsubsection{$\lexpmech$ non-Differential Privacy}
-Exponential mechanism with local sensitivity non-differential privacy.
+% \subsubsection{$\lexpmech$ non-Differential Privacy}
+% Exponential mechanism with local sensitivity non-differential privacy.
 
@@
 
-We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$), standard exponential mechanism ($\mathsf{expMech}$), non-private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
+We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$),
+standard exponential mechanism ($\mathsf{expMech}$),
+non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
 
@@
 \ref{fig_theory}, it can be derived that all these mechanisms (except standard exponential mechanism $\expmech$ in green line) can output good results with larger probability.
-The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non-private.
+The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non private.
 For these are $\epsilon -$differentially private, the improved laplace mechanism $\ilapmech$ with $\ell_1$ norm metric can produce good results with higher probability, i.e., perform better in terms of accuracy than others.

### 2019-01-20 ICML2019/main.tex
fix appednix

--- 2019-01-20 ICML2019/main.tex
@@
 Differential privacy was proposed a decade ago to address these
-situations and it is on its way to become the gold standard in data
+situations and it on its way to become a gold standard in data
 privacy.
@@
 Bayesian inference is a standard statistical tool that is useful to
-estimate a posterior distribution when a prior distribution is given
-and some data is observed.
+estimate a posterior distribution when given a prior distribution and
+some observed data.
 
@@
 motivated by recent developments in the area of probabilistic
-programming where several tools have been proposed to perform
+programming where several tools have been proposed to perfor
 parametric and non-parametric Bayesian inference in an efficient
-way.
-
-We focus on two classical models: the Beta-Binomial and the
-Dirichlet-Multinomial models. In the Beta-Binomial model the goal
-is to estimate an unknown fraction of a population from a sequence
-of Bernoulli trials each of which is either 0 or 1 and from an initial
-prior belief, a Beta distribution, on that fraction; the trials are assumed to be independent
-given the value of the bias. In the Dirichlet-Multinomial model a Multinomial
-distribution is used to describe categorical data with more than
-two possible outcomes. Similarly, the aim is to learn the various
-unknown proportions of a population from a sequence of trials
-each of which having more than two possible outcomes. Again,
-a prior belief, a Dirichlet distribution, is used to describe the initial knowledge
-about those fractions. The posterior distributions on the proportions will be
-respectively a Beta distribution and a Dirichlet distribution.
-
-In our work  the posterior distribution is the analysis result we obtained from the data.
-While the prior distributions are considerd public information,  publishing the posterior distribution
-inferred from a sensitive dataset can leak information about the individuals in the dataset.
+way. The in
+for our work is the recent development of
+
+In particular
+we focus on two classical models: the Beta-Binomial and the
+Dirichlet-Multinomial models. These are classical models
+
+Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
+Publishing the posterior distribution inferred from a sensitive dataset can
+leak information about the individuals in the dataset.
 In order to guarantee differential privacy and to protect the
 individuals' data we can add noise to the posterior before releasing it.
-The amount of the noise that we need to introduce
+The amount of the noise that we need to introduced
 depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
@@
 Sensitivity can be computed in many different ways based on which metric space
-we consider on the output space of the mechanism. In the literature on private Bayesian
-inference (e.g. \cite{zhang2016differential,xiao2012bayesian}), it is usually measured on
-the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
-A more natural approach which we explore here, is to measure sensitivity with respect to
-a metric on the space of inferred probability distributions.
-Another question is that of how to measure accuracy. Again,
-this can be answered in different ways based on the metric
-imposed on the output space, and yet again
+we consider on the output set of the mechanism. In the literature on private Bayesian
+inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
+respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
+A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
+A re-loved question is that of how to measure accuracy. Again,
+this can be answered in different ways based on the metric imposed on the output space, and yet again
 only in few works in literature (e.g. \cite{zhang2016differential})
@@
 \noindent \textbf{Main contributions.}
-What follows is a summary of the main contributions of this work.
 \begin{itemize}
@@
 the extension to the Dirichelet-Multinomial model is straightforward.
-Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
+Given a prior distribution $\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
 we define the follwing set  where the mechanism will sample from:
 \[
-  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
+  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta),\dataobs)\mid \dataobs \in \{0,1\}^n\}.
 \]
@@
 \subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
-Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
-\[
-\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
-{\exp(\frac{\epsilon u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
-\]
-where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
+Our exploration starts from the standard exponential mechanism $\expmech(\dataobs,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(\dataobs,r)}{2 GS})$:
+\[
+\underset{z \thicksim \expmech(\dataobs,u,\candidateset) }{\Pr}[z=r] = \frac
+{\exp(\frac{- \epsilon u(\dataobs,r)}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(\dataobs,r')}{2 GS})},
+\]
+where $u(\dataobs,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
 the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
@@
 \end{equation*}
+  \begin{algorithm}
+  \caption{$\expmech$ in Beta-binomial model}
+  \label{mech:expmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
+  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
+  \end{algorithmic}
+  \end{algorithm}
 
@@
 \label{subsec_emls}
-In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$.
+In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(\dataobs,u,\candidateset)$.
 This is just an attempt since local sensitivity is non-private.
-$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
+$\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{- \epsilon u(\dataobs,r)}{2 LS(\dataobs)})$:
 \[
 \underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
-{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
+{\exp(\frac{- \epsilon u(\dataobs,r)}{2 LS(\dataobs)})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(\dataobs,r')}{2 LS(\dataobs)})},
 \]
@@
 \begin{lem}
+\label{lem_loc_opt}
 \[
@@
 
-(Proof is in Appendix IV.)
+(Proof is in Appendix.)
 
@@
 \subsection{Privacy of Laplace Mechanism Family}
-Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+\begin{lem}
+$\lapmech$ and $\ilapmech$ are $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
+\end{lem}
 
@@
 \subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
-Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+\begin{lem}
+$\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
+\end{lem}
 
 \subsubsection{$\lexpmech$ non-Differential Privacy}
-Exponential mechanism with local sensitivity non-differential privacy.
+\begin{lem}
+$\lexpmech$ is non-differentially private.
+\end{lem}
 
@@
 \end{lem}
-(Proof is in Appendix II)
+(Proof is in Appendix)
 
@@
 \newpage
-\section*{Appendix I}
-\label{app_sensitivity}
+\section*{Appendix}
+
+\noindent \textbf{Theorem \ref{thm_gamma_smooth}.}
+\emph{
+Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
+whenever $\adj{\dataobs}{\dataobs'}$, 
+%\begin{equation}
+%\label{eq_gamma_smooth}
+$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
+}
+
 \begin{proof}
@@
 
-\section*{Appendix II}
-\label{app_privacyproof}
+\noindent \textbf{Lemma \ref{lem_loc_opt}.}
+\emph{
+\[
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+\]
+}
+
+\begin{proof} of Lemma \ref{lem_loc_opt}.\\
+For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
+\begin{align*}
+&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+& = 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+\end{cases}\\
+& \leq 
+\begin{cases}
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+\end{cases}\\
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+\end{align*}
+The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+Hence, we conclude the statement of this lemma.
+\end{proof}
+
+\noindent \textbf{ Lemma \ref{lem_hexpmech_privacy}. } 
+\emph{
+$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
+}
+
 \begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
@@
 
-\section*{Appendix III}
-\begin{proof} of Lemma \ref{lem_acc_lap}.
-
+\noindent \textbf{ Lemma \ref{lem_acc_lap}.}
+\emph{
+Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
+\begin{align*}
+&
+\lapmechPr{\dataobs}{
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+}
+\\
+&\qquad = 
+\begin{cases}
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\end{cases}
+\end{align*}
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+}
+
+\begin{proof} of Lemma \ref{lem_acc_lap}.\\
 Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
@@
 
-\section*{Appendix IV}
-\begin{proof}
-For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
-\begin{align*}
-&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
-& = 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
-\end{cases}\\
-& \leq 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
-\end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
-\end{align*}
-The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
-Hence, we conclude the statement of this lemma.
-\end{proof}
 \end{document}

### 2019-01-20 ICML2019/main.tex

--- 2019-01-20 ICML2019/main.tex
@@
 
+% <<<<<<< HEAD
+% \subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
+% Our exploration starts from the standard exponential mechanism $\expmech(\dataobs,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(\dataobs,r)}{2 GS})$:
+% \[
+% \underset{z \thicksim \expmech(\dataobs,u,\candidateset) }{\Pr}[z=r] = \frac
+% {\exp(\frac{- \epsilon u(\dataobs,r)}{2 GS})}
+% {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(\dataobs,r')}{2 GS})},
+% \]
+% where $u(\dataobs,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
+the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
+% =======
 \subsubsection{A first approach: the $\expmech$ mechanism}
@@
 \end{equation*}
+
+  \begin{algorithm}
+  \caption{$\expmech$ in Beta-binomial model}
+  \label{mech:expmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
+  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
+  \end{algorithmic}
+  \end{algorithm}
+
 Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{??} proves privacy $\epsilon$ differential privacy of $\expmech$.
@@
 \label{subsec_emls}
+
 Figure \ref{??} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
@@
 \subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
-Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
+\begin{lem}
+$\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
+\end{lem}
 

### 2019-01-21 ICML2019/main.tex
add algorithms

@@
 
-% <<<<<<< HEAD
-% \subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
-% Our exploration starts from the standard exponential mechanism $\expmech(\dataobs,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(\dataobs,r)}{2 GS})$:
-% \[
-% \underset{z \thicksim \expmech(\dataobs,u,\candidateset) }{\Pr}[z=r] = \frac
-% {\exp(\frac{- \epsilon u(\dataobs,r)}{2 GS})}
-% {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(\dataobs,r')}{2 GS})},
-% \]
-% where $u(\dataobs,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e.
-the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
-% =======
 \subsubsection{A first approach: the $\expmech$ mechanism}
@@
 \end{equation*}
-
+%
   \begin{algorithm}
@@
   \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
-  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
-  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
-  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
-  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
-  % \RETURN $a_{k+1}$.
-  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
-  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \STATE \quad {\bf For} $r$ in $\candidateset$:
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
+  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+  \STATE {\bf return} $z$
   \end{algorithmic}
@@
 calibrate the noise.
+
+  \begin{algorithm}
+  \caption{$\lexpmech$ in Beta-binomial model}
+  \label{mech:expmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \STATE \quad {\bf For} $r$ in $\candidateset$:
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
+  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+  \STATE {\bf return} $z$
+  \end{algorithmic}
+  \end{algorithm}
 
@@
 \end{lem}
-The interested reader can check the proof in the Appendix \ref{??}.
+The interested reader can check the proof in the Appendix.
 
@@
 where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
+  \begin{algorithm}
+  \caption{$\hexpmech$ in Beta-binomial model}
+  \label{mech:expmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \STATE \quad {\bf For} $r$ in $\candidateset$:
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
+  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+  \STATE {\bf return} $z$
+  \end{algorithmic}
+  \end{algorithm}
 

### 2019-01-21 ICML2019/main.tex
add algorithms

@@
   prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $GS$ be the global sensitivity of scoring function.  
   \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
@@
   prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $LS$ be the local sensitivity of scoring function.  
   \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
@@
   \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+  {\exp(\frac{\epsilon\cdot u(x,r)}{2 LS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS})}$
 \STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
@@
 \end{thm}
-The interested reader will find the proof in Appendix \ref{??}.
+The interested reader will find the proof in Appendix.
 We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
@@
   prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $S(\dataobs)$ be the vector of $\gamma-$sensitivity of scoring function. 
   \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
@@
   \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+  {\exp(\frac{\epsilon \cdot \ux{r}}{2 S(\dataobs)})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot}{2\cdot S(\dataobs)})}$
 \STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.

### 2019-01-21 codes/discrete_probability_on_betabinomial.py
update plots

@@ -255,11 +255,11 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 
 	labels = [
-		r'$\mathsf{expMech}^{smoo}$ ',
-		r"$\mathsf{expMech}^{local}$",
-		r"$\mathsf{expMech}$",
-		r'$\mathsf{ilapMech}$ (sensitivity = '+ str(sensitivity1) +')', 
-		r'$\mathsf{lapMech}$ (sensitivity = '+ str(sensitivity2) +')']
+		r'Alg 5 - $\mathsf{EHDS}$ ',
+		r"Alg 4 - $\mathsf{EHDL}$",
+		r"Alg 3 - $\mathsf{EHD}$",
+		r'Alg 1 - $\mathsf{LSDim}$ (sensitivity = '+ str(sensitivity2) +')', 
+		r'Alg 2 - $\mathsf{LSHist}$ (sensitivity = '+ str(sensitivity1) +')']
 
 
 	#############################################################################
@@ -267,16 +267,20 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 	#############################################################################
 
 	plt.figure()
-	plt.plot(step, exp_gamma, 'o', label=(labels[0]))
-
-
-	plt.plot(step, exp_LS, '-', label=(labels[1]))
+	plt.plot(step, lap_2, '-',color = 'lightblue', label=(labels[3]))
+	
+	plt.plot(step, lap_1,'-', color = 'navy', label=(labels[4]))
 
 	plt.plot(step, exp_GS, '-', label=(labels[2]))
 
-	plt.plot(step, lap_1,'-', color = 'navy', label=(labels[3]))
+	plt.plot(step, exp_LS, '-', label=(labels[1]))
 
-	plt.plot(step, lap_2, '-',color = 'lightblue', label=(labels[4]))
+	plt.plot(step, exp_gamma, '-', label=(labels[0]))
+
+
+
+
+
 
 	# plt.plot(step, exp,  label=(labels[0]))
 
@@ -296,7 +300,7 @@ def row_discrete_probabilities(sample_size,epsilon,delta,prior,observation):
 
 	plt.xlabel("c / Hellinger distance from true posterior")
 	plt.ylabel("Pr[H(BI(x),r) = c]")
-	plt.title("Discrete Probabilities", fontsize=15)
[…]

### 2019-01-21 ICML2019/main.tex
add algorithms
update plots
fix bib file

@@
 \frac
-  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})},
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
+{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot GS})},
 \]
@@
   \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot GS})}$
 \STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
@@
 
-Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{??} proves privacy $\epsilon$ differential privacy of $\expmech$.
+Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{lem_exp_private} proves privacy $\epsilon$ differential privacy of $\expmech$.
 
@@
 
-Figure \ref{??} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
+Figure \ref{fig_theory} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
 $GS$ is relatively big and hence the variance of the distribution $\expmech$ ends up also being too big. In order to solve this issue we
@@
   \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot u(x,r)}{2 LS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS})}$
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 LS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot LS})}$
 \STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
@@
 \frac
-  {\exp(\frac{\epsilon \cdot u(x,r)}{2\cdot LS(\dataobs)})}
-{\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS(\dataobs)})},
+  {\exp(\frac{\epsilon \cdot \ux{r}}{2\cdot LS(\dataobs)})}
+{\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot LS(\dataobs)})},
 \]
@@
   \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
-  {\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{4\cdot S(\dataobs)})},
+  {\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{4\cdot S(\dataobs)})},
 \]
@@
   \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon \cdot \ux{r}}{2 S(\dataobs)})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot}{2\cdot S(\dataobs)})}$
+  {\exp(\frac{\epsilon \cdot \ux{r}}{4 S(\dataobs)})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot \ux{r'}}{4 \cdot S(\dataobs)})}$
 \STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
@@
 \begin{lem}
+\label{lem_exp_private}
 $\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
@@
 \end{lem}
-(Proof is in Appendix III)
+(Proof is in Appendix)
 
@@
 
-\newpage
-\section*{Appendix}
+\appendix
 

### 2019-01-21 ICML2019/main.tex
tweak
moved related works
sketch of points for the intro

@@
 \label{sec_intro}
+%%Data analysis and privacy are important
 Data analysis techniques have brought significant improvements in a
@@
 
+%%Bayesian inference is a standard tool for data analysis which is
+%% also a building block of probabilistic programming languages
 Bayesian inference is a standard statistical tool that is useful to
@@
 
+%%Several works have considered differentially private bayesian
+%%inference
+
+%%we consider bayesian inference with posterior perturbation 
+%%which could be used as a plug and play in PPL citing CCS2016
 In this work we consider the design space of  parametric Bayesian
@@
 way.
+
+%%we focus on discrete simple models
+
+%%we focus on hellinger distance
+
+%%the contribution is a comparative study of several ways to achieve
+%%differential privacy in this setting.
+
+%%findings: Laplace with histogram is the best mechanism and this is
+%%because when the data size grows the hellinger between the
+%%posteriors induced by adjacent datasets decreases, and so the impact
+%%of Laplace also decreases. This is a particular case because of the
+%%hellinger, if the Laplace is added accordingly to the dimension the
+%%performance is worse. The exponential with smooth sensitivity is
+%%better than the standard exponential with global sensitivity but it
+%%does not achieve the same performance as the previous ones.
 
@@
 \end{itemize}
+
+\section{Related Work}
+
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
+
+In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+\cite{dimitrakakis2014robust,zhang2016differential,zheng2015differential,wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
+3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
+The third topic where our work focus on is still very new.
+moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism.
+That's why we explore different metrics and different algorithms over the design space.
 
@@
 
-\section{Related Work}
-
-A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
-
-In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
-3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
-The third topic where our work focus on is still very new.
-moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism.
-That's why we explore different metrics and different algorithms over the design space.
-
 \section{Conclusion}

### 2019-01-21 ICML2019/main.tex
pass section 4

--- 2019-01-21 ICML2019/main.tex
@@
 
+\section{Related Work}
+
+A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
+
+In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
+\cite{dimitrakakis2014robust,zhang2016differential,zheng2015differential,wang2015privacy}.
+2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
+3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
+The third topic where our work focus on is still very new.
+moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism.
+That's why we explore different metrics and different algorithms over the design space.
+
 \section{Preliminaries}
@@
 \label{sec_mechs}
+In this section we will describe and analyse a series of mechanisms.
+Section \ref{sec_ell1_dim} presents a first mechanism called $\lapmech$ based on the Laplace primitive
+where the sensitivity is measured w.r.t. to $\ell_1$ norm.
+We will then notice, Section \ref{??}, that this mechanism's accuracy can be improved by performing a better analysis on
+the sensitivity of the inference process.
+Section \ref{???}, shows an instance of the exponential mechanism where the scoring
+function is based on the Hellinger distance, we will see how this mechanisms performs
+poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
+Section \ref{???}
 \subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
+\label{sec_ell1_dim}
 We start off by presenting a mechanism based on the Laplace primitive.

### 2019-01-22 ICML2019/main.tex
working on the problem statement

--- 2019-01-21 ICML2019/main.tex
@@
 Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
-and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is defined as:
+and an observation $\dataobs$, the posterior distribution on $\theta$
+given $\dataobs$ is defined by Bayes' Theorem as:
 \[
-  \Pr(\theta | \dataobs) \equiv \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
+  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
 \]
@@
 \emph{likelihood} of observing $\dataobs$ under a value of
-$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
-a function of $\theta$.
-For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
-Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
-the initial belief on $\theta$, that is, when no data has been observed. In practice though,
-prior distributions and likelihood functions are usually chosen so that the posterior
-belongs to the same \emph{family} of distribution of the prior. In this case we say that the prior
+$\theta$. 
+% Since we consider $\dataobs$ to be fixed, the likelihood is
+% a function of $\theta$.
+% For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
+% Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
+% the initial belief on $\theta$, that is, when no data has been
+% observed. In practice though,
+In parametric statistics, prior distributions and likelihood functions are usually chosen so that the posterior
+belongs to the same \emph{family} of distributions as the prior. In this case we say that the prior
 is conjugate to the likelihood function. Use of a conjugate prior
 simplifies calculations and allows for inference to be performed in a
-recursive fashion over the data.
-% Then, we have:
+recursive fashion over the data. This approach is implemented in a
+precise or approximate way in the compiler of several
+probabilistic programming languages~\cite{}.
+
+%  support bayesian inference
+% by means of a language primitive, often called $\bysinfer$, which
+% supports the (precise or approximate) parametric computation of the
+% posterior of a given model. In the rest of the paper, we will use the following
+% notation as a shorthand for the inference process:
 % \[
@@
 % \]
-% \noindent \textbf{Beta-binomial System.}
-In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-We will consider the situation where the underlying data is drawn from a binomial distribution
-($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
-the parameter --informally called \emph{bias}-- of a Bernoulli
-distributed random variable and $n$ is the number of draws. The
-prior distribution over $\theta\in [0,1]$ is going to be a beta
-distribution, $\betad(\alpha, \beta)$, with parameters
-$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+\noindent \textbf{Dirichlet-multinomial model.}
+In this work we will focus on the Dirichlet-Multinomial model for
+categorical data and its restriction to binary data: the Beta-Binomial
+model. 
+That is, we will consider the situation where 
+the underlying categorical data is drawn from a multinomial
+distribution with parameter the vector $\vtheta\in [0,1]^{k}$. The prior distribution over $\vtheta$
+is given by a Dirichlet distribution, $\dirichlet{\valpha}$, for,
+$\valpha\in(\mathbb{R}^{+})^{k}$ and $k\in\mathbb{N}$, with p.d.f:
 \[
-  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
-\]
-where $\betaf(\cdot,\cdot)$ is the beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
-\[
-  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
-\]
-where $\Delta \alpha = \sum_{i=1}^{n}x_i$.
-The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
-From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
-posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
-in section \ref{} when the private mechanisms will be described.
-% \noindent \textbf{Dirichlet-multinomial Systems.}
-
-The Beta-Binomial model can be immediately generalized to the Dirichlet-Multinomial model, with underlying data multinomially distributed.
-The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
-is given by a Dirichlet distribution, $\dirichlet{\valpha}$, for $k\in\mathbb{N}$,
-and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
-\[
-\Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
+\Pr(\vtheta)=\frac{1}{\mbetaf(\valpha)}\cdot\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
 \]
 where $\mbetaf(\cdot)$ is the generalized beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
-coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
-The likelihood function will be:
-\[
-\Pr(\dataobs|\vtheta)\equiv\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
-\]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents the Iverson bracket notation.
-Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
-\[
-   \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)=\dirichlet{\valpha + \Delta \valpha} 
-\]
-where $+$ denotes the componentwise sum of vectors.
+The data $\dataobs$ is a sequence of $n\in\mathbb{N}$ values
+coming from a universe $\datauni$, such that $|\datauni|=k$.
+The likelihood function is
+$
+\Pr(\dataobs|\vtheta)=\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
+$
+with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\mathbf{1}_{\iverson{x_j=a_i}}$.
+Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots
+\Delta\alpha_k)$ the posterior distribution over $\vtheta$ is
+$\dirichlet{\valpha + \Delta \valpha}$, where $+$ denotes the componentwise sum of vectors.
+In the following we will use the notation $\bysdir(n,\vtheta, \valpha,
+\dataobs)$ to denote the posterior of this process.
+%i.e., $\bysdir(n,\vtheta, \valpha, \dataobs)=\dirichlet{\valpha + \Delta \valpha}$.
+%
+% ($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
+% the parameter --informally called \emph{bias}-- of a Bernoulli
+% distributed random variable and $n$ is the number of draws. The
+% prior distribution over $\theta\in [0,1]$ is going to be a beta
+% distribution, $\betad(\alpha, \beta)$, with parameters
+% $\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+% \[
+%   \Pr(\theta)= \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
+% \]
+% where $\betaf(\cdot,\cdot)$ is the beta function.
+% The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
+% \[
+%   \Pr(\dataobs | \theta)= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
+% \]
+% where $\Delta \alpha = \sum_{i=1}^{n}x_i$.
+% The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
+% From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
+% posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
+% in section \ref{} when the private mechanisms will be described.
+
+% We will consider the situation where the underlying data is drawn from a binomial distribution
+% ($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
+% the parameter --informally called \emph{bias}-- of a Bernoulli
+% distributed random variable and $n$ is the number of draws. The
+% prior distribution over $\theta\in [0,1]$ is going to be a beta
+% distribution, $\betad(\alpha, \beta)$, with parameters
+% $\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
+% \[
+%   \Pr(\theta)= \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
+% \]
+% where $\betaf(\cdot,\cdot)$ is the beta function.
+% The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
+% \[
+%   \Pr(\dataobs | \theta)= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
+% \]
+% where $\Delta \alpha = \sum_{i=1}^{n}x_i$.
+% The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
+% From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
+% posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
+% in section \ref{} when the private mechanisms will be described.
+% \noindent \textbf{Dirichlet-multinomial Systems.}
+%
+The Beta-Binomial model can be obtained from the Dirichlet-Multinomial
+model by fixing $k=2$.
 
 \noindent \textbf{Differential Privacy.}
-\emph{Differential privacy} is a strong quantitative notion of statistical privacy proposed by \cite{dwork2006}.
-Differential privacy of a mechanism implies that changing the input of a mechanism slightly only reflects
+\emph{Differential privacy}~\cite{dwork2006} is a quantitative notion
+of data privacy guaranteeing  a bound on the that changing the input of a mechanism slightly only reflects
 in a controlled and bounded way on the output distribution. 
@@
 
-\noindent \textbf{Problem setting.}
+\section{Problem Statement}
 \label{subsec_problem}
-We are interested in exploring mechanisms for privately releasing the full posterior
-distributions derived in Section \ref{sec_background}.
-It's worth noticing that the posterior distributions are fully characterized
-by their parameters, and the family (Beta and Dirichlet distribution) they belong to. Hence, in case of the
+We are interested in exploring the design space of mechanisms for privately releasing the posterior
+distribution for the Dirichlet-Multinomial model as described in the
+previous section.
+It is worth noticing that the posterior distribution of this model is fully characterized
+by its parameters. That is, we are interested in releasing a private version of
+the Dirichlet distribution with parameter
+$\valpha'=(\valpha + \Delta \valpha)$, or in the case of the
 Beta-Binomial model we are interested in releasing a private version of the Beta distribution with 
-parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-Multinomial model we are interested in a private version of the Dirichlet distribution with parameter
-$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
+parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n -
+\Delta \alpha)$.
+\citet{zhang2016differential} and \citet{xiao2012bayesian}
 have already attacked this problem by adding independent Laplacian noise to the
@@
 \[
-   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
+   \Delta \bysinfer =\max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
 \]
@@
 \[
-  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta),\dataobs)\mid \dataobs \in \{0,1\}^n\}.
+  \candidateset=\{\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta),\dataobs)\mid \dataobs \in \{0,1\}^n\}.
 \]
@@
 \begin{equation*}
-GS \equiv 
+GS = 
 \max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
@@
 \begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)\equiv\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
 \end{equation}

### 2019-01-22 ICML2019/main.tex
pass section 4

--- 2019-01-21 ICML2019/main.tex
@@
 
+\noindent \emph{A note on input data representation.}
+We will represent our input databases $\dataobs$ of length $n$ as histograms 
+with $k$-$1$ bins where $k$ is the dimensionality of the problem.
+This is w.l.o.g. because given the first $k$-$1$ counts, the $k$-th count
+is known.
+
 \noindent \textbf{Problem setting.}
@@
 In this section we will describe and analyse a series of mechanisms.
-Section \ref{sec_ell1_dim} presents a first mechanism called $\lapmech$ based on the Laplace primitive
-where the sensitivity is measured w.r.t. to $\ell_1$ norm.
-We will then notice, Section \ref{??}, that this mechanism's accuracy can be improved by performing a better analysis on
-the sensitivity of the inference process.
-Section \ref{???}, shows an instance of the exponential mechanism where the scoring
+Section \ref{sec_ell1_dim} presents a first mechanism, $\lapmech$,
+based on the Laplace primitive where the sensitivity is measured w.r.t. to $\ell_1$ norm.
+Section \ref{sec_ell1_hist}, shows that $\lapmech$'s accuracy can be improved
+by performing a better analysis on the sensitivity of the inference process.
+Section \ref{sec_ehd}, shows an instance of the exponential mechanism, $\expmech$, where the scoring
 function is based on the Hellinger distance, we will see how this mechanisms performs
 poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
-Section \ref{???}
+Section \ref{sec_ehdl} introduces, $\lexpmech$, a variation of $\expmech$ which uses a lower bound
+on the global sensitivity called local sensitivity.
+Unfortunately, despite improving on accuracy $\lexpmech$ is non-private.
+Finally, building on $\lexpmech$, Section \ref{sec_ehds} introduces $\hexpmech$:
+which, based on the notion of \emph{smooth} sensitivity, achieves $\epsilon$-differential privacy and
+has good accuracy in specific cases.
+In presenting these mechanisms we will denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  $\dirichlet{\valpha'}$
+obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
+Two different upper bounds to the value
+\begin{align}
+  \label{eqn:eq1}
+  \max_{\substack{\adj{\dataobs}{\dataobs'},\\
+      \dirichlet{\valpha}=\inferd{\valpha}{\vtheta}{\dataobs},\\
+      \dirichlet{\valpha'}=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
+\end{align}
+will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
+
 \subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
 \label{sec_ell1_dim}
-We start off by presenting a mechanism based on the Laplace primitive.
-The mechanism, denoted by $\lapmech$, takes in input the data $\dataobs$, a mechanism, $\bysinfer$, that is used to perform inference on some parameter,
-a prior and a likelihood function, and the $\epsilon$ parameter measuring the privacy level.
-Now, $\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$,
-simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
-post-processing phase by flooring and  truncating the noisy parameters so that they belong to the right interval.
-In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
-with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
-$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
-Since we are adding noise directly to the parameters, the sensitivity should be calibrated w.r.t $\ell_1$-norm. That is,
-the sensitivity is defined as:
-\[
-   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
-\]
-This value can be quickly seen as being upper bounded by  the dimensionality. (e.g. 2 for the Beta-Binomial model and  $k$ for
-the Dirichlet-Multinomial model).
+We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
+The idea of $\lapmech$ is to add Laplacian noise to the differences of the respective numeric parameters of the prior
+and posterior distribution. 
 \begin{algorithm}
-  \caption{$\lapmech$ for the Beta-Binomial model}
-  \label{mech:lapmech}
+  \caption{$\lapmech$}
+  \label{lapmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
-  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
-  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
-  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
+  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
+  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}| - 1$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{|\mathcal{X}|}{\epsilon}}$
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
   % \RETURN $a_{k+1}$.
-  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
+  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\tilde{\valpha}$
   \end{algorithmic}
 \end{algorithm}
-
-  In Dirichlet-Multinomial model, $\lapmech$ produces output:
-  $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0},$
-  where $\eta_i \thicksim \lap{0}{\frac{k - 1}{\epsilon}}$.
-  We will use $ \lapmech(\dataobs) = \betad(\tilde{\alpha}, \tilde{\beta})$ or $\dirichlet{\tilde{\valpha}}$ for short.
+\begin{lem}
+  Algorithm \ref{lapmech} is $\epsilon$-d.p.
+  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to \ref{eqn:eq1}. \end{proof}
+\end{lem}
 
 \subsection{Improving the sensitivity ($\ilapmech$)}
- The accuracy of $\lapmech$ can be reduced to a constant.
- Indeed, two adjacent data sets $\dataobs, \dataobs'$  induce posterior distributions -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ --
- whose parameters differ by at most 2 w.r.t $\ell_1$ norm. This because we can see the parameters of the distributions as an histogram.
- Hence, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.
- {\color{red} Notice that we are using the bounded notion of differential privacy \cite{????}.}
- \todo{why 1 in 2 dimensions?}
- We denote the mechanism which calibrates the noise to this smaller sensitivity as $\ilapmech$.
- $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces:
- $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0) $
- where $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in the Beta-binomial model and
- $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
- with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}. We will also from now on
- write $\ilapmech(\dataobs)$ when the other parameters are obvious from the context.
+\label{sec_ell1_hist}
+By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to \ref{eqn:eq1}.
+Indeed  $\lapmech$ can be reduced to a constant. Algorithm $\ilapmech$ in Algorithm \ref{mech:ilapmech} takes advantage of this fact. 
+Indeed, when $\mathcal{X}=2$, \ref{eqn:eq1} is upper bounded by 1, while when $\mathcal{X}=2$ \ref{eqn:eq1} is upper bounded by 2.
+In Algorithm \ref{mech:ilapmech} the algorithm $\ilapmech$ is presented.
 \begin{algorithm}
@@
 \subsection{A new family of mechanisms}
+\label{sec_exp}
 In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
-of the exponential mechanism \cite{??} where the scoring function is based on a metric over
-probability distributoins.
+of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
+probability distributions.
 The idea is that $\expmech$ will sample and output a distribution with higher probability when
@@
 \subsubsection{A first approach: the $\expmech$ mechanism}
+\label{sec_ehd}
 $\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
@@
 \subsubsection{A second approach based on local sensitivity: $\lexpmech$}
-\label{subsec_emls}
-
+\label{sec_ehdl}
 Figure \ref{fig_theory} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
@@
 \subsubsection{A third approach based on smooth sensitivity: $\hexpmech$}
-\label{subsec_hexpmech}
+\label{sec_ehds}
 In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and $\epsilon$-differential privacy simultaneously,

### 2019-01-22 ICML2019/main.tex

--- 2019-01-22 ICML2019/main.tex
@@
 
+\noindent \emph{A note on input data representation.}
+We will represent our input databases $\dataobs$ of length $n$ as histograms 
+with $k$-$1$ bins where $k$ is the dimensionality of the problem.
+This is w.l.o.g. because given the first $k$-$1$ counts, the $k$-th count
+is known.
+
 \section{Problem Statement}
@@
 \label{sec_mechs}
+In this section we will describe and analyse a series of mechanisms.
+Section \ref{sec_ell1_dim} presents a first mechanism, $\lapmech$,
+based on the Laplace primitive where the sensitivity is measured w.r.t. to $\ell_1$ norm.
+Section \ref{sec_ell1_hist}, shows that $\lapmech$'s accuracy can be improved
+by performing a better analysis on the sensitivity of the inference process.
+Section \ref{sec_ehd}, shows an instance of the exponential mechanism, $\expmech$, where the scoring
+function is based on the Hellinger distance, we will see how this mechanisms performs
+poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
+Section \ref{sec_ehdl} introduces, $\lexpmech$, a variation of $\expmech$ which uses a lower bound
+on the global sensitivity called local sensitivity.
+Unfortunately, despite improving on accuracy $\lexpmech$ is non-private.
+Finally, building on $\lexpmech$, Section \ref{sec_ehds} introduces $\hexpmech$:
+which, based on the notion of \emph{smooth} sensitivity, achieves $\epsilon$-differential privacy and
+has good accuracy in specific cases.
+In presenting these mechanisms we will denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  $\dirichlet{\valpha'}$
+obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
+Two different upper bounds to the value
+\begin{align}
+  \label{eqn:eq1}
+  \max_{\substack{\adj{\dataobs}{\dataobs'},\\
+      \dirichlet{\valpha}=\inferd{\valpha}{\vtheta}{\dataobs},\\
+      \dirichlet{\valpha'}=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
+\end{align}
+will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
+
 \subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
-We start off by presenting a mechanism based on the Laplace primitive.
-The mechanism, denoted by $\lapmech$, takes in input the data $\dataobs$, a mechanism, $\bysinfer$, that is used to perform inference on some parameter,
-a prior and a likelihood function, and the $\epsilon$ parameter measuring the privacy level.
-Now, $\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$,
-simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
-post-processing phase by flooring and  truncating the noisy parameters so that they belong to the right interval.
-In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
-with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
-$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
-Since we are adding noise directly to the parameters, the sensitivity should be calibrated w.r.t $\ell_1$-norm. That is,
-the sensitivity is defined as:
-\[
-   \Delta \bysinfer =\max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
-\]
-This value can be quickly seen as being upper bounded by  the dimensionality. (e.g. 2 for the Beta-Binomial model and  $k$ for
-the Dirichlet-Multinomial model).
+\label{sec_ell1_dim}
+We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
+The idea of $\lapmech$ is to add Laplacian noise to the differences of the respective numeric parameters of the prior
+and posterior distribution. 
 \begin{algorithm}
-  \caption{$\lapmech$ for the Beta-Binomial model}
-  \label{mech:lapmech}
+  \caption{$\lapmech$}
+  \label{lapmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
-  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
-  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
-  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
+  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
+  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}| - 1$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{|\mathcal{X}|}{\epsilon}}$
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
   % \RETURN $a_{k+1}$.
-  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
+  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\tilde{\valpha}$
   \end{algorithmic}
 \end{algorithm}
-
-  In Dirichlet-Multinomial model, $\lapmech$ produces output:
-  $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0},$
-  where $\eta_i \thicksim \lap{0}{\frac{k - 1}{\epsilon}}$.
-  We will use $ \lapmech(\dataobs) = \betad(\tilde{\alpha}, \tilde{\beta})$ or $\dirichlet{\tilde{\valpha}}$ for short.
+\begin{lem}
+  Algorithm \ref{lapmech} is $\epsilon$-d.p.
+  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to \ref{eqn:eq1}. \end{proof}
+\end{lem}
 
 \subsection{Improving the sensitivity ($\ilapmech$)}
- The accuracy of $\lapmech$ can be reduced to a constant.
- Indeed, two adjacent data sets $\dataobs, \dataobs'$  induce posterior distributions -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ --
- whose parameters differ by at most 2 w.r.t $\ell_1$ norm. This because we can see the parameters of the distributions as an histogram.
- Hence, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.
- {\color{red} Notice that we are using the bounded notion of differential privacy \cite{????}.}
- \todo{why 1 in 2 dimensions?}
- We denote the mechanism which calibrates the noise to this smaller sensitivity as $\ilapmech$.
- $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces:
- $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0) $
- where $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in the Beta-binomial model and
- $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
- with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}. We will also from now on
- write $\ilapmech(\dataobs)$ when the other parameters are obvious from the context.
+\label{sec_ell1_hist}
+By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to \ref{eqn:eq1}.
+Indeed  $\lapmech$ can be reduced to a constant. Algorithm $\ilapmech$ in Algorithm \ref{mech:ilapmech} takes advantage of this fact. 
+Indeed, when $\mathcal{X}=2$, \ref{eqn:eq1} is upper bounded by 1, while when $\mathcal{X}=2$ \ref{eqn:eq1} is upper bounded by 2.
+In Algorithm \ref{mech:ilapmech} the algorithm $\ilapmech$ is presented.
 \begin{algorithm}

### 2019-01-22 ICML2019/main.tex
work on 5

@@
 obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
-Two different upper bounds to the value
+Two different upper bounds to the value of
 \begin{align}
@@
 We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
-The idea of $\lapmech$ is to add Laplacian noise to the differences of the respective numeric parameters of the prior
+The idea of $\lapmech$ is to add Laplacian noise with scale proportional to $\mathcal{X}$ to
+the differences between the respective numeric parameters of the prior
 and posterior distribution. 
@@
   Algorithm \ref{lapmech} is $\epsilon$-d.p.
-  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to \ref{eqn:eq1}. \end{proof}
+  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to the value denoted by (\ref{eqn:eq1}). \end{proof}
 \end{lem}
@@
 \label{sec_ell1_hist}
-By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to \ref{eqn:eq1}.
-Indeed  $\lapmech$ can be reduced to a constant. Algorithm $\ilapmech$ in Algorithm \ref{mech:ilapmech} takes advantage of this fact. 
-Indeed, when $\mathcal{X}=2$, \ref{eqn:eq1} is upper bounded by 1, while when $\mathcal{X}=2$ \ref{eqn:eq1} is upper bounded by 2.
-In Algorithm \ref{mech:ilapmech} the algorithm $\ilapmech$ is presented.
+By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to the value denoted by (\ref{eqn:eq1}).
+Indeed a constant will do. Algorithm $\ilapmech$ in Algorithm \ref{ilapmech} takes advantage of this fact. 
+Indeed, when $\mathcal{X}=2$, 1 is an upper bound for the value of (\ref{eqn:eq1}), while when $\mathcal{X}>2$, 2 is.
+In Algorithm \ref{ilapmech} the algorithm $\ilapmech$ is presented.
 \begin{algorithm}
-  \caption{$\ilapmech$ in Dirichlet-Multinomial model}
-  \label{mech:ilapmech}
+  \caption{$\ilapmech$}
+  \label{ilapmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
-  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
-  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
-  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
+  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad ${\bf let}\ k=\left \{
+        \begin{array}{lll}          
+          1&\text{if}& |\mathcal{X}|=2\\
+          2&\text{otherwise}
+        \end{array}
+      \right .\ $
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
+  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}|-1$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{k}{\epsilon}}$
   \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
   % \RETURN $a_{k+1}$.
-  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
-  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
+  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\tilde{\valpha}$
   \end{algorithmic}
 \end{algorithm}
+\begin{lem}
+  Algorithm \ref{ilapmech} is $\epsilon$-d.p.
+  \begin{proof} By noticing that 1 and 2 are upper bounds to the value denoted by (\ref{eqn:eq1}), respectively when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
+  \end{proof}
+\end{lem}
 

### 2019-01-22 codes/realdata_betabinomial_bayesinfer.py
update experiments

@@ -14,20 +14,20 @@ from decimal import *
 from scipy.special import gammaln
 from dirichlet import dirichlet
 from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
-
+import glob
 #################################################################################
 ###READ DATA FROM FILE###########################################################
 #################################################################################
 def read_data(filename, col):
 	data = []
-	with i = open(filename):
+	with open(filename) as i:
 		for line in i:
-			t = i.split(" ")
-			data.append(t[col])
+			data.append(int(line[col]))
 	return data
 
 def read_datas(folder):
 	datas = []
+	print glob.glob(folder)
 	for f in glob.glob(folder):
 		datas.append(read_data(f, 0))
 	return datas
@@ -52,19 +52,20 @@ def run_experiments(times, datasizes, observations,epsilon, delta, prior):
 		Bayesian_Model._experiments(times)
 		print("finished" + str(observation))
 
-		for i in range(len(mean_error)):
-			errors[i].append(Bayesian_Model._accuracy[Bayesian_Model._keys[i]])
+		for i in range(5):
+			data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[i]])
 
-	plot_error_box(errors, "Data Set", 
+	plot_error_box(data, "Different Data Sets", 
 		["bike", "cryotherapy", "immunotherapy", "badges"], 
 		"Experiments on Real Data", 
 		[
+		r'Alg 1 - $\mathsf{LSDim}$ (sensitivity = 2.0)', 
+		r'Alg 2 - $\mathsf{LSHist}$ (sensitivity = 1.0)',
 		r'Alg 5 - $\mathsf{EHDS}$ ',
-		r"Alg 4 - $\mathsf{EHDL}$",
 		r"Alg 3 - $\mathsf{EHD}$",
-		r'Alg 1 - $\mathsf{LSDim}$ (sensitivity = '+ str(sensitivity2) +')', 
-		r'Alg 2 - $\mathsf{LSHist}$ (sensitivity = '+ str(sensitivity1) +')'],
-		["skyblue", "navy", "lightblue", "lightcyan", "blueviolet"] )
+		r"Alg 4 - $\mathsf{EHDL}$"
+		],
+		["skyblue", "navy", "coral", "crimson", "blueviolet"] )
 
 	return 
 
[…]

### 2019-01-22 ICML2019/main.tex
update experiments

@@
 In this section, we evaluate the accuracy of the mechanisms defined in
-Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
-data variance, prior distribution, and some combinations thereof.
+Section (\ref{sec_mechs}) w.r.t. data sizes and dimensions by experimenting on real data sets.
 Every plot is an average over 1000 runs. In all the experiments we set
@@
 
-\paragraph{Fixed dataset varying balanced priors}
-\label{subsubsec_vs_prior}
-In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ .
-We studied the accuracy under different priors, where the priors considered  are also balanced.
-Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
+\paragraph{Experiments on Real Data Sets}
+We use four data sets from UCI Machine Learning repository. Each data set contains 1 binary variable. By setting the prior distribution as $\betad(1,1)$, we 
 \begin{figure}
 \centering
-\includegraphics[width=0.35\textwidth]{sampling_prior.eps}
-\caption{Observed data set is: $(50,50)$, varying balanced priors}
+\includegraphics[width=0.35\textwidth]{realdata.eps}
+\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
 \label{fig_vs_prior}
@@
 The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
+\ref{sec_ehds} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
 We calculate the concrete privacy value in following ways wrt.

### 2019-01-22 ICML2019/main.tex
update the experiments section

@@
 \paragraph{Experiments on Real Data Sets}
-We use four data sets from UCI Machine Learning repository. Each data set contains 1 binary variable. By setting the prior distribution as $\betad(1,1)$, we 
+We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
+Each data set contains 1 binary variable, which applys our Beta-binomial model.
+By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
+The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
+The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
+The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
 \begin{figure}

### 2019-01-22 ICML2019/main.tex
update experimnts

@@
 
-\paragraph{Experiments on Real Data Sets}
+\paragraph{Experiments on Real Data Sets in Beta-binomial Model}
 We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
@@
 The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
+The size of the four data set are $731, 90, 294, 90$.
+The accuracy are shown in Figure \ref{fig_real_2d}.
 \begin{figure}
@@
 \caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
-\label{fig_vs_prior}
+\label{fig_real_2d}
+\end{figure}
+
+\paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
+We use three real data sets from the same repository repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
+Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model.
+By setting the prior distribution as $\dirichlet(1,1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
+The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
+The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
+The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
+The size of the four data set are $731, 90, 90$.
+The accuracy are shown in Figure \ref{fig_real_3d}.
+\begin{figure}
+\centering
+\includegraphics[width=0.35\textwidth]{realdata_3d.eps}
+\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
+\label{fig_real_3d}
 \end{figure}

### 2019-01-22 codes/realdata_betabinomial_bayesinfer.py

@@ -32,11 +32,11 @@ def read_datas(folder):
 		datas.append(read_data(f, 0))
 	return datas
 
-def data_process(datas):
+def data_process(datas, dimension):
 	observations = []
 	datasizes = []
 	for data in datas:
-		observations.append([sum(data), len(data) - sum(data)])
+		observations.append([data.count(i) for i in range(dimension) ])
 		datasizes.append(len(data))
 	return datasizes,observations
 
@@ -56,7 +56,7 @@ def run_experiments(times, datasizes, observations,epsilon, delta, prior):
 			data.append(Bayesian_Model._accuracy[Bayesian_Model._keys[i]])
 
 	plot_error_box(data, "Different Data Sets", 
-		["bike", "cryotherapy", "immunotherapy", "badges"], 
+		["bike", "cryotherapy", "immunotherapy"], 
 		"Experiments on Real Data", 
 		[
 		r'Alg 1 - $\mathsf{LSDim}$ (sensitivity = 2.0)', 
@@ -145,9 +145,10 @@ if __name__ == "__main__":
 
 	epsilon = 1.0
 	delta = 0.00000001
-	prior = dirichlet([1,1])
+	prior = dirichlet([1,1,1])
 
-	datasizes, observations = data_process(read_datas("./datas/*.txt"))
+	datasizes, observations = data_process(read_datas("./datas/3d/*.txt"), 3)
+	print datasizes
 	run_experiments(1000, datasizes, observations,epsilon, delta, prior)
 
 

### 2019-01-22 ICML2019/main.tex
update the experiments description

@@
 difference of medians; The whiskers extend from the box to show the
-range of the data. A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
-w.r.t Hellinger distance-- while the green box next to
-it represents the performance of a variation of the basic Laplace
-mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
-settings: that is $\epsilon$, data, prior. The variation
-considered performs a postprocessing on the released parameters so
-that they are consistent. For instance when the sum of the noised
-parameters is greater than $n$ we will truncate them so that they sum
-up to $n$.
-
-\paragraph{Increasing data size with balanced datasets}
-\label{subsubsec_vs_datasize}
-
-\begin{figure}[ht]
-\begin{center}
-\centering
-\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
-{ \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
-\label{fig_vs_datasize_2d}
-}
-
-\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
-{
-  \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
-  \label{fig_vs_datasize_3d}
-}
-\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
-{
-  \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
-  \label{fig_vs_datasize_4d}
-}
-\end{center}
-\end{figure}
-
-In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
-of observations. The results show that when the data size increases, the average errors of
-$\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
-i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
-But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
-we considered data sets of the order of 15 thousands elements,
-the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
-Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
+range of the data. 
+% A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
+% w.r.t Hellinger distance-- while the green box next to
+% it represents the performance of a variation of the basic Laplace
+% mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
+% settings: that is $\epsilon$, data, prior. The variation
+% considered performs a postprocessing on the released parameters so
+% that they are consistent. For instance when the sum of the noised
+% parameters is greater than $n$ we will truncate them so that they sum
+% up to $n$.
+
+% \paragraph{Increasing data size with balanced datasets}
+% \label{subsubsec_vs_datasize}
+
+% \begin{figure}[ht]
+% \begin{center}
+% \centering
+% \subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
+% { \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
+% \label{fig_vs_datasize_2d}
+% }
+
+% \subfigure[Increasing data size with $\dirichlet{1,1,1}$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
+% {
+%   \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
+%   \label{fig_vs_datasize_3d}
+% }
+% \subfigure[Increasing data size with $\dirichlet{1,1,1,1}$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
+% {
+%   \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
+%   \label{fig_vs_datasize_4d}
+% }
+% \end{center}
+% \end{figure}
+
+% In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
+% of observations. The results show that when the data size increases, the average errors of
+% $\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
+% i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
+% But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
+% we considered data sets of the order of 15 thousands elements,
+% the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
+% Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
 
@@
 Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model.
-By setting the prior distribution as $\dirichlet(1,1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
+By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
 The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.

### 2019-01-22 ICML2019/main.tex
update experiments

@@
 \paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
-We use three real data sets from the same repository repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
+We use three real data sets from the same repository repository.
 Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model.

### 2019-01-22 ICML2019/main.tex
pass on section 5

@@
 obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
+To minimize notation we will identify the distribution $\dirichlet{\valpha}$ with its vector
+of parameters.
 Two different upper bounds to the value of
@@
   \max_{\substack{\adj{\dataobs}{\dataobs'},\\
-      \dirichlet{\valpha}=\inferd{\valpha}{\vtheta}{\dataobs},\\
-      \dirichlet{\valpha'}=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
+      \valpha=\inferd{\valpha}{\vtheta}{\dataobs},\\
+      \valpha'=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
 \end{align}
 will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
+Finally, with $\bysinfer{\dataobs}$, and $\bys{\dataobs}{\vtheta}$ we will denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when $\valpha, \vtheta$ or just $\valpha$
+are known from the context.
 
@@
   \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
   \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
@@
   \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
   \STATE \quad ${\bf let}\ k=\left \{
@@
 distributions as opposed to a metric over the parameters that represent it. In this work we will
-use the Hellinger distance, but this approach could be extended to other $f$-divergences. We will
-start by describing how the mechanism works in the case of the Beta-Binomial model noticing that
-the extension to the Dirichelet-Multinomial model is straightforward.
-Given a prior distribution $\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
+use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
+Given a prior distribution $\dirichlet{\valpha}$,
 we define the follwing set  where the mechanism will sample from:
 \[
-  \candidateset=\{\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta),\dataobs)\mid \dataobs \in \{0,1\}^n\}.
+  \candidateset=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
 \]
-Where $\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)$ denotes the posterior beta distribution inferred starting from the parameters in input.
-Notice that the above set reduces to:
+In general $|\candidateset|=\binom{n + 1}{|\mathcal{X}| - 1}$, and in the specific case of $|\mathcal{X}|=2$, that is the Beta-Binomial model,
+the above reduces to:
 \[
-  \{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
+  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
 \]
-We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process on the observed data $\dataobs$
-when the other two parameters, that is prior and likelihood, are fixed.
-
-\subsubsection{A first approach: the $\expmech$ mechanism}
-\label{sec_ehd}
-$\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
+where $\valpha=(\alpha,\beta)$.
+
+\noindent \textbf{A first approach: the $\expmech$ mechanism.} $\expmech$'s pseudocode is shown in Algorithm \ref{mech:expmech1}.
+Given the input $\dataobs\in\{0,1\}^n$ and a prior $\betad(\alpha, \beta)$, the mechanism $\expmech$ outputs an element $r\in\candidateset$ with  probability: 
 \[
-%\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
 \frac
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
 {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot GS})},
 \]
-where $u(x,r)$ is the Hellinger scoring function: $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
-\begin{equation*}
+where $u(\dataobs,r)$ is the Hellinger based score function:
+$-\hellinger(\bysinfer{\dataobs}, r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
+\[
 GS = 
-\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
-|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
-\end{equation*}
+\max_{\dataobs,\dataobs': \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
+|\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs'}, r)|
+\]
 % 
   \begin{algorithm}
-  \caption{$\expmech$ in Beta-binomial model}
-  \label{mech:expmech}
+  \caption{$\expmech$}
+  \label{mech:expmech1}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $GS$ be the global sensitivity of scoring function.  
-  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
+  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad calculate the outputting probability of $r$.
-  \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
+  \STATE \quad \quad $pr[r] = 
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
 / {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot GS})}$
-\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
 \STATE {\bf return} $z$
@@
   \end{algorithm}
-
-Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{lem_exp_private} proves privacy $\epsilon$ differential privacy of $\expmech$.
-
-\subsubsection{A second approach based on local sensitivity: $\lexpmech$}
-\label{sec_ehdl}
-Figure \ref{fig_theory} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
-$GS$ is relatively big and hence the variance of the distribution $\expmech$ ends up also being too big. In order to solve this issue we
-will proceed in two steps. We will first define $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
+\begin{lem}
+  Algorithm \ref{mech:expmech1} is $\epsilon$-d.p.
+\end{lem}
+
+\noindent \textbf{A second approach based on local sensitivity: $\lexpmech$.} Figure \ref{fig_theory} shows that  the accuracy of
+$\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
+$GS$ is relatively large and hence the variance of the distribution $\expmech$ ends up also being too large. In order to solve this issue we
+will proceed in two steps. We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
 the noise. This is known to be a non private approach, but it will guide us towards new insights.
@@
   \begin{algorithm}
-  \caption{$\lexpmech$ in Beta-binomial model}
-  \label{mech:expmech}
+  \caption{$\lexpmech$}
+  \label{mech:lexpmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $LS$ be the local sensitivity of scoring function.  
-  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
+  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad calculate the outputting probability of $r$.
-  \STATE \quad \quad $Pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2 LS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot LS})}$
-\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+  \STATE \quad \quad $pr[r] = 
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot LS(\dataobs)})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot LS(\dataobs)})}$
+\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
 \STATE {\bf return} $z$
@@
 
-$\lexpmech$ shares candidate set and utility function with $\expmech$,
-and outputs a result $r \in \mathcal{R}$ with probability:
+Given $\dataobs, \lexpmech$ samples an element $r \in \mathcal{R}$ with probability:
 \[
-%\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
 \frac
@@
 \begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
+LS(\dataobs)=\max_{\dataobs'\in\mathcal{X}^n,\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer{\dataobs'}, r) - \hellinger(\bysinfer{\dataobs'}, r)\rvert 
 \end{equation}
-The above can be proven to simplify to:
+Lemma \ref{lem_loc_opt}  provides a useful characterization of the above function, the interested reader can check the proof in the Appendix.
 \begin{lem}
 \label{lem_loc_opt}
-\[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
-\]
+For $\dataobs\in\mathcal{X}^n$, 
+\[LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs'})\]
 \end{lem}
-The interested reader can check the proof in the Appendix.
 
@@
 \label{sec_ehds}
-In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and $\epsilon$-differential privacy simultaneously,
+In this section, we explore a new mechanism, which compromises between $\expmech$ and $\lexpmech$ and  achieves good accuracy and $\epsilon$-differential privacy simultaneously,
 by scaling the noise to a smooth upper bound on the local sensitivity.
-We first define the smooth sensitivity on a input $\dataobs$. The following definition is specific to binary data, that is it will
-be useful to privately release a posterior Beta distribution. The extension to categorical data is straightforward.
+We first define the smooth sensitivity on a input $\dataobs\in\{0,1\}^n$.
+% The following definition is specific to binary data, hence it will
+% be useful to privately release only posterior Beta distributions in the Beta-Binomial model. The extension to categorical data is straightforward.
 \begin{definition}
 \label{def_gamma_smooth}
-Given a data set $\dataobs$ of size $n$, we define the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer(\dataobs),\cdot)$ as:
+For $\dataobs\in\mathcal{X}^n$, and $\gamma \in \mathbb{R}^{> 0}$, the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer{\dataobs},\cdot)$ is defined as:
 \begin{equation}
   \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
+   S(\dataobs)=\max_{\dataobs' \in \mathcal{X}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
@@
 \end{thm}
-The interested reader will find the proof in Appendix.
-We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+again, the interested reader will find the proof in Appendix.
+We are now ready to describe the mechanism $\hexpmech$ in Algorithm \ref{mech:sexpmech}. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \[
@@
 \]
-where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
+where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer{\dataobs},\cdot)$. {\color{red}{why do we choose 1???}}
   \begin{algorithm}
-  \caption{$\hexpmech$ in Beta-binomial model}
-  \label{mech:expmech}
+  \caption{$\hexpmech$}
+  \label{mech:sexpmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
-  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
-  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $S(\dataobs)$ be the vector of $\gamma-$sensitivity of scoring function. 
-  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$,  prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bys{\valpha}{\dataobs}$.
+  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad calculate the outputting probability of $r$.
-  \STATE \quad \quad $Pr[r] = 
+  \STATE \quad \quad $pr[r] = 
   {\exp(\frac{\epsilon \cdot \ux{r}}{4 S(\dataobs)})}
 / {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot \ux{r'}}{4 \cdot S(\dataobs)})}$
-\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
+\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
 \STATE {\bf return} $z$
@@
 
-As already mentioned $\expmech, \lexpmech, \hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
-Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
-\[
-  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
-\]
-and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
-distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
-over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
-that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here? and was $\datauni$} defined?}
-
-\section{Privacy Analysis}
-
-\subsection{Privacy of Laplace Mechanism Family}
-The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
-Mechanisms $\lapmech$ and $\ilapmech$ are trivially $\epsilon$-differentially private since the mechanisms
-add Laplacian noise proportional to the $\ell_1$-norm sensitivity to the arguments of the posterior distributions.
-\begin{lem}
-  $\lapmech$, $\ilapmech$ are $\epsilon$-differentially private.
-\end{lem}
-
-\subsection{Privacy of Exponential Mechanism Family}
-\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
-\begin{lem}
-\label{lem_exp_private}
-$\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
-\end{lem}
-
-% \subsubsection{$\lexpmech$ non-Differential Privacy}
-% Exponential mechanism with local sensitivity non-differential privacy.
-
-\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}
-
-\begin{lem}
-\label{lem_hexpmech_privacy}
-$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
-\end{lem}
-(Proof is in Appendix)
-
+\begin{thm}
+  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
+\end{thm}
+% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
+% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
+% \[
+%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+% \]
+% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
+% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
+% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
 \section{Accuracy Analysis}
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
 \end{cases}
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
 \end{cases}
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 }
@@
 Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
+Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta }}$, where $Y \thicksim \lap{0}{\frac{\Delta }{\epsilon}}$ in our setting.
 
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta }} - e^{\frac{\epsilon (t + 1)}{\Delta }}) & t < 0
 \end{cases}
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
 \end{cases}
@@
   &\Pr\left[
-\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
+\begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2}\\
 &= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
@@
 \right] \\
-  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
+  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
   \end{align*}
@@
 \right] \\
-   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
+   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
   \end{align*}

### 2019-01-23 ICML2019/main.tex
tweak
Pass on Section 6 and 7.

--- 2019-01-22 ICML2019/main.tex
@@
 \section{Privacy Analysis}
-
+The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
 \subsection{Privacy of Laplace Mechanism Family}
-The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
 Mechanisms $\lapmech$ and $\ilapmech$ are trivially $\epsilon$-differentially private since the mechanisms
@@
 \end{lem}
-
 \subsection{Privacy of Exponential Mechanism Family}
-\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
+%\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
+By applying the result of \cite{dwork2014algorithmic},
+we obtain $\epsilon-$differential privacy of the mechanism $\expmech$.
 \begin{lem}
 \label{lem_exp_private}
-$\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
+$\expmech$ is $\epsilon-$differentially private.
 \end{lem}
-
 % \subsubsection{$\lexpmech$ non-Differential Privacy}
 % Exponential mechanism with local sensitivity non-differential privacy.
-
-\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}
-
+%\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}
+In this paper, we prove the $\epsilon-$differential privacy of the 
+exponential mechanism $\hexpmech$ with $\gamma$-smooth sensitivity.
 \begin{lem}
 \label{lem_hexpmech_privacy}
-$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
+$\hexpmech$ is $\epsilon$-differential private when $\gamma = 1.0$.
 \end{lem}
+\todo{(Tetsuya) I think this should be theorem or proposition.}
 (Proof is in Appendix)
@@
 \section{Accuracy Analysis}
-
+We will observe accuracy of mechanisms.
+In this section, we fix $\alpha$ and $\beta$, and for simplicity, we define the term of difference from $\betad(\alpha, \beta)$, the true posterior distribution.
+\[
+c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+\]
+%where $\betad(\alpha, \beta)$ is the true posterior distribution
 \subsection{Accuracy Bound for Baseline Mechanisms}
@@
 \label{lem_acc_lap}
-Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
+%Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
+The accuracy bound of $\lapmech$ is given by
 \begin{align*}
@@
 \lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\hellinger(\bysinfer(\dataobs), z ) = c(t)
+%\end{aligned}
 }
@@
 \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
-\end{cases}
+\end{cases}.
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+%where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-\begin{align*}
-&\lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-}\\
-& \qquad = \begin{cases}
+%\begin{align*}
+%&\lapmechPr{\dataobs}{
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+%\end{aligned}
+%
+%}\\
+%& \qquad = \begin{cases}
+%0.19673467014 & t = 0\\
+%0.11932560927 & t = 1\\
+%0.07237464051 & t = 2
+%\end{cases}.
+%\end{align*}
+\[
+\Pr[\hellinger(\bysinfer(\dataobs), z ) = c(t)]
+=
+\begin{cases}
 0.19673467014 & t = 0\\
@@
 \end{cases}.
-\end{align*}
+\]
 
@@
 Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.
-
-Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
-
 \begin{align*}
@@
 \ilapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+%\begin{aligned}
+%\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+%&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+%\end{aligned}
+\hellinger(\bysinfer(\dataobs), z ) = c(t)
 }
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-\begin{align*}
-&\ilapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-}\\
-& \qquad = \begin{cases}
+Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
+\[
+\Pr[\hellinger(\bysinfer(\dataobs), z ) = c(t)]
+= \begin{cases}
 0.31606027941 & t = 0\\
@@
 \end{cases}.
-\end{align*}
-
+\]
 \subsection{Accuracy Bound for $\hexpmech$}
@@
   \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
-  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
-  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  &  = \frac{\exp{(\frac{- \epsilon c(t)}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}%\\
+%  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
 \end{table*}
-
 % In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
@@
 
-By solving following equations:
+By solving equations on accuracy such as:
+\begin{align*}
+\lefteqn{\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }}\\
+&\qquad =
+\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }
+=
+0.19673467 
+\end{align*}
 %  \[
   %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
- & = 0.19673467 \text{ or } 0.316060279
-\end{align*}
+%\begin{align*}
+% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
+% & = 0.19673467 \text{ or } 0.316060279
+%\end{align*}
 %  \]
@@
 %   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
-  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
-  &= 0.119325609 \text{ or } 0.116272079
-\end{align*}
+%\begin{align*}
+%  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
+%  &= 0.119325609 \text{ or } 0.116272079
+%\end{align*}
 %  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
@@
 %    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
- &=0.072374641 \text{ or }  0.042774107
+%\begin{align*}
+% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
+% &=0.072374641 \text{ or }  0.042774107
 %\]
-\end{align*}
+%\end{align*}
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

### 2019-01-23 ICML2019/main.tex

--- 2019-01-22 ICML2019/main.tex
@@
 	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
+    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. \gp{it's only eps-d.p for now}
 	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions
@@
 \noindent \emph{A note on input data representation.}
-We will represent our input databases $\dataobs$ of length $n$ as histograms 
+We will think of our input databases $\dataobs$ of length $n$ as histograms 
 with $k$-$1$ bins where $k$ is the dimensionality of the problem.
@@
 \]
-When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$, we can unfold the above and derive: 
+When $\textup{P}=\dirichlet{\valpha_1}$ and $\textup{Q}=\dirichlet{\valpha_2}$, we can unfold the above and derive: 
  \[
- \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
  \]

### 2019-01-23 ICML2019/main.tex
Merge

@@
 \section{Accuracy Analysis}
-
+We will observe accuracy of mechanisms.
+In this section, we fix $\alpha$ and $\beta$, and for simplicity, we define the term of difference from $\betad(\alpha, \beta)$, the true posterior distribution.
+\[
+c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+\]
 \subsection{Accuracy Bound for Baseline Mechanisms}
@@
 \lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+\hellinger(\bysinfer{\dataobs}, z ) = c(t)
 }
@@
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $z$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 %  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.19673467014$.\\
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 %  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
 %  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 %&\lapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
+%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0
 %} = 0.19673467014,\\
@@
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
 %& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
@@
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
 %& = 1 - 
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-\begin{align*}
-&\lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-}\\
-& \qquad = \begin{cases}
+\[
+\Pr[\hellinger(\bysinfer{\dataobs}, z ) = c(t)]
+= \begin{cases}
 0.19673467014 & t = 0\\
@@
 \end{cases}.
-\end{align*}
+\]
+%\begin{align*}
+%&\ilapmechPr{\dataobs}{
+%\hellinger(\bysinfer{\dataobs}, z ) = c(t)
+%}\\
+%& \qquad =  \begin{cases}
+%0.31606027941 & t = 0\\
+%0.11627207896 & t = 1\\
+%0.04277410743 & t = 2
+%\end{cases}.
+%\end{align*}
 
@@
 \ilapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
+\hellinger(\bysinfer{\dataobs}, z ) = c(t)
 }
@@
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.31606027941$.
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 %  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
 %  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 %&\ilapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
+%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0}= 0.31606027941,\\
 %&\ilapmechPr{\dataobs}{
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
 %& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-\begin{align*}
-&\ilapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-}\\
-& \qquad = \begin{cases}
+
+Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
+\[
+\Pr[
+\hellinger(\bysinfer{\dataobs}, z ) = c(t)
+]
+ =  \begin{cases}
 0.31606027941 & t = 0\\
@@
 %  \label{eq_acc}
-%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
+%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c  }\\ 
 %  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
@@
   \begin{align*}
-  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
-  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
-  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(t)  } }\\ 
+  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+%  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
 %  \hline
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z ) = c} $
 %  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
 %  \hline
-%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
 %  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
 %  \hline
-%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
+%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
 %  & $\frac{1}{\nomalizer{\dataobs}}$ 
@@
 
-By solving following equations:
+By solving equations on accuracy such as:
+\begin{align*}
+\lefteqn{\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }}\\
+&\qquad =
+\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }
+=
+0.19673467 
+\end{align*}
+%By solving following equations:
 %  \[
-  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
- & = 0.19673467 \text{ or } 0.316060279
-\end{align*}
+%  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
+%\begin{align*}
+% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(0)  } \\
+% & = 0.19673467 \text{ or } 0.316060279
+%\end{align*}
 %  \]
@@
 %   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
-  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
-  &= 0.119325609 \text{ or } 0.116272079
-\end{align*}
+%\begin{align*}
+%  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }\\
+%  &= 0.119325609 \text{ or } 0.116272079
+%\end{align*}
 %  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
@@
 %    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-\begin{align*}
- &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
- &=0.072374641 \text{ or }  0.042774107
+%\begin{align*}
+% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(2)  }\\
+% &=0.072374641 \text{ or }  0.042774107
 %\]
-\end{align*}
+%\end{align*}
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
@@
 % %\[
-% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
 % %\]
@@
 % \[
-% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
 % \]
@@
 % \begin{align*}
-% &\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+% &\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
 % & = 
 % \begin{cases}
-% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
 % \end{cases}\\
@@
 % \begin{cases}
-% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
 % \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
 % \end{cases}\\
-% &= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+% &= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
 % \end{align*}
-% The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+% The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
 % Hence, we conclude the statement of this lemma.
@@
 
-%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
+%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer{\dataobs}$.
 %\begin{equation*}
@@
 %LS(\dataobs) 
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
-%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs}) \\
+%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\} \\
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\}.
 %\end{split}
@@
 %\begin{aligned}
-%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
-%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+%&\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs})\\
+%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
 %\end{aligned}
@@
 %  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
+%\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs}).
 %\end{align*}
@@
 We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
-It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
+It is shown that maximum value taken when  $r = \bysinfer{\dataobs}$.
 
@@
 \[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
 \]
@@
 \begin{align*}
-&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+&\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
 & = 
 \begin{cases}
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
+\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
 \end{cases}\\
@@
 \begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
 \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
-\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
+\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
 \end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
 \end{align*}
-The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
+The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
 Hence, we conclude the statement of this lemma.
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+\lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
 
-Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 By applying Hellinger distance in our case, we get:
@@
 %\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
 %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
@@
 %\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
+%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
 %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
   & \Pr\left[
-  \begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
+  \begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2} \\
   & =

### 2019-01-23 ICML2019/main.tex
changes to intro

--- 2019-01-23 ICML2019/main.tex
@@
 We explore the design space of differentially private Bayesian
-inference mechanisms with accuracy measured in terms of Hellinger
-distance over posterior distributions.  
+inference mechanisms with accuracy measured in terms of the Hellinger
+distance between posterior distributions.  
 We focus on two discrete models for parametric Bayesian
 inference: the Beta-Binomial and the Dirichlet-Multinomial
-models. We study two mechanisms based on the 
-Laplace perturbation of the parameters of the posterior distribution under
+models. We study two mechanisms based on 
+Laplace perturbation of the parameters of the posterior distribution under the
 $\ell_1$ norm, and compare them with a discrete mechanism
@@
 Accuracy is measured through the Hellinger distance between the posterior
-distribution released by the different mechanisms and the real one.
-We compare the accuracy theoretically and experimentally.
+distribution released by a given mechanism and the one obtained via non-private inference.
+We compare the accuracy of our mechanisms theoretically and experimentally.
 \end{abstract}
@@
 %%Data analysis and privacy are important
-Data analysis techniques have brought significant improvements in a
-variety of applications including applications from the medical,
-financial, social, and transportation fields. In order to provide
-better services, these applications need large amounts of users data
+Modern data analysis techniques have enabled significant advances in a
+variety of applications in medicine, finance, social science, and transportation.
+In order to provide better services, these applications need large amounts of users' data,
 putting at risk the privacy of individual users contributing their data. 
-Differential privacy was proposed a decade ago to address these
-situations and it is on its way to become the gold standard in data
-privacy.
+Differential privacy was proposed a decade ago to address privacy concerns
+in these situations, and is now the standard for privacy-preserving data analysis.
+ %and it is on its way to become the gold standard in data
+%privacy.
 
@@
 %% also a building block of probabilistic programming languages
-Bayesian inference is a standard statistical tool that is useful to
-estimate a posterior distribution when a prior distribution is given
-and some data is observed.
+Many statistical applications are driven by Bayesian inference.
+This is a standard statistical tool in which a prior distribution is combined
+with a sample of observed data in order to estimate a new posterior distribution.
+%is a standard statistical tool that is useful to
+%estimate a posterior distribution when a prior distribution is given
+%and some data is observed.
 
@@
 
-We focus on two classical models: the Beta-Binomial and the
-Dirichlet-Multinomial models. In the Beta-Binomial model the goal
-is to estimate an unknown fraction of a population from a sequence
-of Bernoulli trials each of which is either 0 or 1 and from an initial
-prior belief, a Beta distribution, on that fraction; the trials are assumed to be independent
-given the value of the bias. In the Dirichlet-Multinomial model a Multinomial
-distribution is used to describe categorical data with more than
-two possible outcomes. Similarly, the aim is to learn the various
-unknown proportions of a population from a sequence of trials
-each of which having more than two possible outcomes. Again,
-a prior belief, a Dirichlet distribution, is used to describe the initial knowledge
-about those fractions. The posterior distributions on the proportions will be
-respectively a Beta distribution and a Dirichlet distribution.
-
-In our work  the posterior distribution is the analysis result we obtained from the data.
-While the prior distributions are considerd public information,  publishing the posterior distribution
-inferred from a sensitive dataset can leak information about the individuals in the dataset.
-In order to guarantee differential privacy and to protect the
-individuals' data we can add noise to the posterior before releasing it.
+We focus on inference tasks based on two classical statistical models: the Beta-Binomial and the
+Dirichlet-Multinomial models. In the Beta-Binomial model, we are given a
+dataset consisting of independent Bernoulli trials with bias $p$. Given an initial
+prior belief that $p$ follows a Beta distribution, we may use the dataset to infer a
+posterior belief that $p$ follows a Beta distribution with updated parameters. This model
+generalizes to the Dirichlet-Multinomial model, in which a multinomial distribution
+is used to describe categorial data with more than two possible outcomes. Similarly, the goal
+is infer a belief about the proportions of each outcome. Given a prior belief that these proportions
+come from a Dirichlet distribution, the posterior belief given multinomial data will
+also follow a Dirichlet distribution.
+
+%
+%In the Beta-Binomial model the goal
+%is to estimate an unknown fraction of a population from a sequence
+%of Bernoulli trials each of which is either 0 or 1 and from an initial
+%prior belief, a Beta distribution, on that fraction; the trials are assumed to be independent
+%given the value of the bias. In the Dirichlet-Multinomial model a Multinomial
+%distribution is used to describe categorical data with more than
+%two possible outcomes. Similarly, the aim is to learn the various
+%unknown proportions of a population from a sequence of trials
+%each of which having more than two possible outcomes. Again,
+%a prior belief, a Dirichlet distribution, is used to describe the initial knowledge
+%about those fractions. The posterior distributions on the proportions will be
+%respectively a Beta distribution and a Dirichlet distribution.
+
+In our work, we consider mechanisms which output a complete description of the posterior
+distribution inferred using private data.
+While the prior distribution associated to a given inference task is considered public information,
+the inferred posterior distribution may leak information about the individuals in the dataset.
+In order to guarantee differential privacy, we introduce random noise to the posterior before releasing it.
+Our goal is to design mechanisms which are accurate, in the sense that this noisy posterior is close
+to the posterior one would have inferred without concern for privacy. The most natural way
+to measure closeness is via a distance between probability distributions -- nevertheless, only a few works 
+in the literature (e.g., \cite{zhang2016differential}) actually state accuracy guarantees in this way.
+
 The amount of the noise that we need to introduce
-depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
-small changes in the data set. 
-Sensitivity can be computed in many different ways based on which metric space
-we consider on the output space of the mechanism. In the literature on private Bayesian
-inference (e.g. \cite{zhang2016differential,xiao2012bayesian}), it is usually measured on
-the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
-A more natural approach which we explore here, is to measure sensitivity with respect to
-a metric on the space of inferred probability distributions.
-Another question is that of how to measure accuracy. Again,
-this can be answered in different ways based on the metric
-imposed on the output space, and yet again
-only in few works in literature (e.g. \cite{zhang2016differential})
-distances between probability measures have been used for these purposes.
-
-The question that this work aims at answering is whether
-an approach based on probability metrics can improve on
-the accuracy of approaches based on metrics over
-the numeric parameters of the distributions. 
-We will see that in some cases this can happen.
+depends on the differential privacy parameter $\epsilon$ and the sensitivity of the inference to
+small changes in the input dataset.
+As with accuracy, sensitivity may be measured in many different ways, with each choice giving rise to a different
+method of introducing noise for differential privacy.
+%Sensitivity can be computed in many different ways based on which metric space
+%we consider on the output space of the mechanism. 
+In the existing literature on private Bayesian
+inference (e.g. \cite{zhang2016differential,xiao2012bayesian}), sensitivity is measured via a norm (e.g., the $\ell_1$ norm)
+on the the vector of numbers parametrizing the output distribution. But when the accuracy of a mechanism is determined by
+a distance on distributions themselves, this may not be such a natural choice. The distance between
+two parameterized distributions may behave wildly as a function of the distance between the vectors of parameters characterizing them.
+
+A more natural approach, which we propose here, is to also directly measure sensitivity with respect
+to a metric on the space of inferred probability distributions. Our goal is to identify cases where jointly measuring
+accuracy and sensitivity in terms of a single metric on probability distributions can yield improved accuracy. 
+{\color{red}{MB: Is this accurate? Would we ever want to use different metrics for accuracy and sensitivity?}}
+
+%A more natural approach which we explore here, is to measure sensitivity with respect to
+%a metric on the space of inferred probability distributions.
+%Another question is that of how to measure accuracy. Again,
+%this can be answered in different ways based on the metric
+%imposed on the output space, and yet again
+%only in few works in literature (e.g. \cite{zhang2016differential})
+%distances between probability measures have been used for these purposes.
+
+%The question that this work aims at answering is whether
+%an approach based on probability metrics can improve on
+%the accuracy of approaches based on metrics over
+%the numeric parameters of the distributions. 
+%We will see that in some cases this can happen.
 
@@
 \begin{itemize}
-	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. \gp{it's only eps-d.p for now}
-	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions
-      (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale
-      the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
-  \item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing their performances in terms of accuracy and privacy.
+	\item We give a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
+   %    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
+	\item We propose two ways of improving the accuracy of this basic mechanism: 1) We calibrate noise to a measure of sensitivity determined by a metric between distributions
+      (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) We scale noise according to a a smooth upper bound on the local sensitivity, rather than according to global sensitivity.
+  \item We implement the new proposed mechanism and other art-of-state mechanisms, comparing their performances in terms of accuracy and privacy.
 \end{itemize}

### 2019-01-23 ICML2019/main.tex
working on section 3 and 4

--- 2019-01-23 ICML2019/main.tex
@@
 	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
-    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. \gp{it's only eps-d.p for now}
+    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
 	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions
@@
 
+\noindent \textbf{Hellinger distance.}
+\emph{Hellinger} distance $\hellinger(\cdot,\cdot)$ is a statistical
+divergence measuring the distance between two probability
+distributions. Given two probability distributions $\textup{P}$ and $\textup{Q}$,
+the Hellinger distance between them is defined as:
+\[
+\hellinger(P,Q) =\sqrt{\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda}
+\]
+When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$, we can unfold the above and derive: 
+\[
+ \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+\]
+
 \noindent \textbf{Differential Privacy.}
@@
 \noindent \emph{A note on input data representation.}
-We will think of our input databases $\dataobs$ of length $n$ as histograms 
+We will represent our input databases $\dataobs$ of length $n$ as histograms 
 with $k$-$1$ bins where $k$ is the dimensionality of the problem.
@@
 We are interested in exploring the design space of mechanisms for privately releasing the posterior
-distribution for the Dirichlet-Multinomial model as described in the
-previous section.
+distribution for the Dirichlet-Multinomial model by output
+perturbation with accuracy measured in Hellinger distance.
 It is worth noticing that the posterior distribution of this model is fully characterized
@@
 the Dirichlet distribution with parameter
-$\valpha'=(\valpha + \Delta \valpha)$, or in the case of the
-Beta-Binomial model we are interested in releasing a private version of the Beta distribution with 
+$\valpha'=(\valpha + \Delta \valpha)$, where $\valpha$ is the
+parameter of the prior, and $\Delta \valpha$ is computed from the data
+as discussed in the previous section. In the case of the
+Beta-Binomial model this specialize to releasing a private version of the Beta distribution with 
 parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n -
-\Delta \alpha)$.
-\citet{zhang2016differential} and \citet{xiao2012bayesian}
-have already attacked this problem by adding independent Laplacian noise to the
+\Delta \alpha)$, where $\alpha$ and $\beta$ are the parameters of the
+prior, and $\Delta \alpha$ is the number of $1$ in the data.
+
+Previous work by \citet{zhang2016differential} and \citet{xiao2012bayesian}
+have considered the problem of releasing the posterior of the
+Beta-Binomial model by output perturbation with accuracy measured in terms of
+$\ell_1$ norm. In addition,   \citet{zhang2016differential} has also
+considered KL-divergence between posteriors. 
+In this work we consider instead the Hellinger Distance between
+posteriors. Similarly to KL-divergence, Hellinger Distance is an
+$f$-divergence measuring levels of similarities between
+distributions. However, unlikely KL-divergence, Hellinger Distance is a proper
+distance satisfying reflexivity, symmetry and triangle
+inequality. These properties gives Hellinger Distance analytical
+advantages and makes the minimum hellinger distance  an efficient and
+robust estimator~\cite{}.
+
+attacked this problem by adding independent Laplacian noise to the
 parameters of the posteriors. That is, in the case of the Beta-Binomial system,
@@
 
-We will use the \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$.
-Given two probability distributions $\textup{P}$ and $\textup{Q}$,
-the square of the Hellinger distance between them is defined as:
-\[
-\hellinger(P,Q)^2 =\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
-\]
-When $\textup{P}=\dirichlet{\valpha_1}$ and $\textup{Q}=\dirichlet{\valpha_2}$, we can unfold the above and derive: 
- \[
-   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
- \]
 Our choice to use Hellinger distance is motivated by three facts:
@@
 obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
-To minimize notation we will identify the distribution $\dirichlet{\valpha}$ with its vector
-of parameters.
 Two different upper bounds to the value of
@@
   \max_{\substack{\adj{\dataobs}{\dataobs'},\\
-      \valpha=\inferd{\valpha}{\vtheta}{\dataobs},\\
-      \valpha'=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
+      \dirichlet{\valpha}=\inferd{\valpha}{\vtheta}{\dataobs},\\
+      \dirichlet{\valpha'}=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
 \end{align}
 will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
-Finally, with $\bysinfer{\dataobs}$, and $\bys{\dataobs}{\vtheta}$ we will denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when $\valpha, \vtheta$ or just $\valpha$
-are known from the context.
 
@@
   \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
   \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
@@
   \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \inferd{\valpha}{\vtheta}{\dataobs}$
   \STATE \quad ${\bf let}\ k=\left \{
@@
 distributions as opposed to a metric over the parameters that represent it. In this work we will
-use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
-Given a prior distribution $\dirichlet{\valpha}$,
+use the Hellinger distance, but this approach could be extended to other $f$-divergences. We will
+start by describing how the mechanism works in the case of the Beta-Binomial model noticing that
+the extension to the Dirichelet-Multinomial model is straightforward.
+Given a prior distribution $\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
 we define the follwing set  where the mechanism will sample from:
 \[
-  \candidateset=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
+  \candidateset=\{\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta),\dataobs)\mid \dataobs \in \{0,1\}^n\}.
 \]
-In general $|\candidateset|=\binom{n + 1}{|\mathcal{X}| - 1}$, and in the specific case of $|\mathcal{X}|=2$, that is the Beta-Binomial model,
-the above reduces to:
+Where $\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)$ denotes the posterior beta distribution inferred starting from the parameters in input.
+Notice that the above set reduces to:
 \[
-  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
+  \{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
 \]
-where $\valpha=(\alpha,\beta)$.
-
-\noindent \textbf{A first approach: the $\expmech$ mechanism.} $\expmech$'s pseudocode is shown in Algorithm \ref{mech:expmech1}.
-Given the input $\dataobs\in\{0,1\}^n$ and a prior $\betad(\alpha, \beta)$, the mechanism $\expmech$ outputs an element $r\in\candidateset$ with  probability: 
+We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process on the observed data $\dataobs$
+when the other two parameters, that is prior and likelihood, are fixed.
+
+\subsubsection{A first approach: the $\expmech$ mechanism}
+\label{sec_ehd}
+$\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
 \[
+%\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
 \frac
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
 {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot GS})},
 \]
-where $u(\dataobs,r)$ is the Hellinger based score function:
-$-\hellinger(\bysinfer{\dataobs}, r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
-\[
+where $u(x,r)$ is the Hellinger scoring function: $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
+\begin{equation*}
 GS = 
-\max_{\dataobs,\dataobs': \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
-|\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs'}, r)|
-\]
+\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
+|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
+\end{equation*}
 %
   \begin{algorithm}
-  \caption{$\expmech$}
-  \label{mech:expmech1}
+  \caption{$\expmech$ in Beta-binomial model}
+  \label{mech:expmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $GS$ be the global sensitivity of scoring function.  
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 GS})}
 / {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot GS})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
   \STATE {\bf return} $z$
@@
   \end{algorithm}
-\begin{lem}
-  Algorithm \ref{mech:expmech1} is $\epsilon$-d.p.
-\end{lem}
-
-\noindent \textbf{A second approach based on local sensitivity: $\lexpmech$.} Figure \ref{fig_theory} shows that  the accuracy of
-$\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
-$GS$ is relatively large and hence the variance of the distribution $\expmech$ ends up also being too large. In order to solve this issue we
-will proceed in two steps. We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
+
+Lemma \ref{??} gives us a finite bound on $GS$, while lemma \ref{lem_exp_private} proves privacy $\epsilon$ differential privacy of $\expmech$.
+
+\subsubsection{A second approach based on local sensitivity: $\lexpmech$}
+\label{sec_ehdl}
+Figure \ref{fig_theory} show that  the accuracy of $\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
+$GS$ is relatively big and hence the variance of the distribution $\expmech$ ends up also being too big. In order to solve this issue we
+will proceed in two steps. We will first define $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
 the noise. This is known to be a non private approach, but it will guide us towards new insights.
@@
   \begin{algorithm}
-  \caption{$\lexpmech$}
-  \label{mech:lexpmech}
+  \caption{$\lexpmech$ in Beta-binomial model}
+  \label{mech:expmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $LS$ be the local sensitivity of scoring function.  
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot LS(\dataobs)})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot LS(\dataobs)})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
+  {\exp(\frac{\epsilon\cdot \ux{r}}{2 LS})}
+/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot LS})}$
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
   \STATE {\bf return} $z$
@@
 
-Given $\dataobs, \lexpmech$ samples an element $r \in \mathcal{R}$ with probability:
+$\lexpmech$ shares candidate set and utility function with $\expmech$,
+and outputs a result $r \in \mathcal{R}$ with probability:
 \[
+%\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
 \frac
@@
 \begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)=\max_{\dataobs'\in\mathcal{X}^n,\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer{\dataobs'}, r) - \hellinger(\bysinfer{\dataobs'}, r)\rvert 
+LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
 \end{equation}
-Lemma \ref{lem_loc_opt}  provides a useful characterization of the above function, the interested reader can check the proof in the Appendix.
+The above can be proven to simplify to:
 \begin{lem}
 \label{lem_loc_opt}
-For $\dataobs\in\mathcal{X}^n$, 
-\[LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs'})\]
+\[
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
+\]
 \end{lem}
+The interested reader can check the proof in the Appendix.
 
@@
 \label{sec_ehds}
-In this section, we explore a new mechanism, which compromises between $\expmech$ and $\lexpmech$ and  achieves good accuracy and $\epsilon$-differential privacy simultaneously,
+In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and $\epsilon$-differential privacy simultaneously,
 by scaling the noise to a smooth upper bound on the local sensitivity.
-We first define the smooth sensitivity on a input $\dataobs\in\{0,1\}^n$.
-% The following definition is specific to binary data, hence it will
-% be useful to privately release only posterior Beta distributions in the Beta-Binomial model. The extension to categorical data is straightforward.
+We first define the smooth sensitivity on a input $\dataobs$. The following definition is specific to binary data, that is it will
+be useful to privately release a posterior Beta distribution. The extension to categorical data is straightforward.
 \begin{definition}
 \label{def_gamma_smooth}
-For $\dataobs\in\mathcal{X}^n$, and $\gamma \in \mathbb{R}^{> 0}$, the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer{\dataobs},\cdot)$ is defined as:
+Given a data set $\dataobs$ of size $n$, we define the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer(\dataobs),\cdot)$ as:
 \begin{equation}
   \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs' \in \mathcal{X}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
+   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
 \end{equation}
@@
 \end{thm}
-again, the interested reader will find the proof in Appendix.
-We are now ready to describe the mechanism $\hexpmech$ in Algorithm \ref{mech:sexpmech}. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
+The interested reader will find the proof in Appendix.
+We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
 \[
@@
 \]
-where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer{\dataobs},\cdot)$. {\color{red}{why do we choose 1???}}
+where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
   \begin{algorithm}
-  \caption{$\hexpmech$}
-  \label{mech:sexpmech}
+  \caption{$\hexpmech$ in Beta-binomial model}
+  \label{mech:expmech}
   \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$,  prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bys{\valpha}{\dataobs}$.
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
+  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
+  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $S(\dataobs)$ be the vector of $\gamma-$sensitivity of scoring function. 
+  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
   \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
+  \STATE \quad \quad calculate the outputting probability of $r$.
+  \STATE \quad \quad $Pr[r] = 
   {\exp(\frac{\epsilon \cdot \ux{r}}{4 S(\dataobs)})}
 / {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot \ux{r'}}{4 \cdot S(\dataobs)})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
+\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
   \STATE {\bf return} $z$
@@
 
-\begin{thm}
-  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
-\end{thm}
-% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
-% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
-% \[
-%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
-% \]
-% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
-% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
-% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
+As already mentioned $\expmech, \lexpmech, \hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
+Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
+\[
+  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+\]
+and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
+distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
+over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
+that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here? and was $\datauni$} defined?}
+
+\section{Privacy Analysis}
+
+\subsection{Privacy of Laplace Mechanism Family}
+The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
+Mechanisms $\lapmech$ and $\ilapmech$ are trivially $\epsilon$-differentially private since the mechanisms
+add Laplacian noise proportional to the $\ell_1$-norm sensitivity to the arguments of the posterior distributions.
+\begin{lem}
+  $\lapmech$, $\ilapmech$ are $\epsilon$-differentially private.
+\end{lem}
+
+\subsection{Privacy of Exponential Mechanism Family}
+\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
+\begin{lem}
+\label{lem_exp_private}
+$\expmech$ is $\epsilon-$differentially private by \cite{dwork2014algorithmic}.
+\end{lem}
+
+% \subsubsection{$\lexpmech$ non-Differential Privacy}
+% Exponential mechanism with local sensitivity non-differential privacy.
+
+\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}
+
+\begin{lem}
+\label{lem_hexpmech_privacy}
+$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
+\end{lem}
+(Proof is in Appendix)
+
 \section{Accuracy Analysis}
-We will observe accuracy of mechanisms.
-In this section, we fix $\alpha$ and $\beta$, and for simplicity, we define the term of difference from $\betad(\alpha, \beta)$, the true posterior distribution.
-\[
-c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
-\]
+
 \subsection{Accuracy Bound for Baseline Mechanisms}
@@
 \lapmechPr{\dataobs}{
-\hellinger(\bysinfer{\dataobs}, z ) = c(t)
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
 }
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
 \end{cases}
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $z$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 \end{lem}
@@
 %  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.19673467014$.\\
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 %  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
 %  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 %&\lapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0
+%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
 %} = 0.19673467014,\\
@@
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
 %& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
@@
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
 %& = 1 - 
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-\[
-\Pr[\hellinger(\bysinfer{\dataobs}, z ) = c(t)]
-= \begin{cases}
+\begin{align*}
+&\lapmechPr{\dataobs}{
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+}\\
+& \qquad = \begin{cases}
 0.19673467014 & t = 0\\
@@
 \end{cases}.
-\]
-%\begin{align*}
-%&\ilapmechPr{\dataobs}{
-%\hellinger(\bysinfer{\dataobs}, z ) = c(t)
-%}\\
-%& \qquad =  \begin{cases}
-%0.31606027941 & t = 0\\
-%0.11627207896 & t = 1\\
-%0.04277410743 & t = 2
-%\end{cases}.
-%\end{align*}
+\end{align*}
 
@@
 Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.
+
+Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
+
 \begin{align*}
@@
 \ilapmechPr{\dataobs}{
-\hellinger(\bysinfer{\dataobs}, z ) = c(t)
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
 }
@@
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.31606027941$.
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 %  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
 %
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
 %  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
@@
 %&\ilapmechPr{\dataobs}{
-%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0}= 0.31606027941,\\
+%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
 %&\ilapmechPr{\dataobs}{
 %\begin{aligned}
-%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
+%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
 %& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
@@
 %In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
-
-Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
-\[
-\Pr[
-\hellinger(\bysinfer{\dataobs}, z ) = c(t)
-]
- =  \begin{cases}
+\begin{align*}
+&\ilapmechPr{\dataobs}{
+\begin{aligned}
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
+&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+\end{aligned}
+}\\
+& \qquad = \begin{cases}
 0.31606027941 & t = 0\\
@@
 %  \label{eq_acc}
-%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c  }\\ 
+%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
 %  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
@@
   \begin{align*}
-  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(t)  } }\\ 
-  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-%  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
+  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
+  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
+  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
   \end{align*}
@@
 %  \hline
-%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z ) = c} $
+%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 %  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
 %  \hline
-%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
+%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 %  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
 %  \hline
-%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
+%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 %  & $\frac{1}{\nomalizer{\dataobs}}$ 
@@
 
-By solving equations on accuracy such as:
+By solving following equations:
+%  \[
+  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
 \begin{align*}
-\lefteqn{\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }}\\
-&\qquad =
-\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }
-=
-0.19673467 
+ &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
+ & = 0.19673467 \text{ or } 0.316060279
 \end{align*}
-%By solving following equations:
-%  \[
-%  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
-%\begin{align*}
-% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(0)  } \\
-% & = 0.19673467 \text{ or } 0.316060279
-%\end{align*}
 %  \]
@@
 %   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-%\begin{align*}
-%  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }\\
-%  &= 0.119325609 \text{ or } 0.116272079
-%\end{align*}
+\begin{align*}
+  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
+  &= 0.119325609 \text{ or } 0.116272079
+\end{align*}
 %  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
@@
 %    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
-%\begin{align*}
-% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(2)  }\\
-% &=0.072374641 \text{ or }  0.042774107
+\begin{align*}
+ &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
+ &=0.072374641 \text{ or }  0.042774107
 %\]
-%\end{align*}
+\end{align*}
 we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
@@
 % %\[
-% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
+% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
 % %\]
@@
 % \[
-% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
+% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
 % \]
@@
 % \begin{align*}
-% &\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+% &\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
 % & = 
 % \begin{cases}
-% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
+% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
 % \end{cases}\\
@@
 % \begin{cases}
-% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
 % \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
-% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
+% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
 % \end{cases}\\
-% &= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
+% &= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
 % \end{align*}
-% The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
+% The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
 % Hence, we conclude the statement of this lemma.
@@
 
-%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer{\dataobs}$.
+%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
 %\begin{equation*}
@@
 %LS(\dataobs) 
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs}) \\
-%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\} \\
-%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\}.
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
+%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
+%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
 %\end{split}
@@
 %\begin{aligned}
-%&\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs})\\
-%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
+%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
+%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
 %\end{aligned}
@@
 %  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
-%\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs}).
+%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
 %\end{align*}
@@
 We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$.
-It is shown that maximum value taken when  $r = \bysinfer{\dataobs}$.
+It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.
 
@@
 \[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
+LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
 \]
@@
 \begin{align*}
-&\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
 & = 
 \begin{cases}
-\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
 \end{cases}\\
@@
 \begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
 \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
-\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
+\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
+\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
 \end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
+&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
 \end{align*}
-The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
+The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
 Hence, we conclude the statement of this lemma.
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
+\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
 \end{cases}
 \end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 }
@@
 Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta }}$, where $Y \thicksim \lap{0}{\frac{\Delta }{\epsilon}}$ in our setting.
+Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
 
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta }} - e^{\frac{\epsilon (t + 1)}{\Delta }}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}) & t < 0
 \end{cases}
@@
 
-Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 By applying Hellinger distance in our case, we get:
@@
 %\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
 %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
@@
 %\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
+%& \Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
 %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
@@
 \begin{aligned}
-\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )}\\ 
+\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
 &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
@@
 \begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
+\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
+\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
 \end{cases}
@@
   &\Pr\left[
-\begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2}\\
+\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
 &= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
@@
 \right] \\
-  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
+  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
   \end{align*}
@@
   & \Pr\left[
-  \begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2} \\
+  \begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
   & =
@@
 \right] \\
-   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
+   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
   \end{align*}

### 2019-01-23 ICML2019/main.tex
working on section 3 and 4.

@@
 \noindent \textbf{Hellinger distance.}
-\emph{Hellinger} distance $\hellinger(\cdot,\cdot)$ is a statistical
+The \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$ is a statistical
 divergence measuring the distance between two probability
@@
 \]
-When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$, we can unfold the above and derive: 
+When we consider the Hellinger distance between Dirichlet
+distributions we can simplify this definition to close form. If $\textup{P}=\dirichlet{\valpha_1}$ and
+$\textup{Q}=\dirichlet{\valpha_2}$ we have: 
  \[
- \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
+   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
  \]
@@
 
-We will use the \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$.
-Given two probability distributions $\textup{P}$ and $\textup{Q}$,
-the square of the Hellinger distance between them is defined as:
-\[
-\hellinger(P,Q)^2 =\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
-\]
-When $\textup{P}=\dirichlet{\valpha_1}$ and $\textup{Q}=\dirichlet{\valpha_2}$, we can unfold the above and derive: 
- \[
-   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
- \]
-Our choice to use Hellinger distance is motivated by three facts:
-\begin{itemize}
-  \item It simplifies calculations in the case of the probabilistic models considered here.
-
-  \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an adversary can have in distingishing two distributions.
-
-  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. Indeed, as shown in Figure \ref{fig_sensitivity}, there can be a gap
-    between the global sensitivity and the local sensitivity.
 \begin{figure}[ht]
@@
 \end{figure}
-\end{itemize}
 

### 2019-01-23 ICML2019/main.tex
fixed notation section 5

@@
 \STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
+\STATE {\bf return} $z$
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{thm}
+  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
+\end{thm}
+% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
+% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
+% \[
+%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
+% \]
+% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
+% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
+% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
+% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
+\section{Private Mechanisms}
+\label{sec_mechs}
+In this section we will describe and analyse a series of mechanisms to privately compute and release
+a posterior distribution.
+Section \ref{sec_ell1_dim} presents a first mechanism, $\lapmech$,
+based on the Laplace primitive where the sensitivity is measured w.r.t. to $\ell_1$ norm.
+Section \ref{sec_ell1_hist}, shows that $\lapmech$'s accuracy can be improved
+by performing a better analysis on the sensitivity of the inference process.
+Section \ref{sec_ehd}, shows an instance of the exponential mechanism, $\expmech$, where the scoring
+function is based on the Hellinger distance, we will see how this mechanisms performs
+poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
+We then proceed to introduce $\lexpmech$, a variation of $\expmech$ which uses a lower bound
+on the global sensitivity called local sensitivity.
+Unfortunately, despite improving on accuracy $\lexpmech$ is non-private.
+Finally, building on $\lexpmech$, we introduce $\hexpmech$:
+which, based on the notion of \emph{smooth} sensitivity, achieves $\epsilon$-differential privacy and
+has good accuracy in specific cases.
+In presenting these mechanisms we will denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  $\dirichlet{\valpha'}$
+obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
+To minimize notation we will identify the distribution $\dirichlet{\valpha}$ with its vector
+of parameters.
+Two different upper bounds to the value of
+\begin{align}
+  \label{eqn:eq1}
+  \max_{\substack{\adj{\dataobs}{\dataobs'},\\
+      \valpha=\inferd{\valpha}{\vtheta}{\dataobs},\\
+      \valpha'=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
+\end{align}
+will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
+Finally, with $\bys{\dataobs}{\vtheta}$ we will denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when no confusion can arise.
+
+\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
+\label{sec_ell1_dim}
+We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
+The idea of $\lapmech$ is to add Laplacian noise with scale proportional to $\mathcal{X}$ to
+the differences between the respective numeric parameters of the prior
+and posterior distribution. 
+\begin{algorithm}
+  \caption{$\lapmech$}
+  \label{lapmech}
+  \begin{algorithmic}
+  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
+  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
+  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}| - 1$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{|\mathcal{X}|}{\epsilon}}$
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\tilde{\valpha}$
+  \end{algorithmic}
+\end{algorithm}
+\begin{lem}
+  Algorithm \ref{lapmech} is $\epsilon$-d.p.
+  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to the value denoted by (\ref{eqn:eq1}). \end{proof}
+\end{lem}
+
+\subsection{Improving the sensitivity ($\ilapmech$)}
+\label{sec_ell1_hist}
+By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to the value denoted by (\ref{eqn:eq1}).
+Indeed a constant will do. Algorithm $\ilapmech$ in Algorithm \ref{ilapmech} takes advantage of this fact. 
+Indeed, when $\mathcal{X}=2$, 1 is an upper bound for the value of (\ref{eqn:eq1}), while when $\mathcal{X}>2$, 2 is.
+In Algorithm \ref{ilapmech} the algorithm $\ilapmech$ is presented.
+\begin{algorithm}
+  \caption{$\ilapmech$}
+  \label{ilapmech}
+  \begin{algorithmic}
+  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
+  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
+  \STATE \quad ${\bf let}\ k=\left \{
+        \begin{array}{lll}          
+          1&\text{if}& |\mathcal{X}|=2\\
+          2&\text{otherwise}
+        \end{array}
+      \right .\ $
+  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
+  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}|-1$:
+  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{k}{\epsilon}}$
+  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
+  % \RETURN $a_{k+1}$.
+  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE {\bf return} $\tilde{\valpha}$
+  \end{algorithmic}
+\end{algorithm}
+\begin{lem}
+  Algorithm \ref{ilapmech} is $\epsilon$-d.p.
+  \begin{proof} By noticing that 1 and 2 are upper bounds to the value denoted by (\ref{eqn:eq1}), respectively when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
+  \end{proof}
+\end{lem}
+
+\subsection{A new family of mechanisms}
+\label{sec_exp}
+In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
+of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
+probability distributions.
+The idea is that $\expmech$ will sample and output a distribution with higher probability when
+it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
+distributions as opposed to a metric over the parameters that represent it. In this work we will
+use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
+Given a prior distribution $\dirichlet{\valpha}$,
+we define the follwing set  where the mechanism will sample from:
+\[
+  \candidateset{\valpha}=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
+\]
+In general $|\candidateset{\valpha}|=\binom{n + 1}{|\mathcal{X}| - 1}$ when $\valpha\in\mathcal{X}^n$. In the specific case of $|\mathcal{X}|=2$ with $\valpha=(\alpha,\beta)$,
+that is the Beta-Binomial model, the above reduces to:
+\[
+  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
+\]
+
+\noindent \textbf{A first approach: the $\expmech$ mechanism.}
+\label{sec_ehd}
+$\expmech$'s pseudocode is shown in Algorithm \ref{mech:expmech1}. $\expmech$ is an instance
+of the Exponential mechanism where the scoring function is instantiated with the function: $r\mapsto -\hellinger(\bysinfer{\dataobs}, r)$.
+Given the input $\dataobs\in\mathcal{X}^n$ and a prior $\dirichlet{\valpha}$, the mechanism $\expmech$ outputs an element $r\in\candidateset{\valpha}$ with  probability: 
+\[
+\frac
+  {\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r)}{2\cdot GS})}
+{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r')}{2\cdot GS})},
+\]
+where $GS$ is the global sensitivity of the scoring function, defined as:
+\[
+\max_{\dataobs,\dataobs': \\ \adj{\dataobs}{\dataobs'}}\max_{r\in \candidateset{\valpha}}
+|\hellinger(\bys{\dataobs}{\valpha}, r) - \hellinger(\bys{\dataobs'}{\valpha}, r)|
+\]
+% 
+  \begin{algorithm}
+  \caption{$\expmech$}
+  \label{mech:expmech1}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
+  \STATE \quad {\bf set} $z=r$ with probability $\frac
+  {\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r)}{2\cdot GS})}
+{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r')}{2\cdot GS})}$
+\STATE {\bf return} $z$
+  \end{algorithmic}
+  \end{algorithm}
+\begin{lem}
+  Algorithm \ref{mech:expmech1} is $\epsilon$-d.p.
+\end{lem}
+
+\noindent \textbf{A second approach based on local sensitivity: $\lexpmech$.}
+\label{sec_ehdl}
+Figure \ref{fig_theory} shows that  the accuracy of
+$\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
+$GS$ is relatively large and hence the variance of the distribution $\expmech$ ends up also being too large. In order to solve this issue we
+will proceed in two steps. We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
+the noise. This is known to be a non private approach, but it will guide us towards new insights.
+We will then proceed to use a smooth bound the local sensitivity to
+calibrate the noise.
+
+  \begin{algorithm}
+  \caption{$\lexpmech$}
+  \label{mech:lexpmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.
+  \STATE \quad {\bf set} $z=r$ with probability $\frac
+  {\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r)}{2\cdot LS(\dataobs)})}
+{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r')}{2\cdot LS(\dataobs)})}$
+\STATE {\bf return} $z$
+  \end{algorithmic}
+  \end{algorithm}
+
+Given $\dataobs$, and a prior $\dirichlet{\valpha}$, $\lexpmech$ samples an element $r \in \candidateset{\valpha}$ with probability:
+\[
+ \frac
+  {\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r)}{2\cdot LS(\dataobs)})}
+{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r')}{2\cdot LS(\dataobs)})}
+\]
+where $LS(\dataobs)$ is the local sensitivity of the scoring function, defined as:
+\begin{equation}\label{eq:local_sensitivity_scoring}
+\max_{\dataobs'\in\mathcal{X}^n,\adj{\dataobs}{\dataobs'}, r\in \candidateset{\valpha}}\lvert \hellinger(\bys{\dataobs}{\valpha}, r) - \hellinger(\bys{\dataobs'}{\valpha}, r)\rvert 
+\end{equation}
+Lemma \ref{lem_loc_opt}  provides a useful characterization of the above function, the interested reader can check the proof in the Appendix.
+\begin{lem}
+\label{lem_loc_opt}
+For $\dataobs\in\mathcal{X}^n$, 
+\[LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bys{\dataobs}{\valpha}, \bys{\dataobs'}{\valpha})\]
+\end{lem}
+
+\noindent \textbf{A third approach based on smooth sensitivity: $\hexpmech$}. 
+\label{sec_ehds}
+In this section, we explore a new mechanism, which compromises between $\expmech$ and $\lexpmech$ and  achieves good accuracy and $\epsilon$-differential privacy simultaneously,
+by scaling the noise to a smooth upper bound on the local sensitivity.
+%We first define the smooth sensitivity on a input $\dataobs\in\{0,1\}^n$.
+% The following definition is specific to binary data, hence it will
+% be useful to privately release only posterior Beta distributions in the Beta-Binomial model. The extension to categorical data is straightforward.
+\begin{definition}
+\label{def_gamma_smooth}
+For $\dataobs\in\mathcal{X}^n$, and $\gamma \in \mathbb{R}^{> 0}$, the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer{\dataobs},\cdot)$ is defined as:
+\begin{equation}
+  \label{eq_smooth}
+   S(\dataobs)=\max_{\dataobs' \in \mathcal{X}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
+\end{equation}
+where $d$ is the Hamming distance between two data sets.
+\end{definition}
+
+\begin{thm}
+  \label{thm_gamma_smooth}
+  For any $\dataobs, \dataobs'\in\mathcal{X}^n$, and $\gamma \in \mathbb{R}^{+}$
+  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
+\end{thm}
+again, the interested reader will find the proof in Appendix.
+We are now ready to describe the mechanism $\hexpmech$ in Algorithm \ref{mech:sexpmech}. $\hexpmech$ outputs a candidate $r \in \candidateset{\valpha}$ with probability
+\[
+ \frac
+  {\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r)}{4\cdot S(\dataobs)})}
+{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{-\epsilon\cdot \hellinger(\bys{\dataobs}{\valpha}, r')}{4\cdot S(\dataobs)})}
+\]
+where $S(\dataobs)$ is the 1-smooth sensitivity of  the function $\hellinger(\bysinfer{\dataobs},\cdot)$. {\color{red}{why do we choose 1???}}
+  \begin{algorithm}
+  \caption{$\hexpmech$}
+  \label{mech:sexpmech}
+  \begin{algorithmic}
+  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
+  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
+  \STATE \quad {\bf set} $z=r$ with probability $\frac{\exp(\frac{\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)})}{\Sigma_{r' \in \candidateset{\valpha}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{4\cdot S(\dataobs)})}$
 \STATE {\bf return} $z$

### 2019-01-23 ICML2019/main.tex
rewrite section 5

@@
 \label{sec_mechs}
-In this section we will describe and analyse a series of mechanisms.
-Section \ref{sec_ell1_dim} presents a first mechanism, $\lapmech$,
-based on the Laplace primitive where the sensitivity is measured w.r.t. to $\ell_1$ norm.
-Section \ref{sec_ell1_hist}, shows that $\lapmech$'s accuracy can be improved
-by performing a better analysis on the sensitivity of the inference process.
-Section \ref{sec_ehd}, shows an instance of the exponential mechanism, $\expmech$, where the scoring
-function is based on the Hellinger distance, we will see how this mechanisms performs
-poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
-Section \ref{sec_ehdl} introduces, $\lexpmech$, a variation of $\expmech$ which uses a lower bound
-on the global sensitivity called local sensitivity.
-Unfortunately, despite improving on accuracy $\lexpmech$ is non-private.
-Finally, building on $\lexpmech$, Section \ref{sec_ehds} introduces $\hexpmech$:
-which, based on the notion of \emph{smooth} sensitivity, achieves $\epsilon$-differential privacy and
-has good accuracy in specific cases.
-In presenting these mechanisms we will denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  $\dirichlet{\valpha'}$
-obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
-To minimize notation we will identify the distribution $\dirichlet{\valpha}$ with its vector
-of parameters.
-Two different upper bounds to the value of
-\begin{align}
-  \label{eqn:eq1}
-  \max_{\substack{\adj{\dataobs}{\dataobs'},\\
-      \valpha=\inferd{\valpha}{\vtheta}{\dataobs},\\
-      \valpha'=\inferd{\valpha}{\vtheta}{\dataobs'}}}||\valpha-\valpha'||_1 
-\end{align}
-will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
-Finally, with $\bysinfer{\dataobs}$, and $\bys{\dataobs}{\vtheta}$ we will denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when $\valpha, \vtheta$ or just $\valpha$
-are known from the context.
-
-\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
-\label{sec_ell1_dim}
-We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
-The idea of $\lapmech$ is to add Laplacian noise with scale proportional to $\mathcal{X}$ to
-the differences between the respective numeric parameters of the prior
-and posterior distribution. 
-\begin{algorithm}
-  \caption{$\lapmech$}
-  \label{lapmech}
-  \begin{algorithmic}
-  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
-  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
-  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}| - 1$:
-  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{|\mathcal{X}|}{\epsilon}}$
-  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
-  % \RETURN $a_{k+1}$.
-  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
-  \STATE {\bf return} $\tilde{\valpha}$
-  \end{algorithmic}
-\end{algorithm}
-\begin{lem}
-  Algorithm \ref{lapmech} is $\epsilon$-d.p.
-  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to the value denoted by (\ref{eqn:eq1}). \end{proof}
-\end{lem}
-
-\subsection{Improving the sensitivity ($\ilapmech$)}
-\label{sec_ell1_hist}
-By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to the value denoted by (\ref{eqn:eq1}).
-Indeed a constant will do. Algorithm $\ilapmech$ in Algorithm \ref{ilapmech} takes advantage of this fact. 
-Indeed, when $\mathcal{X}=2$, 1 is an upper bound for the value of (\ref{eqn:eq1}), while when $\mathcal{X}>2$, 2 is.
-In Algorithm \ref{ilapmech} the algorithm $\ilapmech$ is presented.
-\begin{algorithm}
-  \caption{$\ilapmech$}
-  \label{ilapmech}
-  \begin{algorithmic}
-  \INPUT $\dataobs\in\mathcal{X}^n$, $\dirichlet{\valpha}$
-  \STATE \quad {\bf let} $\valpha' = \inferd{\valpha}{\vtheta}{\dataobs}$
-  \STATE \quad ${\bf let}\ k=\left \{
-        \begin{array}{lll}          
-          1&\text{if}& |\mathcal{X}|=2\\
-          2&\text{otherwise}
-        \end{array}
-      \right .\ $
-  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )\in \mathbb{N}^{|\mathcal{X}|}$ 
-  \STATE \quad {\bf For} $i = 1 \dots |\mathcal{X}|-1$:
-  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{k}{\epsilon}}$
-  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
-  % \RETURN $a_{k+1}$.
-  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
-  \STATE {\bf return} $\tilde{\valpha}$
-  \end{algorithmic}
-\end{algorithm}
-\begin{lem}
-  Algorithm \ref{ilapmech} is $\epsilon$-d.p.
-  \begin{proof} By noticing that 1 and 2 are upper bounds to the value denoted by (\ref{eqn:eq1}), respectively when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
-  \end{proof}
-\end{lem}
-
-\subsection{A new family of mechanisms}
-\label{sec_exp}
-In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
-of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
-probability distributions.
-The idea is that $\expmech$ will sample and output a distribution with higher probability when
-it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
-distributions as opposed to a metric over the parameters that represent it. In this work we will
-use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
-Given a prior distribution $\dirichlet{\valpha}$,
-we define the follwing set  where the mechanism will sample from:
-\[
-  \candidateset=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
-\]
-In general $|\candidateset|=\binom{n + 1}{|\mathcal{X}| - 1}$, and in the specific case of $|\mathcal{X}|=2$, that is the Beta-Binomial model,
-the above reduces to:
-\[
-  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
-\]
-where $\valpha=(\alpha,\beta)$.
-
-\noindent \textbf{A first approach: the $\expmech$ mechanism.} $\expmech$'s pseudocode is shown in Algorithm \ref{mech:expmech1}.
-Given the input $\dataobs\in\{0,1\}^n$ and a prior $\betad(\alpha, \beta)$, the mechanism $\expmech$ outputs an element $r\in\candidateset$ with  probability: 
-\[
-\frac
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
-{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot GS})},
-\]
-where $u(\dataobs,r)$ is the Hellinger based score function:
-$-\hellinger(\bysinfer{\dataobs}, r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
-\[
-GS = 
-\max_{\dataobs,\dataobs': \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
-|\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs'}, r)|
-\]
-% 
-  \begin{algorithm}
-  \caption{$\expmech$}
-  \label{mech:expmech1}
-  \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
-  \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot GS})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot GS})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
-\STATE {\bf return} $z$
-  \end{algorithmic}
-  \end{algorithm}
-\begin{lem}
-  Algorithm \ref{mech:expmech1} is $\epsilon$-d.p.
-\end{lem}
-
-\noindent \textbf{A second approach based on local sensitivity: $\lexpmech$.} Figure \ref{fig_theory} shows that  the accuracy of
-$\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
-$GS$ is relatively large and hence the variance of the distribution $\expmech$ ends up also being too large. In order to solve this issue we
-will proceed in two steps. We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
-the noise. This is known to be a non private approach, but it will guide us towards new insights.
-We will then proceed to use a smooth bound the local sensitivity to
-calibrate the noise.
-
-  \begin{algorithm}
-  \caption{$\lexpmech$}
-  \label{mech:lexpmech}
-  \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'}= \bys{\dataobs}{\valpha}$.   
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
-  \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
-  {\exp(\frac{\epsilon\cdot \ux{r}}{2\cdot LS(\dataobs)})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(\dataobs, r')}{2\cdot LS(\dataobs)})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
-\STATE {\bf return} $z$
-  \end{algorithmic}
-  \end{algorithm}
-
-Given $\dataobs, \lexpmech$ samples an element $r \in \mathcal{R}$ with probability:
-\[
-\frac
-  {\exp(\frac{\epsilon \cdot \ux{r}}{2\cdot LS(\dataobs)})}
-{\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{2\cdot LS(\dataobs)})},
-\]
-where $LS(\dataobs)$ is the local sensitivity of the scoring function, defined as:
-\begin{equation}\label{eq:local_sensitivity_scoring}
-LS(\dataobs)=\max_{\dataobs'\in\mathcal{X}^n,\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer{\dataobs'}, r) - \hellinger(\bysinfer{\dataobs'}, r)\rvert 
-\end{equation}
-Lemma \ref{lem_loc_opt}  provides a useful characterization of the above function, the interested reader can check the proof in the Appendix.
-\begin{lem}
-\label{lem_loc_opt}
-For $\dataobs\in\mathcal{X}^n$, 
-\[LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs'})\]
-\end{lem}
-
-\subsubsection{A third approach based on smooth sensitivity: $\hexpmech$}
-\label{sec_ehds}
-In this section, we explore a new mechanism, which compromises between $\expmech$ and $\lexpmech$ and  achieves good accuracy and $\epsilon$-differential privacy simultaneously,
-by scaling the noise to a smooth upper bound on the local sensitivity.
-We first define the smooth sensitivity on a input $\dataobs\in\{0,1\}^n$.
-% The following definition is specific to binary data, hence it will
-% be useful to privately release only posterior Beta distributions in the Beta-Binomial model. The extension to categorical data is straightforward.
-\begin{definition}
-\label{def_gamma_smooth}
-For $\dataobs\in\mathcal{X}^n$, and $\gamma \in \mathbb{R}^{> 0}$, the $\gamma$-smooth sensitivity of $\hellinger(\bysinfer{\dataobs},\cdot)$ is defined as:
-\begin{equation}
-  \label{eq_smooth}
-   S(\dataobs)=\max_{\dataobs' \in \mathcal{X}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
-\end{equation}
-where $d$ is the Hamming distance between two data sets.
-\end{definition}
-
-\begin{thm}
-  \label{thm_gamma_smooth}
-  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
-  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
-\end{thm}
-again, the interested reader will find the proof in Appendix.
-We are now ready to describe the mechanism $\hexpmech$ in Algorithm \ref{mech:sexpmech}. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
-\[
-  \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
-  {\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot \ux{r'}}{4\cdot S(\dataobs)})},
-\]
-where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer{\dataobs},\cdot)$. {\color{red}{why do we choose 1???}}
-  \begin{algorithm}
-  \caption{$\hexpmech$}
-  \label{mech:sexpmech}
-  \begin{algorithmic}
-  \INPUT observed data set $\dataobs \in \mathcal{X}^n$,  prior: $\dirichlet{\valpha}$, $\epsilon$
-  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bys{\valpha}{\dataobs}$.
-  \STATE \quad {\bf Initialize} associative map $pr$ of size $|\candidateset|$.
-  \STATE \quad {\bf For} $r$ in $\candidateset$:
-  \STATE \quad \quad $pr[r] = 
-  {\exp(\frac{\epsilon \cdot \ux{r}}{4 S(\dataobs)})}
-/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot \ux{r'}}{4 \cdot S(\dataobs)})}$
-\STATE \quad {\bf sample} in $z$ from probability distribution $pr$.
-\STATE {\bf return} $z$
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{thm}
-  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
-\end{thm}
-% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
-% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
-% \[
-%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
-% \]
-% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
-% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
-% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
-% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
-\section{Private Mechanisms}
-\label{sec_mechs}
 In this section we will describe and analyse a series of mechanisms to privately compute and release

### 2019-01-23 ICML2019/main.tex
tweak

@@
 
-\appendix
-
-\noindent \textbf{Theorem \ref{thm_gamma_smooth}.}
-\emph{
-Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
-whenever $\adj{\dataobs}{\dataobs'}$, 
-%\begin{equation}
-%\label{eq_gamma_smooth}
-$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
-}
-
-\begin{proof}
-of Theorem. \ref{thm_gamma_smooth}.\\
-For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
-From Equation (\ref{eq_smooth}), we can get:
-\[
-\frac{1}{S(\dataobs)} 
- = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
-\]
-
-Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
-
-\begin{equation*}
-\begin{split}
-& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
-& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
-\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
-\}\\
-& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
-\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
-\}\\
-& = \gamma + \frac{1}{S(\dataobs')}
-\end{split}
-\end{equation*}
-Then we can get:
-$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
-\end{proof}
-
-\noindent \textbf{Lemma \ref{lem_loc_opt}.}
-\emph{
-\[
-LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
-\]
-}
-
-\begin{proof} of Lemma \ref{lem_loc_opt}.\\
-For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
-\begin{align*}
-&\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
-& = 
-\begin{cases}
-\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
-\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
-\end{cases}\\
-& \leq 
-\begin{cases}
-\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
-\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
-\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
-\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
-\end{cases}\\
-&= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
-\end{align*}
-The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
-Hence, we conclude the statement of this lemma.
-\end{proof}
-
-\noindent \textbf{ Lemma \ref{lem_hexpmech_privacy}. } 
-\emph{
-$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
-}
-
-\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
-  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
-  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
-  \begin{equation*}
-  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
-  \end{equation*}
-  By definition \ref{def_smoo_2}:
-  \begin{equation*}
-  \begin{split}
-  \hexpmechPr{\dataobs}{z = r} 
-  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
-  & = \frac {\exp\big(
-  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}} \\
-  & = \frac {\exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}}
-  \\
-  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
-  \end{split}
-  \end{equation*}
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \frac {\exp\big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)}
-  {\unomalizer{\dataobs}}
-  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
-  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)\\
-  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
-  \big)\\
-  \end{split}
-  \end{equation*}
-
-  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  & \cdot \exp
-  \big(
-  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
-  \big)\\
-  \end{split}
-  \end{equation*}
-
-  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}
-  \exp
-  \big(
-  \frac{\epsilon}{4} \cdot \gamma
-  \big)\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {\unomalizer{\dataobs}}\\
-  \end{split}
-  \end{equation*}
-
-  Doing the same transformation in the denominator:
-  \begin{equation*}
-  \begin{split}
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
-  & \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  \end{split}
-  \end{equation*}
-
-  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
-  \big)
-  }\\
-  & \cdot 
-  \frac{1}
-  {
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
-  \big)
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)}\\
-  & \cdot\frac{1}{
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon\cdot(\ux{r'})}{4}
-  (\frac{1}{S(\dataobs)}
--
-  \frac{1}{S(\dataobs')})
-  \big)
-  }
-  \end{split}
-  \end{equation*}
-
-  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)}\\
-  & \cdot \frac{1}{
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon}{4}
-  (\frac{1}{S(\dataobs)}
--
-  \frac{1}{S(\dataobs')})
-  \big)
-  }\\
-  \end{split}
-  \end{equation*}
-
-  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
-  $\frac{- \epsilon}{4}
-  (\frac{1}{S(\dataobs)}-
-  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
-  \begin{equation*}
-  \begin{split}
-  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4}
-  \big)
-  \exp
-  \big(
-  \frac{- \epsilon}{4} \cdot \gamma
-  \big)
-  }\\
-  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \sum_{r'\in \candidateset} 
-  \exp 
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
-  \big)
-  \exp 
-  \big(
-  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
-  \big)
-  }\\
-  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
-  \frac {
-  \exp
-  \big(
-  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
-  \big)
-  } 
-  {
-  \unomalizer{\dataobs'}
-  }\\
-  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
-  \end{split}
-  \end{equation*}
-
-  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
-
-\end{proof}
-
-\noindent \textbf{ Lemma \ref{lem_acc_lap}.}
-\emph{
-Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
-\begin{align*}
-&
-\lapmechPr{\dataobs}{
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-}
-\\
-&\qquad = 
-\begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
-\end{cases}
-\end{align*}
-where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
-}
-
-\begin{proof} of Lemma \ref{lem_acc_lap}.\\
-Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
-Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta }}$, where $Y \thicksim \lap{0}{\frac{\Delta }{\epsilon}}$ in our setting.
-
-Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
-%\[
-%\Pr\big[\lfloor Y \rfloor = t\big] 
-%= \Pr[ t \leq Y < t + 1] 
-%= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-%\]
-%when $t \geq 0$, and
-%\[
-%\Pr\big[\lfloor Y \rfloor = t\big] 
-%= \Pr[ t \leq Y < t + 1] 
-%= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
-%\]
-%when $t < 0$.
-\begin{align*}
-\Pr\big[\lfloor Y \rfloor = t\big]&= \Pr[ t \leq Y < t + 1]\\
-&= 
-\begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta }} - e^{\frac{\epsilon (t + 1)}{\Delta }}) & t < 0
-\end{cases}
-\end{align*}
-
-Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+% \appendix
+
+% \noindent \textbf{Theorem \ref{thm_gamma_smooth}.}
+% \emph{
+% Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
+% whenever $\adj{\dataobs}{\dataobs'}$, 
+% %\begin{equation}
+% %\label{eq_gamma_smooth}
+% $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
+% }
+
+% \begin{proof}
+% of Theorem. \ref{thm_gamma_smooth}.\\
+% For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
+% From Equation (\ref{eq_smooth}), we can get:
+% \[
+% \frac{1}{S(\dataobs)} 
+%  = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
+% \]
+
+% Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:
+
+% \begin{equation*}
+% \begin{split}
+% & \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
+% & = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+% \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
+% \}\\
+% & = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
+% \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
+% \}\\
+% & = \gamma + \frac{1}{S(\dataobs')}
+% \end{split}
+% \end{equation*}
+% Then we can get:
+% $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
+% \end{proof}
+
+% \noindent \textbf{Lemma \ref{lem_loc_opt}.}
+% \emph{
+% \[
+% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
+% \]
+% }
+
+% \begin{proof} of Lemma \ref{lem_loc_opt}.\\
+% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
+% \begin{align*}
+% &\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
+% & = 
+% \begin{cases}
+% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
+% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
+% \end{cases}\\
+% & \leq 
+% \begin{cases}
+% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
+% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
+% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
+% \end{cases}\\
+% &= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
+% \end{align*}
+% The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
+% Hence, we conclude the statement of this lemma.
+% \end{proof}
+
+% \noindent \textbf{ Lemma \ref{lem_hexpmech_privacy}. } 
+% \emph{
+% $\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
+% }
+
+% \begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
+%   By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
+%   For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
+%   \begin{equation*}
+%   \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
+%   \end{equation*}
+%   By definition \ref{def_smoo_2}:
+%   \begin{equation*}
+%   \begin{split}
+%   \hexpmechPr{\dataobs}{z = r} 
+%   & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
+%   & = \frac {\exp\big(
+%   \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
+%   \big)}
+%   {\unomalizer{\dataobs}} \\
+%   & = \frac {\exp\big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+%   \big)}
+%   {\unomalizer{\dataobs}}
+%   \\
+%   & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
+%   \end{split}
+%   \end{equation*}
+%   Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \frac {\exp\big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+%   \big)}
+%   {\unomalizer{\dataobs}}
+%   \cdot \exp\big( \frac{\epsilon}{4} \big) \\
+%   & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
+%   \big)
+%   } 
+%   {\unomalizer{\dataobs}}\\
+%   & \cdot \exp
+%   \big(
+%   \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)\\
+%   & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {\unomalizer{\dataobs}}\\
+%   & \cdot \exp
+%   \big(
+%   \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+%   \big)\\
+%   \end{split}
+%   \end{equation*}
+
+%   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {\unomalizer{\dataobs}}\\
+%   & \cdot \exp
+%   \big(
+%   \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
+%   \big)\\
+%   \end{split}
+%   \end{equation*}
+
+%   Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {\unomalizer{\dataobs}}
+%   \exp
+%   \big(
+%   \frac{\epsilon}{4} \cdot \gamma
+%   \big)\\
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {\unomalizer{\dataobs}}\\
+%   \end{split}
+%   \end{equation*}
+
+%   Doing the same transformation in the denominator:
+%   \begin{equation*}
+%   \begin{split}
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
+%   \big)
+%   }\\
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
+%   & \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+%   \big)
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
+%   \big)
+%   }\\
+%   \end{split}
+%   \end{equation*}
+
+%   Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+%   \big)
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4}
+%   \big)
+%   }\\
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
+%   \big)
+%   }\\
+%   & \cdot 
+%   \frac{1}
+%   {
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
+%   \big)
+%   }\\
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+%   \big)}\\
+%   & \cdot\frac{1}{
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{- \epsilon\cdot(\ux{r'})}{4}
+%   (\frac{1}{S(\dataobs)}
+% -
+%   \frac{1}{S(\dataobs')})
+%   \big)
+%   }
+%   \end{split}
+%   \end{equation*}
+
+%   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+%   \big)}\\
+%   & \cdot \frac{1}{
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{- \epsilon}{4}
+%   (\frac{1}{S(\dataobs)}
+% -
+%   \frac{1}{S(\dataobs')})
+%   \big)
+%   }\\
+%   \end{split}
+%   \end{equation*}
+
+%   Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
+%   $\frac{- \epsilon}{4}
+%   (\frac{1}{S(\dataobs)}-
+%   \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
+%   \begin{equation*}
+%   \begin{split}
+%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+%   \big)
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4}
+%   \big)
+%   \exp
+%   \big(
+%   \frac{- \epsilon}{4} \cdot \gamma
+%   \big)
+%   }\\
+%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \sum_{r'\in \candidateset} 
+%   \exp 
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
+%   \big)
+%   \exp 
+%   \big(
+%   \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
+%   \big)
+%   }\\
+%   & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
+%   \frac {
+%   \exp
+%   \big(
+%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
+%   \big)
+%   } 
+%   {
+%   \unomalizer{\dataobs'}
+%   }\\
+%   & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
+%   \end{split}
+%   \end{equation*}
+
+%   Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
+
+% \end{proof}
+
+% \noindent \textbf{ Lemma \ref{lem_acc_lap}.}
+% \emph{
+% Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
+% \begin{align*}
+% &
+% \lapmechPr{\dataobs}{
+% \begin{aligned}
+% \lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
+% &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+% \end{aligned}
+% }
+% \\
+% &\qquad = 
+% \begin{cases}
+% \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+% \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
+% \end{cases}
+% \end{align*}
+% where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
+% }
+
+% \begin{proof} of Lemma \ref{lem_acc_lap}.\\
+% Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
+% Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta }}$, where $Y \thicksim \lap{0}{\frac{\Delta }{\epsilon}}$ in our setting.
+
+% Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
+% %\[
+% %\Pr\big[\lfloor Y \rfloor = t\big] 
+% %= \Pr[ t \leq Y < t + 1] 
+% %= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+% %\]
+% %when $t \geq 0$, and
+% %\[
+% %\Pr\big[\lfloor Y \rfloor = t\big] 
+% %= \Pr[ t \leq Y < t + 1] 
+% %= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
+% %\]
+% %when $t < 0$.
+% \begin{align*}
+% \Pr\big[\lfloor Y \rfloor = t\big]&= \Pr[ t \leq Y < t + 1]\\
+% &= 
+% \begin{cases}
+% \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+% \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta }} - e^{\frac{\epsilon (t + 1)}{\Delta }}) & t < 0
+% \end{cases}
+% \end{align*}
+
+% Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
 By applying Hellinger distance in our case, we get:
-%$$
-%\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
-%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
-%& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
-%\end{array}
-%$$
-%when $t \geq 0$, and\\
-%$$
-%\begin{array}{rcl}
-%& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
-%= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
-%& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
-%\end{array}
-%$$
-%when $t < 0$.\\
-\begin{align*}
-&
-\Pr\left[
-\begin{aligned}
-\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )}\\ 
-&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
-\end{aligned}
-\right]
-\\
-&\qquad = 
-\begin{cases}
-\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
-\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
-\end{cases}
-\end{align*}
-
-Unfolding the Hellinger distance formula, we get:\\
-  \noindent \textbf{case: t is even}
-  \begin{align*}
-  &\Pr\left[
-\begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2}\\
-&= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
-  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
-  \cdot\prod_{k = 1}^{\frac{t}{2}}
-  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
-\end{aligned}
-\right] \\
-  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
-  \end{align*}
-  \noindent \textbf{case: t is odd}
-  let $t = 2 m + 1$
-  \begin{align*}
-  & \Pr\left[
-  \begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2} \\
-  & =
-  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
-\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
-&\cdot 
-  \prod_{k = 0}^{m-1}
-  \sqrt{(1 + \frac{1}{2(\alpha + k)})
-  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
-  }\\ &\cdot 
-  \prod_{k = 1}^{m} 
-  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
-\right] \\
-   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
-  \end{align*}
-
-\end{proof}
+% %$$
+% %\begin{array}{rcl}
+% %& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
+% %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
+% %& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
+% %\end{array}
+% %$$
+% %when $t \geq 0$, and\\
+% %$$
+% %\begin{array}{rcl}
+% %& \Pr\big[\hellinger(\bysinfer{\dataobs}, r_L ) 
+% %= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
+% %& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
+% %\end{array}
+% %$$
+% %when $t < 0$.\\
+% \begin{align*}
+% &
+% \Pr\left[
+% \begin{aligned}
+% \lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )}\\ 
+% &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
+% \end{aligned}
+% \right]
+% \\
+% &\qquad = 
+% \begin{cases}
+% \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
+% \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
+% \end{cases}
+% \end{align*}
+
+% Unfolding the Hellinger distance formula, we get:\\
+%   \noindent \textbf{case: t is even}
+%   \begin{align*}
+%   &\Pr\left[
+% \begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2}\\
+% &= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
+%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
+%   \cdot\prod_{k = 1}^{\frac{t}{2}}
+%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
+% \end{aligned}
+% \right] \\
+%   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
+%   \end{align*}
+%   \noindent \textbf{case: t is odd}
+%   let $t = 2 m + 1$
+%   \begin{align*}
+%   & \Pr\left[
+%   \begin{aligned}\lefteqn{\hellinger(\bysinfer{\dataobs}, r_L )^2} \\
+%   & =
+%   1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
+% \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
+% &\cdot 
+%   \prod_{k = 0}^{m-1}
+%   \sqrt{(1 + \frac{1}{2(\alpha + k)})
+%   (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
+%   }\\ &\cdot 
+%   \prod_{k = 1}^{m} 
+%   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
+% \right] \\
+%    &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }})
+%   \end{align*}
+
+% \end{proof}
 

### 2019-01-23 ICML2019/main.tex
Finished pass on section 4.

@@
 distribution for the Dirichlet-Multinomial model by output
-perturbation with accuracy measured in Hellinger distance.
-It is worth noticing that the posterior distribution of this model is fully characterized
+perturbation with accuracy measured in Hellinger distance. We assume
+that the prior is given and non-private and we aim at protecting the
+privacy of the observed data.
+It is worth noticing that the posterior distribution of the Dirichlet-Multinomial model is fully characterized
 by its parameters. That is, we are interested in releasing a private version of
@@
 considered KL-divergence between posteriors. 
-In this work we consider instead the Hellinger Distance between
-posteriors. Similarly to KL-divergence, Hellinger Distance is an
+In this work we consider instead the Hellinger distance between
+posteriors. Similarly to KL-divergence, Hellinger distance is an
 $f$-divergence measuring levels of similarities between
-distributions. However, unlikely KL-divergence, Hellinger Distance is a proper
+distributions. However, unlikely KL-divergence, Hellinger distance is a proper
 distance satisfying reflexivity, symmetry and triangle
-inequality. These properties gives Hellinger Distance analytical
+inequality. These properties gives Hellinger distance analytical
 advantages and makes the minimum hellinger distance  an efficient and
@@
 
-attacked this problem by adding independent Laplacian noise to the
-parameters of the posteriors. That is, in the case of the Beta-Binomial system,
-the values released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
-and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
-This mechanism is $\epsilon$-differentially private, and the noise is
-calibrated w.r.t. to a sensitivity of 2 which is derived by using
-$\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
-distributions, characterized by the pairs
-$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
-$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Section \ref{sec_mechs}.\\
-However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
-\[
-  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
-\]
-where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
-However, distance between
-distributions are more naturally  measured by distribution
-metrics such as $f$-divergences, e.g. Hellinger distance, etc., than the $\ell_1$ norm shown above.
-{\color{blue} still not sure this is a good way to put it...}
-This gives us motivation for exploring the design space
-of mechanisms by considering different norms. e.g. a norm over space of measures.
-to compute the sensitivity and provide guarantees on the accuracy.
+% attacked this problem by adding independent Laplacian noise to the
+% parameters of the posteriors. That is, in the case of the Beta-Binomial system,
+% the values released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
+% where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
+% and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
+% This mechanism is $\epsilon$-differentially private, and the noise is
+% calibrated w.r.t. to a sensitivity of 2 which is derived by using
+% $\ell_1$ norm over the pair of parameters. Indeed, considering two
+% adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
+% distributions, characterized by the pairs
+% $(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
+% $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
+% This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Section \ref{sec_mechs}.\\
+% However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
+% \[
+%   \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
+% \]
+% where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
+% However, distance between
+% distributions are more naturally  measured by distribution
+% metrics such as $f$-divergences, e.g. Hellinger distance, etc., than the $\ell_1$ norm shown above.
+% {\color{blue} still not sure this is a good way to put it...}
+% This gives us motivation for exploring the design space
+% of mechanisms by considering different norms. e.g. a norm over space of measures.
+% to compute the sensitivity and provide guarantees on the accuracy.
+
+One of the challenges in working with the Hellinger distance for the
+Dirichlet-multinomial model is that a difference in the parameters of two
+Dirichlet distributions can results in different values  in terms of Hellinger distance
+depending on the value of the parameter
+themselves. The plot in Figure~\ref{fig_sensitivity} illustrates
+this by showing the Hellinger distance between beta distributions
+whose parameters differ by one, for each value of the parameter
+$\alpha$. The reason why this change is relevant
+for differential privacy is that this quantity corresponds to the local
+sensitivity of the function $\hellinger$.
 
@@
 \includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
-\caption{Local sensitivity of $\hellinger$. Data size is 100. $\alpha$ is the number of 1s.}
+\caption{Hellinger distance between the Beta distributions
+  corresponding to two adjacent datasets of size 100
+  when  $\alpha$ (the number of 1s) changes. This quantity corresponds
+  to the local sensitivity of the function $\hellinger$.}
 \label{fig_sensitivity}

### 2019-01-23 ICML2019/main.tex
update section 7

@@
 We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$),
-standard exponential mechanism ($\mathsf{expMech}$),
-non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
+standard exponential mechanism ($\expmech$),
+non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $1-$smooth sensitivity achieving $\epsilon-$dp).
 
@@
 Section (\ref{sec_mechs}) w.r.t. data sizes and dimensions by experimenting on real data sets.
-Every plot is an average over 1000 runs. In all the experiments we set
+Every plot is over 1000 runs. In all following experiments we set
 $\epsilon = 1.0$.
 
-\noindent In the following some of the plots show
-mean error as a function of the datasize while one
-is a whiskers-plot where the y-axis shows the average
-accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
-different balanced priors used. The boxes extend from the lower to the upper quartile values
+\noindent In the following whiskers-plots, the y-axis shows the
+accuracy (or equivalently, the error measured by the Hellinger distance) of the mechanisms, and the x-axis, instead shows
+different data sets we are using. The boxes extend from the lower to the upper quartile values
 of the data, with a line at the median. A notch on the box around the
@@
 We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
-Each data set contains 1 binary variable, which applys our Beta-binomial model.
+Each data set contains 1 binary variable, which applys to our Beta-binomial model.
 By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
 The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
-The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
+The second and third data set are the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
 The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
@@
 We use three real data sets from the same repository repository.
-Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model.
+Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which applys to our 3 dimension Dirichlet-multinomial model.
 By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
-The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
-The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
-The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
+The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions.
+The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the 2 diseases.
 The size of the four data set are $731, 90, 90$.

### 2019-01-23 codes/privacyloss.py

@@ -21,23 +21,34 @@ from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 #########################################################################################################################
 #OBTAIN OUTPUTTING PROBABILITIES OF ONE DATA SET
 #########################################################################################################################	
-def probability_values(datasize,epsilon,delta,prior,observation):
+def probability_values(datasize,epsilon,delta,prior,observation, mech):
 	
 	Bayesian_Model = BayesInferwithDirPrior(prior, datasize, epsilon, delta)
 	Bayesian_Model._set_observation(observation)
 
 	Bayesian_Model._set_candidate_scores()
 	Bayesian_Model._set_local_sensitivities()
-	Bayesian_Model._set_up_exp_mech_with_alpha_SS()
+	if(mech == r'Alg 3 - $\mathsf{EHD}$'):
+		Bayesian_Model._set_up_exp_mech_with_GS()
+	elif(mech == r'Alg 4 - $\mathsf{EHDL}$'):
+		Bayesian_Model._set_up_exp_mech_with_LS()
+	elif(mech == r'Alg 5 - $\mathsf{EHDS}$'):
+		Bayesian_Model._set_up_exp_mech_with_gamma_SS()
 	
 
 	probabilities_exp = {}
 
 	for i in range(len(Bayesian_Model._candidates)):
 		z = Bayesian_Model._candidates[i]
-		probabilities_exp[str(z._alphas)] = Bayesian_Model._alpha_SS_probabilities[i]
+		if(mech == r'Alg 3 - $\mathsf{EHD}$'):
+			probabilities_exp[str(z._alphas)] = Bayesian_Model._GS_probabilities[i]
+		elif(mech == r'Alg 4 - $\mathsf{EHDL}$'):
+			probabilities_exp[str(z._alphas)] = Bayesian_Model._LS_probabilities[i]
+		elif(mech == r'Alg 5 - $\mathsf{EHDS}$'):
+			probabilities_exp[str(z._alphas)] = Bayesian_Model._gamma_SS_probabilities[i]
 	
 	return probabilities_exp
+
 
 #########################################################################################################################
 #OBTAIN DECOMPOSED OUTPUTTING PROBABILITIES OF ONE DATA SET
@@ -62,10 +73,10 @@ def decomposed_probability_values(datasize,epsilon,delta,prior,observation):
 #########################################################################################################################
[…]

### 2019-01-23 ICML2019/main.tex
related works

--- 2019-01-23 ICML2019/main.tex
@@
 with a sample of observed data in order to estimate a new posterior distribution.
+
 %is a standard statistical tool that is useful to
@@
 %%which could be used as a plug and play in PPL citing CCS2016
+
 In this work we consider the design space of  parametric Bayesian
@@
 
-\noindent \textbf{Main contributions.}
-What follows is a summary of the main contributions of this work.
+%\noindent \textbf{Main contributions.}
+In summary, the main contributions of our work are:
 \begin{itemize}
@@
 
-A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
-
-In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference.
-\cite{dimitrakakis2014robust,zhang2016differential,zheng2015differential,wang2015privacy}.
-2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}.
-3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
+% A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.
+
+Several works have considered the intersection of Bayesian Inference and differential
+privacy. \citet{williams2010probabilistic} explored the use of
+probabilistic inference to improve the accuracy of differentially
+private data analyses. A similar approach has been also studied by
+\citet{xiao2012bayesian}.
+
+A general trend has been to study robustness conditions
+for different likelihood functions and different classes of conjugate priors 
+guaranteeing differential privacy for samples taken from a
+posterior distribution. \citet{dimitrakakis2014robust}
+consider this approach and identify some general robustness technique
+which can be applied to several models including the one considered in
+this paper. Similarly, \citet{zheng2015differential} considers a similar approach
+but with different conditions. \citet{zhang2016differential} extend
+the previous approaches to address more general models with multiple
+random variables. 
+\citet{wang2015privacy} identifies
+conditions guaranteeing differential privacy for samples generated
+using standard montecarlo algorithm.
+\citet{GeumlekSC17} consider the problem of releasing samples from
+distributions in the exponential family under the constraints imposed
+by Renyi differential privacy. 
+\citet{Zhang2017privbayes} propose a technique for releasing high
+dimensional data based on the differentially private learning of a
+Bayesian graphical model.
+
+Few works take an approach similar to the one we consider here. 
+\citet{dimitrakakis2015differential} study differentially private
+posterior release by output perturbation based on Laplace noise for the Beta-Binomial
+model. However, they measure accuracy in terms of $\ell_1$
+distance over the parameters and in term of KL-divergence over the distribution.  \citet{foulds2016theory}
+generalizes the approach of \citet{dimitrakakis2015differential} by
+analyzing further the impact that Laplace noise has on the inference.
+They also focus on accuracy measured in term of  $\ell_1$ distance
+over the parameters. \citet{BartheFGAGHS16} study a verification
+method for probabilistic programs including constructs for Bayesian
+inference. In their work they also study an approach based on the use
+of the exponential mechanism with the Hellinger distance as scoring
+function. We show here that their approach achieve very poor utility.
+
+% 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy.
 The third topic where our work focus on is still very new.

### 2019-01-23 ICML2019/main.tex
update section 7

--- 2019-01-23 ICML2019/main.tex
@@
 
+The red box representing the $\expmech$ plays worst in terms of accuracy.
+While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).
+
 \subsection{Privacy Evaluation}
@@
     \includegraphics[width=0.35\textwidth]{privacyloss.eps}
-\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
+\caption{The privacy loss in practice under different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
 \label{fig_privacy}

### 2019-01-23 ICML2019/main.tex
changes to section 5

--- 2019-01-23 ICML2019/main.tex
@@
 \label{sec_mechs}
-In this section we will describe and analyse a series of mechanisms to privately compute and release
+In this section we describe and analyze a variety of mechanisms which privately compute and release
 a posterior distribution.
 Section \ref{sec_ell1_dim} presents a first mechanism, $\lapmech$,
-based on the Laplace primitive where the sensitivity is measured w.r.t. to $\ell_1$ norm.
-Section \ref{sec_ell1_hist}, shows that $\lapmech$'s accuracy can be improved
-by performing a better analysis on the sensitivity of the inference process.
-Section \ref{sec_ehd}, shows an instance of the exponential mechanism, $\expmech$, where the scoring
-function is based on the Hellinger distance, we will see how this mechanisms performs
-poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
-We then proceed to introduce $\lexpmech$, a variation of $\expmech$ which uses a lower bound
-on the global sensitivity called local sensitivity.
-Unfortunately, despite improving on accuracy $\lexpmech$ is non-private.
-Finally, building on $\lexpmech$, we introduce $\hexpmech$:
-which, based on the notion of \emph{smooth} sensitivity, achieves $\epsilon$-differential privacy and
+based on Laplace noise addition calibrated to sensitivity measured with respect to the $\ell_1$ norm.
+In Section \ref{sec_ell1_hist} we observe that the accuracy of $\lapmech$ can be optimized
+through a better analysis of the sensitivity of the inference process.
+Section \ref{sec_ehd} describes an instantiation of the exponential mechanism, $\expmech$, where the scoring
+function is based on the Hellinger distance. We will see that this mechanism performs
+poorly due to the very high global sensitivity of the inference process with respect to this metric.
+We then proceed to introduce $\lexpmech$, a variation of $\expmech$ based on local sensitivity,
+a quantity which is at most the global sensitivity but which can be much lower.
+Unfortunately, $\lexpmech$ by itself is non-private, but its accuracy guarantees serve as a useful benchmark.
+Building on $\lexpmech$, we introduce $\hexpmech$
+which instead relies on the notion of  \emph{smooth} sensitivity. This mechanism is $\epsilon$-differentially private and
 has good accuracy in specific cases.
-In presenting these mechanisms we will denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  $\dirichlet{\valpha'}$
-obtained starting from the prior $\dirichlet{\valpha}$, likelihood $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
+
+When describing these mechanisms, we denote by $\inferd{\valpha}{\vtheta}{\dataobs}$ the posterior  distribution $\dirichlet{\valpha'}$
+obtained from the prior $\dirichlet{\valpha}$, likelihood function $\multinomial{|\dataobs|}{\vtheta}$, and observed data $\dataobs$.
 To minimize notation we will identify the distribution $\dirichlet{\valpha}$ with its vector
 of parameters.
-Two different upper bounds to the value of
+Two different upper bounds on the value of
 \begin{align}
@@
 \end{align}
-will be used to calibrate the noise in the mechanisms based on the Laplacian primitive.
-Finally, with $\bys{\dataobs}{\vtheta}$ we will denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when no confusion can arise.
+will be used to calibrate the noise in the mechanisms based on the Laplace primitive.
+Finally, we use the abbreviation $\bys{\dataobs}{\vtheta}$ to denote $\inferd{\valpha}{\vtheta}{\dataobs}$ when the underlying vector $\valpha$
+is understood.
 
@@
 We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$),
-standard exponential mechanism ($\expmech$),
-non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $1-$smooth sensitivity achieving $\epsilon-$dp).
+standard exponential mechanism ($\mathsf{expMech}$),
+non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
 
@@
 Section (\ref{sec_mechs}) w.r.t. data sizes and dimensions by experimenting on real data sets.
-Every plot is over 1000 runs. In all following experiments we set
+Every plot is an average over 1000 runs. In all the experiments we set
 $\epsilon = 1.0$.
 
-\noindent In the following whiskers-plots, the y-axis shows the
-accuracy (or equivalently, the error measured by the Hellinger distance) of the mechanisms, and the x-axis, instead shows
-different data sets we are using. The boxes extend from the lower to the upper quartile values
+\noindent In the following some of the plots show
+mean error as a function of the datasize while one
+is a whiskers-plot where the y-axis shows the average
+accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
+different balanced priors used. The boxes extend from the lower to the upper quartile values
 of the data, with a line at the median. A notch on the box around the
@@
 We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
-Each data set contains 1 binary variable, which applys to our Beta-binomial model.
+Each data set contains 1 binary variable, which applys our Beta-binomial model.
 By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
 The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
-The second and third data set are the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
+The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
 The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
@@
 We use three real data sets from the same repository repository.
-Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which applys to our 3 dimension Dirichlet-multinomial model.
+Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model.
 By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
-The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions.
-The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the 2 diseases.
+The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
+The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not.
+The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
 The size of the four data set are $731, 90, 90$.
@@
 
-The red box representing the $\expmech$ plays worst in terms of accuracy.
-While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).
-
 \subsection{Privacy Evaluation}
@@
     \includegraphics[width=0.35\textwidth]{privacyloss.eps}
-\caption{The privacy loss in practice under different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
+\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
 \label{fig_privacy}

### 2019-01-23 ICML2019/main.tex
Fix oversize of a formula.
update section 7

--- 2019-01-23 ICML2019/main.tex
@@
 
-\noindent In the following whiskers-plots, the y-axis shows the
-accuracy (or equivalently, the error measured by the Hellinger distance) of the mechanisms, and the x-axis, instead shows
+\noindent In the following whiskery-plots, the y-axis shows the
+accuracy (or equivalently, the error measured by the Hellinger distance) of the mechanisms, and the x-axis shows
 different data sets we are using. The boxes extend from the lower to the upper quartile values
@@
 We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}.
-Each data set contains 1 binary variable, which applys to our Beta-binomial model.
+Each data set contains 1 binary variable, which fits our Beta-binomial model.
 By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
@@
 \paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
-We use three real data sets from the same repository repository.
-Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which applys to our 3 dimension Dirichlet-multinomial model.
+We use three data sets from the same repository repository.
+Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which fits our 3 dimension Dirichlet-multinomial model.
 By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
@@
 While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).
+The purple one representing the $\lexpmech$ although performs better than $\expmech$ and $\hexpmech$, but it is non-private.
 
@@
 \label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_ehds} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
+In order to see our privacy behavior, we study the privacy loss under concrete cases.
+The $\epsilon$ - differential privacy we proved in Sec.
+\ref{sec_mechs} is just an upper bound, the $\epsilon$ in practice might be smaller than upper bound.
+We calculate the actual privacy loss of $\expmech$, $\lexpmech$ and $\hexpmech$ w.r.t.
 the data size, and obtain plots in Fig.
@@
 
-$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected.
+We can observe from Fig.
+\ref{fig_privacy} that the actual privacy loss of $\expmech$ and $\hexpmech$ are smaller than the upper bound.
+That is to say, we achieved a higher privacy level than expected.
 

### 2019-01-23 ICML2019/main.tex

--- 2019-01-23 ICML2019/main.tex
@@
 \[
-  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
+\candidateset{\valpha}=  \left \{(\alpha',\beta') ~\vline~ \begin{aligned} & \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha, \\ & \Delta\alpha={\textstyle \sum x_i}, \dataobs\in \{0,1\}^n \end{aligned} \right\}.
 \]
@@
 
+The red box representing the $\expmech$ plays worst in terms of accuracy.
+While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).
+The purple one representing the $\lexpmech$ although performs better than $\expmech$ and $\hexpmech$, but it is non-private.
+
 \subsection{Privacy Evaluation}
 \label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_ehds} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
+In order to see our privacy behavior, we study the privacy loss under concrete cases.
+The $\epsilon$ - differential privacy we proved in Sec.
+\ref{sec_mechs} is just an upper bound, the $\epsilon$ in practice might be smaller than upper bound.
+We calculate the actual privacy loss of $\expmech$, $\lexpmech$ and $\hexpmech$ w.r.t.
 the data size, and obtain plots in Fig.

### 2019-01-23 ICML2019/main.tex
update section 7

@@
 The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions.
-The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the 2 diseases.
+The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the diseases.
 The size of the four data set are $731, 90, 90$.
@@
 The red box representing the $\expmech$ plays worst in terms of accuracy.
-While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).
+While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to a smooth bound on Hellinger distance (the accuracy metric we are using).
 The purple one representing the $\lexpmech$ although performs better than $\expmech$ and $\hexpmech$, but it is non-private.
@@
 \section{Conclusion}
-From what we have seen in the previous sections we can obtain following conclusions.
+From what we have seen in the previous sections, we can obtain following conclusions.
 We explored the design space of the mechanisms for differentially privacy Bayesian inference, by considering different metrics and different algorithms.
@@
   \item The accuracy can change a lot when considering different metrics and using different sensitivity values.
-  \item Different algorithms have different performance w.r.t.
-different aspect.
-From the experimental results, Laplace mechanism family have a good efficiency and accuracy when using $\ell_1$ norm metric.
-But exponential mechanism family can be a good application when considering different metrics.
+
+  \item Different algorithms have different performance in terms of accuracy and privacy.
+From the experimental results, mechanisms calibrating to $\ell_1$ norm metric have fixed probability of outputting certain candidate when data size changes, while mechanisms calibrating to Hellinger distance have varying probability.
+
+  \item Mechanisms calibrating to global sensitivity has large improve space in terms of accuracy.
+The accuracy of $\expmech$ is improved by applying a smooth bound to the sensitivity of scoring function in $\hexpmech$.
 \end{itemize}

### 2019-01-23 ICML2019/main.tex
tweak

@@
 $\dirichlet{\valpha + \Delta \valpha}$, where $+$ denotes the componentwise sum of vectors.
-In the following we will use the notation $\bysdir(n,\vtheta, \valpha,
+In the following we will use the notation $\bysinfer(\valpha,\vtheta,
 \dataobs)$ to denote the posterior of this process.
@@
 We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
-The idea of $\lapmech$ is to add Laplacian noise with scale proportional to $\mathcal{X}$ to
+The idea of $\lapmech$ is to add Laplacian noise with scale
+proportional to $\mathcal{X}$ (the dimension of the parameter space) to
 the differences between the respective numeric parameters of the prior

### 2019-01-23 ICML2019/main.tex
tweak

@@
 \begin{lem}
-  Algorithm \ref{lapmech} is $\epsilon$-d.p.
+  Algorithm \ref{lapmech} is $\epsilon$-differentially private.
   \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to the value denoted by (\ref{eqn:eq1}). \end{proof}
@@
 \begin{lem}
-  Algorithm \ref{ilapmech} is $\epsilon$-d.p.
+  Algorithm \ref{ilapmech} is $\epsilon$-differentially private.
   \begin{proof} By noticing that 1 and 2 are upper bounds to the value denoted by (\ref{eqn:eq1}), respectively when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
@@
 \begin{lem}
-  Algorithm \ref{mech:expmech1} is $\epsilon$-d.p.
+  Algorithm \ref{mech:expmech1} is $\epsilon$-differentially private.
 \end{lem}
@@
 \begin{thm}
-  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
+  Algorithm \ref{mech:sexpmech} is $\epsilon$-differentially private.
 \end{thm}

### 2019-01-23 ICML2019/main.tex
some more changes to section 5

@@
 \label{sec_ell1_dim}
-We start off by presenting $\lapmech$, in Algorithm \ref{lapmech}, based on the Laplace primitive.
-The idea of $\lapmech$ is to add Laplacian noise with scale
-proportional to $\mathcal{X}$ (the dimension of the parameter space) to
-the differences between the respective numeric parameters of the prior
-and posterior distribution. 
+We first present $\lapmech$, in Algorithm \ref{lapmech}, which is based on the Laplace primitive.
+The idea of $\lapmech$ is to add Laplace noise with scale
+proportional to $|\mathcal{X}|$ (the dimension of the parameter space) to
+the vector of numeric parameters of the posterior distribution.
 \begin{algorithm}
@@
   % \RETURN $a_{k+1}$.
-  \STATE \quad $\tilde{\alpha_{|\mathcal{X}|}} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
+  \STATE \quad $\tilde{\alpha}_{|\mathcal{X}|} = \alpha_{|\mathcal{X}|} + \lfloor n - \sum_{i = 1}^{|\mathcal{X}|-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
   \STATE {\bf return} $\tilde{\valpha}$
@@
   Algorithm \ref{lapmech} is $\epsilon$-differentially private.
-  \begin{proof} By noticing that $\mathcal{X}-1$ is an upper bound to the value denoted by (\ref{eqn:eq1}). \end{proof}
+  \begin{proof} Privacy follows by noticing that $|\mathcal{X}|-1$ is an upper bound on the $\ell_1$ sensitivity denoted by (\ref{eqn:eq1}). \end{proof}
 \end{lem}
@@
 \label{sec_ell1_hist}
-By seeing the parameters of the distributions as histograms, we can give a tighter upper bound to the value denoted by (\ref{eqn:eq1}).
-Indeed a constant will do. Algorithm $\ilapmech$ in Algorithm \ref{ilapmech} takes advantage of this fact. 
-Indeed, when $\mathcal{X}=2$, 1 is an upper bound for the value of (\ref{eqn:eq1}), while when $\mathcal{X}>2$, 2 is.
-In Algorithm \ref{ilapmech} the algorithm $\ilapmech$ is presented.
+By viewing the parameters of a Dirichlet distribution as a histogram, we can give a tighter upper bound on the sensitivity (\ref{eqn:eq1}).
+Indeed a constant suffices independent of the dimension $|\mathcal{X}| - 1$. Algorithm $\ilapmech$ in Algorithm \ref{ilapmech} takes advantage of this fact. 
+Indeed, when $\mathcal{X}=2$ (corresponding to the Beta-Binomial model), we have an upper bound of $1$ (\ref{eqn:eq1}), whereas when $\mathcal{X}>2$, we have an upper bound of $2$.
+In Algorithm \ref{ilapmech} we present the algorithm $\ilapmech$.
 \begin{algorithm}
@@
   Algorithm \ref{ilapmech} is $\epsilon$-differentially private.
-  \begin{proof} By noticing that 1 and 2 are upper bounds to the value denoted by (\ref{eqn:eq1}), respectively when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
+  \begin{proof} This follows immediately from the upper bounds of $1$ and $2$ on the sensitivity (\ref{eqn:eq1}), respectively, when $|\mathcal{X}|=2$ and $|\mathcal{X}|>2$.
   \end{proof}
@@
 
-\subsection{A new family of mechanisms}
+\subsection{Variants of the Exponential Mechanism}
 \label{sec_exp}
-In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
+In this section, we describe a mechanism which we denote by $\expmech$. $\expmech$ is an instantiation
 of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
@@
 The idea is that $\expmech$ will sample and output a distribution with higher probability when
-it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
-distributions as opposed to a metric over the parameters that represent it. In this work we will
+it is closer to the real posterior; importantly,  \emph{closeness} is measured using a metric over probability
+distributions as opposed to a metric over the underlying space of parameters. In this work we will
 use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
 Given a prior distribution $\dirichlet{\valpha}$,
-we define the follwing set  where the mechanism will sample from:
+we define the following set from which the mechanism samples:
 \[
@@
 In general $|\candidateset{\valpha}|=\binom{n + 1}{|\mathcal{X}| - 1}$ when $\valpha\in\mathcal{X}^n$. In the specific case of $|\mathcal{X}|=2$ with $\valpha=(\alpha,\beta)$,
-that is the Beta-Binomial model, the above reduces to:
+i.e., the Beta-Binomial model, the above reduces to:
 \[
-\candidateset{\valpha}=  \left \{(\alpha',\beta') ~\vline~ \begin{aligned} & \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha, \\ & \Delta\alpha={\textstyle \sum x_i}, \dataobs\in \{0,1\}^n \end{aligned} \right\}.
+\candidateset{\valpha}=  \left \{(\alpha',\beta') ~\vline~ \begin{aligned} & \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha, \\ & \Delta\alpha={\textstyle \sum x_i} \text{ for } \dataobs\in \{0,1\}^n \end{aligned} \right\}.
 \]
@@
 $\expmech$'s pseudocode is shown in Algorithm \ref{mech:expmech1}. $\expmech$ is an instance
-of the Exponential mechanism where the scoring function is instantiated with the function: $r\mapsto -\hellinger(\bysinfer{\dataobs}, r)$.
+of the Exponential mechanism where the score is taken to be the function: $r\mapsto -\hellinger(\bysinfer{\dataobs, \valpha}, r)$.
 Given the input $\dataobs\in\mathcal{X}^n$ and a prior $\dirichlet{\valpha}$, the mechanism $\expmech$ outputs an element $r\in\candidateset{\valpha}$ with  probability: 
@@
 Figure \ref{fig_theory} shows that  the accuracy of
-$\expmech$ is poor if compared with the one of $\ilapmech$. This is due to the fact that
-$GS$ is relatively large and hence the variance of the distribution $\expmech$ ends up also being too large. In order to solve this issue we
-will proceed in two steps. We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, will use the local sensitivity to calibrate
-the noise. This is known to be a non private approach, but it will guide us towards new insights.
-We will then proceed to use a smooth bound the local sensitivity to
-calibrate the noise.
+$\expmech$ is poor in comparison to that of $\ilapmech$. This is because
+$GS$ is relatively large and hence the variance of the distribution $\expmech$ is large as well. To resolve this issue we
+will proceed in two steps.
+We will first define, in Algorithm   \ref{mech:lexpmech}, $\lexpmech$, which instead of using the global sensitivity, dampens the score function proportional to the local sensitivity.
+This approach by itself does not guarantee differential privacy, but it suggests new insights and provides a useful benchmark for comparing accuracy.
+We will then proceed to modify this algorithm by using a smooth upper bound on the local sensitivity.
 

### 2019-01-23 ICML2019/main.tex
fix bugs

@@
 \begin{thm}
+\label{thm_hexpmech_privacy}
   Algorithm \ref{mech:sexpmech} is $\epsilon$-differentially private.
@@
 Each data set contains 1 binary variable, which fits our Beta-binomial model.
-By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
+By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to obtain the posterior distribution of these data.
 The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend.
@@
 Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which fits our 3 dimension Dirichlet-multinomial model.
-By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data.
+By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to obtain the posterior distribution of these data.
 The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions.

### 2019-02-25 notes/AccuracyAnalysis/main.tex
rename and update the notes for Lapalce mechanism optimal analysis

--- 2018-09-26 paper/main.tex
@@
 \begin{document}
-\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}
+\title{Accuracy Analysis For Three Mechanisms}
 
-\begin{abstract} Bayesian inference is a statistical method which
-allows one to derive a \emph{posterior} distribution,
-starting from a \emph{prior} distribution and observed data. Several
-approaches have been explored in order to make this process differentially
-private. For example, \citet{dimitrakakis2014robust}, and
-\citet{wang2015privacy} proved that, under specific conditions, sampling from
-the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
-designed differentially private mechanisms that output a
-representation of the full posterior distribution.
-
-When the output of a differentially private mechanism is a probability
-distribution, accuracy is naturally measured by means of
-\emph{probabilistic distances} measuring how far this distribution is
-from the original one. Some classical examples are total variation distance,
-Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
-
-In this work, we design a mechanism for
-bayesian inference exploring the idea of calibrating noise using the
-same probabilistic distance we want to measure accuracy with. 
-We focus on two discrete models, the Beta-Binomial and the
-Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
-Our mechanism can be understood as a version of  the exponential mechanism
-where the noise is calibrated to the smooth sensitivity of the
-utility function, rather than to its global sensitivity. In our
-setting, the utility function is the probability distance we want to
-use to measure accuracy. To show the usefulness of this mechanism we
-show an experimental analysis comparing it with an approach based on
-the Laplace mechanism.
+\begin{abstract} 
 \end{abstract}
 
-% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-% \begin{CCSXML}
-% <ccs2012>
-% <concept>
-% <concept_id>10002978.10003029.10011703</concept_id>
-% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-% <concept_significance>500</concept_significance>
-% </concept>
-% </ccs2012>
-% \end{CCSXML}
-
-% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-% % -- end of section to replace with generated code
-
-\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords
+\keywords{Accuracy analysis} % TODO: replace with your keywords
 
@@
 
-\section{An informal motivation}
+\section{Introduction}
 \label{sec_intro}
-Publishing the posterior distribution inferred from a sensitive dataset can
-leak information about the individuals in the dataset.
-In order to guarantee differential privacy and to protect the
-individuals' data we can add noise to the posterior before releasing it.
-The amount of the noise that we need to  introduced
-depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
-small changes in the data set. 
-Sensitivity can be computed in many different ways based on which metric space
-we consider on the output set of the mechanism. In the literature on private Bayesian
-inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
-respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
-A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
-A re-loved question is that of how to measure accuracy. Again,
-this can be answered in different ways based on the metric imposed on the output space, and yet again
-only in few works in literature (e.g. \cite{zhang2016differential})
-distances between probability measures have been used for these purposes.
-
-The question that this work aims at answering is whether
-an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
-the numeric parameters of the distributions. 
-We will see that in some cases this can happen.
-
-\section{Bayesian Inference Background}
-\label{sec_background}
-Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
-and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
-\[
-  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
-\]
-where the expression $\Pr(\dataobs | \theta)$ denotes the
-\emph{likelihood} of observing $\dataobs$ under a value of
-$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
-a function of $\theta$.
-For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
-Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
-the initial belief on $\theta$, that is, when no data has been observed. In practice though,
-prior distributions and likelihood functions are usually chosen so that the posterior
-belongs to the same \emph{family} of distributions. In this case we say that the prior
-is conjugate to the likelihood function. Use of a conjugate prior
-simplifies calculations and allows for inference to be performed in a
-recursive fashion over the data.
-In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
-Specifically, we will consider the situation where $\theta$ represents
-the parameter --informally called \emph{bias}-- of a Bernoulli
-distributed random variable, and its immediate generalization where
-the parameter $\vtheta$ represents the vector of parameters of a
-categorically distributed random variable.  In the former case, the
-prior distribution over $\theta\in [0,1]$ is going to be a beta
-distribution, $\betad(\alpha, \beta)$, with parameters
-$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
-
-\[
-  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
-\]
-where $\betaf(\cdot,\cdot)$ is the beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
-\[
-  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
-\]
-where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
-From this it can easily be derived that the posterior distribution is:
-\[
-  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
-\]
-In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
-is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
-and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
-\[
-  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
-\]
-where $\mbetaf(\cdot)$ is the generalized beta function.
-The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
-coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
-The likelihood function will be:
-\[
-  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
-\]
-with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
-Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
-\[
-  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
-\]
-where $+$ denotes the componentwise sum of vectors of reals.
-
-\section{The Problem Statement}
-\label{sec:base}
-We are interested in designing a mechanism for privately releasing the full posterior
-distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
-It's worth noticing that the posterior distributions are fully characterized
-by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
-Beta-Binomial model we are interested in releasing a private version of the pair of
-parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
-in the case of the Dirichlet-Multinomial model we are interested in a private version of
-$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
-have already attacked this problem by adding independent Laplacian noise to the
-parameters of the posteriors. That is, in the case of the Beta-Binomial system,
-the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
-where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
-and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
-This mechanism is $\epsilon$-differentially private, and the noise is
-calibrated w.r.t. to a sensitivity of 2 which is derived by using
-$\ell_1$ norm over the pair of parameters. Indeed, considering two
-adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
-$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
-$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
-distributions, characterized by the pairs
-$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
-$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
-This argument extends similarly to the Dirichelet-Multinomial system.
-
-\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
-\[
-  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
-\]
-where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
-In this work we will use a metric based on a different norm to compute the sensitivity
-and provide guarantees on the accuracy. In particular we will consider a metric
-over probability measures and not over the parameters that represent them.
-Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
-Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
-calculations in the case of the probabilistic models considered here
-and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
-an unbounded adversary can have in distingishing two distributions. 
-Given two beta distributions
-$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
-\[
-  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
-  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
-\]
-The same change of metric will be applied to the experimental accuracy guarantees.
 
@@
 
-\subsection{Baseline Approach}
-
-\subsubsection{Laplace Mechanism}
-\label{subsec_lap}
+\subsection{Baseline Approaches}
 
 \subsubsection{Exponential Mechanism}
-\label{subsec_emgs}
 
-% \subsubsection{Mechanism Set up}
-
-Exponential mechanism $\expmech{}{x}$ samples a element from the candidate set $\betaset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
+Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
 \begin{equation*}
-\underset{z \thicksim \expmech{}{x}}{Pr}[z=r] = \frac
-{exp(\frac{\epsilon u(x,r)}{2 GS(x)})}
+\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
+{exp(\frac{\epsilon u(x,r)}{2 GS})}
 {\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
@@
 
-% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$.
-Since $\hlg$ is monotonic, i.e.
-our utility function is monotonic.
-
-% \subsubsection{Security Analysis}
-% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private.
-We denote the $\bysinfer$ with privacy mechanism as $\privinfer$.
-For adjacent data set $||x,y||_1 = 1$:
-% \begin{equation*}
-% \begin{split}
-% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
-% & =\frac
-% {\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
-% {\frac
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
-% & = \left(\frac
-% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
-% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp\left(\frac
-% {\epsilon (u(x,r) - u(y,r))}
-% {2 \Delta_{g}u}
-% \right)
-% \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & \leq
-% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
-% \left(\frac
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
-% \right)\\
-% & = exp(\epsilon).
-% \end{split}
-% \end{equation*}
-
-% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.
-
 \subsubsection{Exponential Mechanism with Local Sensitivity}
@@
 By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private.
-
-\subsubsection{Sliding Property of Exponential Mechanism}
-\begin{lem}
-Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
-calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
-\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
-\begin{equation*}
-\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-\leq
-e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
-\end{equation*}
-
-\end{lem}
-
-\begin{proof}
-
-In what follows, we will use a correspondence between the probability
- $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
- $r\in\betaset$ and the probability 
- $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
- $r\in\betaset$ we have:
-
-$$
-\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
-\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
- \hlg(\bysinfer(x),r)]\Big )
-$$
-
-To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$.
-We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$.
-We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis.
-It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.
-This parameter can be eliminate in both sides in proof.
-
-We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
-\begin{equation*}
-\begin{split}
-LHS 
-  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
-& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
-& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
-\end{split}
-\end{equation*}
-
-By bounding the $\Delta \geq -S(x)$, we can get:
-
-\begin{equation*}
-\begin{split}
-\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
-& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
-&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
-\end{split}
-\end{equation*}
-
-\end{proof}
-
-\subsubsection{Dilation Property of Exponential Mechanism}
-\begin{lem}
-for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
-
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
-\leq
-e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
-\end{equation*}
-where the sensitivity in mechanism is still smooth sensitivity as above.
-\end{lem}
-
-\begin{proof}
-
-The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:
-
-We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.
-
-We first consider $\lambda < 0$.
-In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.
-
-Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$.
-Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$.
-Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$.
-The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$.
-Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\
-
-\textbf{Detail proof:}
-
-	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
-\begin{itemize}
-	\item $\lambda < 0$
-
-		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
-		\begin{equation*}
-		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-		\end{equation*}
-		is always true when $\lambda < 0$
-	\item $\lambda > 0$
-
-Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
-\begin{equation*}
-u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
-\end{equation*}
-By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
-\begin{equation*}
-\begin{split}
-Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
-\end{split}
-\end{equation*}
-
-In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
-\begin{equation*}
-\begin{split}
-Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
-& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
-& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
-\end{split}
-\end{equation*}
-
-When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
-
-\end{itemize}
-
-\end{proof}
-
-\subsubsection{Privacy Analysis}
-\begin{lem}
-\label{lem_hexpmech_privacy}
-$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
-\end{lem}
-
-\begin{proof}
-of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
-\begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
-\end{equation*}
-Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$.
-Then,
-
-\begin{equation*}
-\begin{split}
-2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
-& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
-& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
-& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
-& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
-\end{split}
-\end{equation*}
-
-The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$.
-The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
-
-\end{proof}
 
@@
 
-% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
-% \begin{equation*}
-% \begin{split}
-% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
-% & = \gamma
-% \end{split} 
-% \end{equation*}
-
-\subsection{Exponential Mechanism with Global Sensitivity}
+\subsection{Accuracy Bound for Exponential Mechanism}
 \label{subsec_accuracy_global}
-Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
+The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
 \begin{equation*}
-\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
+Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
+		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
 \end{equation*}
-where $|R|$ is the size of the candidate set.
-Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$
+where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal results.
 
@@
 
-Within the three accuracy bounds, we will mainly use the first one in following analysis.
+Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:
+
+\begin{equation*}
+\begin{split}
+Pr[u(\hexpmech(x)) \leq c] 
+& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
+\end{split}
+\end{equation*}
+
+which has been used in the dilation property proof.
 
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.48\textwidth]{efficiency}
-\label{fig_efficiency}
-\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
-\end{figure}
-
-\section{Experimental Evaluations}
-\label{sec_experiment}
-
-\subsection{Computation Efficiency}
-\label{subsec_effi}
-The formula for computing the local sensitivity presented in Sec.
-\ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property.
-i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$.
-We also have some experiments for validating our proposal as in Fig.
-\ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$.
-It is shown that maximum value taken when  $r = \bysinfer(x)$.
-
-\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
-\label{subsec_vs_variables}
-In this section, we evaluate the accuracy of the mechanisms defined in
-Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
-data variance, prior distribution, and some combinations thereof.
-Every plot is an average over 1000 runs. In all the experiments we set
-$\epsilon = 0.8$, and $\delta = 10^{-8}$.
-
-\noindent In the following some of the plots show
-mean error as a function of the datasize while one
-is a whiskers-plot where the y-axis shows the average
-accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
-different balanced priors used. The boxes extend from the lower to the upper quartile values
-of the data, with a line at the median. A notch on the box around the
-median is also drawn to give a rough guide to the significance of
-difference of medians; The whiskers extend from the box to show the
-range of the data. A blue box in the plots represents our newly
-designed exponential mechanism's behavior-- where the sensitivity is calibrated
-w.r.t Hellinger distance-- while the yellow box next to
-it represents the performance of a variation of the basic Laplace
-mechanism presented in Section (\ref{sec:base}) with the same
-settings: that is $\epsilon, \delta$, data, prior. The variation
-considered performs a postprocessing on the released parameters so
-that they are consistent. For instance when the sum of the noised
-parameters is greater than $n$ we will truncate them so that they sum
-up to $n$.
-
-\paragraph{Increasing data size with balanced datasets}
-\label{subsubsec_vs_datasize}
-
-\begin{figure}[H]
-\begin{center}
-\centering
-  \subfigure[Data set size from $300$ to $800$ ]{
-    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
-    \label{subsubsec_vs_datasize1a}
-  }
-  \subfigure[Data set size from $14000$ to $20000$]{
-    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
-  \label{subsubsec_vs_datasize1b}} 
-\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize}
-\end{center}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{center}
-\centering
-  % \subfigure[Data set size from $300$ to $800$ ]{
-  %   \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
-  %   \label{subsubsec_vs_datasize1adir}
-  % }
-  \subfigure[Data set size from $14000$ to $20000$]{
-     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
-  \label{subsubsec_vs_datasize1bdir}
-  } 
-\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
-\label{fig_vs_datasize_dir}
-\end{center}
-\end{figure}
-
-In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
-of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
-and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
-Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
-the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
-The results show that when the data size
-increases, the average errors of
-$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
-i.e with size less 650 in the case of Beta-Binomial systems,
-the Laplace mechanisms outperforms the exponential mechanisms,
-but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
-we considered data sets of the order of 15 thousands elements,
-the exponential mechanisms outperforms the Laplace mechanism.
-Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
-but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
-too high run time of the algorithm.
-
-\paragraph{Fixed dataset varying balanced priors}
-\label{subsubsec_vs_prior}
-In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
-We also considered balanced priors with increasing values in their dimensions.
-The plot shows that in the beginning the Laplace mechanism performs better but
-it is outperformed after a while.
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
-\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
-\label{fig_vs_prior}
-\end{figure}
-
-\subsection{Experiment Evaluations on Privacy}
-\label{subsec_experiment_privacy}
-In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section.
-The $(\epsilon, \delta)$ - differential privacy we proved in Sec.
-\ref{sec_smoo} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism.
-We calculate the concrete privacy value in following ways wrt.
-the data size, and obtain plots in Fig.
-\ref{fig_privacy}.
-
-\begin{figure*}
-\begin{center}
-\centering
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20.eps}}
-  \subfigure[data size range from 90 to 180]{
-    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20(2).eps}} 
-\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
-\label{fig_privacy}
-\end{center}
-\end{figure*}
-
-$\epsilon = 0.8$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound.
-That is to say, we achieved a higher privacy level than expected.
-In next step, we are going to improve the accuracy using this property.
-
 \bibliographystyle{ACM-Reference-Format}

### 2019-02-25 codes/Lapopt.py

@@ -139,6 +139,7 @@ def get_ratio(datasizes, prior, epsilon, times):
 	r_post = []
 
 	for n in datasizes:
+		print n
 
 		meanerror, _ = mean_error_fix_n(n, prior, epsilon, times, "lap")
 
@@ -234,15 +235,15 @@ def gen_gammas(r, step, scale):
 if __name__ == "__main__":
 
 	datasize = 500
-	epsilon = 0.3
+	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
 	dataset = [50,50]
-	datasizes = gen_datasizes((50, 1000), 50)
+	datasizes = gen_datasizes((50, 2000), 50)
 
 	#get_separatevalue(datasize, prior, epsilon, 500)
 
-	get_ratio(datasizes, prior, epsilon, 10000)
+	get_ratio(datasizes, prior, epsilon, 5000)
 
 
 

### 2019-02-25 codes/Laplace_CDF.py
update the accuracy analysis for laplace mechanism

@@ -1,0 +1,19 @@
+import math
+
+
+
+def LAPLACE_CDF(interval, scale):
+	if interval[0] >= 0.0:
+		return (1 - 0.5 * math.exp( (-interval[1]*1.0/scale))) - (1 - 0.5 * math.exp( (-interval[0]/scale)))
+	else:
+		return (0.5 * math.exp( (interval[1]*1.0/scale))) - (0.5 * math.exp( (interval[0]/scale)))
+
+
+if __name__ == "__main__":
+	print (0.5 * (LAPLACE_CDF((1,2), 1.0)) + 0.5 * (LAPLACE_CDF((-1,0), 1.0)))
+
+
+
+
+	
+

### 2019-02-26 codes/Laplace_CDF.py
update the accuracy analysis for Laplace mechanism

@@ -10,7 +10,10 @@ def LAPLACE_CDF(interval, scale):
 
 
 if __name__ == "__main__":
-	print (0.5 * (LAPLACE_CDF((1,2), 1.0)) + 0.5 * (LAPLACE_CDF((-1,0), 1.0)))
+	print (0.5 * ( 0.5 - LAPLACE_CDF((0,2), 1.0) ) + 0.5 * (0.5 - LAPLACE_CDF((-1,0), 1.0)))
+	print ((LAPLACE_CDF((0,1), 1.0)))
+	
+	print (0.341969860293 + 0.316060279414 + 0.341969860293)
 
 
 

### 2019-02-26 codes/dirichlet.py

@@ -154,5 +154,3 @@ class dirichlet(object):
 		return LS
 
 
-# print "yes" if (opt_hellinger(dirichlet([20, 22, 21]),dirichlet([21, 21, 21]))) == (opt_hellinger(dirichlet([20, 21, 22]),dirichlet([21, 21, 21]))) else "no"
-

### 2019-03-22 codes/Laplace_CDF.py
update the proof

@@ -10,8 +10,8 @@ def LAPLACE_CDF(interval, scale):
 
 
 if __name__ == "__main__":
-	print (0.5 * ( 0.5 - LAPLACE_CDF((0,2), 1.0) ) + 0.5 * (0.5 - LAPLACE_CDF((-1,0), 1.0)))
-	print ((LAPLACE_CDF((0,1), 1.0)))
+	print (0.5 * (0.5 - LAPLACE_CDF((0,2), 1.0) ) + 0.5 * (0.5 - LAPLACE_CDF((-1,0), 1.0)))
+	print (0.5 * (0.5 - LAPLACE_CDF((0,1), 1.0))) + 0.25
 	
 	print (0.341969860293 + 0.316060279414 + 0.341969860293)
 

### 2019-03-22 codes/dirichlet.py

@@ -153,4 +153,4 @@ class dirichlet(object):
 			temp[i] -= 1
 		return LS
 
-
+print opt_hellinger(dirichlet([4,2]), dirichlet([5,1]))

### 2019-04-05 codes/Lapopt.py
update the theory prob of laplace mecahism and exp mechanism

@@ -22,29 +22,46 @@ def LAPLACE_CDF(interval, scale):
 		return (0.5 * math.exp( (interval[1]*1.0/scale))) - (0.5 * math.exp( (interval[0]/scale)))
 
 
+def lap_distribution_over_candidates(dataobs, prior, eps):
+	lap_prob = {}
+
+	n = sum(dataobs)
+
+	k = dataobs[0]
+
+	candidates = []
+	sensitivity = 1.0
+
+	############### the expected error when the noises are valid######
+	for t in range(- k, n - k + 1):
+		c = dirichlet([k + t, n - k - t])
+		candidates.append(c)
+		lap_prob[c] = 0.5 * LAPLACE_CDF((t, t+1), sensitivity/eps) + 0.5 * LAPLACE_CDF((-t, -t + 1), sensitivity/eps)
+
+	############### the expected error when the noises are not valid######
+	lap_prob[candidates[0]] += 0.5 * (0.5 - LAPLACE_CDF((- k, 0.0), sensitivity/eps)) +  0.5 * (0.5 - LAPLACE_CDF((0.0, k + 1), sensitivity/eps))
+
+	lap_prob[candidates[n]] += 0.5 * (0.5 - LAPLACE_CDF((0.0, n - k + 1), sensitivity/eps)) + 0.5 * (0.5 - LAPLACE_CDF((-(n - k), 0.0), sensitivity/eps))
+	
+	############### the expected error when the noises are not valid######
+	for c,prob in lap_prob.items():
+		print c._alphas, prob
+	return lap_prob
+
+
 def expect_error_Lap(post, prior, eps):
 	expect = 0.0
 
 	n = post._alphas[0] + post._alphas[1] - prior._alphas[0] - prior._alphas[1]
 
 	k = post._alphas[0] - prior._alphas[0]
-	############### the expected error when the noises are valid######
-	for t in range(- k, n - k):
-		expect += 0.5 * LAPLACE_CDF((t, t+1), 1.0/eps) * ((dirichlet([k + t, n - k - t]) + prior) - post) 
 
-	############### the expected error when the noises are not valid######
-	expect += 0.5 * (0.5 - LAPLACE_CDF((-k, 0.0), 1.0/eps)) * ((dirichlet([0, n])+ prior) - post)
-
[…]

### 2019-04-05 codes/dirichlet.py

@@ -102,6 +102,9 @@ class dirichlet(object):
 		self._alphas = list(numpy.array(self._alphas) - numpy.array(other._alphas))
 		return self
 
+	def _pointwise_sub(self, other):
+		return dirichlet(list(numpy.array(self._alphas) - numpy.array(other._alphas)))
+
 	def __add__(self, other):
 		return dirichlet(list(numpy.array(self._alphas) + numpy.array(other._alphas)))
 

### 2019-04-05 codes/privacyloss.py

@@ -60,13 +60,13 @@ def decomposed_probability_values(datasize,epsilon,delta,prior,observation):
 
 	Bayesian_Model._set_candidate_scores()
 	Bayesian_Model._set_local_sensitivities()
-	nomalizer = Bayesian_Model._set_up_exp_mech_with_alpha_SS()
+	nomalizer = Bayesian_Model._set_up_exp_mech_with_gamma_SS()
 	
 	probabilities_exp = {}
 
 	for i in range(len(Bayesian_Model._candidates)):
 		z = Bayesian_Model._candidates[i]
-		probabilities_exp[str(z._alphas)] = nomalizer * Bayesian_Model._alpha_SS_probabilities[i]
+		probabilities_exp[str(z._alphas)] = nomalizer * Bayesian_Model._gamma_SS_probabilities[i]
 	
 	return nomalizer, probabilities_exp
 

### 2019-04-05 codes/prob_by_bin.py

@@ -60,15 +60,15 @@ def calculate_prob_exp(bins, Bayesian_Model, mechanism_parameter, sensitivity, s
 	#SORT AND SPLIT THE PROBABILITY FROM PAIRS #WRITE DATAS INTO FILE
 	#############################################################################
 
-	f_exp = open("datas/discrete_prob/data_" + str(Bayesian_Model._observation_counts) + savename, "w")
+	# f_exp = open("datas/discrete_prob/data_" + str(Bayesian_Model._observation_counts) + savename, "w")
 
-	f_exp.write("Candidates_of_the_same_steps&Hellinger Distance&Probabilities \n")
+	# f_exp.write("Candidates_of_the_same_steps&Hellinger Distance&Probabilities \n")
 
-	for triple in probability_distance_pairs_in_exp:
-		#WRITE DATAS INTO FILE
-		f_exp.write(str(triple[2]) + "&" + str(triple[0]) + "&" + str(triple[1]) + "\n")
+	# for triple in probability_distance_pairs_in_exp:
+	# 	#WRITE DATAS INTO FILE
+	# 	f_exp.write(str(triple[2]) + "&" + str(triple[0]) + "&" + str(triple[1]) + "\n")
 	
-	f_exp.close()
+	# f_exp.close()
 
 
 	t, exp, _ = zip(*probability_distance_pairs_in_exp)
@@ -85,9 +85,9 @@ def calculate_prob_lap(bins, Bayesian_Model, sensitivity, savename):
 	#SENSITIVITY SETTING
 	#############################################################################
 	
-	f_lap = open("datas/discrete_prob/data_" + str(Bayesian_Model._observation_counts) + savename, "w")
+	# f_lap = open("datas/discrete_prob/data_" + str(Bayesian_Model._observation_counts) + savename, "w")
 	
-	f_lap.write("Candidates_of_the_same_steps, Hellinger Distance, Probabilities \n")
+	# f_lap.write("Candidates_of_the_same_steps, Hellinger Distance, Probabilities \n")
 
 	
 	#############################################################################
@@ -117,9 +117,9 @@ def calculate_prob_lap(bins, Bayesian_Model, sensitivity, savename):
 	for i in range(len(probability_distance_pairs_in_lap)):
 		e = probability_distance_pairs_in_lap[i]
 
-		f_lap.write(str(e[2]) + "&" + str(e[0]) +"&" + str(e[1]) + "\n")
[…]

### 2019-04-05 codes/theory_prob.py

@@ -1,0 +1,81 @@
+import numpy
+import matplotlib.pyplot as plt
+from copy import deepcopy
+import random
+import math
+import scipy
+from scipy.stats import beta
+from fractions import Fraction
+import operator
+import time
+from matplotlib.patches import Polygon
+import statistics
+from decimal import *
+from scipy.special import gammaln
+from dirichlet import dirichlet
+from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
+
+def LAPLACE_CDF(interval, scale):
+	if interval[0] >= 0.0:
+		return (1 - 0.5 * math.exp( (-interval[1]*1.0/scale))) - (1 - 0.5 * math.exp( (-interval[0]/scale)))
+	else:
+		return (0.5 * math.exp( (interval[1]*1.0/scale))) - (0.5 * math.exp( (interval[0]/scale)))
+
+
+def lap_distribution_over_candidates(dataobs, prior, eps):
+	lap_prob = {}
+
+	n = sum(dataobs)
+
+	k = dataobs[0]
+
+	candidates = []
+	sensitivity = 1.0
+
+	############### the expected error when the noises are valid######
+	for t in range(- k, n - k + 1):
+		c = dirichlet([k + t, n - k - t])
+		candidates.append(c)
+		lap_prob[c] = 0.5 * LAPLACE_CDF((t, t+1), sensitivity/eps) + 0.5 * LAPLACE_CDF((-t, -t + 1), sensitivity/eps)
+
+	############### the expected error when the noises are not valid######
+	lap_prob[candidates[0]] += 0.5 * (0.5 - LAPLACE_CDF((- k, 0.0), sensitivity/eps)) +  0.5 * (0.5 - LAPLACE_CDF((0.0, k + 1), sensitivity/eps))
+
+	lap_prob[candidates[n]] += 0.5 * (0.5 - LAPLACE_CDF((0.0, n - k + 1), sensitivity/eps)) + 0.5 * (0.5 - LAPLACE_CDF((-(n - k), 0.0), sensitivity/eps))
+	
+	############### the expected error when the noises are not valid######
+	for c,prob in lap_prob.items():
+		print c._alphas, prob
+	return lap_prob
+
+def exp_distribution_over_candidates(dataobs, prior, epsilon):
+	n = sum(dataobs)
+	Bayesian_Model = BayesInferwithDirPrior(prior, n, epsilon)
[…]

### 2019-04-05 codes/theory_prob.py
update Laplace mechanism accuracy analysis

@@ -22,30 +22,29 @@ def LAPLACE_CDF(interval, scale):
 		return (0.5 * math.exp( (interval[1]*1.0/scale))) - (0.5 * math.exp( (interval[0]/scale)))
 
 
-def lap_distribution_over_candidates(dataobs, prior, eps):
+def lap_distribution_over_candidates(dataobs, prior, eps, sensitivity = 1.0):
 	lap_prob = {}
 
 	n = sum(dataobs)
 
 	k = dataobs[0]
 
-	candidates = []
-	sensitivity = 1.0
+	
 
 	############### the expected error when the noises are valid######
 	for t in range(- k, n - k + 1):
-		c = dirichlet([k + t, n - k - t])
-		candidates.append(c)
-		lap_prob[c] = 0.5 * LAPLACE_CDF((t, t+1), sensitivity/eps) + 0.5 * LAPLACE_CDF((-t, -t + 1), sensitivity/eps)
+		c = [k + t, n - k - t]
+		lap_prob[str(c)] = 0.5 * LAPLACE_CDF((t, t+1), sensitivity/eps) + 0.5 * LAPLACE_CDF((-t, -t + 1), sensitivity/eps)
 
 	############### the expected error when the noises are not valid######
-	lap_prob[candidates[0]] += 0.5 * (0.5 - LAPLACE_CDF((- k, 0.0), sensitivity/eps)) +  0.5 * (0.5 - LAPLACE_CDF((0.0, k + 1), sensitivity/eps))
+	lap_prob[str([0,n])] += 0.5 * (0.5 - LAPLACE_CDF((- k, 0.0), sensitivity/eps)) +  0.5 * (0.5 - LAPLACE_CDF((0.0, k + 1), sensitivity/eps))
 
-	lap_prob[candidates[n]] += 0.5 * (0.5 - LAPLACE_CDF((0.0, n - k + 1), sensitivity/eps)) + 0.5 * (0.5 - LAPLACE_CDF((-(n - k), 0.0), sensitivity/eps))
+	lap_prob[str([n,0])] += 0.5 * (0.5 - LAPLACE_CDF((0.0, n - k + 1), sensitivity/eps)) + 0.5 * (0.5 - LAPLACE_CDF((-(n - k), 0.0), sensitivity/eps))
 	
 	############### the expected error when the noises are not valid######
-	for c,prob in lap_prob.items():
-		print c._alphas, prob
+
+	print lap_prob
+
 	return lap_prob
 
[…]

### 2019-04-05 codes/theory_prob.py
update the theory probability of lapmech and expmech with data size 3 and 4 and epsilon 1.0

@@ -121,10 +121,10 @@ def gen_priors(r, step, d):
 if __name__ == "__main__":
 
 	datasize = 50
-	epsilon = 0.1
+	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
-	dataobs = [2,0]
+	dataobs = [4,0]
 	datasizes = gen_datasizes((50, 2000), 50)
 
 	lap_prob = lap_distribution_over_candidates(dataobs, prior, epsilon, 1.0)

### 2020-03-06 codes/dpbayesinfer_Betabinomial.py
update v 2020

@@ -208,6 +208,8 @@ class BayesInferwithDirPrior(object):
 		
 		self._LS = self._posterior._hellinger_sensitivity()
 
+		self._LS = dirichlet([sum(self._posterior._alphas)/2, sum(self._posterior._alphas)/2])._hellinger_sensitivity()
+
 		
 		nomalizer = 0.0
 		for r in self._candidates:
@@ -319,7 +321,7 @@ class BayesInferwithDirPrior(object):
 
 		self._set_up_baseline_lap_mech()
 		self._set_up_improved_lap_mech()
-		# self._set_up_exp_mech_with_SS()
+		self._set_up_exp_mech_with_SS()
 		self._set_up_exp_mech_with_gamma_SS()
 		self._set_up_exp_mech_with_GS()
 		self._set_up_exp_mech_with_LS()
@@ -349,26 +351,26 @@ class BayesInferwithDirPrior(object):
 			#############################################################################
 			#SAMPLING WITH THE EXPONENTIAL MECHANISM OF SMOOTH SENSITIVITY
 			#############################################################################
-			# self._exponentialize_SS()
-			# self._accuracy[self._keys[2]].append(self._posterior - self._exponential_posterior)
-
-			#############################################################################
-			#SAMPLING WITH THE EXPONENTIAL MECHANISM OF ALPHA SMOOTH SENSITIVITY
-			# #############################################################################
-			self._exponentialize_gamma_SS()
+			self._exponentialize_SS()
 			self._accuracy[self._keys[2]].append(self._posterior - self._exponential_posterior)
 
 			#############################################################################
 			#SAMPLING WITH THE EXPONENTIAL MECHANISM OF ALPHA SMOOTH SENSITIVITY
 			# #############################################################################
-			self._exponentialize()
+			self._exponentialize_gamma_SS()
 			self._accuracy[self._keys[3]].append(self._posterior - self._exponential_posterior)
+
+			#############################################################################
+			#SAMPLING WITH THE EXPONENTIAL MECHANISM OF ALPHA SMOOTH SENSITIVITY
+			# #############################################################################
+			self._exponentialize()
+			self._accuracy[self._keys[4]].append(self._posterior - self._exponential_posterior)
 			
 			#############################################################################
 			#SAMPLING WITH THE EXPONENTIAL MECHANISM OF ALPHA SMOOTH SENSITIVITY
 			# #############################################################################
 			self._exponentialize_LS()
[…]

### 2020-03-06 codes/sampling_on_betabinomial_bayesinfer.py

@@ -76,7 +76,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
 		Bayesian_Model._set_observation(observation)
 		print("start" + str(observation))
-		Bayesian_Model._experiments(5000)
+		Bayesian_Model._experiments(500)
 		print("finished" + str(observation))
 
 		for i in range(len(mean_error)):
@@ -245,7 +245,7 @@ if __name__ == "__main__":
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS
 #############################################################################
 	epsilons = numpy.arange(5, 2, 0.1)
-	datasizes = gen_datasizes((2000,5000),500)# + gen_datasizes((150,500),50) + gen_datasizes((600,1000),100)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = gen_datasizes((100,500),50) + gen_datasizes((600,1000),100)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.5,0.5]
 	datasets = gen_datasets(percentage, datasizes)
 	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2)# + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)

### 2020-03-06 codes/theory_prob.py

@@ -124,8 +124,8 @@ if __name__ == "__main__":
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
-	dataobs = [4,0]
-	datasizes = gen_datasizes((50, 2000), 50)
+	dataobs = [10,10]
+	# datasizes = gen_datasizes((50, 200), 50)
 
 	lap_prob = lap_distribution_over_candidates(dataobs, prior, epsilon, 1.0)
 	lap_prob_2 = lap_distribution_over_candidates(dataobs, prior, epsilon, 2.0)

### 2020-03-10 ICML2019/main.tex
update the theory prob of laplace mecahism and exp mechanism
update v 2020
prelimilary

@@
 accuracy and sensitivity in terms of a single metric on probability distributions can yield improved accuracy. 
-{\color{red}{MB: Is this accurate? Would we ever want to use different metrics for accuracy and sensitivity?}}
+% {\color{red}{MB: Is this accurate? Would we ever want to use different metrics for accuracy and sensitivity?}}
 
@@
 $\dirichlet{\valpha + \Delta \valpha}$, where $+$ denotes the componentwise sum of vectors.
-In the following we will use the notation $\bysinfer(\valpha,\vtheta,
-\dataobs)$ to denote the posterior of this process.
+In the following we will use the notation $\bysinfer{\valpha,\vtheta,
+\dataobs}$ to denote the posterior of this process.
 %i.e., $\bysdir(n,\vtheta, \valpha, \dataobs)=\dirichlet{\valpha + \Delta \valpha}$.
@@
 \]
-where $S(\dataobs)$ is the 1-smooth sensitivity of  the function $\hellinger(\bysinfer{\dataobs},\cdot)$. {\color{red}{why do we choose 1???}}
+where $S(\dataobs)$ is the 1-smooth sensitivity of  the function $\hellinger(\bysinfer{\dataobs},\cdot)$. 
+% {\color{red}{why do we choose 1???}}
   \begin{algorithm}
@@
   \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(t)  } }\\ 
-  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
+  &  = \frac{\exp{(\frac{- \epsilon c(t)}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
 %  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).

### 2020-03-12 codes/dpbayesinfer_Betabinomial.py
update accuracy and theory experiments

@@ -78,7 +78,7 @@ class BayesInferwithDirPrior(object):
 
 	def _set_candidate_scores(self):
 		start = time.clock()
-		self._set_candidates([], numpy.sum(self._observation))
+		self._set_candidates([], self._sample_size)
 
 		for r in self._candidates:
 			self._candidate_scores[r] = -(self._posterior - r)

### 2020-03-12 codes/prob_by_bin.py

@@ -26,54 +26,99 @@ def LAPLACE_CDF(interval, scale):
 #############################################################################
 #SUM UP the prob within the same bin
 #############################################################################
+def exp_distribution_over_candidates(dataobs, prior, epsilon, mech):
+	n = sum(dataobs)
+	Bayesian_Model = BayesInferwithDirPrior(prior, n, epsilon)
+	Bayesian_Model._set_observation(dataobs)
 
-def calculate_prob_exp(bins, Bayesian_Model, mechanism_parameter, sensitivity, savename):
+	Bayesian_Model._set_candidate_scores()
+	Bayesian_Model._set_local_sensitivities()
+	if mech == "exp":
 
-	#############################################################################
-	#CALCULATING THE UNOMARLIZED PROBABILITY OF EACH BIN
-	#############################################################################
+		Bayesian_Model._set_up_exp_mech_with_GS()
+	elif mech == "gamma":
+		Bayesian_Model._set_up_exp_mech_with_gamma_SS()
+	else:
+		Bayesian_Model._set_up_exp_mech_with_LS()
 
-	probability_distance_pairs_in_exp =[]
+	exp_prob = {}
 
-	nomalizer = 0.0
+	for i in range(len(Bayesian_Model._candidates)):
+		z = Bayesian_Model._candidates[i]._pointwise_sub(prior)
+		if mech == "exp":
+			exp_prob[str(z._alphas)] = Bayesian_Model._GS_probabilities[i]
+		elif mech == "gamma":
+			exp_prob[str(z._alphas)] = Bayesian_Model._gamma_SS_probabilities[i]
+		else:
+			exp_prob[str(z._alphas)] = Bayesian_Model._LS_probabilities[i]
 
-	for key,item in bins.items():
-		distance = -Bayesian_Model._candidate_scores[item[0]]
+
 		
-		#THE PROBABILITY OF THIS BIN
-		prob = (len(item) * math.exp(Bayesian_Model._epsilon * Bayesian_Model._candidate_scores[item[0]]/(mechanism_parameter * sensitivity)))
-
-		probability_distance_pairs_in_exp.append((distance, prob, [i._alphas for i in item]))
-
-		nomalizer += prob
-
-	#############################################################################
-	#NOMARLIZING PROBABILITY
-	#############################################################################
-
-	probability_distance_pairs_in_exp = [(t[0],t[1]/nomalizer,t[2]) for t in probability_distance_pairs_in_exp]
-
-
[…]

### 2020-03-12 codes/theory_prob.py

@@ -15,6 +15,10 @@ from scipy.special import gammaln
 from dirichlet import dirichlet
 from dpbayesinfer_Betabinomial import BayesInferwithDirPrior
 
+
+# class TheoryProbs(object):
+# 	def __init__(self, dataobs, prior, eps):
+		
 def LAPLACE_CDF(interval, scale):
 	if interval[0] >= 0.0:
 		return (1 - 0.5 * math.exp( (-interval[1]*1.0/scale))) - (1 - 0.5 * math.exp( (-interval[0]/scale)))
@@ -41,28 +45,35 @@ def lap_distribution_over_candidates(dataobs, prior, eps, sensitivity = 1.0):
 
 	lap_prob[str([n,0])] += 0.5 * (0.5 - LAPLACE_CDF((0.0, n - k + 1), sensitivity/eps)) + 0.5 * (0.5 - LAPLACE_CDF((-(n - k), 0.0), sensitivity/eps))
 	
-	############### the expected error when the noises are not valid######
 
-	print lap_prob
+	print sensitivity, lap_prob
 
 	return lap_prob
 
-def exp_distribution_over_candidates(dataobs, prior, epsilon):
+def exp_distribution_over_candidates(dataobs, prior, epsilon, mech):
 	n = sum(dataobs)
 	Bayesian_Model = BayesInferwithDirPrior(prior, n, epsilon)
 	Bayesian_Model._set_observation(dataobs)
 
 	Bayesian_Model._set_candidate_scores()
 	Bayesian_Model._set_local_sensitivities()
-	Bayesian_Model._set_up_exp_mech_with_gamma_SS()
+	if mech == "exp":
+
+		Bayesian_Model._set_up_exp_mech_with_GS()
+	elif mech == "gamma":
+		Bayesian_Model._set_up_exp_mech_with_gamma_SS()
 
 	exp_prob = {}
 
 	for i in range(len(Bayesian_Model._candidates)):
 		z = Bayesian_Model._candidates[i]._pointwise_sub(prior)
-		exp_prob[str(z._alphas)] = Bayesian_Model._gamma_SS_probabilities[i]
-	
-	print exp_prob
+		if mech == "exp":
+			exp_prob[str(z._alphas)] = Bayesian_Model._GS_probabilities[i]
+		elif mech == "gamma":
[…]

### 2020-03-17 codes/dpbayesinfer_Betabinomial.py
update notes

@@ -259,14 +259,10 @@ class BayesInferwithDirPrior(object):
 
 	def _laplace_mechanism(self, sensitivity):
 		noised = [i + math.floor(numpy.random.laplace(0, sensitivity/self._epsilon)) for i in self._observation_counts]
-		noised = [self._sample_size if i > self._sample_size else i for i in noised]
-		noised = [0.0 if i < 0.0 else i for i in noised]
-		if self._sample_size - sum(noised[:-1]) < 0:
-			noised[-1] = 0
-		elif self._sample_size - sum(noised[:-1]) > self._sample_size:
-			noised[-1] = self._sample_size
-		else:
-			noised[-1] = self._sample_size - sum(noised[:-1]) 
+		noised = [self._sample_size if i > self._sample_size else 0.0 if i < 0.0 else i for i in noised]
+		r = self._sample_size - sum(noised[:-1])
+		noised[-1] = 0.0 if r < 0.0 else self._sample_size if r > self._sample_size else r
+
 		self._laplaced_posterior = dirichlet(noised) + self._prior
 
 

### 2020-03-19 codes/dpbayesinfer_Betabinomial.py
update smooth sensitivity

@@ -152,8 +152,9 @@ class BayesInferwithDirPrior(object):
 		#CALCULATING THE OUTPUTTING PROBABILITIES
 		###################################################################################################################################
 		nomalizer = 0.0
+		eps = self._epsilon/(0.5 + 0.5 * self._gamma)
 		for r in self._candidates:
-			temp = math.exp(self._epsilon * self._candidate_scores[r]/(4.0 * self._SS))
+			temp = math.exp(eps * self._candidate_scores[r]/(4.0 * self._SS))
 			self._SS_probabilities.append(temp)
 			nomalizer += temp
 

### 2020-03-19 codes/sampling_on_betabinomial_bayesinfer.py

@@ -73,7 +73,7 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	mean_error = [[],[],[],[],[],[]]
 	for i in range(len(datasizes)):
 		observation = observations[i]
-		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta)
+		Bayesian_Model = BayesInferwithDirPrior(prior, sum(observation), epsilon, delta, 0.2)
 		Bayesian_Model._set_observation(observation)
 		print("start" + str(observation))
 		Bayesian_Model._experiments(500)
@@ -93,13 +93,13 @@ def accuracy_VS_datasize(epsilon,delta,prior,observations,datasizes):
 	print('Accuracy / prior: ' + str(prior._alphas) + ", delta: " 
 		+ str(delta) + ", epsilon:" + str(epsilon))
 
-	print mean_error
+	# print mean_error
 
 	plot_mean_error(datasizes, mean_error, datasizes, 
 		"Different Datasizes", 
 		[r"$\mathsf{LSDim}$",
 		r"$\mathsf{LSHist}$",
-		r"$\mathsf{LSDimNa}$",
+		r"$\mathsf{LSZhang}$",
 		r"$\mathsf{EHDS}$",
 		r"$\mathsf{EHD}$",
 		r"$\mathsf{EHDL}$"], "")
@@ -211,6 +211,34 @@ def accuracy_VS_prior_mean(sample_size,epsilon,delta,priors,observations):
 
 	return
 	
+
+
+def accuracy_VS_gamma(epsilon,prior, data, gammas):
+	mean_error = [[]]
+	for g in gammas:
+		Bayesian_Model = BayesInferwithDirPrior(prior, sum(data), epsilon, 0.1, g)
+		Bayesian_Model._set_observation(data)
+		print("start" + str(g))
+		Bayesian_Model._experiments(1000)
+		print("finished" + str(g))
+
+		mean_error[0].append(Bayesian_Model._accuracy_mean[Bayesian_Model._keys[3]])
+
+
+	print('Accuracy / prior: ' + str(prior._alphas) + ", delta: " 
+		+ str(delta) + ", epsilon:" + str(epsilon))
+
+	# print mean_error
+
+	plot_mean_error(gammas, mean_error, gammas, 
+		"Different Gammas for Smooth Sensitivity", 
+		[r"$\mathsf{EHDS}$"], "")
+	
[…]

### 2020-03-19 codes/theory_prob.py

@@ -94,8 +94,6 @@ def exp_distribution_over_candidates(dataobs, prior, epsilon, mech):
 	if mech == "exp":
 		Bayesian_Model._set_up_exp_mech_with_GS()
 	elif mech == "gamma":
-		Bayesian_Model._gamma = 0.25
-		Bayesian_Model._epsilon = epsilon * 8.0/5
 		Bayesian_Model._set_up_exp_mech_with_gamma_SS()
 
 	exp_prob = {}
@@ -112,19 +110,51 @@ def exp_distribution_over_candidates(dataobs, prior, epsilon, mech):
 	
 	return exp_prob
 
-
-
-def get_steps(dataobs, prior, epsilon):
+def exp_smooth_theoryProb(dataobs, prior, epsilon, gamma):
 	n = sum(dataobs)
-	# Bayesian_Model = BayesInferwithDirPrior(prior, n, epsilon)
-	# Bayesian_Model._set_observation(dataobs)
+	Bayesian_Model = BayesInferwithDirPrior(prior, n, epsilon, 0.1, gamma)
+	Bayesian_Model._set_observation(dataobs)
 
-	# Bayesian_Model._set_candidate_scores()
+	Bayesian_Model._set_candidate_scores()
+	Bayesian_Model._set_local_sensitivities()
+	Bayesian_Model._gamma = gamma
+	Bayesian_Model._set_up_exp_mech_with_gamma_SS()
 
-	# cpara = []
-	# for c in Bayesian_Model._candidates:
-	# 	cpara.append(str(c._minus(prior)._alphas))
+	exp_prob = {}
+
+	for i in range(len(Bayesian_Model._candidates)):
+		z = Bayesian_Model._candidates[i]._pointwise_sub(prior)
+		exp_prob[list2key(z._alphas)] = Bayesian_Model._gamma_SS_probabilities[i]
 	
+	return exp_prob
+
+
+def exp_distribution_vs_gammas(dataobs, prior, epsilon, gammas):
+	probs = []
+	# keys = get_steps_opt(dataobs, prior, epsilon)
+	for g in gammas:
+		probdict = exp_smooth_theoryProb(dataobs, prior, epsilon, g)
+		probs.append(probdict)
+		print g, probs
+		# prob = list_of_map(keys, probdict)
+		# probs.append((keys, prob))
+	
+	return probs
+
[…]

### 2020-03-23 codes/theory_prob.py
update bounds

@@ -188,7 +188,7 @@ def plot_2d(y, xstick, labels, title):
 				y_.append(y[i][j])
 				x_.append(x[j])
 		plt.plot(x_, y_, "o-", label=labels[i])
-	plt.xlabel(r"different dataset: $[k, n- k]$")
+	plt.xlabel(r"different dataset")
 	plt.xticks(x, xstick,rotation=70,fontsize=6)
 	plt.title(title)
 	plt.legend(loc='best',fontsize=6)
@@ -222,18 +222,18 @@ if __name__ == "__main__":
 	gammas = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
 	# datasizes = gen_datasizes((50, 200), 50)
 
-	# lap_prob = lap_distribution_over_candidates(dataobs, prior, epsilon, 1.0)
-	# lap_prob_2 = lap_distribution_over_candidates(dataobs, prior, epsilon, 2.0)
-	# exp_prob = exp_distribution_over_candidates(dataobs, prior, epsilon, "exp")
-	# exp_prob2 = exp_distribution_over_candidates(dataobs, prior, epsilon, "gamma")
-	# lap3 = lap_distribution_over_candidates_naive(dataobs, prior, epsilon)
-	# steps = get_steps_full(dataobs, prior, epsilon)
+	lap_prob = lap_distribution_over_candidates(dataobs, prior, epsilon, 1.0)
+	lap_prob_2 = lap_distribution_over_candidates(dataobs, prior, epsilon, 2.0)
+	exp_prob = exp_distribution_over_candidates(dataobs, prior, epsilon, "exp")
+	exp_prob2 = exp_distribution_over_candidates(dataobs, prior, epsilon, "gamma")
+	lap3 = lap_distribution_over_candidates_naive(dataobs, prior, epsilon)
+	steps = get_steps_full(dataobs, prior, epsilon)
 
-	# plot_2d(list_of_map(steps, [lap_prob, lap_prob_2, lap3, exp_prob, exp_prob2]),
-	# 	steps, [r"$\mathsf{LSHist}$", r"$\mathsf{LSDim}$", r"$\mathsf{LSDimNa}$", r"$\mathsf{EHD}$", r"$\mathsf{EHDS}$"], "prob of each candidates with data: "+str(dataobs)+", eps: " + str(epsilon))
[…]

### 2020-05-11 ICML2019/main.tex
updates

@@
 If $\nu\geq \frac{\Delta_f}{\epsilon}$, with $\Delta_f=\displaystyle\max_{d,d':\adj{d}{d'}}{\lvert f(d_1)-f(d_2)\lvert}$
-then the mechanism is $\epsilon$-differentially private as proven in \cite{???}.
+then the mechanism is $\epsilon$-differentially private as proven in \cite{Zhang2017privbayes}
 

### 2020-05-11 codes/sampling_on_betabinomial_bayesinfer.py

@@ -273,10 +273,10 @@ if __name__ == "__main__":
 #SETTING UP THE PARAMETERS WHEN DOING GROUPS EXPERIMENTS
 #############################################################################
 	epsilons = numpy.arange(5, 2, 0.1)
-	datasizes = gen_datasizes((10,50),10) + gen_datasizes((100,500),100)# + gen_datasizes((600,1000),200) + gen_datasizes((1000,5000),1000)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
+	datasizes = gen_datasizes((10,50),10) + gen_datasizes((100,500),100) + gen_datasizes((600,1000),200)# + gen_datasizes((1000,5000),1000)#[300] #[8,12,18,24,30,36,42,44,46,48]#,50,52,54,56,58,60,62,64,66,68,70,72,74,76,78,80]
 	percentage = [0.5,0.5]
 	datasets = gen_datasets(percentage, datasizes)
-	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2)# + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)
+	priors = gen_priors([20,50], 10, 2) + gen_priors([100,200], 50, 2) + gen_priors([200,500], 100, 2) + gen_priors([600,2000], 200, 2)
 	
 	gammas = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
 

### 2020-05-11 codes/theory_prob.py

@@ -218,7 +218,7 @@ if __name__ == "__main__":
 	epsilon = 1.0
 	delta = 0.00000001
 	prior = dirichlet([1,1])
-	dataobs = [3, 3]
+	dataobs = [4, 4]
 	gammas = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
 	# datasizes = gen_datasizes((50, 200), 50)
 
